### 2013-04-14 doc/p3p.tex
initial commit

\documentclass[12pt]{article}
\usepackage{amsmath}

\begin{document}
\title{Comments on the period three cycle}
\author{Cheng Zhang}
\maketitle

In this note, we shall
  find the bifurcation point of the period-3 cycle,
  and show the orbit is real after the onset.

\section{The bifurcation point}
Due to heavier algebra, we shall work with simplified map
\[
x_{n+1} = f(x_n) = R - {x_n}^2,
\]
and $a$, $b$ and $c$ denote three successive points in the period-3 orbit,
$b=f(a), c=f(b), a=f(c)$.
For $X \equiv a + b + c$, we have
\begin{align}
X^2 - X + 2 - R = 0.
\label{eq:xr}
\end{align}
%
Now
\begin{align}
 Y \equiv a b + b c + c a
= \frac{1}{2} [ (a + b + c)^2 - (a^2 + b^2 + c^2) ]
= X - R - 1,
\label{eq:y}
\end{align}
where we have used $(a^2 + b^2 + c^2) = 3R - (a+b+c)$ and \eqref{eq:xr}.

Similarly, we express $Z \equiv abc$ in terms of $X$ by
\begin{align}
  a^3 + b^3 + c^3 - 3 a b c =
 (a + b + c) (a^2 + b^2 + c^2 - a b - b c - c a)
\label{eq:pow3}
\end{align}
For the left hand side, we have $a^2 = R - b$, so $a^3 = R a - ab$, and
\begin{align}
  a^3 +b^3 + c^3
= R (a+b+c) - (ab+bc+ca)
= (R - 1) X + R + 1.
\label{eq:pow3a}
\end{align}
%
For the right hand side,
\begin{align}
& (a + b + c) (a^2 + b^2 + c^2 - a b - b c - c a)
= X [X^2 - 3(ab + bc + ca)] \notag\\
=& X (-2X + 4R + 1)
= (4R-1) X -2(R-2).
\label{eq:pow3b}
\end{align}
Plugging \eqref{eq:pow3a} and \eqref{eq:pow3b} to \eqref{eq:pow3}, we have
\begin{equation}
Z \equiv abc = -RX + R - 1.
\label{eq:abc}
\end{equation}
Solving \eqref{eq:abc} yields $X = 1 + (1+Z)/R$.
Plugging it into \eqref{eq:xr} yields
\begin{equation}
  R^3 - 2R^2 + (1+Z)R + (1+Z)^2 = 0.
\end{equation}

At the onset point $(-2a)(-2b)(-2c) = 1$, or $Z = -1/8$, we have
\[
  (R-7/4) (R^2 - R/4 + 7/16) = 0.
\]
The only real solution is $R = 7/4$, so $r = 1+\sqrt{1+4R} = 1+ \sqrt 8$.

At the bifurcation point $(-2a)(-2b)(-2c) = -1$, or $Z = 1/8$, we have
\[
  R^3 - 2 R^2 + 9R/8 - 81/64 = 0.
\]
The only real solution is
$
R = \frac{2}{3}
  +\frac{1}{4} \sqrt[3]{ \frac{1915}{54} + \frac{5}{2} \sqrt{201}}
  +\frac{1}{4} \sqrt[3]{ \frac{1915}{54} - \frac{5}{2} \sqrt{201}}.
$

\section{The existence of the real orbit}

Next we show that the orbit is real after the onset, i.e., $R>7/4$.
By definition $a$, $b$ and $c$ are solutions of
\[
  q^3 - X q^2 + Y q - Z = 0.
\]
The discriminant is
\[
\Delta = X^2 Y^2 - 4 Y^3 - 4 X^3 Z + 18 X Y Z - 27 Z^2
  = (4X^2 - 6X + 9)^2,
\]
where we have used \eqref{eq:y} and \eqref{eq:abc},
and eliminated $R$ by \eqref{eq:xr}.
Thus as long as $X$ is real, $\Delta > 0$, which means there are always three
real solutions.

\end{document}

### 2013-04-14 doc/pc-ijbc.tex
initial commit

\documentclass{ws-ijbc}
\usepackage{multirow}
\usepackage{centernot}
%\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{calc}
\usepackage{cancel} % strike out (cancel) in math mode
\usepackage{ws-rotating}
\begin{document}

\newcommand{\odd}{\mathrm{odd}}

% bold font for vectors
\newcommand{\vct}[1]{\mathbf{#1}}
% the cycle and sum operator
%\newcommand{\C}{\mathcal{C}}

% center column in tabularx
\newcolumntype{C}{>{\centering\arraybackslash}X}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}

\newcommand{\vx}{\vct x}
\newcommand{\Bset}{\mathcal B}
\newcommand{\NB}{N_\Bset}
\newcommand{\RX}{(R, \lambda)}

%\newcommand{\eq}{}
%\newcommand{\eqs}{}
\newcommand{\eq}{Eq.}
\newcommand{\eqs}{Eqs.}
\newcommand{\req}[1]{(\ref{eq:#1})}
\newcommand{\refeq}[1]{\eq\,\req{#1}}
\newcommand{\refeqs}[1]{\eqs\,\req{#1}}
\newcommand{\reqsub}[2]{(\ref{eq:#1}#2)}
\newcommand{\refeqsub}[2]{\eq\,\reqsub{#1}{#2}}
\newcommand{\refeqssub}[2]{\eqs\,\reqsub{#1}{#2}}

\newcommand{\refthm}[1]{Theorem \ref{thm:#1}}
\newcommand{\refthms}[1]{Theorems \ref{thm:#1}}
\newcommand{\refsec}[1]{Section \ref{sec:#1}}
\newcommand{\refsecs}[1]{Sections \ref{sec:#1}}
\newcommand{\refapd}[1]{Appendix \ref{apd:#1}}
\newcommand{\reftab}[1]{Table \ref{tab:#1}}
\newcommand{\reftabs}[1]{Tables \ref{tab:#1}}
\newcommand{\reffig}[1]{Fig. \ref{fig:#1}}
\newcommand{\reffigs}[1]{Figs. \ref{fig:#1}}

% ws-ijbc doesn't like the following lines
%\newtheorem{theorem}{Theorem}
%\newenvironment{remark}[1][1]%
%{\par\noindent\textbf{Remark #1.} }{\medskip}

\catchline{}{}{}{}{}

\title{Cycles of the logistic map}
\author{Cheng Zhang}
%\affiliation{Applied Physics Program and Department of Bioengineering, \
%Rice University, Houston, TX 77005}
\address{Applied Physics Program \& Department of Bioengineering,
Rice University, Houston, TX 77005, USA}

\maketitle

\begin{history}
\received{}
\end{history}

\begin{abstract}
%\abstract{
%
The onset and bifurcation points of the $n$-cycles of
  a polynomial map are located
  through a characteristic equation
  connecting cyclic polynomials formed by periodic orbit points.
The minimal polynomials of the critical parameters
  of the logistic, H\'enon, and cubic maps are obtained
  for $n$ up to 13, 9, and 8,
  respectively.
%
%}
\end{abstract}

\keywords{Logistic map; H\'enon map; cubic map; cycles; exact polynomials.}

%\maketitle

%
%
\section{Introduction}
%
%

Consider the logistic map \cite{may, strogatz}:
%
\begin{equation}
  x_{k+1} = f(x_k) \equiv r \, x_k \, ( 1 - x_k ).
\label{eq:logmap}
\end{equation}
%
If we iterate \refeq{logmap} from $k = 0$,
what does the resulting sequence $x_0$,
  $x_1 = f(x_0)$,
  $x_2 = f(x_1)$, $\ldots$ look like?
%
%
%
We can visualize the sequence on the cobweb plot,
  see \reffig{cobweb} for examples.
%
Starting from $(x_0, x_0)$ on the diagonal,
  each vertical arrow takes $(x_k, x_k)$ to $(x_k, y)$,
  where $y = f(x_k) = x_{k+1}$;
the next horizontal arrow then reflects $(x_k, y)$ to
  $(y, y) = (x_{k+1}, x_{k+1})$,
  which starts the next iteration.

\begin{figure}[h]
  \begin{minipage}{\linewidth}
    \begin{center}
        \includegraphics[angle=-90, width=\linewidth]{cobweb.pdf}
    \end{center}
  \end{minipage}%
  \caption{\label{fig:cobweb}
  Cobweb plot of the logistic map.}
\end{figure}

Three outcomes are possible:
  (i) a \emph{fixed point},
      which is a constant (including infinity),
      e.g., \reffig{cobweb}(a);
  (ii) a periodic \emph{cycle},
      which is a self-repeating pattern,
      e.g., \reffigs{cobweb}(b)-(e);
%On the cobweb plot, an $n$-cycle is a loop of $2n$ segments.
or
  (iii) a chaotic trajectory,
      e.g., \reffig{cobweb}(f).
We will focus on the first two cases here.

A fixed point is a solution of $x^* = f(x^*)$.
%
If $x_0$ deviates slightly from $x^*$
  and the sequence still converges to $x^*$,
  we call it \emph{stable}.
%
For a differentiable $f$,
  a stable fixed point requires $|f'(x^*)| \le 1$
  to reduce deviations in successive iterations \cite{strogatz}.

In an $n$-cycle, $n$ is the smallest positive integer
  that allows $x_1 = x_{n+1} = f^n(x_1)$,
  where $f^n$ is the $n$th iterate of $f$,
  e.g., $f^3(x) = f(f(f(x)))$.
Thus, any $x_k$ in an $n$-cycle of $f$ must be a fixed point of $f^n$
%
\big[the reverse is, however, untrue, for a fixed point of $f^n$
  can also be a fixed point of $f^d$ as long as $d|n$:
  if $f^d(x) = x$, then $f^n(x) = f^d(\cdots f^d(x)\cdots) = x$\big].
%
%
We can therefore classify a cycle as stable or unstable
  by the corresponding fixed point of $f^n$:
  a stable cycle requires
  $\big| \frac {d} {dx} f^n(x_1) \big| \le 1$,
  or by the chain rule,
%
%
%
\begin{equation}
  \Big| f'(x_1) \dots f'(x_n) \Big| \le 1,
\label{eq:der}
\end{equation}
where $x_1. \ldots, x_n$ are the $n$ points within the cycle, or the orbit.
Further, the onset and bifurcation points
  are defined at the loci
  where $\frac {d} {dx} f^n(x_1)$ reaches $+1$ and $-1$,
  respectively \cite{strogatz}.
%
%
%

The outcome of the iterated sequence of course
  depends on the parameter $r$.
%
Below we will present an algorithm to identify
  all regions of $r$ that allow stable $n$-cycles.
%We ask,
%  by which $r$ values can a stable $n$-cycle exist?
%

\section{\label{sec:logmap}Logistic map}

We will illustrate the algorithm on the logistic map \cite{may, strogatz},
  defined in \refeq{logmap}.
If $r$ is real,
  we will find windows $(r_a, r_b)$,
    within which stable $n$-cycles can exist.
%
%The window boundaries can be classified
%  to onset and bifurcation points according to \refeq{der};
Here, if $r > 0$, then
  $r_a$ ($r_b$) are the onset (bifurcation) points.
%
There are generally multiple such windows even for a single $n$,
but all onset points satisfy the same polynomial equation,
  and all bifurcation points another.
%
Our goal is thus to find the two polynomials for a given $n$.

To simplify the calculation, we first change variables \cite{saha} by
%
%\begin{equation}
\[
    x^{(\mathrm{new})} \leftarrow r(x^{(\mathrm{old})} - 1/2),
    \quad R \leftarrow r(r-2)/4,
\]
%\label{eq:chvars}
%\end{equation}
%
and rewrite the map, in terms of $x^{(\mathrm{new})}$, as
%
\begin{equation}
  x_{k+1} = f(x_k) \equiv R - {x_k}^2.
  %\tag{$\ref{eq:logmap}'$}
\label{eq:logmaps}
\end{equation}
%
%\refeq{logmaps} simplifies \refeq{logmap} as $x_k$ now only occurs once.
%
We will solve the cycle boundaries as zeros of the polynomials of $R$,
and the corresponding polynomials for $r$ can be obtained by $R \rightarrow r(r-2)/4$.
%
%the numerical $r$ values can always be obtained from $r = 1 + \sqrt{1 + 4R}$.
%

\subsection{Overall plan}

We solve the problem in two steps.
Since the $n$-cycles form a subset of the fixed points of $f^n$,
we will first find
  the polynomials at the stability boundaries of
  the fixed points of $f^n$
  (\refsecs{cyclic} to \ref{sec:examples}),
then remove contributions from shorter $d$-cycles ($d|n$)
  (\refsecs{primfac} and \ref{sec:degprimfac}).

Let us consider the first step of finding the fixed points of $f^n$.
At the first glance, the problem can be tackled by brute force:
  we can solve
  %the $n$ equations
  \refeqs{logmaps} and express $x_1, \ldots, x_n$
  in terms of $R$,
  and then plug the solution into \req{der}.
The result contains $R$ only (no $x_k$),
  and is therefore the answer.
But since \refeqs{logmaps} are nonlinear,
  it quickly becomes impossible for $n > 2$,
  as the degree of polynomials grows exponentially;
  thus it is nontrivial to reduce the final equation of $R$
  into a polynomial one.
Nonetheless, on a computer, one can
  construct a Gr\"obner basis \cite{kk1}
  to automate the reduction.
%
The approach, albeit straightforward, does not
  exploit the cyclic structure of \refeqs{logmaps},
can thus be improved by the following alternative.

Instead of solving \refeqs{logmaps} for $x_k$,
  we will derive a set of \emph{homogeneous linear} equations
  of cyclic polynomials of $x_k$
  (an example of a cyclic polynomial is $x_1 x_2 + x_2 x_3 + \dots + x_n x_1$).
%
%We know then that
  Now the matrix formed by the coefficients of the homogeneous linear equations
  must have a zero determinant,
  for the cyclic polynomials are not zeros altogether.
%
%As the coefficients are polynomials of $R$ only,
Thus, the zero-determinant condition gives
  the needed polynomial equations of $R$,
whose roots contain all fixed points of $f^n$.
This completes the first step.
%
%Note that we will obtain different equations
%  at the onset and bifurcation points
%  because the coefficients,
%  hence the matrices and determinants,
%  will be different.
%

For the second step,
we show
that short cycles serve as
factors in the polynomials obtained above,
and thus can be readily factored out.

\subsection{\label{sec:cyclic}Cyclic polynomials}

A polynomial is cyclic if it is invariant
  under the cycling of variables
  $x_1 \rightarrow x_2, x_2 \rightarrow x_3,
  \ldots, x_n \rightarrow x_1$,
  e.g., $a(\vx) = x_1 x_2 + x_2 x_3 + x_3 x_4 + x_4 x_1$
  and $b(\vx) = x_1 x_3 + x_2 x_4$,
  for $n = 4$, where $\vx \equiv \{x_1, \ldots, x_n\}$.
A cyclic polynomial should not to be confused with a symmetric polynomial,
  which is invariant under the exchange of any two $x_k$ and $x_{j}$ ($j \ne k$);
  e.g., $a(\vx)$ and $b(\vx)$ are not symmetric,
  but $a(\vx) + b(\vx)$ is.

A cyclic polynomial can be generated by summing over
  distinct cyclic versions of a simpler polynomial of $x_k$, or a \emph{generator},
e.g.,
$x_1 x_2$ is a generator of $a(\vx)$;
$x_1 x_3$ is that of $b(\vx)$;
and
$x_1 x_2 + \frac{1}{2} x_1 x_3$ is that of $a(\vx) + b(\vx)$;
note that the coefficient before $x_1 x_3$
  is 1 in the second case
  for there are only two distinct versions,
  but is $\frac{1}{2}$ in the third case
  for there are four. % distinct versions of the generator.

We now consider cyclic polynomials
  generated from a monomial of unit coefficient,
  such as $a(\vx)$ and $b(\vx)$, but not $a(\vx) + b(\vx)$.
They can be systematically labeled as follows.
We pick the monomial generator,
  which can be written as
  ${x_1}^{e_1} {x_2}^{e_2} \dots {x_n}^{e_n}$,
  then form a sequence $p$ of indices with
  $e_1$ 1's, $e_2$ 2's, \ldots, $e_n$ $n$'s;
  the corresponding cyclic polynomial is denoted by $C_p(\vx)$,
e.g.,
  $C_{12}(\vx)  = x_1 x_2 + x_2 x_3 + \dots + x_n x_1$ and
  $C_{112}(\vx) = {x_1}^2 x_2 + {x_2}^2 x_3 + \dots + {x_n}^2 x_1$.
We omit the length $n$ in this notation,
  for we will mostly work with a fixed $n$ at a time.
Since a cyclic polynomial can have multiple generators,
  e.g., both $x_1 x_2$ and $x_2 x_3$ are generators of $C_{12}(\vx)$
   (assuming $n \ge 3$),
  we pick the one that corresponds to
  the smallest $p$
  in the sense of lexicographic order,
  e.g., we choose $x_1 x_2$ instead of $x_2 x_3$ for $C_{12}(\vx)$,
  because $12 < 23$.
Finally, we add $C_0(\vx) \equiv 1$ for completeness.
%
%
%

\subsection{Square-free cyclic polynomials}

We further restrict ourselves to
  a subset of square-free cyclic polynomials,
  which have no square or higher powers of any $x_k$,
  e.g., $C_{12}(\vx) = x_1 x_2 + \dots$ is square-free,
  $C_{112}(\vx) = {x_1}^2 x_2 + \dots$ is not,
see \reftab{sqrfreepoly} for more examples.
Obviously, the label $p$ of a square-free polynomial
  has no repeated index.
We denote the set of all square-free $p$ by
$\Bset = \{0, 1, 12, 13, \ldots, 123, 124, \ldots, 12\dots n\}$
%  ($n \ge 4$),
such that its size $|\Bset|$ equals the number $\NB$ of
  square-free cyclic polynomials.

\begin{table}[h]\footnotesize
\tbl{
Square-free cyclic polynomials $C_p(\vx)$ for the logistic map ($n \ge 5$).}
%\begin{center}
{
\begin{tabular}{c c c c c}
\hline
$p$ & $C_p(\vx)$ & Generator$^\dagger$ & Necklace$^\ddagger$ & $p$ as an index set$^*$\\
\hline
0             & 1 & 1 & $0\ldots0$ & $\emptyset$ \\
1             & $x_1 + x_2 + \dots + x_n$
              & $x_1$ (or $x_2$, \ldots)
              & $10\ldots0$
              & $\{1\}$ (or $\{2\}$, \ldots) \\
12            & $x_1 x_2 + x_2 x_3 + \dots + x_n x_1$
              & $x_1 x_2$ (or $x_2 x_3$, \ldots)
              & $110\ldots0$
              & $\{1, 2\}$ (or $\{2, 3\}$, \ldots) \\
13            & $x_1 x_3 + x_2 x_4 + \dots + x_n x_2$
              & $x_1 x_3$ (or $x_2 x_4$, \ldots)
              & $1010\ldots0$
              & $\{1, 3\}$ (or $\{2, 4\}$, \ldots) \\
$\vdots$      & $\vdots$ \\
123           & \hspace{1mm}$x_1 x_2 x_3 + x_2 x_3 x_4 + \dots + x_n x_1 x_2$\hspace{1mm}
              & \hspace{1mm}$x_1 x_2 x_3$ (or $x_2 x_3 x_4$, \ldots)\hspace{1mm}
              & $1110\ldots0$
              & $\{1, 2, 3\}$ (or $\{2, 3, 4\}$, \ldots) \\
124           & $x_1 x_2 x_4 + x_2 x_3 x_5 + \dots + x_n x_1 x_3$
              & $x_1 x_2 x_4$ (or $x_2 x_3 x_5$, \ldots)
              & $11010\ldots0$
              & $\{1, 2, 4\}$ (or $\{2, 3, 4\}$, \ldots) \\
$\vdots$      & $\vdots$ \\
$12\dots n$  & $x_1 x_2 \dots x_n$
              & $x_1 x_2 \dots x_n$
              & $11\ldots1$
              & $\{1, 2, \ldots, n\}$  \\
\hline
\multicolumn{5}{p{\linewidth}}{
$^\dagger$ Alternative generators are shown in parentheses.
}\\
\multicolumn{5}{p{\linewidth}}{
$^\ddagger$ The corresponding binary necklaces.
}\\
\multicolumn{5}{p{\linewidth}}{
$^*$ The label $p$ of a square-free cyclic polynomial
    has no repeated indices;
    so the indices can be cast to a set.
}\\
\hline
\end{tabular}
\label{tab:sqrfreepoly}
}
%\end{center}
\end{table}

We first show that
  the square-free cyclic polynomials
  serve as a basis for expanding cyclic polynomials:

\begin{theorem}
  For the logistic map \refeq{logmaps},
  any cyclic polynomial $K(\vx)$
  formed by the $n$-cycle points
  $\vct x = \{x_1, \ldots, x_n\}$
  is a linear combination of
the square-free cyclic polynomials $C_p(\vx)$:
\[
  K(\vx) = \sum_{p \in \Bset} f_p(R) \, C_p(\vx),
\]
  where $\Bset = \{0, 1, 12, 13, \ldots, 12\dots n\}$ is
  the set of indices of all square-free cyclic polynomials,
  and $f_p(R)$ are polynomials of $R$.
  \label{thm:sqrfree}
\end{theorem}

\begin{proof}
We show the theorem by the following square-free reduction.
%
Given a cyclic polynomial $K(\vx)$,
  we recursively apply \refeq{logmaps} as
  $x_k^2 \rightarrow R - x_{k+1}$,
  until all squares or higher powers of $x_k$ are eliminated.
The process will not last indefinitely
  for each substitution reduces the degree in $x_k$ (no matter which $k$)
  by one.
Since the original polynomial is cyclic,
  so is the reduced one.
All terms that involve no $x_k$
  are collected to serve as the coefficient before $C_0(\vx)$, which is 1.
Since no square or higher powers of $x_k$
  can survive the reduction,
  all cyclic polynomials in the final result
  are square-free.
The coefficients are polynomials of $R$,
  for $R$ is the only variable introduced by the substitutions.
\end{proof}

For example, for $n = 2$, the cyclic polynomial
  $K(\vx) = {x_1}^2 \, x_2 + {x_2}^2 \, x_1$
can be written as $K(\vx) = (R + 1) \, C_{1}(\vx) - 2 R \, C_0(\vx)$
for
${x_1}^2 \, x_2 = R \, x_2 - {x_2}^2 = R \, x_2 - R + x_1$ and
${x_2}^2 \, x_1 = R \, x_1 - R + x_2$.

\refthm{sqrfree}
  shows that any cyclic polynomial
  can be expanded
  as a combination of the square-free ones,
  which serve as a basis.
Below we show that at the onset and bifurcation points,
  the square-free cyclic polynomials $C_p(\vx)$ are themselves
  linearly connected by an $\NB \times \NB$ matrix equation.
The determinant of matrix must vanish,
  and this condition yields the solution of the problem.

\subsection{\label{sec:algo}Algorithm for fixed points of $f^n$}

We first observe that the derivative of $f^n$
is a cyclic polynomial:
%
\begin{equation}
  \Lambda(\vx)
   = \frac{d}{dx}f^{n}(x_1)
   = f'(x_n) \dots f'(x_1)
   = (-2)^n x_1 \dots x_n.
\label{eq:logder}
\end{equation}

Now, for any $p$, $\Lambda(\vx) \, C_p(\vx)$
  is also a cyclic polynomial,
since the product of two cyclic polynomials is cyclic too.
We can therefore expand it by \refthm{sqrfree} as
\begin{equation}
  \Lambda(\vx) \, C_p(\vx) = \sum_{q \in \Bset} T_{pq}(R) \, C_q(\vx),
\label{eq:xcp0}
\end{equation}
where $T_{pq}(R)$ is a polynomial of $R$,
and $p, q \in \Bset$.

By \refeq{der}, at the onset or bifurcation point,
  $\Lambda(\vx)$ is equal to a number
  $\lambda = +1$ or $-1$, respectively;
  so \refeq{xcp0}
  becomes a homogeneous linear equation of
  $C_p(\vx)$:
\begin{equation}
  \lambda \, C_p(\vx) = \sum_{q \in \Bset} T_{pq}(R) \, C_q(\vx),
\label{eq:xcp}
\end{equation}
%
%
%where $\lambda$ is $+1$ and $-1$ at the onset and bifurcation points, respectively;
or in matrix form,
\begin{equation}
  \big[ \lambda \, \vct I - \vct T(R) \big] \, \vct C = 0,
\tag{\ref{eq:xcp}'}
\end{equation}
%
%
where
$\vct I$ is the $\NB \times \NB$ identity matrix,
$\vct T(R) = \{T_{pq}(R)\}$ is an $\NB \times \NB$ matrix,
and
$\vct C = \{C_p(\vx)\}$ is an $\NB$-dimensional column vector.

Since a set of homogeneous linear equations
  has a non-trivial solution
  only if the determinant of the coefficient matrix
  is zero, we have
\begin{equation}
  A_n\RX \equiv \big| \lambda \, \vct I - \vct T(R) \big| = 0.
\label{eq:xr}
\end{equation}
Here we have defined $A_n\RX$ as a polynomial of $R$ and $\lambda$,
  and we have also attached the subscript $n$,
  for later use with $A_d\RX$, where $d$ are divisors of $n$.
\refeq{xr} is a necessary condition
  since $C_p(\vx)$ cannot vanish altogether;
and since it involves $R$ only,
  the polynomial expansion of the determinant
  gives the answer to our problem.
%Note that we did not solve the values $C_p$ in the process.

To summarize, we have
\begin{theorem}
  At the onset and bifurcation points,
  the square-free cyclic polynomials $C_p(\vx)$
  are linear related by \refeq{xcp}, with
  $\lambda$ being $+1$ and $-1$, respectively,
  and $T_{pq}(R)$ the coefficients
  from the square-free reduction of $\Lambda(\vx) \, C_p(\vx)$
  with $\Lambda(\vx)$ specified by \refeq{logder}.
  Thus, $R$ at the two points are the roots of the
  polynomials $A_n(R, \lambda = \pm1)$
  obtained from the characteristic equation \refeq{xr}.
  \label{thm:main}
\end{theorem}

\begin{remark}
%\begin{remark}[1]
  For complex $R$ and $\vx$,
  $\lambda$ should be generalized from $\pm1$
  to any $\lambda = \exp(i\phi)$,
  where $\phi \in [0, 2\pi]$,
  the algorithm still applies.
  By increasing $\phi$ from 0 to $2\pi$,
  we can trace a two-dimensional region of a complex $R$
  for stable cycles.
  These regions are bulbs in the Mandelbrot set,
  %(however, we need the replacement
  %$x_k \rightarrow -z_k$
  %and
  %$R \rightarrow -c$)
  see ref. \cite{stephenson} and \reffig{logbulb}.

  Further, with $\lambda = 0$,
  the algorithm determines the superstable point,
  at which the deviation from a cycle point vanishes
  to the linear order after $n$ iterations of $f$.
  But we have a better algorithm in this case:
  since at least one of the $x_k$ is zero by \refeq{logder},
  then $f^n(x_k = 0) = x_{n+k} = 0$ provides
  the needed polynomial equation of $R$ \cite{strogatz}.
\end{remark}

\subsection{\label{sec:examples}Examples}

We illustrate the above algorithm by cases of small $n$.
%
It is still helpful to have a mathematical software verify some steps
  (e.g., in computing the determinants and their factorization).

For $n = 1$, we have two square-free cyclic polynomials
  $C_0(\vx) = 1$ and $C_1(\vx) = x_1$;
  and $\Lambda(\vx) = -2 \, x_1$
\big[we shall drop ``$(\vx)$'' below for convenience\big].
Thus $\Lambda \, C_0 = -2 \, x_1 = -2 \, C_1$,
$\Lambda \, C_1 = -2 \, x_1^2 = -2 \, R + 2 x_1 = -2 \, R \, C_0 + 2 \, C_1$,
or
\[
  \lambda
  \left( \begin{array}{c}
  C_0 \\
  C_1
  \end{array} \right)
  =
  \left( \begin{array}{cc}
  0     & -2 \\
  -2R   &  2
  \end{array}\right)
  \left( \begin{array}{c}
  C_0 \\
  C_1
  \end{array} \right),
\]
and \refeq{xr} reads
\begin{equation}
0=  \left| \begin{array}{cc}
  \lambda     & 2          \\
  2 R         & \lambda - 2
  \end{array} \right| = -4R - 2\lambda + \lambda^2,
  \tag{\ref{eq:xr}-1}
\label{eq:xr1}
\end{equation}
which is just the equation for a fixed point.
The fixed point begins at $\lambda = +1$ or $R_a = -1/4$,
  and becomes impossible when $\lambda = -1$, or $R_b = 3/4$.

For $n = 2$, the cyclic variables are
$C_0 = 1$,
$C_1 = x_1 + x_2$,
$C_{12} = x_1 x_2$,
and $\Lambda = 4 x_1 x_2$.
Thus,
$\Lambda \, C_0 = 4 C_{12}$,
$\Lambda \, C_1 = 4 \, {x_1}^2 \, x_2 + 4 \, x_1 \, {x_2}^2
  = 4 \, R \, (x_1 + x_2) - 4 ({x_1}^2 + {x_2}^2)
  = 4 \, R \, (x_1 + x_2) - 8 \, R + 4 \, (x_1 + x_2)
  = 4 \, (R + 1) \, C_1 - 8 \, R \, C_0$,
$\Lambda \, C_{12}
  = 4 \, (R-x_2)\, (R-x_1)
  = 4\, R^2  \, C_0 - 4 \, R \, C_1 + 4 \, C_{12}$,
or
\[
\lambda
  \left( \begin{array}{c}
  C_0 \\
  C_1 \\
  C_{12}
  \end{array} \right)
 =
  \left( \begin{array}{ccc}
  0           & 0         & 4 \\
  -8R         & 4(R+1)    & 0 \\
  4R^2        & -4R       & 4
  \end{array} \right)
  \left( \begin{array}{c}
  C_0 \\
  C_1 \\
  C_{12}
  \end{array} \right),
\]
%
%
%
and \refeq{xr} reads
%
%
%
\begin{align}
0 &=
  \left| \begin{array}{ccc}
  \lambda     & 0               & -4 \\
  8R          & \lambda-4(R+1)  & 0 \\
  -4R^2       & 4R              & \lambda-4
  \end{array} \right| \nonumber\\
  &= (4R - 4 + \lambda) [(4 R-\lambda)^2 - 4 \lambda].
  \tag{\ref{eq:xr}-2}
\label{eq:xr2}
\end{align}
%
%
%
We only use the first factor
(the choice will be explained later, same for the following cases).
%
Setting it to zero yields $R = 1 - \lambda/4$;
$\lambda = +1$ gives the onset value $R_a = 3/4$ ($r_a = 3$)
while
$\lambda = -1$ gives the bifurcation value $R_b = 5/4$ ($r_b = 1+\sqrt 6$).
%
Note that the onset point of the only 2-cycle
  is located at $R = 3/4$,
  where the fixed point bifurcates \cite{strogatz}
  \big[compare \reffigs{cobweb}(a) and (b)\big].

For $n = 3$ \cite{saha, bechhoefer, gordon, burm, zhang},
we have
$C_0 = 1$,
$C_1 = x_1 + x_2 + x_3$,
$C_{12} = x_1 x_2 + x_2 x_3 + x_3 x_1$,
$C_{123} = x_1 x_2 x_3$,
and
$\Lambda = -8 x_1 x_2 x_3$.
%
The square-free reduction yields
%
%
%
\begin{align}
\lambda
\left( \begin{array}{c}
  C_0 \\
  C_1 \\
  C_{12} \\
  C_{123}
\end{array} \right)
=
\left( \begin{array}{cccc}
 0            & 0                 & 0               & -8 \\
 -24 R        & 8(R+1)            & -8R             & 0 \\
 24 R^2       & -8R(R+2)          & 8(R+1)          & 0 \\
 -8R^3        & 8R^2              & -8R             & 8
  \end{array} \right)
\left( \begin{array}{c}
  C_0 \\
  C_1 \\
  C_{12} \\
  C_{123}
\end{array} \right),
\end{align}
%
%
%
and \refeq{xr} reads:
\begin{align}
  0
&=\left| \begin{array}{cccc}
 \lambda      & 0                 & 0               & 8 \\
 24 R         & \lambda - 8(R+1)  & 8R              & 0 \\
 -24 R^2      & 8R(R+2)           & \lambda-8(R+1)  & 0 \\
 8R^3         & -8R^2             & 8R              & \lambda-8
  \end{array} \right| \nonumber \\
&= -\big[
  64R^3 - 128 R^2 - 8 (\lambda - 8) R - (\lambda -8)^2
  \big]
  \big(
  \lambda^2 - 8\lambda - 24 R\lambda - 64 R^3
  \big).
  \tag{\ref{eq:xr}-3}
\label{eq:xr3}
\end{align}
%
Using the first factor, we find at the onset point
  $\lambda = 1$,
  $\left(
  R-\frac74
  \right)
  \left(
  R^2-\frac14 R + \frac{7}{16}
  \right)=0$
  and its only real solution is $R_a = 7/4$ ($r_a = 1+\sqrt 8$).
%
At the bifurcation point $\lambda = -1$,
  the equation $R^3-2R^2 + \frac{9}{8} R -\frac{81}{64}=0$
  yields
  $R_b = \frac14
      \left(
      \frac{8}{3} +
        \sqrt[3]{\frac{1915}{54} - \frac52\sqrt{201}}
       +\sqrt[3]{\frac{1915}{54} + \frac52\sqrt{201}}
      \right)$,
whose corresponding $r = 1+\sqrt{1+4R}$
is identical to that in ref. \cite{gordon, burm}.
%

For $n = 4$ \cite{stephenson}, the cyclic variables are
$C_0 = 1$,
$C_1 = x_1 + x_2 + x_3 + x_4$,
$C_{12} = x_1 x_2 + x_2 x_3 + x_3 x_4 + x_4 x_1$,
$C_{13} = x_1 x_3 + x_2 x_4$,
$C_{123} = x_1 x_2 x_3 + x_2 x_3 x_4 + x_3 x_4 x_1 + x_4 x_1 x_2$
$C_{1234} = x_1 x_2 x_3 x_4$,
and
$\Lambda = 16 x_1 x_2 x_3 x_4$.
%
\refeq{xr} reads
%
\begin{align}
0 & = \left|
\begin{array}{cccccc}
 \lambda  & 0               & 0                 & 0     & 0     & -16 \\
 64 R     & \lambda-16(R+1) & 16 R              & 0     & -16R  & 0 \\
 -64 R^2  & 16R(R+2)        & \lambda-16(R^2+1) & -32 R & 16R   & 0 \\
 -32 R^2  & 16R(R+1)        & -16R              & \lambda-16(R^2+1)  & 0 & 0 \\
 64 R^3   & -16R^2(R+3)     & 16R(R+2)        & 32 R (R+1)       & \lambda-16(R+1) & 0 \\
 -16R^4   & 16R^3           & - 16R^2           & -16R^2            & 16R & \lambda - 16
\end{array}
\right | \nonumber  \\
& =
    \big[
    4096 R^6-12288 R^5 + 256 (\lambda + 48) (R^4- R^3)
      -16 (\lambda + 32)(\lambda - 16) R^2
      -(\lambda - 16)^3 \big]  \nonumber \\
& \quad
    \big[ 16 (R-1)^2 - \lambda \big]
 \, \big[(16 R^2 + \lambda)^2 - 16 (2R+1)^2 \lambda \big],
  \tag{\ref{eq:xr}-4}
\label{eq:xr4}
\end{align}
%
%
%
From the first factor, we have
$ (
    4R - 5
  )
\, \big[
  (4R + 1)^2 + 4
  \big]
\, \big[
  (4R - 3)^3 - 108
  \big] =0$
at the onset point $\lambda = 1$.
%
%
%
It has two real roots:
$R_a' = 5/4$
\big($r_a' = 1+\sqrt{6} \approx 3.4495$\big)
for the cycle from period-doubling the 2-cycle
  \big[compare \reffigs{cobweb}(b) and (d)\big],
and
$R_a = (3+\sqrt[3]{108})/4$
\big($r_a = 1+\sqrt{4+\sqrt[3]{108}} \approx 3.9601$\big)
for an original cycle \big[\reffig{cobweb}(e)\big].
%
At the bifurcation point, $\lambda = -1$, and
$4096 R^6 - 12288 R^5 + 12032 (R^4 - R^3)
  + 8432 R^2 + 4913 = 0$,
which upon $R \rightarrow r(r-2)/4$ yields the same polynomial
obtained previously
\cite{bailey1, kk1, bailey2, lewis}.
%
%
%
The only two positive roots $r_b \approx 3.9608$
and $r_b' \approx 3.5441$
correspond to $r_a$ and $r_a'$ respectively.
%
As a verification, the polynomials are
alternatively derived in the Appendix.

\begin{table}[h]\footnotesize
  %\caption{
  \tbl{
  Characteristic polynomials $A_n\RX$ of
  the fixed points of $f^n$ of
  the simplified logistic map \refeq{logmaps}.
  }
%\begin{center}
{
\begin{tabular}{lc}
\hline
  $n$
& $A_n(R, \; \lambda = 2^n X)
  \big\slash
   2^{n \NB(n)}$ $^\dagger$
\\
\hline
1
&
$X^2-X-R$
\\
2
&
  $
  \big[ \cancel{(R-X)^2 - X}\big]
  (R + X - 1)
  $
\\
3
&
$\begin{aligned}
\big[\cancel{
  X^2-(3R+1)X-R^3
}\big]
  \big[
  (X-1)^2
 + X R
 - R(R-1)^2
  \big]
\end{aligned}$
\\
4
&
$\begin{aligned}
\big[ \cancel{
  (R-1)^2 - X
} \big]
\big[ \cancel{
(R^2+X)^2 -(2R+1)^2 X
} \big]
\big[
  R^6-3 R^5+(X+3) (R^4 - R^3) -(X+2)(X-1) R^2 - (X-1)^3
\big]
\end{aligned}$
\\
5
&
\begin{minipage}{.97\linewidth}
\vspace*{2mm}
$\begin{aligned}
&\big[ \cancel{
  X^2-5 X (R^2+R)-X - R^5
  %R^5+5 X (R^2+R)-X^2+X
} \big]
\big[
-R^{15}+8 R^{14}-28 R^{13}+(X+60) R^{12}-(7 X+94) R^{11}
+(3 X^2 +20 X
\\
+&116) R^{10}
-(11 X^2+33 X+114) R^9
+2(3 X^2+20 X+47) R^8
-(2 X^3-20 X^2+37 X+69) R^7 \\
+&(3 X-11)(3X^2-3X+44) R^6
%-(3 X^4+17 X^3-53 X^2+7 X+26) R^5
-(X-1) (3 X^3+20 X^2-33 X-26) R^5
+(X-1)^2 (3 X^2+27 X+14) R^4 \\
+&(X-1)^3 (6 X+5) R^3
+(X-1)^4 (X+2) R^2+(X-1)^5 R+(X-1)^6
\big]
\end{aligned}$
\vspace{1mm}
\end{minipage}
\\
6
&
$\begin{aligned}
&\big[\cancel {
  (R-1)^3 + X
}\big]
\big[\cancel {
 (R^3 - X)^2 - (3R+1)^2 X
}\big]
\big[\cancel {
\big(R(R-1)^2-1-X\big)^2-(R-2)^2 X
}\big]
\big[
R^{27}-13 R^{26}+78 R^{25}\\
&+(X-293) R^{24}
+\dots
+(X-1)^6 (X^2+10 X+3) R^3
+(X-1)^7 (X+1) R^2-(X-1)^8 R+(X-1)^9
\big]
\end{aligned}$
\\
7
&
\begin{minipage}{.97\linewidth}
\vspace{1mm}
$\begin{aligned}
&\big[\cancel {
  -R^7 - 7 X R (R+1)^2 + X^2 - X
}\big]
\big[
-R^{63}+32 R^{62}-496 R^{61}
+4976 R^{60} + (X - 36440) R^{59}
- (30X
\\
-&208336) R^{58}
+\dots
+(X-1)^{15} (X^2+14 X+5) R^3
+2(X-1)^{16} (X+1) R^2
+(X-1)^{17} R
+(X-1)^{18}
\big]
\end{aligned}$
\end{minipage}
\\
\vdots & \vdots
\\
\hline
\multicolumn{2}{p{\textwidth}}{
$^\dagger$
$\NB(n) = (1/n) \sum_{d|n} \phi(n/d) 2^d$ [\refeq{necklace}]
is the number of the square-free cyclic polynomials.
%
The change of variable $\lambda \rightarrow X$ and
  the division by $2^{n \NB(n)}$ make the polynomials more compact.
%
The irrelevant factors from shorter cycles
(see \refsec{primfac}) are struck out.
The polynomials of $r$ for the original logistic map \refeq{logmap}
can be obtained by $R\rightarrow r(r-2)/4$.
} \\
\hline
\end{tabular}
\label{tab:Anlog}
}
%\end{center}
\end{table}

The algorithm was coded into a Mathematica program,
which was used to compute the polynomials for $n$ up to 13.
The polynomials for a general $\lambda$
and those at $\lambda = \pm1$ (onset and bifurcation points) are listed
in \reftab{Anlog} and \reftab{Pnlog}, respectively, for some small $n$.
%
For complex $R$, $\lambda$, and $\vx$,
the method can also compute the region of stability for $R$,
with $\lambda$ being $\exp(i\phi)$ \big[$\phi \in (0, 2\pi)$\big]
  instead of $\pm1$;
the results are shown in \reffig{logbulb}
for $n$ up to $8$.
%
For polynomials of larger $n$, see the website in \refsec{end}.
The representative $r$ values are listed in \reftab{rval}.

\begin{table}[h]\footnotesize
  %\caption{
  \tbl{
  Smallest positive $r$ at the onset and bifurcation points
  of the $n$-cycles of the logistic map.
  }
%\begin{center}
{
\begin{tabular}{llllllll}
%\begin{tabularx}{\textwidth}{
%  >{\hsize=0.5\hsize\centering\arraybackslash}X
%  >{\hsize=1.6\hsize}X
%  >{\hsize=1.6\hsize}X
%  >{\hsize=0.3\hsize\raggedright\arraybackslash}X |
%  >{\hsize=0.5\hsize\centering\arraybackslash}X
%  >{\hsize=1.6\hsize}X
%  >{\hsize=1.6\hsize}X
%  >{\hsize=0.3\hsize\raggedright\arraybackslash}X
%}
\hline
  $n^\dagger$
& Onset$^\ddagger$
& Bifurcation$^\ddagger$
& \#$^*$
&
  $n^\dagger$
& Onset$^\ddagger$
& Bifurcation$^\ddagger$
& \#$^*$ \\
\hline
$1$     & $1.0000000000_1$      &  $3.0000000000_1$       & 1   &
$8'$    & $3.9607686524_{6}$    &  $3.9610986335_{120}$   & 1   \\
$2'$    & $3.0000000000_1$      &  $3.4494897428_1$       & 1   &
$8'''$  & $3.5440903596_{6}$    &  $3.5644072661_{120}$   & 1   \\
$3$     & $3.8284271247_1$      &  $3.8414990075_3$       & 1   &
$9$     & $3.6871968733_{240}$  &  $3.6872742105_{252}$   & 28  \\
$4$     & $3.9601018827_3$      &  $3.9607686524_6$       & 1   &
$10$    & $3.6052080669_{472}$  &  $3.6059169323_{495}$   & 48  \\
$4''$   & $3.4494897428_1$      &  $3.5440903596_6$       & 1   &
$10'$   & $3.7411207566_{15}$   &  $3.7425706462_{495}$   & 3   \\
$5$     & $3.7381723753_{11}$   &  $3.7411207566_{15}$    & 3   &
$11$    & $3.6817160194_{1013}$ &  $3.6817266457_{1023}$  & 93  \\
$6$     & $3.6265531617_{20}$   &  $3.6303887000_{27}$    & 4   &
$12$    & $3.5820230011_{1959}$ &  $3.5828117795_{2010}$  & 165 \\
$6'$    & $3.8414990075_{3}$    &  $3.8476106612_{27}$    & 1   &
$12'$   & $3.6303887000_{27}$   &  $3.6321857392_{2010}$  & 4   \\
$7$     & $3.7016407642_{57}$   &  $3.7021549282_{63}$    & 9   &
$12''$  & $3.8476106612_{27}$   &  $3.8490363152_{2010}$  & 1   \\
$8$     & $3.6621089132_{108}$  &  $3.6624407072_{120}$   & 14  &
$13$    & $3.6797024578_{4083}$ &  $3.6797038498_{4095}$  & 315 \\
\hline
\multicolumn{8}{p{\textwidth}}{
$^\dagger$
  $\,'$, $\,''$, or $\,'''$ means
    a cycle undergoing
    the first, second, or third successive period-doubling, respectively.
} \\
\multicolumn{8}{p{\textwidth}}{
$^\ddagger$
  The subscripts are the degrees of the corresponding minimal polynomial
    of $R = r(r-2)/4$.
} \\
\multicolumn{8}{p{\textwidth}}{
$^*$
  The number of similar cycles.
} \\
\hline
%\end{tabularx}
\end{tabular}
\label{tab:rval}
}
%\end{center}
\end{table}

\subsection{\label{sec:primfac}Minimal polynomial for the $n$-cycles}

The factors ignored in \refsec{examples}
  come from shorter $d$-cycles whose periods $d$ divide $n$,
%
  because $A_n\RX$,
  from the characteristic equation \refeq{xr},
  is derived for all fixed points of $f^n$,
  and thus encompasses the shorter cycles as well.
%
We filter the contributions from the shorter cycles by the following theorem.

\begin{theorem}
  The minimal polynomial $P_n\RX$ of all $n$-cycles
  is a factor of $A_n\RX$ [defined in \refeq{xr}],
  and can be computed as
  \begin{equation}
    P_n\RX
    = \prod_{cd = n} B_{d,c}\RX^{\mu(c)},
  \label{eq:primfac}
  \end{equation}
where
  $B_{d, c}\RX \equiv \prod_{k=1}^c A_{d}(R, e^{2k\pi i/c} \lambda^{1/c})$,
  $\lambda^{1/c}$ is a complex $c$th root of $\lambda$,
  and $\mu(c)$ is the M\"obius function.
  \label{thm:primfac}
\end{theorem}

%\begin{remark}[1]
\begin{remark}
The M\"obius function $\mu(n)$ is $(-1)^k$
  if $n$ is the product of $k$ distinct primes,
  or 0 if $n$ is divisible by a square of a prime.
$\mu(n)$ = 1, $-1$, $-1$, 0, $-1$, 1, \ldots,
  starting from $n = 1$.
The $\mu(n)$ is useful for inversion:
$g(n) = \sum_{d|n} \mu(n/d) \, h(d)$
if and only if $h(n) = \sum_{d|n} g(d)$
\cite{hardy}.
\end{remark}

%\begin{remark}[2]
\begin{remark}
$B_{d,c}\RX$ is a polynomial of $\lambda$.
Despite the argument $\lambda^{1/c}$,
  the product $\prod_{k=1}^c A_d(R, e^{2k\pi i/c} \lambda^{1/c})$
  is free from radicals of powers of $\lambda^{1/c}$,
  for it is invariant under $\lambda \rightarrow e^{2\pi i} \lambda$;
and $\deg_\lambda B_{d,c}\RX = \deg_\lambda A_d\RX$.
Particularly, $B_{n,1}\RX = A_n\RX$.
\end{remark}

%We will refer to $P_n\RX$ as the \emph{primitive factor} below.

Let us see some examples.
%
For $n = 1$,
there is no irrelevant factor
in \refeq{xr1} and
$P_1\RX = B_{1,1}\RX = A_1\RX = \lambda^2 - 2\lambda - 4R$.

For $n = 2$, since
$B_{1,2}\RX
=
(\lambda +2\sqrt{\lambda} - 4R)
\,
(\lambda -2\sqrt{\lambda} - 4R)
=(4R-\lambda)^2 -4\lambda$,
%
$P_2\RX = A_2\RX \, B_{1,2}\RX^{-1} = 4R - 4 + \lambda$.

For $n = 3$,
one can verify that
$B_{1,3}\RX
= \prod_{k=1}^3 A_1(R, e^{2k\pi i/3} \, \sqrt[3]{\lambda})
=  \lambda^2 - 24 R \lambda - 8 \lambda - 64 R^3$.
%
So
$P_3\RX = A_3\RX \, B_{1,3}\RX^{-1}
= -\big[64 R^3- 128 R^2 -8(\lambda -8)R-(\lambda-8)^2\big]$.

For $n = 4$,
we have
$16 (R-1)^2 - \lambda
= (4R - 4 + \sqrt{\lambda})(4R - 4 - \sqrt{\lambda})$
and
$
(16 R^2 + \lambda)^2 - 16 (2R+1)^2 \lambda
=
\big[(4R - \sqrt{\lambda})^2  - 4\sqrt{\lambda}\,\big]
\big[(4R + \sqrt{\lambda})^2  + 4\sqrt{\lambda}\,\big]$.
Thus, the last two factors of \refeq{xr4}
can be written as
$B_{2,2}\RX = \prod_{k=1}^2 A_2(R, e^{k \pi i} \sqrt{\lambda})$,
and
%
$P_4\RX
    = A_4\RX \, B_{2,2}\RX^{-1}
    = 4096 R^6-12288 R^5+ 256 (\lambda + 48) (R^4- R^3)
    -16(\lambda + 32)(\lambda - 16) R^2 - (\lambda-16)^3$.
Note, $B_{1,4}\RX$ is unused for $\mu(4) = 0$.

The irrelevant factors for $n$ up to 7 are listed in \reftab{Anlog}.

\newcommand{\T}{{R_4}}

\begin{table}[h]\footnotesize
  %\caption{
  \tbl{
  Onset and bifurcation polynomials %$P_n(R, \pm1)$
  of the $n$-cycles of the simplified logistic map \refeq{logmaps}.
  }
{
\label{tab:Pnlog}
\begin{tabular}{lcc}
\hline
  $n$
& Onset $P_n(R, \; +1)$ $^{\dagger, \ddagger}$
& Bifurcation $P_n(R, \; -1)$ $^\dagger$
\\
\hline
1
&
$-\T-1$
&
$-\T+3$
\\
2
&
$-(\cancel{3-\T})$
&
$\T-5$
\\
3
&
$\begin{aligned}
-
\big( \cancel{
  \T^2-\T+7
}\big)
  (\T-7)
\end{aligned}$
&
$\begin{aligned}
 - \T^3 + 8\T^2 - 18\T + 81
\end{aligned}$
\\
4
&
$\begin{aligned}
\big( \cancel{
  \T - 5
} \big)
\big[ \cancel{
  (\T+1)^2 + 4
} \big]
\big[
  (\T-3)^3 - 108
\big]
\end{aligned}$

&

$
\T^6-12 \T^5+47 \T^4-188 \T^3+527 \T^2+4913
$
\\
5

&

\begin{minipage}{.48\linewidth}
%\vspace{3mm}
$\begin{aligned}
-
&\big( \cancel{
\T^4-\T^3+\T^2+9 \T+31
} \big)
\big(
\T^{11}-31 \T^{10} \\
+&416 \T^9 -3404 \T^8 +20548 \T^7-98258 \T^6 \\
+&370146 \T^5 -1171676 \T^4 +3301996 \T^3\\
-&7507332 \T^2+15699857 \T-28629151
\big)
\end{aligned}$
%\vspace{2mm}
\end{minipage}

&

\begin{minipage}{.49\linewidth}
\vspace{1mm}
$\begin{aligned}
-&\T^{15}+32 \T^{14}-448 \T^{13}+3838 \T^{12}-24008 \T^{11}\\
+&118147 \T^{10} -462764 \T^9+1519712 \T^8\\
-&4444924 \T^7 +11351480 \T^6 -26978787 \T^5\\
+&58697100 \T^4 -88548768 \T^3+149426046 \T^2\\
-&313083144 \T +1291467969
\end{aligned}$
\vspace{1mm}
\end{minipage}

\\
6

&

\begin{minipage}{.48\linewidth}
%\vspace{1mm}
$\begin{aligned}
&\big( \cancel{
\T^2-9 \T+21
} \big)
\big( \cancel{
\T^2+3 \T+3
} \big)
\big( \cancel{
\T^3-8\T^2} \\
+&\cancel{18\T-81
} \big)
\big(
\T^{20}-\dots+3063651608241
\big)
\end{aligned}$
%\vspace{2mm}
\end{minipage}

&

\begin{minipage}{.49\linewidth}
%\vspace{3mm}
$\begin{aligned}
&\T^{27}-52 \T^{26}+1248 \T^{25}-18753 \T^{24}+\dots\\
&-5098317006250000 \T-20711912837890625
\end{aligned}$
%\vspace{2mm}
\end{minipage}

\\
7

&

\begin{minipage}{.48\linewidth}
%\vspace{1mm}
$\begin{aligned}
-
&\big( \cancel{
\T^6-\T^5+\T^4-\T^3
%\T^3(\T^2+1)(\T-1)
 +15T^2+97 \T+127
} \big) \\
&\big(
\T^{57}
-127\T^{56}
+\dots+
%581652040856250348581103942808504447
58165204\dots8504447
\big)
\end{aligned}$
%\vspace{2mm}
\end{minipage}

&

\begin{minipage}{.49\linewidth}
%\vspace{3mm}
$\begin{aligned}
&-\T^{63}+128 \T^{62}-7936 \T^{61}+318464 \T^{60}-\dots\\
%&-24275883989858911295570196314376441888 T \\
%&+97862157334118736160267353892330031361
&-2427583\dots6441888 \T +9786215\dots0031361
\end{aligned}$
%\vspace{2mm}
\end{minipage}

\\
\vdots & \vdots & \vdots
\\
13
&

\begin{minipage}{.48\linewidth}
%\vspace{1mm}
$\begin{aligned}
-&\big(\cancel{
\T^{12}-\T^{11}+\T^{10}
%-\T^9+\T^8-\T^7+\T^6+25 \T^5+703 \T^4+5121 \T^3+14847 \T^2
-\dots
+18433 \T+8191
}\big) \\
\big(
&\T^{4083}
 - 8191\T^{4082}
+ 33529856 \T^{4081}
- \dots \\
-&30826655683291995
\dots
27828275886475354111
\big)
\end{aligned}$
%\vspace{2mm}
\end{minipage}

&

\begin{minipage}{.49\linewidth}
%\vspace{1mm}
$\begin{aligned}
-&\T^{4095} + 8192 \T^{4094} -33538048 \T^{4093} \\
+&\dots
-7361199006999 % 0439512081857
\dots
96207964555264\T
\\
+&29448390363448812
%0567620
\dots
%1182
352154556569141249
\end{aligned}$
%\vspace{2mm}
\end{minipage}

\\
\hline
\multicolumn{3}{p{\textwidth}}{
$^\dagger$ $\T = 4R$.
The polynomials of $r$ for the original logistic map \refeq{logmap}
can be obtained by $\T\rightarrow r(r-2)$.
} \\
\multicolumn{3}{p{\textwidth}}{
$^\ddagger$
Factors for the $n$-cycles born out of shorter cycles (see \refsec{origfac})
are struck out.
} \\
\hline
\end{tabular}
}
\end{table}

\begin{figure}[h]
  \begin{minipage}{\linewidth}
    \begin{center}
        \includegraphics[angle=-90, width=.67\linewidth]{logbulb.pdf}
    \end{center}
  \end{minipage}%
  \caption{
  \label{fig:logbulb}
  Stable regions of the $n$-cycles of the simplified logistic map \refeq{logmaps}
  with a complex $R$;
  obtained from $P_n(R, e^{i\phi}) = 0$ with $\phi \in [0, 2\pi]$,
  cf. Fig. 3 in \cite{stephenson}.
}
\end{figure}

\refthm{primfac} is not always necessary.
For $n \ge 4$,
  $P_n\RX$ is readily recognized as
  the factor
  of $A_n\RX$
  with the highest degree in $R$,
  see \reftab{Anlog} and \refsec{degR}.
It can be, however, problematic,
   if $P_n(R, \lambda)$ is solved for $\lambda = 1$
   instead of a general $\lambda$,
   for $P_n(R, 1)$ itself can be further factorized,
  see \reftab{Pnlog}.
%
Due to the technical nature of the derivation and subsequent discussions,
  the reader may wish to skip the rest of \refsec{logmap}
  on first reading.

\subsection{\label{sec:degprimfac}Counting cycles}

%We will prove \refthm{primfac} by the following steps.
%
To show \refthm{primfac}, we first find the degrees in $\lambda$ of
  $A_n\RX$ (\refthm{necklace}) and $P_n\RX$ (\refthm{lyndon}).
By comparing the degrees,
  we then show that each $P_d\RX$ with ($d|n$),
  after some transformation,
  contributes one polynomial factor to $A_n\RX$
  (\refthm{prod}),
  and the inversion of the relation
  yields \refthm{primfac}.

\subsubsection{Number of the square-free cyclic polynomials}

To count the square-free cyclic polynomials,
  we establish a one-to-one mapping
  between the square-free cyclic polynomials
  and the binary necklaces (defined below).
The task is then to count the latter.

A binary necklace
  is a nonequivalent binary $0$-$1$ string.
%
Two strings are equivalent if they differ only by a circular shift.
%
For example, for $n = 3$, there are $2^3 = 8$ binary strings,
but only four necklaces: 000, 001, 011 and 111,
since 010 and 100 are equivalent to 001,
so are 110 and 101 to 011.
%
The period of a necklace, or a binary string,
  is the length of the shortest non-repeating sub-sequence,
  e.g., the periods of $1111$, $0101$ and $0001$
        are 1, 2, and 4, respectively.
%
Obviously, the period $m$ divides $n$;
  and a period-$m$ necklace
  encompasses $m$ binary strings
  differed by circular shifts,
  e.g., $0101$ represents
  both $0101$ and $1010$.

\begin{table}[h]\footnotesize
%\caption{
\tbl{
Two ways of counting the $N(4) = 6$ necklaces for $n = 4$.
}
%\begin{center}
{
%\begin{tabularx}{\textwidth}{c | c  c | c | c | c | c | c }
\begin{tabular}{c | c  c | c | c | c | c | c }
\hline
        & \multicolumn{2}{c|}{$m = 1$}
        & $m = 2$
        & $m = 4$   & $2^d$ & $\phi(n/d)$ & $\phi(n/d) 2^d$\\
\hline
$d = 1$ & \hspace{1mm} $\mathbf{0}_{\times4}$ \hspace{1mm}
        & \hspace{1mm} $\mathbf{1}_{\times4}$ \hspace{1mm} & & & $2 = 2$ & $2$ & 4 \\
\hline
$d = 2$ & $\mathbf{00}_{\times2}$ & $\mathbf{11}_{\times2}$
        & \hspace{1mm} $\mathbf{10}_{\times2} (01_{\times2})$
          \hspace{1mm} & & $2 + 2 =4$ & $1$ & 4 \\
\hline
\multirow{3}{*}{$d = 4$}
      & & & & \hspace{1mm} $\mathbf{1000} (0100, 0010, 0001)$
              \hspace{1mm} & $2 + 2 + 12$& \\
      & $\mathbf{0000}$ & $\mathbf{1111}$ & $\mathbf{1010} (0101)$
            & $\mathbf{1100} (1001, 0110, 0011)$ & $=16$ & $1$ & 16 \\
      & & & &   $\mathbf{1110} (1101, 1011, 0111)$ & &  \\
\hline
$m \sum_{m|d, d|n} \phi(\frac{n}{d})$
      & \multicolumn{2}{c|}{$1\cdot(2+1+1) = 4$}
      & $2\cdot(1+1) = 4$ & $4\cdot1 = 4$ &  \multicolumn{2}{c|}{} &  $\downarrow$\\
\hline
$N(n)\cdot n$ & \multicolumn{2}{c|}{$2 \cdot 4$} & $1 \cdot 4$ & $3 \cdot 4$ &
  \multicolumn{2}{c|}{$\rightarrow$} & $6\cdot4 = 24$ \\
\hline
\multicolumn{8}{p{\linewidth}}{
  Bold strings are necklaces; others are their cyclic versions.
}
\\
\multicolumn{8}{p{\linewidth}}{
The subscript of a binary string means the number of repeats;
e.g.,
$\mathbf{0}_{\times4}$ means $\mathbf{0}$ repeated four times, or $\mathbf{0000}$;
$\mathbf{10}_{\times2}$ means $\mathbf{10}$ repeated twice, or $\mathbf{1010}$, etc.
}
\\
\hline
\end{tabular}
%\end{tabularx}
%\end{center}
\label{tab:countnecklace}
}
\end{table}

To compute the number of the binary necklaces $N(n)$,
we construct a sum for the length-$n$ binary strings and count it in two ways.
\reftab{countnecklace} shows the example for the $n=4$ case.
%
For each divisor $d$ of $n$, we collect
  all length-$n$ binary strings
  whose periods $m$ divide $d$.
%
The total is $2^d$,
  for we have enumerated all binary strings whose periods divide $d$.
%and each period-$m$ necklace contributes $m$ cyclic versions.
%
We then weight them by the Euler's totient function $\phi(n/d)$.
%
Here, $\phi(m)$ gives the number of integers from 1 to $m$
  that are coprime to $m$,
  e.g.,
  $\phi(1) = 1$,
  $\phi(3) = 2$ for 1 and 2,
  $\phi(6) = 2$ for 1 and 5.
We repeat the process over other divisors $d$ of $n$,
  and the resulting sum is $\sum_{d|n} \phi(n/d) 2^d$.
%
The process for a fixed $d$ is exemplified
  by a row in \reftab{countnecklace}.

%

We can count the above sum in another way.
We recall that a period-$m$ necklace always contributes
  $m$ strings in the above process for a fixed $d$,
  and it does so for all multiples $d$ of $m$.
So the total weighted contribution by this necklace is
\begin{equation}
m \sum_{m|d, d|n} \phi(n/d) =
 m \sum_{\frac{n}{d}|\frac{n}{m}} \phi(n/d) = m \,  \frac{n}{m}  = n,
\label{eq:mphind}
\end{equation}
where we have used the identity $\sum_{d'|m'} \phi(d') = m'$,
with $d' = n/d$ and $m' = n/m$.
%
Summing over the necklaces yields $N(n) \, n$. Thus,
$N(n) = (1/n) \sum_{d|n} \phi(n/d) 2^d$.
The process for a fixed necklace is exemplified
  by a column in \reftab{countnecklace}.
%

Back to our problem, there is
  a correspondence between the binary necklaces
  and the square-free cyclic polynomials.
For a square-free cyclic polynomial,
  we construct a binary string according to its generator:
if it contains $x_k$, the $k$th character from the left is 1,
  otherwise 0.
The resulting string corresponds to a unique necklace;
  the alternative generators give
  the circularly-shifted binary strings.
The mapping is reversible, or one-to-one.
For example, if $n = 3$,
 the square-free polynomials for $000$, $100$, $110$ and $111$ are
  $C_0 = 1$ (generator: 1),
  $C_1 = x_1 + x_2 + x_3$ (generator: $x_1$),
  $C_{12} = x_1 x_2 + x_2 x_3 + x_3 x_1$ (generator: $x_1 x_2$)
  and $C_{123} = x_1 x_2 x_3$ (generator: $x_1 x_2 x_3$), respectively.
\reftab{sqrfreepoly} shows a few more examples.
%
Thus,

\begin{theorem}
The number $\NB(n)$ of the square-free cyclic polynomials $C_p(\vx)$ ($p \in \Bset$)
  formed by $\vx = \{x_1, \ldots, x_n\}$ is
\begin{equation}
  \NB(n) = N(n) = (1/n) \sum_{d|n} \phi(n/d) 2^{\,d},
\label{eq:necklace}
\end{equation}
%
which is also equal to $\deg_\lambda A_n\RX$.
\label{thm:necklace}
\end{theorem}
%
$N(n)$ = 2, 3, 4, 6, 8, 14, 20, 36, 60, 108, 188, 352, 632, \ldots,
  starting from $n = 1$.

\subsubsection{Number of the $n$-cycles}

\begin{theorem}
The degree in $\lambda$ of the minimal polynomial $P_n\RX$ of all $n$-cycles
  is equal to the number of the $n$-cycles,
  and is given by
\begin{equation}
  \deg_\lambda P_n\RX = L(n) = (1/n)\sum_{d | n} \mu(n/d) 2^{\,d}.
\label{eq:lyndon}
\end{equation}
\label{thm:lyndon}
\end{theorem}

\begin{proof}
Except a few special values of $R$,
the iterated map $f^{n}$ generally
has $2^n$ distinct complex fixed points,
%
for otherwise $f^{n}(x) - x$ would have a repeated zero at any $R$,
  but at $R=0$, $-x^{2^n} - x$ has no repeated root; a contradiction.

Each fixed point can be assigned to
  a point in a $d$-cycle, with $d$ being a divisor of $n$.
%
The assignment
  is both complete (for a $d$-cycle point
  must also be a fixed point of $f^n$)
  and non-redundant (for there is no
  repeated fixed point of $f^n$).
%
Since each of the $L(d)$ $d$-cycles
  contributes $d$ fixed points,
we have
$2^n = \sum_{d\,|\,n} L(d) \, d$.
%
The M\"obius inversion yields $L(n) = (1/n) \sum_{d\,|\,n} \mu(n/d) 2^{\,d}$.
This formula was known to several authors \cite{hao, hao2, lutzky}.

We now define $\lambda_c$ as the value of $\Lambda(\vx)$,
  evaluated at the cycle points
  $\vx^{(c)} \equiv \{ {x_1}^{(c)}, \ldots, {x_n}^{(c)} \}$
  of cycle $c$.
Of course, $\lambda_c$ is a function of $R$.
If we assume that $\lambda_c$ are distinct (see Remark \ref{remark:distinct} below),
  then the minimal polynomial $P_n\RX$,
  as a polynomial of $\lambda$,
  takes the form of $\prod_c (\lambda - \lambda_c)$.
Thus, the degree of $P_n\RX$ in $\lambda$
  must be the same as the number of the $n$-cycles.
\end{proof}

%\begin{remark}[1]
\begin{remark}
\label{remark:distinct}
Although all trajectory points $\vx^{(c)}$ are distinct in
  different cycles,
the value $\lambda_c$ of the polynomial $\Lambda(\vx^{(c)})$
  may happen to be the same.
In this case,
  we shall find another cyclic polynomial $Y(\vx)$ that
  has different values in the two cycles
  [$Y(\vx)$ exists for otherwise $\vx$ are the same in the two cycles],
  use $\Lambda'(\vx) = \Lambda(\vx) + \epsilon Y(\vx)$
  to list \refeqs{xcp0},
  then take the limit
  $\epsilon \rightarrow 0$.
\end{remark}

%\begin{remark}[2]
\begin{remark}
$L(n)$ is also the number of aperiodic (i.e., period equal to $n$)
  necklaces of length $n$,
  e.g., for $n = 4$,
  out of the six necklaces, $0001$, $0011$, and $0111$ are aperiodic;
  but $0000$, $1111$, and $0101$ are periodic.
%
Since a period-$d$ ($d|n$) necklace is just an aperiodic one
  of length-$d$ repeated $n/d$ times,
and each contributes $d$ binary strings,
we can count the $2^n$ binary strings of length $n$ as
  $2^n = \sum_{d|n} L(d) \, d$.
The M\"obius inversion leads to the same result of \refeq{lyndon}.
\end{remark}

$L(n)$ =
2, 1, 2, 3, 6, 9, 18, 30, 56, 99, 186, 335, 630, \ldots,
starting from $n = 1$.

Since the period $d$ of a length-$n$ necklace always divides $n$,
we have
\begin{equation}
N(n) = \sum_{d|n} L(d).
\label{eq:necklacelyndon}
\end{equation}
%
We can also show this by explicit computation:
\begin{align*}
\sum_{d | n} L(d)
  &= \sum_{d | n} (1/d) \sum_{c |  d} \mu(d/c) 2^{\,c}
   = (1/n) \sum_{c | n} 2^{\,c} \sum_{d'  |  (n/c)}
        \mu\left(\frac{n/c}{d'}\right) d' \\
  &= (1/n) \sum_{c \, | \, n} 2^{\,c} \, \phi(n/c)
  = N(n),
\end{align*}
where we have used $\phi(m) = \sum_{d' | m} \mu(\frac{m}{d'}) \, d'$,
which is the inversion of $m = \sum_{d' | m} \phi(d')$,
and \refeq{necklace}.
%
We will use \refeq{necklacelyndon} in proving the next theorem.

\subsubsection{Relation between $P_n\RX$ and $A_n\RX$}

\begin{theorem}
The minimal polynomials $P_d\RX$ of all $d$-cycles
  of periods $d|n$
and $A_n\RX$ [defined in \refeq{xr}] are related by
  \begin{equation}
    A_n\RX = \prod_{cd = n} Q_{d, c}\RX,
    \label{eq:prod}
  \end{equation}
  where
  $Q_{d,c}\RX = \prod_{k=1}^{c} P_d(R, e^{2 k \pi i/c} \lambda^{1/c})$
  is a polynomial of degree $L(d)$ in $\lambda$
  representing contributions from $d$-cycles.
%encompassed by $A_n\RX$.
\label{thm:prod}
\end{theorem}

\begin{proof}
Since $A_n\RX$ represent all $d$-cycles with $d|n$,
and each cycle holds a distinct $\lambda$,
  $\deg_\lambda A_n\RX$
  is at least $\sum_{d|n} L(d)$
  according to \refeq{lyndon},
  which is equal to
  $N(n)$ by \refeq{necklacelyndon}.
Since $\deg_\lambda A_n\RX = N(n)$ by \refeq{necklace},
  each $n$-cycle occurs exactly once in $A_n\RX$.

In a $d$-cycle,
 we have $\Lambda(\{x_1, \ldots, x_n\}) = (-2)^n x_1 \dots x_n
   = {\Lambda_d}^c$,
where
$\Lambda_d(\{x_1, \ldots, x_d\}) \equiv (-2)^d x_1 \dots x_d$
and
$c \equiv n/d$.
So the $d$-cycle satisfies a polynomial
  $P_d(R, \lambda^{1/c}) = 0$,
where $\lambda = \Lambda(\{x_1,\ldots,x_n\})$.
%
This is, however, not a polynomial equation, and
%
the radical $\lambda^{1/c}$ can be removed by the product
$Q_{d,c}\RX
  \equiv \prod_{k=1}^c P_d(R, e^{2k\pi i/c} \, \lambda^{1/c}) = 0$.
%
Now $Q_{d,c}\RX$ is a polynomial of $\lambda$
  for it is invariant under
  $\lambda \rightarrow e^{2\pi i} \lambda$,
and thus free from radicals of the form $\lambda^{l/c}$
  \big[if $(l, c) \ne c$\big].
And since
  $\deg_\lambda Q_{d,c}\RX
    = \deg_\lambda P_d\RX = L(d)$,
  it is also a polynomial
  of the lowest possible degree in $\lambda$.

Therefore, the product $\prod_{cd=n} Q_{d,c}\RX$
  can differ from $A_n\RX$ only by
  a multiple.
Since $Q_{n,1}\RX = P_n\RX$,
  and the coefficient of highest power of $\lambda$ is always
  unity in $A_n\RX$ \big[see the definition \refeq{xr}\big],
  we know by induction that the coefficients of the highest power of $\lambda$
  in all $P_n\RX$ and $Q_{d,c}\RX$
  are also unities.
So the multiple is one, hence \refeq{prod}.
%
%
%
\end{proof}

We can now prove \refthm{primfac} as a corollary of \refthm{prod},
\begin{align*}
 B_{n, m} \RX
 & = \prod_{l = 1}^{m} A_n(R, e^{2l\pi i/m} \lambda^{1/m}) \\
 & = \prod_{c | n} \prod_{l=1}^m \prod_{k=1}^c P_{n/c}(R, e^{2k\pi i/c + 2l\pi i/(m c)} \lambda^{1/(m c)}) \\
 & = \prod_{c | n} \prod_{k'=1}^{m c} P_{n/c}(R, e^{2k'\pi i/(m c)} \lambda^{1/(m c)})
  = \prod_{c | n} Q_{n /c, m c}\RX.
\end{align*}
Taking the logarithm (formally) yields
  $\log B_{n, m} = \sum_{d|n} \log Q_{d, m n/d}$,
where $d = n/c$.
The inversion is
  $\log Q_{n, m} = \sum_{d|n} \mu(n/d) \log B_{d, m n/d}$,
or
\begin{equation}
  Q_{n, m}\RX
= \prod_{d|n} B_{d, m n/d}\RX^{\mu(n/d)},
\tag{$\ref{eq:primfac}'$}
\end{equation}
which is reduced to \refeq{primfac} with $m = 1$
for $Q_{n, 1}\RX = P_n\RX$.

\subsection{\label{sec:origfac}Intersection of cycles
  and further factorization at the onset point}

\reftab{Pnlog} shows that
the onset polynomial
  $P_n(R, \lambda = 1)$ for the $n$-cycles
  can be further factorized.
%
This is because the intersection of an $n$-cycle
  and a shorter $d$-cycle ($d|n$, $d < n$)
  forces the two to share orbits
  (this cannot happen if $d \centernot| n$,
  for the orbits would be out of phase).
%
Consequently, upon the intersection,
  $P_n\RX$ from the $n$-cycle
  has to accommodate $P_d(R, \lambda')$ from the $d$-cycle,
  with $\lambda'$ being a primitive $(n/d)\,$th root of $\lambda$.

At the intersection,
  the shorter $d$-cycle is branched or ``bifurcated''
  by $(n/d)$-fold to the $n$-cycle.
%
The simplest example is the first bifurcation point
  at $R = 3/4$ for $d = 1, n = 2$,
  where the fixed point \refeq{xr1}
  bifurcates to
  the 2-cycle \refeq{xr2}.
%[recall the $\lambda = -1$ case in \refeq{xr1}
%  and $\lambda = +1$ case in \req{xr2} in \refsec{examples}];
The second bifurcation point at $R=5/4$ for $d = 2, n = 4$ is similar,
  cf. \refsec{examples}.

We will show below that such branching generally can only happen
  at the onset of the $n$-cycle, where $\lambda = 1$.
%
Further, with a real $R$, only a two-fold branching is possible,
  but a complex $R$ allows higher-fold branchings.

If an $n$-cycle is not born out of the above branching,
  we call it an \emph{original} cycle,
  e.g., the 4-cycle at $R_a' = 5/4$
  is born out of bifurcation, see \reffig{cobweb}(d),
  but the other at $R_a = (3+\sqrt[3]{108})/4$
  is original, see \reffig{cobweb}(e),
  also the discussion after \refeq{xr4}.
%
Both types of cycles exist in $P_n(R, \lambda = +1)$,
  as separate factors;
and the factor responsible for the original cycles,
  or the \emph{original factor} below,
  is given by the following formula.

\begin{theorem}
  The original factor $S_n(R)$ of $P_n\RX$ at the onset is given by
  \begin{equation}
    S_n(R)
    = \frac
    {
      P_n(R, 1)
    }
    {
      \prod_{c d =  n, \; c > 1}
      \left[ \,
        \prod_{(k, c) = 1}
      P_{d}
        \left(
          R, e^{2k\pi i/c}
        \right)
      \right]
    },
  \label{eq:origfac}
  \end{equation}
  where the inner product on the denominator is carried over
   $k$ from 1 to $c$ that are coprime to $c$.
  \label{thm:origfac}
\end{theorem}

We illustrate \refthm{origfac} through a few examples
  before giving a proof.
%
For $n = 1$,
$S_1(R) = P_1(R, 1) = -4R - 1$
as the denominator is unity.

For $n = 2$,
$P_2(R, 1) = 4R - 3$.
But $P_1(R, -1) = -4R + 3$.
So $S_2(R) = P_2(R, 1)/P_1(R, -1) = -1$.
This means that there is no original 2-cycle
  and the only 2-cycle comes from period doubling.

For $n = 3$,
$P_3(R, 1) = -(4R - 7)(16 R^2 - 4 R + 7)$,
whose second factor is equal to
$
\big(-4R + \frac{1 - 3 \sqrt3 i}{2}\big)
\big(-4R + \frac{1 + 3 \sqrt3 i}{2}\big)
= \prod_{k=1,2} P_1(R, e^{2 k \pi i/3})$.
%
Thus $S_3(R) = -4R + 7$.

For $n = 4$,
$P_4(R, 1)
= (4R - 5) (16 R^2 + 8 R + 5)
  \bigl[
    (4R - 3)^3 - 108
  \bigr]$.
But
$P_2(R, -1) = 4R - 5$ (for $c = 2$)
and
$\prod_{k=1,3} P_1(R, e^{k\pi i/2})
=(-4R-2i-1)(-4R+2i-1)
=16R^2+8R+5$
(for $c = 4$).
Dividing $P_4(R, 1)$ by the two factors yields
$S_4(R) = (4R-3)^3 - 108$,
  whose only real root $R=(3+\sqrt[3]{108})/4$ corresponds to
  the onset of the original cycle.
Note $R = 5/4$ is excluded from $S_4(R)$
  as it comes from period-doubling the 2-cycle.

%\section{\label{sec:degorigfac} Degree of the original factor}

We now prove \refthm{origfac}.
Suppose $n = c \,d$, we have, from \refeq{logmaps},
\[
  x_{l+1} - x_{d+l+1} = - (x_l + x_{d+l}) (x_l - x_{d+l}).
\]
We apply the equation to $l = 1, \ldots, m$, and the product is
\[
  x_{m+1} - x_{m + d+1} =
  (-1)^{m} \left[ \, \prod_{l=1}^{m} (x_l + x_{d+l}) \right]
    (x_1 - x_{d+1}).
\]
We now set $m$ to $0, d, \ldots, (c-1)\,d$ in this equation,
  add them together, eliminate $x_1 - x_{d+1}$
  (which is nonzero in a cycle), and
\begin{equation}
  \sum_{c' = 0}^{c-1}
    (-1)^{c' d} \prod_{l=1}^{c' d} (x_l + x_{d+l})
   = 0.
\label{eq:stair}
\end{equation}
%
Note \refeq{stair} holds for every divisor $c$ of $n$ ($c > 1$). We now have

\begin{theorem}
An $n$-cycle and a shorter $d$-cycle ($d|n$, $d< n$)
  intersect only at the onset of the $n$-cycle,
%
and $\prod_{k=1}^{d} f'(x_k) = (-2)^d x_1 \dots x_d$ is
a \emph{primitive} $(n/d)$th root of unity there.
\label{thm:cbifur}
\end{theorem}

\begin{proof}
At the intersection of the $n$- and $d$-cycles,
  $x_l$ repeats itself after $d$ steps, so
  $x_{d + l} = x_l$;
and \refeq{stair} becomes,
%
\begin{equation}
  1 + q + \dots + q^{c-1} = 0,
\label{eq:cbifur}
\end{equation}
%
where $q = (-2)^d \, x_1 \dots x_d$.
%
Multiplying \refeq{cbifur} by $q - 1$ yields
  $1 = q^c = (-2)^n \, x_1 \dots x_n$.
So the $n$-cycle is at its onset.

Further $q$ is a \emph{primitive} $c$th root of unity.
%
Suppose the contrary: $q = e^{2k\pi i/c}$ and $(k, c) = g >1$,
  then by $c_1 \equiv c/g$, $k_1 \equiv k/g$, we have
\begin{equation}
  q = e^{2k_1\pi i/ c_1}.
\label{eq:qd}
\end{equation}
Similar to \refeq{cbifur}, we can apply \refeq{stair} with $c \rightarrow g$ and $d \rightarrow d c_1$, and
\[
  1 + q_1 + \dots + {q_1}^{g-1} = 0,
\]
  where $q_1 = (-2)^{d c_1} \, x_1 \dots x_{dc_1} = q^{c_1}$.
But by \refeq{qd}, $q^{c_1} = e^{2 k_1\pi i} = 1$,
and $1 + q_1 + \dots + {q_1}^{g-1} = g > 0$; a contradiction.
%
\end{proof}

\begin{remark}
The only real $q$ is $q = -1$ for $c=2$, i.e., a period-doubling.
%
On the complex domain, however, we can have a $c$-fold branching with $c>2$,
  which corresponds to a contact points between ``bulbs''
  in the Mandelbrot set, see \reffig{logbulb}.
\end{remark}

By \refthm{cbifur}, $P_n\RX$ at the onset point
includes $P_d(R, e^{2 k \pi i/c} \lambda^{1/c})$ for every
  possible combination of $k$ and $c$, such that
  $(k, c) = 1$, $c|n$, and $c > 1$.
%
Dividing the factors from $P_n\RX$ yields \refthm{origfac}.

\subsection{\label{sec:degR}Degrees in $R$}

\begin{theorem}
The degrees in $R$ of $A_n\RX$, $P_n\RX$ and $S_n(R)$ are
\begin{subequations}
\begin{align}
\deg_R A_n\RX &= \sum_{d|n} \phi(n/d) 2^{d-1}, \\
\deg_R P_n\RX &= \sum_{d|n} \mu(n/d) 2^{d-1} \equiv \beta(n), \\
\deg S_n(R) &= \beta(n) - \sum_{d | n, d < n} \beta(d) \, \phi(n/d).
\end{align}
\label{eq:degR}
\end{subequations}
\label{thm:degR}
\end{theorem}

\begin{proof}
We first prove \refeqsub{degR}{a}.
%
We recall the subscript $p$ of $C_p$ denotes a sequence of indices $k$
  in the generating monomial $\prod_k {x_k}^{e_k}$.
But for a square-free cyclic polynomial,
  each $k$ occurs no more than once,
so $p$ also represents a \emph{set} of indices,
%
e.g.,
$p = 1$ represents $\{1\}$,
  ($C_1 = x_1 + \dots + x_n$, generator: $x_1$)
and
$p = 13$ represents $\{1, 3\}$
  ($C_{13} = x_1 \, x_3 + x_2 \, x_4 + \dots + x_n \, x_2$,
  generator: $x_1 \, x_3 $, assuming $n \ge 4$);
more examples are listed in \reftab{sqrfreepoly}).
%
In this proof,
we shall also use $p$ to denote the corresponding index set,
  $|p|$ the set size, i.e., the number of indices in the set,
  and
  $\bar p \equiv \{1,\ldots,n\} \backslash p$ the complementary set.
%
Obviously, $|\bar p| + |p| = n$.
%
Further, we will include $p$ that correspond to alternative generators
  of the same cyclic polynomial,
e.g., we allow $p = \{2\}$, $\{3\}$, \dots, $\{n\}$,
  although they represent the same cyclic polynomial $C_1$
  as $p = \{1\}$.

Next, we recall the matrix elements $T_{pq}(R)$ arise from the square-free reduction
of $\Lambda(\vx) C_p(\vx) = (-2)^n x_1 \dots x_n \, C_p(\vx)$.
%
A single replacement ${x_k}^2 \rightarrow R - x_{k+1}$
produces two new terms:
in the first, ${x_k}^2 \rightarrow R$,
and in the second, ${x_k}^2 \rightarrow - x_{k+1}$.
We call the two type 1 and type 2 replacements, respectively.
%
If a monomial term $t(R, \vx)$
results from $l_1$ type 1 and $l_2$ type 2 replacements
during the reduction of a term $s(\vx)$ in $\Lambda(\vx) C_p(\vx)$,
then the degrees in $\vct x$, for any $x_k$, of $s(\vx)$ and $t(R, \vx)$
are related as
%
\begin{equation}
  \deg_\vx s(\vx) - \deg_\vx t(R, \vx) = 2 l_1 + l_2.
\label{eq:degxdiffst}
\end{equation}
%
Similarly, the degrees in $R$ satisfy
\[
  \deg_R s(\vx) - \deg_R t(R, \vx) = - l_1,
\]
but since $\deg_R s(\vx) = 0$,
\begin{equation}
  \deg_R t(R, \vx) = l_1.
\label{eq:degRt}
\end{equation}

%
Now if the monomial $t(R, \vx)$ settles in the $q$th column of
  the matrix $\vct T(R)$, as part
  of $T_{pq}(R) C_q(\vx)$ in \refeq{xcp0},
then
  $t(R, \vx)$
  must be
%the product of
%  a monomial of $R$ \big[as part of $T_{pq}(R)$\big]
%  and one of the
  a generator of $C_q(\vx)$;
so
%
\begin{equation}
  \deg_\vx t(R, \vx) = |q|.
\label{eq:degxt}
\end{equation}
%
Since $s(\vx)$ is part of $\Lambda(\vx) C_p(\vx)$,
  we have
%
\begin{equation}
  \deg_\vx s(\vx) = \deg_\vx \Lambda(\vx) + \deg_\vx C_p(\vx)
  = n + |p|.
\label{eq:degxs}
\end{equation}
%
%
From \refeqs{degxdiffst}, \req{degxt}, \req{degxs}, we get
\[
  n + |p| - |q| = 2 \, l_1 + l_2,
\]
and
\begin{equation}
  l_1  =    (n + |p| - |q| - l_2)/2
             \le  (n + |p| - |q|)/2.
\label{eq:l1limit}
\end{equation}
By \refeq{degRt}, we get
\begin{align*}
  \deg_R T_{pq}(R)
  = \max\{ \deg_R t(R, \vx) \}
  = \max\{ l_1 \}
  \le   (n + |p| - |q|)/2,
\end{align*}
where the equality holds when all replacements are type 1 ($l_2 = 0$).

Finally, each term of the determinant
$A_n\RX = \big|\lambda \, \vct I - \vct T(R)\big|$
is given by
$(-1)^s \prod_{p} \big[\lambda \, \delta_{p q} - T_{pq}(R)\big]$,
where $p$ runs through rows of the matrix
  and $\{q\}$ is a permutation of $\{p\}$,
  with $(-1)^s$ being the proper sign.
Summing over rows under this condition yields
\begin{align*}
  \deg_R A_n\RX
  = \max \sum_{p \in \Bset} \deg T_{pq}(R)
  \le N(n) \, \big(n + |p| - |q|\big)/2 = n N(n)/2,
\end{align*}
where equality can be achieved if $q = \bar p$ in every row.
By \refeq{necklace} we have \refeqsub{degR}{a}.
%
The first few values are 1, 3, 6, 12, 20, 42, 70, 144, 270, 540, 1034, 2112, 4108, \dots, starting from $n = 1$.

To show \refeqsub{degR}{b}, we take the degree in $R$ of \refeq{prod}.
So $\sum_{d|n} \beta(d) \, \big(n/d\big) = N(n) \, n/2$,
whose inversion is
  $\beta(n)/n = \sum_{d|n} \mu(n/d) \, N(d)/2 = L(n)/2$.
The last step follows from inverting \refeq{necklacelyndon}.
%
The first few values are 1, 1, 3, 6, 15, 27, 63, 120, 252, 495, 1023, 2010, 4095, \dots, starting from $n = 1$.

\refeqsub{degR}{c} follows directly from taking the degree in $R$ of \refeq{origfac}.
The first few values are 1, 0, 1, 3, 11, 20, 57, 108, 240, 472, 1013, 1959, 4083, \dots, starting from $n = 1$.
\end{proof}

\refeqsub{degR}{b} was long known \cite{mira, stephenson2},
and \reqsub{degR}{c} was recently derived \cite{blackhurst}.

\section{\label{sec:henon}H\'enon map}

We now extend the method to the H\'enon map \cite{henon}:
\begin{equation}
  x_{k+1} = 1 + y_k - a \, {x_k}^2, \quad
  y_{k+1} = b \, x_k.
\label{eq:henon}
\end{equation}
%
We change variable $x_k \leftarrow a x_k$, $y_k \leftarrow a y_k$, and
\begin{equation}
  x_{k+1} = a + y_k - {x_k}^2, \quad
  y_{k+1} = b \, x_k.
\tag{$\ref{eq:henon}'$}
\label{eq:henons}
\end{equation}
%
Since neither $a$ nor $b$ is changed during the transformation,
\refeq{henon} and \refeq{henons} share the
same onset and bifurcation points
in terms of $a$ and $b$.
%
We also see that if $b \rightarrow 0$ and $a \rightarrow R$,
\refeq{henons} is reduced to the logistic map \refeq{logmaps}.

Since $y_k = b \, x_{k-1}$, we can ignore $y_k$ and work with
  cyclic polynomials of $x_k$ only,
the square free reduction is now
${x_k}^2 \rightarrow a + b x_{k-1} - x_{k+1}$.

The stability of \refeq{henons} can be found from the Jacobian matrix
\[
  J_b(x_k)
  \equiv \left(
    \begin{array}{ccc}
      \partial x_{k+1}/\partial x_k & \partial x_{k+1}/\partial y_k \\
      \partial y_{k+1}/\partial x_k & \partial y_{k+1}/\partial y_k \\
    \end{array}
  \right)
  =
  \left(
    \begin{array}{ccc}
      -2 x_k & 1 \\
      b & 0
    \end{array}
  \right).
\]
The eigenvalue $\lambda$ of the composite Jacobian
$J_b(x_1) \cdots J_b(x_n)$ can be computed from
%
\begin{equation}
\big|\, \lambda \, \vct I - J_b(x_1) \cdots J_b(x_n) \,\big|
  = \lambda^2 - \Theta(\vx) \,\lambda +(-b)^n = 0,
%\tag{$\ref{eq:der}'$}
\label{eq:henonder}
\end{equation}
%
where $\Theta(\vx)$ and $(-b)^n$
are the trace and determinant of
the matrix product $J_b(x_1) \cdots J_b(x_n)$,
respectively \cite{hitzl}.
In a stable cycle, the magnitude of $\lambda$
cannot exceed 1; so we replace $\lambda$ by $+1$ or $-1$
in \refeq{henonder}
to obtain the onset or bifurcation point, respectively.
\refeq{henonder} is the counterpart of \refeq{der}.

Since cyclically rotating matrices in a product does not alter the trace,
$\Theta(\vx)$ is a cyclic polynomial of $\vx = \{ x_k \}$.
%e.g.,
%$\Theta(\vx) = 4 x_1 x_2 + 2 \, b$ for $n = 2$ and
%$\Theta(\vx) = -8 x_1 x_2 x_3 - 2 \, b (x_1+ x_2+ x_3)$ for $n = 3$.
%
Thus, we can use $\Theta(\vx)$ to list \refeqs{xcp}
and then replace $\Theta(\vx)$ by $\lambda + (-b)^n/\lambda$
or $\pm\big[ 1 + (-b)^n \big]$
in \refeq{xr} to complete the solution.

\newcommand{\BB}[2]{B^{(2)}_{#1,#2}}
\newcommand{\BBB}[3]{B^{(4)}_{#1,#2,#3}}
\newcommand{\BBBB}[4]{B^{(6)}_{#1,#2,#3,#4}}

\begin{table}[h]\footnotesize
%\caption{
\tbl{Onset and bifurcation polynomials of the $n$-cycles of the H\'enon map.}
{\begin{tabular*}{\linewidth}{c c c c}
%{c p{.2\linewidth} p{.35\linewidth} p{.35\linewidth}}
\hline
$n$
& $\Theta(\vx)$
& Onset $P_n(a, b, +1)$ $^{\dagger, \ddagger}$
& Bifurcation $P_n(a, b, -1)$ $^{\dagger, \ddagger}$ \\
\hline
1
& $-2 x_1$
& $-A - (b-1)^2$
& $-A + 3(b-1)^2$ \\
%\hline
2
& $4 C_{12} + 2 b$
& $A-3 (b-1)^2$
& $A - \BB{5}{-6}$ \\
%\hline
3
&
  $-8C_{123}-2b C_1$
&
  \begin{minipage}[h]{.35\linewidth}
  $\left( -A + \BB{7}{10} \right)$ \\
  $\left\{ \left[ A -\frac{1}{2}\BB{1}{-8} \right]^2 + \frac{27}{4} (b^2-1)^2 \right\}$
  \end{minipage}

&
  \begin{minipage}[h]{.35\linewidth}
  \vspace{5mm}
  $\begin{aligned}
  -A^3&+2 \BB{4}{1} A^2 - 9 \BBB{2}{-6}{-7} A \\
  &+9 \BBBB{9}{6}{2}{-10}
  \end{aligned}$
  \vspace{5mm}
  \end{minipage} \\
%\hline
4
& \begin{minipage}[h]{.2\linewidth}
  $16 C_{1234} + 4 b C_{12} + 2b^2$
  \end{minipage}
& \begin{minipage}[h]{.35\linewidth}
  $\left(A - \BB{5}{-6}\right)$ \\
  $\left\{ \left[A + (b+1)^2\right]^2 + 4(b^2-1)^2 \right\}$ \\
  $\left\{ \left[A - 3(b+1)^2\right]^3 - 108(b-1)^2(b+1)^4 \right\}$
  \end{minipage}
& %\begin{minipage}[h]{.35\linewidth}
  $\begin{aligned}
  &A^6 - 4A^5 \BB{3}{2} + A^4 \BBB{47}{68}{38} \\
  &-3A^3\BBBB{47}{62}{-83}{-212} + \left({\BBB{17}{12}{-6}}\right)^3  \\
  &+ A^2\BBB{17}{12}{-6}\BBB{31}{-60}{-186}
  \end{aligned}$
  %\end{minipage}
\\
%\hline
5
& %\begin{minipage}[m]{.2\linewidth}
  $\begin{aligned}
  -&32C_{12345}\\
  -&8bC_{123} -2b^2C_1
  \end{aligned}$
  %\end{minipage}
&
  \begin{minipage}[m]{.35\linewidth}
  \vspace{3mm}
  $\begin{aligned}
    &-\Big( A^4  -\BB{1}{-12} A^3 + \BBB{1}{6}{21}A^2 \\
    &+\BBBB{9}{-14}{70}{-80} A + \BBB{1}{1}{1}\BBB{31}{-89}{121}
    \Big) \\
    &\Big( A^{11} - \BB{31}{14} A^{10} + 2 \BBB{208}{206}{377} A^9 \\
    &-\cdots -75728722 b - 28629151\Big)
  \end{aligned}$
  \end{minipage}
& %\begin{minipage}[m]{.35\linewidth}
  $\begin{aligned}
  -A^{15} &+ 2 \BB{16}{1} A^{14}- \BBB{448}{60}{669} A^{13} \\
  &+ \cdots + 1291467969
  \end{aligned}$
  %\end{minipage}
\\
\vdots & \vdots & \vdots & \vdots
\\
9
& %\begin{minipage}{.2\linewidth}
  $\begin{aligned}
  &-512 C_{1\dots9}\\
  &-\cdots-2b^4 C_1
  \end{aligned}$
%  \begin{align*}
%  -512 C_{1\dots9} -128 b C_{1\dots7} -2b^4 C_1 \\
%  -32b^2(C_{12345} + C_{12347} + C_{12367}) \\
%  -8b^3 (C_{123} + C_{125} + C_{145} + C_{147})
%  \end{align*}
  %\end{minipage}

& %\begin{minipage}{.35\linewidth}
  $\begin{aligned}
  &-(A^6 + 12 b A^5 + \dots)
   \big( A^6 - 4\BB{4}{1}A^5 + \dots \big) \\
  &\Big( A^{240} - 8\BB{61}{1}A^{239} +4\BBB{29525}{1019}{58188}A^{238} \\
  &  -\dots +120670698649\dots712084645033 \Big)
  \end{aligned}$
  %\end{minipage}

& %\begin{minipage}{.35\linewidth}
  $\begin{aligned}
  &-\big(
   A^{252} - 504 (1+b^2) A^{251} \\
  +& 4 \BBB{31500}{16}{62067} A^{250} - \dots \\
  +& 5842146539\dots9260477441
  \big)
  \end{aligned}$
  %\end{minipage}
\\
\hline
\multicolumn{4}{p{\linewidth}}{
$^\dagger$
Definitions: $A \equiv 4 a$,
$\BB{p}{q} \equiv p (b^2+1) + q b$,
$\BBB{p}{q}{r} \equiv p (b^4+1) + q (b^3 + b) +r b^2$,
$\BBBB{p}{q}{r}{s} \equiv p (b^6 + 1) + q (b^5 + b) +r (b^4 + b^2) + sb^3$,
$\dots$.
}
\\
\multicolumn{4}{p{\linewidth}}{
$^\ddagger$
  The onset polynomials for $n$ from 1 to 4,
  and the bifurcation polynomials for $n$ from 1 to 3,
  agree with those in ref. \cite{hitzl}.
}\\
\hline
\end{tabular*}
\label{tab:henonpoly}
}
\end{table}

We computed the polynomials of $a$ and $b$
  at the onset and bifurcation points for $n$ up to 9.
The polynomials of $a$ and $b$
  at the onset and bifurcation points,
  as well as $\Theta(\vx)$,
  are listed in \reftab{henonpoly} for small $n$
(for larger $n$, see the website in \refsec{end}).

\section{\label{sec:cubic}Cubic map}

We now study the following cubic map \cite{strogatz}
\begin{equation}
  x_{k + 1} = f(x_k) = r \, x_k - {x_k}^3.
\label{eq:cubic}
\end{equation}
Since the new replacement rule
\begin{equation}
  {x_k}^3 \rightarrow r \, x_k - x_{k+1}
\label{eq:cubreplace}
\end{equation}
no longer eliminates squares,
%
we must extend the basis set of cyclic polynomials
  from the square-free ones to the cube-free ones,
  in using \refeq{xcp}.
We include in the basis of expansion
  $C_{112} = {x_1}^2 x_2 + {x_2}^2 x_3 + \dots + {x_n}^2 x_1$ ($n\ge3$),
but not
  $C_{1112} = {x_1}^3 x_2 + {x_2}^3 x_3 + \dots + {x_n}^3 x_1$.

%An interesting feature of the cubic map
%is that it is odd:
%for a trajectory $x_0, x_1, x_2, \ldots$
%the mirror $-x_0, -x_1, -x_2, \ldots$
%also satisfies the map.
%
%As a result,
However, we only need the cube-free cyclic polynomials of even degrees in $\vx$
to solve the problem,
%
because \refeq{cubic} contains only linear and cubic terms,
a cyclic polynomial with an odd (even) degree in $\vx$
can never be reduced to one with an even (odd) degree
by \refeq{cubreplace}.
%
%Thus we only need polynomials of even degrees.
%
For technical reasons, we will not use polynomials of odd degrees,
because the map allows a symmetric $2n$-cycle:
$x_1, x_2, \ldots, x_n, -x_1, -x_2, \ldots, -x_n$
(see \reffig{oddcycle}),
which makes all odd cyclic polynomials zero,
e.g., $C_1 = x_1 + x_2 + \dots + x_n - x_1 - x_2 - \dots - x_n = 0$.
%
Thus, the zero determinant condition, similar to that in \refeq{xr},
  would be useless for these cycles,
  if the odd-degree polynomials were used.

\begin{figure}[h]
  \begin{minipage}{\linewidth}
    \begin{center}
        \includegraphics[angle=-90, width=\linewidth]{oddcycle.pdf}
    \end{center}
  \end{minipage}%
  \caption{\label{fig:oddcycle}
  Odd-cycles of the cubic map.}
\end{figure}

We therefore have a theorem similar to \refthm{sqrfree}.
%
%
\begin{theorem}
  For the cubic map \refeq{cubic},
  any cyclic polynomial $K(\vx)$ of
  an $n$-cycle orbit
  $\vct x = \{x_1, \ldots, x_n\}$
  with an even degree in $\vct x$
  is a linear combination of
the even cube-free cyclic polynomials $C_p(\vx)$:
\[
  K(\vx) = \sum_{p \in \Bset} f_p(R) C_p(\vx),
\]
  where $\Bset = \{0, 11, 12, 13, \ldots, 1122, 1123, \ldots \}$ is
  the set of indices of all even cube-free cyclic polynomials,
  and $f_p(R)$ are polynomials of $R$.
  \label{thm:cubfree}
\end{theorem}

With the above change, the rest derivation is similar to that of the logistic map.
The new $\Lambda(\vx)$ should be
$\prod_{k=1}^n f'(x_k) = \prod_{k=1}^n (r - 3 {x_k}^2)$.
%
The polynomials of $r$
  at the onset and bifurcation points
for some small $n$ are shown in \reftab{cubpolygen} (general $\lambda$)
and \reftab{cubpoly} ($\lambda = \pm1$);
for larger $n$ up to 8,
we have saved the data on the website in \refsec{end}.
%
The representative $r$ values are listed in \reftab{crval}.
%
For complex $r$ and $\vx$,
we have plotted \reffig{cubbulb} for regions of stability.

\begin{table}[h]\footnotesize
  %\caption{
  \tbl{
  Minimal polynomials $P_n(r, \lambda)$ of
  the $n$-cycles of the cubic map \refeq{cubic}.
  }
%\begin{center}
{
\begin{tabular}{lc}
\hline
  $n$
& $P_n(r, \; \lambda)$ $^\dagger$
\\
\hline
1
&
$(\lambda - r) (\lambda + 2 r - 3)$
\\
2
&
  $
  \big[
  \cancel{\lambda - (2r+3)^2}
  \big]
  (\lambda + 2r^2 - 9)
  $
\\
3
&
$\begin{aligned}
  &\lambda^4
  + 2 (r+6)(r^2-9) \lambda^3
  -6 \big(8 r^6+12 r^5-66 r^4-81 r^3+54 r^2-243 r-729\big)
  \lambda^2
+2 (r^2-9) \big(16 r^7-252 r^5\\
-&216 r^4 +648 r^3+972 r^2+2187 r+4374\big) \lambda
+2 r (2r-3) (2 r+3)^2 (r^2-9) (2 r^2 - 9)^2 (4 r^2+9) + 531441
\end{aligned}$
\\
4
&
\begin{minipage}{.97\linewidth}
\vspace*{1mm}
$\begin{aligned}
&\big[ \cancel{
  (\lambda-8r^4+54r^2+81)^2
-4 (r^2-9)^2 \lambda
} \big]
\,^\ddagger\,
\big[
\lambda^8
+2(5 r^4-324) \lambda^7
+2(112 r^8-1296 r^6+3807 r^4-91854) \lambda^6 \\
+&\dots
+18075490334784 r^8
-61004779879896 r^6
-411782264189298 r^4
+1853020188851841
\big]
\end{aligned}$
\end{minipage}
\\
%5
%&
%\begin{minipage}{.97\linewidth}
%\vspace*{1mm}
%$\begin{aligned}
%\end{aligned}$
%\vspace{1mm}
%\end{minipage}
%\\
\vdots & \vdots
\\
\hline
\multicolumn{2}{p{\textwidth}}{
$^\dagger$
The factors from odd-cycles (see \refsec{oddcycle}) are struck out.
}\\
\multicolumn{2}{p{\textwidth}}{
$^\ddagger$
The $n = 4$ odd-cycles satisfy
$(\lambda^\odd + 9)^2 - 2(\lambda^\odd-27) r^2 - 8 r^4 = 0$,
  where $\lambda^\odd=\pm\sqrt\lambda$.
} \\
\hline
\end{tabular}
\label{tab:cubpolygen}
}
%\end{center}
\end{table}

\begin{table}[h]\footnotesize
\tbl{
%\caption{
Onset and bifurcation polynomials of the $n$-cycles of the cubic map \refeq{cubic}.}
%\begin{center}
{
\begin{tabular*}{\linewidth}{l c c}
%{c p{.2\linewidth} p{.35\linewidth} p{.35\linewidth}}
\hline
$n$
&
Onset $P_n(r, +1)$ $^\dagger$
&
Bifurcation $P_n(r, -1)$ $^\dagger$
\\
\hline
1
&
$-(r-1)^2$
&
$-(r+1)(r-2)$
\\
2
&
$-2 (r-2) (r+1) (r+2)^2$
&
$-(r^2-5) (2 r^2+6 r+5)$
\\
3
&
\begin{minipage}{.45\linewidth}
\vspace{3mm}
$\begin{aligned}
&(r^2+r+1) (4 r^2-14 r+13) \\
&(4 r^8+16 r^7-35 r^6-206 r^5-113 r^4\\
&+376 r^3+715 r^2+1690 r+2197)
\end{aligned}$
\vspace{1mm}
\end{minipage}
&
\begin{minipage}{.5\linewidth}
\vspace{3mm}
$\begin{aligned}
&16 r^{12}+24 r^{11}-288 r^{10}-434 r^9\\
+&1539 r^8+2358 r^7-1434 r^6-2556 r^5-8541 r^4\\
-&11816 r^3+15288 r^2+24696 r+38416
\end{aligned}$
\vspace{1mm}
\end{minipage}
\\
4
&
\begin{minipage}{.45\linewidth}
\vspace{3mm}
$\begin{aligned}
-&8(r^2-8) (r^2-5) (r^2+1) (2 r^2-6 r+5) \\
&(2 r^2+6 r+5) (2 r^4-13 r^2-25)^2 \\
&(1024 r^{22}-32512 r^{20}+402304 r^{18} \\
-&2364832 r^{16}+5389924 r^{14}+9715769 r^{12} \\
-&73067038 r^{10}+58934785 r^{8}+235761152 r^6 \\
-&160907264 r^4-671088640 r^2-2097152000)
\end{aligned}$
\vspace{3mm}
\end{minipage}
&
$\begin{aligned}
&-(16 r^8-216 r^6+410 r^4+2142 r^2+1681) \\
&(8192 r^{32}-387072 r^{30}+7834624 r^{28} -88031232 r^{26}\\
&+585876512 r^{24}-2158227720 r^{22} +2211361312 r^{20}\\
&+15958823175 r^{18}  -68871388441 r^{16} +59290039854 r^{14}\\
&+234882618673 r^{12} -524807876277 r^{10} -72612143404 r^8\\
&+308406843576 r^6 +1539579145957 r^4-7984925229121)
\end{aligned}$
\\
\vdots & \vdots & \vdots
\\
8
&
$\begin{aligned}
&-8192 (r^4+1) (2 r^4-18 r^2+41) \\
&(8 r^4-48 r^3+108 r^2-108 r+41) \\
&(8 r^4+48 r^3+108 r^2+108 r+41) \dots\\
%&(16 r^8-216 r^6+410 r^4+2142 r^2+1681) \\
%&(8192 r^{32}-\dots-7984925229121) \\
%&(16384 r^{36}-\dots-1310720000000000) \\
%&(131072 r^{40}-\dots-13422659310152401)^2 \\
&(22016722240\dots14954924752896r^{3108} \\
&-\dots-180097954\dots2522413056\times 10^{400})
\end{aligned}$
&
$\begin{aligned}
-&(17592186044416 r^{80} +\dots+ \\
&144564714832407908402064153121600801) \\
&(4841528421712030\dots03048551060078592 r^{3200}\\
&-\dots-25263420710\dots173884723232001)
\end{aligned}$
\\
\hline
\multicolumn{3}{p{\linewidth}}
{
$^\dagger$
Although $P_n(r, \lambda)$ is the minimal polynomial for a general $\lambda$,
it may contain a pre-factor (e.g., $-2$ in the $n=2, \lambda=+1$ case).
}\\
\hline
\end{tabular*}
%\end{center}
\label{tab:cubpoly}
}
\end{table}

\begin{table}[h]\footnotesize

%\caption{
\tbl{
  Smallest positive $r$ at the onset and bifurcation points
  of the $n$-cycles of the cubic map.
  }
%\begin{center}
{
\begin{tabular}{l l l l l l l l}
%\begin{tabularx}{\textwidth}{
%  >{\hsize=0.5\hsize\centering\arraybackslash}X
%  >{\hsize=1.6\hsize}X
%  >{\hsize=1.6\hsize}X
%  >{\hsize=0.3\hsize\raggedright\arraybackslash}X |
%  >{\hsize=0.5\hsize\centering\arraybackslash}X
%  >{\hsize=1.6\hsize}X
%  >{\hsize=1.6\hsize}X
%  >{\hsize=0.3\hsize\raggedright\arraybackslash}X
%}
%\begin{tabular*}{\textwidth}{l l l l c | c l l l l}
\hline
  $n^\dagger$
& Onset$^\ddagger$
& Bifurcation$^\ddagger$
& \#$^*$
&
%\hspace{2mm} & $\hspace{2mm}$ &
  $n^\dagger$
& Onset$^\ddagger$
& Bifurcation$^\ddagger$
& \#$^*$ \\
\hline
$1$     & $1.0000000000_1$      &  $2.0000000000_1$       & 2   &
$6$     & $2.3334877526_{304}$  &  $2.3355337580_{336}$   & 56  \\
$2'$    & $2.0000000000_1$      &  $2.2360679775_2$       & 2   &
$6'$    & $2.4608286739_{12}$   &  $2.4657090579_{336}$   & 4   \\
$3$     & $2.4504409645_{8}$    &  $2.4608286739_{12}$    & 4   &
$7$     & $2.3729872678_{1080}$ &  $2.3732727868_{1092}$  & 156 \\
$4$     & $2.5478350393_{22}$   &  $2.5488312193_{32}$    & 8   &
$8$     & $2.3525990555_{3108}$ &  $2.3527637793_{3200}$  & 400 \\
$4''$   & $2.2360679775_{2}$    &  $2.2880317545_{32}$    & 2   &
$8'$    & $2.5488312193_{32}$   &  $2.5493247379_{3200}$  & 8   \\
$5$     & $2.3939250274_{112}$  &  $2.3957922744_{120}$   & 24  &
$8'''$  & $2.2880317545_{32}$   &  $2.2992279397_{3200}$  & 2   \\
\hline
\multicolumn{8}{p{\textwidth}}{
$^\dagger$
  $\,'$, $\,''$, or $\,'''$ means
    a cycle under
    the first, second, or third successive period-doubling, respectively.
} \\
\multicolumn{8}{l}{
$^\ddagger$
  The subscripts are the degrees of the corresponding minimal polynomial.
} \\
\multicolumn{8}{l}{
$^*$
  The number of similar cycles
    (for $n > 1$, only half of them have positive $r$).
} \\
\hline
\end{tabular}
%\end{tabularx}
%\end{tabular*}
%\end{center}
\label{tab:crval}
}
\end{table}

\begin{figure}[h]
  \begin{minipage}{\linewidth}
    \begin{center}
        \includegraphics[angle=-90, width=\linewidth]{cubbulb.pdf}
    \end{center}
  \end{minipage}%
  \caption{
  \label{fig:cubbulb}
  Stable regions of the $n$-cycles of the cubic map \refeq{cubic}
  with a complex $R$;
  obtained from $P_n(R, e^{i\phi}) = 0$ with $\phi \in [0, 2\pi]$
  cf. \reffig{logbulb}.
}
\end{figure}

\subsection{Counting cycles}

We now compute the number of the even cube-free cyclic polynomials
by establishing a one-to-one correspondence between
the cube-free cyclic polynomials and the \emph{ternary} necklaces,
in which each bead of the string is assigned a number
0, 1, or 2, instead of just 0 or 1.
%
For example, the necklace $\mathbf{212001\cdots}$
corresponds to $C_{112336}(\vx)$,
whose generator is
${x_1}^2 \, {x_2} \, {x_3}^2 \, x_6$:
the first bead is \textbf{2} for ${x_1}^\mathbf{2}$,
 the second is \textbf{1} for ${x_2}^\mathbf{1}$,
 the third is \textbf{2} for ${x_3}^\mathbf{2}$,
 and the sixth is \textbf{1} for ${x_6}^\mathbf{1}$.
%
A necklace is even,
if the corresponding cyclic polynomial has an even degree in $\vx$.
%
This means that the sum of numbers (0, 1, or 2)
  on the beads of the necklace,
  which equals the degree in $\vx$ of the polynomial, is also even.

%Now, the number of the cube-free cyclic polynomials
%is now equal to that of total necklaces
%\[
%  N_3(n) = (1/n) \sum_{d|n} \phi(n/d) 3^d.
%\]
%
%The proof is similar to that in \refsec{degprimfac}.
%For even necklaces, we have

\begin{theorem}
The number of the even ternary necklaces
or the cube-free cyclic polynomials for the cubic map of even degrees in $\vx$
is given by
\begin{equation}
  N_e(n) = \frac{1}{n} \sum_{c d = n} \phi(c)
    \left[
      3^d - \odd(c) \frac{3^d-1}{2}
    \right],
\label{eq:cubnecklace}
\end{equation}
where
$\odd(c) \equiv \big[1 - (-1)^c\big]/2$ is 1 if $c$ is odd or 0 if even.
\label{thm:cubnecklace}
\end{theorem}

\begin{proof}
We first show that the number of even ternary strings is $(3^n + 1)/2$.
%
Consider the generating function
\[
  Z\big(\{x_1, x_2,\dots, x_n\}\big) = \prod_{i=1}^n (1+x_i+{x_i}^2),
\]
where $1$, $x_i$, and $x_i^2$ correspond to the states that bead $i$
taking the number $0$, $1$, and $2$, respectively;
and the product over $n$ sums over states of independent beads.
%
In the expansion of $Z(\vx)$,
 each term (which takes the form
  ${x_1}^{e_1} {x_2}^{e_2} \dots {x_n}^{e_n}$,
  with $e_i = 0, 1, 2$)
represents a unique ternary string $e_1 e_2 \dots e_n$,
which is even, if $e_1 + e_2 + \dots + e_n$ is so.
%
By setting $x_1 = x_2 = \dots = x_n = 1$,
$Z=3^n$ equals the total number of ternary strings.
%
By setting $x_1 = x_2 = \dots = x_n = -1$,
a term representing an even (odd) ternary string
  is $+1$ ($-1$);
and $Z=(1-1+1)^n=1$
equals the difference between the number of even strings
  and that of odd strings.
%
Thus, the average $(3^n+1)/2$
gives the number of even ternary strings.

\begin{table}[h]\footnotesize
\tbl{
%\caption{
Two ways of counting the $N_e(2) = 4$ ternary necklaces for $n = 2$.
}
%\begin{center}
{
\begin{tabular}{c | c  c c | c  | c | c | c | c }
%\begin{tabularx}{\textwidth}{c | c  c c | c  | c | c | c | c }
\hline
        & \multicolumn{3}{c|}{$m = 1$}
        & $m = 2$
        & $c = n/d$
        & $T(d, c)$ $^\dagger$
        & $\phi(c)$ & $\phi(n/d) T(d, c)$\\
\hline
$d = 1$ & \hspace{1mm} $\mathbf{0}_{\times2}$ \hspace{1mm}
        & \hspace{1mm} $\mathbf{1}_{\times2}$ \hspace{1mm}
        & \hspace{1mm} $\mathbf{2}_{\times2}$ \hspace{1mm}
        & & $2$ & $3$ & $1$ & 3 \\
\hline
$d = 2$ & $\mathbf{00}$
        & $\mathbf{11}$
        & $\mathbf{22}$
        & \hspace{1mm} $\mathbf{20} (02)$ $^\ddagger$ \hspace{1mm}
        & $1$ & $3+1\cdot2=5$ & $1$ & 5 \\
\hline
$m \sum_{m|d, d|n} \phi(\frac{n}{d})$
      & \multicolumn{3}{c|}{$1\cdot(1+1) = 2$}
      & $2\cdot1 = 2$ &    \multicolumn{3}{c|}{} &  $\downarrow$\\
\hline
$N_e(n)\cdot n$
    & \multicolumn{3}{c|}{$3 \cdot 2$} & $1 \cdot 2$ &
  \multicolumn{3}{c|}{$\rightarrow$} & $4\cdot2 = 3 + 5$ \\
\hline
\multicolumn{9}{p{\linewidth}}{
  Bold strings are necklaces; others are their cyclic versions.
}
\\
\multicolumn{9}{p{\linewidth}}{
The subscript of a string means the number of repeats;
e.g.,
$\mathbf{1}_{\times2}$ means $\mathbf{1}$ repeated twice, or $\mathbf{11}$;
}
\\
\multicolumn{9}{p{\linewidth}}{
$^\dagger$ $T(d, c) \equiv 3^d - \odd(c)(3^d-1)/2$,
which is $3^d$ if $c$ is even,
or $(3^d+1)/2$ if $c$ is odd.
}
\\
\multicolumn{9}{p{\linewidth}}{
$^\ddagger$
The odd binary strings $\mathbf{10}$, $01$, $\mathbf{21}$, and $12$
  do not contribute to the sum, and are excluded from $T(d, c)$.
}
\\
\hline
\end{tabular}
%\end{tabularx}
%\end{center}
\label{tab:countcubnecklace}
}
\end{table}

The rest counting process is similar to that in \refsec{degprimfac}:
%
we construct the sum $n N_e(n)$ by two ways, as exemplified in \reftab{countcubnecklace}.
%
In the first way,
  for a fixed $d$ ($d|n$),
  if $c\equiv n/d$ is even,
    we count all ternary strings whose period $m$ divide $d$,
  but if $c$ is odd, we count only ternary strings
    whose first $d$ beads are even
    (because repeating an odd string an odd number times
    does not yield an even string);
  in either case, we multiple the result by $\phi(c)$.
%
The process for a fixed $d$ corresponds to a row of \reftab{countcubnecklace}.
%
Repeating the process for all $d$ gives
  $\sum_{cd = n} T(d, c) \, \phi(c)$,
  where $T(d, c)$ is the total number $3^d$ of period-$d$ ternary strings if $c$ is even,
  or the number $(3^d+1)/2$ of even strings if $c$ is odd.

In the second way,
  we look at the contribution from each necklace to the above sum.
An even period-$m$ necklace contributes a total of
  $m \times \sum_{m|d, d|n} \phi(n/d) = n$
  \big[the multiplier $m$ is for the $m$ cyclic versions, cf. \refeq{mphind}\big],
  while an odd necklace contributes nothing.
Thus, the sum equals $N_e(n)\cdot n$.
%
The process for a fixed necklace corresponds to
  a column of \reftab{countcubnecklace}.

So
\[
  N_e(n) \cdot n = \sum_{cd = n} T(d, c) \, \phi(c),
\]
which is \refeq{cublyndon}
after we divide both sides by $n$.
\end{proof}

%
$N_e(n)$ = 2, 4, 6, 14, 26, 68, 158, 424, \dots, starting from $n = 1$.
%

The characteristic polynomial $A_n(r, \lambda)$
  from the determinant equation
  has a degree $N_e(n)$ in $\lambda$.
Again, it encompasses the factors for the $n$-cycles
  and the shorter $d$-cycles, as long as $d|n$.
The minimal polynomial for the $n$-cycles can be obtained
  by \refthm{primfac} with proper substitutions
  \big[$R\rightarrow r$,
    $A_n(R, \lambda) \rightarrow A_n(r, \lambda)$,
    etc.\big].
The degree of the polynomial is given by

\begin{theorem}
The degree in $\lambda$ of
the minimal polynomial $P_n(r, \lambda)$ of the $n$-cycles is
\begin{equation}
  L_e(n) = \frac{1}{n} \sum_{cd = n} \mu(c)
    \left[
      1 + \odd(c)\frac{3^d-1}{2}
    \right],
\label{eq:cublyndon}
\end{equation}
where $\odd(n) = [1 - (-1)^n]/2$
is $1$ for an odd $n$,
but $0$ for an even $n$.
\label{thm:cublyndon}
\end{theorem}

\begin{proof}
Similar to the logistic map case \refeq{necklacelyndon},
  we have, for the cubic map,
\[
  N_e(n) = \sum_{d|n} L_e(d).
\]
Thus, we only need to inverse this equation to obtain $L_e(n)$.
But owing to the complexity of \refeq{cubnecklace},
  we need the Dirichlet generating function
  to simplify the result.

For a series $\alpha(n)$,
the Dirichlet generating function is defined as
\[
    G_\alpha(s) \equiv \sum_{n=1}^\infty \alpha(n) \, n^{-s}.
\]
In \reftab{genfunc}, we list the generating functions of
some common series,
and define a few new ones for $N_e(n)$ and $L_e(n)$, etc..

\begin{table}[h]\footnotesize
\tbl{
%\caption{
  Dirichlet generating functions for ternary necklaces.
}
%\begin{center}
{
\begin{tabular}{cccc}
%\begin{tabularx}{\textwidth}{
%  >{\hsize=0.6\hsize\raggedleft\arraybackslash}X
%  >{\hsize=1.4\hsize\centering\arraybackslash}X
%  >{\hsize=0.6\hsize\raggedleft\arraybackslash}X
%  >{\hsize=1.4\hsize\centering\arraybackslash}X
%}
\hline
$\alpha(n)$   &   $G_\alpha(s) = \sum_{n} \alpha(n)/n^{s}$  &
$\alpha(n)$   &   $G_\alpha(s) = \sum_{n} \alpha(n)/n^{s}$
\\
\hline
1             & $\zeta(s)$ $^\dagger$ &
\multicolumn{1}{|r}
{$N_e(n)$}      & $G_N(s)$ $^\ddagger$
\\
$\delta_{n,1}$         & $1$ $^\dagger$ &
\multicolumn{1}{|r}
{$n N_e(n)$}  & $G_N(s-1)$ $^\ddagger$
\\
$\mu(n)$    & $\zeta(s)^{-1}$ $^\dagger$ &
\multicolumn{1}{|r}
{$L_e(n)$}    & $G_L(s)$ $^\ddagger$
\\
$\phi(n)$   & $\zeta(s-1)/\zeta(s)$ $^\dagger$ &
\multicolumn{1}{|r}
{$nL_e(n)$}   & $G_L(s-1)$ $^\ddagger$
\\
$\odd(n)$   & $\zeta(s) (1-2^{-s})$ &
\multicolumn{1}{|r}
{$3^n$}       & $t(s)$ $^\ddagger$
\\
\cline{3-4}
$\mu(n) \, \odd(n)$
  & $\Big[ \zeta(s) (1-2^{-s}) \Big]^{-1}$ &
$\phi(n) \, \odd(n)$
  & $\frac{\zeta(s-1)}{\zeta(s)} \frac{1-2^{-s+1}}{1-2^{-s}}$
\\
\hline
\multicolumn{4}{p{\linewidth}}{
$^\dagger$
See ref. \cite{hardy} for proofs.
$\zeta(s) = \sum_n n^{-s}$ is the zeta function.
}\\
\multicolumn{4}{p{\linewidth}}{
$^\ddagger$
The sum is truncated at a large $M$ to avoid divergence.
}\\
\hline
\end{tabular}
%\end{tabularx}
%\end{center}
\label{tab:genfunc}
}
\end{table}

The generating function has an important property:
$G_\gamma(s) = G_\alpha(s) G_\beta(s)$,
if and only if $\gamma(n) = \sum_{d|n} \alpha(n/d)\, \beta(d)$ \cite{hardy}.
Thus,
  the terms of the sum $\sum_{d|n} \alpha(n/d)\, \beta(d)$
  of two sequences $\alpha$ and $\beta$
  can be readily found from expanding the generating function.

Another fact is if $G_\alpha(s)$ is the generating function of $\alpha(n)$,
then $G_\alpha(s-1)$ is that of $n \alpha(n)$,
for $\alpha(n)/n^{s-1} = \big[ n \alpha(n) \big] / n^s$.
Thus, the generating function of $n$ is $\zeta(s-1)$,
and
that of $n N_e(n)$ is $G_N(s-1)$
\big[$\zeta(s)$ is the generating function of 1,
  and $G_N(s)$ is that of $N_e(n)$,
  see \reftab{genfunc}\big].

We now compute the generating function of $\mu(n)\odd(n)$.
First, recall the generating function $G_\mu(s)$ of $\mu(n)$ is
\[
  G_\mu(s) = \sum_{n=1}^{\infty} \frac{\mu(n)}{n^s}
  = \prod_p \left( 1 - \frac{1}{p^s} \right),
\]
where $p$ goes through every prime.
%
The follows directly from expanding the product
  and the definition of $\mu(n)$,
which is $-1$ to the power of the number of distinct prime factors.
%
The same reasoning applies to
$G_{\mu, \odd}(s) = \sum_{n \text{ odd}} \mu(n)/n^s$
with the only difference being that all multiples $n$ of 2
are absent. So
%
\[
  G_{\mu, \odd}(s)
  = \sum_{n=1}^{\infty} \frac{\mu(n) \, \odd(n)}{n^s}
  = \sum_{n \text{ odd}} \frac{\mu(n)}{n^s}
  = \prod_{p \ge 3} \left( 1 - \frac{1}{p^s} \right).
\]
Comparing the two formulas yields
\[
  G_{\mu, \odd}(s)
  = G_{\mu}(s)
  \left(1- \frac{1}{2^s}\right)^{-1}
  =
   \left[ \zeta(s) \left(1- \frac{1}{2^s}\right) \right]^{-1}.
\]

Similarly,
we can compute the generating function of $\odd(n)$ as
\[
  G_\odd(s)
  \equiv \sum_{n=1}^{\infty} \frac{\odd(n)}{n^s}
  = \sum_{n \text{ odd}} \frac{1}{n^s}
  = \zeta(s) \left(1 - \frac{1}{2^s} \right).
\]
This can also be derived by taking the generating function of
both sides of the identity:
$\sum_{d|n} \mu(d) \odd(d) \, \odd(n/d) = \delta_{n, 1}$
\big[which is a modification of
$\sum_{d|n} \mu(d) = \delta_{n, 1}$\big].
%
It follows that the generating function of $n \, \odd(n)$ is $G_\odd(s-1)$.

The generating function $G_{\phi,\odd}(s)$
of $\phi(n) \odd(n)$ can be computed by taking the generating function
of both sides of the identity
\[
  n \, \odd(n)  = \sum_{d|n} \phi(d) \, \odd(d) \; \odd(n/d),
\]
i.e., if $n$ is even, then both sides are 0;
if odd, then $n = \sum_{d|n} \phi(d)$.
So
\[
  G_{\phi,\odd}(s) = \frac{G_\odd(s-1)}{G_\odd(s)}
  = \frac{\zeta(s-1)}{\zeta(s)} \frac{1 - 2^{-s + 1}}{1 - 2^{-s}}.
\]

We can now compute the generating function $G_N(s)$ of $N_e(s)$.
By multiplying $n$ to both sides of \refeq{cubnecklace},
and taking the generating function,
we find that
\begin{align*}
  G_N(s - 1)
    = G_\phi(s) t(s)- G_{\phi, \odd}(s) \frac{t(s)-\zeta(s)}{2}
    =
      \frac{\zeta(s-1) \Big[ t(s) + \zeta(s) \big( 1  - 2^{-s+1} \big) \Big]  }
           {2 \, \zeta(s) (1 - 2^{-s}) }
\end{align*}
where the left side $G_N(s-1)$ is
  the generating function of $N_e(n) \, n$,
and formulas in \reftab{genfunc} have been used.

Finally, we take the generating function of both sides of
 $N_e(n) = \sum_{d|n} L_e(d)$:
\[
  G_N(s) = \zeta(s) \, G_L(s),
\]
and
\begin{align*}
  G_L(s-1) = \frac{G_N(s - 1)}{\zeta(s-1)}
       = 1
        + \frac{ t(s) - \zeta(s) }
          {2 \, \zeta(s) \big(1 - 2^{-s}\big)}
       = 1 + \frac{t(s) - \zeta(s)}{2} G_{\mu, \odd}(s).
\end{align*}
Comparing the coefficients of the $n$th term ($n \ll M$),
  we find
\[
  n L_e(n) = \delta_{n,1} + \sum_{cd = n} \mu(c) \, \odd(c) \frac{3^d-1}{2},
\]
which is \refeq{cublyndon}, note that $\delta_{n,1} = \sum_{c|n}\mu(c)$.
%
\end{proof}

%
$L_e(n)$ = 2, 2, 4, 10, 24, 60, 156, 410, \ldots, starting from $n = 1$.
%
This is also the number of the $n$-cycles \cite{hao, hao2}.
Note that, for $n>1$, half of the cycles have negative $r$,
and the $x_k$ are imaginary.
However, in a transformed map,
\[
z_{k+1} = r \, z_k \, (1 - {z_k}^2),
\]
which differs from \refeq{cubic} by $x_k = \sqrt{r} z_k$,
$z_k$ in the negative-$r$ cycles are real.

Following a similar proof to \refthm{degR},
we find the corresponding degrees in $r$
of the characteristic polynomial $A_n(r, \lambda)$
  and minimal polynomial $P_n(r, \lambda)$ of the $n$-cycles
are $n N_e(n)$ and $n L_e(n)$, respectively.

\subsection{\label{sec:oddcycle}Odd-cycles}

Because of the symmetry $f(-x) = -f(x)$,
the minimal polynomial $P_n(r, \lambda)$
is subject to factorization for an even $n$.
%
If $x_{(n/2)+1} = -x_1$,
  then $x_1, \ldots, x_{n/2}, -x_1, \ldots, -x_{n/2}$
  is an $n$-cycle,
  for $x_{n+1} = - x_{(n/2)+1} = x_1$.
We call such a cycle an odd-cycle,
see \reffig{oddcycle} for examples.
%
Odd-cycles satisfy a polynomial
  of lower degrees in $\lambda$,
  which causes the factorization.
%
Suppose $\Lambda^\odd(\vx) \equiv \prod_{k = 1}^{n/2} f'(x_k)$ in the odd-cycle
 satisfies $P_{n/2}^\odd(r, \lambda^\odd) = 0$
\big[where $\lambda^\odd$ is the value of $\Lambda^\odd(\vx)$,
and $\lambda^\odd = \pm\sqrt \lambda$\,\big],
then $P^\odd_{n/2}(r, \sqrt \lambda) P^\odd_{n/2}(r, -\sqrt \lambda)$
is a factor of $P_{n}(r, \lambda)$.
%
For example, by solving the $n = 2$ odd-cycle,
  we have $- x_1 = r x_1 - {x_1}^3$, or ${x_1}^2 = r + 1$.
Since $\lambda^\odd = r - 3 {x_1}^2$,
$P^\odd_1(r, \lambda^\odd) = \lambda^\odd + 2 r + 3$.
%
Now the factor for 2-cycles (see \reftab{cubpolygen})
  is
  $P_2(r,\lambda) = -\big[(2r+3)^2 - \lambda\big]\,(\lambda + 2r^2-9)$,
  whose first factor is indeed
  $P^\odd_1(r, \sqrt \lambda) \, P^\odd_1(r, -\sqrt \lambda)
   = (\sqrt \lambda + 2 r + 3)(-\sqrt \lambda + 2 r + 3)$.
%
The example for $n=4$ is shown in \reftab{cubpolygen}.

\section{\label{sec:end}Summary and discussions}

We now summarize the algorithm for a one-dimensional polynomial map.
%
First, we list \refeqs{xcp}  with $\Lambda(\vx) = \prod_{k=1}^n f'(x_k)$.
This step populates elements of the matrix $\vct T(r)$,
where $r$ is the parameter of the map.
%
The determinant $A_n(r, \lambda) = \big|\lambda \, \vct I - \vct T(r)\big|$,
with $\lambda$ being $+1$ and $-1$, then gives the characteristic
polynomial at onset and bifurcation points, respectively.
%
To filter out factors for the shorter $d$-cycles with $d|n$,
  we repeat the process for other divisors $d$ of $n$
  and then apply \req{primfac}.
%

When implemented on a computer,
it is often helpful to evaluate $A_n(r,\lambda)$ by Lagrange interpolation,
that is, we evaluate $A_n(r, \lambda)$ at a few different $r$,
e.g., $r = 0, \pm1, \pm2,\ldots$, then piece them together
to a polynomial.
The strategy also allows a trivial parallelization.

The algorithm (implemented as a Mathematica program)
was quite efficient.
%
For the logistic map, the bifurcation point for $n = 8$
took three seconds to compute on a desktop computer
(single core, Intel\textsuperscript{\textregistered} Dual-Core CPU 2.50GHz).
%
In comparison,
  the same problem took roughly 5.5 hours \cite{kk1}
  using Gr\"obner basis
  and 44 minutes in a later study \cite{lewis}.
To be fair, using the latest Magma, computing the Gr\"obner basis
  took 81 and 14 minutes, on the same machine
  for \refeq{logmap} and \refeq{logmaps}, respectively;
even so, our approach still had a 200-fold speed-up.

%
The exact polynomials of these maps are generally too large to print on paper,
  e.g., the polynomial for the logistic map with $n = 13$
    takes roughly seven megabytes to write down.
%
We therefore save the polynomials and programs of the three maps on the web site
http://logperiod.appspot.com.

%Compared with other approaches \cite{hitzl, gordon, bailey1, kk1, hao, hao2}
%it appeared to be simpler and more transparent,
%as it only requires the computation of a determinant.

%\section*{Acknowledgements}
\nonumsection{Acknowledgments} \noindent
I thank Drs. T. Gilbert and Y. Mei for helpful communications.
Computing time on the Shared University Grid at Rice,
funded by NSF under Grant EIA-0216467, is gratefully acknowledged.

%\appendix{}

% ws-ijbc dislike the following
%\appendix

%\appendixpage

\appendix{\label{apd:per4}Simple derivation of 4-cycles}

The polynomials for the 4-cycles permits a short derivation.
We first list the explicit equations:
%
%
%
\begin{subequations}
\label{eq:x4}
\begin{align}
  x_2 &= R - x_1^2, \\
  x_3 &= R - x_2^2, \\
  x_4 &= R - x_3^2, \\
  x_1 &= R - x_4^2,
\end{align}
\end{subequations}
%
$\big[\mathrm{\refeqsub{x4}{a}} - \mathrm{\refeqsub{x4}{c}}\big]
\times
\big[\mathrm{\refeqsub{x4}{b}} - \mathrm{\refeqsub{x4}{d}}\big]$
yields $1 + (x_1 + x_3) (x_2 + x_4) = 0$,
since $x_1 \ne x_3, x_2 \ne x_4$.
%
Hence, with
$y_1 \equiv x_1 + x_3$, $y_2 \equiv x_2 + x_4$,
$z \equiv y_1 + y_2$,
we have
%
%
%
\begin{subequations}
\begin{align}
y_1 y_2       &= -1 \\
y_1^2 + y_2^2 & = (y_1 + y_2)^2 - 2 y_1 y_2 = z^2 + 2 \\
y_1^3 + y_2^3 & = (y_1 + y_2)^3 - 3 y_1 y_2 (y_1 + y_2) = z^3 + 3 z.
\end{align}
\label{eq:ypow4}
\end{subequations}
%
%
Multiplying \refeqsub{x4}{a} by $x_1$ or $x_3$,
then summing over cyclic versions yields
\begin{subequations}
\begin{align}
y_1 y_2 &= R z - \big[(x_1^3 + x_3^3) + (x_2^3 + x_4^3)\big],\\
y_1 y_2 &= R z - \big[x_1 x_3 (x_1 + x_3) + x_2 x_4 (x_2 + x_4)\big].
\end{align}
\label{eq:p4q}
\end{subequations}
%
From
$\mathrm{\refeqsub{p4q}{a}} + 3 \times \mathrm{\refeqsub{p4q}{b}}$,
we have
$4 \, y_1 y_2 = 4 R z - (y_1^3 + y_2^3)$,
%
and by \refeqs{ypow4},
\begin{equation}
  z^3 - (4 R - 3) z - 4 = 0.
  \label{eq:xr4s}
\end{equation}
%
%
Since $2 x_1 x_3 = y_1^2 - (x_1^2 + x_3^2) = y_1^2 - 2 R + y_2$,
and $2 x_2 x_4 = y_2^2 - 2 R + y_1$,
%
%Using \refeqs{ypow4} to simplify the right hand side, we find
\begin{equation}
  X \equiv x_1 x_2 x_3 x_4 = \frac{1}{2} R z(1 - z) + (R^2 - R + 1),
\label{eq:der4}
\end{equation}
where we have used \refeqs{ypow4} and \req{xr4s} to simplify the result.
%$X=1/16$ and $-1/16$ at the onset and bifurcation points, respectively.
%
Dividing the polynomial in \refeq{xr4s} by that in \refeq{der4}
yields $z = (R^2-3R-X+1)/(R^2-R+X-1)$,
and plugging it back to \refeq{der4} gives
   $R^6 -3 R^5
  + (3 + X) (R^4 - R^3)
  + (1 - X) (2 + X) R^2
  + (1 - X)^3 = 0$,
which is the same as the first factor of \refeq{xr4}
  with $X = \lambda/16$.

%\section{\label{apd:cublyndon}Proof of \refthm{cublyndon}}

\begin{thebibliography}{50}

\bibitem[May(1976)]{may}
  May, R. H. [1976]
  ``Simple mathematical models with very complicated dynamics,''
  {\it Nature}
  \textbf{261},
  459--467.

\bibitem[Strogatz(1994)]{strogatz}
  Strogatz, S. H. [1994]
  {\it Nonlinear Dynamics and Chaos}
  (Addison-Wesley. Reading, MA).

\bibitem[Saha \& Strogatz(1995)]{saha}
  Saha, P. \& Strogatz, S. H. [1995]
  ``The birth of period three,''
  {\it Mathematics Magazine}
  \textbf{68},
  42--47.

\bibitem[Kotsireas \& Karamanos(2004)]{kk1}
  Kotsireas, I. S. \& Karamanos, K. [2004]
  ``Exact computation of the bifurcation point $B_4$ of the logistic map
  and  the Bailey-Broadhurst conjectures,''
  {\it International Journal of Bifurcation and Chaos}
  \textbf{14},
  2417--2423.

\bibitem[Stephenson(1992)]{stephenson}
  Stephenson, J. [1992]
  ``Formulae for cycles in the Mandelbrot set III,''
  {\it Physica A}
  \textbf{190},
  117--129.

\bibitem[Bechhoefer(1996)]{bechhoefer}
  Bechhoefer, J. [1996]
  ``The birth of period 3, revisited,''
  {\it Mathematics Magazine}
  \textbf{69},
  115--118.

\bibitem[Gordon(1996)]{gordon}
  Gordon, W. B. [1996]
  ``Period three trajectories of the logistic map,''
  {\it Mathematics Magazine}
  \textbf{69},
  118--120.

\bibitem[Burm \& Fishback(2001)]{burm}
  Burm, J. \& Fishback, P. [2001]
  ``Period-3 Orbits via Sylvester's Theorem and Resultants,''
  {\it Mathematics Magazine}
  \textbf{74},
  47--51.

\bibitem[Zhang(2010)]{zhang}
  Zhang, C. [2010]
  ``Period three begins,''
  {\it Mathematics Magazine}
  \textbf{83},
  295--297.

\bibitem[Bailey \& Broadhurst(2000)]{bailey1}
  Bailey, D. H. \& Broadhurst, D. J. [2000]
  ``Parallel integer relation detection: techniques and applications,''
  {\it Mathematics of Computation}
  \textbf{70},
  1719--1736.

\bibitem[Bailey {\it et al.}(2006)]{bailey2}
  Bailey, D. H., Borwein, J. M., Kapour, V. \& Weisstein, E. W. [2006]
  ``Ten problems in experimental mathematics,''
  {\it The American Mathematical Monthly}
  \textbf{113},
  481--509.

\bibitem[Lewis(2008)]{lewis}
  Lewis, R. H. [2008]
  ``Heuristics to accelerate the Dixon resultant,''
  {\it Mathematics and Computers in Simulation}
  \textbf{77},
  400--407.

\bibitem[Hardy \& Wright(2008)]{hardy}
  Hardy, G. H. \& Wright, E. M. [2008]
  {\it An Introduction to the Theory of Numbers}
  (Oxford University Press, USA).

\bibitem[Hao(1989)]{hao}
  Hao, B.-L. [1989]
  {\it Elementary Symbolic Dynamics and Chaos in  Dissipative Systems}
  (World Scientific, Singapore).

\bibitem[Hao(2000)]{hao2}
  Hao, B.-L. [2000]
  ``Number of periodic orbits in continuous maps of
  the interval complete solution of the counting problem,''
  {\it Annals of Combinatorics}
  \textbf{4},
  339--346.

\bibitem[Lutzky(1988)]{lutzky}
  Lutzky, M. [1988]
  ``Counting stable cycles in unimodal iterations,''
  {\it Physics Letters A}
  \textbf{131},
  248--250.

\bibitem[Mira(1987)]{mira}
  Mira, C. [1987]
  {\it Chaotic Dynamics}
  (World Scientific, Singapore).

\bibitem[Stephenson(1991)]{stephenson2}
  Stephenson, J. [1991]
  ``Formulae for cycles in the Mandelbrot set,''
  {\it Physica A}
  \textbf{177},
  416--420.

\bibitem[Blackhurst(2011)]{blackhurst}
  Blackhurst, J. [2011]
  ``Polynomials of the bifurcation points of the logistic map,''
  {\it International Journal of Bifurcation and Chaos}
  \textbf{21},
  1869--1877.

\bibitem[H\'enon(1976)]{henon}
  H\'enon, M. [1976]
  ``A two-dimensional mapping with a strange attractor,''
  {\it Communications in Mathematical Physics}
  \textbf{50},
  69--77.

\bibitem[Hitzl(1985)]{hitzl}
  Hitzl, D. L. \& Zele, F. [1985]
  ``An exploration of the H\'enon quadratic map,''
  {\it Physica D}
  \textbf{14},
  305--326.

\end{thebibliography}

\end{document}

### 2013-04-14 doc/pc.tex
initial commit

--- 2013-04-14 doc/pc-ijbc.tex
@@
-\documentclass{ws-ijbc}
+\documentclass[preprint]{revtex4-1}
+%\usepackage[width=5.65in, height=9.3in]{geometry}
+\usepackage{amsmath}
+\usepackage{amsthm}
+\usepackage{tabularx}
 \usepackage{multirow}
 \usepackage{centernot}
-%\usepackage{hyperref}
+\usepackage{hyperref}
 \usepackage{graphicx}
-\usepackage{epstopdf}
+%\usepackage{setspace}
+\usepackage{booktabs}
 \usepackage{calc}
 \usepackage{cancel} % strike out (cancel) in math mode
-\usepackage{ws-rotating}
+%\usepackage{appendix}
 \begin{document}
@@
 
-% ws-ijbc doesn't like the following lines
-%\newtheorem{theorem}{Theorem}
-%\newenvironment{remark}[1][1]%
-%{\par\noindent\textbf{Remark #1.} }{\medskip}
-
-\catchline{}{}{}{}{}
+\newtheorem{theorem}{Theorem}
+\newenvironment{remark}[1][1]%
+{\par\noindent\textbf{Remark #1.} }{\medskip}
 
@@
 \author{Cheng Zhang}
-%\affiliation{Applied Physics Program and Department of Bioengineering, \
-%Rice University, Houston, TX 77005}
-\address{Applied Physics Program \& Department of Bioengineering,
-Rice University, Houston, TX 77005, USA}
-
-\maketitle
-
-\begin{history}
-\received{}
-\end{history}
+\affiliation{Applied Physics Program and Department of Bioengineering, \
+Rice Univeristy, Houston, TX 77005}
+%\maketitle
 
@@
 \end{abstract}
-
-\keywords{Logistic map; H\'enon map; cubic map; cycles; exact polynomials.}
-
-%\maketitle
+\maketitle
 
@@
 \begin{table}[h]\footnotesize
-\tbl{
-Square-free cyclic polynomials $C_p(\vx)$ for the logistic map ($n \ge 5$).}
-%\begin{center}
-{
+\caption{Square-free cyclic polynomials $C_p(\vx)$ for the logistic map ($n \ge 5$).}
+\begin{center}
 \begin{tabular}{c c c c c}
@@
 \end{tabular}
+\end{center}
 \label{tab:sqrfreepoly}
-}
-%\end{center}
 \end{table}
@@
 
-\subsection{\label{sec:algo}Algorithm for fixed points of $f^n$}
+\subsection{\label{sec:algo}Algorithm for locating fixed points of $f^n$}
 
@@
   \big[ \lambda \, \vct I - \vct T(R) \big] \, \vct C = 0,
-\tag{\ref{eq:xcp}'}
+\tag{$\ref{eq:xcp}'$}
 \end{equation}
@@
 \begin{equation}
-  A_n\RX \equiv \big| \lambda \, \vct I - \vct T(R) \big| = 0.
+  A_n\RX \equiv \Big| \lambda \, \vct I - \vct T(R) \Big| = 0.
 \label{eq:xr}
@@
 
-\begin{remark}
-%\begin{remark}[1]
+\begin{remark}[1]
   For complex $R$ and $\vx$,
@@
 As a verification, the polynomials are
-alternatively derived in the Appendix.
+alternatively derived in \refapd{per4}.
 
 \begin{table}[h]\footnotesize
-  %\caption{
-  \tbl{
+  \caption{
   Characteristic polynomials $A_n\RX$ of
@@
   }
-%\begin{center}
-{
+\begin{center}
 \begin{tabular}{lc}
@@
 \end{tabular}
+\end{center}
 \label{tab:Anlog}
-}
-%\end{center}
 \end{table}
@@
 \begin{table}[h]\footnotesize
-  %\caption{
-  \tbl{
+  \caption{
   Smallest positive $r$ at the onset and bifurcation points
@@
   }
-%\begin{center}
-{
-\begin{tabular}{llllllll}
-%\begin{tabularx}{\textwidth}{
-%  >{\hsize=0.5\hsize\centering\arraybackslash}X
-%  >{\hsize=1.6\hsize}X
-%  >{\hsize=1.6\hsize}X
-%  >{\hsize=0.3\hsize\raggedright\arraybackslash}X |
-%  >{\hsize=0.5\hsize\centering\arraybackslash}X
-%  >{\hsize=1.6\hsize}X
-%  >{\hsize=1.6\hsize}X
-%  >{\hsize=0.3\hsize\raggedright\arraybackslash}X
-%}
+\begin{center}
+\begin{tabularx}{\textwidth}{
+  >{\hsize=0.5\hsize\centering\arraybackslash}X
+  >{\hsize=1.6\hsize}X
+  >{\hsize=1.6\hsize}X
+  >{\hsize=0.3\hsize\raggedright\arraybackslash}X |
+  >{\hsize=0.5\hsize\centering\arraybackslash}X
+  >{\hsize=1.6\hsize}X
+  >{\hsize=1.6\hsize}X
+  >{\hsize=0.3\hsize\raggedright\arraybackslash}X
+}
 \hline
@@
 \hline
-%\end{tabularx}
-\end{tabular}
+\end{tabularx}
+\end{center}
 \label{tab:rval}
-}
-%\end{center}
 \end{table}
@@
 
-%\begin{remark}[1]
-\begin{remark}
+\begin{remark}[1]
 The M\"obius function $\mu(n)$ is $(-1)^k$
@@
   or 0 if $n$ is divisible by a square of a prime.
-$\mu(n)$ = 1, $-1$, $-1$, 0, $-1$, 1, \ldots,
-  starting from $n = 1$.
+$\mu(n)$ = 1, $-1$, $-1$, 0, $-1$, 1, \ldots, starting from $n = 1$.
 The $\mu(n)$ is useful for inversion:
@@
 
-%\begin{remark}[2]
-\begin{remark}
+\begin{remark}[2]
 $B_{d,c}\RX$ is a polynomial of $\lambda$.
@@
 \begin{table}[h]\footnotesize
-  %\caption{
-  \tbl{
+  \caption{
   Onset and bifurcation polynomials %$P_n(R, \pm1)$
-  of the $n$-cycles of the simplified logistic map \refeq{logmaps}.
-  }
-{
-\label{tab:Pnlog}
+  of the $n$-cycles of the simplified logistic map \refeq{logmaps}.}
+\begin{center}
 \begin{tabular}{lcc}
@@
 \end{tabular}
-}
+\end{center}
+\label{tab:Pnlog}
 \end{table}
@@
   with a complex $R$;
-  obtained from $P_n(R, e^{i\phi}) = 0$ with $\phi \in [0, 2\pi]$,
+  obtained from $P_n(R, e^{i\phi}) = 0$ with $\phi \in [0, 2\pi]$
   cf. Fig. 3 in \cite{stephenson}.
@@
 
-%We will prove \refthm{primfac} by the following steps.
-%
 To show \refthm{primfac}, we first find the degrees in $\lambda$ of
@@
 \begin{table}[h]\footnotesize
-%\caption{
-\tbl{
-Two ways of counting the $N(4) = 6$ necklaces for $n = 4$.
+\caption{Two ways of counting the $N(4) = 6$ necklaces for $n = 4$.
 }
-%\begin{center}
-{
-%\begin{tabularx}{\textwidth}{c | c  c | c | c | c | c | c }
-\begin{tabular}{c | c  c | c | c | c | c | c }
+\begin{center}
+\begin{tabularx}{\textwidth}{c | c  c | c | c | c | c | c }
 \hline
@@
 \hline
-\end{tabular}
-%\end{tabularx}
-%\end{center}
+\end{tabularx}
+\end{center}
 \label{tab:countnecklace}
-}
 \end{table}
@@
 %
-$N(n)$ = 2, 3, 4, 6, 8, 14, 20, 36, 60, 108, 188, 352, 632, \ldots,
-  starting from $n = 1$.
+$N(n)$ = 2, 3, 4, 6, 8, 14, 20, 36, 60, 108, 188, 352, 632, \ldots, starting from $n = 1$.
 
@@
 \begin{proof}
+%
 Except a few special values of $R$,
@@
 The M\"obius inversion yields $L(n) = (1/n) \sum_{d\,|\,n} \mu(n/d) 2^{\,d}$.
-This formula was known to several authors \cite{hao, hao2, lutzky}.
+This formula was known to several authors \cite{hao, lutzky}.
 
@@
 Of course, $\lambda_c$ is a function of $R$.
-If we assume that $\lambda_c$ are distinct (see Remark \ref{remark:distinct} below),
+If we assume that $\lambda_c$ are distinct (see Remark 1 below),
   then the minimal polynomial $P_n\RX$,
@@
 
-%\begin{remark}[1]
-\begin{remark}
-\label{remark:distinct}
+\begin{remark}[1]
 Although all trajectory points $\vx^{(c)}$ are distinct in
@@
 
-%\begin{remark}[2]
-\begin{remark}
+\begin{remark}[2]
 $L(n)$ is also the number of aperiodic (i.e., period equal to $n$)
@@
 \begin{proof}
+%
 At the intersection of the $n$- and $d$-cycles,
@@
 
-\refeqsub{degR}{b} was long known \cite{mira, stephenson2},
+\refeqsub{degR}{b} was long known \cite{mira},
 and \reqsub{degR}{c} was recently derived \cite{blackhurst}.
@@
 \begin{table}[h]\footnotesize
-%\caption{
-\tbl{Onset and bifurcation polynomials of the $n$-cycles of the H\'enon map.}
-{\begin{tabular*}{\linewidth}{c c c c}
+\caption{Onset and bifurcation polynomials of the $n$-cycles of the H\'enon map.}
+\begin{center}
+\begin{tabular*}{\linewidth}{c c c c}
 %{c p{.2\linewidth} p{.35\linewidth} p{.35\linewidth}}
@@
 \end{tabular*}
+\end{center}
 \label{tab:henonpoly}
-}
 \end{table}
@@
 \begin{table}[h]\footnotesize
-  %\caption{
-  \tbl{
+  \caption{
   Minimal polynomials $P_n(r, \lambda)$ of
@@
 \end{tabular}
+\end{center}
 \label{tab:cubpolygen}
-}
-%\end{center}
 \end{table}
@@
 \begin{table}[h]\footnotesize
-\tbl{
-%\caption{
-Onset and bifurcation polynomials of the $n$-cycles of the cubic map \refeq{cubic}.}
-%\begin{center}
-{
+\caption{Onset and bifurcation polynomials of the $n$-cycles of the cubic map \refeq{cubic}.}
+\begin{center}
 \begin{tabular*}{\linewidth}{l c c}
@@
 \end{tabular*}
-%\end{center}
+\end{center}
 \label{tab:cubpoly}
-}
 \end{table}
@@
 \begin{table}[h]\footnotesize
-
-%\caption{
-\tbl{
+  \caption{
   Smallest positive $r$ at the onset and bifurcation points
@@
   }
-%\begin{center}
-{
-\begin{tabular}{l l l l l l l l}
-%\begin{tabularx}{\textwidth}{
-%  >{\hsize=0.5\hsize\centering\arraybackslash}X
-%  >{\hsize=1.6\hsize}X
-%  >{\hsize=1.6\hsize}X
-%  >{\hsize=0.3\hsize\raggedright\arraybackslash}X |
-%  >{\hsize=0.5\hsize\centering\arraybackslash}X
-%  >{\hsize=1.6\hsize}X
-%  >{\hsize=1.6\hsize}X
-%  >{\hsize=0.3\hsize\raggedright\arraybackslash}X
-%}
+\begin{center}
+\begin{tabularx}{\textwidth}{
+  >{\hsize=0.5\hsize\centering\arraybackslash}X
+  >{\hsize=1.6\hsize}X
+  >{\hsize=1.6\hsize}X
+  >{\hsize=0.3\hsize\raggedright\arraybackslash}X |
+  >{\hsize=0.5\hsize\centering\arraybackslash}X
+  >{\hsize=1.6\hsize}X
+  >{\hsize=1.6\hsize}X
+  >{\hsize=0.3\hsize\raggedright\arraybackslash}X
+}
 %\begin{tabular*}{\textwidth}{l l l l c | c l l l l}
@@
 \hline
-\end{tabular}
-%\end{tabularx}
+\end{tabularx}
 %\end{tabular*}
-%\end{center}
+\end{center}
 \label{tab:crval}
-}
 \end{table}
@@
   with a complex $R$;
-  obtained from $P_n(R, e^{i\phi}) = 0$ with $\phi \in [0, 2\pi]$
+  obtained from $P_n(R, e^{i\phi}) = 0$ with $\phi \in [0, 2\pi]$,
   cf. \reffig{logbulb}.
@@
 \begin{proof}
+
 We first show that the number of even ternary strings is $(3^n + 1)/2$.
@@
 \begin{table}[h]\footnotesize
-\tbl{
-%\caption{
-Two ways of counting the $N_e(2) = 4$ ternary necklaces for $n = 2$.
+\caption{Two ways of counting the $N_e(2) = 4$ ternary necklaces for $n = 2$.
 }
-%\begin{center}
-{
-\begin{tabular}{c | c  c c | c  | c | c | c | c }
-%\begin{tabularx}{\textwidth}{c | c  c c | c  | c | c | c | c }
+\begin{center}
+\begin{tabularx}{\textwidth}{c | c  c c | c  | c | c | c | c }
 \hline
@@
 \hline
-\end{tabular}
-%\end{tabularx}
-%\end{center}
+\end{tabularx}
+\end{center}
 \label{tab:countcubnecklace}
-}
 \end{table}
@@
 
-\begin{proof}
+\refeq{cublyndon} follows from the inversion
+  $L_e(n) = \sum_{d|n} \mu(n/d) \, N_e(n)$,
+after some algebra, as shown in \refapd{cublyndon}.
+%
+$L_e(n)$ = 2, 2, 4, 10, 24, 60, 156, 410, \ldots, starting from $n = 1$.
+%
+This is also the number of the $n$-cycles \cite{hao}.
+Note that, for $n>1$, half of the cycles have negative $r$,
+and the $x_k$ are imaginary.
+However, in a transformed map,
+\[
+z_{k+1} = r \, z_k \, (1 - {z_k}^2),
+\]
+which differs from \refeq{cubic} by $x_k = \sqrt{r} z_k$,
+$z_k$ in the negative-$r$ cycles are real.
+
+Following a similar proof to \refthm{degR},
+we find the corresponding degrees in $r$
+of the characteristic polynomial $A_n(r, \lambda)$
+  and minimal polynomial $P_n(r, \lambda)$ of the $n$-cycles
+are $n N_e(n)$ and $n L_e(n)$, respectively.
+
+\subsection{\label{sec:oddcycle}Odd-cycles}
+
+Because of the symmetry $f(-x) = -f(x)$,
+the minimal polynomial $P_n(r, \lambda)$
+is subject to factorization for an even $n$.
+%
+If $x_{(n/2)+1} = -x_1$,
+  then $x_1, \ldots, x_{n/2}, -x_1, \ldots, -x_{n/2}$
+  is an $n$-cycle,
+  for $x_{n+1} = - x_{(n/2)+1} = x_1$.
+We call such a cycle an odd-cycle,
+see \reffig{oddcycle} for examples.
+%
+Odd-cycles satisfy a polynomial
+  of lower degrees in $\lambda$,
+  which causes the factorization.
+%
+Suppose $\Lambda^\odd(\vx) \equiv \prod_{k = 1}^{n/2} f'(x_k)$ in the odd-cycle
+ satisfies $P_{n/2}^\odd(r, \lambda^\odd) = 0$
+\big[where $\lambda^\odd$ is the value of $\Lambda^\odd(\vx)$,
+and $\lambda^\odd = \pm\sqrt \lambda$\,\big],
+then $P^\odd_{n/2}(r, \sqrt \lambda) P^\odd_{n/2}(r, -\sqrt \lambda)$
+is a factor of $P_{n}(r, \lambda)$.
+%
+For example, by solving the $n = 2$ odd-cycle,
+  we have $- x_1 = r x_1 - {x_1}^3$, or ${x_1}^2 = r + 1$.
+Since $\lambda^\odd = r - 3 {x_1}^2$,
+$P^\odd_1(r, \lambda^\odd) = \lambda^\odd + 2 r + 3$.
+%
+Now the factor for 2-cycles (see \reftab{cubpolygen})
+  is
+  $P_2(r,\lambda) = -\big[(2r+3)^2 - \lambda\big]\,(\lambda + 2r^2-9)$,
+  whose first factor is indeed
+  $P^\odd_1(r, \sqrt \lambda) \, P^\odd_1(r, -\sqrt \lambda)
+   = (\sqrt \lambda + 2 r + 3)(-\sqrt \lambda + 2 r + 3)$.
+%
+The example for $n=4$ is shown in \reftab{cubpolygen}.
+
+\section{\label{sec:end}Summary and discussions}
+
+We now summarize the algorithm for a one-dimensional polynomial map.
+%
+First, we list \refeqs{xcp}  with $\Lambda(\vx) = \prod_{k=1}^n f'(x_k)$.
+This step populates elements of the matrix $\vct T(r)$,
+where $r$ is the parameter of the map.
+%
+The determinant $A_n(r, \lambda) = \big|\lambda \, \vct I - \vct T(r)\big|$,
+with $\lambda$ being $+1$ and $-1$, then gives the characteristic
+polynomial at onset and bifurcation points, respectively.
+%
+To filter out factors for the shorter $d$-cycles with $d|n$,
+  we repeat the process for other divisors $d$ of $n$
+  and then apply \req{primfac}.
+%
+
+When implemented on a computer,
+it is often helpful to evaluate $A_n(r,\lambda)$ by Lagrange interpolation,
+that is, we evaluate $A_n(r, \lambda)$ at a few different $r$,
+e.g., $r = 0, \pm1, \pm2,\ldots$, then piece them together
+to a polynomial.
+The strategy also allows a trivial parallelization.
+
+The algorithm (implemented as a Mathematica program)
+was quite efficient.
+%
+For the logistic map, the bifurcation point for $n = 8$
+took three seconds to compute on a desktop computer
+(single core, Intel\textsuperscript{\textregistered} Dual-Core CPU 2.50GHz).
+%
+In comparison,
+  the same problem took roughly 5.5 hours \cite{kk1}
+  using Gr\"obner basis
+  and 44 minutes in a later study \cite{lewis}.
+To be fair, using the latest Magma, computing the Gr\"obner basis
+  took 81 and 14 minutes, on the same machine
+  for \refeq{logmap} and \refeq{logmaps}, respectively;
+even so, our approach still had a 200-fold speed-up.
+
+%
+The exact polynomials of these maps are generally too large to print on paper,
+  e.g., the polynomial for the logistic map with $n = 13$
+    takes roughly seven megabytes to write down.
+%
+We therefore save the polynomials and programs of the three maps on the web site
+http://logperiod.appspot.com.
+
+%Compared with other approaches \cite{hitzl, gordon, bailey1, kk1, hao}
+%it appeared to be simpler and more transparent,
+%as it only requires the computation of a determinant.
+
+\section*{Acknowledgements}
+
+I thank Drs. T. Gilbert and Y. Mei for helpful communications.
+Computing time on the Shared University Grid at Rice,
+funded by NSF under Grant EIA-0216467, is gratefully acknowledged.
+
+\appendix
+%\appendixpage
+
+\section{\label{apd:per4}Simple derivation of 4-cycles}
+
+The polynomials for the 4-cycles permits a short derivation.
+We first list the explicit equations:
+%
+%
+%
+\begin{subequations}
+\label{eq:x4}
+\begin{align}
+  x_2 &= R - x_1^2, \\
+  x_3 &= R - x_2^2, \\
+  x_4 &= R - x_3^2, \\
+  x_1 &= R - x_4^2,
+\end{align}
+\end{subequations}
+%
+$\big[\mathrm{\refeqsub{x4}{a}} - \mathrm{\refeqsub{x4}{c}}\big]
+\times
+\big[\mathrm{\refeqsub{x4}{b}} - \mathrm{\refeqsub{x4}{d}}\big]$
+yields $1 + (x_1 + x_3) (x_2 + x_4) = 0$,
+since $x_1 \ne x_3, x_2 \ne x_4$.
+%
+Hence, with
+$y_1 \equiv x_1 + x_3$, $y_2 \equiv x_2 + x_4$,
+$z \equiv y_1 + y_2$,
+we have
+%
+%
+%
+\begin{subequations}
+\begin{align}
+y_1 y_2       &= -1 \\
+y_1^2 + y_2^2 & = (y_1 + y_2)^2 - 2 y_1 y_2 = z^2 + 2 \\
+y_1^3 + y_2^3 & = (y_1 + y_2)^3 - 3 y_1 y_2 (y_1 + y_2) = z^3 + 3 z.
+\end{align}
+\label{eq:ypow4}
+\end{subequations}
+%
+%
+Multiplying \refeqsub{x4}{a} by $x_1$ or $x_3$,
+then summing over cyclic versions yields
+\begin{subequations}
+\begin{align}
+y_1 y_2 &= R z - \big[(x_1^3 + x_3^3) + (x_2^3 + x_4^3)\big],\\
+y_1 y_2 &= R z - \big[x_1 x_3 (x_1 + x_3) + x_2 x_4 (x_2 + x_4)\big].
+\end{align}
+\label{eq:p4q}
+\end{subequations}
+%
+From
+$\mathrm{\refeqsub{p4q}{a}} + 3 \times \mathrm{\refeqsub{p4q}{b}}$,
+we have
+$4 \, y_1 y_2 = 4 R z - (y_1^3 + y_2^3)$,
+%
+and by \refeqs{ypow4},
+\begin{equation}
+  z^3 - (4 R - 3) z - 4 = 0.
+  \label{eq:xr4s}
+\end{equation}
+%
+%
+Since $2 x_1 x_3 = y_1^2 - (x_1^2 + x_3^2) = y_1^2 - 2 R + y_2$,
+and $2 x_2 x_4 = y_2^2 - 2 R + y_1$,
+%
+%Using \refeqs{ypow4} to simplify the right hand side, we find
+\begin{equation}
+  X \equiv x_1 x_2 x_3 x_4 = \frac{1}{2} R z(1 - z) + (R^2 - R + 1),
+\label{eq:der4}
+\end{equation}
+where we have used \refeqs{ypow4} and \req{xr4s} to simplify the result.
+%$X=1/16$ and $-1/16$ at the onset and bifurcation points, respectively.
+%
+Dividing the polynomial in \refeq{xr4s} by that in \refeq{der4}
+yields $z = (R^2-3R-X+1)/(R^2-R+X-1)$,
+and plugging it back to \refeq{der4} gives
+   $R^6 -3 R^5
+  + (3 + X) (R^4 - R^3)
+  + (1 - X) (2 + X) R^2
+  + (1 - X)^3 = 0$,
+which is the same as the first factor of \refeq{xr4}
+  with $X = \lambda/16$.
+
+\section{\label{apd:cublyndon}Proof of \refthm{cublyndon}}
+
+Here we prove \refthm{cublyndon} \big[or \refeq{cublyndon}\big]
+  for the cubic map.
+%
 Similar to the logistic map case \refeq{necklacelyndon},
@@
 \begin{table}[h]\footnotesize
-\tbl{
-%\caption{
-  Dirichlet generating functions for ternary necklaces.
+  \caption{Dirichlet generating functions for ternary necklaces.}
+\begin{center}
+\begin{tabularx}{\textwidth}{
+  >{\hsize=0.6\hsize\raggedleft\arraybackslash}X
+  >{\hsize=1.4\hsize\centering\arraybackslash}X
+  >{\hsize=0.6\hsize\raggedleft\arraybackslash}X
+  >{\hsize=1.4\hsize\centering\arraybackslash}X
 }
-%\begin{center}
-{
-\begin{tabular}{cccc}
-%\begin{tabularx}{\textwidth}{
-%  >{\hsize=0.6\hsize\raggedleft\arraybackslash}X
-%  >{\hsize=1.4\hsize\centering\arraybackslash}X
-%  >{\hsize=0.6\hsize\raggedleft\arraybackslash}X
-%  >{\hsize=1.4\hsize\centering\arraybackslash}X
-%}
 \hline
@@
 $^\dagger$
+$\zeta(s) = \sum_n n^{-s}$ is the zeta function.
 See ref. \cite{hardy} for proofs.
-$\zeta(s) = \sum_n n^{-s}$ is the zeta function.
 }\\
@@
 \hline
-\end{tabular}
-%\end{tabularx}
-%\end{center}
+\end{tabularx}
+\end{center}
 \label{tab:genfunc}
-}
 \end{table}
@@
 \]
-which is \refeq{cublyndon}, note that $\delta_{n,1} = \sum_{c|n}\mu(c)$.
-%
-\end{proof}
-
-%
-$L_e(n)$ = 2, 2, 4, 10, 24, 60, 156, 410, \ldots, starting from $n = 1$.
-%
-This is also the number of the $n$-cycles \cite{hao, hao2}.
-Note that, for $n>1$, half of the cycles have negative $r$,
-and the $x_k$ are imaginary.
-However, in a transformed map,
-\[
-z_{k+1} = r \, z_k \, (1 - {z_k}^2),
-\]
-which differs from \refeq{cubic} by $x_k = \sqrt{r} z_k$,
-$z_k$ in the negative-$r$ cycles are real.
-
-Following a similar proof to \refthm{degR},
-we find the corresponding degrees in $r$
-of the characteristic polynomial $A_n(r, \lambda)$
-  and minimal polynomial $P_n(r, \lambda)$ of the $n$-cycles
-are $n N_e(n)$ and $n L_e(n)$, respectively.
-
-\subsection{\label{sec:oddcycle}Odd-cycles}
-
-Because of the symmetry $f(-x) = -f(x)$,
-the minimal polynomial $P_n(r, \lambda)$
-is subject to factorization for an even $n$.
-%
-If $x_{(n/2)+1} = -x_1$,
-  then $x_1, \ldots, x_{n/2}, -x_1, \ldots, -x_{n/2}$
-  is an $n$-cycle,
-  for $x_{n+1} = - x_{(n/2)+1} = x_1$.
-We call such a cycle an odd-cycle,
-see \reffig{oddcycle} for examples.
-%
-Odd-cycles satisfy a polynomial
-  of lower degrees in $\lambda$,
-  which causes the factorization.
-%
-Suppose $\Lambda^\odd(\vx) \equiv \prod_{k = 1}^{n/2} f'(x_k)$ in the odd-cycle
- satisfies $P_{n/2}^\odd(r, \lambda^\odd) = 0$
-\big[where $\lambda^\odd$ is the value of $\Lambda^\odd(\vx)$,
-and $\lambda^\odd = \pm\sqrt \lambda$\,\big],
-then $P^\odd_{n/2}(r, \sqrt \lambda) P^\odd_{n/2}(r, -\sqrt \lambda)$
-is a factor of $P_{n}(r, \lambda)$.
-%
-For example, by solving the $n = 2$ odd-cycle,
-  we have $- x_1 = r x_1 - {x_1}^3$, or ${x_1}^2 = r + 1$.
-Since $\lambda^\odd = r - 3 {x_1}^2$,
-$P^\odd_1(r, \lambda^\odd) = \lambda^\odd + 2 r + 3$.
-%
-Now the factor for 2-cycles (see \reftab{cubpolygen})
-  is
-  $P_2(r,\lambda) = -\big[(2r+3)^2 - \lambda\big]\,(\lambda + 2r^2-9)$,
-  whose first factor is indeed
-  $P^\odd_1(r, \sqrt \lambda) \, P^\odd_1(r, -\sqrt \lambda)
-   = (\sqrt \lambda + 2 r + 3)(-\sqrt \lambda + 2 r + 3)$.
-%
-The example for $n=4$ is shown in \reftab{cubpolygen}.
-
-\section{\label{sec:end}Summary and discussions}
-
-We now summarize the algorithm for a one-dimensional polynomial map.
-%
-First, we list \refeqs{xcp}  with $\Lambda(\vx) = \prod_{k=1}^n f'(x_k)$.
-This step populates elements of the matrix $\vct T(r)$,
-where $r$ is the parameter of the map.
-%
-The determinant $A_n(r, \lambda) = \big|\lambda \, \vct I - \vct T(r)\big|$,
-with $\lambda$ being $+1$ and $-1$, then gives the characteristic
-polynomial at onset and bifurcation points, respectively.
-%
-To filter out factors for the shorter $d$-cycles with $d|n$,
-  we repeat the process for other divisors $d$ of $n$
-  and then apply \req{primfac}.
-%
-
-When implemented on a computer,
-it is often helpful to evaluate $A_n(r,\lambda)$ by Lagrange interpolation,
-that is, we evaluate $A_n(r, \lambda)$ at a few different $r$,
-e.g., $r = 0, \pm1, \pm2,\ldots$, then piece them together
-to a polynomial.
-The strategy also allows a trivial parallelization.
-
-The algorithm (implemented as a Mathematica program)
-was quite efficient.
-%
-For the logistic map, the bifurcation point for $n = 8$
-took three seconds to compute on a desktop computer
-(single core, Intel\textsuperscript{\textregistered} Dual-Core CPU 2.50GHz).
-%
-In comparison,
-  the same problem took roughly 5.5 hours \cite{kk1}
-  using Gr\"obner basis
-  and 44 minutes in a later study \cite{lewis}.
-To be fair, using the latest Magma, computing the Gr\"obner basis
-  took 81 and 14 minutes, on the same machine
-  for \refeq{logmap} and \refeq{logmaps}, respectively;
-even so, our approach still had a 200-fold speed-up.
-
-%
-The exact polynomials of these maps are generally too large to print on paper,
-  e.g., the polynomial for the logistic map with $n = 13$
-    takes roughly seven megabytes to write down.
-%
-We therefore save the polynomials and programs of the three maps on the web site
-http://logperiod.appspot.com.
-
-%Compared with other approaches \cite{hitzl, gordon, bailey1, kk1, hao, hao2}
-%it appeared to be simpler and more transparent,
-%as it only requires the computation of a determinant.
-
-%\section*{Acknowledgements}
-\nonumsection{Acknowledgments} \noindent
-I thank Drs. T. Gilbert and Y. Mei for helpful communications.
-Computing time on the Shared University Grid at Rice,
-funded by NSF under Grant EIA-0216467, is gratefully acknowledged.
-
-%\appendix{}
-
-% ws-ijbc dislike the following
-%\appendix
-
-%\appendixpage
-
-\appendix{\label{apd:per4}Simple derivation of 4-cycles}
-
-The polynomials for the 4-cycles permits a short derivation.
-We first list the explicit equations:
-%
-%
-%
-\begin{subequations}
-\label{eq:x4}
-\begin{align}
-  x_2 &= R - x_1^2, \\
-  x_3 &= R - x_2^2, \\
-  x_4 &= R - x_3^2, \\
-  x_1 &= R - x_4^2,
-\end{align}
-\end{subequations}
-%
-$\big[\mathrm{\refeqsub{x4}{a}} - \mathrm{\refeqsub{x4}{c}}\big]
-\times
-\big[\mathrm{\refeqsub{x4}{b}} - \mathrm{\refeqsub{x4}{d}}\big]$
-yields $1 + (x_1 + x_3) (x_2 + x_4) = 0$,
-since $x_1 \ne x_3, x_2 \ne x_4$.
-%
-Hence, with
-$y_1 \equiv x_1 + x_3$, $y_2 \equiv x_2 + x_4$,
-$z \equiv y_1 + y_2$,
-we have
-%
-%
-%
-\begin{subequations}
-\begin{align}
-y_1 y_2       &= -1 \\
-y_1^2 + y_2^2 & = (y_1 + y_2)^2 - 2 y_1 y_2 = z^2 + 2 \\
-y_1^3 + y_2^3 & = (y_1 + y_2)^3 - 3 y_1 y_2 (y_1 + y_2) = z^3 + 3 z.
-\end{align}
-\label{eq:ypow4}
-\end{subequations}
-%
-%
-Multiplying \refeqsub{x4}{a} by $x_1$ or $x_3$,
-then summing over cyclic versions yields
-\begin{subequations}
-\begin{align}
-y_1 y_2 &= R z - \big[(x_1^3 + x_3^3) + (x_2^3 + x_4^3)\big],\\
-y_1 y_2 &= R z - \big[x_1 x_3 (x_1 + x_3) + x_2 x_4 (x_2 + x_4)\big].
-\end{align}
-\label{eq:p4q}
-\end{subequations}
-%
-From
-$\mathrm{\refeqsub{p4q}{a}} + 3 \times \mathrm{\refeqsub{p4q}{b}}$,
-we have
-$4 \, y_1 y_2 = 4 R z - (y_1^3 + y_2^3)$,
-%
-and by \refeqs{ypow4},
-\begin{equation}
-  z^3 - (4 R - 3) z - 4 = 0.
-  \label{eq:xr4s}
-\end{equation}
-%
-%
-Since $2 x_1 x_3 = y_1^2 - (x_1^2 + x_3^2) = y_1^2 - 2 R + y_2$,
-and $2 x_2 x_4 = y_2^2 - 2 R + y_1$,
-%
-%Using \refeqs{ypow4} to simplify the right hand side, we find
-\begin{equation}
-  X \equiv x_1 x_2 x_3 x_4 = \frac{1}{2} R z(1 - z) + (R^2 - R + 1),
-\label{eq:der4}
-\end{equation}
-where we have used \refeqs{ypow4} and \req{xr4s} to simplify the result.
-%$X=1/16$ and $-1/16$ at the onset and bifurcation points, respectively.
-%
-Dividing the polynomial in \refeq{xr4s} by that in \refeq{der4}
-yields $z = (R^2-3R-X+1)/(R^2-R+X-1)$,
-and plugging it back to \refeq{der4} gives
-   $R^6 -3 R^5
-  + (3 + X) (R^4 - R^3)
-  + (1 - X) (2 + X) R^2
-  + (1 - X)^3 = 0$,
-which is the same as the first factor of \refeq{xr4}
-  with $X = \lambda/16$.
-
-%\section{\label{apd:cublyndon}Proof of \refthm{cublyndon}}
+which is \refeq{cublyndon}
+\big[also note $\delta_{n,1} = \sum_{c|n}\mu(c)$\big].
 
@@
 
-\bibitem[May(1976)]{may}
-  May, R. H. [1976]
-  ``Simple mathematical models with very complicated dynamics,''
-  {\it Nature}
+\bibitem{strogatz} S. H. Strogatz,
+  \textit{Nonlinear Dynamics and Chaos}
+  (Addison-Wesley. Reading, MA, 1994).
+
+\bibitem{may} R. M. May,
+  Simple mathematical models with very complicated dynamics,
+  \textit{Nature}
   \textbf{261},
-  459--467.
-
-\bibitem[Strogatz(1994)]{strogatz}
-  Strogatz, S. H. [1994]
-  {\it Nonlinear Dynamics and Chaos}
-  (Addison-Wesley. Reading, MA).
-
-\bibitem[Saha \& Strogatz(1995)]{saha}
-  Saha, P. \& Strogatz, S. H. [1995]
-  ``The birth of period three,''
-  {\it Mathematics Magazine}
+  459-467
+  (1976).
+
+\bibitem{saha} P. Saha and S. H. Strogatz,
+  The birth of period three,
+  \textit{Mathematics Magazine}
   \textbf{68},
-  42--47.
-
-\bibitem[Kotsireas \& Karamanos(2004)]{kk1}
-  Kotsireas, I. S. \& Karamanos, K. [2004]
-  ``Exact computation of the bifurcation point $B_4$ of the logistic map
-  and  the Bailey-Broadhurst conjectures,''
-  {\it International Journal of Bifurcation and Chaos}
+  42-47
+  (1995).
+
+\bibitem{kk1} I. S. Kotsireas and K. Karamanos,
+  Exact computation of the bifurcation point $B_4$ of the logistic map and
+    the Bailey-Broadhurst conjectures,
+  \textit{International Journal of Bifurcation and Chaos}
   \textbf{14},
-  2417--2423.
-
-\bibitem[Stephenson(1992)]{stephenson}
-  Stephenson, J. [1992]
-  ``Formulae for cycles in the Mandelbrot set III,''
-  {\it Physica A}
+  2417-2423
+  (2004).
+
+\bibitem{stephenson} J. Stephenson,
+  Formulae for cycles in the Mandelbrot set III,
+  \textit{Physica A}
   \textbf{190},
-  117--129.
-
-\bibitem[Bechhoefer(1996)]{bechhoefer}
-  Bechhoefer, J. [1996]
-  ``The birth of period 3, revisited,''
-  {\it Mathematics Magazine}
+  117-129
+  (1992).
+
+\bibitem{bechhoefer} J. Bechhoefer,
+  The birth of period 3, revisited,
+  \textit{Mathematics Magazine}
   \textbf{69},
-  115--118.
-
-\bibitem[Gordon(1996)]{gordon}
-  Gordon, W. B. [1996]
-  ``Period three trajectories of the logistic map,''
-  {\it Mathematics Magazine}
+  115-118
+  (1996).
+
+\bibitem{gordon} W. B. Gordon,
+  Period three trajectories of the logistic map,
+  \textit{Mathematics Magazine}
   \textbf{69},
-  118--120.
-
-\bibitem[Burm \& Fishback(2001)]{burm}
-  Burm, J. \& Fishback, P. [2001]
-  ``Period-3 Orbits via Sylvester's Theorem and Resultants,''
-  {\it Mathematics Magazine}
+  118-120
+  (1996).
+
+\bibitem{burm} J. Burm, P. Fishback,
+  Period-3 Orbits via Sylvester's Theorem and Resultants,
+  \textit{Mathematics Magazine}
   \textbf{74},
-  47--51.
-
-\bibitem[Zhang(2010)]{zhang}
-  Zhang, C. [2010]
-  ``Period three begins,''
-  {\it Mathematics Magazine}
+  47-51
+  (2001).
+
+\bibitem{zhang} C. Zhang,
+  Period three begins,
+  \textit{Mathematics Magazine}
   \textbf{83},
-  295--297.
-
-\bibitem[Bailey \& Broadhurst(2000)]{bailey1}
-  Bailey, D. H. \& Broadhurst, D. J. [2000]
-  ``Parallel integer relation detection: techniques and applications,''
-  {\it Mathematics of Computation}
+  295-297
+  (2010).
+
+\bibitem{bailey1} D. H. Bailey and D. J. Broadhurst,
+  Parallel integer relation detection: techniques and applications,
+  \textit{Mathematics of Computation}
   \textbf{70},
-  1719--1736.
-
-\bibitem[Bailey {\it et al.}(2006)]{bailey2}
-  Bailey, D. H., Borwein, J. M., Kapour, V. \& Weisstein, E. W. [2006]
-  ``Ten problems in experimental mathematics,''
-  {\it The American Mathematical Monthly}
+  1719-1736
+  (2000).
+
+\bibitem{bailey2} D. H. Bailey, J. M. Borwein, V. Kapour and E. W. Weisstein,
+  Ten problems in experimental mathematics,
+  \textit{The American Mathematical Monthly}
   \textbf{113},
-  481--509.
-
-\bibitem[Lewis(2008)]{lewis}
-  Lewis, R. H. [2008]
-  ``Heuristics to accelerate the Dixon resultant,''
-  {\it Mathematics and Computers in Simulation}
+  481-509
+  (2006).
+
+\bibitem{lewis} R. H. Lewis,
+  Heuristics to accelerate the Dixon resultant,
+  \textit{Mathematics and Computers in Simulation}
   \textbf{77},
-  400--407.
-
-\bibitem[Hardy \& Wright(2008)]{hardy}
-  Hardy, G. H. \& Wright, E. M. [2008]
-  {\it An Introduction to the Theory of Numbers}
-  (Oxford University Press, USA).
-
-\bibitem[Hao(1989)]{hao}
-  Hao, B.-L. [1989]
-  {\it Elementary Symbolic Dynamics and Chaos in  Dissipative Systems}
-  (World Scientific, Singapore).
-
-\bibitem[Hao(2000)]{hao2}
-  Hao, B.-L. [2000]
-  ``Number of periodic orbits in continuous maps of
-  the interval complete solution of the counting problem,''
-  {\it Annals of Combinatorics}
+  400-407
+  (2008).
+
+\bibitem{hardy} G. H. Hardy,
+  \textit{An Introduction to the Theory of Numbers}
+  (Oxford University Press, USA, 2008).
+
+\bibitem{hao} B.-L. Hao,
+  \textit{Elementary Symbolic Dynamics and Chaos in  Dissipative Systems}
+  (World Scientific, Singapore, 1989);
+  Number of periodic orbits in continuous maps of
+    the interval complete solution of the counting problem,
+  \textit{Annals of Combinatorics}
   \textbf{4},
-  339--346.
-
-\bibitem[Lutzky(1988)]{lutzky}
-  Lutzky, M. [1988]
-  ``Counting stable cycles in unimodal iterations,''
-  {\it Physics Letters A}
+  339-346
+  (2000).
+
+\bibitem{lutzky} M. Lutzky,
+  Counting stable cycles in unimodal iterations,
+  \textit{Physics Letters A}
   \textbf{131},
-  248--250.
-
-\bibitem[Mira(1987)]{mira}
-  Mira, C. [1987]
-  {\it Chaotic Dynamics}
-  (World Scientific, Singapore).
-
-\bibitem[Stephenson(1991)]{stephenson2}
-  Stephenson, J. [1991]
-  ``Formulae for cycles in the Mandelbrot set,''
-  {\it Physica A}
+  248-250
+  (1988).
+
+\bibitem{mira}
+  C. Mira,
+  \textit{Chaotic Dynamics}
+  (World Scientific, Singapore, 1987);
+  J. Stephenson,
+  Formulae for cycles in the Mandelbrot set,
+  \textit{Physica A}
   \textbf{177},
-  416--420.
-
-\bibitem[Blackhurst(2011)]{blackhurst}
-  Blackhurst, J. [2011]
-  ``Polynomials of the bifurcation points of the logistic map,''
-  {\it International Journal of Bifurcation and Chaos}
+  416-420
+  (1991).
+
+\bibitem{blackhurst} J. Blackhurst,
+  Polynomials of the bifurcation points of the logistic map,
+  \textit{International Journal of Bifurcation and Chaos}
   \textbf{21},
-  1869--1877.
-
-\bibitem[H\'enon(1976)]{henon}
-  H\'enon, M. [1976]
-  ``A two-dimensional mapping with a strange attractor,''
-  {\it Communications in Mathematical Physics}
+  1869-1877
+  (2011).
+
+\bibitem{henon} M. H\'enon,
+  A two-dimensional mapping with a strange attractor,
+  \textit{Communications in Mathematical Physics}
   \textbf{50},
-  69--77.
-
-\bibitem[Hitzl(1985)]{hitzl}
-  Hitzl, D. L. \& Zele, F. [1985]
-  ``An exploration of the H\'enon quadratic map,''
-  {\it Physica D}
+  69-77
+  (1976).
+
+\bibitem{hitzl} D. L. Hitzl and F. Zele,
+  An exploration of the H\'enon quadratic map,
+  \textit{Physica D}
   \textbf{14},
-  305--326.
+  305-326
+  (1985).
 

### 2013-04-14 logperiod/js/main.js

@@ -1,0 +1,89 @@
+/* Copyright (c) Cheng Zhang 2010-2012 */
+window.onload = init;
+
+
+function init()
+{
+  appendspaces(); // at spaces at the bottom of the page
+  toc_init(); // initialize a toc
+  dtbox_init(); // bar for data and time
+  makeimgslinks(); // add links to the page
+}
+
+function toc_init() // create a table of content
+{
+  var nodes = document.getElementsByTagName("h2");
+  for (s = "", i = 0; i < nodes.length; i++) {
+    cap = nodes[i].innerHTML;
+    nodes[i].innerHTML = '<a name="h2_' + i + '"></a>' + cap; // add a marker
+    s += '<li><a href="#h2_' + i + '">' + cap + '</a></li>'; // add to TOC
+  }
+  if (s == "") return; else s = "<ul>" + s + "</ul>";
+
+  var env = document.createElement("div"); // envelope
+  env.setAttribute("id", "tocbox");
+
+  var title = document.createElement("div");
+  title.setAttribute("id", "toctitle");
+  title.innerHTML = document.getElementsByTagName('title')[0].innerHTML;
+  env.appendChild(title);
+
+  var list = document.createElement("div");
+  list.setAttribute("id", "toclist");
+  list.innerHTML = s;
+  env.appendChild(list);
+
+  var links = document.createElement("div");
+  links.innerHTML = '<hr>'
+    + '<div class="toclinkhead">Links:</div>'
+    + '<ul class="toclinks">'
+    + '<li><a href="/">Home</a>'
+    + '<li><a href="/log">Logistic</a>'
+    + '<li><a href="/cubic">Cubic</a>'
+    + '<li><a href="/henon">H&eacute;non</a>';
+    '</ul>';
+  env.appendChild(links);
+
+  env.onmouseover = function () { tocshow(1); };
+  env.onmouseout = function () { tocshow(0); };
+
+  nodes[0].parentNode.insertBefore(env, nodes[0]);
+  tocshow(0);
+}
+
+function tocshow(open)
+  { document.getElementById("tocbox").style.left = (open ? "0px" : "-200px"); }
+
+
+var dtbox;
+function dtbox_init() // create a date/time box
+{
+  dtbox = document.createElement("div");
+  dtbox.id = "dtbox";
+  dtbox.setAttribute("style", "font: small-caps 100% sans-serif; position: fixed;"
[…]

### 2013-04-14 logperiod/logperiod.py

@@ -1,0 +1,64 @@
+import os, sys
+from google.appengine.ext import webapp
+from google.appengine.ext.webapp import template
+from google.appengine.ext.webapp.util import run_wsgi_app
+
+class MainPage(webapp.RequestHandler):
+  def get(self, html="index.html"):
+    self.response.headers['Content-Type'] = 'text/html'
+    path = os.path.join(os.path.dirname(__file__), html)
+    template_values = {
+        'prim_ref': '''<h3>Primary reference</h3>
+<ul>
+<li>Cheng Zhang,
+<i>Period cycles of the logistic map</i>,
+<a href="http://arxiv.org/abs/1204.0546">arXiv:1204.0546</a>, 2012.
+</li>
+</ul>''',
+
+        'go_home':
+        '''<div class="linkenv">
+        <ul class="links">
+        <li class="linkhead">Links:
+        <li><a href="/">Home</a>,
+        <li><a href="/log">Logistic</a>,
+        <li><a href="/cubic">Cubic</a>,
+        <li><a href="/henon">H&eacute;non</a>
+        </ul></div>''',
+
+        'last_update':
+        '<p>Last update: May. 7th, 2012.',
+    }
+    self.response.out.write(template.render(path, template_values))
+
+class LogPage(MainPage):
+  def get(self):
+    MainPage.get(self, "log.html")
+
+class CubicPage(MainPage):
+  def get(self):
+    MainPage.get(self, "cubic.html")
+
+class HenonPage(MainPage):
+  def get(self):
+    MainPage.get(self, "henon.html")
+
+class AboutPage(webapp.RequestHandler):
+  def get(self):
+    self.response.headers['Content-Type'] = 'text/plain'
+    self.response.out.write('test page')
+
+application = webapp.WSGIApplication(
+  [('/', MainPage),
+   ('/log', LogPage),
+   ('/cubic', CubicPage),
+   ('/henon', HenonPage),
+   ('/about', AboutPage)],
+  debug=True)
+
+def main():
+  run_wsgi_app(application)
+
+if __name__ == "__main__":
+  main()
+

### 2013-04-14 logperiod/prog/figtree/fig.c

@@ -1,0 +1,91 @@
+/* draw fig tree */
+#include <stdio.h>
+#include <math.h>
+
+double rmin = 2.0;
+double rmax = 3.0;
+double delr = 0.002;
+int itermax = 100000000;
+int trajmax = 100;
+double dxtol = 1e-6;
+const char *fnout = "cub.fig";
+
+#ifndef xnew
+#define xnew(x, n) if ((x = calloc(n, sizeof(*(x)))) == NULL) { \
+    fprintf(stderr, "no memory for %s x %u\n", #x, (unsigned) (n)); exit(1); }
+#endif
+
+/* logistic map */
+double logistic(double r, double x) { return r*x*(1 - x); }
+
+/* cubic map */
+double cubic(double r, double x) { 
+  // return x*r*(1 - x*x);  // allows the negative part
+  return x*(r - x*x); 
+}
+
+/* get period trajectories
+ * trj[]: trajectories, trjmax is its size
+ * itmax: maximal number of iterations  */
+int gettrj(double trj[], int trjmax, 
+    double r, double (*f)(double, double), int itmax, 
+    double x0, double tol)
+{
+  int i, j;
+  double x = x0;
+
+  if (itmax < trjmax) itmax = trjmax;
+  for (i = 0; i < itmax; ) {
+    /* a set of trjmax iterations */
+    for (j = 0; j < trjmax && i < itmax; j++, i++) {
+      x = (*f)(r, x);
+      if (j > 0 && fabs(trj[0] - x) < tol) {
+        //fprintf(stderr, "detected period-%d, r %g, x %g vs %g, i %d\n", j, r, x, trj[0], i);
+        break;
+      }
+      trj[j] = x;
+    }
+    if (j < trjmax) return j;
+  }
+  fprintf(stderr, "failed to converge for r = %.8f\n", r);
+  return trjmax;
+}
+
+/* save the figure tree */
+int mkfigtree(double r0, double r1, double dr, 
+    int trjmax, int itmax, double tol,
+    const char *fn)
+{
+  int i, j, k, cnt, rcnt;
+  double r, *trj, x0;
+  FILE *fp;
+
+  xnew(trj, trjmax + 1);
+  rcnt = (int)((r1 - r0)/dr + .5);
+  dr = (r1 - r0)/rcnt;
+  if ((fp = fopen(fn, "w")) == NULL) {
[…]

### 2013-04-14 logperiod/prog/mkinterp.py

@@ -1,0 +1,1 @@
+../../prog/mkinterp.py

### 2013-04-14 logperiod/prog/mknsolv.py

@@ -1,0 +1,1 @@
+../../prog/mknsolv.py

### 2013-04-14 prog/magma/mat2magma.py

@@ -1,0 +1,159 @@
+#!/usr/bin/env python
+
+import os, sys, re
+from numbthy import *
+
+if len(sys.argv) <= 1:
+  print "need an input file"
+  exit(1)
+
+matpfx = "mats"
+fn = sys.argv[1];
+fn0 = os.path.splitext(fn)[0]
+i =  fn0.rfind(matpfx)
+if i < 0:
+  print "unknown file name", fn
+n = int(fn0[len(matpfx):])
+
+
+def skipsp(buf, i):
+  ''' skip spaces '''
+  n = len(buf)
+  while i < n and buf[i].isspace(): i += 1
+  return i
+
+
+def readch(buf, i, ch):
+  ''' skip space until an excepted character is read '''
+  i = skipsp(buf, i)
+  if i >= len(buf):
+    print "EOF met, cannot read", ch
+    raise Exception
+  if buf[i] != ch:
+    print "expected %s got '%s' at %d" % (ch, buf[i:i+15], i)
+    raise Exception
+  return i+1
+
+
+def readchopt(buf, i, ch):
+  ''' skip optional character '''
+  i = skipsp(buf, i)
+  if i < len(buf) and buf[i] == ch: i += 1
+  return i
+
+
+def readmats(fn, n):
+  ''' read the matrix from mathematica '''
+  buf = open(fn).read().strip()[1:-1]
+  buf = re.sub(r'\s', '', buf)
+  divs = divisors(n)
+  fid = 0
+  mats = [0]*len(divs)
+  for k in range(len(divs)):
+    d = divs[k]
+    fid = readch(buf, fid, "{")
+    Nd = necklace(d)
+    #print d, Nd
+    # read the matrix for d
+    mat = [0]*Nd
+    for i in range(Nd): # reading ith row
+      fid = readch(buf, fid, "{")
+      fjd = buf.find("}", fid)
+      if fjd < 0: raise Exception
+      mat[i] = [c.strip() for c in buf[fid:fjd].split(",")]
+      fid = readchopt(buf, fjd+1, ",")
+    mats[k] = mat
+    fid = readch(buf, fid, "}")
+    fid = readchopt(buf, fid, ",")
+  return mats
+
+
+def mkintmat(mat, n):
+  ''' transform the matrix so its on integer domain '''
+  dm = len(mat)
+  num = "2^%s" % n
+  nnum = "-2^%s" % n
+  if n%2 == 0: num, nnum = nnum, num;
[…]

### 2013-04-14 prog/magma/numbthy.py

@@ -1,0 +1,252 @@
+'''
+NUMBTHY.PY
+Basic Number Theory functions implemented in Python
+Note: Currently requires Python 2.x (uses +=, %= and other 2.x-isms)
+Note: Currently requires Python 2.3 (uses implicit long integers - could be back-ported though)
+Author: Robert Campbell, <campbell@math.umbc.edu>
+        modified by Cheng Zhang (functions with *)
+Date: 27 April, 2007
+Version 0.41
+License: Simplified BSD (see details at bottom)
+'''
+"""Basic number theory functions.
+   Functions implemented are:
+       gcd(a,b) - Compute the greatest common divisor of a and b.
+       xgcd(a,b) - Find [g,x,y] such that g=gcd(a,b) and g = ax + by.
+       powmod(b,e,n) - Compute b^e mod n efficiently.
+       isprime(n) - Test whether n is prime using a variety of pseudoprime tests.
+       isprimeF(n,b) - Test whether n is prime or a Fermat pseudoprime to base b.
+       isprimeE(n,b) - Test whether n is prime or an Euler pseudoprime to base b.
+       eulerphi(n) - Computer Euler's Phi function of n - the number of integers strictly less than n which are coprime to n.
+     * moebiusmu(n) - Compute Moebius Mu function of n
+       carmichaellambda(n) - Computer Carmichael's Lambda function of n - the smallest exponent e such that b**e = 1 for all b coprime to n.
+       factor(n) - Find a factor of n using a variety of methods.
+       factors(n) - Return a sorted list of the prime factors of n.
+       factorPR(n) - Find a factor of n using the Pollard Rho method
+     * divisors(n) - return a list of divisors of n
+     * necklace(n, k) - number of k-ary necklaces
+     * lyndon(n, k) - number of k-ary Lyndon words
+
+    isprimitive(g,n) - Test whether g is primitive - generates the group of units mod n.
+   A list of the functions implemented in numbthy is printed by the command info()."""
+
+
+Version = 'NUMBTHY.PY, version 0.41, 27 Apr, 2007, by Robert Campbell, <campbell@math.umbc.edu>'
+
+import math  # Use sqrt, floor
+
+def gcd(a,b):
+  """gcd(a,b) returns the greatest common divisor of the integers a and b."""
+  if a == 0:
+    return b
[…]

### 2013-04-14 prog/mkinterp.py

@@ -1,0 +1,150 @@
+#!/usr/bin/env python
+
+''' make a mathematica script for interpolation from a list file
+    the output is fit.ma, to run it type
+      math < fit.ma >/dev/null
+    which writes fit.txt
+'''
+import os, sys, re
+
+if len(sys.argv) <= 1:
+  print "require an argument"
+  exit(1)
+
+input = sys.argv[1]
+
+kmin = kmax = None
+argid = 2
+if len(sys.argv) > argid:
+  kmin = int(sys.argv[argid])
+  if kmin <= 1: kmin = 1
+argid += 1
+if len(sys.argv) > argid:
+  kmax = int(sys.argv[argid])
+  if kmax < kmin:
+    print "kmax %s must be >= kmin %s" % (kmin, kmax)
+    raise Exception
+argid += 1
+print kmin, kmax
+
+
+s = open(input).read().strip("{} \n\r")
+s = [a.strip(" \n{").split(", ") for a in s.split("}")]
+n = len(s)
+print "list contains", n, "items"
+
+for i in range(n):
+  #s[i][0] = int(s[i][0])  # note, s[i][0] might be expression like -101/4, so not int
+  # only for checking parity
+  #s[i][1] = re.sub(r"[\\\n]", "", s[i][1])
+  s[i][1] = re.sub(r"\\\n", "", s[i][1])
+
+'''
+# add mirrors
+t = []
+for i in range(n):
+  id = s[i][0]
+  if id <= 0: continue
+  for j in range(i):
+    if s[j][0] == -id:
+      break
+  else:
+    print "adding ", -s[i][0]
+    t = [[-s[i][0], s[i][1]]] + t
+s = t + s
+str = ''.join(  [("{%s, %s}\n" % (l[0], l[1])) for l in s]  )
+open("xxx.txt", "w").write(str)
+'''
+
+
+'''
+# check parity
+for i in range(n):
+  id = s[i][0]
+  if id >= 0: break
+  for j in range(i+1, n):
+    if s[j][0] == -id:
+      break
+  else:
+    continue
+
+  if s[i][1] == s[j][1]:
+    pass #print "i %s, id %s checked" % (i, id)
+  else:
+    print "i %s, id %s bad" % (i, id)
+'''
+
+
+ls = "ls = {"
+for i in range(n):
+  ls += "{%s, %s},\n" % (s[i][0], s[i][1])
[…]

### 2013-04-14 prog/mknsolv.py

@@ -1,0 +1,269 @@
+#!/usr/bin/env python
+
+''' make a mathematica script for numeric solutions of the logistic and cubic maps
+
+      mknsolv.py file [prec] [wprec] [fnbra] [kmin] [kmax] [tmfindroot] [tmfactor]
+
+    where
+      prec is the target precision
+      wprec is the working precision
+      fnbra is a saved bracket file
+      kmin is the smallest root index
+      kmax is the largest root index (inclusive)
+      tmfindroot is the maximal time for time out
+      tmfactor is the maximal time to try to factor
+    the output is nsolv.ma, to run it type
+
+      math < nsolv.ma
+
+    which writes nsolv.txt and possibly solvT.txt
+    for harder problem the onset
+      mknsolv.py T11a.txt 20 1000 fnbra
+      math < nsolv.ma
+'''
+import os, sys, re
+
+if len(sys.argv) <= 1:
+  print "require an argument"
+  exit(1)
+
+input = sys.argv[1]
+
+prec = 11
+wprec = 100
+fnbra = None
+kmin = kmax = None
+tmfindroot = 1000
+tmfactor = 1
+
+argid = 2
+# precision
+if len(sys.argv) > argid:
+  prec = int(sys.argv[argid])
+argid += 1
+
+# working precision
+if len(sys.argv) > argid:
+  wprec = int(sys.argv[argid])
+argid += 1
+
+# brackets
+if len(sys.argv) > argid:
+  fnbra = sys.argv[argid]
+  if not fnbra.endswith(".txt"):
+    print "bracket file %s must end with .txt" % fnbra
+    raise Exception
+  fnbra = '"%s"' % fnbra # add quotes
+argid += 1
+
+if len(sys.argv) > argid:
+  kmin = int(sys.argv[argid])
+argid += 1
+if len(sys.argv) > argid:
+  kmax = int(sys.argv[argid])
+argid += 1
+
+if len(sys.argv) > argid:
+  tmfindroot = int(sys.argv[argid])
+argid += 1
+
+if len(sys.argv) > argid:
+  tmfactor = int(sys.argv[argid])
+argid += 1
+
+s = open(input).read().strip(" \n\r")
[…]

### 2013-04-14 prog/script/cubrep.py

@@ -1,0 +1,125 @@
+#!/usr/bin/env python
+
+import os, sys
+
+def mkpbs(id, kmin, kmax, ch="a", n=13):
+  return '''#!/bin/bash
+#PBS -N cub%s%s%s
+#PBS -l nodes=1:ppn=1,walltime=24:00:00
+#PBS -V
+
+#which math
+#echo "My job ran on: "
+#cat $PBS_NODEFILE
+cd $PBS_O_WORKDIR
+pwd
+math < cub0.ma %s %s %s %s > /dev/null
+''' % (n, ch, id, n, ch, kmin, kmax)
+
+def lsnm(n, ch):
+  return "cls%s%s0.txt" % (n ,ch)
+
+def getkminmax(ls, i):
+  ''' (kmin, kmax) '''
+  deg = 3392
+  base = -deg/2
+  step = 106
+  kmin = base + step*(i - 1)
+  kmax = base + step*i
+  try:
+    if ls != None:
+      s = open(ls, "r").read()
+      id = s.rfind("{") # search from the end
+      kmin = eval( "1*" + s[id+1:].split(", ")[0] ) + 1
+  except:
+    pass
+  if i == 32: kmax = deg + 2 + base + 5
+  return kmin, kmax
+
+def reprod(ch, n):
+  for i in range(1, 33):
+    dir = "%s%s%s" % (n, ch, i)
+    os.system("mkdir %s" % dir);
+    os.chdir(dir)
+    os.system("ln -sf ../test/cmats%s.txt ." % n)
+    os.system("ln -sf ../test/cub0.ma .")
+    kmin, kmax = getkminmax(None, i)
+    str = mkpbs(i, kmin, kmax, ch, n);
+    open("foo.pbs", "w").write(str)
+    os.system("chmod 755 foo.pbs")
+    os.chdir("..")
+
+def collect(ch, n):
+  ''' collect lists '''
+  str = ""
+  ls = lsnm(n, ch)
+  cnt = 0
+  for i in range(1, 33):
+    dir = "%s%s%s" % (n, ch, i)
+    os.chdir(dir)
+    try:
+      s = open(ls, "r").read()
+      cnt += s.count("{")
+      str += s
+    except:
+      print "cannot open %s" % (ls)
+    os.chdir("..")
+  open(ls, "w").write(str)
+  print "counted %d solutions" % cnt
+
+def modifypbs(ch, n):
+  print "trimming pbs"
+  tot = 0
[…]

### 2013-04-14 prog/script/henrep.py

@@ -1,0 +1,138 @@
+#!/usr/bin/env python
+
+import os, sys
+
+def mkpbs(id, kmin, kmax, ch="a", n=13):
+  return '''#!/bin/bash
+#PBS -N hen%s%s%s
+#PBS -l nodes=1:ppn=1,walltime=24:00:00
+#PBS -V
+
+#which math
+#echo "My job ran on: "
+#cat $PBS_NODEFILE
+cd $PBS_O_WORKDIR
+pwd
+math < hen.ma %s %s %s %s > /dev/null
+''' % (n, ch, id, n, ch, kmin, kmax)
+
+def lsnm(n, ch):
+  return "hls%s%s.txt" % (n ,ch)
+
+def getkminmax(ls, i):
+  ''' (kmin, kmax) '''
+  deg = 252
+  base = -deg/2
+  step = 8
+  kmin = base + step*(i - 1)
+  kmax = base + step*i
+  try:
+    if ls != None:
+      s = open(ls, "r").read()
+      id = s.rfind("{") # search from the end
+      kmin = eval( "1*" + s[id+1:].split(", ")[0] ) + 1
+  except:
+    pass
+  if i == 32: kmax = deg + 2 + base
+  return kmin, kmax
+
+def reprod(ch, n):
+  for i in range(1, 33):
+    dir = "%s%s%s" % (n, ch, i)
+    os.system("mkdir %s" % dir);
+    os.chdir(dir)
+    os.system("ln -sf ../test/hmats%s.txt ." % n)
+    os.system("ln -sf ../test/hen.ma .")
+    kmin, kmax = getkminmax(None, i)
+    str = mkpbs(i, kmin, kmax, ch, n);
+    open("foo.pbs", "w").write(str)
+    os.system("chmod 755 foo.pbs")
+    os.chdir("..")
+
+def collect(ch, n):
+  ''' collect lists '''
+  str = ""
+  ls = lsnm(n, ch)
+  cnt = 0
+  edict = {}
+  for i in range(1, 33):
+    dir = "%s%s%s" % (n, ch, i)
+    os.chdir(dir)
+    try:
+      s = open(ls, "r").read()
+    except:
+      print "cannot open %s" % (ls)
+      os.chdir("..")
+      continue
+    q = 0
+    while 1:
+      p = s.find("{", q)
+      if p < 0: break
+      q = s.find("}", p)
+      ent = s[p+1:q].split(",")[0].strip();
+      if ent in edict:
[…]

### 2013-04-14 prog/script/logrep.py

@@ -1,0 +1,122 @@
+#!/usr/bin/env python
+
+import os, sys
+
+def mkpbs(id, kmin, kmax, ch="a", n=13):
+  return '''#!/bin/bash
+#PBS -N prd%s%s%s
+#PBS -l nodes=1:ppn=1,walltime=24:00:00
+#PBS -V
+
+#which math
+#echo "My job ran on: "
+#cat $PBS_NODEFILE
+cd $PBS_O_WORKDIR
+pwd
+math < prd.ma %s %s %s %s > /dev/null
+''' % (n, ch, id, n, ch, kmin, kmax)
+
+def lsnm(n, ch):
+  return "ls%s%s.txt" % (n ,ch)
+
+def getkminmax(ls, i):
+  ''' (kmin, kmax) '''
+  kmin = -2048 + 128*(i - 1)
+  kmax = -2048 + 128*i
+  try:
+    if ls != None:
+      s = open(ls, "r").read()
+      id = s.rfind("{")
+      kmin = eval( "4*" + s[id+1:].split(", ")[0] ) + 1
+  except:
+    pass
+  if i == 32: kmax += 5
+  if kmax == 0: kmax -= 1
+  return kmin, kmax
+
+def reprod(ch, n):
+  for i in range(1, 33):
+    dir = "%s%s%s" % (n, ch, i)
+    os.system("mkdir %s" % dir);
+    os.chdir(dir)
+    os.system("ln -sf ../test/mats%s.txt ." % n)
+    os.system("ln -sf ../test/prd.ma .")
+    kmin, kmax = getkminmax(None, i)
+    str = mkpbs(i, kmin, kmax, ch, n);
+    open("foo.pbs", "w").write(str)
+    os.system("chmod 755 foo.pbs")
+    os.chdir("..")
+
+def collect(ch, n):
+  ''' collect lists '''
+  str = ""
+  ls = lsnm(n, ch)
+  cnt = 0
+  for i in range(1, 33):
+    dir = "%s%s%s" % (n, ch, i)
+    os.chdir(dir)
+    try:
+      s = open(ls, "r").read()
+      cnt += s.count("{")
+      str += s
+    except:
+      print "cannot open %s" % (ls)
+    os.chdir("..")
+  open(ls, "w").write(str)
+  print "counted %d solutions" % cnt
+
+def modifypbs(ch, n):
+  print "trim pbs"
+  tot = 0
+  for i in range(1, 33):
[…]

### 2013-04-15 doc/pc-ijbc.tex
doc: change \phi to \varphi

@@
   $\lambda$ should be generalized from $\pm1$
-  to any $\lambda = \exp(i\phi)$,
-  where $\phi \in [0, 2\pi]$,
+  to any $\lambda = \exp(i\theta)$,
+  where $\theta \in [0, 2\pi]$,
   the algorithm still applies.
-  By increasing $\phi$ from 0 to $2\pi$,
+  By increasing $\theta$ from 0 to $2\pi$,
   we can trace a two-dimensional region of a complex $R$
@@
 $^\dagger$
-$\NB(n) = (1/n) \sum_{d|n} \phi(n/d) 2^d$ [\refeq{necklace}]
+$\NB(n) = (1/n) \sum_{d|n} \varphi(n/d) 2^d$ [\refeq{necklace}]
 is the number of the square-free cyclic polynomials.
@@
 the method can also compute the region of stability for $R$,
-with $\lambda$ being $\exp(i\phi)$ \big[$\phi \in (0, 2\pi)$\big]
+with $\lambda$ being $\exp(i\theta)$ \big[$\theta \in (0, 2\pi)$\big]
   instead of $\pm1$;
@@
   with a complex $R$;
-  obtained from $P_n(R, e^{i\phi}) = 0$ with $\phi \in [0, 2\pi]$,
+  obtained from $P_n(R, e^{i\theta}) = 0$ with $\theta \in [0, 2\pi]$,
   cf. Fig. 3 in \cite{stephenson}.
@@
         & $m = 2$
-        & $m = 4$   & $2^d$ & $\phi(n/d)$ & $\phi(n/d) 2^d$\\
+        & $m = 4$   & $2^d$ & $\varphi(n/d)$ & $\varphi(n/d) 2^d$\\
 \hline
@@
 \hline
-$m \sum_{m|d, d|n} \phi(\frac{n}{d})$
+$m \sum_{m|d, d|n} \varphi(\frac{n}{d})$
       & \multicolumn{2}{c|}{$1\cdot(2+1+1) = 4$}
@@
 %
-We then weight them by the Euler's totient function $\phi(n/d)$.
-%
-Here, $\phi(m)$ gives the number of integers from 1 to $m$
+We then weight them by the Euler's totient function $\varphi(n/d)$.
+%
+Here, $\varphi(m)$ gives the number of integers from 1 to $m$
   that are coprime to $m$,
   e.g.,
-  $\phi(1) = 1$,
-  $\phi(3) = 2$ for 1 and 2,
-  $\phi(6) = 2$ for 1 and 5.
+  $\varphi(1) = 1$,
+  $\varphi(3) = 2$ for 1 and 2,
+  $\varphi(6) = 2$ for 1 and 5.
 We repeat the process over other divisors $d$ of $n$,
-  and the resulting sum is $\sum_{d|n} \phi(n/d) 2^d$.
+  and the resulting sum is $\sum_{d|n} \varphi(n/d) 2^d$.
 %
@@
 \begin{equation}
-m \sum_{m|d, d|n} \phi(n/d) =
- m \sum_{\frac{n}{d}|\frac{n}{m}} \phi(n/d) = m \,  \frac{n}{m}  = n,
+m \sum_{m|d, d|n} \varphi(n/d) =
+ m \sum_{\frac{n}{d}|\frac{n}{m}} \varphi(n/d) = m \,  \frac{n}{m}  = n,
 \label{eq:mphind}
 \end{equation}
-where we have used the identity $\sum_{d'|m'} \phi(d') = m'$,
+where we have used the identity $\sum_{d'|m'} \varphi(d') = m'$,
 with $d' = n/d$ and $m' = n/m$.
@@
 Summing over the necklaces yields $N(n) \, n$. Thus,
-$N(n) = (1/n) \sum_{d|n} \phi(n/d) 2^d$.
+$N(n) = (1/n) \sum_{d|n} \varphi(n/d) 2^d$.
 The process for a fixed necklace is exemplified
@@
 \begin{equation}
-  \NB(n) = N(n) = (1/n) \sum_{d|n} \phi(n/d) 2^{\,d},
+  \NB(n) = N(n) = (1/n) \sum_{d|n} \varphi(n/d) 2^{\,d},
 \label{eq:necklace}
@@
         \mu\left(\frac{n/c}{d'}\right) d' \\
-  &= (1/n) \sum_{c \, | \, n} 2^{\,c} \, \phi(n/c)
+  &= (1/n) \sum_{c \, | \, n} 2^{\,c} \, \varphi(n/c)
   = N(n),
 \end{align*}
-where we have used $\phi(m) = \sum_{d' | m} \mu(\frac{m}{d'}) \, d'$,
-which is the inversion of $m = \sum_{d' | m} \phi(d')$,
+where we have used $\varphi(m) = \sum_{d' | m} \mu(\frac{m}{d'}) \, d'$,
+which is the inversion of $m = \sum_{d' | m} \varphi(d')$,
 and \refeq{necklace}.
@@
 \begin{align}
-\deg_R A_n\RX &= \sum_{d|n} \phi(n/d) 2^{d-1}, \\
+\deg_R A_n\RX &= \sum_{d|n} \varphi(n/d) 2^{d-1}, \\
 \deg_R P_n\RX &= \sum_{d|n} \mu(n/d) 2^{d-1} \equiv \beta(n), \\
-\deg S_n(R) &= \beta(n) - \sum_{d | n, d < n} \beta(d) \, \phi(n/d).
+\deg S_n(R) &= \beta(n) - \sum_{d | n, d < n} \beta(d) \, \varphi(n/d).
 \end{align}
@@
   with a complex $R$;
-  obtained from $P_n(R, e^{i\phi}) = 0$ with $\phi \in [0, 2\pi]$
+  obtained from $P_n(R, e^{i\theta}) = 0$ with $\theta \in [0, 2\pi]$
   cf. \reffig{logbulb}.
@@
 %\[
-%  N_3(n) = (1/n) \sum_{d|n} \phi(n/d) 3^d.
+%  N_3(n) = (1/n) \sum_{d|n} \varphi(n/d) 3^d.
 %\]
@@
 \begin{equation}
-  N_e(n) = \frac{1}{n} \sum_{c d = n} \phi(c)
+  N_e(n) = \frac{1}{n} \sum_{c d = n} \varphi(c)
     \left[
@@
         & $T(d, c)$ $^\dagger$
-        & $\phi(c)$ & $\phi(n/d) T(d, c)$\\
+        & $\varphi(c)$ & $\varphi(n/d) T(d, c)$\\
 \hline
@@
 \hline
-$m \sum_{m|d, d|n} \phi(\frac{n}{d})$
+$m \sum_{m|d, d|n} \varphi(\frac{n}{d})$
       & \multicolumn{3}{c|}{$1\cdot(1+1) = 2$}
@@
     does not yield an even string);
-  in either case, we multiple the result by $\phi(c)$.
+  in either case, we multiple the result by $\varphi(c)$.
 %
@@
 Repeating the process for all $d$ gives
-  $\sum_{cd = n} T(d, c) \, \phi(c)$,
+  $\sum_{cd = n} T(d, c) \, \varphi(c)$,
   where $T(d, c)$ is the total number $3^d$ of period-$d$ ternary strings if $c$ is even,
@@
 An even period-$m$ necklace contributes a total of
-  $m \times \sum_{m|d, d|n} \phi(n/d) = n$
+  $m \times \sum_{m|d, d|n} \varphi(n/d) = n$
   \big[the multiplier $m$ is for the $m$ cyclic versions, cf. \refeq{mphind}\big],
@@
 \[
-  N_e(n) \cdot n = \sum_{cd = n} T(d, c) \, \phi(c),
+  N_e(n) \cdot n = \sum_{cd = n} T(d, c) \, \varphi(c),
 \]
@@
 \\
-$\phi(n)$   & $\zeta(s-1)/\zeta(s)$ $^\dagger$ &
+$\varphi(n)$   & $\zeta(s-1)/\zeta(s)$ $^\dagger$ &
 \multicolumn{1}{|r}
@@
   & $\Big[ \zeta(s) (1-2^{-s}) \Big]^{-1}$ &
-$\phi(n) \, \odd(n)$
+$\varphi(n) \, \odd(n)$
   & $\frac{\zeta(s-1)}{\zeta(s)} \frac{1-2^{-s+1}}{1-2^{-s}}$
@@
 
-The generating function $G_{\phi,\odd}(s)$
-of $\phi(n) \odd(n)$ can be computed by taking the generating function
+The generating function $G_{\varphi,\odd}(s)$
+of $\varphi(n) \odd(n)$ can be computed by taking the generating function
 of both sides of the identity
 \[
-  n \, \odd(n)  = \sum_{d|n} \phi(d) \, \odd(d) \; \odd(n/d),
+  n \, \odd(n)  = \sum_{d|n} \varphi(d) \, \odd(d) \; \odd(n/d),
 \]
 i.e., if $n$ is even, then both sides are 0;
-if odd, then $n = \sum_{d|n} \phi(d)$.
+if odd, then $n = \sum_{d|n} \varphi(d)$.
 So
 \[
-  G_{\phi,\odd}(s) = \frac{G_\odd(s-1)}{G_\odd(s)}
+  G_{\varphi,\odd}(s) = \frac{G_\odd(s-1)}{G_\odd(s)}
   = \frac{\zeta(s-1)}{\zeta(s)} \frac{1 - 2^{-s + 1}}{1 - 2^{-s}}.
@@
   G_N(s - 1)
-    = G_\phi(s) t(s)- G_{\phi, \odd}(s) \frac{t(s)-\zeta(s)}{2}
+    = G_\varphi(s) t(s)- G_{\varphi, \odd}(s) \frac{t(s)-\zeta(s)}{2}
     =

### 2013-04-15 doc/pc.tex
doc: change \phi to \varphi

@@
   with a complex $R$;
-  obtained from $P_n(R, e^{i\phi}) = 0$ with $\phi \in [0, 2\pi]$
+  obtained from $P_n(R, e^{i\theta}) = 0$ with $\theta \in [0, 2\pi]$
   cf. Fig. 3 in \cite{stephenson}.
@@
   with a complex $R$;
-  obtained from $P_n(R, e^{i\phi}) = 0$ with $\phi \in [0, 2\pi]$,
+  obtained from $P_n(R, e^{i\theta}) = 0$ with $\theta \in [0, 2\pi]$,
   cf. \reffig{logbulb}.

### 2013-04-15 doc/pc-ijbc.tex
doc: x^{new} remove () around the subscript
edit the intro of homogeneous linear eqs.

@@
 \[
-    x^{(\mathrm{new})} \leftarrow r(x^{(\mathrm{old})} - 1/2),
+    x^{\mathrm{new}} \leftarrow r(x^{\mathrm{old}} - 1/2),
     \quad R \leftarrow r(r-2)/4,
@@
 %
-and rewrite the map, in terms of $x^{(\mathrm{new})}$, as
+and rewrite the map, in terms of $x^{\mathrm{new}}$, as
 %
@@
   we will derive a set of \emph{homogeneous linear} equations
-  of cyclic polynomials of $x_k$
+  $\sum_j A_{ij} C_j = 0$
+  regarding cyclic polynomials $\{C_j\}$ of $x_k$
   (an example of a cyclic polynomial is $x_1 x_2 + x_2 x_3 + \dots + x_n x_1$).
 %
-%We know then that
-  Now the matrix formed by the coefficients of the homogeneous linear equations
+Now the matrix formed by the coefficients $A_{ij}$ of the equations
   must have a zero determinant,
-  for the cyclic polynomials are not zeros altogether.
+  for the cyclic polynomials $\{C_j\}$ are not zeros altogether.
 %
 %As the coefficients are polynomials of $R$ only,
-Thus, the zero-determinant condition gives
-  the needed polynomial equations of $R$,
+Thus, the zero-determinant condition $|\mathbf A| = 0$ gives
+  the needed polynomial equation of $R$,
 whose roots contain all fixed points of $f^n$.

### 2013-04-15 doc/p3p.tex
improve p3p.tex, add two Makefiles and links

@@
-\documentclass[12pt]{article}
+%\documentclass[12pt]{article}
+\documentclass[twocolumn,prl]{revtex4-1}
 \usepackage{amsmath}
@@
 \begin{document}
-\title{Comments on the period three cycle}
+\title{On the 3-cycle of the logistic map}
 \author{Cheng Zhang}
+\date{April 15, 2012}
+\begin{abstract}
+We review a simple derivation of 
+  the onset and bifurcation points the 3-cycle
+  of the logistic map.
+\end{abstract}
 \maketitle
 
-In this note, we shall
-  find the bifurcation point of the period-3 cycle,
-  and show the orbit is real after the onset.
+%\section{Introduction}
+The logistic map reads
+\[
+  z_{n+1} = F(z_n) = r z_n (1 - z_n),
+\]
+We want to find what $r$ values permit a \emph{stable} 3-cycle,
+i.e., a solution of $z_{n+3} = z_n$,
+which can sustain a small deviation in the initial $z_0$.
+The two boundary points $r_0$ and $r_1$ 
+  of the permissible window $(r_0, r_1)$
+  are called the \emph{onset} and \emph{bifurcation} points.
+%
+By a change of variables
+\begin{equation}
+  x_n = r (z_n - 1/2),
+  R = (2 r - r^2)/4,
+\label{eq:chvars}
+\end{equation}
+we get a simplified map
+\[
+x_{n+1} = f(x_n) = R - {x_n}^2.
+\]
+The onset and bifurcation points will be solved
+  in terms of $R$, and the corresponding $r$ values 
+  are obtained by \eqref{eq:chvars}.
 
-\section{The bifurcation point}
-Due to heavier algebra, we shall work with simplified map
+%\section{Cyclic polynomials}
+
+Let $a$, $b$ and $c$ be the three points in the 3-cycle:
+\begin{equation}
+  b=f(a), c=f(b), a=f(c).
+\label{eq:abc}
+\end{equation}
+We define the cyclic polynomials
+$X = a+b+c$,
+$X_k = a^k+b^k+c^k$ (for $k = 2,3$),
+$Y = ab+bc+ca$, and $Z = abc$.
+We will show that the equations of $X$, $Y$, and $Z$
+are more helpful in determining the two points of the 3-cycle.
+
+%\section{Onset point}
+
+For the onset point \cite{zhang},
+we obtain from $c - b = f(b) - f(a)$ that
+$c-b = -(b+a)(b-a)$;
+Similar,
+$a-c = -(c+b)(c-b)=(c+b)(b+a)(b-a)$.
+Now $(b-a) + (c-b) + (a-c) = 0$ means
 \[
-x_{n+1} = f(x_n) = R - {x_n}^2,
+1 - (b+a) + (c+b)(b+a) = 0.
 \]
-and $a$, $b$ and $c$ denote three successive points in the period-3 orbit,
-$b=f(a), c=f(b), a=f(c)$.
-For $X \equiv a + b + c$, we have
+Cycling variables
+$a\rightarrow b$,
+$b\rightarrow c$,
+$c\rightarrow a$,
+and adding up the three distinct versions yields
+\begin{equation}
+3 - 2X + X^2 + Y = 0.
+\label{eq:stair}
+\end{equation}
+%
+On the other hand, the sum of \eqref{eq:abc} gives
+$X = 3R - X_2$,
+and $X^2 = X_2 + 2 Y$;
+so
+\begin{equation}
+X = 3R - X^2 + 2Y.
+\label{eq:XY}
+\end{equation}
+%
+Eliminating $Y$ by \eqref{eq:stair} and \eqref{eq:XY}, we get
+\begin{equation}
+  X^2 - X + 2 - R = 0,
+\label{eq:XR}
+\end{equation}
+This equation has a real root only if $2 - R \le 1/4$.
+Thus, $R = 7/4$ (so $r = 1+\sqrt{1+4R} = 1+ \sqrt 8$)
+is the onset for the only real 3-cycle.
+
+%\section{Bifurcation point}
+
+Let us express cyclic polynomials as linear functions of $X$.
+Using \eqref{eq:stair} and \eqref{eq:XR}, we get
 \begin{align}
-X^2 - X + 2 - R = 0.
-\label{eq:xr}
+  Y    &= X - R - 1, \notag \\
+  X_2  &= X^2 - 2Y = 3R-X,
+\label{eq:Y}
 \end{align}
 %
-Now
-\begin{align}
- Y \equiv a b + b c + c a
-= \frac{1}{2} [ (a + b + c)^2 - (a^2 + b^2 + c^2) ]
-= X - R - 1,
-\label{eq:y}
-\end{align}
-where we have used $(a^2 + b^2 + c^2) = 3R - (a+b+c)$ and \eqref{eq:xr}.
-
-Similarly, we express $Z \equiv abc$ in terms of $X$ by
-\begin{align}
-  a^3 + b^3 + c^3 - 3 a b c =
- (a + b + c) (a^2 + b^2 + c^2 - a b - b c - c a)
-\label{eq:pow3}
-\end{align}
-For the left hand side, we have $a^2 = R - b$, so $a^3 = R a - ab$, and
-\begin{align}
-  a^3 +b^3 + c^3
-= R (a+b+c) - (ab+bc+ca)
-= (R - 1) X + R + 1.
-\label{eq:pow3a}
-\end{align}
+For $X_3$,
+we have $a^3 = R a - ab$ from $b = f(a)$,
+summing over cyclic versions yields,
+\begin{equation}
+X_3 = R X - Y = (R-1) X + R + 1.
+\label{eq:X3}
+\end{equation}
 %
-For the right hand side,
-\begin{align}
-& (a + b + c) (a^2 + b^2 + c^2 - a b - b c - c a)
-= X [X^2 - 3(ab + bc + ca)] \notag\\
-=& X (-2X + 4R + 1)
-= (4R-1) X -2(R-2).
-\label{eq:pow3b}
-\end{align}
-Plugging \eqref{eq:pow3a} and \eqref{eq:pow3b} to \eqref{eq:pow3}, we have
+By the identity
+$X_3 - 3 Z = X (X_2 - Y)$,
+\eqref{eq:X3}, \eqref{eq:Y}, and \eqref{eq:XR},
+we have
 \begin{equation}
-Z \equiv abc = -RX + R - 1.
-\label{eq:abc}
+Z = -RX + R - 1.
+\label{eq:Z}
 \end{equation}
-Solving \eqref{eq:abc} yields $X = 1 + (1+Z)/R$.
-Plugging it into \eqref{eq:xr} yields
+Now \eqref{eq:XR} can be rewritten in terms of $Z$:
 \begin{equation}
   R^3 - 2R^2 + (1+Z)R + (1+Z)^2 = 0.
+\label{eq:RZ}
 \end{equation}
 
-At the onset point $(-2a)(-2b)(-2c) = 1$, or $Z = -1/8$, we have
+We now use the derivative condition:
+at the onset (bifurcation) point,
+$\frac{d}{da}f(f(f(a))) = +1$ ($-1$),
+which by the chain rule, gives
+$f'(c)f'(b)f'(a) = -8abc = \pm1$, or
+\begin{equation}
+  Z = \mp1/8.
+\label{eq:Zder}
+\end{equation}
+%
+At the onset point $Z = -1/8$, \eqref{eq:RZ} becomes
 \[
@@
 \]
-The only real solution is $R = 7/4$, so $r = 1+\sqrt{1+4R} = 1+ \sqrt 8$.
-
-At the bifurcation point $(-2a)(-2b)(-2c) = -1$, or $Z = 1/8$, we have
+The real solution $R = 7/4$ agrees with the previous solution.
+%
+At the bifurcation point $Z = 1/8$, we have
 \[
@@
 
-\section{The existence of the real orbit}
-
-Next we show that the orbit is real after the onset, i.e., $R>7/4$.
-By definition $a$, $b$ and $c$ are solutions of
+We can also show $a$, $b$, $c$ are real after the onset ($R\ge7/4$).
+By definition, $a$, $b$ and $c$ are the distinct roots of
 \[
-  q^3 - X q^2 + Y q - Z = 0.
+  x^3 - X x^2 + Y x - Z = 0.
 \]
@@
 \]
-where we have used \eqref{eq:y} and \eqref{eq:abc},
-and eliminated $R$ by \eqref{eq:xr}.
+where we have used \eqref{eq:Y} and \eqref{eq:Z},
+and eliminated $R$ by \eqref{eq:XR}.
 Thus as long as $X$ is real, $\Delta > 0$, which means there are always three
@@
 
+\begin{thebibliography}{}
+\bibitem{zhang} C. Zhang,
+  Period three begins,
+  \textit{Mathematics Magazine}
+  \textbf{83},
+  295-297
+  (2010).
+\end{thebibliography}
+
 \end{document}

### 2013-04-15 doc/pc-ijbc.tex
improve p3p.tex, add two Makefiles and links

@@
   for $n = 4$, where $\vx \equiv \{x_1, \ldots, x_n\}$.
-A cyclic polynomial should not to be confused with a symmetric polynomial,
+Note that a cyclic polynomial is different from a symmetric polynomial,
   which is invariant under the exchange of any two $x_k$ and $x_{j}$ ($j \ne k$);
@@
   linearly connected by an $\NB \times \NB$ matrix equation.
-The determinant of matrix must vanish,
+The determinant of the matrix must vanish,
   and this condition yields the solution of the problem.

### 2013-04-17 doc/p3p.tex
new webapp2, update p3p.tex, figtree, log.html
new webapp2 interface
figtree: add gnuplot scripts
p3p: improved text, upload to the website
improved text in log.html, cubic.html

@@
 \author{Cheng Zhang}
-\date{April 15, 2012}
+\date{April 17, 2013}
 \begin{abstract}
@@
 %\section{Introduction}
-The logistic map reads
+The logistic map is defined as
 \[
-  z_{n+1} = F(z_n) = r z_n (1 - z_n),
+  z_{n+1} = F(z_n) = r z_n (1 - z_n).
 \]
@@
 which can sustain a small deviation in the initial $z_0$.
-The two boundary points $r_0$ and $r_1$ 
-  of the permissible window $(r_0, r_1)$
-  are called the \emph{onset} and \emph{bifurcation} points.
+The two boundaries $r_0$ and $r_1$ 
+  of the stable window $(r_0, r_1)$
+  are called the \emph{onset} and \emph{bifurcation} points, respectively.
 %
@@
   x_n = r (z_n - 1/2),
-  R = (2 r - r^2)/4,
+  R = (r^2 - 2 r)/4,
 \label{eq:chvars}
@@
   in terms of $R$, and the corresponding $r$ values 
-  are obtained by \eqref{eq:chvars}.
+  are obtained by (\ref{eq:chvars}).
 
@@
 $Y = ab+bc+ca$, and $Z = abc$.
-We will show that the equations of $X$, $Y$, and $Z$
-are more helpful in determining the two points of the 3-cycle.
+We will show that the equations of $X$, $X_k$, $Y$, and $Z$
+are helpful in determining the two points of the 3-cycle.
 
 %\section{Onset point}
-
-For the onset point \cite{zhang},
+\textbf{Onset point.}
+%
+As in Ref. \cite{zhang},
 we obtain from $c - b = f(b) - f(a)$ that
@@
 %
-On the other hand, the sum of \eqref{eq:abc} gives
-$X = 3R - X_2$,
-and $X^2 = X_2 + 2 Y$;
-so
-\begin{equation}
-X = 3R - X^2 + 2Y.
-\label{eq:XY}
-\end{equation}
+On the other hand, the sum of (\ref{eq:abc}) gives
+$X = 3R - X_2 = 3R - X^2 + 2Y$ (for $X^2 = X_2 + 2 Y$).
 %
-Eliminating $Y$ by \eqref{eq:stair} and \eqref{eq:XY}, we get
+Using (\ref{eq:stair}) for $Y$ yields
 \begin{equation}
@@
 Thus, $R = 7/4$ (so $r = 1+\sqrt{1+4R} = 1+ \sqrt 8$)
-is the onset for the only real 3-cycle.
+is the onset point of the only real 3-cycle.
 
 %\section{Bifurcation point}
-
+\textbf{Bifurcation point.}
+%
 Let us express cyclic polynomials as linear functions of $X$.
-Using \eqref{eq:stair} and \eqref{eq:XR}, we get
-\begin{align}
-  Y    &= X - R - 1, \notag \\
-  X_2  &= X^2 - 2Y = 3R-X,
+Using (\ref{eq:stair}) and (\ref{eq:XR}), we get
+\begin{equation}
+  Y  = X - R - 1,
 \label{eq:Y}
-\end{align}
+\end{equation}
+and
+\begin{equation}
+  X_2  = X^2 - 2Y = 3R-X,
+\label{eq:X2}
+\end{equation}
 %
@@
 we have $a^3 = R a - ab$ from $b = f(a)$,
-summing over cyclic versions yields,
+summing over cyclic versions yields
 \begin{equation}
@@
 %
-By the identity
-$X_3 - 3 Z = X (X_2 - Y)$,
-\eqref{eq:X3}, \eqref{eq:Y}, and \eqref{eq:XR},
+By 
+$X_3 - 3 Z = X (X_2 - Y)$ and
+(\ref{eq:XR})-(\ref{eq:X3}),
 we have
@@
 \end{equation}
-Now \eqref{eq:XR} can be rewritten in terms of $Z$:
+Now (\ref{eq:XR}) can be rewritten in terms of $Z$:
 \begin{equation}
@@
 
-We now use the derivative condition:
-at the onset (bifurcation) point,
-$\frac{d}{da}f(f(f(a))) = +1$ ($-1$),
-which by the chain rule, gives
-$f'(c)f'(b)f'(a) = -8abc = \pm1$, or
+The composite map $f(f(f(x)))$ is marginally stable
+at the onset (bifurcation) point, so
+$\frac{d}{da}f(f(f(a))) = f'(c)f'(b)f'(a) = +1 (-1)$
+\cite{saha}.
+Since $f'(x) = -2x$, we have
 \begin{equation}
@@
 %
-At the onset point $Z = -1/8$, \eqref{eq:RZ} becomes
+At the onset point $Z = -1/8$, (\ref{eq:RZ}) becomes
 \[
-  (R-7/4) (R^2 - R/4 + 7/16) = 0.
+  (R-7/4) (R^2 - R/4 + 7/16) = 0,
 \]
-The real solution $R = 7/4$ agrees with the previous solution.
+whose real solution $R = 7/4$ agrees with the previous solution.
 %
@@
 
-We can also show $a$, $b$, $c$ are real after the onset ($R\ge7/4$).
-By definition, $a$, $b$ and $c$ are the distinct roots of
+Since $a$, $b$ and $c$ are the distinct roots of
 \[
@@
 \]
-where we have used \eqref{eq:Y} and \eqref{eq:Z},
-and eliminated $R$ by \eqref{eq:XR}.
+where we have used (\ref{eq:Y}) and (\ref{eq:Z}),
+and eliminated $R$ by (\ref{eq:XR}).
 Thus as long as $X$ is real, $\Delta > 0$, which means there are always three
-real solutions.
+real roots after the onset $R \ge 7/4$
+(Thank Beiye Feng for correspondence on this point).
 
@@
   (2010).
+
+\bibitem{saha} P. Saha and S. H. Strogatz,
+  The birth of period three,
+  \textit{Mathematics Magazine}
+  \textbf{68},
+  42-47
+  (1995).
+
 \end{thebibliography}

### 2013-04-17 logperiod/logperiod.py

@@ -1,17 +1,20 @@
 import os, sys
-from google.appengine.ext import webapp
-from google.appengine.ext.webapp import template
-from google.appengine.ext.webapp.util import run_wsgi_app
+import webapp2, jinja2
 
-class MainPage(webapp.RequestHandler):
-  def get(self, html="index.html"):
+JINJA_ENVIRONMENT = jinja2.Environment(
+    loader=jinja2.FileSystemLoader(os.path.dirname(__file__)))
+
+class MainPage(webapp2.RequestHandler):
+  def get(self, fnhtml="index.html"):
     self.response.headers['Content-Type'] = 'text/html'
-    path = os.path.join(os.path.dirname(__file__), html)
+
+    template = JINJA_ENVIRONMENT.get_template(fnhtml)
+    
     template_values = {
         'prim_ref': '''<h3>Primary reference</h3>
 <ul>
 <li>Cheng Zhang,
-<i>Period cycles of the logistic map</i>,
+<i>Cycles of the logistic map</i>,
 <a href="http://arxiv.org/abs/1204.0546">arXiv:1204.0546</a>, 2012.
 </li>
 </ul>''',
@@ -27,9 +30,9 @@ class MainPage(webapp.RequestHandler):
         </ul></div>''',
 
         'last_update':
-        '<p>Last update: May. 7th, 2012.',
+        '<p>Last update: April. 17th, 2013.',
     }
-    self.response.out.write(template.render(path, template_values))
+    self.response.write(template.render(template_values))
 
 class LogPage(MainPage):
   def get(self):
@@ -43,22 +46,16 @@ class HenonPage(MainPage):
   def get(self):
     MainPage.get(self, "henon.html")
 
-class AboutPage(webapp.RequestHandler):
+class AboutPage(webapp2.RequestHandler):
   def get(self):
     self.response.headers['Content-Type'] = 'text/plain'
-    self.response.out.write('test page')
+    self.response.write('test page')
 
-application = webapp.WSGIApplication(
+app = webapp2.WSGIApplication(
   [('/', MainPage),
    ('/log', LogPage),
    ('/cubic', CubicPage),
    ('/henon', HenonPage),
    ('/about', AboutPage)],
   debug=True)
-
-def main():
-  run_wsgi_app(application)
-
-if __name__ == "__main__":
-  main()
 

### 2013-04-17 logperiod/prog/figtree/figtree.c

@@ -1,23 +1,33 @@
-/* draw fig tree */
+/* draw a fig tree */
 #include <stdio.h>
+#include <stdlib.h>
+#include <string.h>
 #include <math.h>
 
-double rmin = 2.0;
-double rmax = 3.0;
-double delr = 0.002;
 int itermax = 100000000;
 int trajmax = 100;
 double dxtol = 1e-6;
-const char *fnout = "cub.fig";
 
 #ifndef xnew
 #define xnew(x, n) if ((x = calloc(n, sizeof(*(x)))) == NULL) { \
     fprintf(stderr, "no memory for %s x %u\n", #x, (unsigned) (n)); exit(1); }
 #endif
 
+/* logistic map parameters */
+double rmin_l = 2.8;
+double rmax_l = 4;
+double rdel_l = 0.002;
+int x0cnt_l = 1;
+double x0arr_l[1] = {0.1};
 /* logistic map */
 double logistic(double r, double x) { return r*x*(1 - x); }
 
+/* cubic map parameters */
+double rmin_c = 1.8;
+double rmax_c = 3.0;
+double rdel_c = 0.002;
+int x0cnt_c = 2;
+double x0arr_c[2] = {-0.1, 0.1};
 /* cubic map */
 double cubic(double r, double x) { 
   // return x*r*(1 - x*x);  // allows the negative part
@@ -47,45 +57,52 @@ int gettrj(double trj[], int trjmax,
     }
     if (j < trjmax) return j;
   }
-  fprintf(stderr, "failed to converge for r = %.8f\n", r);
+  fprintf(stderr, "failed to converge r %.8f, x0 %g, x %g\n", r, x0, x);
   return trjmax;
 }
 
 /* save the figure tree */
-int mkfigtree(double r0, double r1, double dr, 
+int mkfigtree(double (*func)(double, double), 
+    double r0, double r1, double dr,
+    int x0cnt, double x0arr[], 
     int trjmax, int itmax, double tol,
-    const char *fn)
+    FILE *fp)
 {
   int i, j, k, cnt, rcnt;
-  double r, *trj, x0;
-  FILE *fp;
+  double r, *trj;
 
   xnew(trj, trjmax + 1);
   rcnt = (int)((r1 - r0)/dr + .5);
   dr = (r1 - r0)/rcnt;
-  if ((fp = fopen(fn, "w")) == NULL) {
[…]

### 2013-04-18 doc/p3p.tex
improving p3p.tex
improve the tth command

@@
 %
-As in Ref. \cite{zhang},
-we obtain from $c - b = f(b) - f(a)$ that
-$c-b = -(b+a)(b-a)$;
-Similar,
+%As in Ref. \cite{zhang},
+From (\ref{eq:abc}), we have
+$c-b = f(b) - f(a) = -(b+a)(b-a)$;
+similar,
 $a-c = -(c+b)(c-b)=(c+b)(b+a)(b-a)$.
@@
 $b\rightarrow c$,
-$c\rightarrow a$,
-and adding up the three distinct versions yields
+$c\rightarrow a$
+twice,
+and adding up the three versions yields
 \begin{equation}
@@
 Thus, $R = 7/4$ (so $r = 1+\sqrt{1+4R} = 1+ \sqrt 8$)
-is the onset point of the only real 3-cycle.
+is the onset point of the only real 3-cycle
+\cite{saha, bechhoefer, gordon, burm, zhang}.
 
@@
 \cite{saha}.
-Since $f'(x) = -2x$, we have
+As $f'(x) = -2x$, we get
 \begin{equation}
-  Z = \mp1/8.
+  Z = a b c = \mp1/8.
 \label{eq:Zder}
@@
 \]
-whose real solution $R = 7/4$ agrees with the previous solution.
+whose real solution $R = 7/4$ agrees with the previous result.
 %
@@
 The only real solution is
-$
-R = \frac{2}{3}
+$R = \frac{2}{3}
   +\frac{1}{4} \sqrt[3]{ \frac{1915}{54} + \frac{5}{2} \sqrt{201}}
-  +\frac{1}{4} \sqrt[3]{ \frac{1915}{54} - \frac{5}{2} \sqrt{201}}.
-$
+  +\frac{1}{4} \sqrt[3]{ \frac{1915}{54} - \frac{5}{2} \sqrt{201}}$
+\cite{gordon, burm}.
 
@@
 \]
-The discriminant is
+The discriminant $\Delta$ is a square:
 \[
-\Delta = X^2 Y^2 - 4 Y^3 - 4 X^3 Z + 18 X Y Z - 27 Z^2
+X^2 Y^2 - 4 Y^3 - 4 X^3 Z + 18 X Y Z - 27 Z^2
   = (4X^2 - 6X + 9)^2,
@@
 and eliminated $R$ by (\ref{eq:XR}).
-Thus as long as $X$ is real, $\Delta > 0$, which means there are always three
-real roots after the onset $R \ge 7/4$
-(Thank Beiye Feng for correspondence on this point).
+Thus, as long as $X$ is real
+[which is true after the onset $R \ge 7/4$ by (\ref{eq:XR})],
+we have $\Delta > 0$, and the cycle points are real.
+(Thank Beiye Feng for suggesting this point).
 
 \begin{thebibliography}{}
-\bibitem{zhang} C. Zhang,
-  Period three begins,
-  \textit{Mathematics Magazine}
-  \textbf{83},
-  295-297
-  (2010).
 
@@
 
+\bibitem{bechhoefer} J. Bechhoefer,
+  The birth of period 3, revisited,
+  \textit{Mathematics Magazine}
+  \textbf{69},
+  115-118
+  (1996).
+
+\bibitem{gordon} W. B. Gordon,
+  Period three trajectories of the logistic map,
+  \textit{Mathematics Magazine}
+  \textbf{69},
+  118-120
+  (1996).
+
+\bibitem{burm} J. Burm, P. Fishback,
+  Period-3 Orbits via Sylvester's Theorem and Resultants,
+  \textit{Mathematics Magazine}
+  \textbf{74},
+  47-51
+  (2001).
+
+\bibitem{zhang} C. Zhang,
+  Period three begins,
+  \textit{Mathematics Magazine}
+  \textbf{83},
+  295-297
+  (2010).
+
 \end{thebibliography}

### 2013-04-19 doc/p3p.tex
cobweb.gp oddcycls.gp: nicer arrows and colors
small HTML modifications

@@
 \usepackage{amsmath}
+\usepackage{times}
 
@@
 \date{April 17, 2013}
+
 \begin{abstract}
@@
 \]
-We want to find what $r$ values permit a \emph{stable} 3-cycle,
+We want to find the $r$ values that permit a \emph{stable} 3-cycle,
 i.e., a solution of $z_{n+3} = z_n$,
@@
 $Y = ab+bc+ca$, and $Z = abc$.
-We will show that the equations of $X$, $X_k$, $Y$, and $Z$
-are helpful in determining the two points of the 3-cycle.
+The equations of $X$, $X_k$, $Y$, and $Z$
+are more helpful than those of $a$, $b$ and $c$
+in determining the two points of the 3-cycle.
 

### 2013-04-19 logperiod/logperiod.py

@@ -30,7 +30,7 @@ class MainPage(webapp2.RequestHandler):
         </ul></div>''',
 
         'last_update':
-        '<p>Last update: April. 17th, 2013.',
+        '<p>Last updated on April. 17th, 2013.',
     }
     self.response.write(template.render(template_values))
 

### 2013-04-30 doc/pc-ijbc.tex
edit till sec. 2.4

--- 2013-04-15 doc/pc-ijbc.tex
@@
   through a characteristic equation
-  connecting cyclic polynomials formed by periodic orbit points.
+  connecting the cyclic polynomials of the periodic orbit points.
 The minimal polynomials of the critical parameters
@@
 %
-If we iterate \refeq{logmap} from $k = 0$,
-what does the resulting sequence $x_0$,
-  $x_1 = f(x_0)$,
-  $x_2 = f(x_1)$, $\ldots$ look like?
-%
-%
-%
-We can visualize the sequence on the cobweb plot,
-  see \reffig{cobweb} for examples.
-%
-Starting from $(x_0, x_0)$ on the diagonal,
+If we iterate \refeq{logmap} from $k = 1$,
+the resulting sequence $x_1$,
+  $x_2 = f(x_1)$,
+  $x_3 = f(x_2)$, $\ldots$
+can be conveniently visualized on the cobweb plot,
+  as shown in \reffig{cobweb}.
+%
+Starting from $(x_1, x_1)$ on the diagonal,
   each vertical arrow takes $(x_k, x_k)$ to $(x_k, y)$,
@@
   which starts the next iteration.
-
+%
+%
 \begin{figure}[h]
@@
 \end{figure}
-
-Three outcomes are possible:
+%
+%
+After many iterations, there are three ultimate patterns:
   (i) a \emph{fixed point},
@@
 %
-If $x_0$ deviates slightly from $x^*$
+If $x_1$ deviates slightly from $x^*$
   and the sequence still converges to $x^*$,
-  we call it \emph{stable}.
+  then it is \emph{stable}.
 %
@@
 %
-\big[the reverse is, however, untrue, for a fixed point of $f^n$
+\big[the converse is, however, untrue, for a fixed point of $f^n$
   can also be a fixed point of $f^d$ as long as $d|n$:
-  if $f^d(x) = x$, then $f^n(x) = f^d(\cdots f^d(x)\cdots) = x$\big].
-%
-%
-We can therefore classify a cycle as stable or unstable
-  by the corresponding fixed point of $f^n$:
+  if $f^d(x) = x$, then $f^n(x) = f^d(\cdots f^d(x)\cdots) = x$\big],
+%
+%
+and a cycle can be classified as stable or unstable
+  according to the corresponding fixed point of $f^n$:
   a stable cycle requires
@@
 \begin{equation}
-  \Big| f'(x_1) \dots f'(x_n) \Big| \le 1,
+  \Big| f'(x_1) \cdots f'(x_n) \Big| \le 1,
 \label{eq:der}
@@
 %
-
-The outcome of the iterated sequence of course
-  depends on the parameter $r$.
+The orbit and cycle stability depend on the parameter $r$.
 %
@@
   all regions of $r$ that allow stable $n$-cycles.
-%We ask,
-%  by which $r$ values can a stable $n$-cycle exist?
-%
 
@@
 \[
-    x^{\mathrm{new}} \leftarrow r(x^{\mathrm{old}} - 1/2),
-    \quad R \leftarrow r(r-2)/4,
+    x^{\mathrm{new}} \equiv r(x^{\mathrm{old}} - 1/2),
+    \quad R \equiv r(r-2)/4,
 \]
@@
 %
-We will solve the cycle boundaries as zeros of the polynomials of $R$,
+We will solve the cycle boundaries as zeros of some polynomials of $R$,
 and the corresponding polynomials for $r$ can be obtained by $R \rightarrow r(r-2)/4$.
@@
 
-We solve the problem in two steps.
-Since the $n$-cycles form a subset of the fixed points of $f^n$,
+Since the $n$-cycles constitute a subset of the fixed points of $f^n$,
 we will first find
-  the polynomials at the stability boundaries of
-  the fixed points of $f^n$
-  (\refsecs{cyclic} to \ref{sec:examples}),
-then remove contributions from shorter $d$-cycles ($d|n$)
+  the polynomials at the stability boundaries
+  for the fixed points of $f^n$
+  (\refsecs{cyclic} to \ref{sec:examples}).
+The contributions from shorter $d$-cycles ($d|n$)
+  are lower-degree factors of the polynomials,
+  and can be readily removed
   (\refsecs{primfac} and \ref{sec:degprimfac}).
 
-Let us consider the first step of finding the fixed points of $f^n$.
-At the first glance, the problem can be tackled by brute force:
-  we can solve
-  %the $n$ equations
+At the first glance, the polynomials of the fixed points of $f^n$
+  can be obtained by brute force.
+We can solve
   \refeqs{logmaps} and express $x_1, \ldots, x_n$
@@
   and then plug the solution into \req{der}.
-The result contains $R$ only (no $x_k$),
+The result would contain $R$ only,
   and is therefore the answer.
 But since \refeqs{logmaps} are nonlinear,
-  it quickly becomes impossible for $n > 2$,
-  as the degree of polynomials grows exponentially;
-  thus it is nontrivial to reduce the final equation of $R$
-  into a polynomial one.
+  it is nontrivial to reduce the final equation of $R$
+  into a polynomial form.
 Nonetheless, on a computer, one can
-  construct a Gr\"obner basis \cite{kk1}
-  to automate the reduction.
-%
-The approach, albeit straightforward, does not
+  construct a polynomial Gr\"obner basis \cite{kk1}
+  that gradually eliminates $x_k$ out of the $n+1$ equations.
+As a special case, if $x_2, \dots, x_n$ are eliminated first,
+  the final elimination of $x_1$ can be accomplished
+  by setting the resultant of $f^n(x_1) = x_1$ and
+  \refeq{der} or $\frac{d}{dx}f^n (x_1) = \pm 1$
+  to zero \cite{burm},
+  which furnishes the needed polynomial equation of $R$.
+%
+These approaches, however, do not
   exploit the cyclic structure of \refeqs{logmaps},
-can thus be improved by the following alternative.
+  and can thus be improved by the following alternative.
 
@@
 whose roots contain all fixed points of $f^n$.
-This completes the first step.
 %
@@
 %
-
-For the second step,
-we show
-that short cycles serve as
-factors in the polynomials obtained above,
-and thus can be readily factored out.
 
@@
   and $b(\vx) = x_1 x_3 + x_2 x_4$,
-  for $n = 4$, where $\vx \equiv \{x_1, \ldots, x_n\}$.
-A cyclic polynomial should not to be confused with a symmetric polynomial,
+  where $\vx \equiv \{x_1, \ldots, x_n\}$ and $n = 4$.
+Note that a cyclic polynomial is not necessarily a symmetric one,
   which is invariant under the exchange of any two $x_k$ and $x_{j}$ ($j \ne k$);
@@
 
-We now consider cyclic polynomials
-  generated from a monomial of unit coefficient,
-  such as $a(\vx)$ and $b(\vx)$, but not $a(\vx) + b(\vx)$.
-They can be systematically labeled as follows.
-We pick the monomial generator,
-  which can be written as
+Cyclic polynomials
+  generated from monomials of unit coefficient
+  [such as $a(\vx)$ and $b(\vx)$, but not $a(\vx) + b(\vx)$]
+  can be labeled as follows.
+We first write the monomial generator as
   ${x_1}^{e_1} {x_2}^{e_2} \dots {x_n}^{e_n}$,
-  then form a sequence $p$ of indices with
-  $e_1$ 1's, $e_2$ 2's, \ldots, $e_n$ $n$'s;
-  the corresponding cyclic polynomial is denoted by $C_p(\vx)$,
-e.g.,
+  then the sequence $p$ of indices with
+  $e_1$ 1's, $e_2$ 2's, \ldots, $e_n$ $n$'s
+  serves as the label of the cyclic polynomial $C_p(\vx)$.
+For example,
   $C_{12}(\vx)  = x_1 x_2 + x_2 x_3 + \dots + x_n x_1$ and
   $C_{112}(\vx) = {x_1}^2 x_2 + {x_2}^2 x_3 + \dots + {x_n}^2 x_1$.
-We omit the length $n$ in this notation,
-  for we will mostly work with a fixed $n$ at a time.
-Since a cyclic polynomial can have multiple generators,
-  e.g., both $x_1 x_2$ and $x_2 x_3$ are generators of $C_{12}(\vx)$
-   (assuming $n \ge 3$),
-  we pick the one that corresponds to
-  the smallest $p$
+The cycle length $n$ is omitted for convenience.
+%  for we will mostly work with a fixed $n$ at a time.
+In case the cyclic polynomial has several generators,
+%  e.g., both $x_1 x_2$ and $x_2 x_3$ are generators of $C_{12}(\vx)$
+%   (assuming $n \ge 3$),
+  we pick the one with the smallest $p$
   in the sense of lexicographic order,
-  e.g., we choose $x_1 x_2$ instead of $x_2 x_3$ for $C_{12}(\vx)$,
-  because $12 < 23$.
+  e.g., we choose $x_1 x_2$ instead of $x_2 x_3$ for $C_{12}(\vx)$
+  because $12 < 23$ ($n \ge 3$).
 Finally, we add $C_0(\vx) \equiv 1$ for completeness.
@@
 
-\subsection{Square-free cyclic polynomials}
-
-We further restrict ourselves to
-  a subset of square-free cyclic polynomials,
-  which have no square or higher powers of any $x_k$,
-  e.g., $C_{12}(\vx) = x_1 x_2 + \dots$ is square-free,
-  $C_{112}(\vx) = {x_1}^2 x_2 + \dots$ is not,
-see \reftab{sqrfreepoly} for more examples.
-Obviously, the label $p$ of a square-free polynomial
+\subsection{Square-free reduction}
+
+We now consider
+  a subset of \emph{square-free} cyclic polynomials,
+  which have no square or higher powers of $x_k$.
+For example, $C_{12}(\vx) = x_1 x_2 + \cdots$ is square-free,
+  $C_{112}(\vx) = {x_1}^2 x_2 + \cdots$ is not.
+%see \reftab{sqrfreepoly} for more examples.
+The label $p$ of a square-free polynomial
   has no repeated index.
-We denote the set of all square-free $p$ by
-$\Bset = \{0, 1, 12, 13, \ldots, 123, 124, \ldots, 12\dots n\}$
-%  ($n \ge 4$),
-such that its size $|\Bset|$ equals the number $\NB$ of
+The set of all square-free $p$ is denoted by
+$\Bset = \{0, 1, 12, 13, \ldots, 123, 124, \ldots, 12\dots n\}$,
+and its size $|\Bset|$ equals the number $\NB$ of
   square-free cyclic polynomials.
-
-\begin{table}[h]\footnotesize
-\tbl{
-Square-free cyclic polynomials $C_p(\vx)$ for the logistic map ($n \ge 5$).}
-%\begin{center}
-{
-\begin{tabular}{c c c c c}
-\hline
-$p$ & $C_p(\vx)$ & Generator$^\dagger$ & Necklace$^\ddagger$ & $p$ as an index set$^*$\\
-\hline
-0             & 1 & 1 & $0\ldots0$ & $\emptyset$ \\
-1             & $x_1 + x_2 + \dots + x_n$
-              & $x_1$ (or $x_2$, \ldots)
-              & $10\ldots0$
-              & $\{1\}$ (or $\{2\}$, \ldots) \\
-12            & $x_1 x_2 + x_2 x_3 + \dots + x_n x_1$
-              & $x_1 x_2$ (or $x_2 x_3$, \ldots)
-              & $110\ldots0$
-              & $\{1, 2\}$ (or $\{2, 3\}$, \ldots) \\
-13            & $x_1 x_3 + x_2 x_4 + \dots + x_n x_2$
-              & $x_1 x_3$ (or $x_2 x_4$, \ldots)
-              & $1010\ldots0$
-              & $\{1, 3\}$ (or $\{2, 4\}$, \ldots) \\
-$\vdots$      & $\vdots$ \\
-123           & \hspace{1mm}$x_1 x_2 x_3 + x_2 x_3 x_4 + \dots + x_n x_1 x_2$\hspace{1mm}
-              & \hspace{1mm}$x_1 x_2 x_3$ (or $x_2 x_3 x_4$, \ldots)\hspace{1mm}
-              & $1110\ldots0$
-              & $\{1, 2, 3\}$ (or $\{2, 3, 4\}$, \ldots) \\
-124           & $x_1 x_2 x_4 + x_2 x_3 x_5 + \dots + x_n x_1 x_3$
-              & $x_1 x_2 x_4$ (or $x_2 x_3 x_5$, \ldots)
-              & $11010\ldots0$
-              & $\{1, 2, 4\}$ (or $\{2, 3, 4\}$, \ldots) \\
-$\vdots$      & $\vdots$ \\
-$12\dots n$  & $x_1 x_2 \dots x_n$
-              & $x_1 x_2 \dots x_n$
-              & $11\ldots1$
-              & $\{1, 2, \ldots, n\}$  \\
-\hline
-\multicolumn{5}{p{\linewidth}}{
-$^\dagger$ Alternative generators are shown in parentheses.
-}\\
-\multicolumn{5}{p{\linewidth}}{
-$^\ddagger$ The corresponding binary necklaces.
-}\\
-\multicolumn{5}{p{\linewidth}}{
-$^*$ The label $p$ of a square-free cyclic polynomial
-    has no repeated indices;
-    so the indices can be cast to a set.
-}\\
-\hline
-\end{tabular}
-\label{tab:sqrfreepoly}
-}
-%\end{center}
-\end{table}
-
-We first show that
-  the square-free cyclic polynomials
-  serve as a basis for expanding cyclic polynomials:
+%
+%
+The square-free cyclic polynomials
+  furnish a basis for expanding cyclic polynomials:
+
+%\begin{table}[h]\footnotesize
+%\tbl{
+%Square-free cyclic polynomials $C_p(\vx)$ for the logistic map ($n \ge 5$).}
+%%\begin{center}
+%{
+%\begin{tabular}{c c c c c}
+%\hline
+%$p$ & $C_p(\vx)$ & Generator$^\dagger$ & Necklace$^\ddagger$ & $p$ as an index set$^*$\\
+%\hline
+%0             & 1 & 1 & $0\ldots0$ & $\emptyset$ \\
+%1             & $x_1 + x_2 + \dots + x_n$
+%              & $x_1$ (or $x_2$, \ldots)
+%              & $10\ldots0$
+%              & $\{1\}$ (or $\{2\}$, \ldots) \\
+%12            & $x_1 x_2 + x_2 x_3 + \dots + x_n x_1$
+%              & $x_1 x_2$ (or $x_2 x_3$, \ldots)
+%              & $110\ldots0$
+%              & $\{1, 2\}$ (or $\{2, 3\}$, \ldots) \\
+%13            & $x_1 x_3 + x_2 x_4 + \dots + x_n x_2$
+%              & $x_1 x_3$ (or $x_2 x_4$, \ldots)
+%              & $1010\ldots0$
+%              & $\{1, 3\}$ (or $\{2, 4\}$, \ldots) \\
+%$\vdots$      & $\vdots$ \\
+%123           & \hspace{1mm}$x_1 x_2 x_3 + x_2 x_3 x_4 + \dots + x_n x_1 x_2$\hspace{1mm}
+%              & \hspace{1mm}$x_1 x_2 x_3$ (or $x_2 x_3 x_4$, \ldots)\hspace{1mm}
+%              & $1110\ldots0$
+%              & $\{1, 2, 3\}$ (or $\{2, 3, 4\}$, \ldots) \\
+%124           & $x_1 x_2 x_4 + x_2 x_3 x_5 + \dots + x_n x_1 x_3$
+%              & $x_1 x_2 x_4$ (or $x_2 x_3 x_5$, \ldots)
+%              & $11010\ldots0$
+%              & $\{1, 2, 4\}$ (or $\{2, 3, 4\}$, \ldots) \\
+%$\vdots$      & $\vdots$ \\
+%$12\dots n$  & $x_1 x_2 \dots x_n$
+%              & $x_1 x_2 \dots x_n$
+%              & $11\ldots1$
+%              & $\{1, 2, \ldots, n\}$  \\
+%\hline
+%\multicolumn{5}{p{\linewidth}}{
+%$^\dagger$ Alternative generators are shown in parentheses.
+%}\\
+%\multicolumn{5}{p{\linewidth}}{
+%$^\ddagger$ The corresponding binary necklaces.
+%}\\
+%\multicolumn{5}{p{\linewidth}}{
+%$^*$ The label $p$ of a square-free cyclic polynomial
+%    has no repeated indices;
+%    so the indices can be cast to a set.
+%}\\
+%\hline
+%\end{tabular}
+%\label{tab:sqrfreepoly}
+%}
+%%\end{center}
+%\end{table}
 
@@
 \]
-  where $\Bset = \{0, 1, 12, 13, \ldots, 12\dots n\}$ is
-  the set of indices of all square-free cyclic polynomials,
+  where $\Bset$ % = \{0, 1, 12, 13, \ldots, 12\dots n\}$ is
+  is the set of indices of all square-free cyclic polynomials,
   and $f_p(R)$ are polynomials of $R$.
@@
 \begin{proof}
-We show the theorem by the following square-free reduction.
+Consider the following square-free reduction.
 %
@@
 The process will not last indefinitely
-  for each substitution reduces the degree in $x_k$ (no matter which $k$)
+  for each substitution reduces the degree in $x_k$ %(no matter which $k$)
   by one.
 Since the original polynomial is cyclic,
-  so is the reduced one.
+  so is the reduced one, which is also square-free.
 All terms that involve no $x_k$
-  are collected to serve as the coefficient before $C_0(\vx)$, which is 1.
-Since no square or higher powers of $x_k$
-  can survive the reduction,
-  all cyclic polynomials in the final result
-  are square-free.
-The coefficients are polynomials of $R$,
+  are collected to serve as the coefficient before $C_0(\vx) \equiv 1$.
+%Since no square or higher powers of $x_k$
+%  can survive the reduction,
+%  the final cyclic polynomials are square-free;
+The coefficients $f_p$ are polynomials of $R$,
   for $R$ is the only variable introduced by the substitutions.
@@
   the square-free cyclic polynomials $C_p(\vx)$ are themselves
-  linearly connected by an $\NB \times \NB$ matrix equation.
-The determinant of matrix must vanish,
-  and this condition yields the solution of the problem.
+  linearly connected by $\NB$ homogeneous equations.
+The matrix of the connecting coefficients must have a zero determinant,
+  which yields the desired polynomial.
 
@@
 \end{equation}
-Here we have defined $A_n\RX$ as a polynomial of $R$ and $\lambda$,
-  and we have also attached the subscript $n$,
-  for later use with $A_d\RX$, where $d$ are divisors of $n$.
+Here, $A_n\RX$ is a polynomial of $R$ and $\lambda$,
+  and the subscript $n$ is attached such that 
+  it can be used later with $A_d\RX$ of divisors $d$ of $n$.
 \refeq{xr} is a necessary condition
@@
   $\lambda$ being $+1$ and $-1$, respectively,
-  and $T_{pq}(R)$ the coefficients
+  and $T_{pq}(R)$ are the coefficients
   from the square-free reduction of $\Lambda(\vx) \, C_p(\vx)$
@@
   for stable cycles.
-  These regions are bulbs in the Mandelbrot set,
+  These regions are bulbs in the inverted Mandelbrot set,
   %(however, we need the replacement
@@
   %$R \rightarrow -c$)
-  see ref. \cite{stephenson} and \reffig{logbulb}.
+  see ref. \cite{stephenson}. % and \reffig{logbulb}.
 
@@
   since at least one of the $x_k$ is zero by \refeq{logder},
-  then $f^n(x_k = 0) = x_{n+k} = 0$ provides
-  the needed polynomial equation of $R$ \cite{strogatz}.
+  then $f^n(x_k = 0) = x_{n+k} = 0$, which provides
+  the desired equation of $R$ \cite{strogatz}.
 \end{remark}
@@
 For complex $R$, $\lambda$, and $\vx$,
-the method can also compute the region of stability for $R$,
+the method can also compute the region of stability for $R$
+  (i.e., the inverted Mandelbrot set),
 with $\lambda$ being $\exp(i\theta)$ \big[$\theta \in (0, 2\pi)$\big]
-  instead of $\pm1$;
-the results are shown in \reffig{logbulb}
-for $n$ up to $8$.
+  instead of $\pm1$.
+%the results are shown in \reffig{logbulb}
+%for $n$ up to $8$.
 %
@@
 
-\begin{figure}[h]
-  \begin{minipage}{\linewidth}
-    \begin{center}
-        \includegraphics[angle=-90, width=.67\linewidth]{logbulb.pdf}
-    \end{center}
-  \end{minipage}%
-  \caption{
-  \label{fig:logbulb}
-  Stable regions of the $n$-cycles of the simplified logistic map \refeq{logmaps}
-  with a complex $R$;
-  obtained from $P_n(R, e^{i\theta}) = 0$ with $\theta \in [0, 2\pi]$,
-  cf. Fig. 3 in \cite{stephenson}.
-}
-\end{figure}
+%\begin{figure}[h]
+%  \begin{minipage}{\linewidth}
+%    \begin{center}
+%        \includegraphics[angle=-90, width=.67\linewidth]{logbulb.pdf}
+%    \end{center}
+%  \end{minipage}%
+%  \caption{
+%  \label{fig:logbulb}
+%  Stable regions of the $n$-cycles of the simplified logistic map \refeq{logmaps}
+%  with a complex $R$;
+%  obtained from $P_n(R, e^{i\theta}) = 0$ with $\theta \in [0, 2\pi]$,
+%  cf. Fig. 3 in \cite{stephenson}.
+%}
+%\end{figure}
 
@@
   and $C_{123} = x_1 x_2 x_3$ (generator: $x_1 x_2 x_3$), respectively.
-\reftab{sqrfreepoly} shows a few more examples.
+%\reftab{sqrfreepoly} shows a few more examples.
 %
@@
   which corresponds to a contact points between ``bulbs''
-  in the Mandelbrot set, see \reffig{logbulb}.
+  in the inverted Mandelbrot set, see \reffig{logbulb}.
 \end{remark}
@@
   ($C_{13} = x_1 \, x_3 + x_2 \, x_4 + \dots + x_n \, x_2$,
-  generator: $x_1 \, x_3 $, assuming $n \ge 4$);
-more examples are listed in \reftab{sqrfreepoly}).
+  generator: $x_1 \, x_3 $, assuming $n \ge 4$).
+%more examples are listed in \reftab{sqrfreepoly}).
 %
@@
 %is that it is odd:
-%for a trajectory $x_0, x_1, x_2, \ldots$
-%the mirror $-x_0, -x_1, -x_2, \ldots$
+%for a trajectory $x_1, x_2, \ldots$
+%the mirror $-x_1, -x_2, \ldots$
 %also satisfies the map.
@@
 
+\bibitem[Burm \& Fishback(2001)]{burm}
+  Burm, J. \& Fishback, P. [2001]
+  ``Period-3 Orbits via Sylvester's Theorem and Resultants,''
+  {\it Mathematics Magazine}
+  \textbf{74},
+  47--51.
+
 \bibitem[Stephenson(1992)]{stephenson}
@@
   118--120.
-
-\bibitem[Burm \& Fishback(2001)]{burm}
-  Burm, J. \& Fishback, P. [2001]
-  ``Period-3 Orbits via Sylvester's Theorem and Resultants,''
-  {\it Mathematics Magazine}
-  \textbf{74},
-  47--51.
 

### 2013-04-30 doc/pc.tex
edit till sec. 2.4

@@
 
-The outcome of the iterated sequence of course
-  depends on the parameter $r$.
+The orbit and cycle stability depend on the parameter $r$.
 %
@@
 
-We solve the problem in two steps.
+%We solve the problem in two steps.
 Since the $n$-cycles form a subset of the fixed points of $f^n$,
@@
   the fixed points of $f^n$
-  (\refsecs{cyclic} to \ref{sec:examples}),
-then remove contributions from shorter $d$-cycles ($d|n$)
+  (\refsecs{cyclic} to \ref{sec:examples}).
+The contributions from shorter $d$-cycles ($d|n$)
+  are lower-degree factors of the polynomials,
+  and can be readily removed
   (\refsecs{primfac} and \ref{sec:degprimfac}).
 
-Let us consider the first step of finding the fixed points of $f^n$.
-At the first glance, the problem can be tackled by brute force:
-  we can solve
-  %the $n$ equations
+%Let us consider the first step of finding the fixed points of $f^n$.
+At the first glance, the polynomials of the fixed points of $f^n$
+  can be obtained by brute force.
+We can solve
   \refeqs{logmaps} and express $x_1, \ldots, x_n$
@@
   and then plug the solution into \req{der}.
-The result contains $R$ only (no $x_k$),
+The result would contain $R$ only,
   and is therefore the answer.
 But since \refeqs{logmaps} are nonlinear,
-  it quickly becomes impossible for $n > 2$,
-  as the degree of polynomials grows exponentially;
-  thus it is nontrivial to reduce the final equation of $R$
-  into a polynomial one.
+  it is nontrivial to reduce the final equation of $R$
+  into a polynomial form.
 Nonetheless, on a computer, one can
-  construct a Gr\"obner basis \cite{kk1}
-  to automate the reduction.
-%
-The approach, albeit straightforward, does not
+  construct a (polynomial) Gr\"obner basis \cite{kk1}
+  that gradually eliminates $x_k$ out of the $n+1$ equations.
+As a special case, if $x_2, \dots, x_n$ are eliminated first,
+  the final elimination of $x_1$ can be accomplished
+  by setting the resultant of $f^n(x_1) = x_1$ and
+  \refeq{der} or $\frac{d}{dx}f^n (x_1) = \pm 1$
+  to zero \cite{burm},
+  which furnishes the needed polynomial equation of $R$.
+%
+These approaches, however, do not
   exploit the cyclic structure of \refeqs{logmaps},
-can thus be improved by the following alternative.
+  and can thus be improved by the following alternative.
 
@@
   and $b(\vx) = x_1 x_3 + x_2 x_4$,
-  for $n = 4$, where $\vx \equiv \{x_1, \ldots, x_n\}$.
-Note that a cyclic polynomial is different from a symmetric polynomial,
+  where $\vx \equiv \{x_1, \ldots, x_n\}$ and $n = 4$.
+Note that a cyclic polynomial is not necessarily from a symmetric one,
   which is invariant under the exchange of any two $x_k$ and $x_{j}$ ($j \ne k$);
@@
 
-\subsection{Square-free cyclic polynomials}
-
-We further restrict ourselves to
-  a subset of square-free cyclic polynomials,
+\subsection{Square-free reduction}
+
+We now consider
+  a subset of \emph{square-free} cyclic polynomials,
   which have no square or higher powers of any $x_k$,
-  e.g., $C_{12}(\vx) = x_1 x_2 + \dots$ is square-free,
-  $C_{112}(\vx) = {x_1}^2 x_2 + \dots$ is not,
+  e.g., $C_{12}(\vx) = x_1 x_2 + \cdots$ is square-free,
+  $C_{112}(\vx) = {x_1}^2 x_2 + \cdots$ is not,
   see \reftab{sqrfreepoly} for more examples.
-Obviously, the label $p$ of a square-free polynomial
+The label $p$ of a square-free polynomial
   has no repeated index.
@@
   the square-free cyclic polynomials $C_p(\vx)$ are themselves
-  linearly connected by an $\NB \times \NB$ matrix equation.
+  linearly connected by $\NB$ homogeneous equations.
 The determinant of the matrix must vanish,
@@
 
+\bibitem{burm} J. Burm, P. Fishback,
+  Period-3 Orbits via Sylvester's Theorem and Resultants,
+  \textit{Mathematics Magazine}
+  \textbf{74},
+  47-51
+  (2001).
+
 \bibitem{stephenson} J. Stephenson,
@@
   (1996).
-
-\bibitem{burm} J. Burm, P. Fishback,
-  Period-3 Orbits via Sylvester's Theorem and Resultants,
-  \textit{Mathematics Magazine}
-  \textbf{74},
-  47-51
-  (2001).
 

### 2013-05-01 doc/pc-ijbc.tex
remove spaces, polish introduction

@@
 %
-If we iterate \refeq{logmap} from $k = 1$,
-the resulting sequence $x_1$,
+The iterated \refeq{logmap} sequence $x_1$,
   $x_2 = f(x_1)$,
@@
   $(y, y) = (x_{k+1}, x_{k+1})$,
-  which starts the next iteration.
+  where the next iteration starts.
 %
@@
 %
-After many iterations, there are three ultimate patterns:
-  (i) a \emph{fixed point},
-      which is a constant (including infinity),
+After many iterations, there can be three ultimate patterns:
+  (i) a \emph{fixed point} or a constant (including infinity),
       e.g., \reffig{cobweb}(a);
-  (ii) a periodic \emph{cycle},
-      which is a self-repeating pattern,
+  (ii) a periodic \emph{cycle} or a self-repeating loop,
       e.g., \reffigs{cobweb}(b)-(e);
-%On the cobweb plot, an $n$-cycle is a loop of $2n$ segments.
 or
@@
 \big[the converse is, however, untrue, for a fixed point of $f^n$
-  can also be a fixed point of $f^d$ as long as $d|n$:
+  can also be a fixed point of $f^d$ of a divisor $d$ of $dn$:
   if $f^d(x) = x$, then $f^n(x) = f^d(\cdots f^d(x)\cdots) = x$\big],
@@
 \end{equation}
-where $x_1. \ldots, x_n$ are the $n$ points within the cycle, or the orbit.
-Further, the onset and bifurcation points
+The set of the $n$ points within the cycle $x_1. \ldots, x_n$
+   is called the \emph{orbit}.
+The onset and bifurcation points
   are defined at the loci

### 2013-05-01 logperiod/logperiod.py

@@ -9,7 +9,7 @@ class MainPage(webapp2.RequestHandler):
     self.response.headers['Content-Type'] = 'text/html'
 
     template = JINJA_ENVIRONMENT.get_template(fnhtml)
-    
+
     template_values = {
         'prim_ref': '''<h3>Primary reference</h3>
 <ul>

### 2013-05-01 logperiod/prog/figtree/figtree.c

@@ -29,16 +29,16 @@ double rdel_c = 0.002;
 int x0cnt_c = 2;
 double x0arr_c[2] = {-0.1, 0.1};
 /* cubic map */
-double cubic(double r, double x) { 
+double cubic(double r, double x) {
   // return x*r*(1 - x*x);  // allows the negative part
-  return x*(r - x*x); 
+  return x*(r - x*x);
 }
 
 /* get period trajectories
  * trj[]: trajectories, trjmax is its size
  * itmax: maximal number of iterations  */
-int gettrj(double trj[], int trjmax, 
-    double r, double (*f)(double, double), int itmax, 
+int gettrj(double trj[], int trjmax,
+    double r, double (*f)(double, double), int itmax,
     double x0, double tol)
 {
   int i, j;
@@ -62,9 +62,9 @@ int gettrj(double trj[], int trjmax,
 }
 
 /* save the figure tree */
-int mkfigtree(double (*func)(double, double), 
+int mkfigtree(double (*func)(double, double),
     double r0, double r1, double dr,
-    int x0cnt, double x0arr[], 
+    int x0cnt, double x0arr[],
     int trjmax, int itmax, double tol,
     FILE *fp)
 {
@@ -76,7 +76,7 @@ int mkfigtree(double (*func)(double, double),
   dr = (r1 - r0)/rcnt;
   for (i = 0; i <= rcnt; i++) {
     r = r0 + i * dr;
-    /* because there are multiple stable period trajectories, 
+    /* because there are multiple stable period trajectories,
      * we explore them by different initial values */
     for (k = 0; k < x0cnt; k++) {
       cnt = gettrj(trj, trjmax, r, func, itmax, x0arr[k], tol);

### 2013-05-01 prog/script/logrep.py

@@ -89,7 +89,7 @@ def modifypbs(ch, n):
   print "%s solutions to do" % tot
 
 def submit(ch, n):
-  c = raw_input("will now submit jobs?").strip().lower()  
+  c = raw_input("will now submit jobs?").strip().lower()
   for i in range(1, 33):
     dir = "%s%s%s" % (n, ch, i)
     os.chdir(dir)

### 2013-05-01 doc/pc-ijbc.tex
doc: a simplified version

@@
 \newcommand{\vx}{\vct x}
-\newcommand{\Bset}{\mathcal B}
-\newcommand{\NB}{N_\Bset}
-\newcommand{\RX}{(R, \lambda)}
+% basis set of cyclic polynomials
+\newcommand{\Pset}{\mathcal P}
+\newcommand{\NB}{N_\Pset}
+\newcommand{\Rlam}{(R, \lambda)}
 
@@
 \begin{figure}[h]
-  \begin{minipage}{\linewidth}
   \begin{center}
+  \begin{minipage}{0.5 \linewidth}
         \includegraphics[angle=-90, width=\linewidth]{cobweb.pdf}
+  \end{minipage}%
   \end{center}
-  \end{minipage}%
   \caption{\label{fig:cobweb}
@@
 \big[the converse is, however, untrue, for a fixed point of $f^n$
-  can also be a fixed point of $f^d$ of a divisor $d$ of $dn$:
+  can also be a fixed point of $f^d$ for a divisor $d$ of $dn$:
   if $f^d(x) = x$, then $f^n(x) = f^d(\cdots f^d(x)\cdots) = x$\big],
@@
 
-We will illustrate the algorithm on the logistic map \cite{may, strogatz},
+We will illustrate the algorithm on the logistic map \cite{may, strogatz}
   defined in \refeq{logmap}.
@@
 %
-There are generally multiple such windows even for a single $n$,
+There are generally multiple such windows for a single $n$,
   but all onset points satisfy the same polynomial equation,
@@
 
-To simplify the calculation, we first change variables \cite{saha} by
+To simplify the calculation, we first change variables \cite{saha} as
 %
@@
   it is nontrivial to reduce the final equation of $R$
-  into a polynomial form.
+  into a polynomial one.
 Nonetheless, on a computer, one can
@@
   where $\vx \equiv \{x_1, \ldots, x_n\}$ and $n = 4$.
-Note that a cyclic polynomial is not necessarily a symmetric one,
-  which is invariant under the exchange of any two $x_k$ and $x_{j}$ ($j \ne k$);
+Note that a cyclic polynomial is not necessarily symmetric
+  (i.e., invariant under the exchange of any two $x_k$ and $x_{j}$),
   e.g., $a(\vx)$ and $b(\vx)$ are not symmetric,
@@
 A cyclic polynomial can be generated by summing over
-  distinct cyclic versions of a simpler polynomial of $x_k$, or a \emph{generator},
-e.g.,
+  distinct cyclic versions of a simpler polynomial of $x_k$, or a \emph{generator}.
+For example,
 $x_1 x_2$ is a generator of $a(\vx)$;
@@
 and
-$x_1 x_2 + \frac{1}{2} x_1 x_3$ is that of $a(\vx) + b(\vx)$;
-note that the coefficient before $x_1 x_3$
+$x_1 x_2 + \frac{1}{2} x_1 x_3$ is that of $a(\vx) + b(\vx)$.
+Note that the coefficient before $x_1 x_3$
   is 1 in the second case
@@
 
-We now consider
-  a subset of \emph{square-free} cyclic polynomials,
-  which have no square or higher powers of $x_k$.
-For example, $C_{12}(\vx) = x_1 x_2 + \cdots$ is square-free,
+A cyclic polynomial is \emph{square-free}
+  if it has no square or higher powers of $x_k$,
+e.g., $C_{12}(\vx) = x_1 x_2 + \cdots$ is square-free,
   $C_{112}(\vx) = {x_1}^2 x_2 + \cdots$ is not.
@@
 The set of all square-free $p$ is denoted by
-$\Bset = \{0, 1, 12, 13, \ldots, 123, 124, \ldots, 12\dots n\}$,
-and its size $|\Bset|$ equals the number $\NB$ of
+$\Pset = \{0, 1, 12, 13, \ldots, 123, 124, \ldots, 12\dots n\}$,
+and its size $|\Pset|$ equals the number $\NB$ of
   square-free cyclic polynomials.
@@
 %
-The square-free cyclic polynomials
-  furnish a basis for expanding cyclic polynomials:
-
-%\begin{table}[h]\footnotesize
-%\tbl{
-%Square-free cyclic polynomials $C_p(\vx)$ for the logistic map ($n \ge 5$).}
-%%\begin{center}
-%{
-%\begin{tabular}{c c c c c}
-%\hline
-%$p$ & $C_p(\vx)$ & Generator$^\dagger$ & Necklace$^\ddagger$ & $p$ as an index set$^*$\\
-%\hline
-%0             & 1 & 1 & $0\ldots0$ & $\emptyset$ \\
-%1             & $x_1 + x_2 + \dots + x_n$
-%              & $x_1$ (or $x_2$, \ldots)
-%              & $10\ldots0$
-%              & $\{1\}$ (or $\{2\}$, \ldots) \\
-%12            & $x_1 x_2 + x_2 x_3 + \dots + x_n x_1$
-%              & $x_1 x_2$ (or $x_2 x_3$, \ldots)
-%              & $110\ldots0$
-%              & $\{1, 2\}$ (or $\{2, 3\}$, \ldots) \\
-%13            & $x_1 x_3 + x_2 x_4 + \dots + x_n x_2$
-%              & $x_1 x_3$ (or $x_2 x_4$, \ldots)
-%              & $1010\ldots0$
-%              & $\{1, 3\}$ (or $\{2, 4\}$, \ldots) \\
-%$\vdots$      & $\vdots$ \\
-%123           & \hspace{1mm}$x_1 x_2 x_3 + x_2 x_3 x_4 + \dots + x_n x_1 x_2$\hspace{1mm}
-%              & \hspace{1mm}$x_1 x_2 x_3$ (or $x_2 x_3 x_4$, \ldots)\hspace{1mm}
-%              & $1110\ldots0$
-%              & $\{1, 2, 3\}$ (or $\{2, 3, 4\}$, \ldots) \\
-%124           & $x_1 x_2 x_4 + x_2 x_3 x_5 + \dots + x_n x_1 x_3$
-%              & $x_1 x_2 x_4$ (or $x_2 x_3 x_5$, \ldots)
-%              & $11010\ldots0$
-%              & $\{1, 2, 4\}$ (or $\{2, 3, 4\}$, \ldots) \\
-%$\vdots$      & $\vdots$ \\
-%$12\dots n$  & $x_1 x_2 \dots x_n$
-%              & $x_1 x_2 \dots x_n$
-%              & $11\ldots1$
-%              & $\{1, 2, \ldots, n\}$  \\
-%\hline
-%\multicolumn{5}{p{\linewidth}}{
-%$^\dagger$ Alternative generators are shown in parentheses.
-%}\\
-%\multicolumn{5}{p{\linewidth}}{
-%$^\ddagger$ The corresponding binary necklaces.
-%}\\
-%\multicolumn{5}{p{\linewidth}}{
-%$^*$ The label $p$ of a square-free cyclic polynomial
-%    has no repeated indices;
-%    so the indices can be cast to a set.
-%}\\
-%\hline
-%\end{tabular}
-%\label{tab:sqrfreepoly}
-%}
-%%\end{center}
-%\end{table}
+The set of square-free cyclic polynomials
+  furnishes a basis for expanding cyclic polynomials:
 
@@
 \[
-  K(\vx) = \sum_{p \in \Bset} f_p(R) \, C_p(\vx),
+  K(\vx) = \sum_{p \in \Pset} f_p(R) \, C_p(\vx),
 \]
-  where $\Bset$ % = \{0, 1, 12, 13, \ldots, 12\dots n\}$ is
+  where $\Pset$ % = \{0, 1, 12, 13, \ldots, 12\dots n\}$ is
   is the set of indices of all square-free cyclic polynomials,
@@
 Since the original polynomial is cyclic,
-  so is the reduced one, which is also square-free.
-All terms that involve no $x_k$
+  so is the final square-free polynomial.
+Terms involving no $x_k$
   are collected to serve as the coefficient before $C_0(\vx) \equiv 1$.
@@
 \refthm{sqrfree}
-  shows that any cyclic polynomial
-  can be expanded
-  as a combination of the square-free ones,
-  which serve as a basis.
+  shows that any cyclic polynomial can be expanded
+  as a combination of the square-free ones.
 Below we show that at the onset and bifurcation points,
@@
   linearly connected by $\NB$ homogeneous equations.
-The matrix of the connecting coefficients must have a zero determinant,
+The matrix of the connecting coefficients then must have a zero determinant,
   which yields the desired polynomial.
@@
 is a cyclic polynomial:
+%
 %
@@
 \end{equation}
-
-Now, for any $p$, $\Lambda(\vx) \, C_p(\vx)$
-  is also a cyclic polynomial,
-since the product of two cyclic polynomials is cyclic too.
-We can therefore expand it by \refthm{sqrfree} as
-\begin{equation}
-  \Lambda(\vx) \, C_p(\vx) = \sum_{q \in \Bset} T_{pq}(R) \, C_q(\vx),
+%
+%
+Since $C_p(\vx)$ is also cyclic,
+  so is the product $\Lambda(\vx) \, C_p(\vx)$,
+  which can be expanded by \refthm{sqrfree} as
+\begin{equation}
+  \Lambda(\vx) \, C_p(\vx) = \sum_{q \in \Pset} T_{pq}(R) \, C_q(\vx),
 \label{eq:xcp0}
@@
 where $T_{pq}(R)$ is a polynomial of $R$,
-and $p, q \in \Bset$.
+and $p, q \in \Pset$.
 
@@
 \begin{equation}
-  \lambda \, C_p(\vx) = \sum_{q \in \Bset} T_{pq}(R) \, C_q(\vx),
+  \lambda \, C_p(\vx) = \sum_{q \in \Pset} T_{pq}(R) \, C_q(\vx),
 \label{eq:xcp}
@@
 \begin{equation}
-  A_n\RX \equiv \big| \lambda \, \vct I - \vct T(R) \big| = 0.
+  A_n\Rlam \equiv \big| \lambda \, \vct I - \vct T(R) \big| = 0.
 \label{eq:xr}
 \end{equation}
-Here, $A_n\RX$ is a polynomial of $R$ and $\lambda$,
+Here, $A_n\Rlam$ is a polynomial of $R$ and $\lambda$,
   and the subscript $n$ is attached such that
-  it can be used later with $A_d\RX$ of divisors $d$ of $n$.
+  it can be used later with $A_d\Rlam$ of divisors $d$ of $n$.
 \refeq{xr} is a necessary condition
@@
   the square-free cyclic polynomials $C_p(\vx)$
-  are linear related by \refeq{xcp}, with
-  $\lambda$ being $+1$ and $-1$, respectively,
-  and $T_{pq}(R)$ are the coefficients
-  from the square-free reduction of $\Lambda(\vx) \, C_p(\vx)$
-  with $\Lambda(\vx)$ specified by \refeq{logder}.
-  Thus, $R$ at the two points are the roots of the
-  polynomials $A_n(R, \lambda = \pm1)$
-  obtained from the characteristic equation \refeq{xr}.
+  of the orbit points $\vx = \{x_k\}$
+  are linear related by % \refeq{xcp},
+  $\lambda \, C_p(\vx) = \sum_{q \in \Pset} T_{pq}(R) \, C_q(\vx)$,
+  with $\lambda$ being $+1$ and $-1$, respectively,
+  and $T_{pq}(R)$ being the coefficients
+  from the square-free reduction of the cyclic polynomial
+  $C_p(\vx) \, \prod_k f'(x_k)$. %[\refeq{logder}].
+  Thus, the fixed point of $f^n$
+  is marginally stable when $R$ satisfies
+  characteristic equation $\big| \lambda \, \vct I - \vct T(R) \big| = 0$.
   \label{thm:main}
@@
 \begin{remark}
-%\begin{remark}[1]
-  For complex $R$ and $\vx$,
-  $\lambda$ should be generalized from $\pm1$
-  to any $\lambda = \exp(i\theta)$,
-  where $\theta \in [0, 2\pi]$,
-  the algorithm still applies.
-  By increasing $\theta$ from 0 to $2\pi$,
-  we can trace a two-dimensional region of a complex $R$
-  for stable cycles.
-  These regions are bulbs in the inverted Mandelbrot set,
-  %(however, we need the replacement
-  %$x_k \rightarrow -z_k$
-  %and
-  %$R \rightarrow -c$)
+  Generally, the algorithm can trace a contour of marginal stability of $R$
+  in the complex plane
+  for complex cycles (i.e., complex $R$ and $\vx$)
+  if $\lambda$ is set to $\exp(i\theta)$ with $\theta \in [0, 2\pi]$.
+  The region enclosed by the contour corresponds to a bulb in the inverted Mandelbrot set
+  (the correspondence follows from the transformation $z_k = -x_k, c = -R$, which
+  reduces \refeq{logmaps} to the quadratic map $z_{k+1} = c + {z_k}^2$
+  used in the Mandelbrot set),
   see ref. \cite{stephenson}. % and \reffig{logbulb}.
-
-  Further, with $\lambda = 0$,
-  the algorithm determines the superstable point,
-  at which the deviation from a cycle point vanishes
+\end{remark}
+
+\begin{remark}
+  With $\lambda = 0$,
+  the algorithm yields the polynomial of the superstable point,
+  at which the initial deviation from a cycle point vanishes
   to the linear order after $n$ iterations of $f$.
@@
 
-We illustrate the above algorithm by cases of small $n$.
-%
-It is still helpful to have a mathematical software verify some steps
+We illustrate the above algorithm by several small-$n$ cases.
+%
+It is still helpful to have a mathematical software
+  in order to verify certain steps
   (e.g., in computing the determinants and their factorization).
@@
 For $n = 1$, we have two square-free cyclic polynomials
-  $C_0(\vx) = 1$ and $C_1(\vx) = x_1$;
-  and $\Lambda(\vx) = -2 \, x_1$
-\big[we shall drop ``$(\vx)$'' below for convenience\big].
-Thus $\Lambda \, C_0 = -2 \, x_1 = -2 \, C_1$,
+\big[omitting ``$(\vx)$''\big]
+  $C_0 = 1$ and $C_1 = x_1$;
+  and $\Lambda = -2 \, x_1$
+Thus, $\Lambda \, C_0 = -2 \, C_1$,
 $\Lambda \, C_1 = -2 \, x_1^2 = -2 \, R + 2 x_1 = -2 \, R \, C_0 + 2 \, C_1$,
@@
 \]
-and \refeq{xr} reads
+and the characteristic equation (\ref{eq:xr}) reads
 \begin{equation}
@@
   2 R         & \lambda - 2
-  \end{array} \right| = -4R - 2\lambda + \lambda^2,
+  \end{array} \right| = -4R - 2\lambda + \lambda^2.
   \tag{\ref{eq:xr}-1}
@@
 \end{equation}
-which is just the equation for a fixed point.
-The fixed point begins at $\lambda = +1$ or $R_a = -1/4$,
-  and becomes impossible when $\lambda = -1$, or $R_b = 3/4$.
-
-For $n = 2$, the cyclic variables are
+Thus, the fixed point begins at $R_a = -1/4$ ($\lambda = +1$),
+  and becomes unstable at $R_b = 3/4$ ($\lambda = -1$).
+
+For $n = 2$, the cyclic polynomials
+  are
 $C_0 = 1$,
 $C_1 = x_1 + x_2$,
-$C_{12} = x_1 x_2$,
+$C_{12} = x_1 x_2$;
 and $\Lambda = 4 x_1 x_2$.
 Thus,
-$\Lambda \, C_0 = 4 C_{12}$,
+$\Lambda \, C_0 = 4 \, C_{12}$,
 $\Lambda \, C_1 = 4 \, {x_1}^2 \, x_2 + 4 \, x_1 \, {x_2}^2
@@
 \begin{align}
-0 &=
-  \left| \begin{array}{ccc}
-  \lambda     & 0               & -4 \\
-  8R          & \lambda-4(R+1)  & 0 \\
-  -4R^2       & 4R              & \lambda-4
-  \end{array} \right| \nonumber\\
-  &= (4R - 4 + \lambda) [(4 R-\lambda)^2 - 4 \lambda].
+0 &= (4R - 4 + \lambda) [(4 R-\lambda)^2 - 4 \lambda].
   \tag{\ref{eq:xr}-2}
@@
 %
-We only use the first factor
-(the choice will be explained later, same for the following cases).
-%
-Setting it to zero yields $R = 1 - \lambda/4$;
+Setting the first factor (which is responsible for the 2-cycle,
+  while the second factor is for unstable fixed points, see later)
+  to zero yields $R = 1 - \lambda/4$;
 $\lambda = +1$ gives the onset value $R_a = 3/4$ ($r_a = 3$)
@@
 %
-Note that the onset point of the only 2-cycle
-  is located at $R = 3/4$,
-  where the fixed point bifurcates \cite{strogatz}
-  \big[compare \reffigs{cobweb}(a) and (b)\big].
+%Note that the onset point of the 2-cycle
+%  is located at $R = 3/4$,
+%  where the fixed point bifurcates \cite{strogatz}.
+%  \big[compare \reffigs{cobweb}(a) and (b)\big].
 
 For $n = 3$ \cite{saha, bechhoefer, gordon, burm, zhang},
-we have
+%we have
+the cyclic polynomials are
 $C_0 = 1$,
@@
 and
-$\Lambda = -8 x_1 x_2 x_3$.
+$\Lambda = -8 \, C_{123}$.
 %
@@
 %
-\begin{align}
+\begin{align*}
 \lambda
@@
 \end{array} \right),
-\end{align}
+\end{align*}
 %
@@
   0
-&=\left| \begin{array}{cccc}
- \lambda      & 0                 & 0               & 8 \\
- 24 R         & \lambda - 8(R+1)  & 8R              & 0 \\
- -24 R^2      & 8R(R+2)           & \lambda-8(R+1)  & 0 \\
- 8R^3         & -8R^2             & 8R              & \lambda-8
-  \end{array} \right| \nonumber \\
-&= -\big[
+= -\big[
   64R^3 - 128 R^2 - 8 (\lambda - 8) R - (\lambda -8)^2
@@
 
-For $n = 4$ \cite{stephenson}, the cyclic variables are
-$C_0 = 1$,
-$C_1 = x_1 + x_2 + x_3 + x_4$,
-$C_{12} = x_1 x_2 + x_2 x_3 + x_3 x_4 + x_4 x_1$,
-$C_{13} = x_1 x_3 + x_2 x_4$,
-$C_{123} = x_1 x_2 x_3 + x_2 x_3 x_4 + x_3 x_4 x_1 + x_4 x_1 x_2$
-$C_{1234} = x_1 x_2 x_3 x_4$,
-and
-$\Lambda = 16 x_1 x_2 x_3 x_4$.
+For $n = 4$ \cite{stephenson, bailey1, kk1, bailey2, lewis},
+we have six cyclic polynomials, and
+%$C_0 = 1$,
+%$C_1 = x_1 + \cdots + x_4$,
+%$C_{12} = x_1 x_2 + \cdots + x_4 x_1$,
+%$C_{13} = x_1 x_3 + x_2 x_4$,
+%$C_{123} = x_1 x_2 x_3 + \cdots + x_4 x_1 x_2$,
+%$C_{1234} = x_1 x_2 x_3 x_4$,
+%and
+%$\Lambda = 16 \, C_{1234}$.
 %
@@
 \begin{align}
-0 & = \left|
-\begin{array}{cccccc}
- \lambda  & 0               & 0                 & 0     & 0     & -16 \\
- 64 R     & \lambda-16(R+1) & 16 R              & 0     & -16R  & 0 \\
- -64 R^2  & 16R(R+2)        & \lambda-16(R^2+1) & -32 R & 16R   & 0 \\
- -32 R^2  & 16R(R+1)        & -16R              & \lambda-16(R^2+1)  & 0 & 0 \\
- 64 R^3   & -16R^2(R+3)     & 16R(R+2)        & 32 R (R+1)       & \lambda-16(R+1) & 0 \\
- -16R^4   & 16R^3           & - 16R^2           & -16R^2            & 16R & \lambda - 16
-\end{array}
-\right | \nonumber  \\
+0
+%& = \left|
+%\begin{array}{cccccc}
+% \lambda  & 0               & 0                 & 0     & 0     & -16 \\
+% 64 R     & \lambda-16(R+1) & 16 R              & 0     & -16R  & 0 \\
+% -64 R^2  & 16R(R+2)        & \lambda-16(R^2+1) & -32 R & 16R   & 0 \\
+% -32 R^2  & 16R(R+1)        & -16R              & \lambda-16(R^2+1)  & 0 & 0 \\
+% 64 R^3   & -16R^2(R+3)     & 16R(R+2)        & 32 R (R+1)       & \lambda-16(R+1) & 0 \\
+% -16R^4   & 16R^3           & - 16R^2           & -16R^2            & 16R & \lambda - 16
+%\end{array}
+%\right | \nonumber  \\
 & =
@@
 %
-As a verification, the polynomials are
-alternatively derived in the Appendix.
-
-\begin{table}[h]\footnotesize
-  %\caption{
-  \tbl{
-  Characteristic polynomials $A_n\RX$ of
-  the fixed points of $f^n$ of
-  the simplified logistic map \refeq{logmaps}.
-  }
-%\begin{center}
-{
-\begin{tabular}{lc}
-\hline
-  $n$
-& $A_n(R, \; \lambda = 2^n X)
-  \big\slash
-   2^{n \NB(n)}$ $^\dagger$
-\\
-\hline
-1
-&
-$X^2-X-R$
-\\
-2
-&
-  $
-  \big[ \cancel{(R-X)^2 - X}\big]
-  (R + X - 1)
-  $
-\\
-3
-&
-$\begin{aligned}
-\big[\cancel{
-  X^2-(3R+1)X-R^3
-}\big]
-  \big[
-  (X-1)^2
- + X R
- - R(R-1)^2
-  \big]
-\end{aligned}$
-\\
-4
-&
-$\begin{aligned}
-\big[ \cancel{
-  (R-1)^2 - X
-} \big]
-\big[ \cancel{
-(R^2+X)^2 -(2R+1)^2 X
-} \big]
-\big[
-  R^6-3 R^5+(X+3) (R^4 - R^3) -(X+2)(X-1) R^2 - (X-1)^3
-\big]
-\end{aligned}$
-\\
-5
-&
-\begin{minipage}{.97\linewidth}
-\vspace*{2mm}
-$\begin{aligned}
-&\big[ \cancel{
-  X^2-5 X (R^2+R)-X - R^5
-  %R^5+5 X (R^2+R)-X^2+X
-} \big]
-\big[
--R^{15}+8 R^{14}-28 R^{13}+(X+60) R^{12}-(7 X+94) R^{11}
-+(3 X^2 +20 X
-\\
-+&116) R^{10}
--(11 X^2+33 X+114) R^9
-+2(3 X^2+20 X+47) R^8
--(2 X^3-20 X^2+37 X+69) R^7 \\
-+&(3 X-11)(3X^2-3X+44) R^6
-%-(3 X^4+17 X^3-53 X^2+7 X+26) R^5
--(X-1) (3 X^3+20 X^2-33 X-26) R^5
-+(X-1)^2 (3 X^2+27 X+14) R^4 \\
-+&(X-1)^3 (6 X+5) R^3
-+(X-1)^4 (X+2) R^2+(X-1)^5 R+(X-1)^6
-\big]
-\end{aligned}$
-\vspace{1mm}
-\end{minipage}
-\\
-6
-&
-$\begin{aligned}
-&\big[\cancel {
-  (R-1)^3 + X
-}\big]
-\big[\cancel {
- (R^3 - X)^2 - (3R+1)^2 X
-}\big]
-\big[\cancel {
-\big(R(R-1)^2-1-X\big)^2-(R-2)^2 X
-}\big]
-\big[
-R^{27}-13 R^{26}+78 R^{25}\\
-&+(X-293) R^{24}
-+\dots
-+(X-1)^6 (X^2+10 X+3) R^3
-+(X-1)^7 (X+1) R^2-(X-1)^8 R+(X-1)^9
-\big]
-\end{aligned}$
-\\
-7
-&
-\begin{minipage}{.97\linewidth}
-\vspace{1mm}
-$\begin{aligned}
-&\big[\cancel {
-  -R^7 - 7 X R (R+1)^2 + X^2 - X
-}\big]
-\big[
--R^{63}+32 R^{62}-496 R^{61}
-+4976 R^{60} + (X - 36440) R^{59}
-- (30X
-\\
--&208336) R^{58}
-+\dots
-+(X-1)^{15} (X^2+14 X+5) R^3
-+2(X-1)^{16} (X+1) R^2
-+(X-1)^{17} R
-+(X-1)^{18}
-\big]
-\end{aligned}$
-\end{minipage}
-\\
-\vdots & \vdots
-\\
-\hline
-\multicolumn{2}{p{\textwidth}}{
-$^\dagger$
-$\NB(n) = (1/n) \sum_{d|n} \varphi(n/d) 2^d$ [\refeq{necklace}]
-is the number of the square-free cyclic polynomials.
-%
-The change of variable $\lambda \rightarrow X$ and
-  the division by $2^{n \NB(n)}$ make the polynomials more compact.
-%
-The irrelevant factors from shorter cycles
-(see \refsec{primfac}) are struck out.
-The polynomials of $r$ for the original logistic map \refeq{logmap}
-can be obtained by $R\rightarrow r(r-2)/4$.
-} \\
-\hline
-\end{tabular}
-\label{tab:Anlog}
-}
-%\end{center}
-\end{table}
+A simple elementary derivation of the 4-cycle is
+presented in the Appendix.
 
@@
 which was used to compute the polynomials for $n$ up to 13.
-The polynomials for a general $\lambda$
-and those at $\lambda = \pm1$ (onset and bifurcation points) are listed
-in \reftab{Anlog} and \reftab{Pnlog}, respectively, for some small $n$.
-%
-For complex $R$, $\lambda$, and $\vx$,
-the method can also compute the region of stability for $R$
-  (i.e., the inverted Mandelbrot set),
-with $\lambda$ being $\exp(i\theta)$ \big[$\theta \in (0, 2\pi)$\big]
-  instead of $\pm1$.
-%the results are shown in \reffig{logbulb}
-%for $n$ up to $8$.
-%
-For polynomials of larger $n$, see the website in \refsec{end}.
+%
+For polynomials of larger $n$ are saved in in the website in \refsec{end}.
+%
 The representative $r$ values are listed in \reftab{rval}.
+%
 
@@
 
-The factors ignored in \refsec{examples}
-  come from shorter $d$-cycles whose periods $d$ divide $n$,
-%
-  because $A_n\RX$,
-  from the characteristic equation \refeq{xr},
-  is derived for all fixed points of $f^n$,
-  and thus encompasses the shorter cycles as well.
-%
-We filter the contributions from the shorter cycles by the following theorem.
+The polynomial $A_n\Rlam$
+  of the characteristic equation \refeq{xr}
+  is derived for the fixed points of $f^n$,
+  and thus encompasses cycles of shorter periods $d$ ($d|n$) as well.
+%
+We can remove the contributions from the shorter cycles by the following theorem.
 
 \begin{theorem}
-  The minimal polynomial $P_n\RX$ of all $n$-cycles
-  is a factor of $A_n\RX$ [defined in \refeq{xr}],
+  The minimal polynomial $P_n\Rlam$ of all $n$-cycles
+  is a factor of $A_n\Rlam$ [defined in \refeq{xr}],
   and can be computed as
   \begin{equation}
-    P_n\RX
-    = \prod_{cd = n} B_{d,c}\RX^{\mu(c)},
+    P_n\Rlam
+    = \prod_{cd = n} B_{d,c}\Rlam^{\mu(c)},
   \label{eq:primfac}
@@
 where
-  $B_{d, c}\RX \equiv \prod_{k=1}^c A_{d}(R, e^{2k\pi i/c} \lambda^{1/c})$,
+  $B_{d, c}\Rlam \equiv \prod_{k=1}^c A_{d}(R, e^{2k\pi i/c} \lambda^{1/c})$,
   $\lambda^{1/c}$ is a complex $c$th root of $\lambda$,
@@
 \begin{remark}
-$B_{d,c}\RX$ is a polynomial of $\lambda$.
+$B_{d,c}\Rlam$ is a polynomial of $\lambda$.
 Despite the argument $\lambda^{1/c}$,
@@
   for it is invariant under $\lambda \rightarrow e^{2\pi i} \lambda$;
-and $\deg_\lambda B_{d,c}\RX = \deg_\lambda A_d\RX$.
-Particularly, $B_{n,1}\RX = A_n\RX$.
+and $\deg_\lambda B_{d,c}\Rlam = \deg_\lambda A_d\Rlam$.
+Particularly, $B_{n,1}\Rlam = A_n\Rlam$.
 \end{remark}
 
-%We will refer to $P_n\RX$ as the \emph{primitive factor} below.
+%We will refer to $P_n\Rlam$ as the \emph{primitive factor} below.
 
 Let us see some examples.
-%
+%%
 For $n = 1$,
-there is no irrelevant factor
-in \refeq{xr1} and
-$P_1\RX = B_{1,1}\RX = A_1\RX = \lambda^2 - 2\lambda - 4R$.
-
+%there is no irrelevant factor in \refeq{xr1} and
+$P_1\Rlam = B_{1,1}\Rlam = A_1\Rlam = \lambda^2 - 2\lambda - 4R$.
+%
+%
+%
 For $n = 2$, since
-$B_{1,2}\RX
+$B_{1,2}\Rlam
 =
@@
 %
-$P_2\RX = A_2\RX \, B_{1,2}\RX^{-1} = 4R - 4 + \lambda$.
-
-For $n = 3$,
-one can verify that
-$B_{1,3}\RX
-= \prod_{k=1}^3 A_1(R, e^{2k\pi i/3} \, \sqrt[3]{\lambda})
-=  \lambda^2 - 24 R \lambda - 8 \lambda - 64 R^3$.
-%
-So
-$P_3\RX = A_3\RX \, B_{1,3}\RX^{-1}
-= -\big[64 R^3- 128 R^2 -8(\lambda -8)R-(\lambda-8)^2\big]$.
-
+$P_2\Rlam = A_2\Rlam \, B_{1,2}\Rlam^{-1} = 4R - 4 + \lambda$.
+%
+%
 For $n = 4$,
@@
 can be written as
-$B_{2,2}\RX = \prod_{k=1}^2 A_2(R, e^{k \pi i} \sqrt{\lambda})$,
+$B_{2,2}\Rlam = \prod_{k=1}^2 A_2(R, e^{k \pi i} \sqrt{\lambda})$,
 and
 %
-$P_4\RX
-    = A_4\RX \, B_{2,2}\RX^{-1}
+$P_4\Rlam
+    = A_4\Rlam \, B_{2,2}\Rlam^{-1}
     = 4096 R^6-12288 R^5+ 256 (\lambda + 48) (R^4- R^3)
     -16(\lambda + 32)(\lambda - 16) R^2 - (\lambda-16)^3$.
-Note, $B_{1,4}\RX$ is unused for $\mu(4) = 0$.
-
-The irrelevant factors for $n$ up to 7 are listed in \reftab{Anlog}.
-
-\newcommand{\T}{{R_4}}
-
-\begin{table}[h]\footnotesize
-  %\caption{
-  \tbl{
-  Onset and bifurcation polynomials %$P_n(R, \pm1)$
-  of the $n$-cycles of the simplified logistic map \refeq{logmaps}.
-  }
-{
-\label{tab:Pnlog}
-\begin{tabular}{lcc}
-\hline
-  $n$
-& Onset $P_n(R, \; +1)$ $^{\dagger, \ddagger}$
-& Bifurcation $P_n(R, \; -1)$ $^\dagger$
-\\
-\hline
-1
-&
-$-\T-1$
-&
-$-\T+3$
-\\
-2
-&
-$-(\cancel{3-\T})$
-&
-$\T-5$
-\\
-3
-&
-$\begin{aligned}
--
-\big( \cancel{
-  \T^2-\T+7
-}\big)
-  (\T-7)
-\end{aligned}$
-&
-$\begin{aligned}
- - \T^3 + 8\T^2 - 18\T + 81
-\end{aligned}$
-\\
-4
-&
-$\begin{aligned}
-\big( \cancel{
-  \T - 5
-} \big)
-\big[ \cancel{
-  (\T+1)^2 + 4
-} \big]
-\big[
-  (\T-3)^3 - 108
-\big]
-\end{aligned}$
-
-&
-
-$
-\T^6-12 \T^5+47 \T^4-188 \T^3+527 \T^2+4913
-$
-\\
-5
-
-&
-
-\begin{minipage}{.48\linewidth}
-%\vspace{3mm}
-$\begin{aligned}
--
-&\big( \cancel{
-\T^4-\T^3+\T^2+9 \T+31
-} \big)
-\big(
-\T^{11}-31 \T^{10} \\
-+&416 \T^9 -3404 \T^8 +20548 \T^7-98258 \T^6 \\
-+&370146 \T^5 -1171676 \T^4 +3301996 \T^3\\
--&7507332 \T^2+15699857 \T-28629151
-\big)
-\end{aligned}$
-%\vspace{2mm}
-\end{minipage}
-
-&
-
-\begin{minipage}{.49\linewidth}
-\vspace{1mm}
-$\begin{aligned}
--&\T^{15}+32 \T^{14}-448 \T^{13}+3838 \T^{12}-24008 \T^{11}\\
-+&118147 \T^{10} -462764 \T^9+1519712 \T^8\\
--&4444924 \T^7 +11351480 \T^6 -26978787 \T^5\\
-+&58697100 \T^4 -88548768 \T^3+149426046 \T^2\\
--&313083144 \T +1291467969
-\end{aligned}$
-\vspace{1mm}
-\end{minipage}
-
-\\
-6
-
-&
-
-\begin{minipage}{.48\linewidth}
-%\vspace{1mm}
-$\begin{aligned}
-&\big( \cancel{
-\T^2-9 \T+21
-} \big)
-\big( \cancel{
-\T^2+3 \T+3
-} \big)
-\big( \cancel{
-\T^3-8\T^2} \\
-+&\cancel{18\T-81
-} \big)
-\big(
-\T^{20}-\dots+3063651608241
-\big)
-\end{aligned}$
-%\vspace{2mm}
-\end{minipage}
-
-&
-
-\begin{minipage}{.49\linewidth}
-%\vspace{3mm}
-$\begin{aligned}
-&\T^{27}-52 \T^{26}+1248 \T^{25}-18753 \T^{24}+\dots\\
-&-5098317006250000 \T-20711912837890625
-\end{aligned}$
-%\vspace{2mm}
-\end{minipage}
-
-\\
-7
-
-&
-
-\begin{minipage}{.48\linewidth}
-%\vspace{1mm}
-$\begin{aligned}
--
-&\big( \cancel{
-\T^6-\T^5+\T^4-\T^3
-%\T^3(\T^2+1)(\T-1)
- +15T^2+97 \T+127
-} \big) \\
-&\big(
-\T^{57}
--127\T^{56}
-+\dots+
-%581652040856250348581103942808504447
-58165204\dots8504447
-\big)
-\end{aligned}$
-%\vspace{2mm}
-\end{minipage}
-
-&
-
-\begin{minipage}{.49\linewidth}
-%\vspace{3mm}
-$\begin{aligned}
-&-\T^{63}+128 \T^{62}-7936 \T^{61}+318464 \T^{60}-\dots\\
-%&-24275883989858911295570196314376441888 T \\
-%&+97862157334118736160267353892330031361
-&-2427583\dots6441888 \T +9786215\dots0031361
-\end{aligned}$
-%\vspace{2mm}
-\end{minipage}
-
-\\
-\vdots & \vdots & \vdots
-\\
-13
-&
-
-\begin{minipage}{.48\linewidth}
-%\vspace{1mm}
-$\begin{aligned}
--&\big(\cancel{
-\T^{12}-\T^{11}+\T^{10}
-%-\T^9+\T^8-\T^7+\T^6+25 \T^5+703 \T^4+5121 \T^3+14847 \T^2
--\dots
-+18433 \T+8191
-}\big) \\
-\big(
-&\T^{4083}
- - 8191\T^{4082}
-+ 33529856 \T^{4081}
-- \dots \\
--&30826655683291995
-\dots
-27828275886475354111
-\big)
-\end{aligned}$
-%\vspace{2mm}
-\end{minipage}
-
-&
-
-\begin{minipage}{.49\linewidth}
-%\vspace{1mm}
-$\begin{aligned}
--&\T^{4095} + 8192 \T^{4094} -33538048 \T^{4093} \\
-+&\dots
--7361199006999 % 0439512081857
-\dots
-96207964555264\T
-\\
-+&29448390363448812
-%0567620
-\dots
-%1182
-352154556569141249
-\end{aligned}$
-%\vspace{2mm}
-\end{minipage}
-
-\\
-\hline
-\multicolumn{3}{p{\textwidth}}{
-$^\dagger$ $\T = 4R$.
-The polynomials of $r$ for the original logistic map \refeq{logmap}
-can be obtained by $\T\rightarrow r(r-2)$.
-} \\
-\multicolumn{3}{p{\textwidth}}{
-$^\ddagger$
-Factors for the $n$-cycles born out of shorter cycles (see \refsec{origfac})
-are struck out.
-} \\
-\hline
-\end{tabular}
-}
-\end{table}
-
-%\begin{figure}[h]
-%  \begin{minipage}{\linewidth}
-%    \begin{center}
-%        \includegraphics[angle=-90, width=.67\linewidth]{logbulb.pdf}
-%    \end{center}
-%  \end{minipage}%
-%  \caption{
-%  \label{fig:logbulb}
-%  Stable regions of the $n$-cycles of the simplified logistic map \refeq{logmaps}
-%  with a complex $R$;
-%  obtained from $P_n(R, e^{i\theta}) = 0$ with $\theta \in [0, 2\pi]$,
-%  cf. Fig. 3 in \cite{stephenson}.
-%}
-%\end{figure}
+Note, $B_{1,4}\Rlam$ is unused for $\mu(4) = 0$.
 
@@
 For $n \ge 4$,
-  $P_n\RX$ is readily recognized as
+  $P_n\Rlam$ is readily recognized as
   the factor
-  of $A_n\RX$
-  with the highest degree in $R$,
-  see \reftab{Anlog} and \refsec{degR}.
+  of $A_n\Rlam$
+  with the highest degree in $R$.
+  %see \reftab{Anlog} and \refsec{degR}.
 It can be, however, problematic,
@@
    instead of a general $\lambda$,
-   for $P_n(R, 1)$ itself can be further factorized,
-  see \reftab{Pnlog}.
+   for $P_n(R, 1)$ itself can be further factorized.
 %
@@
 To show \refthm{primfac}, we first find the degrees in $\lambda$ of
-  $A_n\RX$ (\refthm{necklace}) and $P_n\RX$ (\refthm{lyndon}).
+  $A_n\Rlam$ (\refthm{necklace}) and $P_n\Rlam$ (\refthm{lyndon}).
 By comparing the degrees,
-  we then show that each $P_d\RX$ with ($d|n$),
+  we then show that each $P_d\Rlam$ with ($d|n$),
   after some transformation,
-  contributes one polynomial factor to $A_n\RX$
+  contributes one polynomial factor to $A_n\Rlam$
   (\refthm{prod}),
@@
   between the square-free cyclic polynomials
-  and the binary necklaces (defined below).
-The task is then to count the latter.
-
+  and the binary necklaces.
+%
 A binary necklace
@@
 %
-The period of a necklace, or a binary string,
-  is the length of the shortest non-repeating sub-sequence,
-  e.g., the periods of $1111$, $0101$ and $0001$
-        are 1, 2, and 4, respectively.
-%
-Obviously, the period $m$ divides $n$;
-  and a period-$m$ necklace
-  encompasses $m$ binary strings
-  differed by circular shifts,
-  e.g., $0101$ represents
-  both $0101$ and $1010$.
-
-\begin{table}[h]\footnotesize
-%\caption{
-\tbl{
-Two ways of counting the $N(4) = 6$ necklaces for $n = 4$.
-}
-%\begin{center}
-{
-%\begin{tabularx}{\textwidth}{c | c  c | c | c | c | c | c }
-\begin{tabular}{c | c  c | c | c | c | c | c }
-\hline
-        & \multicolumn{2}{c|}{$m = 1$}
-        & $m = 2$
-        & $m = 4$   & $2^d$ & $\varphi(n/d)$ & $\varphi(n/d) 2^d$\\
-\hline
-$d = 1$ & \hspace{1mm} $\mathbf{0}_{\times4}$ \hspace{1mm}
-        & \hspace{1mm} $\mathbf{1}_{\times4}$ \hspace{1mm} & & & $2 = 2$ & $2$ & 4 \\
-\hline
-$d = 2$ & $\mathbf{00}_{\times2}$ & $\mathbf{11}_{\times2}$
-        & \hspace{1mm} $\mathbf{10}_{\times2} (01_{\times2})$
-          \hspace{1mm} & & $2 + 2 =4$ & $1$ & 4 \\
-\hline
-\multirow{3}{*}{$d = 4$}
-      & & & & \hspace{1mm} $\mathbf{1000} (0100, 0010, 0001)$
-              \hspace{1mm} & $2 + 2 + 12$& \\
-      & $\mathbf{0000}$ & $\mathbf{1111}$ & $\mathbf{1010} (0101)$
-            & $\mathbf{1100} (1001, 0110, 0011)$ & $=16$ & $1$ & 16 \\
-      & & & &   $\mathbf{1110} (1101, 1011, 0111)$ & &  \\
-\hline
-$m \sum_{m|d, d|n} \varphi(\frac{n}{d})$
-      & \multicolumn{2}{c|}{$1\cdot(2+1+1) = 4$}
-      & $2\cdot(1+1) = 4$ & $4\cdot1 = 4$ &  \multicolumn{2}{c|}{} &  $\downarrow$\\
-\hline
-$N(n)\cdot n$ & \multicolumn{2}{c|}{$2 \cdot 4$} & $1 \cdot 4$ & $3 \cdot 4$ &
-  \multicolumn{2}{c|}{$\rightarrow$} & $6\cdot4 = 24$ \\
-\hline
-\multicolumn{8}{p{\linewidth}}{
-  Bold strings are necklaces; others are their cyclic versions.
-}
-\\
-\multicolumn{8}{p{\linewidth}}{
-The subscript of a binary string means the number of repeats;
-e.g.,
-$\mathbf{0}_{\times4}$ means $\mathbf{0}$ repeated four times, or $\mathbf{0000}$;
-$\mathbf{10}_{\times2}$ means $\mathbf{10}$ repeated twice, or $\mathbf{1010}$, etc.
-}
-\\
-\hline
-\end{tabular}
-%\end{tabularx}
-%\end{center}
-\label{tab:countnecklace}
-}
-\end{table}
-
-To compute the number of the binary necklaces $N(n)$,
-we construct a sum for the length-$n$ binary strings and count it in two ways.
-\reftab{countnecklace} shows the example for the $n=4$ case.
-%
-For each divisor $d$ of $n$, we collect
-  all length-$n$ binary strings
-  whose periods $m$ divide $d$.
-%
-The total is $2^d$,
-  for we have enumerated all binary strings whose periods divide $d$.
-%and each period-$m$ necklace contributes $m$ cyclic versions.
-%
-We then weight them by the Euler's totient function $\varphi(n/d)$.
-%
-Here, $\varphi(m)$ gives the number of integers from 1 to $m$
-  that are coprime to $m$,
-  e.g.,
-  $\varphi(1) = 1$,
-  $\varphi(3) = 2$ for 1 and 2,
-  $\varphi(6) = 2$ for 1 and 5.
-We repeat the process over other divisors $d$ of $n$,
-  and the resulting sum is $\sum_{d|n} \varphi(n/d) 2^d$.
-%
-The process for a fixed $d$ is exemplified
-  by a row in \reftab{countnecklace}.
-
-%
-
-We can count the above sum in another way.
-We recall that a period-$m$ necklace always contributes
-  $m$ strings in the above process for a fixed $d$,
-  and it does so for all multiples $d$ of $m$.
-So the total weighted contribution by this necklace is
-\begin{equation}
-m \sum_{m|d, d|n} \varphi(n/d) =
- m \sum_{\frac{n}{d}|\frac{n}{m}} \varphi(n/d) = m \,  \frac{n}{m}  = n,
-\label{eq:mphind}
-\end{equation}
-where we have used the identity $\sum_{d'|m'} \varphi(d') = m'$,
-with $d' = n/d$ and $m' = n/m$.
-%
-Summing over the necklaces yields $N(n) \, n$. Thus,
-$N(n) = (1/n) \sum_{d|n} \varphi(n/d) 2^d$.
-The process for a fixed necklace is exemplified
-  by a column in \reftab{countnecklace}.
-%
-
-Back to our problem, there is
-  a correspondence between the binary necklaces
-  and the square-free cyclic polynomials.
-For a square-free cyclic polynomial,
-  we construct a binary string according to its generator:
-if it contains $x_k$, the $k$th character from the left is 1,
+If the generator of the cyclic polynomial contains $x_k$,
+  the $k$th character from the left of the necklace is 1,
   otherwise 0.
-The resulting string corresponds to a unique necklace;
-  the alternative generators give
-  the circularly-shifted binary strings.
-The mapping is reversible, or one-to-one.
 For example, if $n = 3$,
@@
   and $C_{123} = x_1 x_2 x_3$ (generator: $x_1 x_2 x_3$), respectively.
-%\reftab{sqrfreepoly} shows a few more examples.
-%
 Thus,
@@
 \begin{theorem}
-The number $\NB(n)$ of the square-free cyclic polynomials $C_p(\vx)$ ($p \in \Bset$)
-  formed by $\vx = \{x_1, \ldots, x_n\}$ is
-\begin{equation}
-  \NB(n) = N(n) = (1/n) \sum_{d|n} \varphi(n/d) 2^{\,d},
+The number $\NB(n)$ of the square-free cyclic polynomials $C_p(\vx)$
+  formed by the orbit points $\vx = \{x_1, \ldots, x_n\}$,
+  which is also $\deg_\lambda A_n\Rlam$, is given by
+\begin{equation}
+  \deg_\lambda A_n\Rlam = \NB(n) = N(n) = (1/n) \textstyle\sum_{d|n} \varphi(n/d) 2^{\,d}.
 \label{eq:necklace}
@@
 %
-which is also equal to $\deg_\lambda A_n\RX$.
 \label{thm:necklace}
@@
 %
-$N(n)$ = 2, 3, 4, 6, 8, 14, 20, 36, 60, 108, 188, 352, 632, \ldots,
+Here, $\varphi(m)$ is Euler's totient function,
+which gives the number of integers from 1 to $m$
+  that are coprime to $m$,
+  e.g.,
+  $\varphi(1) = 1$,
+  $\varphi(3) = 2$ for 1 and 2,
+  $\varphi(6) = 2$ for 1 and 5.
+The first few values of $N_\Pset(n)$ are 2, 3, 4, 6, 8, 14, 20, 36, 60, 108, 188, 352, 632, \ldots,
   starting from $n = 1$.
@@
 \begin{theorem}
-The degree in $\lambda$ of the minimal polynomial $P_n\RX$ of all $n$-cycles
+The degree in $\lambda$ of the minimal polynomial $P_n\Rlam$ of all $n$-cycles
   is equal to the number of the $n$-cycles,
@@
 \begin{equation}
-  \deg_\lambda P_n\RX = L(n) = (1/n)\sum_{d | n} \mu(n/d) 2^{\,d}.
+  \deg_\lambda P_n\Rlam = L(n) = (1/n)\textstyle\sum_{d | n} \mu(n/d) 2^{\,d}.
 \label{eq:lyndon}
@@
 \end{theorem}
-
+%
+%
 \begin{proof}
-Except a few special values of $R$,
-the iterated map $f^{n}$ generally
-has $2^n$ distinct complex fixed points,
-%
-for otherwise $f^{n}(x) - x$ would have a repeated zero at any $R$,
-  but at $R=0$, $-x^{2^n} - x$ has no repeated root; a contradiction.
-
-Each fixed point can be assigned to
-  a point in a $d$-cycle, with $d$ being a divisor of $n$.
-%
-The assignment
-  is both complete (for a $d$-cycle point
-  must also be a fixed point of $f^n$)
-  and non-redundant (for there is no
-  repeated fixed point of $f^n$).
-%
-Since each of the $L(d)$ $d$-cycles
-  contributes $d$ fixed points,
-we have
-$2^n = \sum_{d\,|\,n} L(d) \, d$.
-%
-The M\"obius inversion yields $L(n) = (1/n) \sum_{d\,|\,n} \mu(n/d) 2^{\,d}$.
-This formula was known to several authors \cite{hao, hao2, lutzky}.
-
-We now define $\lambda_c$ as the value of $\Lambda(\vx)$,
-  evaluated at the cycle points
-  $\vx^{(c)} \equiv \{ {x_1}^{(c)}, \ldots, {x_n}^{(c)} \}$
-  of cycle $c$.
-Of course, $\lambda_c$ is a function of $R$.
-If we assume that $\lambda_c$ are distinct (see Remark \ref{remark:distinct} below),
-  then the minimal polynomial $P_n\RX$,
-  as a polynomial of $\lambda$,
+The number $L(n)$ of $n$-cycles is known \cite{hao, hao2, lutzky}.
+Denote by $\lambda_c$ the value $\Lambda(\vx^c)$
+  evaluated at the $c$th cycle points,
+  then the minimal polynomial $P_n\Rlam$
   takes the form of $\prod_c (\lambda - \lambda_c)$.
-Thus, the degree of $P_n\RX$ in $\lambda$
-  must be the same as the number of the $n$-cycles.
+Thus, $\deg_\lambda P_n\Rlam$ must be the same as $L(n)$.
 \end{proof}
-
-%\begin{remark}[1]
-\begin{remark}
-\label{remark:distinct}
-Although all trajectory points $\vx^{(c)}$ are distinct in
-  different cycles,
-the value $\lambda_c$ of the polynomial $\Lambda(\vx^{(c)})$
-  may happen to be the same.
-In this case,
-  we shall find another cyclic polynomial $Y(\vx)$ that
-  has different values in the two cycles
-  [$Y(\vx)$ exists for otherwise $\vx$ are the same in the two cycles],
-  use $\Lambda'(\vx) = \Lambda(\vx) + \epsilon Y(\vx)$
-  to list \refeqs{xcp0},
-  then take the limit
-  $\epsilon \rightarrow 0$.
-\end{remark}
-
-%\begin{remark}[2]
-\begin{remark}
-$L(n)$ is also the number of aperiodic (i.e., period equal to $n$)
-  necklaces of length $n$,
-  e.g., for $n = 4$,
-  out of the six necklaces, $0001$, $0011$, and $0111$ are aperiodic;
-  but $0000$, $1111$, and $0101$ are periodic.
-%
-Since a period-$d$ ($d|n$) necklace is just an aperiodic one
-  of length-$d$ repeated $n/d$ times,
-and each contributes $d$ binary strings,
-we can count the $2^n$ binary strings of length $n$ as
-  $2^n = \sum_{d|n} L(d) \, d$.
-The M\"obius inversion leads to the same result of \refeq{lyndon}.
-\end{remark}
-
-$L(n)$ =
+%
+%
+For the first few values, we have $L(n)$ =
 2, 1, 2, 3, 6, 9, 18, 30, 56, 99, 186, 335, 630, \ldots,
 starting from $n = 1$.
-
-Since the period $d$ of a length-$n$ necklace always divides $n$,
+%
+Incidentally, $L(n)$ is also the number of aperiodic necklaces of length $n$.
+  In the $n = 4$ case,
+  $0001$, $0011$, and $0111$ are aperiodic;
+  but $0000$, $1111$, and $0101$ are not
+  owing to the shorter periods 1, 2, and 2, respectively.
+%
+Since an $n$-necklace is either aperiodic or
+  a repeated aperiodic $d$-necklace (with $d|n$),
   we have
 \begin{equation}
-N(n) = \sum_{d|n} L(d).
+  N(n) = \textstyle\sum_{d|n} L(d).
 \label{eq:necklacelyndon}
@@
 %
-We can also show this by explicit computation:
-\begin{align*}
-\sum_{d | n} L(d)
-  &= \sum_{d | n} (1/d) \sum_{c |  d} \mu(d/c) 2^{\,c}
-   = (1/n) \sum_{c | n} 2^{\,c} \sum_{d'  |  (n/c)}
-        \mu\left(\frac{n/c}{d'}\right) d' \\
-  &= (1/n) \sum_{c \, | \, n} 2^{\,c} \, \varphi(n/c)
-  = N(n),
-\end{align*}
-where we have used $\varphi(m) = \sum_{d' | m} \mu(\frac{m}{d'}) \, d'$,
-which is the inversion of $m = \sum_{d' | m} \varphi(d')$,
-and \refeq{necklace}.
-%
-We will use \refeq{necklacelyndon} in proving the next theorem.
-
-\subsubsection{Relation between $P_n\RX$ and $A_n\RX$}
+
+\subsubsection{Relation between $P_n\Rlam$ and $A_n\Rlam$}
 
 \begin{theorem}
-The minimal polynomials $P_d\RX$ of all $d$-cycles
+The minimal polynomials $P_d\Rlam$ of all $d$-cycles
   of periods $d|n$
-and $A_n\RX$ [defined in \refeq{xr}] are related by
-  \begin{equation}
-    A_n\RX = \prod_{cd = n} Q_{d, c}\RX,
+and $A_n\Rlam$ [defined in \refeq{xr}] are related by
+  \begin{equation}
+    A_n\Rlam = \prod_{cd = n} Q_{d, c}\Rlam,
     \label{eq:prod}
@@
   where
-  $Q_{d,c}\RX = \prod_{k=1}^{c} P_d(R, e^{2 k \pi i/c} \lambda^{1/c})$
+  $Q_{d,c}\Rlam = \prod_{k=1}^{c} P_d(R, e^{2 k \pi i/c} \lambda^{1/c})$
   is a polynomial of degree $L(d)$ in $\lambda$
   representing contributions from $d$-cycles.
-%encompassed by $A_n\RX$.
+%encompassed by $A_n\Rlam$.
 \label{thm:prod}
@@
 \begin{proof}
-Since $A_n\RX$ represent all $d$-cycles with $d|n$,
+Since $A_n\Rlam$ represent all $d$-cycles with $d|n$,
 and each cycle holds a distinct $\lambda$,
-  $\deg_\lambda A_n\RX$
+  $\deg_\lambda A_n\Rlam$
   is at least $\sum_{d|n} L(d)$
@@
   $N(n)$ by \refeq{necklacelyndon}.
-Since $\deg_\lambda A_n\RX = N(n)$ by \refeq{necklace},
-  each $n$-cycle occurs exactly once in $A_n\RX$.
+Since $\deg_\lambda A_n\Rlam = N(n)$ by \refeq{necklace},
+  each $n$-cycle occurs exactly once in $A_n\Rlam$.
 
@@
 the radical $\lambda^{1/c}$ can be removed by the product
-$Q_{d,c}\RX
+$Q_{d,c}\Rlam
   \equiv \prod_{k=1}^c P_d(R, e^{2k\pi i/c} \, \lambda^{1/c}) = 0$.
 %
-Now $Q_{d,c}\RX$ is a polynomial of $\lambda$
+Now $Q_{d,c}\Rlam$ is a polynomial of $\lambda$
   for it is invariant under
@@
 And since
-  $\deg_\lambda Q_{d,c}\RX
-    = \deg_\lambda P_d\RX = L(d)$,
+  $\deg_\lambda Q_{d,c}\Rlam
+    = \deg_\lambda P_d\Rlam = L(d)$,
   it is also a polynomial
@@
 
-Therefore, the product $\prod_{cd=n} Q_{d,c}\RX$
-  can differ from $A_n\RX$ only by
+Therefore, the product $\prod_{cd=n} Q_{d,c}\Rlam$
+  can differ from $A_n\Rlam$ only by
   a multiple.
-Since $Q_{n,1}\RX = P_n\RX$,
+Since $Q_{n,1}\Rlam = P_n\Rlam$,
   and the coefficient of highest power of $\lambda$ is always
-  unity in $A_n\RX$ \big[see the definition \refeq{xr}\big],
+  unity in $A_n\Rlam$ \big[see the definition \refeq{xr}\big],
   we know by induction that the coefficients of the highest power of $\lambda$
-  in all $P_n\RX$ and $Q_{d,c}\RX$
+  in all $P_n\Rlam$ and $Q_{d,c}\Rlam$
   are also unities.
@@
 
-We can now prove \refthm{primfac} as a corollary of \refthm{prod},
+\refthm{primfac} is a corollary of \refthm{prod},
 \begin{align*}
- B_{n, m} \RX
+ B_{n, m} \Rlam
  & = \prod_{l = 1}^{m} A_n(R, e^{2l\pi i/m} \lambda^{1/m}) \\
@@
  & = \prod_{c | n} \prod_{k'=1}^{m c} P_{n/c}(R, e^{2k'\pi i/(m c)} \lambda^{1/(m c)})
-  = \prod_{c | n} Q_{n /c, m c}\RX.
+  = \prod_{c | n} Q_{n /c, m c}\Rlam.
 \end{align*}
-Taking the logarithm (formally) yields
-  $\log B_{n, m} = \sum_{d|n} \log Q_{d, m n/d}$,
-where $d = n/c$.
-The inversion is
-  $\log Q_{n, m} = \sum_{d|n} \mu(n/d) \log B_{d, m n/d}$,
-or
-\begin{equation}
-  Q_{n, m}\RX
-= \prod_{d|n} B_{d, m n/d}\RX^{\mu(n/d)},
+The M\"obious inversion yields
+\begin{equation}
+  Q_{n, m}\Rlam
+= \prod_{d|n} B_{d, m n/d}\Rlam^{\mu(n/d)},
 \tag{$\ref{eq:primfac}'$}
 \end{equation}
-which is reduced to \refeq{primfac} with $m = 1$
-for $Q_{n, 1}\RX = P_n\RX$.
+which is reduced to \refeq{primfac} with $m = 1$,
+for $Q_{n, 1}\Rlam = P_n\Rlam$.
 
@@
 
-\reftab{Pnlog} shows that
-the onset polynomial
+The onset polynomial
   $P_n(R, \lambda = 1)$ for the $n$-cycles
@@
 %
-This is because the intersection of an $n$-cycle
-  and a shorter $d$-cycle ($d|n$, $d < n$)
-  forces the two to share orbits
-  (this cannot happen if $d \centernot| n$,
-  for the orbits would be out of phase).
-%
-Consequently, upon the intersection,
-  $P_n\RX$ from the $n$-cycle
-  has to accommodate $P_d(R, \lambda')$ from the $d$-cycle,
-  with $\lambda'$ being a primitive $(n/d)\,$th root of $\lambda$.
-
-At the intersection,
-  the shorter $d$-cycle is branched or ``bifurcated''
-  by $(n/d)$-fold to the $n$-cycle.
+This is caused by the intersection of an $n$-cycle
+  and a shorter $d$-cycle ($d|n$, $d < n$),
+  which forces the two to share orbit.
+%
+One can show that this intersection happens only
+  at the onset of the $n$-cycle, where $\lambda = 1$,
+%
+  and the $d$-cycle branches out, or ``bifurcates'', $n/d$-fold
+  to become the $n$-cycle.
 %
@@
   where the fixed point \refeq{xr1}
-  bifurcates to
-  the 2-cycle \refeq{xr2}.
-%[recall the $\lambda = -1$ case in \refeq{xr1}
-%  and $\lambda = +1$ case in \req{xr2} in \refsec{examples}];
-The second bifurcation point at $R=5/4$ for $d = 2, n = 4$ is similar,
-  cf. \refsec{examples}.
-
-We will show below that such branching generally can only happen
-  at the onset of the $n$-cycle, where $\lambda = 1$.
-%
-Further, with a real $R$, only a two-fold branching is possible,
-  but a complex $R$ allows higher-fold branchings.
+  undergoes period-doubling and becomes the 2-cycle \refeq{xr2}.
+As a result, the polynomial $P_n(R, \lambda)$ from the $n$-cycle
+  has to accommodate $P_d(R, \lambda')$ from the $d$-cycle as a factor,
+  with $\lambda'$ being a primitive $(n/d)\,$th root of $\lambda = 1$.
 
@@
   we call it an \emph{original} cycle,
-  e.g., the 4-cycle at $R_a' = 5/4$
-  is born out of bifurcation, see \reffig{cobweb}(d),
-  but the other at $R_a = (3+\sqrt[3]{108})/4$
-  is original, see \reffig{cobweb}(e),
-  also the discussion after \refeq{xr4}.
-%
-Both types of cycles exist in $P_n(R, \lambda = +1)$,
-  as separate factors;
-and the factor responsible for the original cycles,
-  or the \emph{original factor} below,
-  is given by the following formula.
-
-\begin{theorem}
-  The original factor $S_n(R)$ of $P_n\RX$ at the onset is given by
+The two types of cycles exist
+  as separate factors of $P_n(R, \lambda = 1)$.
+One can then show that the factor $S_n(R)$ responsible for the original cycles
+  %or the \emph{original factor} below,
+  is given by
   \begin{equation}
@@
    $k$ from 1 to $c$ that are coprime to $c$.
-  \label{thm:origfac}
-\end{theorem}
-
-We illustrate \refthm{origfac} through a few examples
-  before giving a proof.
-%
-For $n = 1$,
-$S_1(R) = P_1(R, 1) = -4R - 1$
-as the denominator is unity.
-
-For $n = 2$,
-$P_2(R, 1) = 4R - 3$.
-But $P_1(R, -1) = -4R + 3$.
-So $S_2(R) = P_2(R, 1)/P_1(R, -1) = -1$.
-This means that there is no original 2-cycle
-  and the only 2-cycle comes from period doubling.
-
-For $n = 3$,
-$P_3(R, 1) = -(4R - 7)(16 R^2 - 4 R + 7)$,
-whose second factor is equal to
-$
-\big(-4R + \frac{1 - 3 \sqrt3 i}{2}\big)
-\big(-4R + \frac{1 + 3 \sqrt3 i}{2}\big)
-= \prod_{k=1,2} P_1(R, e^{2 k \pi i/3})$.
-%
-Thus $S_3(R) = -4R + 7$.
-
-For $n = 4$,
+
+Take the $n = 4$ case as an example, we have
+$\prod_{k=1,3} P_1(R, e^{k\pi i/2})
+%=(-4R-2i-1)(-4R+2i-1)
+=16R^2+8R+5$
+(for $c = 4$),
+$P_2(R, -1) = 4R - 5$
+(for $c = 2$),
+and
 $P_4(R, 1)
@@
   \bigr]$.
-But
-$P_2(R, -1) = 4R - 5$ (for $c = 2$)
-and
-$\prod_{k=1,3} P_1(R, e^{k\pi i/2})
-=(-4R-2i-1)(-4R+2i-1)
-=16R^2+8R+5$
-(for $c = 4$).
 Dividing $P_4(R, 1)$ by the two factors yields
 $S_4(R) = (4R-3)^3 - 108$,
-  whose only real root $R=(3+\sqrt[3]{108})/4$ corresponds to
+  whose only real root $R_a=(3+\sqrt[3]{108})/4$ corresponds to
   the onset of the original cycle.
-Note $R = 5/4$ is excluded from $S_4(R)$
+Note $R_a' = 5/4$ is excluded from $S_4(R)$
   as it comes from period-doubling the 2-cycle.
-
-%\section{\label{sec:degorigfac} Degree of the original factor}
-
-We now prove \refthm{origfac}.
-Suppose $n = c \,d$, we have, from \refeq{logmaps},
-\[
-  x_{l+1} - x_{d+l+1} = - (x_l + x_{d+l}) (x_l - x_{d+l}).
-\]
-We apply the equation to $l = 1, \ldots, m$, and the product is
-\[
-  x_{m+1} - x_{m + d+1} =
-  (-1)^{m} \left[ \, \prod_{l=1}^{m} (x_l + x_{d+l}) \right]
-    (x_1 - x_{d+1}).
-\]
-We now set $m$ to $0, d, \ldots, (c-1)\,d$ in this equation,
-  add them together, eliminate $x_1 - x_{d+1}$
-  (which is nonzero in a cycle), and
-\begin{equation}
-  \sum_{c' = 0}^{c-1}
-    (-1)^{c' d} \prod_{l=1}^{c' d} (x_l + x_{d+l})
-   = 0.
-\label{eq:stair}
-\end{equation}
-%
-Note \refeq{stair} holds for every divisor $c$ of $n$ ($c > 1$). We now have
+The two cycles are compared in \reffigs{cobweb}(d) and (e).
+
+%We now prove \refthm{origfac}.
+%Suppose $n = c \,d$, we have, from \refeq{logmaps},
+%\[
+%  x_{l+1} - x_{d+l+1} = - (x_l + x_{d+l}) (x_l - x_{d+l}).
+%\]
+%We apply the equation to $l = 1, \ldots, m$, and the product is
+%\[
+%  x_{m+1} - x_{m + d+1} =
+%  (-1)^{m} \left[ \, \prod_{l=1}^{m} (x_l + x_{d+l}) \right]
+%    (x_1 - x_{d+1}).
+%\]
+%We now set $m$ to $0, d, \ldots, (c-1)\,d$ in this equation,
+%  add them together, eliminate $x_1 - x_{d+1}$
+%  (which is nonzero in a cycle), and
+%\begin{equation}
+%  \sum_{c' = 0}^{c-1}
+%    (-1)^{c' d} \prod_{l=1}^{c' d} (x_l + x_{d+l})
+%   = 0.
+%\label{eq:stair}
+%\end{equation}
+%%
+%Note \refeq{stair} holds for every divisor $c$ of $n$ ($c > 1$). We now have
+%
+%
+%
+%\begin{theorem}
+%An $n$-cycle and a shorter $d$-cycle ($d|n$, $d< n$)
+%  intersect only at the onset of the $n$-cycle,
+%%
+%and $\prod_{k=1}^{d} f'(x_k) = (-2)^d x_1 \dots x_d$ is
+%a \emph{primitive} $(n/d)$th root of unity there.
+%\label{thm:cbifur}
+%\end{theorem}
+%
+%
+%\begin{proof}
+%At the intersection of the $n$- and $d$-cycles,
+%  $x_l$ repeats itself after $d$ steps, so
+%  $x_{d + l} = x_l$;
+%and \refeq{stair} becomes,
+%%
+%\begin{equation}
+%  1 + q + \dots + q^{c-1} = 0,
+%\label{eq:cbifur}
+%\end{equation}
+%%
+%where $q = (-2)^d \, x_1 \dots x_d$.
+%%
+%Multiplying \refeq{cbifur} by $q - 1$ yields
+%  $1 = q^c = (-2)^n \, x_1 \dots x_n$.
+%So the $n$-cycle is at its onset.
+%
+%
+%Further $q$ is a \emph{primitive} $c$th root of unity.
+%%
+%Suppose the contrary: $q = e^{2k\pi i/c}$ and $(k, c) = g >1$,
+%  then by $c_1 \equiv c/g$, $k_1 \equiv k/g$, we have
+%\begin{equation}
+%  q = e^{2k_1\pi i/ c_1}.
+%\label{eq:qd}
+%\end{equation}
+%Similar to \refeq{cbifur}, we can apply \refeq{stair} with $c \rightarrow g$ and $d \rightarrow d c_1$, and
+%\[
+%  1 + q_1 + \dots + {q_1}^{g-1} = 0,
+%\]
+%  where $q_1 = (-2)^{d c_1} \, x_1 \dots x_{dc_1} = q^{c_1}$.
+%But by \refeq{qd}, $q^{c_1} = e^{2 k_1\pi i} = 1$,
+%and $1 + q_1 + \dots + {q_1}^{g-1} = g > 0$; a contradiction.
+%%
+%\end{proof}
+%
+%
+%\begin{remark}
+%The only real $q$ is $q = -1$ for $c=2$, i.e., a period-doubling.
+%%
+%On the complex domain, however, we can have a $c$-fold branching with $c>2$,
+%  which corresponds to a contact points between ``bulbs''
+%  in the inverted Mandelbrot set.
+%\end{remark}
+%
+%By \refthm{cbifur}, $P_n\Rlam$ at the onset point
+%includes $P_d(R, e^{2 k \pi i/c} \lambda^{1/c})$ for every
+%  possible combination of $k$ and $c$, such that
+%  $(k, c) = 1$, $c|n$, and $c > 1$.
+%
+%Dividing the factors from $P_n\Rlam$ yields \refthm{origfac}.
+
+\subsection{\label{sec:degR}Degrees in $R$}
 
 \begin{theorem}
-An $n$-cycle and a shorter $d$-cycle ($d|n$, $d< n$)
-  intersect only at the onset of the $n$-cycle,
-%
-and $\prod_{k=1}^{d} f'(x_k) = (-2)^d x_1 \dots x_d$ is
-a \emph{primitive} $(n/d)$th root of unity there.
-\label{thm:cbifur}
-\end{theorem}
-
-\begin{proof}
-At the intersection of the $n$- and $d$-cycles,
-  $x_l$ repeats itself after $d$ steps, so
-  $x_{d + l} = x_l$;
-and \refeq{stair} becomes,
-%
-\begin{equation}
-  1 + q + \dots + q^{c-1} = 0,
-\label{eq:cbifur}
-\end{equation}
-%
-where $q = (-2)^d \, x_1 \dots x_d$.
-%
-Multiplying \refeq{cbifur} by $q - 1$ yields
-  $1 = q^c = (-2)^n \, x_1 \dots x_n$.
-So the $n$-cycle is at its onset.
-
-Further $q$ is a \emph{primitive} $c$th root of unity.
-%
-Suppose the contrary: $q = e^{2k\pi i/c}$ and $(k, c) = g >1$,
-  then by $c_1 \equiv c/g$, $k_1 \equiv k/g$, we have
-\begin{equation}
-  q = e^{2k_1\pi i/ c_1}.
-\label{eq:qd}
-\end{equation}
-Similar to \refeq{cbifur}, we can apply \refeq{stair} with $c \rightarrow g$ and $d \rightarrow d c_1$, and
-\[
-  1 + q_1 + \dots + {q_1}^{g-1} = 0,
-\]
-  where $q_1 = (-2)^{d c_1} \, x_1 \dots x_{dc_1} = q^{c_1}$.
-But by \refeq{qd}, $q^{c_1} = e^{2 k_1\pi i} = 1$,
-and $1 + q_1 + \dots + {q_1}^{g-1} = g > 0$; a contradiction.
-%
-\end{proof}
-
-\begin{remark}
-The only real $q$ is $q = -1$ for $c=2$, i.e., a period-doubling.
-%
-On the complex domain, however, we can have a $c$-fold branching with $c>2$,
-  which corresponds to a contact points between ``bulbs''
-  in the inverted Mandelbrot set, see \reffig{logbulb}.
-\end{remark}
-
-By \refthm{cbifur}, $P_n\RX$ at the onset point
-includes $P_d(R, e^{2 k \pi i/c} \lambda^{1/c})$ for every
-  possible combination of $k$ and $c$, such that
-  $(k, c) = 1$, $c|n$, and $c > 1$.
-%
-Dividing the factors from $P_n\RX$ yields \refthm{origfac}.
-
-\subsection{\label{sec:degR}Degrees in $R$}
-
-\begin{theorem}
-The degrees in $R$ of $A_n\RX$, $P_n\RX$ and $S_n(R)$ are
+The degrees in $R$ of $A_n\Rlam$, $P_n\Rlam$ and $S_n(R)$ are
 \begin{subequations}
 \begin{align}
-\deg_R A_n\RX &= \sum_{d|n} \varphi(n/d) 2^{d-1}, \\
-\deg_R P_n\RX &= \sum_{d|n} \mu(n/d) 2^{d-1} \equiv \beta(n), \\
-\deg S_n(R) &= \beta(n) - \sum_{d | n, d < n} \beta(d) \, \varphi(n/d).
+\deg_R A_n\Rlam &= \sum_{d|n} \varphi(n/d) 2^{d-1}, \\
+\deg_R P_n\Rlam &= \sum_{d|n} \mu(n/d) 2^{d-1}, \\
+\deg S_n(R) &= \deg_R R_n\Rlam - \sum_{d | n, d < n} \deg_R R_d\Rlam \, \varphi(n/d).
 \end{align}
@@
 \end{theorem}
-
+%
+%
+%
 \begin{proof}
@@
 Finally, each term of the determinant
-$A_n\RX = \big|\lambda \, \vct I - \vct T(R)\big|$
+$A_n\Rlam = \big|\lambda \, \vct I - \vct T(R)\big|$
 is given by
@@
 \begin{align*}
-  \deg_R A_n\RX
-  = \max \sum_{p \in \Bset} \deg T_{pq}(R)
+  \deg_R A_n\Rlam
+  = \max \sum_{p \in \Pset} \deg T_{pq}(R)
   \le N(n) \, \big(n + |p| - |q|\big)/2 = n N(n)/2,
@@
 By \refeq{necklace} we have \refeqsub{degR}{a}.
-%
-The first few values are 1, 3, 6, 12, 20, 42, 70, 144, 270, 540, 1034, 2112, 4108, \dots, starting from $n = 1$.
-
-To show \refeqsub{degR}{b}, we take the degree in $R$ of \refeq{prod}.
-So $\sum_{d|n} \beta(d) \, \big(n/d\big) = N(n) \, n/2$,
-whose inversion is
-  $\beta(n)/n = \sum_{d|n} \mu(n/d) \, N(d)/2 = L(n)/2$.
-The last step follows from inverting \refeq{necklacelyndon}.
-%
-The first few values are 1, 1, 3, 6, 15, 27, 63, 120, 252, 495, 1023, 2010, 4095, \dots, starting from $n = 1$.
-
-\refeqsub{degR}{c} follows directly from taking the degree in $R$ of \refeq{origfac}.
-The first few values are 1, 0, 1, 3, 11, 20, 57, 108, 240, 472, 1013, 1959, 4083, \dots, starting from $n = 1$.
-\end{proof}
-
+
+\refeqsub{degR}{b} and (c) follow from taking taking the degree in $R$ of
+  \refeq{prod} and \refeq{origfac}.
 \refeqsub{degR}{b} was long known \cite{mira, stephenson2},
 and \reqsub{degR}{c} was recently derived \cite{blackhurst}.
+%
+\end{proof}
+%
+The first few values of $\deg_R A_n\Rlam$,
+  $\deg_R P_n\Rlam$,
+  and $\deg S_n(R)$ are
+  1, 3, 6, 12, 20, 42, 70, 144, 270, 540, 1034, 2112, 4108, \dots,
+  1, 1, 3, 6, 15, 27, 63, 120, 252, 495, 1023, 2010, 4095, \dots,
+  1, 0, 1, 3, 11, 20, 57, 108, 240, 472, 1013, 1959, 4083, \dots,
+  respectively (starting from $n = 1$).
 
@@
 
-We now extend the method to the H\'enon map \cite{henon}:
+A natural two-dimensional extension of the logistic map
+  is the H\'enon map \cite{henon}:
 \begin{equation}
@@
 \[
-  J_b(x_k)
+  \vct J_b(x_k)
   \equiv \left(
@@
 The eigenvalue $\lambda$ of the composite Jacobian
-$J_b(x_1) \cdots J_b(x_n)$ can be computed from
-%
-\begin{equation}
-\big|\, \lambda \, \vct I - J_b(x_1) \cdots J_b(x_n) \,\big|
+$\vct J_b(x_1) \cdots \vct J_b(x_n)$ can be computed from
+%
+\begin{equation}
+\big|\, \lambda \, \vct I - \vct J_b(x_1) \cdots \vct J_b(x_n) \,\big|
   = \lambda^2 - \Theta(\vx) \,\lambda +(-b)^n = 0,
@@
 are the trace and determinant of
-the matrix product $J_b(x_1) \cdots J_b(x_n)$,
+the product matrix $\vct J_b(x_1) \cdots \vct J_b(x_n)$,
 respectively \cite{hitzl}.
 In a stable cycle, the magnitude of $\lambda$
-cannot exceed 1; so we replace $\lambda$ by $+1$ or $-1$
-in \refeq{henonder}
-to obtain the onset or bifurcation point, respectively.
+cannot exceed 1; and $\lambda = +1$ or $-1$
+in \refeq{henonder} corresponds to
+the onset or bifurcation point, respectively.
 \refeq{henonder} is the counterpart of \refeq{der}.
 
-Since cyclically rotating matrices in a product does not alter the trace,
-$\Theta(\vx)$ is a cyclic polynomial of $\vx = \{ x_k \}$.
-%e.g.,
-%$\Theta(\vx) = 4 x_1 x_2 + 2 \, b$ for $n = 2$ and
-%$\Theta(\vx) = -8 x_1 x_2 x_3 - 2 \, b (x_1+ x_2+ x_3)$ for $n = 3$.
+Since the trace of the product of two matrices is
+  independent of the order,
+$\Theta(\vx)$ must a cyclic polynomial of $\vx = \{ x_k \}$.
 %
@@
 in \refeq{xr} to complete the solution.
-
-\newcommand{\BB}[2]{B^{(2)}_{#1,#2}}
-\newcommand{\BBB}[3]{B^{(4)}_{#1,#2,#3}}
-\newcommand{\BBBB}[4]{B^{(6)}_{#1,#2,#3,#4}}
-
-\begin{table}[h]\footnotesize
-%\caption{
-\tbl{Onset and bifurcation polynomials of the $n$-cycles of the H\'enon map.}
-{\begin{tabular*}{\linewidth}{c c c c}
-%{c p{.2\linewidth} p{.35\linewidth} p{.35\linewidth}}
-\hline
-$n$
-& $\Theta(\vx)$
-& Onset $P_n(a, b, +1)$ $^{\dagger, \ddagger}$
-& Bifurcation $P_n(a, b, -1)$ $^{\dagger, \ddagger}$ \\
-\hline
-1
-& $-2 x_1$
-& $-A - (b-1)^2$
-& $-A + 3(b-1)^2$ \\
-%\hline
-2
-& $4 C_{12} + 2 b$
-& $A-3 (b-1)^2$
-& $A - \BB{5}{-6}$ \\
-%\hline
-3
-&
-  $-8C_{123}-2b C_1$
-&
-  \begin{minipage}[h]{.35\linewidth}
-  $\left( -A + \BB{7}{10} \right)$ \\
-  $\left\{ \left[ A -\frac{1}{2}\BB{1}{-8} \right]^2 + \frac{27}{4} (b^2-1)^2 \right\}$
-  \end{minipage}
-
-&
-  \begin{minipage}[h]{.35\linewidth}
-  \vspace{5mm}
-  $\begin{aligned}
-  -A^3&+2 \BB{4}{1} A^2 - 9 \BBB{2}{-6}{-7} A \\
-  &+9 \BBBB{9}{6}{2}{-10}
-  \end{aligned}$
-  \vspace{5mm}
-  \end{minipage} \\
-%\hline
-4
-& \begin{minipage}[h]{.2\linewidth}
-  $16 C_{1234} + 4 b C_{12} + 2b^2$
-  \end{minipage}
-& \begin{minipage}[h]{.35\linewidth}
-  $\left(A - \BB{5}{-6}\right)$ \\
-  $\left\{ \left[A + (b+1)^2\right]^2 + 4(b^2-1)^2 \right\}$ \\
-  $\left\{ \left[A - 3(b+1)^2\right]^3 - 108(b-1)^2(b+1)^4 \right\}$
-  \end{minipage}
-& %\begin{minipage}[h]{.35\linewidth}
-  $\begin{aligned}
-  &A^6 - 4A^5 \BB{3}{2} + A^4 \BBB{47}{68}{38} \\
-  &-3A^3\BBBB{47}{62}{-83}{-212} + \left({\BBB{17}{12}{-6}}\right)^3  \\
-  &+ A^2\BBB{17}{12}{-6}\BBB{31}{-60}{-186}
-  \end{aligned}$
-  %\end{minipage}
-\\
-%\hline
-5
-& %\begin{minipage}[m]{.2\linewidth}
-  $\begin{aligned}
-  -&32C_{12345}\\
-  -&8bC_{123} -2b^2C_1
-  \end{aligned}$
-  %\end{minipage}
-&
-  \begin{minipage}[m]{.35\linewidth}
-  \vspace{3mm}
-  $\begin{aligned}
-    &-\Big( A^4  -\BB{1}{-12} A^3 + \BBB{1}{6}{21}A^2 \\
-    &+\BBBB{9}{-14}{70}{-80} A + \BBB{1}{1}{1}\BBB{31}{-89}{121}
-    \Big) \\
-    &\Big( A^{11} - \BB{31}{14} A^{10} + 2 \BBB{208}{206}{377} A^9 \\
-    &-\cdots -75728722 b - 28629151\Big)
-  \end{aligned}$
-  \end{minipage}
-& %\begin{minipage}[m]{.35\linewidth}
-  $\begin{aligned}
-  -A^{15} &+ 2 \BB{16}{1} A^{14}- \BBB{448}{60}{669} A^{13} \\
-  &+ \cdots + 1291467969
-  \end{aligned}$
-  %\end{minipage}
-\\
-\vdots & \vdots & \vdots & \vdots
-\\
-9
-& %\begin{minipage}{.2\linewidth}
-  $\begin{aligned}
-  &-512 C_{1\dots9}\\
-  &-\cdots-2b^4 C_1
-  \end{aligned}$
-%  \begin{align*}
-%  -512 C_{1\dots9} -128 b C_{1\dots7} -2b^4 C_1 \\
-%  -32b^2(C_{12345} + C_{12347} + C_{12367}) \\
-%  -8b^3 (C_{123} + C_{125} + C_{145} + C_{147})
-%  \end{align*}
-  %\end{minipage}
-
-& %\begin{minipage}{.35\linewidth}
-  $\begin{aligned}
-  &-(A^6 + 12 b A^5 + \dots)
-   \big( A^6 - 4\BB{4}{1}A^5 + \dots \big) \\
-  &\Big( A^{240} - 8\BB{61}{1}A^{239} +4\BBB{29525}{1019}{58188}A^{238} \\
-  &  -\dots +120670698649\dots712084645033 \Big)
-  \end{aligned}$
-  %\end{minipage}
-
-& %\begin{minipage}{.35\linewidth}
-  $\begin{aligned}
-  &-\big(
-   A^{252} - 504 (1+b^2) A^{251} \\
-  +& 4 \BBB{31500}{16}{62067} A^{250} - \dots \\
-  +& 5842146539\dots9260477441
-  \big)
-  \end{aligned}$
-  %\end{minipage}
-\\
-\hline
-\multicolumn{4}{p{\linewidth}}{
-$^\dagger$
-Definitions: $A \equiv 4 a$,
-$\BB{p}{q} \equiv p (b^2+1) + q b$,
-$\BBB{p}{q}{r} \equiv p (b^4+1) + q (b^3 + b) +r b^2$,
-$\BBBB{p}{q}{r}{s} \equiv p (b^6 + 1) + q (b^5 + b) +r (b^4 + b^2) + sb^3$,
-$\dots$.
-}
-\\
-\multicolumn{4}{p{\linewidth}}{
-$^\ddagger$
-  The onset polynomials for $n$ from 1 to 4,
-  and the bifurcation polynomials for $n$ from 1 to 3,
-  agree with those in ref. \cite{hitzl}.
-}\\
-\hline
-\end{tabular*}
-\label{tab:henonpoly}
-}
-\end{table}
-
-We computed the polynomials of $a$ and $b$
-  at the onset and bifurcation points for $n$ up to 9.
+%
+%
+%
 The polynomials of $a$ and $b$
-  at the onset and bifurcation points,
-  as well as $\Theta(\vx)$,
-  are listed in \reftab{henonpoly} for small $n$
-(for larger $n$, see the website in \refsec{end}).
+  at the onset and bifurcation points for $n$ up to 9
+  are listed in the website in \refsec{end}.
 
@@
 
-We now study the following cubic map \cite{strogatz}
+For higher-order one-dimensional maps, we consider the following cubic map \cite{strogatz}
+%
 \begin{equation}
@@
 \end{equation}
-Since the new replacement rule
+%
+Unlike the logistic map, this map has a clear parity,
+  that is, $f(-x) = -f(x)$.
+We shall show below that this odd parity can be used to reduce the amount of calculation.
+
+First of all, the new replacement rule
 \begin{equation}
@@
 \end{equation}
-no longer eliminates squares,
-%
-we must extend the basis set of cyclic polynomials
+no longer eliminates squares.
+%
+We must, therefore, extend the basis set of cyclic polynomials
   from the square-free ones to the cube-free ones,
-  in using \refeq{xcp}.
-We include in the basis of expansion
+  in listing equations \eqref{eq:xcp}.
+For example, we include in the basis
   $C_{112} = {x_1}^2 x_2 + {x_2}^2 x_3 + \dots + {x_n}^2 x_1$ ($n\ge3$),
@@
 
-%An interesting feature of the cubic map
-%is that it is odd:
-%for a trajectory $x_1, x_2, \ldots$
-%the mirror $-x_1, -x_2, \ldots$
-%also satisfies the map.
-%
-%As a result,
-However, we only need the cube-free cyclic polynomials of even degrees in $\vx$
-to solve the problem,
-%
-because \refeq{cubic} contains only linear and cubic terms,
-a cyclic polynomial with an odd (even) degree in $\vx$
-can never be reduced to one with an even (odd) degree
-by \refeq{cubreplace}.
+The odd parity, however, allows us to limit
+  the set of cube-free cyclic polynomials
+  to those of even degrees in $\vx$.
+%
+This is because \refeq{cubreplace} contains only linear and cubic terms,
+and a cyclic polynomial with an odd (even) degree in $\vx$
+can never be reduced to one with an even (odd) degree.
 %
@@
 %
-For technical reasons, we will not use polynomials of odd degrees,
-because the map allows a symmetric $2n$-cycle:
-$x_1, x_2, \ldots, x_n, -x_1, -x_2, \ldots, -x_n$
-(see \reffig{oddcycle}),
-which makes all odd cyclic polynomials zero,
-e.g., $C_1 = x_1 + x_2 + \dots + x_n - x_1 - x_2 - \dots - x_n = 0$.
-%
-Thus, the zero determinant condition, similar to that in \refeq{xr},
-  would be useless for these cycles,
-  if the odd-degree polynomials were used.
-
-\begin{figure}[h]
-  \begin{minipage}{\linewidth}
-    \begin{center}
-        \includegraphics[angle=-90, width=\linewidth]{oddcycle.pdf}
-    \end{center}
-  \end{minipage}%
-  \caption{\label{fig:oddcycle}
-  Odd-cycles of the cubic map.}
-\end{figure}
-
-We therefore have a theorem similar to \refthm{sqrfree}.
-%
-%
-\begin{theorem}
-  For the cubic map \refeq{cubic},
-  any cyclic polynomial $K(\vx)$ of
-  an $n$-cycle orbit
-  $\vct x = \{x_1, \ldots, x_n\}$
-  with an even degree in $\vct x$
-  is a linear combination of
-the even cube-free cyclic polynomials $C_p(\vx)$:
-\[
-  K(\vx) = \sum_{p \in \Bset} f_p(R) C_p(\vx),
-\]
-  where $\Bset = \{0, 11, 12, 13, \ldots, 1122, 1123, \ldots \}$ is
-  the set of indices of all even cube-free cyclic polynomials,
-  and $f_p(R)$ are polynomials of $R$.
-  \label{thm:cubfree}
-\end{theorem}
-
+%We therefore have a theorem similar to \refthm{sqrfree}.
+%%
+%%
+%\begin{theorem}
+%  For the cubic map \refeq{cubic},
+%  any cyclic polynomial $K(\vx)$ of
+%  an $n$-cycle orbit
+%  $\vct x = \{x_1, \ldots, x_n\}$
+%  with an even degree in $\vct x$
+%  is a linear combination of
+%the even cube-free cyclic polynomials $C_p(\vx)$:
+%\[
+%  K(\vx) = \sum_{p \in \Pset} f_p(R) C_p(\vx),
+%\]
+%  where $\Pset = \{0, 11, 12, 13, \ldots, 1122, 1123, \ldots \}$ is
+%  the set of indices of all even cube-free cyclic polynomials,
+%  and $f_p(R)$ are polynomials of $R$.
+%  \label{thm:cubfree}
+%\end{theorem}
+%
+%
+%
+%
 With the above change, the rest derivation is similar to that of the logistic map.
@@
   at the onset and bifurcation points
-for some small $n$ are shown in \reftab{cubpolygen} (general $\lambda$)
-and \reftab{cubpoly} ($\lambda = \pm1$);
-for larger $n$ up to 8,
-we have saved the data on the website in \refsec{end}.
+%for some small $n$ are shown in \reftab{cubpolygen} (general $\lambda$)
+%and \reftab{cubpoly} ($\lambda = \pm1$);
+%for larger $n$ up to 8,
+%we have saved the data
+  are listed on the website in \refsec{end}.
 %
@@
 %
-For complex $r$ and $\vx$,
-we have plotted \reffig{cubbulb} for regions of stability.
+%For complex $r$ and $\vx$,
+%we have plotted \reffig{cubbulb} for regions of stability.
 
 \begin{table}[h]\footnotesize
-  %\caption{
-  \tbl{
-  Minimal polynomials $P_n(r, \lambda)$ of
-  the $n$-cycles of the cubic map \refeq{cubic}.
-  }
-%\begin{center}
-{
-\begin{tabular}{lc}
-\hline
-  $n$
-& $P_n(r, \; \lambda)$ $^\dagger$
-\\
-\hline
-1
-&
-$(\lambda - r) (\lambda + 2 r - 3)$
-\\
-2
-&
-  $
-  \big[
-  \cancel{\lambda - (2r+3)^2}
-  \big]
-  (\lambda + 2r^2 - 9)
-  $
-\\
-3
-&
-$\begin{aligned}
-  &\lambda^4
-  + 2 (r+6)(r^2-9) \lambda^3
-  -6 \big(8 r^6+12 r^5-66 r^4-81 r^3+54 r^2-243 r-729\big)
-  \lambda^2
-+2 (r^2-9) \big(16 r^7-252 r^5\\
--&216 r^4 +648 r^3+972 r^2+2187 r+4374\big) \lambda
-+2 r (2r-3) (2 r+3)^2 (r^2-9) (2 r^2 - 9)^2 (4 r^2+9) + 531441
-\end{aligned}$
-\\
-4
-&
-\begin{minipage}{.97\linewidth}
-\vspace*{1mm}
-$\begin{aligned}
-&\big[ \cancel{
-  (\lambda-8r^4+54r^2+81)^2
--4 (r^2-9)^2 \lambda
-} \big]
-\,^\ddagger\,
-\big[
-\lambda^8
-+2(5 r^4-324) \lambda^7
-+2(112 r^8-1296 r^6+3807 r^4-91854) \lambda^6 \\
-+&\dots
-+18075490334784 r^8
--61004779879896 r^6
--411782264189298 r^4
-+1853020188851841
-\big]
-\end{aligned}$
-\end{minipage}
-\\
-%5
-%&
-%\begin{minipage}{.97\linewidth}
-%\vspace*{1mm}
-%$\begin{aligned}
-%\end{aligned}$
-%\vspace{1mm}
-%\end{minipage}
-%\\
-\vdots & \vdots
-\\
-\hline
-\multicolumn{2}{p{\textwidth}}{
-$^\dagger$
-The factors from odd-cycles (see \refsec{oddcycle}) are struck out.
-}\\
-\multicolumn{2}{p{\textwidth}}{
-$^\ddagger$
-The $n = 4$ odd-cycles satisfy
-$(\lambda^\odd + 9)^2 - 2(\lambda^\odd-27) r^2 - 8 r^4 = 0$,
-  where $\lambda^\odd=\pm\sqrt\lambda$.
-} \\
-\hline
-\end{tabular}
-\label{tab:cubpolygen}
-}
-%\end{center}
-\end{table}
-
-\begin{table}[h]\footnotesize
-\tbl{
-%\caption{
-Onset and bifurcation polynomials of the $n$-cycles of the cubic map \refeq{cubic}.}
-%\begin{center}
-{
-\begin{tabular*}{\linewidth}{l c c}
-%{c p{.2\linewidth} p{.35\linewidth} p{.35\linewidth}}
-\hline
-$n$
-&
-Onset $P_n(r, +1)$ $^\dagger$
-&
-Bifurcation $P_n(r, -1)$ $^\dagger$
-\\
-\hline
-1
-&
-$-(r-1)^2$
-&
-$-(r+1)(r-2)$
-\\
-2
-&
-$-2 (r-2) (r+1) (r+2)^2$
-&
-$-(r^2-5) (2 r^2+6 r+5)$
-\\
-3
-&
-\begin{minipage}{.45\linewidth}
-\vspace{3mm}
-$\begin{aligned}
-&(r^2+r+1) (4 r^2-14 r+13) \\
-&(4 r^8+16 r^7-35 r^6-206 r^5-113 r^4\\
-&+376 r^3+715 r^2+1690 r+2197)
-\end{aligned}$
-\vspace{1mm}
-\end{minipage}
-&
-\begin{minipage}{.5\linewidth}
-\vspace{3mm}
-$\begin{aligned}
-&16 r^{12}+24 r^{11}-288 r^{10}-434 r^9\\
-+&1539 r^8+2358 r^7-1434 r^6-2556 r^5-8541 r^4\\
--&11816 r^3+15288 r^2+24696 r+38416
-\end{aligned}$
-\vspace{1mm}
-\end{minipage}
-\\
-4
-&
-\begin{minipage}{.45\linewidth}
-\vspace{3mm}
-$\begin{aligned}
--&8(r^2-8) (r^2-5) (r^2+1) (2 r^2-6 r+5) \\
-&(2 r^2+6 r+5) (2 r^4-13 r^2-25)^2 \\
-&(1024 r^{22}-32512 r^{20}+402304 r^{18} \\
--&2364832 r^{16}+5389924 r^{14}+9715769 r^{12} \\
--&73067038 r^{10}+58934785 r^{8}+235761152 r^6 \\
--&160907264 r^4-671088640 r^2-2097152000)
-\end{aligned}$
-\vspace{3mm}
-\end{minipage}
-&
-$\begin{aligned}
-&-(16 r^8-216 r^6+410 r^4+2142 r^2+1681) \\
-&(8192 r^{32}-387072 r^{30}+7834624 r^{28} -88031232 r^{26}\\
-&+585876512 r^{24}-2158227720 r^{22} +2211361312 r^{20}\\
-&+15958823175 r^{18}  -68871388441 r^{16} +59290039854 r^{14}\\
-&+234882618673 r^{12} -524807876277 r^{10} -72612143404 r^8\\
-&+308406843576 r^6 +1539579145957 r^4-7984925229121)
-\end{aligned}$
-\\
-\vdots & \vdots & \vdots
-\\
-8
-&
-$\begin{aligned}
-&-8192 (r^4+1) (2 r^4-18 r^2+41) \\
-&(8 r^4-48 r^3+108 r^2-108 r+41) \\
-&(8 r^4+48 r^3+108 r^2+108 r+41) \dots\\
-%&(16 r^8-216 r^6+410 r^4+2142 r^2+1681) \\
-%&(8192 r^{32}-\dots-7984925229121) \\
-%&(16384 r^{36}-\dots-1310720000000000) \\
-%&(131072 r^{40}-\dots-13422659310152401)^2 \\
-&(22016722240\dots14954924752896r^{3108} \\
-&-\dots-180097954\dots2522413056\times 10^{400})
-\end{aligned}$
-&
-$\begin{aligned}
--&(17592186044416 r^{80} +\dots+ \\
-&144564714832407908402064153121600801) \\
-&(4841528421712030\dots03048551060078592 r^{3200}\\
-&-\dots-25263420710\dots173884723232001)
-\end{aligned}$
-\\
-\hline
-\multicolumn{3}{p{\linewidth}}
-{
-$^\dagger$
-Although $P_n(r, \lambda)$ is the minimal polynomial for a general $\lambda$,
-it may contain a pre-factor (e.g., $-2$ in the $n=2, \lambda=+1$ case).
-}\\
-\hline
-\end{tabular*}
-%\end{center}
-\label{tab:cubpoly}
-}
-\end{table}
-
-\begin{table}[h]\footnotesize
-
 %\caption{
@@
 
-\begin{figure}[h]
-  \begin{minipage}{\linewidth}
-    \begin{center}
-        \includegraphics[angle=-90, width=\linewidth]{cubbulb.pdf}
-    \end{center}
-  \end{minipage}%
-  \caption{
-  \label{fig:cubbulb}
-  Stable regions of the $n$-cycles of the cubic map \refeq{cubic}
-  with a complex $R$;
-  obtained from $P_n(R, e^{i\theta}) = 0$ with $\theta \in [0, 2\pi]$
-  cf. \reffig{logbulb}.
-}
-\end{figure}
-
-\subsection{Counting cycles}
-
-We now compute the number of the even cube-free cyclic polynomials
-by establishing a one-to-one correspondence between
-the cube-free cyclic polynomials and the \emph{ternary} necklaces,
-in which each bead of the string is assigned a number
-0, 1, or 2, instead of just 0 or 1.
-%
-For example, the necklace $\mathbf{212001\cdots}$
-corresponds to $C_{112336}(\vx)$,
-whose generator is
-${x_1}^2 \, {x_2} \, {x_3}^2 \, x_6$:
-the first bead is \textbf{2} for ${x_1}^\mathbf{2}$,
- the second is \textbf{1} for ${x_2}^\mathbf{1}$,
- the third is \textbf{2} for ${x_3}^\mathbf{2}$,
- and the sixth is \textbf{1} for ${x_6}^\mathbf{1}$.
-%
-A necklace is even,
-if the corresponding cyclic polynomial has an even degree in $\vx$.
-%
-This means that the sum of numbers (0, 1, or 2)
-  on the beads of the necklace,
-  which equals the degree in $\vx$ of the polynomial, is also even.
-
-%Now, the number of the cube-free cyclic polynomials
-%is now equal to that of total necklaces
-%\[
-%  N_3(n) = (1/n) \sum_{d|n} \varphi(n/d) 3^d.
-%\]
-%
-%The proof is similar to that in \refsec{degprimfac}.
-%For even necklaces, we have
-
-\begin{theorem}
-The number of the even ternary necklaces
-or the cube-free cyclic polynomials for the cubic map of even degrees in $\vx$
-is given by
+Similar to the logistic-map case,
+the number of the even cube-free cyclic polynomials
+is equal to the number of even \emph{ternary} necklaces,
+in which each bead of the string can assume
+0, 1, or 2, with the total being even.
+%
+The number of ternary necklaces is
+$N_3(n) = \frac{1}{n} \sum_{c d = n} \varphi(c) 3^d$,
+%\begin{theorem}
+while that of the even ones is
+%or the cube-free cyclic polynomials for the cubic map of even degrees in $\vx$
+%is given by
 \begin{equation}
@@
 where
-$\odd(c) \equiv \big[1 - (-1)^c\big]/2$ is 1 if $c$ is odd or 0 if even.
-\label{thm:cubnecklace}
-\end{theorem}
-
-\begin{proof}
-We first show that the number of even ternary strings is $(3^n + 1)/2$.
-%
-Consider the generating function
-\[
-  Z\big(\{x_1, x_2,\dots, x_n\}\big) = \prod_{i=1}^n (1+x_i+{x_i}^2),
-\]
-where $1$, $x_i$, and $x_i^2$ correspond to the states that bead $i$
-taking the number $0$, $1$, and $2$, respectively;
-and the product over $n$ sums over states of independent beads.
-%
-In the expansion of $Z(\vx)$,
- each term (which takes the form
-  ${x_1}^{e_1} {x_2}^{e_2} \dots {x_n}^{e_n}$,
-  with $e_i = 0, 1, 2$)
-represents a unique ternary string $e_1 e_2 \dots e_n$,
-which is even, if $e_1 + e_2 + \dots + e_n$ is so.
-%
-By setting $x_1 = x_2 = \dots = x_n = 1$,
-$Z=3^n$ equals the total number of ternary strings.
-%
-By setting $x_1 = x_2 = \dots = x_n = -1$,
-a term representing an even (odd) ternary string
-  is $+1$ ($-1$);
-and $Z=(1-1+1)^n=1$
-equals the difference between the number of even strings
-  and that of odd strings.
-%
-Thus, the average $(3^n+1)/2$
-gives the number of even ternary strings.
-
-\begin{table}[h]\footnotesize
-\tbl{
-%\caption{
-Two ways of counting the $N_e(2) = 4$ ternary necklaces for $n = 2$.
-}
-%\begin{center}
-{
-\begin{tabular}{c | c  c c | c  | c | c | c | c }
-%\begin{tabularx}{\textwidth}{c | c  c c | c  | c | c | c | c }
-\hline
-        & \multicolumn{3}{c|}{$m = 1$}
-        & $m = 2$
-        & $c = n/d$
-        & $T(d, c)$ $^\dagger$
-        & $\varphi(c)$ & $\varphi(n/d) T(d, c)$\\
-\hline
-$d = 1$ & \hspace{1mm} $\mathbf{0}_{\times2}$ \hspace{1mm}
-        & \hspace{1mm} $\mathbf{1}_{\times2}$ \hspace{1mm}
-        & \hspace{1mm} $\mathbf{2}_{\times2}$ \hspace{1mm}
-        & & $2$ & $3$ & $1$ & 3 \\
-\hline
-$d = 2$ & $\mathbf{00}$
-        & $\mathbf{11}$
-        & $\mathbf{22}$
-        & \hspace{1mm} $\mathbf{20} (02)$ $^\ddagger$ \hspace{1mm}
-        & $1$ & $3+1\cdot2=5$ & $1$ & 5 \\
-\hline
-$m \sum_{m|d, d|n} \varphi(\frac{n}{d})$
-      & \multicolumn{3}{c|}{$1\cdot(1+1) = 2$}
-      & $2\cdot1 = 2$ &    \multicolumn{3}{c|}{} &  $\downarrow$\\
-\hline
-$N_e(n)\cdot n$
-    & \multicolumn{3}{c|}{$3 \cdot 2$} & $1 \cdot 2$ &
-  \multicolumn{3}{c|}{$\rightarrow$} & $4\cdot2 = 3 + 5$ \\
-\hline
-\multicolumn{9}{p{\linewidth}}{
-  Bold strings are necklaces; others are their cyclic versions.
-}
-\\
-\multicolumn{9}{p{\linewidth}}{
-The subscript of a string means the number of repeats;
-e.g.,
-$\mathbf{1}_{\times2}$ means $\mathbf{1}$ repeated twice, or $\mathbf{11}$;
-}
-\\
-\multicolumn{9}{p{\linewidth}}{
-$^\dagger$ $T(d, c) \equiv 3^d - \odd(c)(3^d-1)/2$,
-which is $3^d$ if $c$ is even,
-or $(3^d+1)/2$ if $c$ is odd.
-}
-\\
-\multicolumn{9}{p{\linewidth}}{
-$^\ddagger$
-The odd binary strings $\mathbf{10}$, $01$, $\mathbf{21}$, and $12$
-  do not contribute to the sum, and are excluded from $T(d, c)$.
-}
-\\
-\hline
-\end{tabular}
-%\end{tabularx}
-%\end{center}
-\label{tab:countcubnecklace}
-}
-\end{table}
-
-The rest counting process is similar to that in \refsec{degprimfac}:
-%
-we construct the sum $n N_e(n)$ by two ways, as exemplified in \reftab{countcubnecklace}.
-%
-In the first way,
-  for a fixed $d$ ($d|n$),
-  if $c\equiv n/d$ is even,
-    we count all ternary strings whose period $m$ divide $d$,
-  but if $c$ is odd, we count only ternary strings
-    whose first $d$ beads are even
-    (because repeating an odd string an odd number times
-    does not yield an even string);
-  in either case, we multiple the result by $\varphi(c)$.
-%
-The process for a fixed $d$ corresponds to a row of \reftab{countcubnecklace}.
-%
-Repeating the process for all $d$ gives
-  $\sum_{cd = n} T(d, c) \, \varphi(c)$,
-  where $T(d, c)$ is the total number $3^d$ of period-$d$ ternary strings if $c$ is even,
-  or the number $(3^d+1)/2$ of even strings if $c$ is odd.
-
-In the second way,
-  we look at the contribution from each necklace to the above sum.
-An even period-$m$ necklace contributes a total of
-  $m \times \sum_{m|d, d|n} \varphi(n/d) = n$
-  \big[the multiplier $m$ is for the $m$ cyclic versions, cf. \refeq{mphind}\big],
-  while an odd necklace contributes nothing.
-Thus, the sum equals $N_e(n)\cdot n$.
-%
-The process for a fixed necklace corresponds to
-  a column of \reftab{countcubnecklace}.
-
-So
-\[
-  N_e(n) \cdot n = \sum_{cd = n} T(d, c) \, \varphi(c),
-\]
-which is \refeq{cublyndon}
-after we divide both sides by $n$.
-\end{proof}
-
-%
-$N_e(n)$ = 2, 4, 6, 14, 26, 68, 158, 424, \dots, starting from $n = 1$.
+$\odd(c)$ %$\equiv \big[1 - (-1)^c\big]/2$
+is 1 if $c$ is odd or 0 if even.
+%\label{thm:cubnecklace}
+%\end{theorem}
+%
+Since $N_e \approx N_3/2$, using the parity saves about half of the equations.
+%
+For the first few values, $N_e(n)$ = 2, 4, 6, 14, 26, 68, 158, 424, \dots, starting from $n = 1$.
 %
@@
   by \refthm{primfac} with proper substitutions
-  \big[$R\rightarrow r$,
+  $R\rightarrow r$,
     $A_n(R, \lambda) \rightarrow A_n(r, \lambda)$,
-    etc.\big].
-The degree of the polynomial is given by
-
-\begin{theorem}
+    etc.
+%The degree of the polynomial,
 The degree in $\lambda$ of
-the minimal polynomial $P_n(r, \lambda)$ of the $n$-cycles is
+the minimal polynomial $P_n(r, \lambda)$ of the $n$-cycles,
+  after some algebra,
+  is given by
+%
+%
+%\begin{theorem}
+%The degree in $\lambda$ of
+%the minimal polynomial $P_n(r, \lambda)$ of the $n$-cycles is
 \begin{equation}
@@
 \end{equation}
-where $\odd(n) = [1 - (-1)^n]/2$
-is $1$ for an odd $n$,
-but $0$ for an even $n$.
-\label{thm:cublyndon}
-\end{theorem}
-
-\begin{proof}
-Similar to the logistic map case \refeq{necklacelyndon},
-  we have, for the cubic map,
-\[
-  N_e(n) = \sum_{d|n} L_e(d).
-\]
-Thus, we only need to inverse this equation to obtain $L_e(n)$.
-But owing to the complexity of \refeq{cubnecklace},
-  we need the Dirichlet generating function
-  to simplify the result.
-
-For a series $\alpha(n)$,
-the Dirichlet generating function is defined as
-\[
-    G_\alpha(s) \equiv \sum_{n=1}^\infty \alpha(n) \, n^{-s}.
-\]
-In \reftab{genfunc}, we list the generating functions of
-some common series,
-and define a few new ones for $N_e(n)$ and $L_e(n)$, etc..
-
-\begin{table}[h]\footnotesize
-\tbl{
-%\caption{
-  Dirichlet generating functions for ternary necklaces.
-}
-%\begin{center}
-{
-\begin{tabular}{cccc}
-%\begin{tabularx}{\textwidth}{
-%  >{\hsize=0.6\hsize\raggedleft\arraybackslash}X
-%  >{\hsize=1.4\hsize\centering\arraybackslash}X
-%  >{\hsize=0.6\hsize\raggedleft\arraybackslash}X
-%  >{\hsize=1.4\hsize\centering\arraybackslash}X
-%}
-\hline
-$\alpha(n)$   &   $G_\alpha(s) = \sum_{n} \alpha(n)/n^{s}$  &
-$\alpha(n)$   &   $G_\alpha(s) = \sum_{n} \alpha(n)/n^{s}$
-\\
-\hline
-1             & $\zeta(s)$ $^\dagger$ &
-\multicolumn{1}{|r}
-{$N_e(n)$}      & $G_N(s)$ $^\ddagger$
-\\
-$\delta_{n,1}$         & $1$ $^\dagger$ &
-\multicolumn{1}{|r}
-{$n N_e(n)$}  & $G_N(s-1)$ $^\ddagger$
-\\
-$\mu(n)$    & $\zeta(s)^{-1}$ $^\dagger$ &
-\multicolumn{1}{|r}
-{$L_e(n)$}    & $G_L(s)$ $^\ddagger$
-\\
-$\varphi(n)$   & $\zeta(s-1)/\zeta(s)$ $^\dagger$ &
-\multicolumn{1}{|r}
-{$nL_e(n)$}   & $G_L(s-1)$ $^\ddagger$
-\\
-$\odd(n)$   & $\zeta(s) (1-2^{-s})$ &
-\multicolumn{1}{|r}
-{$3^n$}       & $t(s)$ $^\ddagger$
-\\
-\cline{3-4}
-$\mu(n) \, \odd(n)$
-  & $\Big[ \zeta(s) (1-2^{-s}) \Big]^{-1}$ &
-$\varphi(n) \, \odd(n)$
-  & $\frac{\zeta(s-1)}{\zeta(s)} \frac{1-2^{-s+1}}{1-2^{-s}}$
-\\
-\hline
-\multicolumn{4}{p{\linewidth}}{
-$^\dagger$
-See ref. \cite{hardy} for proofs.
-$\zeta(s) = \sum_n n^{-s}$ is the zeta function.
-}\\
-\multicolumn{4}{p{\linewidth}}{
-$^\ddagger$
-The sum is truncated at a large $M$ to avoid divergence.
-}\\
-\hline
-\end{tabular}
-%\end{tabularx}
-%\end{center}
-\label{tab:genfunc}
-}
-\end{table}
-
-The generating function has an important property:
-$G_\gamma(s) = G_\alpha(s) G_\beta(s)$,
-if and only if $\gamma(n) = \sum_{d|n} \alpha(n/d)\, \beta(d)$ \cite{hardy}.
-Thus,
-  the terms of the sum $\sum_{d|n} \alpha(n/d)\, \beta(d)$
-  of two sequences $\alpha$ and $\beta$
-  can be readily found from expanding the generating function.
-
-Another fact is if $G_\alpha(s)$ is the generating function of $\alpha(n)$,
-then $G_\alpha(s-1)$ is that of $n \alpha(n)$,
-for $\alpha(n)/n^{s-1} = \big[ n \alpha(n) \big] / n^s$.
-Thus, the generating function of $n$ is $\zeta(s-1)$,
-and
-that of $n N_e(n)$ is $G_N(s-1)$
-\big[$\zeta(s)$ is the generating function of 1,
-  and $G_N(s)$ is that of $N_e(n)$,
-  see \reftab{genfunc}\big].
-
-We now compute the generating function of $\mu(n)\odd(n)$.
-First, recall the generating function $G_\mu(s)$ of $\mu(n)$ is
-\[
-  G_\mu(s) = \sum_{n=1}^{\infty} \frac{\mu(n)}{n^s}
-  = \prod_p \left( 1 - \frac{1}{p^s} \right),
-\]
-where $p$ goes through every prime.
-%
-The follows directly from expanding the product
-  and the definition of $\mu(n)$,
-which is $-1$ to the power of the number of distinct prime factors.
-%
-The same reasoning applies to
-$G_{\mu, \odd}(s) = \sum_{n \text{ odd}} \mu(n)/n^s$
-with the only difference being that all multiples $n$ of 2
-are absent. So
-%
-\[
-  G_{\mu, \odd}(s)
-  = \sum_{n=1}^{\infty} \frac{\mu(n) \, \odd(n)}{n^s}
-  = \sum_{n \text{ odd}} \frac{\mu(n)}{n^s}
-  = \prod_{p \ge 3} \left( 1 - \frac{1}{p^s} \right).
-\]
-Comparing the two formulas yields
-\[
-  G_{\mu, \odd}(s)
-  = G_{\mu}(s)
-  \left(1- \frac{1}{2^s}\right)^{-1}
-  =
-   \left[ \zeta(s) \left(1- \frac{1}{2^s}\right) \right]^{-1}.
-\]
-
-Similarly,
-we can compute the generating function of $\odd(n)$ as
-\[
-  G_\odd(s)
-  \equiv \sum_{n=1}^{\infty} \frac{\odd(n)}{n^s}
-  = \sum_{n \text{ odd}} \frac{1}{n^s}
-  = \zeta(s) \left(1 - \frac{1}{2^s} \right).
-\]
-This can also be derived by taking the generating function of
-both sides of the identity:
-$\sum_{d|n} \mu(d) \odd(d) \, \odd(n/d) = \delta_{n, 1}$
-\big[which is a modification of
-$\sum_{d|n} \mu(d) = \delta_{n, 1}$\big].
-%
-It follows that the generating function of $n \, \odd(n)$ is $G_\odd(s-1)$.
-
-The generating function $G_{\varphi,\odd}(s)$
-of $\varphi(n) \odd(n)$ can be computed by taking the generating function
-of both sides of the identity
-\[
-  n \, \odd(n)  = \sum_{d|n} \varphi(d) \, \odd(d) \; \odd(n/d),
-\]
-i.e., if $n$ is even, then both sides are 0;
-if odd, then $n = \sum_{d|n} \varphi(d)$.
-So
-\[
-  G_{\varphi,\odd}(s) = \frac{G_\odd(s-1)}{G_\odd(s)}
-  = \frac{\zeta(s-1)}{\zeta(s)} \frac{1 - 2^{-s + 1}}{1 - 2^{-s}}.
-\]
-
-We can now compute the generating function $G_N(s)$ of $N_e(s)$.
-By multiplying $n$ to both sides of \refeq{cubnecklace},
-and taking the generating function,
-we find that
-\begin{align*}
-  G_N(s - 1)
-    = G_\varphi(s) t(s)- G_{\varphi, \odd}(s) \frac{t(s)-\zeta(s)}{2}
-    =
-      \frac{\zeta(s-1) \Big[ t(s) + \zeta(s) \big( 1  - 2^{-s+1} \big) \Big]  }
-           {2 \, \zeta(s) (1 - 2^{-s}) }
-\end{align*}
-where the left side $G_N(s-1)$ is
-  the generating function of $N_e(n) \, n$,
-and formulas in \reftab{genfunc} have been used.
-
-Finally, we take the generating function of both sides of
- $N_e(n) = \sum_{d|n} L_e(d)$:
-\[
-  G_N(s) = \zeta(s) \, G_L(s),
-\]
-and
-\begin{align*}
-  G_L(s-1) = \frac{G_N(s - 1)}{\zeta(s-1)}
-       = 1
-        + \frac{ t(s) - \zeta(s) }
-          {2 \, \zeta(s) \big(1 - 2^{-s}\big)}
-       = 1 + \frac{t(s) - \zeta(s)}{2} G_{\mu, \odd}(s).
-\end{align*}
-Comparing the coefficients of the $n$th term ($n \ll M$),
-  we find
-\[
-  n L_e(n) = \delta_{n,1} + \sum_{cd = n} \mu(c) \, \odd(c) \frac{3^d-1}{2},
-\]
-which is \refeq{cublyndon}, note that $\delta_{n,1} = \sum_{c|n}\mu(c)$.
-%
-\end{proof}
-
-%
+%where $\odd(n)$ %$= [1 - (-1)^n]/2$
+%is $1$ for an odd $n$,
+%but $0$ for an even $n$.
+%\label{thm:cublyndon}
+%\end{theorem}
+%
+%
+For the first few values,
   $L_e(n)$ = 2, 2, 4, 10, 24, 60, 156, 410, \ldots, starting from $n = 1$.
@@
 and the $x_k$ are imaginary.
-However, in a transformed map,
-\[
-z_{k+1} = r \, z_k \, (1 - {z_k}^2),
-\]
+However, in a closely-related map
+$z_{k+1} = r \, z_k \, (1 - {z_k}^2)$,
 which differs from \refeq{cubic} by $x_k = \sqrt{r} z_k$,
 $z_k$ in the negative-$r$ cycles are real.
-
+%
+%
 Following a similar proof to \refthm{degR},
@@
 
-\subsection{\label{sec:oddcycle}Odd-cycles}
-
-Because of the symmetry $f(-x) = -f(x)$,
-the minimal polynomial $P_n(r, \lambda)$
-is subject to factorization for an even $n$.
-%
-If $x_{(n/2)+1} = -x_1$,
-  then $x_1, \ldots, x_{n/2}, -x_1, \ldots, -x_{n/2}$
-  is an $n$-cycle,
-  for $x_{n+1} = - x_{(n/2)+1} = x_1$.
-We call such a cycle an odd-cycle,
+%\subsection{\label{sec:oddcycle}Odd-cycles}
+
+%
+%
+\begin{figure}[h]
+  \begin{center}
+  \begin{minipage}{0.5 \linewidth}
+        \includegraphics[angle=-90, width=\linewidth]{oddcycle.pdf}
+  \end{minipage}%
+  \end{center}
+  \caption{\label{fig:oddcycle}
+  Odd-cycles of the cubic map.}
+\end{figure}
+%
+%
+
+The symmetry $f(-x) = -f(x)$ permits
+  a particular \emph{odd-cycle},
   see \reffig{oddcycle} for examples.
-%
-Odd-cycles satisfy a polynomial
-  of lower degrees in $\lambda$,
-  which causes the factorization.
-%
-Suppose $\Lambda^\odd(\vx) \equiv \prod_{k = 1}^{n/2} f'(x_k)$ in the odd-cycle
- satisfies $P_{n/2}^\odd(r, \lambda^\odd) = 0$
+If $x_{n+1} = -x_1$ has a solution,
+  then $x_1, \ldots, x_{n}, -x_1, \ldots, -x_{n}$
+  is a $2n$-cycle, for $x_{2n+1} = - x_{n+1} = x_1$.
+%
+The existence of odd-cycles is why we used even, but not odd, cyclic polynomials
+  in the solution.
+An odd $2n$-cyclic polynomials is also always zero
+  in an $n$-odd-cycle,
+e.g., $C_1 = x_1 + x_2 + \dots + x_n - x_1 - x_2 - \dots - x_n = 0$;
+and the zero determinant condition \refeq{xr}
+  would omit the $n$-odd-cycles from the solution.
+
+Since the $n$-odd-cycles satisfy a polynomial of lower degree,
+  the minimal polynomial $P_{2n}(r, \lambda)$
+  can always be factorized.
+%
+Suppose $\Lambda^\odd(\vx) \equiv \prod_{k = 1}^{n} f'(x_k)$ in the odd-cycle
+ satisfies $P_{n}^\odd(r, \lambda^\odd) = 0$
 \big[where $\lambda^\odd$ is the value of $\Lambda^\odd(\vx)$,
 and $\lambda^\odd = \pm\sqrt \lambda$\,\big],
-then $P^\odd_{n/2}(r, \sqrt \lambda) P^\odd_{n/2}(r, -\sqrt \lambda)$
+then $P^\odd_{n}(r, \sqrt \lambda) P^\odd_{n/2}(r, -\sqrt \lambda)$
 is a factor of $P_{n}(r, \lambda)$.
@@
 %
-Now the factor for 2-cycles (see \reftab{cubpolygen})
-  is
+The minimal polynomial of 2-cycles
   $P_2(r,\lambda) = -\big[(2r+3)^2 - \lambda\big]\,(\lambda + 2r^2-9)$,
-  whose first factor is indeed
+  indeed contains
   $P^\odd_1(r, \sqrt \lambda) \, P^\odd_1(r, -\sqrt \lambda)
-   = (\sqrt \lambda + 2 r + 3)(-\sqrt \lambda + 2 r + 3)$.
-%
-The example for $n=4$ is shown in \reftab{cubpolygen}.
+   = (\sqrt \lambda + 2 r + 3)(-\sqrt \lambda + 2 r + 3)$
+  as a factor.
 

### 2013-05-01 doc/pc.tex
doc: a simplified version

@@
   where $\vx \equiv \{x_1, \ldots, x_n\}$ and $n = 4$.
-Note that a cyclic polynomial is not necessarily from a symmetric one,
-  which is invariant under the exchange of any two $x_k$ and $x_{j}$ ($j \ne k$);
+Note that a cyclic polynomial is not necessarily symmetric
+  (i.e., invariant under the exchange of any two $x_k$ and $x_{j}$),
   e.g., $a(\vx)$ and $b(\vx)$ are not symmetric,
@@
 
-We now consider
-  a subset of \emph{square-free} cyclic polynomials,
-  which have no square or higher powers of any $x_k$,
+A cyclic polynomial is \emph{square-free}
+  if it has no square or higher powers of $x_k$,
 e.g., $C_{12}(\vx) = x_1 x_2 + \cdots$ is square-free,
@@
 We denote the set of all square-free $p$ by
-$\Bset = \{0, 1, 12, 13, \ldots, 123, 124, \ldots, 12\dots n\}$
-%  ($n \ge 4$),
-such that its size $|\Bset|$ equals the number $\NB$ of
+$\Pset = \{0, 1, 12, 13, \ldots, 123, 124, \ldots, 12\dots n\}$,
+and its size $|\Pset|$ equals the number $\NB$ of
   square-free cyclic polynomials.
@@
 
-We first show that
-  the square-free cyclic polynomials
-  serve as a basis for expanding cyclic polynomials:
+The set of square-free cyclic polynomials
+  furnishes a basis for expanding cyclic polynomials:
 
@@
 \end{equation}
-
-Now, for any $p$, $\Lambda(\vx) \, C_p(\vx)$
-  is also a cyclic polynomial,
-since the product of two cyclic polynomials is cyclic too.
-We can therefore expand it by \refthm{sqrfree} as
+%
+%
+Since $C_p(\vx)$ is also cyclic,
+  so is the product $\Lambda(\vx) \, C_p(\vx)$,
+  which can be expanded by \refthm{sqrfree} as
 \begin{equation}
-  \Lambda(\vx) \, C_p(\vx) = \sum_{q \in \Bset} T_{pq}(R) \, C_q(\vx),
+  \Lambda(\vx) \, C_p(\vx) = \sum_{q \in \Pset} T_{pq}(R) \, C_q(\vx),
 \label{eq:xcp0}
@@
 \begin{equation}
-  A_n\RX \equiv \Big| \lambda \, \vct I - \vct T(R) \Big| = 0.
+  A_n\Rlam \equiv \Big| \lambda \, \vct I - \vct T(R) \Big| = 0.
 \label{eq:xr}
 \end{equation}
-Here, $A_n\RX$ is a polynomial of $R$ and $\lambda$,
+Here, $A_n\Rlam$ is a polynomial of $R$ and $\lambda$,
   and the subscript $n$ is attached such that
-  it can be used later with $A_d\RX$ of divisors $d$ of $n$.
+  it can be used later with $A_d\Rlam$ of divisors $d$ of $n$.
 \refeq{xr} is a necessary condition
@@
 The fixed point begins at $\lambda = +1$ or $R_a = -1/4$,
-  and becomes impossible when $\lambda = -1$, or $R_b = 3/4$.
-
-For $n = 2$, the cyclic variables are
+  and becomes unstable when $\lambda = -1$, or $R_b = 3/4$.
+
+For $n = 2$, the cyclic polynomials are
 $C_0 = 1$,
@@
 
-For $n = 4$ \cite{stephenson}, the cyclic variables are
+For $n = 4$ \cite{stephenson, bailey1, kk1, bailey2, lewis},
+the cyclic polynomials are
 $C_0 = 1$,
@@
 $C_{13} = x_1 x_3 + x_2 x_4$,
-$C_{123} = x_1 x_2 x_3 + x_2 x_3 x_4 + x_3 x_4 x_1 + x_4 x_1 x_2$
-$C_{1234} = x_1 x_2 x_3 x_4$,
+$C_{123} = x_1 x_2 x_3 + x_2 x_3 x_4 + x_3 x_4 x_1 + x_4 x_1 x_2$,
+$C_{1234} = x_1 x_2 x_3 x_4$;
 and
@@
   \caption{
-  Characteristic polynomials $A_n\RX$ of
+  Characteristic polynomials $A_n\Rlam$ of
   the fixed points of $f^n$ of
@@
 %
-For complex $R$, $\lambda$, and $\vx$,
-the method can also compute the region of stability for $R$,
-with $\lambda$ being $\exp(i\theta)$ \big[$\theta \in (0, 2\pi)$\big]
-  instead of $\pm1$;
-the results are shown in \reffig{logbulb}
-for $n$ up to $8$.
-%
-For polynomials of larger $n$, see the website in \refsec{end}.
+For polynomials of larger $n$ are saved in in the website in \refsec{end}.
+%
 The representative $r$ values are listed in \reftab{rval}.
+%
+With $\lambda$ set to $\exp(i\theta)$, $\theta \in (0, 2\pi)$,
+  in place of $\pm1$,
+  the method computes the boundaries of a complex $R$
+  for complex cycles.
+This is equivalent to the inverted Mandelbrot set:
+  with $z_k = -x_k, c = -R$, we recover
+  the quadratic map $z_{k+1} = c + {z_k}^2$
+  used in the Mandelbrot set.
 
@@
 %
-  because $A_n\RX$,
+  because $A_n\Rlam$,
   from the characteristic equation \refeq{xr},
@@
 \begin{theorem}
-  The minimal polynomial $P_n\RX$ of all $n$-cycles
-  is a factor of $A_n\RX$ [defined in \refeq{xr}],
+  The minimal polynomial $P_n\Rlam$ of all $n$-cycles
+  is a factor of $A_n\Rlam$ [defined in \refeq{xr}],
   and can be computed as
   \begin{equation}
-    P_n\RX
-    = \prod_{cd = n} B_{d,c}\RX^{\mu(c)},
+    P_n\Rlam
+    = \prod_{cd = n} B_{d,c}\Rlam^{\mu(c)},
   \label{eq:primfac}
@@
 \begin{remark}[2]
-$B_{d,c}\RX$ is a polynomial of $\lambda$.
+$B_{d,c}\Rlam$ is a polynomial of $\lambda$.
 Despite the argument $\lambda^{1/c}$,
@@
   for it is invariant under $\lambda \rightarrow e^{2\pi i} \lambda$;
-and $\deg_\lambda B_{d,c}\RX = \deg_\lambda A_d\RX$.
-Particularly, $B_{n,1}\RX = A_n\RX$.
+and $\deg_\lambda B_{d,c}\Rlam = \deg_\lambda A_d\Rlam$.
+Particularly, $B_{n,1}\Rlam = A_n\Rlam$.
 \end{remark}
 
-%We will refer to $P_n\RX$ as the \emph{primitive factor} below.
+%We will refer to $P_n\Rlam$ as the \emph{primitive factor} below.
 
@@
 in \refeq{xr1} and
-$P_1\RX = B_{1,1}\RX = A_1\RX = \lambda^2 - 2\lambda - 4R$.
+$P_1\Rlam = B_{1,1}\Rlam = A_1\Rlam = \lambda^2 - 2\lambda - 4R$.
 
 For $n = 2$, since
-$B_{1,2}\RX
+$B_{1,2}\Rlam
 =
@@
 %
-$P_2\RX = A_2\RX \, B_{1,2}\RX^{-1} = 4R - 4 + \lambda$.
+$P_2\Rlam = A_2\Rlam \, B_{1,2}\Rlam^{-1} = 4R - 4 + \lambda$.
 
@@
 one can verify that
-$B_{1,3}\RX
+$B_{1,3}\Rlam
 = \prod_{k=1}^3 A_1(R, e^{2k\pi i/3} \, \sqrt[3]{\lambda})
@@
 So
-$P_3\RX = A_3\RX \, B_{1,3}\RX^{-1}
+$P_3\Rlam = A_3\Rlam \, B_{1,3}\Rlam^{-1}
 = -\big[64 R^3- 128 R^2 -8(\lambda -8)R-(\lambda-8)^2\big]$.
@@
 can be written as
-$B_{2,2}\RX = \prod_{k=1}^2 A_2(R, e^{k \pi i} \sqrt{\lambda})$,
+$B_{2,2}\Rlam = \prod_{k=1}^2 A_2(R, e^{k \pi i} \sqrt{\lambda})$,
 and
 %
-$P_4\RX
-    = A_4\RX \, B_{2,2}\RX^{-1}
+$P_4\Rlam
+    = A_4\Rlam \, B_{2,2}\Rlam^{-1}
     = 4096 R^6-12288 R^5+ 256 (\lambda + 48) (R^4- R^3)
     -16(\lambda + 32)(\lambda - 16) R^2 - (\lambda-16)^3$.
-Note, $B_{1,4}\RX$ is unused for $\mu(4) = 0$.
+Note, $B_{1,4}\Rlam$ is unused for $\mu(4) = 0$.
 
@@
 For $n \ge 4$,
-  $P_n\RX$ is readily recognized as
+  $P_n\Rlam$ is readily recognized as
   the factor
-  of $A_n\RX$
+  of $A_n\Rlam$
   with the highest degree in $R$,
@@
 %
-We then weight them by the Euler's totient function $\varphi(n/d)$.
+We then weight them by Euler's totient function $\varphi(n/d)$.
 %
@@
 \begin{theorem}
-The number $\NB(n)$ of the square-free cyclic polynomials $C_p(\vx)$ ($p \in \Bset$)
+The number $\NB(n)$ of the square-free cyclic polynomials $C_p(\vx)$ ($p \in \Pset$)
   formed by $\vx = \{x_1, \ldots, x_n\}$ is
@@
 %
-which is also equal to $\deg_\lambda A_n\RX$.
+which is also equal to $\deg_\lambda A_n\Rlam$.
 \label{thm:necklace}
@@
 \begin{equation}
-  \deg_\lambda P_n\RX = L(n) = (1/n)\sum_{d | n} \mu(n/d) 2^{\,d}.
+  \deg_\lambda P_n\Rlam = L(n) = (1/n)\sum_{d | n} \mu(n/d) 2^{\,d}.
 \label{eq:lyndon}
@@
 If we assume that $\lambda_c$ are distinct (see Remark 1 below),
-  then the minimal polynomial $P_n\RX$,
+  then the minimal polynomial $P_n\Rlam$,
   as a polynomial of $\lambda$,
   takes the form of $\prod_c (\lambda - \lambda_c)$.
-Thus, the degree of $P_n\RX$ in $\lambda$
+Thus, the degree of $P_n\Rlam$ in $\lambda$
   must be the same as the number of the $n$-cycles.
@@
 
-\subsubsection{Relation between $P_n\RX$ and $A_n\RX$}
+\subsubsection{Relation between $P_n\Rlam$ and $A_n\Rlam$}
 
 \begin{theorem}
-The minimal polynomials $P_d\RX$ of all $d$-cycles
+The minimal polynomials $P_d\Rlam$ of all $d$-cycles
   of periods $d|n$
-and $A_n\RX$ [defined in \refeq{xr}] are related by
+and $A_n\Rlam$ [defined in \refeq{xr}] are related by
   \begin{equation}
-    A_n\RX = \prod_{cd = n} Q_{d, c}\RX,
+    A_n\Rlam = \prod_{cd = n} Q_{d, c}\Rlam,
     \label{eq:prod}
@@
 \begin{align*}
- B_{n, m} \RX
+ B_{n, m} \Rlam
  & = \prod_{l = 1}^{m} A_n(R, e^{2l\pi i/m} \lambda^{1/m}) \\
@@
  & = \prod_{c | n} \prod_{k'=1}^{m c} P_{n/c}(R, e^{2k'\pi i/(m c)} \lambda^{1/(m c)})
-  = \prod_{c | n} Q_{n /c, m c}\RX.
+  = \prod_{c | n} Q_{n /c, m c}\Rlam.
 \end{align*}
@@
 \begin{equation}
-  Q_{n, m}\RX
-= \prod_{d|n} B_{d, m n/d}\RX^{\mu(n/d)},
+  Q_{n, m}\Rlam
+= \prod_{d|n} B_{d, m n/d}\Rlam^{\mu(n/d)},
 \tag{$\ref{eq:primfac}'$}
@@
 which is reduced to \refeq{primfac} with $m = 1$
-for $Q_{n, 1}\RX = P_n\RX$.
+for $Q_{n, 1}\Rlam = P_n\Rlam$.
 
@@
   and a shorter $d$-cycle ($d|n$, $d < n$)
-  forces the two to share orbits
+  forces the two to share orbit
   (this cannot happen if $d \centernot| n$,
@@
 Consequently, upon the intersection,
-  $P_n\RX$ from the $n$-cycle
+  $P_n\Rlam$ from the $n$-cycle
   has to accommodate $P_d(R, \lambda')$ from the $d$-cycle,
@@
 
-We will show below that such branching generally can only happen
+We will show below that such branching can only happen
   at the onset of the $n$-cycle, where $\lambda = 1$.
@@
 \begin{theorem}
-  The original factor $S_n(R)$ of $P_n\RX$ at the onset is given by
+  The original factor $S_n(R)$ of $P_n\Rlam$ at the onset is given by
   \begin{equation}
@@
 
-By \refthm{cbifur}, $P_n\RX$ at the onset point
+By \refthm{cbifur}, $P_n\Rlam$ at the onset point
 includes $P_d(R, e^{2 k \pi i/c} \lambda^{1/c})$ for every
@@
 %
-Dividing the factors from $P_n\RX$ yields \refthm{origfac}.
+Dividing the factors from $P_n\Rlam$ yields \refthm{origfac}.
 
@@
 \begin{theorem}
-The degrees in $R$ of $A_n\RX$, $P_n\RX$ and $S_n(R)$ are
+The degrees in $R$ of $A_n\Rlam$, $P_n\Rlam$ and $S_n(R)$ are
 \begin{subequations}
 \begin{align}
-\deg_R A_n\RX &= \sum_{d|n} \varphi(n/d) 2^{d-1}, \\
-\deg_R P_n\RX &= \sum_{d|n} \mu(n/d) 2^{d-1} \equiv \beta(n), \\
+\deg_R A_n\Rlam &= \sum_{d|n} \varphi(n/d) 2^{d-1}, \\
+\deg_R P_n\Rlam &= \sum_{d|n} \mu(n/d) 2^{d-1} \equiv \beta(n), \\
 \deg S_n(R) &= \beta(n) - \sum_{d | n, d < n} \beta(d) \, \varphi(n/d).
@@
 The eigenvalue $\lambda$ of the composite Jacobian
-$J_b(x_1) \cdots J_b(x_n)$ can be computed from
+$\vct J_b(x_1) \cdots \vct J_b(x_n)$ can be computed from
 %
 \begin{equation}
-\big|\, \lambda \, \vct I - J_b(x_1) \cdots J_b(x_n) \,\big|
+\big|\, \lambda \, \vct I - \vct J_b(x_1) \cdots \vct J_b(x_n) \,\big|
   = \lambda^2 - \Theta(\vx) \,\lambda +(-b)^n = 0,
@@
 are the trace and determinant of
-the matrix product $J_b(x_1) \cdots J_b(x_n)$,
+the product matrix $J_b(x_1) \cdots J_b(x_n)$,
 respectively \cite{hitzl}.
@@
 \[
-  K(\vx) = \sum_{p \in \Bset} f_p(R) C_p(\vx),
+  K(\vx) = \sum_{p \in \Pset} f_p(R) C_p(\vx),
 \]
-  where $\Bset = \{0, 11, 12, 13, \ldots, 1122, 1123, \ldots \}$ is
+  where $\Pset = \{0, 11, 12, 13, \ldots, 1122, 1123, \ldots \}$ is
   the set of indices of all even cube-free cyclic polynomials,

### 2013-05-02 doc/pc-ijbc.tex
doc: edited the henon map section

@@
 \newcommand{\vx}{\vct x}
+\newcommand{\Tr}{\mathrm{Tr}}
 % basis set of cyclic polynomials
@@
 
-A natural two-dimensional extension of the logistic map
+A simple two-dimensional extension of the logistic map
   is the H\'enon map \cite{henon}:
@@
 %
-We change variable $x_k \leftarrow a x_k$, $y_k \leftarrow a y_k$, and
+By a change of variables
+  $x_k^\mathrm{new} \equiv a \, x_k^\mathrm{old},
+   y_k^\mathrm{new} \equiv a \, y_k^\mathrm{old}$,
+we have, in terms of the new variables,
 \begin{equation}
@@
 %
-Since neither $a$ nor $b$ is changed during the transformation,
+%Since neither $a$ nor $b$ is changed during the transformation,
 \refeq{henon} and \refeq{henons} share the
@@
 %
-We also see that if $b \rightarrow 0$ and $a \rightarrow R$,
+With $b \rightarrow 0$ and $a \rightarrow R$,
 \refeq{henons} is reduced to the logistic map \refeq{logmaps}.
 
-Since $y_k = b \, x_{k-1}$, we can ignore $y_k$ and work with
-  cyclic polynomials of $x_k$ only,
-the square free reduction is now
+The second equation of \refeq{henons}
+allows us to replace $y_k$ by $b \, x_{k-1}$,
+  such that we can work with the cyclic polynomials of $x_k$ only.
+The square-free reduction is now
   ${x_k}^2 \rightarrow a + b x_{k-1} - x_{k+1}$.
 
-The stability of \refeq{henons} can be found from the Jacobian matrix
+The counterpart of \refeq{der}
+  can be found from the Jacobian of $n$th iterate of \refeq{henons}
 \[
-  \vct J_b(x_k)
-  \equiv \left(
+  \vct J^n
+  \equiv
+  \left(
     \begin{array}{ccc}
-      \partial x_{k+1}/\partial x_k & \partial x_{k+1}/\partial y_k \\
-      \partial y_{k+1}/\partial x_k & \partial y_{k+1}/\partial y_k \\
+      \partial x_{n+1}/\partial x_1 & \partial x_{n+1}/\partial y_1 \\
+      \partial y_{n+1}/\partial x_1 & \partial y_{n+1}/\partial y_1 \\
     \end{array}
-  \right)
+  \right),
+\]
+and the magnitude of both eigenvalues of the matrix must be less than 1.
+By the chain rule, we have
+  $\vct J^n (x_1) = \vct J^1(x_1) \cdots \vct J^1(x_n)$,
+  where
+$\vct J^1(x_k)
   =
   \left(
-    \begin{array}{ccc}
+    \begin{array}{cc}
       -2 x_k & 1 \\
@@
     \end{array}
-  \right).
-\]
-The eigenvalue $\lambda$ of the composite Jacobian
-$\vct J_b(x_1) \cdots \vct J_b(x_n)$ can be computed from
-%
-\begin{equation}
-\big|\, \lambda \, \vct I - \vct J_b(x_1) \cdots \vct J_b(x_n) \,\big|
+  \right)$.
+Thus, the eigenvalues $\lambda$ of $\vct J^n$ can be found from
+%
+\begin{equation}
+\big|\, \lambda \, \vct I - \vct J^n(x_1) \,\big|
   = \lambda^2 - \Theta(\vx) \,\lambda +(-b)^n = 0,
@@
 where $\Theta(\vx)$ and $(-b)^n$
-are the trace and determinant of
-the product matrix $\vct J_b(x_1) \cdots \vct J_b(x_n)$,
+  are the trace and determinant of $\vct J^n(x_1)$,
   respectively \cite{hitzl}.
-In a stable cycle, the magnitude of $\lambda$
-cannot exceed 1; and $\lambda = +1$ or $-1$
-in \refeq{henonder} corresponds to
-the onset or bifurcation point, respectively.
-\refeq{henonder} is the counterpart of \refeq{der}.
-
-Since the trace of the product of two matrices is
-  independent of the order,
-$\Theta(\vx)$ must a cyclic polynomial of $\vx = \{ x_k \}$.
-%
-Thus, we can use $\Theta(\vx)$ to list \refeqs{xcp}
+The onset and bifurcation points
+  correspond to $\lambda = +1$ and $-1$, respectively
+
+Using the matrix identity $\Tr( \vct A \vct B) = \Tr(\vct B \vct A)$,
+  we have
+    $\Tr \, \vct J^n(x_1) = \cdots = \Tr \, \vct J^n(x_n)$,
+i.e., $\Theta(\vx)$ is a cyclic polynomial of $\vx = \{ x_k \}$.
+%e.g., %$\Theta(\vx) = 4 x_1 x_2 + 2 \, b$ for $n = 2$ and
+%$\Theta(\vx) = -8 x_1 x_2 x_3 - 2 \, b (x_1+ x_2+ x_3)$ for $n = 3$.
+%
+Thus, we can expand $\Theta(\vx) \, C_p(\vx)$
+  in terms of square-free cyclic polynomials,
   and then replace $\Theta(\vx)$ by $\lambda + (-b)^n/\lambda$
-or $\pm\big[ 1 + (-b)^n \big]$
-in \refeq{xr} to complete the solution.
+  in the final characteristic equation to obtain the desired polynomials
+  (the procedure is similar to that in \refsec{algo} for the logistic map).
 %
@@
 %
-%Thus we only need polynomials of even degrees.
+%Thus, we only need polynomials of even degrees.
 %

### 2013-05-02 doc/pc.tex
doc: edited the henon map section

@@
 
-We now extend the method to the H\'enon map \cite{henon}:
+A simple two-dimensional extension of the logistic map
+  is the H\'enon map \cite{henon}:
 \begin{equation}
@@
     \end{array}
-  \right).
-\]
-The eigenvalue $\lambda$ of the composite Jacobian
-$\vct J_b(x_1) \cdots \vct J_b(x_n)$ can be computed from
+  \right)$.
+Thus, the eigenvalues $\lambda$ of $\vct J^n$ can be found from
 %
 \begin{equation}
-\big|\, \lambda \, \vct I - \vct J_b(x_1) \cdots \vct J_b(x_n) \,\big|
+\big|\, \lambda \, \vct I - \vct J^n(x_1) \,\big|
   = \lambda^2 - \Theta(\vx) \,\lambda +(-b)^n = 0,
@@
 where $\Theta(\vx)$ and $(-b)^n$
-are the trace and determinant of
-the product matrix $J_b(x_1) \cdots J_b(x_n)$,
+  are the trace and determinant of $\vct J^n(x_1)$,
   respectively \cite{hitzl}.
-In a stable cycle, the magnitude of $\lambda$
-cannot exceed 1; so we replace $\lambda$ by $+1$ or $-1$
-in \refeq{henonder}
-to obtain the onset or bifurcation point, respectively.
-\refeq{henonder} is the counterpart of \refeq{der}.
-
-Since cyclically rotating matrices in a product does not alter the trace,
-$\Theta(\vx)$ is a cyclic polynomial of $\vx = \{ x_k \}$.
-%e.g.,
-%$\Theta(\vx) = 4 x_1 x_2 + 2 \, b$ for $n = 2$ and
+The onset and bifurcation points
+  correspond to $\lambda = +1$ and $-1$, respectively
+
+Using the matrix identity $\Tr( \vct A \vct B) = \Tr(\vct B \vct A)$,
+  we have
+    $\Tr \, \vct J^n(x_1) = \cdots = \Tr \, \vct J^n(x_n)$,
+i.e., $\Theta(\vx)$ is a cyclic polynomial of $\vx = \{ x_k \}$.
+%e.g., %$\Theta(\vx) = 4 x_1 x_2 + 2 \, b$ for $n = 2$ and
 %$\Theta(\vx) = -8 x_1 x_2 x_3 - 2 \, b (x_1+ x_2+ x_3)$ for $n = 3$.
 %
-Thus, we can use $\Theta(\vx)$ to list \refeqs{xcp}
+Thus, we can expand $\Theta(\vx) \, C_p(\vx)$
+  in terms of square-free cyclic polynomials,
   and then replace $\Theta(\vx)$ by $\lambda + (-b)^n/\lambda$
-or $\pm\big[ 1 + (-b)^n \big]$
-in \refeq{xr} to complete the solution.
+  in the final characteristic equation to obtain the desired polynomials
+  (the procedure is similar to that in \refsec{algo} for the logistic map).
+%
+%
+%
+%The polynomials of $a$ and $b$
+%  at the onset and bifurcation points for $n$ up to 9
+%  are listed in the website in \refsec{end}.
+
+We computed the polynomials of $a$ and $b$
+  at the onset and bifurcation points for $n$ up to 9.
+The polynomials of $a$ and $b$
+  at the onset and bifurcation points,
+  as well as $\Theta(\vx)$,
+  are listed in \reftab{henonpoly} for small $n$
+(for larger $n$, see the website in \refsec{end}).
 
@@
 
-We computed the polynomials of $a$ and $b$
-  at the onset and bifurcation points for $n$ up to 9.
-The polynomials of $a$ and $b$
-  at the onset and bifurcation points,
-  as well as $\Theta(\vx)$,
-  are listed in \reftab{henonpoly} for small $n$
-(for larger $n$, see the website in \refsec{end}).
-
 \section{\label{sec:cubic}Cubic map}

### 2013-05-02 doc/pc-ijbc.tex
adjust to two-column format

@@
 
+\twocolumn
 %
@@
 %
-The iterated \refeq{logmap} sequence $x_1$,
+The iterated sequence $x_1$,
   $x_2 = f(x_1)$,
@@
   \begin{center}
-  \begin{minipage}{0.5 \linewidth}
+  \begin{minipage}{\linewidth}
         \includegraphics[angle=-90, width=\linewidth]{cobweb.pdf}
@@
 The square-free reduction is now
-  ${x_k}^2 \rightarrow a + b x_{k-1} - x_{k+1}$.
+  ${x_k}^2 \rightarrow a + b \, x_{k-1} - x_{k+1}$.
 
@@
   \begin{center}
-  \begin{minipage}{0.5 \linewidth}
+  \begin{minipage}{\linewidth}
         \includegraphics[angle=-90, width=\linewidth]{oddcycle.pdf}

### 2013-05-02 doc/pc.tex
adjust to two-column format

@@
-\documentclass[preprint]{revtex4-1}
+\documentclass[twocolumn]{revtex4-1}
 %\usepackage[width=5.65in, height=9.3in]{geometry}
@@
 \usepackage{graphicx}
+%\usepackage{times}
 %\usepackage{setspace}
@@
 
-\begin{table}[h]\footnotesize
+\begin{table*}[t]\footnotesize
 \caption{Square-free cyclic polynomials $C_p(\vx)$ for the logistic map ($n \ge 5$).}
@@
 \label{tab:sqrfreepoly}
-\end{table}
+\end{table*}
 
@@
 %
+\footnotesize
 \begin{align*}
@@
 \end{align*}
+\normalsize
 %
@@
 and \refeq{xr} reads:
+%
 \begin{align}
@@
   64R^3 - 128 R^2 - 8 (\lambda - 8) R - (\lambda -8)^2
-  \big]
+  \big] \notag \\
+&\qquad
   \big(
@@
 %
+\begin{widetext}
+%\footnotesize
 \begin{align}
@@
 \end{align}
+%\normalsize
+\end{widetext}
 %
@@
 
-\begin{table}[h]\footnotesize
+\begin{table*}[t]\footnotesize
   \caption{
@@
 \label{tab:Anlog}
-\end{table}
+\end{table*}
 
@@
 \label{tab:rval}
-\end{table}
+\end{table*}
 
@@
 \label{tab:Pnlog}
-\end{table}
+\end{table*}
 
@@
     \begin{center}
-        \includegraphics[angle=-90, width=.67\linewidth]{logbulb.pdf}
+        \includegraphics[angle=-90, width=\linewidth]{logbulb.pdf}
     \end{center}
@@
 
-\begin{table}[h]\footnotesize
+\begin{table*}[t]\footnotesize
 \caption{Two ways of counting the $N(4) = 6$ necklaces for $n = 4$.
@@
 \label{tab:countnecklace}
-\end{table}
+\end{table*}
 
@@
 \sum_{d | n} L(d)
-  &= \sum_{d | n} (1/d) \sum_{c |  d} \mu(d/c) 2^{\,c}
-   = (1/n) \sum_{c | n} 2^{\,c} \sum_{d'  |  (n/c)}
+  &= \sum_{d | n} (1/d) \sum_{c |  d} \mu(d/c) 2^{\,c} \\
+  &= (1/n) \sum_{c | n} 2^{\,c} \sum_{d'  |  (n/c)}
         \mu\left(\frac{n/c}{d'}\right) d' \\
@@
  & = \prod_{c | n} \prod_{l=1}^m \prod_{k=1}^c P_{n/c}(R, e^{2k\pi i/c + 2l\pi i/(m c)} \lambda^{1/(m c)}) \\
- & = \prod_{c | n} \prod_{k'=1}^{m c} P_{n/c}(R, e^{2k'\pi i/(m c)} \lambda^{1/(m c)})
-  = \prod_{c | n} Q_{n /c, m c}\Rlam.
+ & = \prod_{c | n} \prod_{k'=1}^{m c} P_{n/c}(R, e^{2k'\pi i/(m c)} \lambda^{1/(m c)}) \\
+ & = \prod_{c | n} Q_{n /c, m c}\Rlam.
 \end{align*}
@@
   \deg_R T_{pq}(R)
-  = \max\{ \deg_R t(R, \vx) \}
-  = \max\{ l_1 \}
-  \le   (n + |p| - |q|)/2,
+  &= \max\{ \deg_R t(R, \vx) \}
+  = \max\{ l_1 \} \\
+  &\le   (n + |p| - |q|)/2,
 \end{align*}
@@
   \deg_R A_n\Rlam
-  = \max \sum_{p \in \Pset} \deg T_{pq}(R)
-  \le N(n) \, \big(n + |p| - |q|\big)/2 = n N(n)/2,
+  &= \max \sum_{p \in \Pset} \deg T_{pq}(R) \\
+  &\le N(n) \, \big(n + |p| - |q|\big)/2
+  = n N(n)/2,
 \end{align*}
@@
 
-\begin{table}[h]\footnotesize
+\begin{table*}[t]\footnotesize
 \caption{Onset and bifurcation polynomials of the $n$-cycles of the H\'enon map.}
@@
 \label{tab:henonpoly}
-\end{table}
+\end{table*}
 
@@
 \label{tab:cubpolygen}
-\end{table}
-
-\begin{table}[h]\footnotesize
+\end{table*}
+
+\begin{table*}[t]\footnotesize
 \caption{Onset and bifurcation polynomials of the $n$-cycles of the cubic map \refeq{cubic}.}
@@
 \label{tab:cubpoly}
-\end{table}
-
-\begin{table}[h]\footnotesize
+\end{table*}
+
+\begin{table*}[t]\footnotesize
   \caption{
@@
 \label{tab:crval}
-\end{table}
+\end{table*}
 
@@
 
-\begin{table}[h]\footnotesize
+\begin{table*}[t]\footnotesize
 \caption{Two ways of counting the $N_e(2) = 4$ ternary necklaces for $n = 2$.
@@
 \label{tab:countcubnecklace}
-\end{table}
+\end{table*}
 
@@
     $A_n(R, \lambda) \rightarrow A_n(r, \lambda)$,
-    etc.\big].
+    etc.\big]
 The degree of the polynomial is given by
@@
 \begin{center}
-\begin{tabularx}{\textwidth}{
-  >{\hsize=0.6\hsize\raggedleft\arraybackslash}X
-  >{\hsize=1.4\hsize\centering\arraybackslash}X
-  >{\hsize=0.6\hsize\raggedleft\arraybackslash}X
-  >{\hsize=1.4\hsize\centering\arraybackslash}X
-}
-\hline
-$\alpha(n)$   &   $G_\alpha(s) = \sum_{n} \alpha(n)/n^{s}$  &
+\begin{tabular}{ll}
+\hline
 $\alpha(n)$   &   $G_\alpha(s) = \sum_{n} \alpha(n)/n^{s}$
@@
 \hline
-1             & $\zeta(s)$ $^\dagger$ &
-\multicolumn{1}{|r}
-{$N_e(n)$}      & $G_N(s)$ $^\ddagger$
-\\
-$\delta_{n,1}$         & $1$ $^\dagger$ &
-\multicolumn{1}{|r}
-{$n N_e(n)$}  & $G_N(s-1)$ $^\ddagger$
-\\
-$\mu(n)$    & $\zeta(s)^{-1}$ $^\dagger$ &
-\multicolumn{1}{|r}
-{$L_e(n)$}    & $G_L(s)$ $^\ddagger$
-\\
-$\varphi(n)$   & $\zeta(s-1)/\zeta(s)$ $^\dagger$ &
-\multicolumn{1}{|r}
-{$nL_e(n)$}   & $G_L(s-1)$ $^\ddagger$
-\\
-$\odd(n)$   & $\zeta(s) (1-2^{-s})$ &
-\multicolumn{1}{|r}
-{$3^n$}       & $t(s)$ $^\ddagger$
-\\
-\cline{3-4}
+1
+% add some spaces
+\qquad \qquad \qquad \qquad \qquad \qquad \qquad
+  & $\zeta(s)$ $^\dagger$
+\\
+$\delta_{n,1}$         & $1$ $^\dagger$
+\\
+$\mu(n)$    & $\zeta(s)^{-1}$ $^\dagger$ 
+\\
+$\varphi(n)$   & $\zeta(s-1)/\zeta(s)$ $^\dagger$ 
+\\
 $\mu(n) \, \odd(n)$
-  & $\Big[ \zeta(s) (1-2^{-s}) \Big]^{-1}$ &
+  & $\Big[ \zeta(s) (1-2^{-s}) \Big]^{-1}$
+\\
 $\varphi(n) \, \odd(n)$
@@
 \\
-\hline
-\multicolumn{4}{p{\linewidth}}{
+$\odd(n)$   & $\zeta(s) (1-2^{-s})$ 
+\\
+{$3^n$}       & $t(s)$ $^\ddagger$
+\\
+{$N_e(n)$}      & $G_N(s)$ $^\ddagger$
+\\
+{$n N_e(n)$}  & $G_N(s-1)$ $^\ddagger$
+\\
+$L_e(n)$    & $G_L(s)$ $^\ddagger$
+\\
+$nL_e(n)$   & $G_L(s-1)$ $^\ddagger$
+\\
+\hline
+\multicolumn{2}{p{\linewidth}}{
 $^\dagger$
@@
 }\\
-\multicolumn{4}{p{\linewidth}}{
+\multicolumn{2}{p{\linewidth}}{
 $^\ddagger$
@@
 \hline
-\end{tabularx}
+\end{tabular}
 \end{center}
@@
 %
+\footnotesize
 \[
@@
 \]
+\normalsize
 Comparing the two formulas yields
@@
   G_N(s - 1)
-    = G_\varphi(s) t(s)- G_{\varphi, \odd}(s) \frac{t(s)-\zeta(s)}{2}
-    =
+    &= G_\varphi(s) t(s)- G_{\varphi, \odd}(s) \frac{t(s)-\zeta(s)}{2} \\
+    &=
       \frac{\zeta(s-1) \Big[ t(s) + \zeta(s) \big( 1  - 2^{-s+1} \big) \Big]  }
@@
 \begin{align*}
-  G_L(s-1) = \frac{G_N(s - 1)}{\zeta(s-1)}
+  G_L(s-1)
+  & = \frac{G_N(s - 1)}{\zeta(s-1)}
   = 1
         + \frac{ t(s) - \zeta(s) }
-          {2 \, \zeta(s) \big(1 - 2^{-s}\big)}
-       = 1 + \frac{t(s) - \zeta(s)}{2} G_{\mu, \odd}(s).
+          {2 \, \zeta(s) \big(1 - 2^{-s}\big)} \\
+  &   = 1 + \frac{t(s) - \zeta(s)}{2} G_{\mu, \odd}(s).
 \end{align*}

### 2013-05-03 doc/pc-ijbc.tex
doc: polish the examples
one-column format for two tables

@@
 \big[the converse is, however, untrue, for a fixed point of $f^n$
-  can also be a fixed point of $f^d$ for a divisor $d$ of $dn$:
+  can also be a fixed point of $f^d$ for a divisor $d$ of $n$:
   if $f^d(x) = x$, then $f^n(x) = f^d(\cdots f^d(x)\cdots) = x$\big],
@@
   are lower-degree factors of the polynomials,
-  and can be readily removed
-  (\refsecs{primfac} and \ref{sec:degprimfac}).
+  and can be readily removed (\refsec{primfac}).
 
@@
 
-\subsection{\label{sec:algo}Algorithm for fixed points of $f^n$}
+\subsection{\label{sec:algo}Fixed points of $f^n$}
 
@@
   \Lambda(\vx)
-   = \frac{d}{dx}f^{n}(x_1)
-   = f'(x_n) \dots f'(x_1)
+   = f'(x_1) \dots f'(x_n)
    = (-2)^n x_1 \dots x_n.
@@
 Since $C_p(\vx)$ is also cyclic,
-  so is the product $\Lambda(\vx) \, C_p(\vx)$,
-  which can be expanded by \refthm{sqrfree} as
+  so is $\Lambda(\vx) \, C_p(\vx)$,
+The latter can be expanded by \refthm{sqrfree} as
 \begin{equation}
@@
 
-By \refeq{der}, at the onset or bifurcation point,
-  $\Lambda(\vx)$ is equal to a number
-  $\lambda = +1$ or $-1$, respectively;
+By \refeq{der},
+  $\Lambda(\vx)$ equals to $\lambda = +1$ or $-1$
+  at the onset or bifurcation point,
+  respectively;
   so \refeq{xcp0}
@@
 
-We illustrate the above algorithm by several small-$n$ cases.
+We illustrate the above algorithm on several small-$n$ cases.
 %
@@
   and $\Lambda = -2 \, x_1$
-Thus, $\Lambda \, C_0 = -2 \, C_1$,
-$\Lambda \, C_1 = -2 \, x_1^2 = -2 \, R + 2 x_1 = -2 \, R \, C_0 + 2 \, C_1$,
-or
+Thus,
+$\Lambda \, C_0 = -2 \, x_1$,
+$\Lambda \, C_1 = -2 \, x_1^2 = -2 \, R + 2  \, x_1$,
+and
 \[
-  \lambda
+  \Lambda
   \left( \begin{array}{c}
@@
   C_1
-  \end{array} \right),
+  \end{array} \right).
 \]
-and the characteristic equation (\ref{eq:xr}) reads
+With $\Lambda \rightarrow \lambda$, the characteristic equation (\ref{eq:xr}) reads
 \begin{equation}
@@
 \end{equation}
-Thus, the fixed point begins at $R_a = -1/4$ ($\lambda = +1$),
+Thus, $R = (\lambda^2 -2\lambda)/4$;
+  and the fixed point begins at $R_a = -1/4$ ($\lambda = +1$),
   and becomes unstable at $R_b = 3/4$ ($\lambda = -1$).
@@
 $C_{12} = x_1 x_2$;
-and $\Lambda = 4 x_1 x_2$.
+and $\Lambda = 4 \, x_1 x_2$.
 Thus,
@@
 $\Lambda \, C_1 = 4 \, {x_1}^2 \, x_2 + 4 \, x_1 \, {x_2}^2
-  = 4 \, R \, (x_1 + x_2) - 4 ({x_1}^2 + {x_2}^2)
-  = 4 \, R \, (x_1 + x_2) - 8 \, R + 4 \, (x_1 + x_2)
-  = 4 \, (R + 1) \, C_1 - 8 \, R \, C_0$,
+  = -8 \, R \, C_0 + 4 \, (R + 1) \, C_1$
+(see the example after \refthm{sqrfree}),
 $\Lambda \, C_{12}
-  = 4 \, (R-x_2)\, (R-x_1)
-  = 4\, R^2  \, C_0 - 4 \, R \, C_1 + 4 \, C_{12}$,
-or
+  = 4 \, (R - x_2) (R - x_1)$,
+and
 \[
-\lambda
+\Lambda
   \left( \begin{array}{c}
@@
   C_{12}
-  \end{array} \right),
+  \end{array} \right).
 \]
@@
 %
-and \refeq{xr} reads
+The characteristic equation \refeq{xr} reads
 %
@@
 %
-Setting the first factor (which is responsible for the 2-cycle,
-  while the second factor is for unstable fixed points, see later)
-  to zero yields $R = 1 - \lambda/4$;
+The first factor is responsible for the 2-cycle,
+  while the second factor is for unstable fixed points (see later).
+Setting the former to zero yields $R = 1 - \lambda/4$.
+So
 $\lambda = +1$ gives the onset value $R_a = 3/4$ ($r_a = 3$)
@@
 
-For $n = 3$ \cite{saha, bechhoefer, gordon, burm, zhang},
-%we have
+The $n = 3$ case has sparked several different 
+  elementary derivations \cite{saha, bechhoefer, gordon, burm, zhang}.
+For the current algorithm,
 the cyclic polynomials are
@@
 %
-%
-%
+\footnotesize
 \begin{align*}
-\lambda
+\Lambda
 \left( \begin{array}{c}
@@
   0
-= -\big[
+&= -\big[
   64R^3 - 128 R^2 - 8 (\lambda - 8) R - (\lambda -8)^2
-  \big]
+  \big] \notag \\
+&\qquad
   \big(
@@
 
-For $n = 4$ \cite{stephenson, bailey1, kk1, bailey2, lewis},
-we have six cyclic polynomials, and
+The $n = 4$ case was previously used
+as a test of several algorithms
+\cite{stephenson, bailey1, kk1, bailey2, lewis}.
 %$C_0 = 1$,
@@
 %
-\refeq{xr} reads
-%
+Here, we only list the final characteristic equation \eqref{eq:xr}
+after the square reduction (with six square-free cyclic polynomials):
+%
+\footnotesize
 \begin{align}
@@
     \big[
-    4096 R^6-12288 R^5 + 256 (\lambda + 48) (R^4- R^3)
+    4096 R^6-12288 R^5 + 256 (\lambda + 48) (R^4- R^3) \notag \\
+& \quad
     -16 (\lambda + 32)(\lambda - 16) R^2
-      -(\lambda - 16)^3 \big]  \nonumber \\
+      -(\lambda - 16)^3 \big] \notag \\
 & \quad
@@
 \end{align}
-%
-%
-%
-From the first factor, we have
+\normalsize
+%
+%
+%
+The first (sextic) factor, responsible for the 4-cycle,
+can be factorized as
 $ (
@@
 %
-At the bifurcation point, $\lambda = -1$, and
+At the bifurcation point ($\lambda = -1$), we have
 $4096 R^6 - 12288 R^5 + 12032 (R^4 - R^3)
@@
 %
-%
-%
 The only two positive roots $r_b \approx 3.9608$
-and $r_b' \approx 3.5441$
+and $r_b' \approx 3.5441$ of the sextic equation
 correspond to $r_a$ and $r_a'$ respectively.
 %
-A simple elementary derivation of the 4-cycle is
-presented in the Appendix.
+Since the 4-cycle problem were tackled mainly on computers
+  in the previous studies,
+  we also supply a compact elementary derivation
+  in the Appendix.
 
@@
 {
-\begin{tabular}{llllllll}
-%\begin{tabularx}{\textwidth}{
-%  >{\hsize=0.5\hsize\centering\arraybackslash}X
-%  >{\hsize=1.6\hsize}X
-%  >{\hsize=1.6\hsize}X
-%  >{\hsize=0.3\hsize\raggedright\arraybackslash}X |
+\begin{tabular}{llll}
+%\begin{tabularx}{\linewidth}{
 %  >{\hsize=0.5\hsize\centering\arraybackslash}X
@@
 & Bifurcation$^\ddagger$
-& \#$^*$
-&
-  $n^\dagger$
-& Onset$^\ddagger$
-& Bifurcation$^\ddagger$
 & \#$^*$ \\
 \hline
-$1$     & $1.0000000000_1$      &  $3.0000000000_1$       & 1   &
+$1$     & $1.0000000000_1$      &  $3.0000000000_1$       & 1   \\
+$2'$    & $3.0000000000_1$      &  $3.4494897428_1$       & 1   \\
+$3$     & $3.8284271247_1$      &  $3.8414990075_3$       & 1   \\
+$4$     & $3.9601018827_3$      &  $3.9607686524_6$       & 1   \\
+$4''$   & $3.4494897428_1$      &  $3.5440903596_6$       & 1   \\
+$5$     & $3.7381723753_{11}$   &  $3.7411207566_{15}$    & 3   \\
+$6$     & $3.6265531617_{20}$   &  $3.6303887000_{27}$    & 4   \\
+$6'$    & $3.8414990075_{3}$    &  $3.8476106612_{27}$    & 1   \\
+$7$     & $3.7016407642_{57}$   &  $3.7021549282_{63}$    & 9   \\
+$8$     & $3.6621089132_{108}$  &  $3.6624407072_{120}$   & 14  \\
 $8'$    & $3.9607686524_{6}$    &  $3.9610986335_{120}$   & 1   \\
-$2'$    & $3.0000000000_1$      &  $3.4494897428_1$       & 1   &
 $8'''$  & $3.5440903596_{6}$    &  $3.5644072661_{120}$   & 1   \\
-$3$     & $3.8284271247_1$      &  $3.8414990075_3$       & 1   &
 $9$     & $3.6871968733_{240}$  &  $3.6872742105_{252}$   & 28  \\
-$4$     & $3.9601018827_3$      &  $3.9607686524_6$       & 1   &
 $10$    & $3.6052080669_{472}$  &  $3.6059169323_{495}$   & 48  \\
-$4''$   & $3.4494897428_1$      &  $3.5440903596_6$       & 1   &
 $10'$   & $3.7411207566_{15}$   &  $3.7425706462_{495}$   & 3   \\
-$5$     & $3.7381723753_{11}$   &  $3.7411207566_{15}$    & 3   &
 $11$    & $3.6817160194_{1013}$ &  $3.6817266457_{1023}$  & 93  \\
-$6$     & $3.6265531617_{20}$   &  $3.6303887000_{27}$    & 4   &
 $12$    & $3.5820230011_{1959}$ &  $3.5828117795_{2010}$  & 165 \\
-$6'$    & $3.8414990075_{3}$    &  $3.8476106612_{27}$    & 1   &
 $12'$   & $3.6303887000_{27}$   &  $3.6321857392_{2010}$  & 4   \\
-$7$     & $3.7016407642_{57}$   &  $3.7021549282_{63}$    & 9   &
 $12''$  & $3.8476106612_{27}$   &  $3.8490363152_{2010}$  & 1   \\
-$8$     & $3.6621089132_{108}$  &  $3.6624407072_{120}$   & 14  &
 $13$    & $3.6797024578_{4083}$ &  $3.6797038498_{4095}$  & 315 \\
 \hline
-\multicolumn{8}{p{\textwidth}}{
+\multicolumn{4}{p{\linewidth}}{
 $^\dagger$
   $\,'$, $\,''$, or $\,'''$ means
-    a cycle undergoing
+    that the cycle is undergoing
     the first, second, or third successive period-doubling, respectively.
 } \\
-\multicolumn{8}{p{\textwidth}}{
+\multicolumn{4}{p{\linewidth}}{
 $^\ddagger$
@@
 } \\
-\multicolumn{8}{p{\textwidth}}{
+\multicolumn{4}{p{\linewidth}}{
 $^*$
@@
 
-\subsection{\label{sec:primfac}Minimal polynomial for the $n$-cycles}
-
-The polynomial $A_n\Rlam$
-  of the characteristic equation \refeq{xr}
-  is derived for the fixed points of $f^n$,
-  and thus encompasses cycles of shorter periods $d$ ($d|n$) as well.
+\subsection{\label{sec:primfac}Minimal polynomial of the $n$-cycles}
+
+The characteristic polynomial $A_n\Rlam$ in \refeq{xr}
+  is derived for the fixed points of $f^n$.
+Thus, it encompasses not only the $n$-cycles,
+  but also cycles of shorter periods $d$ ($d|n$).
 %
@@
   The minimal polynomial $P_n\Rlam$ of all $n$-cycles
-  is a factor of $A_n\Rlam$ [defined in \refeq{xr}],
+  is a factor of the characteristic polynomial $A_n\Rlam$,
   and can be computed as
@@
 \end{theorem}
-
+%
+%
 %\begin{remark}[1]
@@
   or 0 if $n$ is divisible by a square of a prime.
-$\mu(n)$ = 1, $-1$, $-1$, 0, $-1$, 1, \ldots,
-  starting from $n = 1$.
+Thus, $\mu(n)$ = 1, $-1$, $-1$, 0, $-1$, 1, \ldots,
+  from $n = 1$.
 The $\mu(n)$ is useful for inversion:
@@
 \end{remark}
-
+%
+%
 %\begin{remark}[2]
 \begin{remark}
-$B_{d,c}\Rlam$ is a polynomial of $\lambda$.
+%$B_{d,c}\Rlam$ is a polynomial of $\lambda$.
 Despite the argument $\lambda^{1/c}$,
-  the product $\prod_{k=1}^c A_d(R, e^{2k\pi i/c} \lambda^{1/c})$
+  the product $\prod_{k=1}^c A_d(R, e^{2k\pi i/c} \lambda^{1/c})$,
+  hence $B_{d,c}\Rlam$,
   is free from radicals of powers of $\lambda^{1/c}$,
-  for it is invariant under $\lambda \rightarrow e^{2\pi i} \lambda$;
+  for it is invariant under $\lambda \rightarrow e^{2\pi i} \lambda$.
+Thus, $B_{d, c}\Rlam$ is a polynomial of $\lambda$,
 and $\deg_\lambda B_{d,c}\Rlam = \deg_\lambda A_d\Rlam$.
@@
 \end{remark}
-
+%
+%
 %We will refer to $P_n\Rlam$ as the \emph{primitive factor} below.
-
-Let us see some examples.
+%
+%
+Let us apply \refeq{primfac}
+to some examples in \refsec{examples}.
+We will omit the argument $R$ below for convenience.
 %%
@@
 %there is no irrelevant factor in \refeq{xr1} and
-$P_1\Rlam = B_{1,1}\Rlam = A_1\Rlam = \lambda^2 - 2\lambda - 4R$.
+$P_1(\lambda) = B_{1,1}(\lambda) = A_1(\lambda)
+  = \lambda^2 - 2\,\lambda - 4\,R$.
 %
@@
 For $n = 2$, since
-$B_{1,2}\Rlam
+$B_{1,2}(\lambda)
 =
-(\lambda +2\sqrt{\lambda} - 4R)
-\,
-(\lambda -2\sqrt{\lambda} - 4R)
-=(4R-\lambda)^2 -4\lambda$,
-%
-$P_2\Rlam = A_2\Rlam \, B_{1,2}\Rlam^{-1} = 4R - 4 + \lambda$.
+A_1(\sqrt{\lambda})
+A_1(-\sqrt{\lambda})
+=
+(4R-\lambda)^2 -4\lambda$,
+%
+$P_2(\lambda) = A_2(\lambda) \, B_{1,2}(\lambda)^{-1} = 4R - 4 + \lambda$.
 %
@@
 For $n = 4$,
-we have
-$16 (R-1)^2 - \lambda
-= (4R - 4 + \sqrt{\lambda})(4R - 4 - \sqrt{\lambda})$
+%we have
+%$16 (R-1)^2 - \lambda
+%= (4R - 4 + \sqrt{\lambda})(4R - 4 - \sqrt{\lambda})$
+%and
+%$
+%(16 R^2 + \lambda)^2 - 16 (2R+1)^2 \lambda
+%=
+%\big[(4R - \sqrt{\lambda})^2  - 4\sqrt{\lambda}\,\big]
+%\big[(4R + \sqrt{\lambda})^2  + 4\sqrt{\lambda}\,\big]$.
+%Thus, 
+we can show that
+the last two factors of \refeq{xr4}
+can be written as
+$B_{2,2}(\lambda) = A_2(\sqrt{\lambda}) A_2(-\sqrt{\lambda})$,
 and
-$
-(16 R^2 + \lambda)^2 - 16 (2R+1)^2 \lambda
-=
-\big[(4R - \sqrt{\lambda})^2  - 4\sqrt{\lambda}\,\big]
-\big[(4R + \sqrt{\lambda})^2  + 4\sqrt{\lambda}\,\big]$.
-Thus, the last two factors of \refeq{xr4}
-can be written as
-$B_{2,2}\Rlam = \prod_{k=1}^2 A_2(R, e^{k \pi i} \sqrt{\lambda})$,
-and
-%
-$P_4\Rlam
-    = A_4\Rlam \, B_{2,2}\Rlam^{-1}
-    = 4096 R^6-12288 R^5+ 256 (\lambda + 48) (R^4- R^3)
-    -16(\lambda + 32)(\lambda - 16) R^2 - (\lambda-16)^3$.
-Note, $B_{1,4}\Rlam$ is unused for $\mu(4) = 0$.
-
-\refthm{primfac} is not always necessary.
+%
+$P_4(\lambda)
+    = A_4(\lambda) \, B_{2,2}(\lambda)^{-1}$
+indeed the yields the sextic factor.
+%$    = 4096 R^6-12288 R^5+ 256 (\lambda + 48) (R^4- R^3)
+%    -16(\lambda + 32)(\lambda - 16) R^2 - (\lambda-16)^3$.
+Note, $B_{1,4}(\lambda)$ is unused for $\mu(4) = 0$.
+
 For $n \ge 4$,
-  $P_n\Rlam$ is readily recognized as
-  the factor
-  of $A_n\Rlam$
+  $P_n\Rlam$ can be easily recognized,
+  without using \refthm{primfac},
+  as the factor of $A_n\Rlam$
   with the highest degree in $R$.
@@
   the $k$th character from the left of the necklace is 1,
-  otherwise 0.
-For example, if $n = 3$,
- the square-free polynomials for $000$, $100$, $110$ and $111$ are
-  $C_0 = 1$ (generator: 1),
-  $C_1 = x_1 + x_2 + x_3$ (generator: $x_1$),
-  $C_{12} = x_1 x_2 + x_2 x_3 + x_3 x_1$ (generator: $x_1 x_2$)
-  and $C_{123} = x_1 x_2 x_3$ (generator: $x_1 x_2 x_3$), respectively.
+  otherwise 0,
+e.g. the above four necklaces correspond to
+  $C_0$, $C_1$, $C_{12}$ and $C_{123}$, respectively.
+%For example, if $n = 3$,
+% the square-free polynomials for $000$, $100$, $110$ and $111$ are
+%  $C_0 = 1$ (generator: 1),
+%  $C_1 = x_1 + x_2 + x_3$ (generator: $x_1$),
+%  $C_{12} = x_1 x_2 + x_2 x_3 + x_3 x_1$ (generator: $x_1 x_2$)
+%  and $C_{123} = x_1 x_2 x_3$ (generator: $x_1 x_2 x_3$), respectively.
 Thus,
@@
 \begin{equation}
-  \deg_\lambda A_n\Rlam = \NB(n) = N(n) = (1/n) \textstyle\sum_{d|n} \varphi(n/d) 2^{\,d}.
+  %\deg_\lambda A_n\Rlam = 
+  \NB(n) = N(n) = (1/n) \textstyle\sum_{d|n} \varphi(n/d) 2^{\,d}.
 \label{eq:necklace}
@@
   is equal to the number of the $n$-cycles,
-  and is given by
-\begin{equation}
-  \deg_\lambda P_n\Rlam = L(n) = (1/n)\textstyle\sum_{d | n} \mu(n/d) 2^{\,d}.
+  which is given by
+\begin{equation}
+  %\deg_\lambda P_n\Rlam = 
+  L(n) = (1/n)\textstyle\sum_{d | n} \mu(n/d) 2^{\,d}.
 \label{eq:lyndon}
@@
 \begin{proof}
-The number $L(n)$ of $n$-cycles is known \cite{hao, hao2, lutzky}.
-Denote by $\lambda_c$ the value $\Lambda(\vx^c)$
-  evaluated at the $c$th cycle points,
-  then the minimal polynomial $P_n\Rlam$
-  takes the form of $\prod_c (\lambda - \lambda_c)$.
-Thus, $\deg_\lambda P_n\Rlam$ must be the same as $L(n)$.
+Let $\lambda_c$ be the value of $\Lambda(\vx^c)$
+  evaluated at the $c$th orbit points $\vx^c$.
+The minimal polynomial $P_n\Rlam$
+  can be written as $\prod_c (\lambda - \lambda_c)$,
+  and $\deg_\lambda P_n\Rlam$ is the same as
+  the number $L(n)$ of $n$-cycles, which is known \cite{hao, hao2, lutzky}.
 \end{proof}
@@
 %
-For the first few values, we have $L(n)$ =
+The first few values of $L(n)$ are
 2, 1, 2, 3, 6, 9, 18, 30, 56, 99, 186, 335, 630, \ldots,
-starting from $n = 1$.
+from $n = 1$.
 %
@@
 
-\subsubsection{Relation between $P_n\Rlam$ and $A_n\Rlam$}
+\subsubsection{Relation between $P_n$ and $A_n$}
 
@@
 \refthm{primfac} is a corollary of \refthm{prod},
+%\footnotesize
 \begin{align*}
- B_{n, m} \Rlam
- & = \prod_{l = 1}^{m} A_n(R, e^{2l\pi i/m} \lambda^{1/m}) \\
- & = \prod_{c | n} \prod_{l=1}^m \prod_{k=1}^c P_{n/c}(R, e^{2k\pi i/c + 2l\pi i/(m c)} \lambda^{1/(m c)}) \\
- & = \prod_{c | n} \prod_{k'=1}^{m c} P_{n/c}(R, e^{2k'\pi i/(m c)} \lambda^{1/(m c)})
-  = \prod_{c | n} Q_{n /c, m c}\Rlam.
+ B_{n, m} (\lambda)
+ & = \prod_{l = 1}^{m} A_n(e^{2l\pi i/m} \lambda^{1/m}) \\
+ & = \prod_{c | n} \prod_{l=1}^m \prod_{k=1}^c 
+    P_{n/c}(e^{\frac{2k\pi i}{c} + \frac{2l\pi i}{m c}} \lambda^{1/(m c)}) \\
+ & = \prod_{c | n} \prod_{k'=1}^{m c}
+    P_{n/c}(e^{2k'\pi i/(m c)} \lambda^{1/(m c)}) \\
+ & = \prod_{c | n} Q_{n /c, m c}(\lambda).
 \end{align*}
+%\normalsize
 The M\"obious inversion yields
@@
 
-\subsection{\label{sec:origfac}Intersection of cycles
-  and further factorization at the onset point}
+\subsection{\label{sec:origfac}%Intersection of cycles and
+  Factors at the onset point}
 
@@
 {
-\begin{tabular}{l l l l l l l l}
+\begin{tabular}{l l l l}
 %\begin{tabularx}{\textwidth}{
-%  >{\hsize=0.5\hsize\centering\arraybackslash}X
-%  >{\hsize=1.6\hsize}X
-%  >{\hsize=1.6\hsize}X
-%  >{\hsize=0.3\hsize\raggedright\arraybackslash}X |
 %  >{\hsize=0.5\hsize\centering\arraybackslash}X
@@
 & Bifurcation$^\ddagger$
-& \#$^*$
-&
-%\hspace{2mm} & $\hspace{2mm}$ &
-  $n^\dagger$
-& Onset$^\ddagger$
-& Bifurcation$^\ddagger$
 & \#$^*$ \\
 \hline
-$1$     & $1.0000000000_1$      &  $2.0000000000_1$       & 2   &
+$1$     & $1.0000000000_1$      &  $2.0000000000_1$       & 2   \\
+$2'$    & $2.0000000000_1$      &  $2.2360679775_2$       & 2   \\
+$3$     & $2.4504409645_{8}$    &  $2.4608286739_{12}$    & 4   \\
+$4$     & $2.5478350393_{22}$   &  $2.5488312193_{32}$    & 8   \\
+$4''$   & $2.2360679775_{2}$    &  $2.2880317545_{32}$    & 2   \\
+$5$     & $2.3939250274_{112}$  &  $2.3957922744_{120}$   & 24  \\
 $6$     & $2.3334877526_{304}$  &  $2.3355337580_{336}$   & 56  \\
-$2'$    & $2.0000000000_1$      &  $2.2360679775_2$       & 2   &
 $6'$    & $2.4608286739_{12}$   &  $2.4657090579_{336}$   & 4   \\
-$3$     & $2.4504409645_{8}$    &  $2.4608286739_{12}$    & 4   &
 $7$     & $2.3729872678_{1080}$ &  $2.3732727868_{1092}$  & 156 \\
-$4$     & $2.5478350393_{22}$   &  $2.5488312193_{32}$    & 8   &
 $8$     & $2.3525990555_{3108}$ &  $2.3527637793_{3200}$  & 400 \\
-$4''$   & $2.2360679775_{2}$    &  $2.2880317545_{32}$    & 2   &
 $8'$    & $2.5488312193_{32}$   &  $2.5493247379_{3200}$  & 8   \\
-$5$     & $2.3939250274_{112}$  &  $2.3957922744_{120}$   & 24  &
 $8'''$  & $2.2880317545_{32}$   &  $2.2992279397_{3200}$  & 2   \\
 \hline
-\multicolumn{8}{p{\textwidth}}{
+\multicolumn{4}{p{\linewidth}}{
 $^\dagger$
-  $\,'$, $\,''$, or $\,'''$ means
-    a cycle under
+  $\,'$, $\,''$, or $\,'''$ means that the cycle is undergoing
     the first, second, or third successive period-doubling, respectively.
 } \\
-\multicolumn{8}{l}{
+\multicolumn{4}{p{\linewidth}}{
 $^\ddagger$
@@
 } \\
-\multicolumn{8}{l}{
+\multicolumn{4}{p{\linewidth}}{
 $^*$
@@
 
-\appendix{\label{apd:per4}Simple derivation of 4-cycles}
+\appendix{\label{apd:per4}Derivation of the 4-cycles}
 
@@
   + (1 - X)^3 = 0$,
-which is the same as the first factor of \refeq{xr4}
+which is the same as the sextic factor of \refeq{xr4}
   with $X = \lambda/16$.

### 2013-05-03 doc/pc.tex
doc: polish the examples
one-column format for two tables

@@
 
-\begin{table*}[t]\footnotesize
+\begin{table}[h]\footnotesize
   \caption{
@@
 \begin{center}
-\begin{tabularx}{\textwidth}{
-  >{\hsize=0.5\hsize\centering\arraybackslash}X
-  >{\hsize=1.6\hsize}X
-  >{\hsize=1.6\hsize}X
-  >{\hsize=0.3\hsize\raggedright\arraybackslash}X |
+%\begin{tabular}{llll}
+\begin{tabularx}{\linewidth}{
   >{\hsize=0.5\hsize\centering\arraybackslash}X
@@
 \end{tabularx}
+%\end{tabular}
 \end{center}
 \label{tab:rval}
-\end{table*}
+\end{table}
 
@@
 
-\refthm{primfac} is not always necessary.
 For $n \ge 4$,
-  $P_n\Rlam$ is readily recognized as
-  the factor
-  of $A_n\Rlam$
+  $P_n\Rlam$ can be easily recognized as
+  the factor of $A_n\Rlam$
   with the highest degree in $R$,
-  see \reftab{Anlog} and \refsec{degR}.
+  see \reftab{Anlog} and \refsec{degR},
+  without using \refthm{primfac}.
 It can be, however, problematic,
@@
 
-\begin{table*}[t]\footnotesize
+\begin{table}[h]\footnotesize
 \caption{
@@
 \begin{center}
-\begin{tabularx}{\textwidth}{
-  >{\hsize=0.5\hsize\centering\arraybackslash}X
-  >{\hsize=1.6\hsize}X
-  >{\hsize=1.6\hsize}X
-  >{\hsize=0.3\hsize\raggedright\arraybackslash}X |
+%\begin{tabular}{l l l l}
+\begin{tabularx}{\linewidth}{
   >{\hsize=0.5\hsize\centering\arraybackslash}X
@@
 \hline
+%\end{tabular}
 \end{tabularx}
@@
 \label{tab:crval}
-\end{table*}
+\end{table}
 
@@
 \begin{table}[h]\footnotesize
-  \caption{Dirichlet generating functions for ternary necklaces.}
+  \caption{Dirichlet generating functions.}
 \begin{center}

### 2013-05-03 doc/pc-ijbc.tex
small edits

@@
 \newcommand{\vx}{\vct x}
+\newcommand{\vxn}[1]{\vx^{(#1)}}
 \newcommand{\Tr}{\mathrm{Tr}}
@@
   \ldots, x_n \rightarrow x_1$,
-  e.g., $a(\vx) = x_1 x_2 + x_2 x_3 + x_3 x_4 + x_4 x_1$
-  and $b(\vx) = x_1 x_3 + x_2 x_4$,
-  where $\vx \equiv \{x_1, \ldots, x_n\}$ and $n = 4$.
+  e.g., $a = x_1 x_2 + x_2 x_3 + x_3 x_4 + x_4 x_1$
+  and $b = x_1 x_3 + x_2 x_4$ (for $n = 4$).
+%
 Note that a cyclic polynomial is not necessarily symmetric
   (i.e., invariant under the exchange of any two $x_k$ and $x_{j}$),
-  e.g., $a(\vx)$ and $b(\vx)$ are not symmetric,
-  but $a(\vx) + b(\vx)$ is.
+  e.g., $a$ and $b$ are not symmetric,
+  but $a + b$ is.
 
@@
 For example,
-$x_1 x_2$ is a generator of $a(\vx)$;
-$x_1 x_3$ is that of $b(\vx)$;
+$x_1 x_2$ is a generator of $a$;
+$x_1 x_3$ is that of $b$;
 and
-$x_1 x_2 + \frac{1}{2} x_1 x_3$ is that of $a(\vx) + b(\vx)$.
+$x_1 x_2 + \frac{1}{2} x_1 x_3$ is that of $a + b$.
 Note that the coefficient before $x_1 x_3$
@@
   for there are only two distinct versions,
-  but is $\frac{1}{2}$ in the third case
+  but $\frac{1}{2}$ in the third case
   for there are four. % distinct versions of the generator.
@@
   generated from monomials of unit coefficient
-  [such as $a(\vx)$ and $b(\vx)$, but not $a(\vx) + b(\vx)$]
+  (such as $a$ and $b$, but not $a + b$ in the above example)
   can be labeled as follows.
@@
   $e_1$ 1's, $e_2$ 2's, \ldots, $e_n$ $n$'s
-  serves as the label of the cyclic polynomial $C_p(\vx)$.
+  serves as the label of the cyclic polynomial $C_p(\vxn{n})$,
+  where $\vxn{n} \equiv \{x_1, \ldots, x_n\}$.
+We will, however, drop the superscript ``$^{(n)}$'' or
+  even the argument ``$(\vxn{n})$'' entirely when it is clear.
 For example,
@@
   $C_{112}(\vx) = {x_1}^2 x_2 + {x_2}^2 x_3 + \dots + {x_n}^2 x_1$.
-The cycle length $n$ is omitted for convenience.
+%The cycle length $n$ is omitted for convenience.
 %  for we will mostly work with a fixed $n$ at a time.
@@
   formed by the $n$-cycle points
-  $\vct x = \{x_1, \ldots, x_n\}$
+  $\vx = \{x_1, \ldots, x_n\}$
   is a linear combination of
@@
 \end{theorem}
-
+%
+%
 \begin{proof}
@@
 \end{proof}
-
-For example, for $n = 2$, the cyclic polynomial
-  $K(\vx) = {x_1}^2 \, x_2 + {x_2}^2 \, x_1$
-can be written as $K(\vx) = (R + 1) \, C_{1}(\vx) - 2 R \, C_0(\vx)$
+%
+%
+For example, the cyclic polynomial
+  $K(\vxn{2}) = {x_1}^2 \, x_2 + {x_2}^2 \, x_1$
+can be written as $K = (R + 1) \, C_{1} - 2 R \, C_0$
 for
@@
 Below we show that at the onset and bifurcation points,
-  the square-free cyclic polynomials $C_p(\vx)$ are themselves
+  the square-free cyclic polynomials $C_p$ are themselves
   linearly connected by $\NB$ homogeneous equations.
@@
 For $n = 1$, we have two square-free cyclic polynomials
-\big[omitting ``$(\vx)$''\big]
   $C_0 = 1$ and $C_1 = x_1$;
@@
 If an $n$-cycle is not born out of the above branching,
-  we call it an \emph{original} cycle,
+  we call it \emph{original}.
 The two types of cycles exist
@@
       \prod_{c d =  n, \; c > 1}
-      \left[ \,
+      %\left[ \,
         \prod_{(k, c) = 1}
@@
         \right)
-      \right]
+      %\right]
     },
@@
 Note $R_a' = 5/4$ is excluded from $S_4(R)$
-  as it comes from period-doubling the 2-cycle.
+  as it is due to period-doubling the 2-cycle.
 The two cycles are compared in \reffigs{cobweb}(d) and (e).

### 2013-05-03 doc/pc-ijbc.tex
edit introduction
improve the webpage

@@
   through a characteristic equation
-  connecting the cyclic polynomials of the periodic orbit points.
+  connecting the cyclic polynomials of the cycle points.
 The minimal polynomials of the critical parameters
@@
 %
-If $x_1$ deviates slightly from $x^*$
-  and the sequence still converges to $x^*$,
-  then it is \emph{stable}.
+It is stable if $x_1$ deviates slightly from $x^*$
+  and the sequence still converges to $x^*$.
 %
@@
 
-In an $n$-cycle, $n$ is the smallest positive integer
-  that allows $x_1 = x_{n+1} = f^n(x_1)$,
+An $n$-cycle is a sequence $x_1, \dots, x_n$,
+  such that $n$ is the smallest positive integer
+  that satisfies $x_1 = x_{n+1} = f^n(x_1)$,
   where $f^n$ is the $n$th iterate of $f$,
   e.g., $f^3(x) = f(f(f(x)))$.
-Thus, any $x_k$ in an $n$-cycle of $f$ must be a fixed point of $f^n$
-%
-\big[the converse is, however, untrue, for a fixed point of $f^n$
+Obviously, any $x_k$ in an $n$-cycle of $f$ is a fixed point of $f^n$
+%
+\big[but the converse is untrue, for a fixed point of $f^n$
   can also be a fixed point of $f^d$ for a divisor $d$ of $n$:
-  if $f^d(x) = x$, then $f^n(x) = f^d(\cdots f^d(x)\cdots) = x$\big],
-%
-%
-and a cycle can be classified as stable or unstable
+  if $f^d(x) = x$, then $f^n(x) = f^d(\cdots f^d(x)\cdots) = x$\big].
+%
+%
+Thus, a cycle can be classified as stable or unstable
   according to the corresponding fixed point of $f^n$:
@@
 \end{equation}
-The set of the $n$ points within the cycle $x_1. \ldots, x_n$
-   is called the \emph{orbit}.
+%
+%
 The onset and bifurcation points
@@
 %
-The orbit and cycle stability depend on the parameter $r$.
-%
-Below we will present an algorithm to identify
+The cycle and its stability depend on the parameter $r$.
+%
+Our purpose is to present an algorithm to identify
   all regions of $r$ that allow stable $n$-cycles.
@@
   the square-free cyclic polynomials $C_p(\vx)$
-  of the orbit points $\vx = \{x_k\}$
+  of the cycle points $\vx = \{x_k\}$
   are linear related by % \refeq{xcp},
@@
 The number $\NB(n)$ of the square-free cyclic polynomials $C_p(\vx)$
-  formed by the orbit points $\vx = \{x_1, \ldots, x_n\}$,
+  formed by the cycle points $\vx = \{x_1, \ldots, x_n\}$,
   which is also $\deg_\lambda A_n\Rlam$, is given by
@@
 Let $\lambda_c$ be the value of $\Lambda(\vx^c)$
-  evaluated at the $c$th orbit points $\vx^c$.
+  evaluated at the $c$th cycle.
 The minimal polynomial $P_n\Rlam$

### 2013-05-03 doc/pc.tex
edit introduction
improve the webpage

@@
 \end{equation}
-The set of the $n$ points within the cycle $x_1. \ldots, x_n$
-   is called the \emph{orbit}.
+%
+%
+%The set of the $n$ points within the cycle $x_1. \ldots, x_n$
+%   is called the \emph{orbit}.
 The onset and bifurcation points
@@
 %
-Below we will present an algorithm to identify
+Our purpose is to present an algorithm to identify
   all regions of $r$ that allow stable $n$-cycles.

### 2013-05-03 doc/pc-ijbc.tex
pc.tex: move binary necklace counting to appendix

@@
   can be labeled as follows.
-We first write the monomial generator as
+We write the monomial generator as
   ${x_1}^{e_1} {x_2}^{e_2} \dots {x_n}^{e_n}$,
-  then the sequence $p$ of indices with
-  $e_1$ 1's, $e_2$ 2's, \ldots, $e_n$ $n$'s
-  serves as the label of the cyclic polynomial $C_p(\vxn{n})$,
-  where $\vxn{n} \equiv \{x_1, \ldots, x_n\}$.
-We will, however, drop the superscript ``$^{(n)}$'' or
-  even the argument ``$(\vxn{n})$'' entirely when it is clear.
+  and form a sequence $p$ of indices with
+  $e_1$ 1's, $e_2$ 2's, \ldots, $e_n$ $n$'s.
+The sequence $p$ serves as the label of the cyclic polynomial $C_p(\vxn{n})$,
+  where $\vxn{n} \equiv \{x_1, \ldots, x_n\}$
+(we will, however, drop the superscript ``$^{(n)}$'' or
+  even the argument ``$(\vxn{n})$'' entirely when it is clear).
 For example,
@@
 The first factor is responsible for the 2-cycle,
-  while the second factor is for unstable fixed points (see later).
-Setting the former to zero yields $R = 1 - \lambda/4$.
-So
-$\lambda = +1$ gives the onset value $R_a = 3/4$ ($r_a = 3$)
-while
-$\lambda = -1$ gives the bifurcation value $R_b = 5/4$ ($r_b = 1+\sqrt 6$).
+  while the second factor is for unstable fixed points. % (see later).
+Setting the former to zero yields $R = 1 - \lambda/4$;
+so the onset ($\lambda = +1$) value is $R_a = 3/4$ ($r_a = 3$)
+and the bifurcation ($\lambda = -1$) value is $R_b = 5/4$ ($r_b = 1+\sqrt 6$).
 %
@@
 
-The $n = 3$ case has sparked several different
+The $n = 3$ case is nontrivial and has sparked several different
   elementary derivations \cite{saha, bechhoefer, gordon, burm, zhang}.
@@
 The first few values of $N_\Pset(n)$ are 2, 3, 4, 6, 8, 14, 20, 36, 60, 108, 188, 352, 632, \ldots,
-  starting from $n = 1$.
+  from $n = 1$.
 
@@
 %
-Since an $n$-necklace is either aperiodic or
+Since an $n$-necklace is either aperiodic itself or
   a repeated aperiodic $d$-necklace (with $d|n$),
@@
   with $(-1)^s$ being the proper sign.
+%
 Summing over rows under this condition yields

### 2013-05-03 doc/pc.tex
pc.tex: move binary necklace counting to appendix

@@
 
-The orbit and cycle stability depend on the parameter $r$.
+The cycle and its stability depend on the parameter $r$.
 %
@@
 
-To count the square-free cyclic polynomials,
-  we establish a one-to-one mapping
-  between the square-free cyclic polynomials
-  and the binary necklaces (defined below).
-The task is then to count the latter.
-
-A binary necklace
+From \refeq{xr}, it is clear that $\deg_\lambda A_n\Rlam$
+  is equal to the number of square cyclic polynomials $N_\Pset$.
+We show below that the latter
+  is equal to the number of binary necklaces (defined below),
+  which can be readily counted (\refapd{bnecklace}).
+
+A binary \emph{necklace}
   is a nonequivalent binary $0$-$1$ string.
 %
-Two strings are equivalent if they differ only by a circular shift.
-%
-For example, for $n = 3$, there are $2^3 = 8$ binary strings,
-but only four necklaces: 000, 001, 011 and 111,
+Two strings are \emph{equivalent} if they differ only by a circular shift.
+%
+For example, among the eight $n=3$ binary strings,
+the four 000, 001, 011 and 111 are necklaces,
 since 010 and 100 are equivalent to 001,
@@
 %
-The period of a necklace, or a binary string,
+The \emph{period} of a necklace, or a binary string,
   is the length of the shortest non-repeating sub-sequence,
@@
   and a period-$m$ necklace
-  encompasses $m$ binary strings
-  differed by circular shifts,
-  e.g., $0101$ represents
-  both $0101$ and $1010$.
-
-\begin{table*}[t]\footnotesize
-\caption{Two ways of counting the $N(4) = 6$ necklaces for $n = 4$.
-}
-\begin{center}
-\begin{tabularx}{\textwidth}{c | c  c | c | c | c | c | c }
-\hline
-        & \multicolumn{2}{c|}{$m = 1$}
-        & $m = 2$
-        & $m = 4$   & $2^d$ & $\varphi(n/d)$ & $\varphi(n/d) 2^d$\\
-\hline
-$d = 1$ & \hspace{1mm} $\mathbf{0}_{\times4}$ \hspace{1mm}
-        & \hspace{1mm} $\mathbf{1}_{\times4}$ \hspace{1mm} & & & $2 = 2$ & $2$ & 4 \\
-\hline
-$d = 2$ & $\mathbf{00}_{\times2}$ & $\mathbf{11}_{\times2}$
-        & \hspace{1mm} $\mathbf{10}_{\times2} (01_{\times2})$
-          \hspace{1mm} & & $2 + 2 =4$ & $1$ & 4 \\
-\hline
-\multirow{3}{*}{$d = 4$}
-      & & & & \hspace{1mm} $\mathbf{1000} (0100, 0010, 0001)$
-              \hspace{1mm} & $2 + 2 + 12$& \\
-      & $\mathbf{0000}$ & $\mathbf{1111}$ & $\mathbf{1010} (0101)$
-            & $\mathbf{1100} (1001, 0110, 0011)$ & $=16$ & $1$ & 16 \\
-      & & & &   $\mathbf{1110} (1101, 1011, 0111)$ & &  \\
-\hline
-$m \sum_{m|d, d|n} \varphi(\frac{n}{d})$
-      & \multicolumn{2}{c|}{$1\cdot(2+1+1) = 4$}
-      & $2\cdot(1+1) = 4$ & $4\cdot1 = 4$ &  \multicolumn{2}{c|}{} &  $\downarrow$\\
-\hline
-$N(n)\cdot n$ & \multicolumn{2}{c|}{$2 \cdot 4$} & $1 \cdot 4$ & $3 \cdot 4$ &
-  \multicolumn{2}{c|}{$\rightarrow$} & $6\cdot4 = 24$ \\
-\hline
-\multicolumn{8}{p{\linewidth}}{
-  Bold strings are necklaces; others are their cyclic versions.
-}
-\\
-\multicolumn{8}{p{\linewidth}}{
-The subscript of a binary string means the number of repeats;
-e.g.,
-$\mathbf{0}_{\times4}$ means $\mathbf{0}$ repeated four times, or $\mathbf{0000}$;
-$\mathbf{10}_{\times2}$ means $\mathbf{10}$ repeated twice, or $\mathbf{1010}$, etc.
-}
-\\
-\hline
-\end{tabularx}
-\end{center}
-\label{tab:countnecklace}
-\end{table*}
-
-To compute the number of the binary necklaces $N(n)$,
-we construct a sum for the length-$n$ binary strings and count it in two ways.
-\reftab{countnecklace} shows the example for the $n=4$ case.
-%
-For each divisor $d$ of $n$, we collect
-  all length-$n$ binary strings
-  whose periods $m$ divide $d$.
-%
-The total is $2^d$,
-  for we have enumerated all binary strings whose periods divide $d$.
-%and each period-$m$ necklace contributes $m$ cyclic versions.
-%
-We then weight them by Euler's totient function $\varphi(n/d)$.
-%
-Here, $\varphi(m)$ gives the number of integers from 1 to $m$
-  that are coprime to $m$,
-  e.g.,
-  $\varphi(1) = 1$,
-  $\varphi(3) = 2$ for 1 and 2,
-  $\varphi(6) = 2$ for 1 and 5.
-We repeat the process over other divisors $d$ of $n$,
-  and the resulting sum is $\sum_{d|n} \varphi(n/d) 2^d$.
-%
-The process for a fixed $d$ is exemplified
-  by a row in \reftab{countnecklace}.
-
-%
-
-We can count the above sum in another way.
-We recall that a period-$m$ necklace always contributes
-  $m$ strings in the above process for a fixed $d$,
-  and it does so for all multiples $d$ of $m$.
-So the total weighted contribution by this necklace is
-\begin{equation}
-m \sum_{m|d, d|n} \varphi(n/d) =
- m \sum_{\frac{n}{d}|\frac{n}{m}} \varphi(n/d) = m \,  \frac{n}{m}  = n,
-\label{eq:mphind}
-\end{equation}
-where we have used the identity $\sum_{d'|m'} \varphi(d') = m'$,
-with $d' = n/d$ and $m' = n/m$.
-%
-Summing over the necklaces yields $N(n) \, n$. Thus,
-$N(n) = (1/n) \sum_{d|n} \varphi(n/d) 2^d$.
-The process for a fixed necklace is exemplified
-  by a column in \reftab{countnecklace}.
-%
+  represents $m$ equivalent binary strings
+  differed only by circular shifts.
+  %e.g., $0101$ represents both $0101$ and $1010$.
 
@@
 Thus,
-
+%
 \begin{theorem}
@@
 \begin{equation}
-  \NB(n) = N(n) = (1/n) \sum_{d|n} \varphi(n/d) 2^{\,d},
+  \NB(n) = N(n) = (1/n) \textstyle\sum_{d|n} \varphi(n/d) 2^{\,d},
 \label{eq:necklace}
@@
 %
-$N(n)$ = 2, 3, 4, 6, 8, 14, 20, 36, 60, 108, 188, 352, 632, \ldots, starting from $n = 1$.
+Here, $\varphi(m)$ is Euler's totient function,
+which gives the number of integers from 1 to $m$
+  that are coprime to $m$,
+  e.g.,
+  $\varphi(1) = 1$,
+  $\varphi(3) = 2$ for 1 and 2,
+  $\varphi(6) = 2$ for 1 and 5.
+The first few values of $N_\Pset(n)$ are 2, 3, 4, 6, 8, 14, 20, 36, 60, 108, 188, 352, 632, \ldots,
+  from $n = 1$.
 
@@
 \begin{remark}[2]
-$L(n)$ is also the number of aperiodic (i.e., period equal to $n$)
+Incidentally, $L(n)$ is also the number of aperiodic (i.e., period equal to $n$)
   necklaces of length $n$,
@@
 
+For the first few values,
 $L(n)$ =
 2, 1, 2, 3, 6, 9, 18, 30, 56, 99, 186, 335, 630, \ldots,
-starting from $n = 1$.
-
-Since the period $d$ of a length-$n$ necklace always divides $n$,
+from $n = 1$.
+
+Since an $n$-necklace is either aperiodic itself or
+  a repeated aperiodic $d$-necklace (with $d|n$),
   we have
@@
 
-\subsection{\label{sec:origfac}Intersection of cycles
-  and further factorization at the onset point}
+\subsection{\label{sec:origfac}Factorization at the onset point}
 
@@
 
+\section{\label{apd:bnecklace}Number of binary necklaces}
+
+To count the number of the binary necklaces $N(n)$,
+we construct a sum for the length-$n$ binary strings and count it in two ways.
+\reftab{countnecklace} shows the example for the $n=4$ case.
+%
+For each divisor $d$ of $n$, we collect
+  all length-$n$ binary strings
+  that can be formed by repeating
+  length-$d$ binary strings over $n/d$ times.
+%
+The total is equal to $2^d$, the number of length-$d$ binary strings.
+%
+We then weight them by the totient function $\varphi(n/d)$
+%
+and repeat the process over other divisors $d$ of $n$.
+%
+The resulting sum is $\sum_{d|n} \varphi(n/d) 2^d$.
+%
+The process for a fixed $d$ is exemplified
+  by a row in \reftab{countnecklace}.
+%
+
+We can count the above sum in another way.
+We recall that a period-$m$ necklace always contributes
+  $m$ strings in the above process for a fixed $d$,
+  and it does so for all multiples $d$ of $m$.
+So the total weighted contribution by this necklace is
+\begin{equation}
+m \sum_{m|d, d|n} \varphi(n/d) =
+ m \sum_{\frac{n}{d}|\frac{n}{m}} \varphi(n/d) = m \,  \frac{n}{m}  = n,
+\label{eq:mphind}
+\end{equation}
+where we have used the identity $\sum_{d'|m'} \varphi(d') = m'$,
+with $d' = n/d$ and $m' = n/m$.
+%
+In other words, the overall contribution from a period-$m$ necklace
+  to the above sum is a constant, $n$.
+% 
+Summing over the necklaces yields $N(n) \, n$. Thus,
+$N(n) = (1/n) \sum_{d|n} \varphi(n/d) 2^d$.
+The process for a fixed necklace is exemplified
+  by a column in \reftab{countnecklace}.
+%
+
+\begin{table*}[t]\footnotesize
+\caption{Two ways of counting the $N(4) = 6$ necklaces for $n = 4$.
+}
+\begin{center}
+\begin{tabularx}{0.82 \textwidth}{c | c  c | c | c | c | c | c }
+\hline
+        & \multicolumn{2}{c|}{$m = 1$}
+        & $m = 2$
+        & $m = 4$   & $2^d$ & $\varphi(n/d)$ & $\varphi(n/d) 2^d$\\
+\hline
+$d = 1$ & \hspace{1mm} $\mathbf{0}_{\times4}$ \hspace{1mm}
+        & \hspace{1mm} $\mathbf{1}_{\times4}$ \hspace{1mm} & & & $2 = 2$ & $2$ & 4 \\
+\hline
+$d = 2$ & $\mathbf{00}_{\times2}$ & $\mathbf{11}_{\times2}$
+        & \hspace{1mm} $\mathbf{10}_{\times2} (01_{\times2})$
+          \hspace{1mm} & & $2 + 2 =4$ & $1$ & 4 \\
+\hline
+\multirow{3}{*}{$d = 4$}
+      & & & & \hspace{1mm} $\mathbf{1000} (0100, 0010, 0001)$
+              \hspace{1mm} & $2 + 2 + 12$& \\
+      & $\mathbf{0000}$ & $\mathbf{1111}$ & $\mathbf{1010} (0101)$
+            & $\mathbf{1100} (1001, 0110, 0011)$ & $=16$ & $1$ & 16 \\
+      & & & &   $\mathbf{1110} (1101, 1011, 0111)$ & &  \\
+\hline
+$m \sum_{m|d, d|n} \varphi(\frac{n}{d})$
+      & \multicolumn{2}{c|}{$1\cdot(2+1+1) = 4$}
+      & $2\cdot(1+1) = 4$ & $4\cdot1 = 4$ &  \multicolumn{2}{c|}{} &  $\downarrow$\\
+\hline
+$N(n)\cdot n$ & \multicolumn{2}{c|}{$2 \cdot 4$} & $1 \cdot 4$ & $3 \cdot 4$ &
+  \multicolumn{2}{c|}{$\rightarrow$} & $6\cdot4 = 24$ \\
+\hline
+\multicolumn{8}{p{.82 \linewidth}}{
+  Bold strings are necklaces; others are their cyclic versions.
+}
+\\
+\multicolumn{8}{p{.82 \linewidth}}{
+The subscript of a binary string means the number of repeats;
+e.g.,
+$\mathbf{0}_{\times4}$ means $\mathbf{0}$ repeated four times, or $\mathbf{0000}$;
+$\mathbf{10}_{\times2}$ means $\mathbf{10}$ repeated twice, or $\mathbf{1010}$, etc.
+}
+\\
+\hline
+\end{tabularx}
+\end{center}
+\label{tab:countnecklace}
+\end{table*}
+
 \section{\label{apd:cublyndon}Proof of \refthm{cublyndon}}

### 2013-05-03 doc/pc.tex
pc.tex: move tenary necklace counting to appendix

@@
 whose generator is
-${x_1}^2 \, {x_2} \, {x_3}^2 \, x_6$:
-the first bead is \textbf{2} for ${x_1}^\mathbf{2}$,
- the second is \textbf{1} for ${x_2}^\mathbf{1}$,
- the third is \textbf{2} for ${x_3}^\mathbf{2}$,
- and the sixth is \textbf{1} for ${x_6}^\mathbf{1}$.
+${x_1}^\mathbf{2} \,
+ {x_2}^\mathbf{1} \,
+ {x_3}^\mathbf{2} \,
+ {x_4}^\mathbf{0} \,
+ {x_5}^\mathbf{0} \,
+ {x_6}^\mathbf{1}$.
 %
@@
 \end{theorem}
-
-\begin{proof}
-
-We first show that the number of even ternary strings is $(3^n + 1)/2$.
-%
-Consider the generating function
-\[
-  Z\big(\{x_1, x_2,\dots, x_n\}\big) = \prod_{i=1}^n (1+x_i+{x_i}^2),
-\]
-where $1$, $x_i$, and $x_i^2$ correspond to the states that bead $i$
-taking the number $0$, $1$, and $2$, respectively;
-and the product over $n$ sums over states of independent beads.
-%
-In the expansion of $Z(\vx)$,
- each term (which takes the form
-  ${x_1}^{e_1} {x_2}^{e_2} \dots {x_n}^{e_n}$,
-  with $e_i = 0, 1, 2$)
-represents a unique ternary string $e_1 e_2 \dots e_n$,
-which is even, if $e_1 + e_2 + \dots + e_n$ is so.
-%
-By setting $x_1 = x_2 = \dots = x_n = 1$,
-$Z=3^n$ equals the total number of ternary strings.
-%
-By setting $x_1 = x_2 = \dots = x_n = -1$,
-a term representing an even (odd) ternary string
-  is $+1$ ($-1$);
-and $Z=(1-1+1)^n=1$
-equals the difference between the number of even strings
-  and that of odd strings.
-%
-Thus, the average $(3^n+1)/2$
-gives the number of even ternary strings.
-
-\begin{table*}[t]\footnotesize
-\caption{Two ways of counting the $N_e(2) = 4$ ternary necklaces for $n = 2$.
-}
-\begin{center}
-\begin{tabularx}{\textwidth}{c | c  c c | c  | c | c | c | c }
-\hline
-        & \multicolumn{3}{c|}{$m = 1$}
-        & $m = 2$
-        & $c = n/d$
-        & $T(d, c)$ $^\dagger$
-        & $\varphi(c)$ & $\varphi(n/d) T(d, c)$\\
-\hline
-$d = 1$ & \hspace{1mm} $\mathbf{0}_{\times2}$ \hspace{1mm}
-        & \hspace{1mm} $\mathbf{1}_{\times2}$ \hspace{1mm}
-        & \hspace{1mm} $\mathbf{2}_{\times2}$ \hspace{1mm}
-        & & $2$ & $3$ & $1$ & 3 \\
-\hline
-$d = 2$ & $\mathbf{00}$
-        & $\mathbf{11}$
-        & $\mathbf{22}$
-        & \hspace{1mm} $\mathbf{20} (02)$ $^\ddagger$ \hspace{1mm}
-        & $1$ & $3+1\cdot2=5$ & $1$ & 5 \\
-\hline
-$m \sum_{m|d, d|n} \varphi(\frac{n}{d})$
-      & \multicolumn{3}{c|}{$1\cdot(1+1) = 2$}
-      & $2\cdot1 = 2$ &    \multicolumn{3}{c|}{} &  $\downarrow$\\
-\hline
-$N_e(n)\cdot n$
-    & \multicolumn{3}{c|}{$3 \cdot 2$} & $1 \cdot 2$ &
-  \multicolumn{3}{c|}{$\rightarrow$} & $4\cdot2 = 3 + 5$ \\
-\hline
-\multicolumn{9}{p{\linewidth}}{
-  Bold strings are necklaces; others are their cyclic versions.
-}
-\\
-\multicolumn{9}{p{\linewidth}}{
-The subscript of a string means the number of repeats;
-e.g.,
-$\mathbf{1}_{\times2}$ means $\mathbf{1}$ repeated twice, or $\mathbf{11}$;
-}
-\\
-\multicolumn{9}{p{\linewidth}}{
-$^\dagger$ $T(d, c) \equiv 3^d - \odd(c)(3^d-1)/2$,
-which is $3^d$ if $c$ is even,
-or $(3^d+1)/2$ if $c$ is odd.
-}
-\\
-\multicolumn{9}{p{\linewidth}}{
-$^\ddagger$
-The odd binary strings $\mathbf{10}$, $01$, $\mathbf{21}$, and $12$
-  do not contribute to the sum, and are excluded from $T(d, c)$.
-}
-\\
-\hline
-\end{tabularx}
-\end{center}
-\label{tab:countcubnecklace}
-\end{table*}
-
-The rest counting process is similar to that in \refsec{degprimfac}:
-%
-we construct the sum $n N_e(n)$ by two ways, as exemplified in \reftab{countcubnecklace}.
-%
-In the first way,
-  for a fixed $d$ ($d|n$),
-  if $c\equiv n/d$ is even,
-    we count all ternary strings whose period $m$ divide $d$,
-  but if $c$ is odd, we count only ternary strings
-    whose first $d$ beads are even
-    (because repeating an odd string an odd number times
-    does not yield an even string);
-  in either case, we multiple the result by $\varphi(c)$.
-%
-The process for a fixed $d$ corresponds to a row of \reftab{countcubnecklace}.
-%
-Repeating the process for all $d$ gives
-  $\sum_{cd = n} T(d, c) \, \varphi(c)$,
-  where $T(d, c)$ is the total number $3^d$ of period-$d$ ternary strings if $c$ is even,
-  or the number $(3^d+1)/2$ of even strings if $c$ is odd.
-
-In the second way,
-  we look at the contribution from each necklace to the above sum.
-An even period-$m$ necklace contributes a total of
-  $m \times \sum_{m|d, d|n} \varphi(n/d) = n$
-  \big[the multiplier $m$ is for the $m$ cyclic versions, cf. \refeq{mphind}\big],
-  while an odd necklace contributes nothing.
-Thus, the sum equals $N_e(n)\cdot n$.
-%
-The process for a fixed necklace corresponds to
-  a column of \reftab{countcubnecklace}.
-
-So
-\[
-  N_e(n) \cdot n = \sum_{cd = n} T(d, c) \, \varphi(c),
-\]
-which is \refeq{cublyndon}
-after we divide both sides by $n$.
-\end{proof}
-
-%
-$N_e(n)$ = 2, 4, 6, 14, 26, 68, 158, 424, \dots, starting from $n = 1$.
-%
-
+%
+The proof is presented in \refapd{tnecklace}.
+The first few values $N_e(n)$ are
+  2, 4, 6, 14, 26, 68, 158, 424, \dots, from $n = 1$.
+%
+%
 The characteristic polynomial $A_n(r, \lambda)$
@@
 \begin{table*}[t]\footnotesize
-\caption{Two ways of counting the $N(4) = 6$ necklaces for $n = 4$.
+\caption{Two ways of counting the $N(4) = 6$ binary necklaces for $n = 4$.
 }
@@
 \label{tab:countnecklace}
+\end{table*}
+
+\section{\label{apd:tnecklace}Number of even ternary necklaces}
+
+We first show that the number of even ternary strings is $(3^n + 1)/2$.
+%
+Consider the generating function
+\[
+  Z\big(\{x_1, x_2,\dots, x_n\}\big) = \prod_{i=1}^n (1+x_i+{x_i}^2),
+\]
+where $1$, $x_i$, and $x_i^2$ correspond to the states that bead $i$
+taking the number $0$, $1$, and $2$, respectively;
+and the product over $n$ sums over states of independent beads.
+%
+In the expansion of $Z(\vx)$,
+ each term (which takes the form
+  ${x_1}^{e_1} {x_2}^{e_2} \dots {x_n}^{e_n}$,
+  with $e_i = 0, 1, 2$)
+represents a unique ternary string $e_1 e_2 \dots e_n$,
+which is even, if $e_1 + e_2 + \dots + e_n$ is so.
+%
+By setting $x_1 = x_2 = \dots = x_n = 1$,
+$Z=3^n$ equals the total number of ternary strings.
+%
+By setting $x_1 = x_2 = \dots = x_n = -1$,
+a term representing an even (odd) ternary string
+  is $+1$ ($-1$);
+and $Z=(1-1+1)^n=1$
+equals the difference between the number of even strings
+  and that of odd strings.
+%
+Thus, the average $(3^n+1)/2$
+gives the number of even ternary strings.
+
+To count the number of even cubic necklaces,
+we construct a sum that is equal to $n N_e(n)$ in two ways,
+as exemplified in \reftab{countcubnecklace}.
+%
+In the first way,
+  for a fixed $d$ ($d|n$),
+  we count all ternary strings 
+    that can be formed by repeating period-$d$ ternary string
+    for $n/d$ times;
+  further, $c\equiv n/d$ is odd,
+    we impose a constraint that 
+    the sub-string of the first $d$ beads must be even
+    (because repeating an odd string an odd number times
+    does not yield an even string);
+  in either case, we multiple the result by $\varphi(c)$.
+%
+The process for a fixed $d$ corresponds to a row of \reftab{countcubnecklace}.
+%
+Repeating the process for all $d$ gives
+  $\sum_{cd = n} T(d, c) \, \varphi(c)$,
+  where $T(d, c)$ is the total number $3^d$ of period-$d$ ternary strings if $c$ is even,
+  or the number $(3^d+1)/2$ of even strings if $c$ is odd:
+%
+\begin{align*}
+  T(d, c) &= [1 - \odd(c)] \, 3^d + \odd(c) \, \tfrac{3^d + 1}{2} \\
+          &= 3^d + \odd(c) \, \tfrac{3^d - 1}{2}.
+\end{align*}
+
+In the second way,
+  we look at the contribution from each necklace to the above sum.
+An even period-$m$ necklace contributes a total of
+  $m \times \sum_{m|d, d|n} \varphi(n/d) = n$
+  \big[the multiplier $m$ is for the $m$ cyclic versions, cf. \refeq{mphind}\big],
+  while an odd necklace contributes nothing.
+Thus, the sum equals $N_e(n)\cdot n$.
+%
+The process for a fixed necklace corresponds to
+  a column of \reftab{countcubnecklace}.
+%
+%
+So
+\[
+  N_e(n) \cdot n = \sum_{cd = n} T(d, c) \, \varphi(c),
+\]
+which is \refeq{cublyndon}
+after we divide both sides by $n$.
+
+\begin{table*}[t]\footnotesize
+\caption{Two ways of counting the $N_e(2) = 4$ ternary necklaces for $n = 2$.
+}
+\begin{center}
+\begin{tabularx}{.8 \linewidth}{c | c  c c | c  | c | c | c | c }
+\hline
+        & \multicolumn{3}{c|}{$m = 1$}
+        & $m = 2$
+        & $c = n/d$
+        & $T(d, c)$ $^\dagger$
+        & $\varphi(c)$ & $\varphi(n/d) T(d, c)$\\
+\hline
+$d = 1$ & \hspace{1mm} $\mathbf{0}_{\times2}$ \hspace{1mm}
+        & \hspace{1mm} $\mathbf{1}_{\times2}$ \hspace{1mm}
+        & \hspace{1mm} $\mathbf{2}_{\times2}$ \hspace{1mm}
+        & & $2$ & $3$ & $1$ & 3 \\
+\hline
+$d = 2$ & $\mathbf{00}$
+        & $\mathbf{11}$
+        & $\mathbf{22}$
+        & \hspace{1mm} $\mathbf{20} (02)$ $^\ddagger$ \hspace{1mm}
+        & $1$ & $3+1\cdot2=5$ & $1$ & 5 \\
+\hline
+$m \sum_{m|d, d|n} \varphi(\frac{n}{d})$
+      & \multicolumn{3}{c|}{$1\cdot(1+1) = 2$}
+      & $2\cdot1 = 2$ &    \multicolumn{3}{c|}{} &  $\downarrow$\\
+\hline
+$N_e(n)\cdot n$
+    & \multicolumn{3}{c|}{$3 \cdot 2$} & $1 \cdot 2$ &
+  \multicolumn{3}{c|}{$\rightarrow$} & $4\cdot2 = 3 + 5$ \\
+\hline
+\multicolumn{9}{p{.8 \linewidth}}{
+  Bold strings are necklaces; others are their cyclic versions.
+}
+\\
+\multicolumn{9}{p{.8 \linewidth}}{
+The subscript of a string means the number of repeats;
+e.g.,
+$\mathbf{1}_{\times2}$ means $\mathbf{1}$ repeated twice, or $\mathbf{11}$;
+}
+\\
+\multicolumn{9}{p{.8 \linewidth}}{
+$^\dagger$ $T(d, c) \equiv 3^d - \odd(c)(3^d-1)/2$,
+which is $3^d$ if $c$ is even,
+or $(3^d+1)/2$ if $c$ is odd.
+}
+\\
+\multicolumn{9}{p{.8 \linewidth}}{
+$^\ddagger$
+The odd binary strings $\mathbf{10}$, $01$, $\mathbf{21}$, and $12$
+  do not contribute to the sum, and are excluded from $T(d, c)$.
+}
+\\
+\hline
+\end{tabularx}
+\end{center}
+\label{tab:countcubnecklace}
 \end{table*}

### 2013-05-03 doc/pc-ijbc.tex
add references, update webpages

@@
 
-To simplify the calculation, we first change variables \cite{saha} as
+To simplify the calculation, we first change variables \cite{mandelbrot, brown1, brown2, saha} as
 %
@@
 
-A polynomial is cyclic if it is invariant
+A cyclic polynomial is an invariant
   under the cycling of variables
@@
 %
-Note that a cyclic polynomial is not necessarily symmetric
+It is, however, not necessarily symmetric
   (i.e., invariant under the exchange of any two $x_k$ and $x_{j}$),
@@
   where $\vxn{n} \equiv \{x_1, \ldots, x_n\}$
-(we will, however, drop the superscript ``$^{(n)}$'' or
-  even the argument ``$(\vxn{n})$'' entirely when it is clear).
+[we will, however, drop the superscript ``$^{(n)}$'' or
+  even the argument ``$(\vxn{n})$'' entirely when it is clear].
 For example,
@@
   in the complex plane
-  for complex cycles (i.e., complex $R$ and $\vx$)
+  for complex cycles $\vx$
   if $\lambda$ is set to $\exp(i\theta)$ with $\theta \in [0, 2\pi]$.
-  The region enclosed by the contour corresponds to a bulb in the inverted Mandelbrot set
+  The region enclosed by the contour corresponds to
+    a bulb in the inverted Mandelbrot set
   (the correspondence follows from the transformation $z_k = -x_k, c = -R$, which
   reduces \refeq{logmaps} to the quadratic map $z_{k+1} = c + {z_k}^2$
-  used in the Mandelbrot set),
-  see ref. \cite{stephenson}. % and \reffig{logbulb}.
+  used in the Mandelbrot set \cite{mandelbrot}),
+  see ref. \cite{stephenson2, stephenson3}. % and \reffig{logbulb}.
 \end{remark}
@@
 
-For $n = 1$, we have two square-free cyclic polynomials
-  $C_0 = 1$ and $C_1 = x_1$;
-  and $\Lambda = -2 \, x_1$
-Thus,
-$\Lambda \, C_0 = -2 \, x_1$,
-$\Lambda \, C_1 = -2 \, x_1^2 = -2 \, R + 2  \, x_1$,
-and
+For $n = 1$, we have
+  $C_0 = 1$, $C_1 = x_1$, $\Lambda = -2 \, x_1$, and
+%Thus,
+%$\Lambda \, C_0 = -2 \, x_1$,
+%$\Lambda \, C_1 = -2 \, x_1^2 = -2 \, R + 2  \, x_1$,
+%and
 \[
@@
 The $n = 3$ case is nontrivial and has sparked several different
-  elementary derivations \cite{saha, bechhoefer, gordon, burm, zhang}.
+  elementary derivations \cite{brown1, saha, bechhoefer, gordon, burm, zhang}.
 For the current algorithm,
-the cyclic polynomials are
-$C_0 = 1$,
-$C_1 = x_1 + x_2 + x_3$,
-$C_{12} = x_1 x_2 + x_2 x_3 + x_3 x_1$,
-$C_{123} = x_1 x_2 x_3$,
-and
-$\Lambda = -8 \, C_{123}$.
-%
-The square-free reduction yields
-%
-\footnotesize
+%the cyclic polynomials are
+%$C_0 = 1$,
+%$C_1 = x_1 + x_2 + x_3$,
+%$C_{12} = x_1 x_2 + x_2 x_3 + x_3 x_1$,
+%$C_{123} = x_1 x_2 x_3$,
+%and
+$\Lambda = -8 \, C_{123}$,
+%
+and the square-free reduction yields
+%
+\begin{small}
 \begin{align*}
@@
 \end{align*}
-\normalsize
+\end{small}
 %
@@
 
-The $n = 4$ case was previously used
-as a test of several algorithms
-\cite{stephenson, bailey1, kk1, bailey2, lewis}.
+For the $n = 4$ case
+\cite{brown1, stephenson1, stephenson3, bailey, kk1, lewis},
 %$C_0 = 1$,
@@
 %
-Here, we only list the final characteristic equation \eqref{eq:xr}
+we only list the final characteristic equation \eqref{eq:xr}
 after the square reduction (with six square-free cyclic polynomials):
 %
-\footnotesize
+\begin{small}
 \begin{align}
@@
 \end{align}
-\normalsize
+\end{small}
 %
@@
 obtained previously
-\cite{bailey1, kk1, bailey2, lewis}.
+\cite{bailey, kk1, lewis}.
 %
@@
 %
-Since the 4-cycle problem were tackled mainly on computers
-  in the previous studies,
-  we also supply a compact elementary derivation
-  in the Appendix.
+%Since the 4-cycle problem were tackled mainly on computers
+%  in the previous studies,
+%  we also supply a compact elementary derivation
+%  in the Appendix.
 
@@
 \begin{table}[h]\footnotesize
-  %\caption{
   \tbl{
@@
   }
-%\begin{center}
 {
@@
 }
-%\end{center}
 \end{table}
@@
   is derived for the fixed points of $f^n$.
-Thus, it encompasses not only the $n$-cycles,
+Thus, it represents not only the $n$-cycles,
   but also cycles of shorter periods $d$ ($d|n$).
@@
   or 0 if $n$ is divisible by a square of a prime.
-Thus, $\mu(n)$ = 1, $-1$, $-1$, 0, $-1$, 1, \ldots,
-  from $n = 1$.
-The $\mu(n)$ is useful for inversion:
-$g(n) = \sum_{d|n} \mu(n/d) \, h(d)$
-if and only if $h(n) = \sum_{d|n} g(d)$
+%Thus,
+$\mu(n)$ = 1, $-1$, $-1$, 0, $-1$, 1, \ldots,
+  from $n = 1$%.
+%The $\mu(n)$ is useful for inversion:
+%$g(n) = \sum_{d|n} \mu(n/d) \, h(d)$
+%if and only if $h(n) = \sum_{d|n} g(d)$
 \cite{hardy}.
@@
 \refthm{primfac} is a corollary of \refthm{prod},
-%\footnotesize
+\begin{small}
 \begin{align*}
  B_{n, m} (\lambda)
- & = \prod_{l = 1}^{m} A_n(e^{2l\pi i/m} \lambda^{1/m}) \\
+% & = \prod_{l = 1}^{m} A_n(e^{2l\pi i/m} \lambda^{1/m}) \\
  & = \prod_{c | n} \prod_{l=1}^m \prod_{k=1}^c
@@
 \end{align*}
-%\normalsize
+\end{small}
 The M\"obious inversion yields
@@
 
-\begin{theorem}
+%\begin{theorem}
 The degrees in $R$ of $A_n\Rlam$, $P_n\Rlam$ and $S_n(R)$ are
-\begin{subequations}
+\begin{subequations}\small
 \begin{align}
 \deg_R A_n\Rlam &= \sum_{d|n} \varphi(n/d) 2^{d-1}, \\
-\deg_R P_n\Rlam &= \sum_{d|n} \mu(n/d) 2^{d-1}, \\
-\deg S_n(R) &= \deg_R R_n\Rlam - \sum_{d | n, d < n} \deg_R R_d\Rlam \, \varphi(n/d).
+\deg_R P_n\Rlam &\equiv \beta(n) = \sum_{d|n} \mu(n/d) 2^{d-1}, \\
+\deg S_n(R) &= \beta(n) - \sum_{d | n, d < n} \beta(d) \, \varphi(n/d).
 \end{align}
@@
 \end{subequations}
-\label{thm:degR}
-\end{theorem}
+%\label{thm:degR}
+%\end{theorem}
 %
@@
   \refeq{prod} and \refeq{origfac}.
-\refeqsub{degR}{b} was long known \cite{mira, stephenson2},
-and \reqsub{degR}{c} was recently derived \cite{blackhurst}.
+\refeqsub{degR}{b} and (\ref{degR}c) were known \cite{mira, stephenson1, blackhurst}.
 %
@@
 \end{equation}
+This map is closely related to the one studied by Brown \cite{brown3, brown4}.
 %
@@
 is equal to the number of even \emph{ternary} necklaces,
-in which each bead of the string can assume
+in which each bead can assume
 0, 1, or 2, with the total being even.
@@
 The number of ternary necklaces is
-$N_3(n) = \frac{1}{n} \sum_{c d = n} \varphi(c) 3^d$,
+$N_3(n) = \frac{1}{n} \sum_{d|n} \varphi(n/d) 3^d$,
 %\begin{theorem}
-while that of the even ones is
+while the even ones sum to
 %or the cube-free cyclic polynomials for the cubic map of even degrees in $\vx$
@@
 %
-Since $N_e \approx N_3/2$, using the parity saves about half of the equations.
-%
-For the first few values, $N_e(n)$ = 2, 4, 6, 14, 26, 68, 158, 424, \dots, starting from $n = 1$.
+Since $N_e \approx N_3/2$, using the parity saves about half of the equations
+  in computation.
+%
+$N_e(n) = $ 2, 4, 6, 14, 26, 68, 158, 424, \dots, from $n = 1$.
 %
@@
 This is also the number of the $n$-cycles \cite{hao, hao2}.
-Note that, for $n>1$, half of the cycles have negative $r$,
-and the $x_k$ are imaginary.
+Note that, for $n>1$, $x_k$ in half of the cycles
+  with negative $r$ are imaginary.
 However, in a closely-related map
@@
 %
-Following a similar proof to \refthm{degR},
+Following similar steps in \refsec{degR},
 we find the corresponding degrees in $r$
@@
 
-%Compared with other approaches \cite{hitzl, gordon, bailey1, kk1, hao, hao2}
+%Compared with other approaches \cite{hitzl, gordon, bailey, kk1, hao, hao2}
 %it appeared to be simpler and more transparent,
@@
 
-% ws-ijbc dislike the following
+% ws-ijbc dislikes the following
 %\appendix
@@
 
-\appendix{\label{apd:per4}Derivation of the 4-cycles}
-
-The polynomials for the 4-cycles permits a short derivation.
-We first list the explicit equations:
-%
-%
-%
-\begin{subequations}
-\label{eq:x4}
-\begin{align}
-  x_2 &= R - x_1^2, \\
-  x_3 &= R - x_2^2, \\
-  x_4 &= R - x_3^2, \\
-  x_1 &= R - x_4^2,
-\end{align}
-\end{subequations}
-%
-$\big[\mathrm{\refeqsub{x4}{a}} - \mathrm{\refeqsub{x4}{c}}\big]
-\times
-\big[\mathrm{\refeqsub{x4}{b}} - \mathrm{\refeqsub{x4}{d}}\big]$
-yields $1 + (x_1 + x_3) (x_2 + x_4) = 0$,
-since $x_1 \ne x_3, x_2 \ne x_4$.
-%
-Hence, with
-$y_1 \equiv x_1 + x_3$, $y_2 \equiv x_2 + x_4$,
-$z \equiv y_1 + y_2$,
-we have
-%
-%
-%
-\begin{subequations}
-\begin{align}
-y_1 y_2       &= -1 \\
-y_1^2 + y_2^2 & = (y_1 + y_2)^2 - 2 y_1 y_2 = z^2 + 2 \\
-y_1^3 + y_2^3 & = (y_1 + y_2)^3 - 3 y_1 y_2 (y_1 + y_2) = z^3 + 3 z.
-\end{align}
-\label{eq:ypow4}
-\end{subequations}
-%
-%
-Multiplying \refeqsub{x4}{a} by $x_1$ or $x_3$,
-then summing over cyclic versions yields
-\begin{subequations}
-\begin{align}
-y_1 y_2 &= R z - \big[(x_1^3 + x_3^3) + (x_2^3 + x_4^3)\big],\\
-y_1 y_2 &= R z - \big[x_1 x_3 (x_1 + x_3) + x_2 x_4 (x_2 + x_4)\big].
-\end{align}
-\label{eq:p4q}
-\end{subequations}
-%
-From
-$\mathrm{\refeqsub{p4q}{a}} + 3 \times \mathrm{\refeqsub{p4q}{b}}$,
-we have
-$4 \, y_1 y_2 = 4 R z - (y_1^3 + y_2^3)$,
-%
-and by \refeqs{ypow4},
-\begin{equation}
-  z^3 - (4 R - 3) z - 4 = 0.
-  \label{eq:xr4s}
-\end{equation}
-%
-%
-Since $2 x_1 x_3 = y_1^2 - (x_1^2 + x_3^2) = y_1^2 - 2 R + y_2$,
-and $2 x_2 x_4 = y_2^2 - 2 R + y_1$,
-%
-%Using \refeqs{ypow4} to simplify the right hand side, we find
-\begin{equation}
-  X \equiv x_1 x_2 x_3 x_4 = \frac{1}{2} R z(1 - z) + (R^2 - R + 1),
-\label{eq:der4}
-\end{equation}
-where we have used \refeqs{ypow4} and \req{xr4s} to simplify the result.
-%$X=1/16$ and $-1/16$ at the onset and bifurcation points, respectively.
-%
-Dividing the polynomial in \refeq{xr4s} by that in \refeq{der4}
-yields $z = (R^2-3R-X+1)/(R^2-R+X-1)$,
-and plugging it back to \refeq{der4} gives
-   $R^6 -3 R^5
-  + (3 + X) (R^4 - R^3)
-  + (1 - X) (2 + X) R^2
-  + (1 - X)^3 = 0$,
-which is the same as the sextic factor of \refeq{xr4}
-  with $X = \lambda/16$.
+%\appendix{\label{apd:per4}Derivation of the 4-cycles}
+%
+%
+%
+%The polynomials for the 4-cycles has a compact derivation.
+%We first list the explicit equations:
+%%
+%%
+%%
+%\begin{subequations}
+%\label{eq:x4}
+%\begin{align}
+%  x_2 &= R - {x_1}^2, \\
+%  x_3 &= R - {x_2}^2, \\
+%  x_4 &= R - {x_3}^2, \\
+%  x_1 &= R - {x_4}^2,
+%\end{align}
+%\end{subequations}
+%%
+%$\big[\mathrm{\refeqsub{x4}{a}} - \mathrm{\refeqsub{x4}{c}}\big]
+%\times
+%\big[\mathrm{\refeqsub{x4}{b}} - \mathrm{\refeqsub{x4}{d}}\big]$
+%yields $1 + (x_1 + x_3) (x_2 + x_4) = 0$,
+%since $x_1 \ne x_3, x_2 \ne x_4$.
+%%
+%Hence, with
+%$y_1 \equiv x_1 + x_3$, $y_2 \equiv x_2 + x_4$,
+%$z \equiv y_1 + y_2$,
+%we have
+%%
+%%
+%%
+%\begin{subequations}
+%\begin{align}
+%y_1 y_2           &= -1, \\
+%{y_1}^2 + {y_2}^2 &= z^2 - 2 \, y_1 y_2 = z^2 + 2, \\
+%{y_1}^3 + {y_2}^3 &= z^3 - 3 \, y_1 y_2 \, z = z^3 + 3 z.
+%\end{align}
+%\label{eq:ypow4}
+%\end{subequations}
+%%
+%%
+%Multiplying \refeqsub{x4}{a} by $x_1$ or $x_3$,
+%then summing over cyclic versions yields
+%\begin{subequations}
+%\begin{align}
+%y_1 y_2 &= R z - \big[({x_1}^3 + {x_3}^3) + ({x_2}^3 + {x_4}^3)\big],\\
+%y_1 y_2 &= R z - \big[x_1 x_3 \, y_1 + x_2 x_4 \, y_2\big].
+%\end{align}
+%\label{eq:p4q}
+%\end{subequations}
+%%
+%From
+%$\mathrm{\refeqsub{p4q}{a}} + 3 \times \mathrm{\refeqsub{p4q}{b}}$,
+%we have
+%$4 \, y_1 y_2 = 4 R z - ({y_1}^3 + {y_2}^3)$,
+%%
+%and by \refeqs{ypow4},
+%\begin{equation}
+%  z^3 - (4 R - 3) z - 4 = 0.
+%  \label{eq:xr4s}
+%\end{equation}
+%%
+%%
+%Since
+%$2 x_1 x_3 = {y_1}^2 - ({x_1}^2 + {x_3}^2)
+%= {y_1}^2 - 2 R + y_2$,
+%and $2 x_2 x_4 = {y_2}^2 - 2 R + y_1$,
+%%
+%%Using \refeqs{ypow4} to simplify the right hand side, we find
+%\begin{equation}
+%  X \equiv x_1 x_2 x_3 x_4 = \tfrac{1}{2} R z(1 - z) + (R^2 - R + 1),
+%\label{eq:der4}
+%\end{equation}
+%where we have used \refeqs{ypow4} and \req{xr4s} to simplify the result.
+%%$X=1/16$ and $-1/16$ at the onset and bifurcation points, respectively.
+%%
+%Dividing the polynomial in \refeq{xr4s} by that in \refeq{der4}
+%yields $z = (R^2-3R-X+1)/(R^2-R+X-1)$,
+%and plugging it back to \refeq{der4} gives
+%   $R^6 -3 R^5
+%  + (3 + X) (R^4 - R^3)
+%  + (1 - X) (2 + X) R^2
+%  + (1 - X)^3 = 0$,
+%which is the same as the sextic factor of \refeq{xr4}
+%  with $X = \lambda/16$.
+%
+%
 
@@
   (Addison-Wesley. Reading, MA).
+
+\bibitem[Mandelbrot(1980)]{mandelbrot}
+  Mandelbrot, B. B. [1980]
+  ``Fractal aspects of the iteration of $z \rightarrow \lambda z(1-z)$
+      for complex $\lambda$ and $z$,''
+  {\it Ann. NY Acad. Sci.}
+  \textbf{357},
+  249--259.
+
+\bibitem[Brown(1981)]{brown1}
+  Brown, A. [1981]
+  ``Equations for periodic solutions of a logistic difference equation,''
+  {\it J. Austral. Math. Soc. Ser. B}
+  \textbf{23},
+  78--94
+  (1981).
+
+\bibitem[Brown(1982)]{brown2}
+  Brown, A. [1982]
+  ``Solutions of period seven for a logistic difference equation,''
+  {\it Bull. Austral. Math. Soc.}
+  \textbf{26},
+  263--284.
 
@@
   Burm, J. \& Fishback, P. [2001]
-  ``Period-3 Orbits via Sylvester's Theorem and Resultants,''
+  ``Period-3 orbits via Sylvester's theorem and resultants,''
   {\it Mathematics Magazine}
@@
 
-\bibitem[Stephenson(1992)]{stephenson}
+\bibitem[Stephenson(1991)]{stephenson1}
+  Stephenson, J. [1991]
+  ``Formulae for cycles in the Mandelbrot set,''
+  {\it Physica A}
+  \textbf{177},
+  416--420.
+
+\bibitem[Stephenson(1992)]{stephenson2}
+  Stephenson, J. [1992]
+  ``Formulae for cycles in the Mandelbrot set II,''
+  {\it Physica A}
+  \textbf{190},
+  104--116.
+
+\bibitem[Stephenson(1992)]{stephenson3}
   Stephenson, J. [1992]
@@
 
-\bibitem[Bailey \& Broadhurst(2000)]{bailey1}
-  Bailey, D. H. \& Broadhurst, D. J. [2000]
-  ``Parallel integer relation detection: techniques and applications,''
-  {\it Mathematics of Computation}
-  \textbf{70},
-  1719--1736.
-
-\bibitem[Bailey {\it et al.}(2006)]{bailey2}
+%\bibitem[Bailey \& Broadhurst(2000)]{bailey1}
+%  Bailey, D. H. \& Broadhurst, D. J. [2000]
+%  ``Parallel integer relation detection: techniques and applications,''
+%  {\it Mathematics of Computation}
+%  \textbf{70},
+%  1719--1736.
+
+\bibitem[Bailey {\it et al.}(2006)]{bailey}
   Bailey, D. H., Borwein, J. M., Kapour, V. \& Weisstein, E. W. [2006]
@@
 
-\bibitem[Stephenson(1991)]{stephenson2}
-  Stephenson, J. [1991]
-  ``Formulae for cycles in the Mandelbrot set,''
-  {\it Physica A}
-  \textbf{177},
-  416--420.
-
 \bibitem[Blackhurst(2011)]{blackhurst}
@@
 
+\bibitem[Brown(1984a)]{brown3}
+  Brown, A. [1984a]
+  ``Solutions of period three for a non-linear difference equation,''
+  {\it J. Austral. Math. Soc. Ser. B}
+  \textbf{25},
+  451--462.
+
+\bibitem[Brown(1984b)]{brown4}
+  Brown, A. [1984b]
+  ``Solutions of period four for a non-linear difference equation,''
+  {\it J. Austral. Math. Soc. Ser. B}
+  \textbf{26},
+  146--164.
+
 \end{thebibliography}

### 2013-05-03 doc/pc.tex
add references, update webpages

@@
 
-To simplify the calculation, we first change variables \cite{saha} as
+To simplify the calculation, we first change variables \cite{mandelbrot, brown1, saha} as
 %
@@
   for stable cycles.
-  These regions are bulbs in the Mandelbrot set,
-  %(however, we need the replacement
-  %$x_k \rightarrow -z_k$
-  %and
-  %$R \rightarrow -c$)
+  These regions are bulbs in the Mandelbrot set
+  (the correspondence follows from the transformation $z_k = -x_k, c = -R$, which
+  reduces \refeq{logmaps} to the quadratic map $z_{k+1} = c + {z_k}^2$
+  used in the Mandelbrot set \cite{mandelbrot}),
   see ref. \cite{stephenson} and \reffig{logbulb}.
@@
 
-For $n = 3$ \cite{saha, bechhoefer, gordon, burm, zhang},
+For $n = 3$ \cite{brown1, saha, bechhoefer, gordon, burm, zhang},
 we have
@@
 %
-\footnotesize
+\begin{footnotesize}
 \begin{align*}
@@
 \end{align*}
-\normalsize
+\end{footnotesize}
 %
@@
 
-For $n = 4$ \cite{stephenson, bailey1, kk1, bailey2, lewis},
+For $n = 4$ \cite{brown1, stephenson, bailey, kk1, lewis},
 the cyclic polynomials are
@@
 \begin{widetext}
-%\footnotesize
+\begin{small}
 \begin{align}
@@
 \end{align}
-%\normalsize
+\end{small}
 \end{widetext}
@@
 \end{equation}
+This map is closely related to the one studied by Brown \cite{brown3}.
 Since the new replacement rule
@@
 
-\begin{theorem}
+%\begin{theorem}
 The number of the even ternary necklaces
@@
 $\odd(c) \equiv \big[1 - (-1)^c\big]/2$ is 1 if $c$ is odd or 0 if even.
-\label{thm:cubnecklace}
-\end{theorem}
+%\label{thm:cubnecklace}
+%\end{theorem}
 %
@@
     etc.\big]
-The degree of the polynomial is given by
-
-\begin{theorem}
+
 The degree in $\lambda$ of
-the minimal polynomial $P_n(r, \lambda)$ of the $n$-cycles is
+the minimal polynomial $P_n(r, \lambda)$ of the $n$-cycles
+satisfies a similar relation to \refeq{necklacelyndon},
+%$N_e(n) = \sum_{d|n} L_e(d)$,
+%
+whose M\"obius inversion
+%  $L_e(n) = \sum_{d|n} \mu(n/d) \, N_e(n)$,
+after some algebra (\refapd{cublyndon}) yields
+%\begin{theorem}
 \begin{equation}
@@
 but $0$ for an even $n$.
-\label{thm:cublyndon}
-\end{theorem}
-
-\refeq{cublyndon} follows from the inversion
-  $L_e(n) = \sum_{d|n} \mu(n/d) \, N_e(n)$,
-after some algebra, as shown in \refapd{cublyndon}.
-%
-$L_e(n)$ = 2, 2, 4, 10, 24, 60, 156, 410, \ldots, starting from $n = 1$.
+%\label{thm:cublyndon}
+%\end{theorem}
+%
+%
+$L_e(n)$ = 2, 2, 4, 10, 24, 60, 156, 410, \ldots, from $n = 1$.
 %
 This is also the number of the $n$-cycles \cite{hao}.
-Note that, for $n>1$, half of the cycles have negative $r$,
-and the $x_k$ are imaginary.
+
+Note that, for $n>1$, $x_k$ in half of the cycles with negative $r$
+are imaginary.
 However, in a transformed map,
@@
 
-%Compared with other approaches \cite{hitzl, gordon, bailey1, kk1, hao}
+%Compared with other approaches \cite{hitzl, gordon, bailey, kk1, hao}
 %it appeared to be simpler and more transparent,
@@
 \begin{align}
-  x_2 &= R - x_1^2, \\
-  x_3 &= R - x_2^2, \\
-  x_4 &= R - x_3^2, \\
-  x_1 &= R - x_4^2,
+  x_2 &= R - {x_1}^2, \\
+  x_3 &= R - {x_2}^2, \\
+  x_4 &= R - {x_3}^2, \\
+  x_1 &= R - {x_4}^2,
 \end{align}
@@
 y_1 y_2       &= -1 \\
-y_1^2 + y_2^2 & = (y_1 + y_2)^2 - 2 y_1 y_2 = z^2 + 2 \\
-y_1^3 + y_2^3 & = (y_1 + y_2)^3 - 3 y_1 y_2 (y_1 + y_2) = z^3 + 3 z.
+{y_1}^2 + {y_2}^2 & = (y_1 + y_2)^2 - 2 y_1 y_2 = z^2 + 2 \\
+{y_1}^3 + {y_2}^3 & = (y_1 + y_2)^3 - 3 y_1 y_2 (y_1 + y_2) = z^3 + 3 z.
 \end{align}
@@
 \begin{align}
-y_1 y_2 &= R z - \big[(x_1^3 + x_3^3) + (x_2^3 + x_4^3)\big],\\
+y_1 y_2 &= R z - \big[({x_1}^3 + {x_3}^3) + ({x_2}^3 + {x_4}^3)\big],\\
 y_1 y_2 &= R z - \big[x_1 x_3 (x_1 + x_3) + x_2 x_4 (x_2 + x_4)\big].
@@
 we have
-$4 \, y_1 y_2 = 4 R z - (y_1^3 + y_2^3)$,
+$4 \, y_1 y_2 = 4 R z - ({y_1}^3 + {y_2}^3)$,
 %
@@
 %
-Since $2 x_1 x_3 = y_1^2 - (x_1^2 + x_3^2) = y_1^2 - 2 R + y_2$,
-and $2 x_2 x_4 = y_2^2 - 2 R + y_1$,
+Since $2 x_1 x_3 = {y_1}^2 - ({x_1}^2 + {x_3}^2) = {y_1}^2 - 2 R + y_2$,
+and $2 x_2 x_4 = {y_2}^2 - 2 R + y_1$,
 %
@@
 \]
-which is \refeq{cublyndon}
+which is \refeq{cubnecklace}
 after we divide both sides by $n$.
@@
 
-\section{\label{apd:cublyndon}Proof of \refthm{cublyndon}}
-
-Here we prove \refthm{cublyndon} \big[or \refeq{cublyndon}\big]
-  for the cubic map.
+\section{\label{apd:cublyndon}Proof of \refeq{cublyndon}}
+
+Here we prove \refeq{cublyndon} for the cubic map.
 %
@@
 %
-\footnotesize
+\begin{small}
 \[
@@
 \]
-\normalsize
+\end{small}
 Comparing the two formulas yields
@@
 
-\bibitem{strogatz} S. H. Strogatz,
+\bibitem{strogatz}
+  S. H. Strogatz,
   \textit{Nonlinear Dynamics and Chaos}
@@
 
-\bibitem{may} R. M. May,
+\bibitem{may}
+  R. M. May,
   Simple mathematical models with very complicated dynamics,
@@
   \textbf{261},
-  459-467
+  459--467
   (1976).
 
-\bibitem{saha} P. Saha and S. H. Strogatz,
+\bibitem{mandelbrot}
+  B. B. Mandelbrot,
+  Fractal aspects of the iteration of $z \rightarrow \lambda z(1-z)$
+      for complex $\lambda$ and $z$,
+  \textit{Ann. NY Acad. Sci.}
+  \textbf{357},
+  249--259
+  (1980).
+
+\bibitem{brown1}
+  A. Brown,
+  Equations for periodic solutions of a logistic difference equation,
+  \textit{J. Austral. Math. Soc. Ser. B}
+  \textbf{23},
+  78--94
+  (1981);
+%\bibitem{brown2} A. Brown,
+  Solutions of period seven for a logistic difference equation,
+  \textit{Bull. Austral. Math. Soc.}
+  \textbf{26},
+  263--284
+  (1982).
+
+\bibitem{saha}
+  P. Saha and S. H. Strogatz,
   The birth of period three,
@@
   \textbf{68},
-  42-47
+  42--47
   (1995).
 
-\bibitem{kk1} I. S. Kotsireas and K. Karamanos,
+\bibitem{kk1}
+  I. S. Kotsireas and K. Karamanos,
   Exact computation of the bifurcation point $B_4$ of the logistic map and
@@
   \textbf{14},
-  2417-2423
+  2417--2423
   (2004).
 
-\bibitem{burm} J. Burm, P. Fishback,
-  Period-3 Orbits via Sylvester's Theorem and Resultants,
+\bibitem{burm}
+  J. Burm, P. Fishback,
+  Period-3 orbits via Sylvester's theorem and resultants,
   \textit{Mathematics Magazine}
   \textbf{74},
-  47-51
+  47--51
   (2001).
 
-\bibitem{stephenson} J. Stephenson,
+\bibitem{stephenson}
+  J. Stephenson,
+  Formulae for cycles in the Mandelbrot set,
+  \textit{Physica A}
+  \textbf{177},
+  416-420
+  (1991);
+  Formulae for cycles in the Mandelbrot set II,
+  \textit{ibid.}
+  \textbf{190},
+  104--116
+  (1992);
   Formulae for cycles in the Mandelbrot set III,
-  \textit{Physica A}
+  \textit{ibid.}
   \textbf{190},
-  117-129
+  117--129
   (1992).
 
-\bibitem{bechhoefer} J. Bechhoefer,
+\bibitem{bechhoefer}
+  J. Bechhoefer,
   The birth of period 3, revisited,
@@
   \textbf{69},
-  115-118
+  115--118
   (1996).
 
-\bibitem{gordon} W. B. Gordon,
+\bibitem{gordon}
+  W. B. Gordon,
   Period three trajectories of the logistic map,
@@
   \textbf{69},
-  118-120
+  118--120
   (1996).
 
-\bibitem{zhang} C. Zhang,
+\bibitem{zhang}
+  C. Zhang,
   Period three begins,
@@
   \textbf{83},
-  295-297
+  295--297
   (2010).
 
-\bibitem{bailey1} D. H. Bailey and D. J. Broadhurst,
-  Parallel integer relation detection: techniques and applications,
-  \textit{Mathematics of Computation}
-  \textbf{70},
-  1719-1736
-  (2000).
-
-\bibitem{bailey2} D. H. Bailey, J. M. Borwein, V. Kapour and E. W. Weisstein,
+%\bibitem{bailey1} D. H. Bailey and D. J. Broadhurst,
+%  Parallel integer relation detection: techniques and applications,
+%  \textit{Mathematics of Computation}
+%  \textbf{70},
+%  1719--1736
+%  (2000).
+%
+\bibitem{bailey}
+  D. H. Bailey, J. M. Borwein, V. Kapour and E. W. Weisstein,
   Ten problems in experimental mathematics,
@@
   \textbf{113},
-  481-509
+  481--509
   (2006).
 
-\bibitem{lewis} R. H. Lewis,
+\bibitem{lewis}
+  R. H. Lewis,
   Heuristics to accelerate the Dixon resultant,
@@
   \textbf{77},
-  400-407
+  400--407
   (2008).
@@
   \textbf{4},
-  339-346
+  339--346
   (2000).
@@
   \textbf{131},
-  248-250
+  248--250
   (1988).
@@
   \textbf{177},
-  416-420
+  416--420
   (1991).
 
-\bibitem{blackhurst} J. Blackhurst,
+\bibitem{blackhurst}
+  J. Blackhurst
   Polynomials of the bifurcation points of the logistic map,
@@
   \textbf{21},
-  1869-1877
+  1869--1877
   (2011).
 
-\bibitem{henon} M. H\'enon,
+\bibitem{henon}
+  M. H\'enon,
   A two-dimensional mapping with a strange attractor,
@@
   \textbf{50},
-  69-77
+  69--77
   (1976).
 
-\bibitem{hitzl} D. L. Hitzl and F. Zele,
+\bibitem{hitzl}
+  D. L. Hitzl and F. Zele,
   An exploration of the H\'enon quadratic map,
@@
   \textbf{14},
-  305-326
+  305--326
   (1985).
 
+\bibitem{brown3}
+  A. Brown,
+  Solutions of period three for a non-linear difference equation,
+  \textit{J. Austral. Math. Soc. Ser. B}
+  \textbf{25},
+  451--462
+  (1984);
+%\bibitem{brown4} A. Brown,
+  Solutions of period four for a non-linear difference equation,
+  %\textit{J. Austral. Math. Soc. Ser. B}
+  \textit{ibid.}
+  \textbf{26},
+  146--164
+  (1984).
+
 \end{thebibliography}

### 2013-05-03 logperiod/logperiod.py

@@ -4,6 +4,7 @@ import webapp2, jinja2
 JINJA_ENVIRONMENT = jinja2.Environment(
     loader=jinja2.FileSystemLoader(os.path.dirname(__file__)))
 
+
 class MainPage(webapp2.RequestHandler):
   def get(self, fnhtml="index.html"):
     self.response.headers['Content-Type'] = 'text/html'
@@ -30,21 +31,25 @@ class MainPage(webapp2.RequestHandler):
         </ul></div>''',
 
         'last_update':
-        '<p>Last updated on April. 17th, 2013.',
+        '<p>Last updated on May. 7th, 2013.',
     }
     self.response.write(template.render(template_values))
+
 
 class LogPage(MainPage):
   def get(self):
     MainPage.get(self, "log.html")
 
+
 class CubicPage(MainPage):
   def get(self):
     MainPage.get(self, "cubic.html")
 
+
 class HenonPage(MainPage):
   def get(self):
     MainPage.get(self, "henon.html")
+
 
 class AboutPage(webapp2.RequestHandler):
   def get(self):

### 2013-05-07 doc/pc-ijbc.tex
add scripts in the data directory

@@
 \begin{abstract}
-%\abstract{
-%
 The onset and bifurcation points of the $n$-cycles of
@@
   respectively.
-%
-%}
 \end{abstract}
@@
 
+% switch text to two-column
 \twocolumn
+
 %
@@
 %
-%For complex $r$ and $\vx$,
-%we have plotted \reffig{cubbulb} for regions of stability.
 
@@
 %  1719--1736.
-
+%
 \bibitem[Bailey {\it et al.}(2006)]{bailey}

### 2013-05-07 data/cubic/getls.py

@@ -1,0 +1,36 @@
+#!/usr/bin/env python
+
+import re, sys, os
+
+
+fnin = "inp.txt"
+if len(sys.argv) >= 2:
+  fnin = sys.argv[1]
+
+sa = open(fnin).read().strip()
+sa = re.sub(r"\n ", " ", sa)
+sa = sa.split('\n')
+ls = []
+lsb = []
+for k in range(len(sa)):
+  s = sa[k].strip("{}() ")
+  s = re.sub(r"\(", ",", s)
+  s = re.sub(r"\)", ",", s)
+  s = s.split(",")
+  try:
+    item = s[1].strip()
+    ls = ls + [item]
+    id = int(s[0].strip())
+    #if len(ls) != id:
+    #  print "Index mismatch: %s vs %s" % (id, len(ls))
+    #print s[0].strip(), item
+    if item.startswith("-"):
+      lsb += [ item[1:] ]
+  except:
+    print "error occured %s" % s
+    raise Exception
+
+lsb.reverse()
+ls = ls + lsb
+s = "{" + ',\n'.join(ls) + "}"
+print s

### 2013-05-07 data/log/getls.py

@@ -1,0 +1,30 @@
+#!/usr/bin/env python
+
+import re, sys, os
+
+
+fnin = "inp.txt"
+if len(sys.argv) >= 2:
+  fnin = sys.argv[1]
+
+sa = open(fnin).read().strip()
+sa = re.sub(r"\n ", " ", sa)
+sa = sa.split('\n')
+ls = []
+for k in range(len(sa)):
+  s = sa[k].strip("{}() ")
+  s = re.sub(r"\(", ",", s)
+  s = re.sub(r"\)", ",", s)
+  s = s.split(",")
+  try:
+    item = s[1].strip()
+    ls = ls + [item]
+    id = int(s[0].strip())
+    if len(ls) != id:
+      print "Index mismatch: %s vs %s" % (id, len(ls))
+    #print s[0].strip(), item
+  except:
+    print "error occured %s" % s
+    raise Exception
+s = "{" + ',\n'.join(ls) + "}"
+print s

### 2013-05-08 doc/pc.tex
add scripts in the data directory
improve prd.ma

@@
 \begin{remark}[1]
+Here, ``minimal'' means that the polynomial contains all zeros;
+  it does not, however, necessarily mean that the polynomial is irreducible.
+\end{remark}
+
+\begin{remark}[2]
 The M\"obius function $\mu(n)$ is $(-1)^k$
@@
 
-\begin{remark}[2]
+\begin{remark}[3]
 $B_{d,c}\Rlam$ is a polynomial of $\lambda$.
@@
   (1984);
-%\bibitem{brown4} A. Brown,
+
   Solutions of period four for a non-linear difference equation,

### 2013-05-08 logperiod/js/main.js
move data directories, improve webpages
prd.ma is renamed as log.ma

@@ -10,7 +10,8 @@ function init()
   makeimgslinks(); // add links to the page
 }
 
-function toc_init() // create a table of content
+// create a table-of-content sidebar
+function toc_init()
 {
   var nodes = document.getElementsByTagName("h2");
   for (s = "", i = 0; i < nodes.length; i++) {
@@ -38,21 +39,27 @@ function toc_init() // create a table of content
     + '<div class="toclinkhead">Links:</div>'
     + '<ul class="toclinks">'
     + '<li><a href="/">Home</a>'
-    + '<li><a href="/log">Logistic</a>'
+    + '<li><a href="/logistic">Logistic</a>'
     + '<li><a href="/cubic">Cubic</a>'
     + '<li><a href="/henon">H&eacute;non</a>';
     '</ul>';
   env.appendChild(links);
 
-  env.onmouseover = function () { tocshow(1); };
-  env.onmouseout = function () { tocshow(0); };
+  env.onmouseover = function () { toc_show(1); };
+  env.onmouseout = function () { toc_show(0); };
 
   nodes[0].parentNode.insertBefore(env, nodes[0]);
-  tocshow(0);
+  toc_show(0);
 }
 
-function tocshow(open)
-  { document.getElementById("tocbox").style.left = (open ? "0px" : "-200px"); }
+// show or hide the table-of-contents sidebar
+function toc_show(open)
+{
+  var box = document.getElementById("tocbox");
+  var width = 200;
+  box.style.width = "" + width  + "px";
+  box.style.left =  (open ? "0px" : "" + (-width-40) + "px");
+}
 
 
 var dtbox;
@@ -60,8 +67,10 @@ function dtbox_init() // create a date/time box
 {
   dtbox = document.createElement("div");
   dtbox.id = "dtbox";
-  dtbox.setAttribute("style", "font: small-caps 100% sans-serif; position: fixed;"
-      + "bottom: 0; left: 0; right: 0; height: 20px; padding: 2px; text-align: center;")
+  dtbox.setAttribute("style",
+      "font: small-caps 100% sans-serif; position: fixed;"
+    + "bottom: 0; left: 0; right: 0; height: 20px; "
+    + "padding: 2px; text-align: center;")
   dtbox.onmouseover = function() { dtbox_update(true); };
   dtbox.onmouseout = function() { dtbox_update(false); };
   document.body.appendChild(dtbox);
[…]

### 2013-05-08 logperiod/logperiod.py

@@ -25,30 +25,30 @@ class MainPage(webapp2.RequestHandler):
         <ul class="links">
         <li class="linkhead">Links:
         <li><a href="/">Home</a>,
-        <li><a href="/log">Logistic</a>,
+        <li><a href="/logistic">Logistic</a>,
         <li><a href="/cubic">Cubic</a>,
         <li><a href="/henon">H&eacute;non</a>
         </ul></div>''',
 
         'last_update':
-        '<p>Last updated on May. 7th, 2013.',
+        '<p>Last updated on May. 9th, 2013.',
     }
     self.response.write(template.render(template_values))
 
 
-class LogPage(MainPage):
+class LogisticPage(MainPage):
   def get(self):
     MainPage.get(self, "log.html")
 
 
 class CubicPage(MainPage):
   def get(self):
-    MainPage.get(self, "cubic.html")
+    MainPage.get(self, "cub.html")
 
 
 class HenonPage(MainPage):
   def get(self):
-    MainPage.get(self, "henon.html")
+    MainPage.get(self, "hen.html")
 
 
 class AboutPage(webapp2.RequestHandler):
@@ -58,9 +58,13 @@ class AboutPage(webapp2.RequestHandler):
 
 app = webapp2.WSGIApplication(
   [('/', MainPage),
-   ('/log', LogPage),
+   ('/index', MainPage), # aliases
+   ('/logistic', LogisticPage),
+   ('/log', LogisticPage), # alias
    ('/cubic', CubicPage),
+   ('/cub', CubicPage), # alias
    ('/henon', HenonPage),
+   ('/hen', HenonPage), # alias
    ('/about', AboutPage)],
   debug=True)
 

### 2013-05-08 prog/mkinterp.py
small changes to the webpages

@@ -11,7 +11,7 @@ if len(sys.argv) <= 1:
   print "require an argument"
   exit(1)
 
-input = sys.argv[1]
+fninp = sys.argv[1]
 
 kmin = kmax = None
 argid = 2
@@ -28,7 +28,7 @@ argid += 1
 print kmin, kmax
 
 
-s = open(input).read().strip("{} \n\r")
+s = open(fninp).read().strip("{} \n\r")
 s = [a.strip(" \n{").split(", ") for a in s.split("}")]
 n = len(s)
 print "list contains", n, "items"
@@ -133,13 +133,13 @@ If[kmin === None && kmax === None,
 """
 
 src = ls + xsave
-if input.startswith("hls"):
+if fninp.startswith("hls"):
   print "write code for Henon map"
-  if input.find("b.txt") >= 0:
+  if fninp.find("b.txt") >= 0:
     src += fit_henon % (kmin, kmax, "")
   else:
     src += fit_henon % (kmin, kmax, "p = Factor[p];")
-elif input.startswith("cls"):
+elif fninp.startswith("cls"):
   print "write code for cubic map"
   src += fit_cubic
 else:

### 2013-05-09 prog/magma/numbthy.py
move magma scripts
start the new benchmark time data

@@ -21,7 +21,7 @@ License: Simplified BSD (see details at bottom)
      * moebiusmu(n) - Compute Moebius Mu function of n
        carmichaellambda(n) - Computer Carmichael's Lambda function of n - the smallest exponent e such that b**e = 1 for all b coprime to n.
        factor(n) - Find a factor of n using a variety of methods.
-       factors(n) - Return a sorted list of the prime factors of n.
+       pfactors(n) - Return a sorted list of the prime factors of n.
        factorPR(n) - Find a factor of n using the Pollard Rho method
      * divisors(n) - return a list of divisors of n
      * necklace(n, k) - number of k-ary necklaces
@@ -37,24 +37,25 @@ import math  # Use sqrt, floor
 
 def gcd(a,b):
   """gcd(a,b) returns the greatest common divisor of the integers a and b."""
-  if a == 0:
-    return b
+  if a == 0: return b
   return abs(gcd(b % a, a))
 
+
 def powmod(b,e,n):
-  """powmod(b,e,n) computes the eth power of b mod n.
+  """ computes the eth power of b mod n.
   (Actually, this is not needed, as pow(b,e,n) does the same thing for positive integers.
   This will be useful in future for non-integers or inverses."""
   accum = 1; i = 0; bpow2 = b
-  while ((e>>i)>0):
-    if((e>>i) & 1):
+  while (e>>i) > 0:
+    if ((e>>i) & 1):
       accum = (accum*bpow2) % n
     bpow2 = (bpow2*bpow2) % n
     i+=1
   return accum
 
+
 def xgcd(a,b):
-  """xgcd(a,b) returns a list of form [g,x,y], where g is gcd(a,b) and
+  """ return a list of form [g,x,y], where g is gcd(a,b) and
   x,y satisfy the equation g = ax + by."""
   a1=1; b1=0; a2=0; b2=1; aneg=1; bneg=1; swap = False
   if(a < 0):
@@ -82,14 +83,17 @@ def xgcd(a,b):
       else:
         return [a, a1*aneg, b1*bneg]
 
+
 def isprime(n):
   """isprime(n) - Test whether n is prime using a variety of pseudoprime tests."""
-  if (n in [2,3,5,7,11,13,17,19,23,29]): return True
+  if n in [2,3,5,7,11,13,17,19,23,29]: return True
   return isprimeE(n,2) and isprimeE(n,3) and isprimeE(n,5)
+
 
 def isprimeF(n,b):
[…]

### 2013-05-09 data/log/getls.py
add mkgb.py

@@ -22,7 +22,6 @@ for k in range(len(sa)):
     id = int(s[0].strip())
     if len(ls) != id:
       print "Index mismatch: %s vs %s" % (id, len(ls))
-    #print s[0].strip(), item
   except:
     print "error occured %s" % s
     raise Exception

### 2013-05-09 logperiod/prog/mkgb.py

@@ -1,0 +1,1 @@
+../../prog/magma/mkgb.py

### 2013-05-09 prog/magma/mkgb.py

@@ -1,0 +1,111 @@
+#!/usr/bin/env python
+
+""" generate magma scripts to compute n-cycle polynomials
+    of the logistic and cubic maps by Groebner basis """
+
+import os, sys, getopt
+
+n = 8
+ch = "b"
+param = "R"
+func = "R-x^2"
+dfunc = "-2*x" # derivative of the function
+
+def mkmagma(n, ch, f, df, par):
+  """ return the magma script as a string """
+
+  xs = eqs = der = ""
+  for i in range(0, n):
+    var = "x" + str(i)
+    vas = "x" + str((i+1) % n)
+    xs += var + ","
+    eqs += f.replace("x", var) + "-" + vas + ","
+    der += "(" + df.replace("x", var) + ")*"
+
+  nvar = n + 1
+  extra = par
+  if ch == "a":
+    frac = "1"
+  elif ch == "b":
+    frac = "-1"
+  else:
+    frac = "d"
+    extra = "d," + param
+    nvar += 1
+  der = frac + "-" + der[:-1]
+
+  s = "Q:=RationalField();\n"
+  s += "P<" + xs + extra + ">:=PolynomialRing(Q," + str(nvar) + ");\n"
+
+  s += "I:=ideal< P|" + eqs + der + ">;\n"
+  s += "time B := GroebnerBasis(I);\n"
+  s += "Factorization(B[#B]);"
+  return s
+
+
+def usage():
+  """ print usage and die """
+  print sys.argv[0], "[Options] n [abc]"
+  print """
+  The first argument `n' is the period length.
+  The second argument can be `a' for the onset point,
+  `b' for the bifurcation point, or `c' for the general case """
+            
+  print "OPTIONS:"
+  print " -f, --func:   specify the map"
+  print " -d, --dfunc:  specify the derivative of the map"
+  print " -p, --param:  specify the tunning parameter of the map"
+  print " -r:           original logistic map, f(x)=r*x*(1-x)"
+  print " -R:           simplified logistic map, f(x)=R-x^2"
+  print " -c:           cubic map, f(x)=r*x-x^3"
+  print " -v: be verbose"
+  exit(1)
+
+
+def doargs():
+  global n, ch, func, dfunc, param
+
+  ''' Handle common parameters from command line options '''
+  try:
+    opts, args = getopt.gnu_getopt(sys.argv[1:], "fdpcrRvh",
+         ["verbose", "func=", "dfunc=", "param=", "help",])
[…]

### 2013-05-10 prog/deploy/logrep.py
add intersection polynomial to log.ma
add logres.ma

@@ -4,7 +4,7 @@ import os, sys
 
 def mkpbs(id, kmin, kmax, ch="a", n=13):
   return '''#!/bin/bash
-#PBS -N prd%s%s%s
+#PBS -N log%s%s%s
 #PBS -l nodes=1:ppn=1,walltime=24:00:00
 #PBS -V
 
@@ -13,7 +13,7 @@ def mkpbs(id, kmin, kmax, ch="a", n=13):
 #cat $PBS_NODEFILE
 cd $PBS_O_WORKDIR
 pwd
-math < prd.ma %s %s %s %s > /dev/null
+math < log.ma %s %s %s %s > /dev/null
 ''' % (n, ch, id, n, ch, kmin, kmax)
 
 def lsnm(n, ch):
@@ -40,7 +40,7 @@ def reprod(ch, n):
     os.system("mkdir %s" % dir);
     os.chdir(dir)
     os.system("ln -sf ../test/mats%s.txt ." % n)
-    os.system("ln -sf ../test/prd.ma .")
+    os.system("ln -sf ../test/log.ma .")
     kmin, kmax = getkminmax(None, i)
     str = mkpbs(i, kmin, kmax, ch, n);
     open("foo.pbs", "w").write(str)

### 2013-05-10 logperiod/js/main.js
format log.ma, correct an error
improve webpages

@@ -1,4 +1,4 @@
-/* Copyright (c) Cheng Zhang 2010-2012 */
+/* Copyright (c) Cheng Zhang 2010-2013 */
 window.onload = init;
 
 
@@ -62,6 +62,8 @@ function toc_show(open)
 }
 
 
+
+// the dynamic data/time bar at the bottom of the page
 var dtbox;
 function dtbox_init() // create a date/time box
 {
@@ -82,13 +84,16 @@ function dtbox_update(open)
   dtbox.innerHTML = open ? new Date().toLocaleString() : "";
 }
 
-// add links to all `style="demo"' `img' elements
+
+
+// add links to all "demo" or "fig" class `img' elements
 function makeimgslinks()
 {
   var imgs = document.getElementsByTagName("img");
 
   for (var i = 0; i < imgs.length; i++)
-    if (imgs[i].className == "demo") {
+    if ( imgs[i].className == "demo"
+      || imgs[i].className == "fig" ) {
       pr = imgs[i].parentNode;
       nb = document.createElement('a');
       nb.setAttribute('href', imgs[i].src);

### 2013-05-11 logperiod/logperiod.py
new version of cub.ma

@@ -31,7 +31,7 @@ class MainPage(webapp2.RequestHandler):
         </ul></div>''',
 
         'last_update':
-        '<p>Last updated on May. 9th, 2013.',
+        '<p>Last updated on May 10th, 2013.',
     }
     self.response.write(template.render(template_values))
 

### 2013-05-12 prog/magma/mats2magma.py
add resultant magma scripts
add logres.magma

minor improvements to the webpages

@@ -73,7 +73,8 @@ def mkintmat(mat, n):
   dm = len(mat)
   num = "2^%s" % n
   nnum = "-2^%s" % n
-  if n%2 == 0: num, nnum = nnum, num;
+  if n % 2 == 0:
+    num, nnum = nnum, num;
   for i in range(dm):
     for j in range(dm):
       aij = mat[i][j]
@@ -127,7 +128,8 @@ def tomagma(mats, n):
 def mkcodesimple(n,delta=1):
   return '''
 P<R> := PolynomialRing(Ring0);
-time f := Factorization(Determinant(fmat%s(R, %s)));
+time f := Determinant(fmat%s(R, %s));
+time f := Factorization(f);
 print f;''' % (n, delta)
 
 def mkcodeinter(n, delta=1):
@@ -146,7 +148,8 @@ for i in [1 .. %s] do
     ys := Append(ys, y);
   end if;
 end for;
-f := Factorization(Interpolation(xs, ys));
+time f := Interpolation(xs, ys);
+time f := Factorization(f);
 ''' % (imax, imax/2, n, delta)
   return str
 
@@ -157,3 +160,4 @@ str += tomagma(mats, n)
 str += mkcodesimple(n)  # 84s for n = 9
 #str += mkcodeinter(n)  # 90s for n = 9
 print str
+

### 2013-05-12 prog/magma/mkgb.py

@@ -34,10 +34,10 @@ def mkmagma(n, ch, f, df, par):
     nvar += 1
   der = frac + "-" + der[:-1]
 
-  s = "Q:=RationalField();\n"
-  s += "P<" + xs + extra + ">:=PolynomialRing(Q," + str(nvar) + ");\n"
+  s = "Q := RationalField();\n"
+  s += "P<" + xs + extra + "> := PolynomialRing(Q, " + str(nvar) + ");\n"
 
-  s += "I:=ideal< P|" + eqs + der + ">;\n"
+  s += "I := ideal< P|" + eqs + der + ">;\n"
   s += "time B := GroebnerBasis(I);\n"
   s += "Factorization(B[#B]);"
   return s

### 2013-05-12 prog/magma/mkgb.py
remove old programs, improve nsolve

@@ -50,7 +50,7 @@ def usage():
   The first argument `n' is the period length.
   The second argument can be `a' for the onset point,
   `b' for the bifurcation point, or `c' for the general case """
-            
+
   print "OPTIONS:"
   print " -f, --func:   specify the map"
   print " -d, --dfunc:  specify the derivative of the map"

### 2013-05-13 doc/pc-ijbc.tex
improve prd.ma
doc: rearrange references
remove some theorem environments

@@
 %
-Our purpose is to present an algorithm to identify
-  all regions of $r$ that allow stable $n$-cycles.
+The problem is to identify
+  all regions of $r$ that allow stable $n$-cycles,
+  which has been the objective of several previous
+  studies
+  \cite{brown1, brown2, stephenson1, stephenson2, stephenson3,
+  saha, bechhoefer, gordon, burm, zhang, bailey1, bailey2, kk1, lewis}.
+Below we present a simple algorithm to do so.
 
@@
     a bulb in the inverted Mandelbrot set
-  (the correspondence follows from the transformation $z_k = -x_k, c = -R$, which
+  (it follows from the transformation $z_k = -x_k, c = -R$, which
   reduces \refeq{logmaps} to the quadratic map $z_{k+1} = c + {z_k}^2$
@@
 
-\begin{remark}
-  With $\lambda = 0$,
-  the algorithm yields the polynomial of the superstable point,
-  at which the initial deviation from a cycle point vanishes
-  to the linear order after $n$ iterations of $f$.
-  But we have a better algorithm in this case:
-  since at least one of the $x_k$ is zero by \refeq{logder},
-  then $f^n(x_k = 0) = x_{n+k} = 0$, which provides
-  the desired equation of $R$ \cite{strogatz}.
-\end{remark}
+%\begin{remark}
+%  With $\lambda = 0$,
+%  the algorithm yields the polynomial of the superstable point,
+%  at which the initial deviation from a cycle point vanishes
+%  to the linear order after $n$ iterations of $f$.
+%  But we have a better algorithm in this case:
+%  since at least one of the $x_k$ is zero by \refeq{logder},
+%  then $f^n(x_k = 0) = x_{n+k} = 0$, which provides
+%  the desired equation of $R$ \cite{strogatz}.
+%\end{remark}
 
@@
 \begin{equation}
-0=  \left| \begin{array}{cc}
-  \lambda     & 2          \\
-  2 R         & \lambda - 2
-  \end{array} \right| = -4R - 2\lambda + \lambda^2.
+0
+  %=\left| \begin{array}{cc}
+  %\lambda     & 2          \\
+  %2 R         & \lambda - 2
+  %\end{array} \right|
+  = -4R - 2\lambda + \lambda^2.
   \tag{\ref{eq:xr}-1}
@@
 $\Lambda \, C_0 = 4 \, C_{12}$,
-$\Lambda \, C_1 = 4 \, {x_1}^2 \, x_2 + 4 \, x_1 \, {x_2}^2
+$\Lambda \, C_1 %= 4 \, {x_1}^2 \, x_2 + 4 \, x_1 \, {x_2}^2
   = -8 \, R \, C_0 + 4 \, (R + 1) \, C_1$
-(see the example after \refthm{sqrfree}),
+by the example after \refthm{sqrfree},
 $\Lambda \, C_{12}
@@
 
-The $n = 3$ case is nontrivial and has sparked several different
-  elementary derivations \cite{brown1, saha, bechhoefer, gordon, burm, zhang}.
-For the current algorithm,
-%the cyclic polynomials are
-%$C_0 = 1$,
-%$C_1 = x_1 + x_2 + x_3$,
-%$C_{12} = x_1 x_2 + x_2 x_3 + x_3 x_1$,
-%$C_{123} = x_1 x_2 x_3$,
-%and
-$\Lambda = -8 \, C_{123}$,
-%
-and the square-free reduction yields
-%
-\begin{small}
-\begin{align*}
-\Lambda
-\left( \begin{array}{c}
-  C_0 \\
-  C_1 \\
-  C_{12} \\
-  C_{123}
-\end{array} \right)
-=
-\left( \begin{array}{cccc}
- 0            & 0                 & 0               & -8 \\
- -24 R        & 8(R+1)            & -8R             & 0 \\
- 24 R^2       & -8R(R+2)          & 8(R+1)          & 0 \\
- -8R^3        & 8R^2              & -8R             & 8
-  \end{array} \right)
-\left( \begin{array}{c}
-  C_0 \\
-  C_1 \\
-  C_{12} \\
-  C_{123}
-\end{array} \right),
-\end{align*}
-\end{small}
-%
-%
-%
-and \refeq{xr} reads:
-\begin{align}
-  0
-&= -\big[
-  64R^3 - 128 R^2 - 8 (\lambda - 8) R - (\lambda -8)^2
-  \big] \notag \\
-&\qquad
-  \big(
-  \lambda^2 - 8\lambda - 24 R\lambda - 64 R^3
-  \big).
-  \tag{\ref{eq:xr}-3}
-\label{eq:xr3}
-\end{align}
-%
-Using the first factor, we find at the onset point
-  $\lambda = 1$,
-  $\left(
-  R-\frac74
-  \right)
-  \left(
-  R^2-\frac14 R + \frac{7}{16}
-  \right)=0$
-  and its only real solution is $R_a = 7/4$ ($r_a = 1+\sqrt 8$).
-%
-At the bifurcation point $\lambda = -1$,
-  the equation $R^3-2R^2 + \frac{9}{8} R -\frac{81}{64}=0$
-  yields
-  $R_b = \frac14
-      \left(
-      \frac{8}{3} +
-        \sqrt[3]{\frac{1915}{54} - \frac52\sqrt{201}}
-       +\sqrt[3]{\frac{1915}{54} + \frac52\sqrt{201}}
-      \right)$,
-whose corresponding $r = 1+\sqrt{1+4R}$
-is identical to that in ref. \cite{gordon, burm}.
-%
+%The $n = 3$ case is nontrivial and has sparked several different
+%  elementary derivations 
+%  \cite{brown1, saha, bechhoefer, gordon, burm, zhang}.
+%For the current algorithm,
+%%the cyclic polynomials are
+%%$C_0 = 1$,
+%%$C_1 = x_1 + x_2 + x_3$,
+%%$C_{12} = x_1 x_2 + x_2 x_3 + x_3 x_1$,
+%%$C_{123} = x_1 x_2 x_3$,
+%%and
+%$\Lambda = -8 \, C_{123}$,
+%%
+%and the square-free reduction yields
+%%
+%\begin{small}
+%\begin{align*}
+%\Lambda
+%\left( \begin{array}{c}
+%  C_0 \\
+%  C_1 \\
+%  C_{12} \\
+%  C_{123}
+%\end{array} \right)
+%=
+%\left( \begin{array}{cccc}
+% 0            & 0                 & 0               & -8 \\
+% -24 R        & 8(R+1)            & -8R             & 0 \\
+% 24 R^2       & -8R(R+2)          & 8(R+1)          & 0 \\
+% -8R^3        & 8R^2              & -8R             & 8
+%  \end{array} \right)
+%\left( \begin{array}{c}
+%  C_0 \\
+%  C_1 \\
+%  C_{12} \\
+%  C_{123}
+%\end{array} \right),
+%\end{align*}
+%\end{small}
+%%
+%%
+%%
+%and \refeq{xr} reads:
+%\begin{align}
+%  0
+%&= -\big[
+%  64R^3 - 128 R^2 - 8 (\lambda - 8) R - (\lambda -8)^2
+%  \big] \notag \\
+%&\qquad
+%  \big(
+%  \lambda^2 - 8\lambda - 24 R\lambda - 64 R^3
+%  \big).
+%  \tag{\ref{eq:xr}-3}
+%\label{eq:xr3}
+%\end{align}
+%%
+%Using the first factor, we find at the onset point
+%  $\lambda = 1$,
+%  $\left(
+%  R-\frac74
+%  \right)
+%  \left(
+%  R^2-\frac14 R + \frac{7}{16}
+%  \right)=0$
+%  and its only real solution is $R_a = 7/4$ ($r_a = 1+\sqrt 8$).
+%%
+%At the bifurcation point $\lambda = -1$,
+%  the equation $R^3-2R^2 + \frac{9}{8} R -\frac{81}{64}=0$
+%  yields
+%  $R_b = \frac14
+%      \left(
+%      \frac{8}{3} +
+%        \sqrt[3]{\frac{1915}{54} - \frac52\sqrt{201}}
+%       +\sqrt[3]{\frac{1915}{54} + \frac52\sqrt{201}}
+%      \right)$,
+%whose corresponding $r = 1+\sqrt{1+4R}$
+%is identical to that in ref. \cite{gordon, burm}.
+%%
 
 For the $n = 4$ case
-\cite{brown1, stephenson1, stephenson3, bailey, kk1, lewis},
+\cite{brown1, stephenson1, stephenson3, bailey1, bailey2, kk1, lewis},
 %$C_0 = 1$,
@@
 we only list the final characteristic equation \eqref{eq:xr}
-after the square reduction (with six square-free cyclic polynomials):
+after the square reduction:%
+%(with six square-free cyclic polynomials):
 %
@@
 obtained previously
-\cite{bailey, kk1, lewis}.
-%
-The only two positive roots $r_b \approx 3.9608$
-and $r_b' \approx 3.5441$ of the sextic equation
-correspond to $r_a$ and $r_a'$ respectively.
+\cite{bailey2, kk1, lewis}.
+%
+%The only two positive roots $r_b \approx 3.9608$
+%and $r_b' \approx 3.5441$ of the sextic equation
+%correspond to $r_a$ and $r_a'$ respectively.
 %
@@
 %
-%\begin{remark}[1]
+%\begin{remark}
+%Here, ``minimal'' means that the polynomial contains all zeros.
+%It happens to be irreducible for a general $\lambda$.
+%At $\lambda = 1$, the polynomial of $R$, however, can be factorized (see later).
+%\end{remark}
+%
 \begin{remark}
@@
 %
-%\begin{remark}[2]
 \begin{remark}
@@
 Let us apply \refeq{primfac}
-to some examples in \refsec{examples}.
+to the examples in \refsec{examples}.
 We will omit the argument $R$ below for convenience.
@@
 To show \refthm{primfac}, we first find the degrees in $\lambda$ of
-  $A_n\Rlam$ (\refthm{necklace}) and $P_n\Rlam$ (\refthm{lyndon}).
+  $A_n\Rlam$ (\refeq{necklace}) and $P_n\Rlam$ (\refeq{lyndon}).
 By comparing the degrees,
@@
   contributes one polynomial factor to $A_n\Rlam$
-  (\refthm{prod}),
+  (\refeq{prod}),
   and the inversion of the relation
@@
 Thus,
-
-\begin{theorem}
-The number $\NB(n)$ of the square-free cyclic polynomials $C_p(\vx)$
+%
+%\begin{theorem}
+the number $\NB(n)$ of the square-free cyclic polynomials $C_p(\vx)$
   formed by the cycle points $\vx = \{x_1, \ldots, x_n\}$,
@@
 %
-\label{thm:necklace}
-\end{theorem}
+%\label{thm:necklace}
+%\end{theorem}
 %
@@
   $\varphi(6) = 2$ for 1 and 5.
-The first few values of $N_\Pset(n)$ are 2, 3, 4, 6, 8, 14, 20, 36, 60, 108, 188, 352, 632, \ldots,
+The first few $N_\Pset(n)$ are 2, 3, 4, 6, 8, 14, 20, 36, 60, 108, 188, 352, 632, \ldots,
   from $n = 1$.
@@
 
-\begin{theorem}
+%\begin{theorem}
 The degree in $\lambda$ of the minimal polynomial $P_n\Rlam$ of all $n$-cycles
@@
 \end{equation}
-\label{thm:lyndon}
-\end{theorem}
+%\label{thm:lyndon}
+%\end{theorem}
 %
@@
 
-\begin{theorem}
+%\begin{theorem}
 The minimal polynomials $P_d\Rlam$ of all $d$-cycles
@@
 %encompassed by $A_n\Rlam$.
-\label{thm:prod}
-\end{theorem}
+%\label{thm:prod}
+%\end{theorem}
 
@@
 
-\refthm{primfac} is a corollary of \refthm{prod},
+\refeq{primfac} is a corollary of \refeq{prod},
 \begin{small}
@@
 = \prod_{d|n} B_{d, m n/d}\Rlam^{\mu(n/d)},
-\tag{$\ref{eq:primfac}'$}
+\notag
+%\tag{$\ref{eq:primfac}'$}
 \end{equation}
@@
   \refeq{prod} and \refeq{origfac}.
-\refeqsub{degR}{b} and (\ref{degR}c) were known \cite{mira, stephenson1, blackhurst}.
+\refeqsub{degR}{b} and (\ref{eq:degR}c) were known \cite{mira, stephenson1, blackhurst}.
 %
@@
 
-%Compared with other approaches \cite{hitzl, gordon, bailey, kk1, hao, hao2}
+%Compared with other approaches \cite{hitzl, gordon, bailey2, kk1, hao, hao2}
 %it appeared to be simpler and more transparent,
@@
 
+\bibitem[Stephenson(1991)]{stephenson1}
+  Stephenson, J. [1991]
+  ``Formulae for cycles in the Mandelbrot set,''
+  {\it Physica A}
+  \textbf{177},
+  416--420.
+
+\bibitem[Stephenson(1992a)]{stephenson2}
+  Stephenson, J. [1992a]
+  ``Formulae for cycles in the Mandelbrot set II,''
+  {\it Physica A}
+  \textbf{190},
+  104--116.
+
+\bibitem[Stephenson(1992b)]{stephenson3}
+  Stephenson, J. [1992b]
+  ``Formulae for cycles in the Mandelbrot set III,''
+  {\it Physica A}
+  \textbf{190},
+  117--129.
+
 \bibitem[Saha \& Strogatz(1995)]{saha}
@@
   42--47.
+
+\bibitem[Bechhoefer(1996)]{bechhoefer}
+  Bechhoefer, J. [1996]
+  ``The birth of period 3, revisited,''
+  {\it Mathematics Magazine}
+  \textbf{69},
+  115--118.
+
+\bibitem[Gordon(1996)]{gordon}
+  Gordon, W. B. [1996]
+  ``Period three trajectories of the logistic map,''
+  {\it Mathematics Magazine}
+  \textbf{69},
+  118--120.
+
+\bibitem[Burm \& Fishback(2001)]{burm}
+  Burm, J. \& Fishback, P. [2001]
+  ``Period-3 orbits via Sylvester's theorem and resultants,''
+  {\it Mathematics Magazine}
+  \textbf{74},
+  47--51.
+
+\bibitem[Zhang(2010)]{zhang}
+  Zhang, C. [2010]
+  ``Period three begins,''
+  {\it Mathematics Magazine}
+  \textbf{83},
+  295--297.
+
+\bibitem[Bailey \& Broadhurst(2000)]{bailey1}
+  Bailey, D. H. \& Broadhurst, D. J. [2000]
+  ``Parallel integer relation detection: techniques and applications,''
+  {\it Mathematics of Computation}
+  \textbf{70},
+  1719--1736.
+
+\bibitem[Bailey {\it et al.}(2006)]{bailey2}
+  Bailey, D. H., Borwein, J. M., Kapour, V. \& Weisstein, E. W. [2006]
+  ``Ten problems in experimental mathematics,''
+  {\it The American Mathematical Monthly}
+  \textbf{113},
+  481--509.
 
@@
 
-\bibitem[Burm \& Fishback(2001)]{burm}
-  Burm, J. \& Fishback, P. [2001]
-  ``Period-3 orbits via Sylvester's theorem and resultants,''
-  {\it Mathematics Magazine}
-  \textbf{74},
-  47--51.
-
-\bibitem[Stephenson(1991)]{stephenson1}
-  Stephenson, J. [1991]
-  ``Formulae for cycles in the Mandelbrot set,''
-  {\it Physica A}
-  \textbf{177},
-  416--420.
-
-\bibitem[Stephenson(1992)]{stephenson2}
-  Stephenson, J. [1992]
-  ``Formulae for cycles in the Mandelbrot set II,''
-  {\it Physica A}
-  \textbf{190},
-  104--116.
-
-\bibitem[Stephenson(1992)]{stephenson3}
-  Stephenson, J. [1992]
-  ``Formulae for cycles in the Mandelbrot set III,''
-  {\it Physica A}
-  \textbf{190},
-  117--129.
-
-\bibitem[Bechhoefer(1996)]{bechhoefer}
-  Bechhoefer, J. [1996]
-  ``The birth of period 3, revisited,''
-  {\it Mathematics Magazine}
-  \textbf{69},
-  115--118.
-
-\bibitem[Gordon(1996)]{gordon}
-  Gordon, W. B. [1996]
-  ``Period three trajectories of the logistic map,''
-  {\it Mathematics Magazine}
-  \textbf{69},
-  118--120.
-
-\bibitem[Zhang(2010)]{zhang}
-  Zhang, C. [2010]
-  ``Period three begins,''
-  {\it Mathematics Magazine}
-  \textbf{83},
-  295--297.
-
-%\bibitem[Bailey \& Broadhurst(2000)]{bailey1}
-%  Bailey, D. H. \& Broadhurst, D. J. [2000]
-%  ``Parallel integer relation detection: techniques and applications,''
-%  {\it Mathematics of Computation}
-%  \textbf{70},
-%  1719--1736.
-%
-\bibitem[Bailey {\it et al.}(2006)]{bailey}
-  Bailey, D. H., Borwein, J. M., Kapour, V. \& Weisstein, E. W. [2006]
-  ``Ten problems in experimental mathematics,''
-  {\it The American Mathematical Monthly}
-  \textbf{113},
-  481--509.
-
 \bibitem[Lewis(2008)]{lewis}

### 2013-05-13 doc/pc.tex
remove old programs, improve nsolve
doc: rearrange references
remove some theorem environments

@@
 %
-Our purpose is to present an algorithm to identify
-  all regions of $r$ that allow stable $n$-cycles.
+The problem is to identify
+  all regions of $r$ that allow stable $n$-cycles,
+  which has been the objective of several previous
+  studies
+  \cite{brown1, brown2, stephenson1, stephenson2, stephenson3,
+  saha, bechhoefer, gordon, burm, zhang, bailey, kk1, lewis}.
+Below we present a simple algorithm to do so.
 
@@
 \begin{remark}[1]
-Here, ``minimal'' means that the polynomial contains all zeros;
-  it does not, however, necessarily mean that the polynomial is irreducible.
+Here, ``minimal'' means that the polynomial contains all zeros.
+It happens to be irreducible for a general $\lambda$.
+At $\lambda = 1$, the polynomial of $R$, however, can be factorized (see later).
 \end{remark}
@@
 
-\bibitem{saha}
-  P. Saha and S. H. Strogatz,
-  The birth of period three,
-  \textit{Mathematics Magazine}
-  \textbf{68},
-  42--47
-  (1995).
-
-\bibitem{kk1}
-  I. S. Kotsireas and K. Karamanos,
-  Exact computation of the bifurcation point $B_4$ of the logistic map and
-    the Bailey-Broadhurst conjectures,
-  \textit{International Journal of Bifurcation and Chaos}
-  \textbf{14},
-  2417--2423
-  (2004).
-
-\bibitem{burm}
-  J. Burm, P. Fishback,
-  Period-3 orbits via Sylvester's theorem and resultants,
-  \textit{Mathematics Magazine}
-  \textbf{74},
-  47--51
-  (2001).
-
 \bibitem{stephenson}
@@
 
+\bibitem{saha}
+  P. Saha and S. H. Strogatz,
+  The birth of period three,
+  \textit{Mathematics Magazine}
+  \textbf{68},
+  42--47
+  (1995).
+
 \bibitem{bechhoefer}
@@
 
+\bibitem{burm}
+  J. Burm, P. Fishback,
+  Period-3 orbits via Sylvester's theorem and resultants,
+  \textit{Mathematics Magazine}
+  \textbf{74},
+  47--51
+  (2001).
+
 \bibitem{zhang}
@@
 
-%\bibitem{bailey1} D. H. Bailey and D. J. Broadhurst,
-%  Parallel integer relation detection: techniques and applications,
-%  \textit{Mathematics of Computation}
-%  \textbf{70},
-%  1719--1736
-%  (2000).
-%
 \bibitem{bailey}
+  D. H. Bailey and D. J. Broadhurst,
+  Parallel integer relation detection: techniques and applications,
+  \textit{Mathematics of Computation}
+  \textbf{70},
+  1719--1736
+  (2000);
   D. H. Bailey, J. M. Borwein, V. Kapour and E. W. Weisstein,
@@
   (2006).
+
+\bibitem{kk1}
+  I. S. Kotsireas and K. Karamanos,
+  Exact computation of the bifurcation point $B_4$ of the logistic map and
+    the Bailey-Broadhurst conjectures,
+  \textit{International Journal of Bifurcation and Chaos}
+  \textbf{14},
+  2417--2423
+  (2004).
 

### 2013-05-13 prog/mknsolv.py
improve mknsolv.py

@@ -7,7 +7,7 @@
     where
       prec is the target precision
       wprec is the working precision
-      fnbra is a saved bracket file
+      fnbra is a saved brackets file for the locations of roots
       kmin is the smallest root index
       kmax is the largest root index (inclusive)
       tmfindroot is the maximal time for time out
@@ -27,8 +27,11 @@ if len(sys.argv) <= 1:
   print "require an argument"
   exit(1)
 
-input = sys.argv[1]
+fninp = sys.argv[1]
 
+fneq = "eq.txt" # one-line equation for fast loading
+fnout = "nsolv.ma"
+fnbraout = "intv.txt"  # root brackets
 prec = 11
 wprec = 100
 fnbra = None
@@ -71,23 +74,38 @@ if len(sys.argv) > argid:
   tmfactor = int(sys.argv[argid])
 argid += 1
 
-s = open(input).read().strip(" \n\r")
-if s.endswith("}"):
-  id = s.rfind("{")
-  if id < 0:
-    print "corrupted"
-    raise Exception
-  s = s[:id].strip()
+def eqload(fninp, fneq):
+  """ load the input file, e.g. T13a.txt or cr8b.txt
+      write a single-line file """
 
-# construct a one-line equation file for fast loading
-s = re.sub(r"\\\n", "", s)
-s = re.sub(r"\n", "", s)
-open("eq.txt", "w").write(s)
+  s = open(fninp).read().strip(" \n\r")
+  # remove the existing solutions
+  if s.endswith("}"):
+    id = s.rfind("{")
+    if id < 0:
+      print "corrupted"
+      raise Exception
+    s = s[:id].strip()
 
-s = 'tm = Timing[eq = xload["eq.txt"];][[1]];\nPrint["Equation loaded in ", tm, "s"];\n'
+  # construct a one-line equation file for fast loading
+  # also remove the trailing "\", the line-continuation mark
+  s = [ ln.strip().rstrip("\\").replace(" ", "") for ln in s.split("\n") ]
+  s = ''.join(s) + "\n"
+  open(fneq, "w").write(s)
+
+eqload(fninp, fneq)
+
+# the equation-loading code
+seqload = '''
+tm = Timing[
+  eq = xload["%s"];
+][[1]];
[…]

### 2013-05-14 doc/pc-ijbc.tex
small doc changes

@@
 \newcommand{\NB}{N_\Pset}
+\newcommand{\LB}{L_\Pset}
 \newcommand{\Rlam}{(R, \lambda)}
@@
   $(y, y) = (x_{k+1}, x_{k+1})$,
-  where the next iteration starts.
+  the starting point of the next iteration.
 %
@@
 
-Since the $n$-cycles constitute a subset of the fixed points of $f^n$,
+Since the $n$-cycles points constitute a subset of the fixed points of $f^n$,
 we will first find
@@
   for the fixed points of $f^n$
-  (\refsecs{cyclic} to \ref{sec:examples}).
+  (\refsecs{cyclic}-\ref{sec:examples}).
 The contributions from shorter $d$-cycles ($d|n$)
@@
 Nonetheless, on a computer, one can
-  construct a polynomial Gr\"obner basis \cite{kk1}
-  that gradually eliminates $x_k$ out of the $n+1$ equations.
+  construct a polynomial Gr\"obner basis \cite{kk1},
+  which gradually eliminates $x_k$ out of the $n+1$ equations.
 As a special case, if $x_2, \dots, x_n$ are eliminated first,
@@
 %
-%As the coefficients are polynomials of $R$ only,
 Thus, the zero-determinant condition $|\mathbf A| = 0$ gives
@@
 whose roots contain all fixed points of $f^n$.
-%
-%Note that we will obtain different equations
-%  at the onset and bifurcation points
-%  because the coefficients,
-%  hence the matrices and determinants,
-%  will be different.
 %
@@
 %
-It is, however, not necessarily symmetric
+It is, however, unnecessarily symmetric
   (i.e., invariant under the exchange of any two $x_k$ and $x_{j}$),
   e.g., $a$ and $b$ are not symmetric,
-  but $a + b$ is.
+  although $a + b$ is.
 
@@
   $C_{112}(\vx) = {x_1}^2 x_2 + {x_2}^2 x_3 + \dots + {x_n}^2 x_1$.
-%The cycle length $n$ is omitted for convenience.
-%  for we will mostly work with a fixed $n$ at a time.
 In case the cyclic polynomial has several generators,
-%  e.g., both $x_1 x_2$ and $x_2 x_3$ are generators of $C_{12}(\vx)$
-%   (assuming $n \ge 3$),
   we pick the one with the smallest $p$
@@
   has no repeated index.
-The set of all square-free $p$ is denoted by
+We denote the set of all square-free $p$ by
 $\Pset = \{0, 1, 12, 13, \ldots, 123, 124, \ldots, 12\dots n\}$,
-and its size $|\Pset|$ equals the number $\NB$ of
-  square-free cyclic polynomials.
+and its size by $\NB$. 
+% is the number of square-free cyclic polynomials.
 %
@@
   by one.
-Since the original polynomial is cyclic,
+Since both the replacement rules and the original polynomial are cyclic,
   so is the final square-free polynomial.
@@
   are collected to serve as the coefficient before $C_0(\vx) \equiv 1$.
-%Since no square or higher powers of $x_k$
-%  can survive the reduction,
-%  the final cyclic polynomials are square-free;
 The coefficients $f_p$ are polynomials of $R$,
-  for $R$ is the only variable introduced by the substitutions.
+  for $R$ is the only new variable introduced by the substitutions.
 \end{proof}
@@
   linearly connected by $\NB$ homogeneous equations.
-The matrix of the connecting coefficients then must have a zero determinant,
-  which yields the desired polynomial.
+The matrix of the connecting coefficients thus has a vanishing determinant,
+  which furnishes the desired polynomial equation.
 
@@
   \big[ \lambda \, \vct I - \vct T(R) \big] \, \vct C = 0,
-\tag{\ref{eq:xcp}'}
+\tag{\ref{eq:xcp}$'$}
 \end{equation}
@@
   has a non-trivial solution
+  (i.e., $C_p(\vx)$ do not vanish altogether)
   only if the determinant of the coefficient matrix
@@
 \end{equation}
-Here, $A_n\Rlam$ is a polynomial of $R$ and $\lambda$,
-  and the subscript $n$ is attached such that
-  it can be used later with $A_d\Rlam$ of divisors $d$ of $n$.
-\refeq{xr} is a necessary condition
-  since $C_p(\vx)$ cannot vanish altogether;
-and since it involves $R$ only,
-  the polynomial expansion of the determinant
-  gives the answer to our problem.
-%Note that we did not solve the values $C_p$ in the process.
-
+%
+Now $A_n\Rlam$, after we expand the determinant,
+  is a polynomial of $R$ and $\lambda$,
+  the equation is the desired answer to our problem.
+%
+We attach the subscript $n$ to $A\Rlam$ because
+  it will later be used with $A_d\Rlam$ of divisors $d$ of $n$.
+%
 To summarize, we have
@@
   of the cycle points $\vx = \{x_k\}$
-  are linear related by % \refeq{xcp},
+  are linearly related by % \refeq{xcp},
   $\lambda \, C_p(\vx) = \sum_{q \in \Pset} T_{pq}(R) \, C_q(\vx)$,
@@
 
-\begin{remark}
-  Generally, the algorithm can trace a contour of marginal stability of $R$
+%\begin{remark}
+More generally, the algorithm can trace a contour of marginal stability of $R$
   in the complex plane
@@
   see ref. \cite{stephenson2, stephenson3}. % and \reffig{logbulb}.
-\end{remark}
+%\end{remark}
 
@@
 It is still helpful to have a mathematical software
-  in order to verify certain steps
+  at hand to verify certain steps
   (e.g., in computing the determinants and their factorization).
@@
 For $n = 1$, we have
-  $C_0 = 1$, $C_1 = x_1$, $\Lambda = -2 \, x_1$, and
-%Thus,
-%$\Lambda \, C_0 = -2 \, x_1$,
-%$\Lambda \, C_1 = -2 \, x_1^2 = -2 \, R + 2  \, x_1$,
-%and
+  $C_0 = 1$, $\Lambda = -2 \, C_1 = -2 \, x_1$, and
 \[
@@
 Thus, $R = (\lambda^2 -2\lambda)/4$;
-  and the fixed point begins at $R_a = -1/4$ ($\lambda = +1$),
-  and becomes unstable at $R_b = 3/4$ ($\lambda = -1$).
+  and the fixed point begins at $R_a = -1/4$ ($\lambda = +1$), and
+  becomes unstable at $R_b = 3/4$ ($\lambda = -1$).
 
@@
 The first factor is responsible for the 2-cycle,
-  while the second factor is for unstable fixed points. % (see later).
+  while the second factor is for the unstable fixed points. % (see later).
 Setting the former to zero yields $R = 1 - \lambda/4$;
@@
 $4096 R^6 - 12288 R^5 + 12032 (R^4 - R^3)
-  + 8432 R^2 + 4913 = 0$,
-which upon $R \rightarrow r(r-2)/4$ yields the same polynomial
-obtained previously
-\cite{bailey2, kk1, lewis}.
+  + 8432 R^2 + 4913 = 0$
+%which upon $R \rightarrow r(r-2)/4$ yields the same polynomial
+%obtained previously
+\cite{stephenson1, stephenson3, bailey2, kk1, lewis}.
 %
@@
 
-The algorithm was coded into a Mathematica program,
-which was used to compute the polynomials for $n$ up to 13.
-%
-For polynomials of larger $n$ are saved in in the website in \refsec{end}.
-%
-The representative $r$ values are listed in \reftab{rval}.
-%
+\subsection{\label{sec:primfac}Minimal polynomial of the $n$-cycles}
+
+The characteristic polynomial $A_n\Rlam$ in \refeq{xr}
+  is derived for the fixed points of $f^n$.
+Thus, it represents not only the $n$-cycles,
+  but also cycles of shorter periods $d$ ($d|n$).
+%
+Fortunately, the contributions from different cycles
+  are separate factors of $A_n\Rlam$.
+For a large $n$,
+  the factor $P_n\Rlam$ that represents all $n$-cycles
+  can be easily recognized
+  as the largest factor of $A_n\Rlam$.
+%
+More systematically, we have
+
+%\begin{theorem}
+%  The polynomial $P_n\Rlam$ of all $n$-cycles
+%  is a factor of the characteristic polynomial $A_n\Rlam$,
+%  and can be computed as
+  \begin{equation}
+    P_n\Rlam
+    = \prod_{cd = n} B_d^c\Rlam^{\mu(c)},
+  \label{eq:primfac}
+  \end{equation}
+where
+  $B_d^c\Rlam \equiv \prod_{k=1}^c A_{d}(R, e^{2k\pi i/c} \lambda^{1/c})$,
+  $\lambda^{1/c}$ is a complex $c$th root of $\lambda$.
+%\end{theorem}
+%
+%
+%\begin{remark}
+%Here, ``minimal'' means that the polynomial contains all zeros.
+%It happens to be irreducible for a general $\lambda$.
+%At $\lambda = 1$, the polynomial of $R$, however, can be factorized (see later).
+%\end{remark}
+%
+%\begin{remark}
+The M\"obius function $\mu(n)$ is $(-1)^k$
+  if $n$ is the product of $k$ distinct primes,
+  or 0 if $n$ is divisible by a square of a prime.
+%Thus,
+The first few $\mu(n) = 1, -1, -1, 0, -1, 1, -1, \ldots,$
+  from $n = 1$%.
+%The $\mu(n)$ is useful for inversion:
+%$g(n) = \sum_{d|n} \mu(n/d) \, h(d)$
+%if and only if $h(n) = \sum_{d|n} g(d)$
+\cite{hardy}.
+%\end{remark}
+%
+%
+\begin{remark}
+%$B_{d,c}\Rlam$ is a polynomial of $\lambda$.
+Despite the argument $\lambda^{1/c}$,
+  the product $\prod_{k=1}^c A_d(R, e^{2k\pi i/c} \lambda^{1/c})$,
+  hence $B_d^c\Rlam$,
+  is free from radicals of powers of $\lambda^{1/c}$,
+  for it is invariant under $\lambda \rightarrow e^{2\pi i} \lambda$.
+Thus, $B_d^c\Rlam$ is a polynomial of $\lambda$,
+and $\deg_\lambda B_d^c\Rlam = \deg_\lambda A_d\Rlam$.
+Particularly, $B_n^1\Rlam = A_n\Rlam$.
+\end{remark}
+%
+%
+%We will refer to $P_n\Rlam$ as the \emph{primitive factor} below.
+%
+%
+Let us apply \refeq{primfac}
+to the examples in \refsec{examples}.
+We will omit the argument $R$ below for convenience.
+%%
+For $n = 1$,
+%there is no irrelevant factor in \refeq{xr1} and
+$P_1(\lambda) = B_1^1(\lambda) = A_1(\lambda)
+  = \lambda^2 - 2\,\lambda - 4\,R$.
+%
+%
+%
+For $n = 2$, since
+$B_1^2(\lambda)
+=
+A_1(\sqrt{\lambda})
+A_1(-\sqrt{\lambda})
+=
+(4R-\lambda)^2 -4\lambda$,
+%
+$P_2(\lambda) = A_2(\lambda) \, B_1^2(\lambda)^{-1} = 4R - 4 + \lambda$.
+%
+%
+For $n = 4$,
+%we have
+%$16 (R-1)^2 - \lambda
+%= (4R - 4 + \sqrt{\lambda})(4R - 4 - \sqrt{\lambda})$
+%and
+%$
+%(16 R^2 + \lambda)^2 - 16 (2R+1)^2 \lambda
+%=
+%\big[(4R - \sqrt{\lambda})^2  - 4\sqrt{\lambda}\,\big]
+%\big[(4R + \sqrt{\lambda})^2  + 4\sqrt{\lambda}\,\big]$.
+%Thus,
+we can show that
+the last two factors of \refeq{xr4}
+can be written as
+$B_2^2(\lambda) = A_2(\sqrt{\lambda}) A_2(-\sqrt{\lambda})$,
+and
+%
+$P_4(\lambda)
+    = A_4(\lambda) \, B_2^2(\lambda)^{-1}$
+indeed the yields the sextic factor.
+%$    = 4096 R^6-12288 R^5+ 256 (\lambda + 48) (R^4- R^3)
+%    -16(\lambda + 32)(\lambda - 16) R^2 - (\lambda-16)^3$.
+Note, $B_1^4(\lambda)$ is unused for $\mu(4) = 0$.
+
+%It can be, however, problematic,
+%   if $P_n(R, \lambda)$ is solved for $\lambda = 1$
+%   instead of a general $\lambda$,
+%   for $P_n(R, 1)$ itself can be further factorized.
+%
+Due to the technical nature of the derivation and subsequent discussions,
+  the reader may wish to skip the rest of \refsec{logmap}
+  on first reading.
+
+\subsection{\label{sec:degprimfac}Counting cycles}
+
+%We will prove \refthm{primfac} by the following steps.
+%
+To show \refeq{primfac}, we first find the degrees in $\lambda$ of
+  $A_n\Rlam$ [\refeq{necklace}] and $P_n\Rlam$ [\refeq{lyndon}].
+By comparing the degrees,
+  we then show that each $P_d\Rlam$ with ($d|n$),
+  after some transformation,
+  contributes one polynomial factor to $A_n\Rlam$
+  [\refeq{prod}],
+  and the inversion of the relation
+  yields \refeq{primfac}.
+
+%\subsubsection{Number of the square-free cyclic polynomials}
+
+First, to count the square-free cyclic polynomials,
+  we notice a one-to-one mapping
+  from the square-free cyclic polynomials
+  to the binary necklaces.
+%
+A binary necklace
+  is a nonequivalent binary $0$-$1$ string.
+%
+Two strings are equivalent if they differ only by a circular shift.
+%
+For example, for $n = 3$, there are $2^3 = 8$ binary strings,
+but only four necklaces: 000, 001, 011 and 111,
+since 010 and 100 are equivalent to 001,
+so are 110 and 101 to 011.
+%
+The mapping is constructed as follows.
+%
+Given a cyclic polynomial, if the generator contains $x_k$,
+  the $k$th character from the left of the necklace is 1,
+  otherwise 0,
+e.g. the above four necklaces correspond to
+  $C_0$, $C_1$, $C_{12}$ and $C_{123}$, respectively.
+%For example, if $n = 3$,
+% the square-free polynomials for $000$, $100$, $110$ and $111$ are
+%  $C_0 = 1$ (generator: 1),
+%  $C_1 = x_1 + x_2 + x_3$ (generator: $x_1$),
+%  $C_{12} = x_1 x_2 + x_2 x_3 + x_3 x_1$ (generator: $x_1 x_2$)
+%  and $C_{123} = x_1 x_2 x_3$ (generator: $x_1 x_2 x_3$), respectively.
+Thus,
+%
+%\begin{theorem}
+the number $\NB(n)$ of the square-free cyclic polynomials $C_p$,
+  %$(\vx)$ formed by the cycle points $\vx = \{x_1, \ldots, x_n\}$,
+  is given by
+\begin{equation}
+  %\deg_\lambda A_n\Rlam =
+  \NB(n) = (1/n) \textstyle\sum_{d|n} \varphi(n/d) 2^{\,d}.
+\label{eq:necklace}
+\end{equation}
+%
+%\label{thm:necklace}
+%\end{theorem}
+%
+Here, $\varphi(m)$ is Euler's totient function,
+which gives the number of integers from 1 to $m$
+  that are coprime to $m$,
+  e.g.,
+  $\varphi(1) = 1$,
+  $\varphi(3) = 2$ for 1 and 2,
+  $\varphi(6) = 2$ for 1 and 5.
+By \refeq{xr},
+  $\NB$ is also $\deg_\lambda A_n\Rlam$.
+The first few $\NB(n)$ are
+2, 3, 4, 6, 8, 14, 20, 36, 60, 108, \dots, % 188, 352, 632, \ldots,
+  from $n = 1$.
+
+%\subsubsection{Number of the $n$-cycles}
+
+%\begin{theorem}
+Next, the degree in $\lambda$ of the polynomial $P_n\Rlam$ of all $n$-cycles
+  is equal to the number of the $n$-cycles,
+  which is given by
+\begin{equation}
+  %\deg_\lambda P_n\Rlam =
+  \LB(n) = (1/n)\textstyle\sum_{d | n} \mu(n/d) 2^{\,d}.
+\label{eq:lyndon}
+\end{equation}
+%\label{thm:lyndon}
+%\end{theorem}
+%
+%
+%\begin{proof}
+The number $\LB$ of $n$-cycles
+  is well known \cite{hao, hao2, lutzky}.
+The minimal polynomial $P_n\Rlam$
+  can be written as $\prod_c (\lambda - \lambda_c)$,
+where $\lambda_c$ is the value of $\Lambda(\vx^c)$
+  evaluated at the $c$th cycle.
+Thus, $\deg_\lambda P_n\Rlam = \LB$.
+%\end{proof}
+%
+The first few $\LB$ are
+2, 1, 2, 3, 6, 9, 18, 30, 56, 99, \dots %186, 335, 630, \ldots,
+from $n = 1$.
+
+Incidentally, $\LB$ is also the number of aperiodic necklaces of length $n$
+(e.g., for $n = 4$,
+  $0011$ is aperiodic, but $0101$ is not due to the shorter period 2).
+%
+Since an $n$-necklace is either aperiodic itself or
+  a repeated aperiodic $d$-necklace (with $d|n$),
+  we have
+\begin{equation}
+  \NB(n) = \textstyle\sum_{d|n} \LB(d).
+\label{eq:necklacelyndon}
+\end{equation}
+%
+Since the left side is also $\deg_\lambda A_n\Rlam$,
+  and $A_n\Rlam$ has to represent all $d$-cycles with $d|n$,
+$A_n\Rlam$
+%and each cycle holds a distinct $\lambda$,
+%  $\deg_\lambda A_n\Rlam$
+%  is at least $\sum_{d|n} L(d)$
+%  according to \refeq{lyndon},
+%  which is equal to
+%  $\NB$ by \refeq{necklacelyndon}.
+%Since $\deg_\lambda A_n\Rlam = \NB$ by \refeq{necklace},
+%  each $n$-cycle occurs exactly once in $A_n\Rlam$.
+
+%\subsubsection{Relation between $P_n$ and $A_n$}
+
+%\begin{theorem}
+We can now show that $P_n\Rlam$ and 
+and $A_n\Rlam$ are related by
+  \begin{equation}
+    A_n\Rlam = \prod_{cd = n} Q_d^c\Rlam,
+    \label{eq:prod}
+  \end{equation}
+  where
+  $Q_d^c\Rlam = \prod_{k=1}^{c} P_d(R, e^{2 k \pi i/c} \lambda^{1/c})$
+  is a polynomial of degree $L(d)$ in $\lambda$
+  representing contributions from $d$-cycles.
+%encompassed by $A_n\Rlam$.
+%\label{thm:prod}
+%\end{theorem}
+
+%\begin{proof}
+In a $d$-cycle,
+ we have $\Lambda(\{x_1, \ldots, x_n\}) = (-2)^n x_1 \dots x_n
+   = {\Lambda_d}^c$,
+where
+$\Lambda_d(\{x_1, \ldots, x_d\}) \equiv (-2)^d x_1 \dots x_d$
+and
+$c \equiv n/d$.
+So the $d$-cycle satisfies a polynomial
+  $P_d(R, \lambda^{1/c}) = 0$,
+where $\lambda = \Lambda(\{x_1,\ldots,x_n\})$.
+%
+This is, however, not a polynomial equation, and
+%
+the radical $\lambda^{1/c}$ can be removed by the product
+$Q_d^c\Rlam
+  \equiv \prod_{k=1}^c P_d(R, e^{2k\pi i/c} \, \lambda^{1/c}) = 0$.
+%
+Now $Q_d^c\Rlam$ is a polynomial of $\lambda$
+  for it is invariant under
+  $\lambda \rightarrow e^{2\pi i} \lambda$,
+and thus free from radicals of the form $\lambda^{l/c}$
+  \big[if $(l, c) \ne c$\big].
+And since
+  $\deg_\lambda Q_d^c\Rlam
+    = \deg_\lambda P_d\Rlam = L(d)$,
+  it is also a polynomial
+  of the lowest possible degree in $\lambda$.
+
+Therefore, the product $\prod_{cd=n} Q_d^c\Rlam$
+  can differ from $A_n\Rlam$ only by
+  a multiple.
+Since $Q_n^1\Rlam = P_n\Rlam$,
+  and the coefficient of highest power of $\lambda$ is always
+  unity in $A_n\Rlam$ \big[see the definition \refeq{xr}\big],
+  we know by induction that the coefficients of the highest power of $\lambda$
+  in all $P_n\Rlam$ and $Q_d^c\Rlam$
+  are also unities.
+So the multiple is one, hence \refeq{prod}.
+%
+%
+%
+%\end{proof}
+
+\refeq{primfac} is a corollary of \refeq{prod},
+\begin{small}
+\begin{align*}
+ B_n^m (\lambda)
+% & = \prod_{l = 1}^{m} A_n(e^{2l\pi i/m} \lambda^{1/m}) \\
+ & = \prod_{c | n} \prod_{l=1}^m \prod_{k=1}^c
+    P_{n/c}(e^{\frac{2k\pi i}{c} + \frac{2l\pi i}{m c}} \lambda^{1/(m c)}) \\
+ & = \prod_{c | n} \prod_{k'=1}^{m c}
+    P_{n/c}(e^{2k'\pi i/(m c)} \lambda^{1/(m c)})% \\
+ %&
+  = \prod_{c | n} Q_{n/c}^{m c}(\lambda).
+\end{align*}
+\end{small}
+The M\"obious inversion yields
+\begin{equation}
+Q_n^m\Rlam
+= \prod_{d|n} B_d^{m n/d}\Rlam^{\mu(n/d)},
+\notag
+%\tag{$\ref{eq:primfac}'$}
+\end{equation}
+which is reduced to \refeq{primfac} with $m = 1$,
+for $Q_n^1 = P_n$.
+
+\subsection{\label{sec:origfac}%Intersection of cycles and
+  Factors at the onset point}
+
+The onset polynomial
+  $P_n(R, \lambda = 1)$ for the $n$-cycles
+  can be further factorized.
+%
+This is caused by the intersection of an $n$-cycle
+  and a shorter $d$-cycle ($d|n$, $d < n$),
+  which forces the two to share orbit.
+%
+One can show that this intersection happens only
+  at the onset of the $n$-cycle, where $\lambda = 1$,
+%
+  and the $d$-cycle branches out, or ``bifurcates,'' $n/d$-fold
+  to become the $n$-cycle.
+%
+The simplest example is the first bifurcation point
+  at $R = 3/4$ for $d = 1, n = 2$,
+  where the fixed point \refeq{xr1}
+  undergoes period-doubling and becomes the 2-cycle \refeq{xr2}.
+As a result, the polynomial $P_n(R, \lambda)$ from the $n$-cycle
+  has to accommodate $P_d(R, \lambda')$ from the $d$-cycle as a factor,
+  with $\lambda'$ being a primitive $(n/d)\,$th root of $\lambda = 1$.
+
+If an $n$-cycle is not born out of the above branching,
+  we call it \emph{original}.
+The two types of cycles exist
+  as separate factors of $P_n(R, \lambda = 1)$.
+One can then show that the factor $S_n(R)$ responsible for the original cycles
+  %or the \emph{original factor} below,
+  is given by
+  \begin{equation}
+    S_n(R)
+    = \frac
+    {
+      P_n(R, 1)
+    }
+    {
+      \prod_{c d =  n, \; c > 1}
+      %\left[ \,
+        \prod_{(k, c) = 1}
+      P_{d}
+        \left(
+          R, e^{2k\pi i/c}
+        \right)
+      %\right]
+    },
+  \label{eq:origfac}
+  \end{equation}
+where the inner product on the denominator is carried over
+   $k$ from 1 to $c$ that are coprime to $c$.
+
+Take the $n = 4$ case as an example, we have
+$\prod_{k=1,3} P_1(R, e^{k\pi i/2})
+%=(-4R-2i-1)(-4R+2i-1)
+=16R^2+8R+5$
+(for $c = 4$),
+$P_2(R, -1) = 4R - 5$
+(for $c = 2$),
+and
+$P_4(R, 1)
+= (4R - 5) (16 R^2 + 8 R + 5)
+  \bigl[
+    (4R - 3)^3 - 108
+  \bigr]$.
+Dividing $P_4(R, 1)$ by the two factors yields
+$S_4(R) = (4R-3)^3 - 108$,
+  whose only real root $R_a=(3+\sqrt[3]{108})/4$ corresponds to
+  the onset of the original cycle.
+Note $R_a' = 5/4$ is excluded from $S_4(R)$
+  as it is due to period-doubling the 2-cycle.
+The two cycles are compared in \reffigs{cobweb}(d) and (e).
+
+%We now prove \refthm{origfac}.
+%Suppose $n = c \,d$, we have, from \refeq{logmaps},
+%\[
+%  x_{l+1} - x_{d+l+1} = - (x_l + x_{d+l}) (x_l - x_{d+l}).
+%\]
+%We apply the equation to $l = 1, \ldots, m$, and the product is
+%\[
+%  x_{m+1} - x_{m + d+1} =
+%  (-1)^{m} \left[ \, \prod_{l=1}^{m} (x_l + x_{d+l}) \right]
+%    (x_1 - x_{d+1}).
+%\]
+%We now set $m$ to $0, d, \ldots, (c-1)\,d$ in this equation,
+%  add them together, eliminate $x_1 - x_{d+1}$
+%  (which is nonzero in a cycle), and
+%\begin{equation}
+%  \sum_{c' = 0}^{c-1}
+%    (-1)^{c' d} \prod_{l=1}^{c' d} (x_l + x_{d+l})
+%   = 0.
+%\label{eq:stair}
+%\end{equation}
+%%
+%Note \refeq{stair} holds for every divisor $c$ of $n$ ($c > 1$). We now have
+%
+%
+%
+%\begin{theorem}
+%An $n$-cycle and a shorter $d$-cycle ($d|n$, $d< n$)
+%  intersect only at the onset of the $n$-cycle,
+%%
+%and $\prod_{k=1}^{d} f'(x_k) = (-2)^d x_1 \dots x_d$ is
+%a \emph{primitive} $(n/d)$th root of unity there.
+%\label{thm:cbifur}
+%\end{theorem}
+%
+%
+%\begin{proof}
+%At the intersection of the $n$- and $d$-cycles,
+%  $x_l$ repeats itself after $d$ steps, so
+%  $x_{d + l} = x_l$;
+%and \refeq{stair} becomes,
+%%
+%\begin{equation}
+%  1 + q + \dots + q^{c-1} = 0,
+%\label{eq:cbifur}
+%\end{equation}
+%%
+%where $q = (-2)^d \, x_1 \dots x_d$.
+%%
+%Multiplying \refeq{cbifur} by $q - 1$ yields
+%  $1 = q^c = (-2)^n \, x_1 \dots x_n$.
+%So the $n$-cycle is at its onset.
+%
+%
+%Further $q$ is a \emph{primitive} $c$th root of unity.
+%%
+%Suppose the contrary: $q = e^{2k\pi i/c}$ and $(k, c) = g >1$,
+%  then by $c_1 \equiv c/g$, $k_1 \equiv k/g$, we have
+%\begin{equation}
+%  q = e^{2k_1\pi i/ c_1}.
+%\label{eq:qd}
+%\end{equation}
+%Similar to \refeq{cbifur}, we can apply \refeq{stair} with $c \rightarrow g$ and $d \rightarrow d c_1$, and
+%\[
+%  1 + q_1 + \dots + {q_1}^{g-1} = 0,
+%\]
+%  where $q_1 = (-2)^{d c_1} \, x_1 \dots x_{dc_1} = q^{c_1}$.
+%But by \refeq{qd}, $q^{c_1} = e^{2 k_1\pi i} = 1$,
+%and $1 + q_1 + \dots + {q_1}^{g-1} = g > 0$; a contradiction.
+%%
+%\end{proof}
+%
+%
+%\begin{remark}
+%The only real $q$ is $q = -1$ for $c=2$, i.e., a period-doubling.
+%%
+%On the complex domain, however, we can have a $c$-fold branching with $c>2$,
+%  which corresponds to a contact points between ``bulbs''
+%  in the inverted Mandelbrot set.
+%\end{remark}
+%
+%By \refthm{cbifur}, $P_n\Rlam$ at the onset point
+%includes $P_d(R, e^{2 k \pi i/c} \lambda^{1/c})$ for every
+%  possible combination of $k$ and $c$, such that
+%  $(k, c) = 1$, $c|n$, and $c > 1$.
+%
+%Dividing the factors from $P_n\Rlam$ yields \refthm{origfac}.
+
+\subsection{\label{sec:degR}Degrees in $R$}
+
+%\begin{theorem}
+The degrees in $R$ of $A_n\Rlam$, $P_n\Rlam$ and $S_n(R)$ are
+\begin{subequations}\small
+\begin{align}
+\deg_R A_n\Rlam &= \sum_{d|n} \varphi(n/d) 2^{d-1}, \\
+\deg_R P_n\Rlam &\equiv \beta(n) = \sum_{d|n} \mu(n/d) 2^{d-1}, \\
+\deg S_n(R) &= \beta(n) - \sum_{d | n, d < n} \beta(d) \, \varphi(n/d).
+\end{align}
+\label{eq:degR}
+\end{subequations}
+%\label{thm:degR}
+%\end{theorem}
+%
+%
+%
+\begin{proof}
+We first prove \refeqsub{degR}{a}.
+%
+We recall the subscript $p$ of $C_p$ denotes a sequence of indices $k$
+  in the generating monomial $\prod_k {x_k}^{e_k}$.
+But for a square-free cyclic polynomial,
+  each $k$ occurs no more than once,
+so $p$ also represents a \emph{set} of indices,
+%
+e.g.,
+$p = 1$ represents $\{1\}$,
+  ($C_1 = x_1 + \dots + x_n$, generator: $x_1$)
+and
+$p = 13$ represents $\{1, 3\}$
+  ($C_{13} = x_1 \, x_3 + x_2 \, x_4 + \dots + x_n \, x_2$,
+  generator: $x_1 \, x_3 $, assuming $n \ge 4$).
+%more examples are listed in \reftab{sqrfreepoly}).
+%
+In this proof,
+we shall also use $p$ to denote the corresponding index set,
+  $|p|$ the set size, i.e., the number of indices in the set,
+  and
+  $\bar p \equiv \{1,\ldots,n\} \backslash p$ the complementary set.
+%
+Obviously, $|\bar p| + |p| = n$.
+%
+Further, we will include $p$ that correspond to alternative generators
+  of the same cyclic polynomial,
+e.g., we allow $p = \{2\}$, $\{3\}$, \dots, $\{n\}$,
+  although they represent the same cyclic polynomial $C_1$
+  as $p = \{1\}$.
+
+Next, we recall the matrix elements $T_{pq}(R)$ arise from the square-free reduction
+of $\Lambda(\vx) C_p(\vx) = (-2)^n x_1 \dots x_n \, C_p(\vx)$.
+%
+A single replacement ${x_k}^2 \rightarrow R - x_{k+1}$
+produces two new terms:
+in the first, ${x_k}^2 \rightarrow R$,
+and in the second, ${x_k}^2 \rightarrow - x_{k+1}$.
+We call the two type 1 and type 2 replacements, respectively.
+%
+If a monomial term $t(R, \vx)$
+results from $l_1$ type 1 and $l_2$ type 2 replacements
+during the reduction of a term $s(\vx)$ in $\Lambda(\vx) C_p(\vx)$,
+then the degrees in $\vct x$, for any $x_k$, of $s(\vx)$ and $t(R, \vx)$
+are related as
+%
+\begin{equation}
+  \deg_\vx s(\vx) - \deg_\vx t(R, \vx) = 2 l_1 + l_2.
+\label{eq:degxdiffst}
+\end{equation}
+%
+Similarly, the degrees in $R$ satisfy
+\[
+  \deg_R s(\vx) - \deg_R t(R, \vx) = - l_1,
+\]
+but since $\deg_R s(\vx) = 0$,
+\begin{equation}
+  \deg_R t(R, \vx) = l_1.
+\label{eq:degRt}
+\end{equation}
+
+%
+Now if the monomial $t(R, \vx)$ settles in the $q$th column of
+  the matrix $\vct T(R)$, as part
+  of $T_{pq}(R) C_q(\vx)$ in \refeq{xcp0},
+then
+  $t(R, \vx)$
+  must be
+%the product of
+%  a monomial of $R$ \big[as part of $T_{pq}(R)$\big]
+%  and one of the
+  a generator of $C_q(\vx)$;
+so
+%
+\begin{equation}
+  \deg_\vx t(R, \vx) = |q|.
+\label{eq:degxt}
+\end{equation}
+%
+Since $s(\vx)$ is part of $\Lambda(\vx) C_p(\vx)$,
+  we have
+%
+\begin{equation}
+  \deg_\vx s(\vx) = \deg_\vx \Lambda(\vx) + \deg_\vx C_p(\vx)
+  = n + |p|.
+\label{eq:degxs}
+\end{equation}
+%
+%
+From \refeqs{degxdiffst}, \req{degxt}, \req{degxs}, we get
+\[
+  n + |p| - |q| = 2 \, l_1 + l_2,
+\]
+and
+\begin{equation}
+  l_1  =    (n + |p| - |q| - l_2)/2
+             \le  (n + |p| - |q|)/2.
+\label{eq:l1limit}
+\end{equation}
+By \refeq{degRt}, we get
+\begin{align*}
+  \deg_R T_{pq}(R)
+  = \max\{ \deg_R t(R, \vx) \}
+  = \max\{ l_1 \}
+  \le   (n + |p| - |q|)/2,
+\end{align*}
+where the equality holds when all replacements are type 1 ($l_2 = 0$).
+%
+Finally, each term of the determinant
+$A_n\Rlam = \big|\lambda \, \vct I - \vct T(R)\big|$
+is given by
+$(-1)^s \prod_{p} \big[\lambda \, \delta_{p q} - T_{pq}(R)\big]$,
+where $p$ runs through rows of the matrix
+  and $\{q\}$ is a permutation of $\{p\}$,
+  with $(-1)^s$ being the proper sign.
+%
+Summing over rows under this condition yields
+\begin{align*}
+  \deg_R A_n\Rlam
+  = \max \sum_{p \in \Pset} \deg T_{pq}(R)
+  \le \NB \, \big(n + |p| - |q|\big)/2 = n \NB/2,
+\end{align*}
+where equality can be achieved if $q = \bar p$ in every row.
+By \refeq{necklace} we have \refeqsub{degR}{a}.
+%
+\refeqsub{degR}{b} and (c) follow from taking taking the degree in $R$ of
+  \refeq{prod} and \refeq{origfac}.
+\refeqsub{degR}{b} and (\ref{eq:degR}c) were known \cite{mira, stephenson1, blackhurst}.
+%
+\end{proof}
+%
+The first few $\deg_R A_n\Rlam$,
+  $\deg_R P_n\Rlam$,
+  and $\deg S_n(R)$ are
+  1, 3, 6, 12, 20, 42, 70, 144, 270, 540, \dots,  %1034, 2112, 4108, \dots,
+  1, 1, 3, 6, 15, 27, 63, 120, 252, 495, \dots, %1023, 2010, 4095, \dots,
+  1, 0, 1, 3, 11, 20, 57, 108, 240, 472, \dots, % 1013, 1959, 4083, \dots,
+  respectively, from $n = 1$.
 
@@
 
-\subsection{\label{sec:primfac}Minimal polynomial of the $n$-cycles}
-
-The characteristic polynomial $A_n\Rlam$ in \refeq{xr}
-  is derived for the fixed points of $f^n$.
-Thus, it represents not only the $n$-cycles,
-  but also cycles of shorter periods $d$ ($d|n$).
-%
-We can remove the contributions from the shorter cycles by the following theorem.
-
-\begin{theorem}
-  The minimal polynomial $P_n\Rlam$ of all $n$-cycles
-  is a factor of the characteristic polynomial $A_n\Rlam$,
-  and can be computed as
-  \begin{equation}
-    P_n\Rlam
-    = \prod_{cd = n} B_{d,c}\Rlam^{\mu(c)},
-  \label{eq:primfac}
-  \end{equation}
-where
-  $B_{d, c}\Rlam \equiv \prod_{k=1}^c A_{d}(R, e^{2k\pi i/c} \lambda^{1/c})$,
-  $\lambda^{1/c}$ is a complex $c$th root of $\lambda$,
-  and $\mu(c)$ is the M\"obius function.
-  \label{thm:primfac}
-\end{theorem}
-%
-%
-%\begin{remark}
-%Here, ``minimal'' means that the polynomial contains all zeros.
-%It happens to be irreducible for a general $\lambda$.
-%At $\lambda = 1$, the polynomial of $R$, however, can be factorized (see later).
-%\end{remark}
-%
-\begin{remark}
-The M\"obius function $\mu(n)$ is $(-1)^k$
-  if $n$ is the product of $k$ distinct primes,
-  or 0 if $n$ is divisible by a square of a prime.
-%Thus,
-$\mu(n)$ = 1, $-1$, $-1$, 0, $-1$, 1, \ldots,
-  from $n = 1$%.
-%The $\mu(n)$ is useful for inversion:
-%$g(n) = \sum_{d|n} \mu(n/d) \, h(d)$
-%if and only if $h(n) = \sum_{d|n} g(d)$
-\cite{hardy}.
-\end{remark}
-%
-%
-\begin{remark}
-%$B_{d,c}\Rlam$ is a polynomial of $\lambda$.
-Despite the argument $\lambda^{1/c}$,
-  the product $\prod_{k=1}^c A_d(R, e^{2k\pi i/c} \lambda^{1/c})$,
-  hence $B_{d,c}\Rlam$,
-  is free from radicals of powers of $\lambda^{1/c}$,
-  for it is invariant under $\lambda \rightarrow e^{2\pi i} \lambda$.
-Thus, $B_{d, c}\Rlam$ is a polynomial of $\lambda$,
-and $\deg_\lambda B_{d,c}\Rlam = \deg_\lambda A_d\Rlam$.
-Particularly, $B_{n,1}\Rlam = A_n\Rlam$.
-\end{remark}
-%
-%
-%We will refer to $P_n\Rlam$ as the \emph{primitive factor} below.
-%
-%
-Let us apply \refeq{primfac}
-to the examples in \refsec{examples}.
-We will omit the argument $R$ below for convenience.
-%%
-For $n = 1$,
-%there is no irrelevant factor in \refeq{xr1} and
-$P_1(\lambda) = B_{1,1}(\lambda) = A_1(\lambda)
-  = \lambda^2 - 2\,\lambda - 4\,R$.
-%
-%
-%
-For $n = 2$, since
-$B_{1,2}(\lambda)
-=
-A_1(\sqrt{\lambda})
-A_1(-\sqrt{\lambda})
-=
-(4R-\lambda)^2 -4\lambda$,
-%
-$P_2(\lambda) = A_2(\lambda) \, B_{1,2}(\lambda)^{-1} = 4R - 4 + \lambda$.
-%
-%
-For $n = 4$,
-%we have
-%$16 (R-1)^2 - \lambda
-%= (4R - 4 + \sqrt{\lambda})(4R - 4 - \sqrt{\lambda})$
-%and
-%$
-%(16 R^2 + \lambda)^2 - 16 (2R+1)^2 \lambda
-%=
-%\big[(4R - \sqrt{\lambda})^2  - 4\sqrt{\lambda}\,\big]
-%\big[(4R + \sqrt{\lambda})^2  + 4\sqrt{\lambda}\,\big]$.
-%Thus,
-we can show that
-the last two factors of \refeq{xr4}
-can be written as
-$B_{2,2}(\lambda) = A_2(\sqrt{\lambda}) A_2(-\sqrt{\lambda})$,
-and
-%
-$P_4(\lambda)
-    = A_4(\lambda) \, B_{2,2}(\lambda)^{-1}$
-indeed the yields the sextic factor.
-%$    = 4096 R^6-12288 R^5+ 256 (\lambda + 48) (R^4- R^3)
-%    -16(\lambda + 32)(\lambda - 16) R^2 - (\lambda-16)^3$.
-Note, $B_{1,4}(\lambda)$ is unused for $\mu(4) = 0$.
-
-For $n \ge 4$,
-  $P_n\Rlam$ can be easily recognized,
-  without using \refthm{primfac},
-  as the factor of $A_n\Rlam$
-  with the highest degree in $R$.
-  %see \reftab{Anlog} and \refsec{degR}.
-It can be, however, problematic,
-   if $P_n(R, \lambda)$ is solved for $\lambda = 1$
-   instead of a general $\lambda$,
-   for $P_n(R, 1)$ itself can be further factorized.
-%
-Due to the technical nature of the derivation and subsequent discussions,
-  the reader may wish to skip the rest of \refsec{logmap}
-  on first reading.
-
-\subsection{\label{sec:degprimfac}Counting cycles}
-
-%We will prove \refthm{primfac} by the following steps.
-%
-To show \refthm{primfac}, we first find the degrees in $\lambda$ of
-  $A_n\Rlam$ (\refeq{necklace}) and $P_n\Rlam$ (\refeq{lyndon}).
-By comparing the degrees,
-  we then show that each $P_d\Rlam$ with ($d|n$),
-  after some transformation,
-  contributes one polynomial factor to $A_n\Rlam$
-  (\refeq{prod}),
-  and the inversion of the relation
-  yields \refthm{primfac}.
-
-\subsubsection{Number of the square-free cyclic polynomials}
-
-To count the square-free cyclic polynomials,
-  we establish a one-to-one mapping
-  between the square-free cyclic polynomials
-  and the binary necklaces.
-%
-A binary necklace
-  is a nonequivalent binary $0$-$1$ string.
-%
-Two strings are equivalent if they differ only by a circular shift.
-%
-For example, for $n = 3$, there are $2^3 = 8$ binary strings,
-but only four necklaces: 000, 001, 011 and 111,
-since 010 and 100 are equivalent to 001,
-so are 110 and 101 to 011.
-%
-If the generator of the cyclic polynomial contains $x_k$,
-  the $k$th character from the left of the necklace is 1,
-  otherwise 0,
-e.g. the above four necklaces correspond to
-  $C_0$, $C_1$, $C_{12}$ and $C_{123}$, respectively.
-%For example, if $n = 3$,
-% the square-free polynomials for $000$, $100$, $110$ and $111$ are
-%  $C_0 = 1$ (generator: 1),
-%  $C_1 = x_1 + x_2 + x_3$ (generator: $x_1$),
-%  $C_{12} = x_1 x_2 + x_2 x_3 + x_3 x_1$ (generator: $x_1 x_2$)
-%  and $C_{123} = x_1 x_2 x_3$ (generator: $x_1 x_2 x_3$), respectively.
-Thus,
-%
-%\begin{theorem}
-the number $\NB(n)$ of the square-free cyclic polynomials $C_p(\vx)$
-  formed by the cycle points $\vx = \{x_1, \ldots, x_n\}$,
-  which is also $\deg_\lambda A_n\Rlam$, is given by
-\begin{equation}
-  %\deg_\lambda A_n\Rlam =
-  \NB(n) = N(n) = (1/n) \textstyle\sum_{d|n} \varphi(n/d) 2^{\,d}.
-\label{eq:necklace}
-\end{equation}
-%
-%\label{thm:necklace}
-%\end{theorem}
-%
-Here, $\varphi(m)$ is Euler's totient function,
-which gives the number of integers from 1 to $m$
-  that are coprime to $m$,
-  e.g.,
-  $\varphi(1) = 1$,
-  $\varphi(3) = 2$ for 1 and 2,
-  $\varphi(6) = 2$ for 1 and 5.
-The first few $N_\Pset(n)$ are 2, 3, 4, 6, 8, 14, 20, 36, 60, 108, 188, 352, 632, \ldots,
-  from $n = 1$.
-
-\subsubsection{Number of the $n$-cycles}
-
-%\begin{theorem}
-The degree in $\lambda$ of the minimal polynomial $P_n\Rlam$ of all $n$-cycles
-  is equal to the number of the $n$-cycles,
-  which is given by
-\begin{equation}
-  %\deg_\lambda P_n\Rlam =
-  L(n) = (1/n)\textstyle\sum_{d | n} \mu(n/d) 2^{\,d}.
-\label{eq:lyndon}
-\end{equation}
-%\label{thm:lyndon}
-%\end{theorem}
-%
-%
-\begin{proof}
-Let $\lambda_c$ be the value of $\Lambda(\vx^c)$
-  evaluated at the $c$th cycle.
-The minimal polynomial $P_n\Rlam$
-  can be written as $\prod_c (\lambda - \lambda_c)$,
-  and $\deg_\lambda P_n\Rlam$ is the same as
-  the number $L(n)$ of $n$-cycles, which is known \cite{hao, hao2, lutzky}.
-\end{proof}
-%
-%
-The first few values of $L(n)$ are
-2, 1, 2, 3, 6, 9, 18, 30, 56, 99, 186, 335, 630, \ldots,
-from $n = 1$.
-%
-Incidentally, $L(n)$ is also the number of aperiodic necklaces of length $n$.
-  In the $n = 4$ case,
-  $0001$, $0011$, and $0111$ are aperiodic;
-  but $0000$, $1111$, and $0101$ are not
-  owing to the shorter periods 1, 2, and 2, respectively.
-%
-Since an $n$-necklace is either aperiodic itself or
-  a repeated aperiodic $d$-necklace (with $d|n$),
-  we have
-\begin{equation}
-  N(n) = \textstyle\sum_{d|n} L(d).
-\label{eq:necklacelyndon}
-\end{equation}
-%
-
-\subsubsection{Relation between $P_n$ and $A_n$}
-
-%\begin{theorem}
-The minimal polynomials $P_d\Rlam$ of all $d$-cycles
-  of periods $d|n$
-and $A_n\Rlam$ [defined in \refeq{xr}] are related by
-  \begin{equation}
-    A_n\Rlam = \prod_{cd = n} Q_{d, c}\Rlam,
-    \label{eq:prod}
-  \end{equation}
-  where
-  $Q_{d,c}\Rlam = \prod_{k=1}^{c} P_d(R, e^{2 k \pi i/c} \lambda^{1/c})$
-  is a polynomial of degree $L(d)$ in $\lambda$
-  representing contributions from $d$-cycles.
-%encompassed by $A_n\Rlam$.
-%\label{thm:prod}
-%\end{theorem}
-
-\begin{proof}
-Since $A_n\Rlam$ represent all $d$-cycles with $d|n$,
-and each cycle holds a distinct $\lambda$,
-  $\deg_\lambda A_n\Rlam$
-  is at least $\sum_{d|n} L(d)$
-  according to \refeq{lyndon},
-  which is equal to
-  $N(n)$ by \refeq{necklacelyndon}.
-Since $\deg_\lambda A_n\Rlam = N(n)$ by \refeq{necklace},
-  each $n$-cycle occurs exactly once in $A_n\Rlam$.
-
-In a $d$-cycle,
- we have $\Lambda(\{x_1, \ldots, x_n\}) = (-2)^n x_1 \dots x_n
-   = {\Lambda_d}^c$,
-where
-$\Lambda_d(\{x_1, \ldots, x_d\}) \equiv (-2)^d x_1 \dots x_d$
-and
-$c \equiv n/d$.
-So the $d$-cycle satisfies a polynomial
-  $P_d(R, \lambda^{1/c}) = 0$,
-where $\lambda = \Lambda(\{x_1,\ldots,x_n\})$.
-%
-This is, however, not a polynomial equation, and
-%
-the radical $\lambda^{1/c}$ can be removed by the product
-$Q_{d,c}\Rlam
-  \equiv \prod_{k=1}^c P_d(R, e^{2k\pi i/c} \, \lambda^{1/c}) = 0$.
-%
-Now $Q_{d,c}\Rlam$ is a polynomial of $\lambda$
-  for it is invariant under
-  $\lambda \rightarrow e^{2\pi i} \lambda$,
-and thus free from radicals of the form $\lambda^{l/c}$
-  \big[if $(l, c) \ne c$\big].
-And since
-  $\deg_\lambda Q_{d,c}\Rlam
-    = \deg_\lambda P_d\Rlam = L(d)$,
-  it is also a polynomial
-  of the lowest possible degree in $\lambda$.
-
-Therefore, the product $\prod_{cd=n} Q_{d,c}\Rlam$
-  can differ from $A_n\Rlam$ only by
-  a multiple.
-Since $Q_{n,1}\Rlam = P_n\Rlam$,
-  and the coefficient of highest power of $\lambda$ is always
-  unity in $A_n\Rlam$ \big[see the definition \refeq{xr}\big],
-  we know by induction that the coefficients of the highest power of $\lambda$
-  in all $P_n\Rlam$ and $Q_{d,c}\Rlam$
-  are also unities.
-So the multiple is one, hence \refeq{prod}.
-%
-%
-%
-\end{proof}
-
-\refeq{primfac} is a corollary of \refeq{prod},
-\begin{small}
-\begin{align*}
- B_{n, m} (\lambda)
-% & = \prod_{l = 1}^{m} A_n(e^{2l\pi i/m} \lambda^{1/m}) \\
- & = \prod_{c | n} \prod_{l=1}^m \prod_{k=1}^c
-    P_{n/c}(e^{\frac{2k\pi i}{c} + \frac{2l\pi i}{m c}} \lambda^{1/(m c)}) \\
- & = \prod_{c | n} \prod_{k'=1}^{m c}
-    P_{n/c}(e^{2k'\pi i/(m c)} \lambda^{1/(m c)}) \\
- & = \prod_{c | n} Q_{n /c, m c}(\lambda).
-\end{align*}
-\end{small}
-The M\"obious inversion yields
-\begin{equation}
-  Q_{n, m}\Rlam
-= \prod_{d|n} B_{d, m n/d}\Rlam^{\mu(n/d)},
-\notag
-%\tag{$\ref{eq:primfac}'$}
-\end{equation}
-which is reduced to \refeq{primfac} with $m = 1$,
-for $Q_{n, 1}\Rlam = P_n\Rlam$.
-
-\subsection{\label{sec:origfac}%Intersection of cycles and
-  Factors at the onset point}
-
-The onset polynomial
-  $P_n(R, \lambda = 1)$ for the $n$-cycles
-  can be further factorized.
-%
-This is caused by the intersection of an $n$-cycle
-  and a shorter $d$-cycle ($d|n$, $d < n$),
-  which forces the two to share orbit.
-%
-One can show that this intersection happens only
-  at the onset of the $n$-cycle, where $\lambda = 1$,
-%
-  and the $d$-cycle branches out, or ``bifurcates'', $n/d$-fold
-  to become the $n$-cycle.
-%
-The simplest example is the first bifurcation point
-  at $R = 3/4$ for $d = 1, n = 2$,
-  where the fixed point \refeq{xr1}
-  undergoes period-doubling and becomes the 2-cycle \refeq{xr2}.
-As a result, the polynomial $P_n(R, \lambda)$ from the $n$-cycle
-  has to accommodate $P_d(R, \lambda')$ from the $d$-cycle as a factor,
-  with $\lambda'$ being a primitive $(n/d)\,$th root of $\lambda = 1$.
-
-If an $n$-cycle is not born out of the above branching,
-  we call it \emph{original}.
-The two types of cycles exist
-  as separate factors of $P_n(R, \lambda = 1)$.
-One can then show that the factor $S_n(R)$ responsible for the original cycles
-  %or the \emph{original factor} below,
-  is given by
-  \begin{equation}
-    S_n(R)
-    = \frac
-    {
-      P_n(R, 1)
-    }
-    {
-      \prod_{c d =  n, \; c > 1}
-      %\left[ \,
-        \prod_{(k, c) = 1}
-      P_{d}
-        \left(
-          R, e^{2k\pi i/c}
-        \right)
-      %\right]
-    },
-  \label{eq:origfac}
-  \end{equation}
-where the inner product on the denominator is carried over
-   $k$ from 1 to $c$ that are coprime to $c$.
-
-Take the $n = 4$ case as an example, we have
-$\prod_{k=1,3} P_1(R, e^{k\pi i/2})
-%=(-4R-2i-1)(-4R+2i-1)
-=16R^2+8R+5$
-(for $c = 4$),
-$P_2(R, -1) = 4R - 5$
-(for $c = 2$),
-and
-$P_4(R, 1)
-= (4R - 5) (16 R^2 + 8 R + 5)
-  \bigl[
-    (4R - 3)^3 - 108
-  \bigr]$.
-Dividing $P_4(R, 1)$ by the two factors yields
-$S_4(R) = (4R-3)^3 - 108$,
-  whose only real root $R_a=(3+\sqrt[3]{108})/4$ corresponds to
-  the onset of the original cycle.
-Note $R_a' = 5/4$ is excluded from $S_4(R)$
-  as it is due to period-doubling the 2-cycle.
-The two cycles are compared in \reffigs{cobweb}(d) and (e).
-
-%We now prove \refthm{origfac}.
-%Suppose $n = c \,d$, we have, from \refeq{logmaps},
-%\[
-%  x_{l+1} - x_{d+l+1} = - (x_l + x_{d+l}) (x_l - x_{d+l}).
-%\]
-%We apply the equation to $l = 1, \ldots, m$, and the product is
-%\[
-%  x_{m+1} - x_{m + d+1} =
-%  (-1)^{m} \left[ \, \prod_{l=1}^{m} (x_l + x_{d+l}) \right]
-%    (x_1 - x_{d+1}).
-%\]
-%We now set $m$ to $0, d, \ldots, (c-1)\,d$ in this equation,
-%  add them together, eliminate $x_1 - x_{d+1}$
-%  (which is nonzero in a cycle), and
-%\begin{equation}
-%  \sum_{c' = 0}^{c-1}
-%    (-1)^{c' d} \prod_{l=1}^{c' d} (x_l + x_{d+l})
-%   = 0.
-%\label{eq:stair}
-%\end{equation}
-%%
-%Note \refeq{stair} holds for every divisor $c$ of $n$ ($c > 1$). We now have
-%
-%
-%
-%\begin{theorem}
-%An $n$-cycle and a shorter $d$-cycle ($d|n$, $d< n$)
-%  intersect only at the onset of the $n$-cycle,
-%%
-%and $\prod_{k=1}^{d} f'(x_k) = (-2)^d x_1 \dots x_d$ is
-%a \emph{primitive} $(n/d)$th root of unity there.
-%\label{thm:cbifur}
-%\end{theorem}
-%
-%
-%\begin{proof}
-%At the intersection of the $n$- and $d$-cycles,
-%  $x_l$ repeats itself after $d$ steps, so
-%  $x_{d + l} = x_l$;
-%and \refeq{stair} becomes,
-%%
-%\begin{equation}
-%  1 + q + \dots + q^{c-1} = 0,
-%\label{eq:cbifur}
-%\end{equation}
-%%
-%where $q = (-2)^d \, x_1 \dots x_d$.
-%%
-%Multiplying \refeq{cbifur} by $q - 1$ yields
-%  $1 = q^c = (-2)^n \, x_1 \dots x_n$.
-%So the $n$-cycle is at its onset.
-%
-%
-%Further $q$ is a \emph{primitive} $c$th root of unity.
-%%
-%Suppose the contrary: $q = e^{2k\pi i/c}$ and $(k, c) = g >1$,
-%  then by $c_1 \equiv c/g$, $k_1 \equiv k/g$, we have
-%\begin{equation}
-%  q = e^{2k_1\pi i/ c_1}.
-%\label{eq:qd}
-%\end{equation}
-%Similar to \refeq{cbifur}, we can apply \refeq{stair} with $c \rightarrow g$ and $d \rightarrow d c_1$, and
-%\[
-%  1 + q_1 + \dots + {q_1}^{g-1} = 0,
-%\]
-%  where $q_1 = (-2)^{d c_1} \, x_1 \dots x_{dc_1} = q^{c_1}$.
-%But by \refeq{qd}, $q^{c_1} = e^{2 k_1\pi i} = 1$,
-%and $1 + q_1 + \dots + {q_1}^{g-1} = g > 0$; a contradiction.
-%%
-%\end{proof}
-%
-%
-%\begin{remark}
-%The only real $q$ is $q = -1$ for $c=2$, i.e., a period-doubling.
-%%
-%On the complex domain, however, we can have a $c$-fold branching with $c>2$,
-%  which corresponds to a contact points between ``bulbs''
-%  in the inverted Mandelbrot set.
-%\end{remark}
-%
-%By \refthm{cbifur}, $P_n\Rlam$ at the onset point
-%includes $P_d(R, e^{2 k \pi i/c} \lambda^{1/c})$ for every
-%  possible combination of $k$ and $c$, such that
-%  $(k, c) = 1$, $c|n$, and $c > 1$.
-%
-%Dividing the factors from $P_n\Rlam$ yields \refthm{origfac}.
-
-\subsection{\label{sec:degR}Degrees in $R$}
-
-%\begin{theorem}
-The degrees in $R$ of $A_n\Rlam$, $P_n\Rlam$ and $S_n(R)$ are
-\begin{subequations}\small
-\begin{align}
-\deg_R A_n\Rlam &= \sum_{d|n} \varphi(n/d) 2^{d-1}, \\
-\deg_R P_n\Rlam &\equiv \beta(n) = \sum_{d|n} \mu(n/d) 2^{d-1}, \\
-\deg S_n(R) &= \beta(n) - \sum_{d | n, d < n} \beta(d) \, \varphi(n/d).
-\end{align}
-\label{eq:degR}
-\end{subequations}
-%\label{thm:degR}
-%\end{theorem}
-%
-%
-%
-\begin{proof}
-We first prove \refeqsub{degR}{a}.
-%
-We recall the subscript $p$ of $C_p$ denotes a sequence of indices $k$
-  in the generating monomial $\prod_k {x_k}^{e_k}$.
-But for a square-free cyclic polynomial,
-  each $k$ occurs no more than once,
-so $p$ also represents a \emph{set} of indices,
-%
-e.g.,
-$p = 1$ represents $\{1\}$,
-  ($C_1 = x_1 + \dots + x_n$, generator: $x_1$)
-and
-$p = 13$ represents $\{1, 3\}$
-  ($C_{13} = x_1 \, x_3 + x_2 \, x_4 + \dots + x_n \, x_2$,
-  generator: $x_1 \, x_3 $, assuming $n \ge 4$).
-%more examples are listed in \reftab{sqrfreepoly}).
-%
-In this proof,
-we shall also use $p$ to denote the corresponding index set,
-  $|p|$ the set size, i.e., the number of indices in the set,
-  and
-  $\bar p \equiv \{1,\ldots,n\} \backslash p$ the complementary set.
-%
-Obviously, $|\bar p| + |p| = n$.
-%
-Further, we will include $p$ that correspond to alternative generators
-  of the same cyclic polynomial,
-e.g., we allow $p = \{2\}$, $\{3\}$, \dots, $\{n\}$,
-  although they represent the same cyclic polynomial $C_1$
-  as $p = \{1\}$.
-
-Next, we recall the matrix elements $T_{pq}(R)$ arise from the square-free reduction
-of $\Lambda(\vx) C_p(\vx) = (-2)^n x_1 \dots x_n \, C_p(\vx)$.
-%
-A single replacement ${x_k}^2 \rightarrow R - x_{k+1}$
-produces two new terms:
-in the first, ${x_k}^2 \rightarrow R$,
-and in the second, ${x_k}^2 \rightarrow - x_{k+1}$.
-We call the two type 1 and type 2 replacements, respectively.
-%
-If a monomial term $t(R, \vx)$
-results from $l_1$ type 1 and $l_2$ type 2 replacements
-during the reduction of a term $s(\vx)$ in $\Lambda(\vx) C_p(\vx)$,
-then the degrees in $\vct x$, for any $x_k$, of $s(\vx)$ and $t(R, \vx)$
-are related as
-%
-\begin{equation}
-  \deg_\vx s(\vx) - \deg_\vx t(R, \vx) = 2 l_1 + l_2.
-\label{eq:degxdiffst}
-\end{equation}
-%
-Similarly, the degrees in $R$ satisfy
-\[
-  \deg_R s(\vx) - \deg_R t(R, \vx) = - l_1,
-\]
-but since $\deg_R s(\vx) = 0$,
-\begin{equation}
-  \deg_R t(R, \vx) = l_1.
-\label{eq:degRt}
-\end{equation}
-
-%
-Now if the monomial $t(R, \vx)$ settles in the $q$th column of
-  the matrix $\vct T(R)$, as part
-  of $T_{pq}(R) C_q(\vx)$ in \refeq{xcp0},
-then
-  $t(R, \vx)$
-  must be
-%the product of
-%  a monomial of $R$ \big[as part of $T_{pq}(R)$\big]
-%  and one of the
-  a generator of $C_q(\vx)$;
-so
-%
-\begin{equation}
-  \deg_\vx t(R, \vx) = |q|.
-\label{eq:degxt}
-\end{equation}
-%
-Since $s(\vx)$ is part of $\Lambda(\vx) C_p(\vx)$,
-  we have
-%
-\begin{equation}
-  \deg_\vx s(\vx) = \deg_\vx \Lambda(\vx) + \deg_\vx C_p(\vx)
-  = n + |p|.
-\label{eq:degxs}
-\end{equation}
-%
-%
-From \refeqs{degxdiffst}, \req{degxt}, \req{degxs}, we get
-\[
-  n + |p| - |q| = 2 \, l_1 + l_2,
-\]
-and
-\begin{equation}
-  l_1  =    (n + |p| - |q| - l_2)/2
-             \le  (n + |p| - |q|)/2.
-\label{eq:l1limit}
-\end{equation}
-By \refeq{degRt}, we get
-\begin{align*}
-  \deg_R T_{pq}(R)
-  = \max\{ \deg_R t(R, \vx) \}
-  = \max\{ l_1 \}
-  \le   (n + |p| - |q|)/2,
-\end{align*}
-where the equality holds when all replacements are type 1 ($l_2 = 0$).
-
-Finally, each term of the determinant
-$A_n\Rlam = \big|\lambda \, \vct I - \vct T(R)\big|$
-is given by
-$(-1)^s \prod_{p} \big[\lambda \, \delta_{p q} - T_{pq}(R)\big]$,
-where $p$ runs through rows of the matrix
-  and $\{q\}$ is a permutation of $\{p\}$,
-  with $(-1)^s$ being the proper sign.
-%
-Summing over rows under this condition yields
-\begin{align*}
-  \deg_R A_n\Rlam
-  = \max \sum_{p \in \Pset} \deg T_{pq}(R)
-  \le N(n) \, \big(n + |p| - |q|\big)/2 = n N(n)/2,
-\end{align*}
-where equality can be achieved if $q = \bar p$ in every row.
-By \refeq{necklace} we have \refeqsub{degR}{a}.
-
-\refeqsub{degR}{b} and (c) follow from taking taking the degree in $R$ of
-  \refeq{prod} and \refeq{origfac}.
-\refeqsub{degR}{b} and (\ref{eq:degR}c) were known \cite{mira, stephenson1, blackhurst}.
-%
-\end{proof}
-%
-The first few values of $\deg_R A_n\Rlam$,
-  $\deg_R P_n\Rlam$,
-  and $\deg S_n(R)$ are
-  1, 3, 6, 12, 20, 42, 70, 144, 270, 540, 1034, 2112, 4108, \dots,
-  1, 1, 3, 6, 15, 27, 63, 120, 252, 495, 1023, 2010, 4095, \dots,
-  1, 0, 1, 3, 11, 20, 57, 108, 240, 472, 1013, 1959, 4083, \dots,
-  respectively (starting from $n = 1$).
+\subsection{\label{sec:end}Implementation}
+
+Let us summarize the algorithm.
+%
+First, we list \refeqs{xcp}  with $\Lambda(\vx) = \prod_{k=1}^n f'(x_k)$.
+This step populates elements of the matrix $\vct T$.
+%
+The characteristic equation $A_n(\lambda) = \big|\lambda \, \vct I - \vct T\big| = 0$,
+with $\lambda$ being $+1$ and $-1$, then gives
+the polynomials at onset and bifurcation points, respectively.
+%
+To filter out the contributions from shorter $d$-cycles with $d|n$,
+  we repeat compute the characteristic equations for all divisors $d$
+  and then apply \req{primfac}.
+%
+
+When implemented on a computer,
+it is often helpful to evaluate $A_n(\lambda)$ by Lagrange interpolation,
+that is, we evaluate $A_n(r, \lambda)$ at a few different $r$,
+e.g., $r = 0, \pm1, \pm2,\ldots$, then piece them together
+to a polynomial.
+The strategy also allows a trivial parallelization.
+%
+The algorithm was coded into a Mathematica program,
+which was used to compute the polynomials for $n$ up to 13.
+%
+For polynomials of larger $n$ are saved in in the website in \refsec{end}.
+%
+The representative $r$ values are listed in \reftab{rval}.
+%
+
+The algorithm (implemented as a Mathematica program)
+was quite efficient.
+%
+For the logistic map, the bifurcation point for $n = 8$
+took three seconds to compute on a desktop computer
+(single core, Intel\textsuperscript{\textregistered} Dual-Core CPU 2.50GHz).
+%
+In comparison,
+  the same problem took roughly 5.5 hours \cite{kk1}
+  using Gr\"obner basis
+  and 44 minutes in a later study \cite{lewis}.
+To be fair, using the latest Magma, computing the Gr\"obner basis
+  took 81 and 14 minutes, on the same machine
+  for \refeq{logmap} and \refeq{logmaps}, respectively;
+even so, our approach still had a 200-fold speed-up.
+
+%
+The exact polynomials of these maps are generally too large to print on paper,
+  e.g., the polynomial for the logistic map with $n = 13$
+    takes roughly seven megabytes to write down.
+%
+We therefore save the polynomials and programs of the three maps on the web site
+http://logperiod.appspot.com.
+
+%Compared with other approaches \cite{hitzl, gordon, bailey2, kk1, hao, hao2}
+%it appeared to be simpler and more transparent,
+%as it only requires the computation of a determinant.
 
@@
 With $b \rightarrow 0$ and $a \rightarrow R$,
-\refeq{henons} is reduced to the logistic map \refeq{logmaps}.
+we recover the logistic map \refeq{logmaps}.
 
@@
 
-\section{\label{sec:cubic}Cubic map}
-
-For higher-order one-dimensional maps, we consider the following cubic map \cite{strogatz}
+\section{\label{sec:cubic}Antisymmetric cubic map}
+
+As an example of a higher-order %one-dimensional 
+map, we consider the following cubic map \cite{strogatz}
 %
@@
 %
-Unlike the logistic map, this map has a clear parity,
+Unlike the logistic map, this map is antisymmetric,
   that is, $f(-x) = -f(x)$.
@@
   from the square-free ones to the cube-free ones,
-  in listing equations \eqref{eq:xcp}.
-For example, we include in the basis
-  $C_{112} = {x_1}^2 x_2 + {x_2}^2 x_3 + \dots + {x_n}^2 x_1$ ($n\ge3$),
-but not
-  $C_{1112} = {x_1}^3 x_2 + {x_2}^3 x_3 + \dots + {x_n}^3 x_1$.
+  in listing equations \eqref{eq:xcp},
+  e.g.,
+  $C_{112} = {x_1}^2 x_2 + \dots + {x_n}^2 x_1$
+  is now included in the basis
+  (but
+  $C_{1112} = {x_1}^3 x_2 + \dots + {x_n}^3 x_1$
+  is still not).
 
@@
 
-Similar to the logistic-map case,
-the number of the even cube-free cyclic polynomials
-is equal to the number of even \emph{ternary} necklaces,
+%Similar to the logistic-map case,
+Even cube-free cyclic polynomials
+can be mapped to \emph{even ternary} necklaces,
 in which each bead can assume
@@
   has a degree $N_e(n)$ in $\lambda$.
-Again, it encompasses the factors for the $n$-cycles
-  and the shorter $d$-cycles, as long as $d|n$.
-The minimal polynomial for the $n$-cycles can be obtained
-  by \refthm{primfac} with proper substitutions
-  $R\rightarrow r$,
-    $A_n(R, \lambda) \rightarrow A_n(r, \lambda)$,
-    etc.
+Again, it encompasses the factors
+  from the shorter $d$-cycles, as long as $d|n$.
+The polynomial for the $n$-cycles can be obtained
+  by \refeq{primfac} with proper substitutions, e.g.,
+  $R\rightarrow r$.
 %The degree of the polynomial,
@@
 
-\section{\label{sec:end}Summary and discussions}
-
-We now summarize the algorithm for a one-dimensional polynomial map.
-%
-First, we list \refeqs{xcp}  with $\Lambda(\vx) = \prod_{k=1}^n f'(x_k)$.
-This step populates elements of the matrix $\vct T(r)$,
-where $r$ is the parameter of the map.
-%
-The determinant $A_n(r, \lambda) = \big|\lambda \, \vct I - \vct T(r)\big|$,
-with $\lambda$ being $+1$ and $-1$, then gives the characteristic
-polynomial at onset and bifurcation points, respectively.
-%
-To filter out factors for the shorter $d$-cycles with $d|n$,
-  we repeat the process for other divisors $d$ of $n$
-  and then apply \req{primfac}.
-%
-
-When implemented on a computer,
-it is often helpful to evaluate $A_n(r,\lambda)$ by Lagrange interpolation,
-that is, we evaluate $A_n(r, \lambda)$ at a few different $r$,
-e.g., $r = 0, \pm1, \pm2,\ldots$, then piece them together
-to a polynomial.
-The strategy also allows a trivial parallelization.
-
-The algorithm (implemented as a Mathematica program)
-was quite efficient.
-%
-For the logistic map, the bifurcation point for $n = 8$
-took three seconds to compute on a desktop computer
-(single core, Intel\textsuperscript{\textregistered} Dual-Core CPU 2.50GHz).
-%
-In comparison,
-  the same problem took roughly 5.5 hours \cite{kk1}
-  using Gr\"obner basis
-  and 44 minutes in a later study \cite{lewis}.
-To be fair, using the latest Magma, computing the Gr\"obner basis
-  took 81 and 14 minutes, on the same machine
-  for \refeq{logmap} and \refeq{logmaps}, respectively;
-even so, our approach still had a 200-fold speed-up.
-
-%
-The exact polynomials of these maps are generally too large to print on paper,
-  e.g., the polynomial for the logistic map with $n = 13$
-    takes roughly seven megabytes to write down.
-%
-We therefore save the polynomials and programs of the three maps on the web site
-http://logperiod.appspot.com.
-
-%Compared with other approaches \cite{hitzl, gordon, bailey2, kk1, hao, hao2}
-%it appeared to be simpler and more transparent,
-%as it only requires the computation of a determinant.
-
-%\section*{Acknowledgements}
 \nonumsection{Acknowledgments} \noindent
@@
 
+\bibitem[Brown(1981)]{brown1}
+  Brown, A. [1981]
+  ``Equations for periodic solutions of a logistic difference equation,''
+  {\it J. Austral. Math. Soc. Ser. B}
+  \textbf{23},
+  78--94
+  (1981).
+
+\bibitem[Brown(1982)]{brown2}
+  Brown, A. [1982]
+  ``Solutions of period seven for a logistic difference equation,''
+  {\it Bull. Austral. Math. Soc.}
+  \textbf{26},
+  263--284.
+
+\bibitem[Stephenson(1991)]{stephenson1}
+  Stephenson, J. [1991]
+  ``Formulae for cycles in the Mandelbrot set,''
+  {\it Physica A}
+  \textbf{177},
+  416--420.
+
+\bibitem[Stephenson(1992a)]{stephenson2}
+  Stephenson, J. [1992a]
+  ``Formulae for cycles in the Mandelbrot set II,''
+  {\it Physica A}
+  \textbf{190},
+  104--116.
+
+\bibitem[Stephenson(1992b)]{stephenson3}
+  Stephenson, J. [1992b]
+  ``Formulae for cycles in the Mandelbrot set III,''
+  {\it Physica A}
+  \textbf{190},
+  117--129.
+
+\bibitem[Saha \& Strogatz(1995)]{saha}
+  Saha, P. \& Strogatz, S. H. [1995]
+  ``The birth of period three,''
+  {\it Mathematics Magazine}
+  \textbf{68},
+  42--47.
+
+\bibitem[Bechhoefer(1996)]{bechhoefer}
+  Bechhoefer, J. [1996]
+  ``The birth of period 3, revisited,''
+  {\it Mathematics Magazine}
+  \textbf{69},
+  115--118.
+
+\bibitem[Gordon(1996)]{gordon}
+  Gordon, W. B. [1996]
+  ``Period three trajectories of the logistic map,''
+  {\it Mathematics Magazine}
+  \textbf{69},
+  118--120.
+
+\bibitem[Burm \& Fishback(2001)]{burm}
+  Burm, J. \& Fishback, P. [2001]
+  ``Period-3 orbits via Sylvester's theorem and resultants,''
+  {\it Mathematics Magazine}
+  \textbf{74},
+  47--51.
+
+\bibitem[Zhang(2010)]{zhang}
+  Zhang, C. [2010]
+  ``Period three begins,''
+  {\it Mathematics Magazine}
+  \textbf{83},
+  295--297.
+
+\bibitem[Bailey \& Broadhurst(2000)]{bailey1}
+  Bailey, D. H. \& Broadhurst, D. J. [2000]
+  ``Parallel integer relation detection: techniques and applications,''
+  {\it Mathematics of Computation}
+  \textbf{70},
+  1719--1736.
+
+\bibitem[Bailey {\it et al.}(2006)]{bailey2}
+  Bailey, D. H., Borwein, J. M., Kapour, V. \& Weisstein, E. W. [2006]
+  ``Ten problems in experimental mathematics,''
+  {\it The American Mathematical Monthly}
+  \textbf{113},
+  481--509.
+
+\bibitem[Kotsireas \& Karamanos(2004)]{kk1}
+  Kotsireas, I. S. \& Karamanos, K. [2004]
+  ``Exact computation of the bifurcation point $B_4$ of the logistic map
+  and  the Bailey-Broadhurst conjectures,''
+  {\it International Journal of Bifurcation and Chaos}
+  \textbf{14},
+  2417--2423.
+
+\bibitem[Lewis(2008)]{lewis}
+  Lewis, R. H. [2008]
+  ``Heuristics to accelerate the Dixon resultant,''
+  {\it Mathematics and Computers in Simulation}
+  \textbf{77},
+  400--407.
+
 \bibitem[Mandelbrot(1980)]{mandelbrot}
@@
 
-\bibitem[Brown(1981)]{brown1}
-  Brown, A. [1981]
-  ``Equations for periodic solutions of a logistic difference equation,''
-  {\it J. Austral. Math. Soc. Ser. B}
-  \textbf{23},
-  78--94
-  (1981).
-
-\bibitem[Brown(1982)]{brown2}
-  Brown, A. [1982]
-  ``Solutions of period seven for a logistic difference equation,''
-  {\it Bull. Austral. Math. Soc.}
-  \textbf{26},
-  263--284.
-
-\bibitem[Stephenson(1991)]{stephenson1}
-  Stephenson, J. [1991]
-  ``Formulae for cycles in the Mandelbrot set,''
-  {\it Physica A}
-  \textbf{177},
-  416--420.
-
-\bibitem[Stephenson(1992a)]{stephenson2}
-  Stephenson, J. [1992a]
-  ``Formulae for cycles in the Mandelbrot set II,''
-  {\it Physica A}
-  \textbf{190},
-  104--116.
-
-\bibitem[Stephenson(1992b)]{stephenson3}
-  Stephenson, J. [1992b]
-  ``Formulae for cycles in the Mandelbrot set III,''
-  {\it Physica A}
-  \textbf{190},
-  117--129.
-
-\bibitem[Saha \& Strogatz(1995)]{saha}
-  Saha, P. \& Strogatz, S. H. [1995]
-  ``The birth of period three,''
-  {\it Mathematics Magazine}
-  \textbf{68},
-  42--47.
-
-\bibitem[Bechhoefer(1996)]{bechhoefer}
-  Bechhoefer, J. [1996]
-  ``The birth of period 3, revisited,''
-  {\it Mathematics Magazine}
-  \textbf{69},
-  115--118.
-
-\bibitem[Gordon(1996)]{gordon}
-  Gordon, W. B. [1996]
-  ``Period three trajectories of the logistic map,''
-  {\it Mathematics Magazine}
-  \textbf{69},
-  118--120.
-
-\bibitem[Burm \& Fishback(2001)]{burm}
-  Burm, J. \& Fishback, P. [2001]
-  ``Period-3 orbits via Sylvester's theorem and resultants,''
-  {\it Mathematics Magazine}
-  \textbf{74},
-  47--51.
-
-\bibitem[Zhang(2010)]{zhang}
-  Zhang, C. [2010]
-  ``Period three begins,''
-  {\it Mathematics Magazine}
-  \textbf{83},
-  295--297.
-
-\bibitem[Bailey \& Broadhurst(2000)]{bailey1}
-  Bailey, D. H. \& Broadhurst, D. J. [2000]
-  ``Parallel integer relation detection: techniques and applications,''
-  {\it Mathematics of Computation}
-  \textbf{70},
-  1719--1736.
-
-\bibitem[Bailey {\it et al.}(2006)]{bailey2}
-  Bailey, D. H., Borwein, J. M., Kapour, V. \& Weisstein, E. W. [2006]
-  ``Ten problems in experimental mathematics,''
-  {\it The American Mathematical Monthly}
-  \textbf{113},
-  481--509.
-
-\bibitem[Kotsireas \& Karamanos(2004)]{kk1}
-  Kotsireas, I. S. \& Karamanos, K. [2004]
-  ``Exact computation of the bifurcation point $B_4$ of the logistic map
-  and  the Bailey-Broadhurst conjectures,''
-  {\it International Journal of Bifurcation and Chaos}
-  \textbf{14},
-  2417--2423.
-
-\bibitem[Lewis(2008)]{lewis}
-  Lewis, R. H. [2008]
-  ``Heuristics to accelerate the Dixon resultant,''
-  {\it Mathematics and Computers in Simulation}
-  \textbf{77},
-  400--407.
-
 \bibitem[Hardy \& Wright(2008)]{hardy}

### 2013-05-14 doc/pc.tex
small doc changes

@@
   $(y, y) = (x_{k+1}, x_{k+1})$,
-  which starts the next iteration.
-
+  the starting point of the next iteration.
+%
 \begin{figure}[h]
@@
   studies
-  \cite{brown1, brown2, stephenson1, stephenson2, stephenson3,
+  \cite{brown1, stephenson,
   saha, bechhoefer, gordon, burm, zhang, bailey, kk1, lewis}.
@@
 Nonetheless, on a computer, one can
-  construct a (polynomial) Gr\"obner basis \cite{kk1}
-  that gradually eliminates $x_k$ out of the $n+1$ equations.
+  construct a (polynomial) Gr\"obner basis \cite{kk1},
+  which gradually eliminates $x_k$ out of the $n+1$ equations.
 As a special case, if $x_2, \dots, x_n$ are eliminated first,
@@
   where $\vx \equiv \{x_1, \ldots, x_n\}$ and $n = 4$.
-Note that a cyclic polynomial is not necessarily symmetric
+Note that a cyclic polynomial is unnecessarily symmetric
   (i.e., invariant under the exchange of any two $x_k$ and $x_{j}$),
@@
   by one.
-Since the original polynomial is cyclic,
+Since both the substitutions and the original polynomial are cyclic,
   so is the final square-free polynomial.
@@
 The coefficients $f_p$ are polynomials of $R$,
-  for $R$ is the only variable introduced by the substitutions.
+  for $R$ is the only new variable introduced by the substitutions.
 \end{proof}
@@
   of the orbit points $\vx = \{x_k\}$
-  are linear related by % \refeq{xcp},
+  are linearly related by % \refeq{xcp},
   $\lambda \, C_p(\vx) = \sum_{q \in \Pset} T_{pq}(R) \, C_q(\vx)$,
@@
 
-\bibitem{mandelbrot}
-  B. B. Mandelbrot,
-  Fractal aspects of the iteration of $z \rightarrow \lambda z(1-z)$
-      for complex $\lambda$ and $z$,
-  \textit{Ann. NY Acad. Sci.}
-  \textbf{357},
-  249--259
-  (1980).
-
 \bibitem{brown1}
@@
 
+\bibitem{mandelbrot}
+  B. B. Mandelbrot,
+  Fractal aspects of the iteration of $z \rightarrow \lambda z(1-z)$
+      for complex $\lambda$ and $z$,
+  \textit{Ann. NY Acad. Sci.}
+  \textbf{357},
+  249--259
+  (1980).
+
 \bibitem{lewis}

### 2013-05-14 doc/pc-ijbc.tex
pc-ijbc: improve sec. 2.7

@@
 \newcommand{\vx}{\vct x}
-\newcommand{\vxn}[1]{\vx^{(#1)}}
+\newcommand{\vxn}[1]{\vx_{#1}}
 \newcommand{\Tr}{\mathrm{Tr}}
@@
 \newcommand{\LB}{L_\Pset}
+\newcommand{\lam}{(\lambda)}
 \newcommand{\Rlam}{(R, \lambda)}
@@
   where $\vxn{n} \equiv \{x_1, \ldots, x_n\}$
-[we will, however, drop the superscript ``$^{(n)}$'' or
+[we will, however, drop the subscript ``$_n$'' or
   even the argument ``$(\vxn{n})$'' entirely when it is clear].
@@
 
-\subsection{\label{sec:primfac}Minimal polynomial of the $n$-cycles}
+\subsection{\label{sec:primfac}$n$-cycle polynomial}
 
@@
 The first few $\mu(n) = 1, -1, -1, 0, -1, 1, -1, \ldots,$
-  from $n = 1$%.
+  from $n = 1$
 %The $\mu(n)$ is useful for inversion:
@@
 %
-%
-\begin{remark}
-%$B_{d,c}\Rlam$ is a polynomial of $\lambda$.
+
+Since the discussions in this and the next sections
+  concern $\lambda$ instead of $R$,
+  we will drop the argument $R$ in $P_n\Rlam$ and $A_n\Rlam$, etc.
+%\begin{remark}
+%$B_{d,c}\lambda$ is a polynomial of $\lambda$.
 Despite the argument $\lambda^{1/c}$,
-  the product $\prod_{k=1}^c A_d(R, e^{2k\pi i/c} \lambda^{1/c})$,
-  hence $B_d^c\Rlam$,
+  the product $\prod_{k=1}^c A_d(e^{2k\pi i/c} \lambda^{1/c})$,
+  hence $B_d^c\lam$,
   is free from radicals of powers of $\lambda^{1/c}$,
   for it is invariant under $\lambda \rightarrow e^{2\pi i} \lambda$.
-Thus, $B_d^c\Rlam$ is a polynomial of $\lambda$,
-and $\deg_\lambda B_d^c\Rlam = \deg_\lambda A_d\Rlam$.
-Particularly, $B_n^1\Rlam = A_n\Rlam$.
-\end{remark}
-%
-%
-%We will refer to $P_n\Rlam$ as the \emph{primitive factor} below.
-%
+Thus, $B_d^c\lam$ is a polynomial of $\lambda$,
+and $\deg_\lambda B_d^c\lam = \deg_\lambda A_d\lam$.
+Particularly, $B_n^1\lam = A_n\lam$.
+%
+%\end{remark}
+
 %
@@
 to the examples in \refsec{examples}.
-We will omit the argument $R$ below for convenience.
 %%
@@
 %
-To show \refeq{primfac}, we first find the degrees in $\lambda$ of
-  $A_n\Rlam$ [\refeq{necklace}] and $P_n\Rlam$ [\refeq{lyndon}].
+We now prove \refeq{primfac}.
+%
+To do so, we first find the degrees in $\lambda$ of
+  $A_n\lam$ [\refeq{necklace}] and $P_n\lam$ [\refeq{lyndon}].
 By comparing the degrees,
-  we then show that each $P_d\Rlam$ with ($d|n$),
+  we then show that each $P_d\lam$ with $d|n$,
   after some transformation,
-  contributes one polynomial factor to $A_n\Rlam$
+  contributes one polynomial factor to $A_n\lam$
   [\refeq{prod}],
@@
 Given a cyclic polynomial, if the generator contains $x_k$,
-  the $k$th character from the left of the necklace is 1,
+  the $k$th character from the right of the necklace is 1,
   otherwise 0,
@@
 \begin{equation}
-  %\deg_\lambda A_n\Rlam =
-  \NB(n) = (1/n) \textstyle\sum_{d|n} \varphi(n/d) 2^{\,d}.
+  %\deg_\lambda A_n\lam =
+  \NB(n) = (1/n) \textstyle\sum_{d|n} \varphi(n/d) 2^{\,d},
 \label{eq:necklace}
@@
 %
-Here, $\varphi(m)$ is Euler's totient function,
+where $\varphi(m)$ is Euler's totient function,
 which gives the number of integers from 1 to $m$
@@
 By \refeq{xr},
-  $\NB$ is also $\deg_\lambda A_n\Rlam$.
+  $\NB$ is also $\deg_\lambda A_n$.
 The first few $\NB(n)$ are
@@
 %\begin{theorem}
-Next, the degree in $\lambda$ of the polynomial $P_n\Rlam$ of all $n$-cycles
-  is equal to the number of the $n$-cycles,
+Next the polynomial $P_n\lam$ can be written as
+\begin{equation}
+  P_n\lam = \textstyle\prod_l [\lambda - \Lambda(\vxn{n}^{(l)})],
+\end{equation}
+where $\vxn{n}^{(l)}$ denotes the $l$th $n$-cycle.
+%
+Thus, $\deg_\lambda P_n\lam$
+  is equal to the number $\LB$ of the $n$-cycles,
   which is given by
-\begin{equation}
-  %\deg_\lambda P_n\Rlam =
+  \cite{hao, hao2, lutzky}.
+\begin{equation}
+  %\deg_\lambda P_n\lam =
   \LB(n) = (1/n)\textstyle\sum_{d | n} \mu(n/d) 2^{\,d}.
@@
 %
-%\begin{proof}
-The number $\LB$ of $n$-cycles
-  is well known \cite{hao, hao2, lutzky}.
-The minimal polynomial $P_n\Rlam$
-  can be written as $\prod_c (\lambda - \lambda_c)$,
-where $\lambda_c$ is the value of $\Lambda(\vx^c)$
-  evaluated at the $c$th cycle.
-Thus, $\deg_\lambda P_n\Rlam = \LB$.
 %\end{proof}
@@
 (e.g., for $n = 4$,
-  $0011$ is aperiodic, but $0101$ is not due to the shorter period 2).
+  ``$0011$'' is aperiodic, but ``$0101$'' is not due to the shorter period 2).
 %
@@
 %
-Since the left side is also $\deg_\lambda A_n\Rlam$,
-  and $A_n\Rlam$ has to represent all $d$-cycles with $d|n$,
-$A_n\Rlam$
-%and each cycle holds a distinct $\lambda$,
-%  $\deg_\lambda A_n\Rlam$
-%  is at least $\sum_{d|n} L(d)$
-%  according to \refeq{lyndon},
-%  which is equal to
-%  $\NB$ by \refeq{necklacelyndon}.
-%Since $\deg_\lambda A_n\Rlam = \NB$ by \refeq{necklace},
-%  each $n$-cycle occurs exactly once in $A_n\Rlam$.
-
-%\subsubsection{Relation between $P_n$ and $A_n$}
-
+Since the left side is the degree in $\lambda$ of $A_n\lam$,
+  which accommodates all fixed points of $f^n$,
+  %\refeq{necklacelyndon} shows that
+  each distinct $d$-cycle (with $d|n$)
+  contributes one and only one zero to $A_n\lam$.
+%
+%
+We may thus write
 %\begin{theorem}
-We can now show that $P_n\Rlam$ and 
-and $A_n\Rlam$ are related by
-  \begin{equation}
-    A_n\Rlam = \prod_{cd = n} Q_d^c\Rlam,
+  \begin{equation}
+    A_n\lam = \textstyle\prod_{d|n} Q_d^{n/d}\lam,
     \label{eq:prod}
   \end{equation}
-  where
-  $Q_d^c\Rlam = \prod_{k=1}^{c} P_d(R, e^{2 k \pi i/c} \lambda^{1/c})$
-  is a polynomial of degree $L(d)$ in $\lambda$
-  representing contributions from $d$-cycles.
-%encompassed by $A_n\Rlam$.
-%\label{thm:prod}
-%\end{theorem}
-
-%\begin{proof}
-In a $d$-cycle,
- we have $\Lambda(\{x_1, \ldots, x_n\}) = (-2)^n x_1 \dots x_n
-   = {\Lambda_d}^c$,
-where
-$\Lambda_d(\{x_1, \ldots, x_d\}) \equiv (-2)^d x_1 \dots x_d$
+where $Q_d^{n/d}(\lambda) \equiv \prod_l
+  \big[\lambda - \Lambda\big(\vxn{n}^{(l)}\big) \big]$
+  with $\vxn{n}^{(l)}$ being the $n$ points
+  corresponding to the $l$th $d$-cycle.
+%
+In order words, $\vxn{n}^{(l)}$ is $\vxn{d}^{(l)}$
+  repeated for $c = n/d$ times:
+\begin{equation}
+  \vxn{n}^{(l)} =
+  \{
+    x_1^{(l)}, \ldots, x_d^{(l)},
+    \; \ldots, \;
+    x_1^{(l)}, \ldots, x_d^{(l)}
+  \}
+  = \vxn{d}^{(l)} * c.
+\notag
+\end{equation}
+%
+It follows that
+$\Lambda(\vxn{n})$ = $[\Lambda(\vxn{d})]^c$.
+By factorizing $\lambda - \Lambda^c$
+  in terms of complex roots of unity, we get
+\begin{align}
+Q_d^{c}\lam
+%  &= \prod_l
+%    \Big\{
+%      \lambda - \big[\Lambda\big(\vxn{d}^{(l)}\big) \big]^{c}
+%    \Big\}
+%    \notag \\
+  &=
+    \prod_l
+    \Big\{
+      \prod_{k=1}^c \,
+      \big[
+          e^{2k\pi i/c} \lambda^{1/c}
+          - \Lambda\big(\vxn{d}^{(l)}\big)
+      \big]
+    \Big\},
+    \notag
+\end{align}
+%
+Now changing the order of the two products yields
+\begin{equation}
+Q_d^{c}\lam
+  =  \prod_{k=1}^c P_d\big(e^{2k\pi i/c} \lambda^{1/c}\big),
+\label{eq:QP}
+\end{equation}
+%
+%
+Despite the presence of $\lambda^{1/c}$,
+  $Q_d^c\lam$ is a polynomial of $\lambda$,
+  thanks to the invariance
+  $\lambda \rightarrow e^{2\pi i} \lambda$;
 and
-$c \equiv n/d$.
-So the $d$-cycle satisfies a polynomial
-  $P_d(R, \lambda^{1/c}) = 0$,
-where $\lambda = \Lambda(\{x_1,\ldots,x_n\})$.
-%
-This is, however, not a polynomial equation, and
-%
-the radical $\lambda^{1/c}$ can be removed by the product
-$Q_d^c\Rlam
-  \equiv \prod_{k=1}^c P_d(R, e^{2k\pi i/c} \, \lambda^{1/c}) = 0$.
-%
-Now $Q_d^c\Rlam$ is a polynomial of $\lambda$
-  for it is invariant under
-  $\lambda \rightarrow e^{2\pi i} \lambda$,
-and thus free from radicals of the form $\lambda^{l/c}$
-  \big[if $(l, c) \ne c$\big].
-And since
-  $\deg_\lambda Q_d^c\Rlam
-    = \deg_\lambda P_d\Rlam = L(d)$,
-  it is also a polynomial
-  of the lowest possible degree in $\lambda$.
-
-Therefore, the product $\prod_{cd=n} Q_d^c\Rlam$
-  can differ from $A_n\Rlam$ only by
-  a multiple.
-Since $Q_n^1\Rlam = P_n\Rlam$,
-  and the coefficient of highest power of $\lambda$ is always
-  unity in $A_n\Rlam$ \big[see the definition \refeq{xr}\big],
-  we know by induction that the coefficients of the highest power of $\lambda$
-  in all $P_n\Rlam$ and $Q_d^c\Rlam$
-  are also unities.
-So the multiple is one, hence \refeq{prod}.
-%
-%
-%
-%\end{proof}
-
-\refeq{primfac} is a corollary of \refeq{prod},
-\begin{small}
+  $\deg_\lambda Q_d^c\lam
+    = \deg_\lambda P_d\lam = \LB(d)$.
+
+%Therefore, the product $\prod_{cd=n} Q_d^c\lam$
+%  can differ from $A_n\lam$ only by
+%  a multiple.
+%Since $Q_n^1\lam = P_n\lam$,
+%  and the coefficient of highest power of $\lambda$ is always
+%  unity in $A_n\lam$ \big[see the definition \refeq{xr}\big],
+%  we know by induction that the coefficients of the highest power of $\lambda$
+%  in all $P_n\lam$ and $Q_d^c\lam$
+%  are also unities.
+%So the multiple is one, hence \refeq{prod}.
+
+\refeq{primfac} can now be derived from
+  \refeqs{prod} and (\ref{eq:QP}),
+%\begin{small}
 \begin{align*}
  B_n^m (\lambda)
-% & = \prod_{l = 1}^{m} A_n(e^{2l\pi i/m} \lambda^{1/m}) \\
- & = \prod_{c | n} \prod_{l=1}^m \prod_{k=1}^c
-    P_{n/c}(e^{\frac{2k\pi i}{c} + \frac{2l\pi i}{m c}} \lambda^{1/(m c)}) \\
- & = \prod_{c | n} \prod_{k'=1}^{m c}
-    P_{n/c}(e^{2k'\pi i/(m c)} \lambda^{1/(m c)})% \\
- %&
+% & = \prod_{r = 1}^{m} A_n(e^{2l\pi i/m} \lambda^{1/m}) \\
+ & = \prod_{k' = 1}^m \prod_{c | n} \prod_{k=1}^c
+      P_{n/c}\big(
+        e^{2k\pi i/c + 2 k' \pi i/(m c)}
+        \lambda^{1/(m c)}
+      \big) \\
+ & = \prod_{c | n} \prod_{k''=1}^{m c}
+    P_{n/c}(e^{2k''\pi i/(m c)} \lambda^{1/(m c)}) \\
+ &
   = \prod_{c | n} Q_{n/c}^{m c}(\lambda).
 \end{align*}
-\end{small}
+%\end{small}
 The M\"obious inversion yields
 \begin{equation}
-Q_n^m\Rlam
-= \prod_{d|n} B_d^{m n/d}\Rlam^{\mu(n/d)},
+Q_n^m\lam
+= \textstyle\prod_{d|n} \big[
+    B_d^{m n/d}\lam
+  \big]^{\mu(n/d)}.
 \notag
@@
 \end{equation}
-which is reduced to \refeq{primfac} with $m = 1$,
+\refeq{primfac} is the special case of $m = 1$,
 for $Q_n^1 = P_n$.
@@
 Since the $n$-odd-cycles satisfy a polynomial of lower degree,
-  the minimal polynomial $P_{2n}(r, \lambda)$
+  the $n$-cycle polynomial $P_{2n}(\lambda)$
+  (omitting the argument $r$)
   can always be factorized.
 %
-Suppose $\Lambda^\odd(\vx) \equiv \prod_{k = 1}^{n} f'(x_k)$ in the odd-cycle
- satisfies $P_{n}^\odd(r, \lambda^\odd) = 0$
-\big[where $\lambda^\odd$ is the value of $\Lambda^\odd(\vx)$,
-and $\lambda^\odd = \pm\sqrt \lambda$\,\big],
-then $P^\odd_{n}(r, \sqrt \lambda) P^\odd_{n/2}(r, -\sqrt \lambda)$
-is a factor of $P_{n}(r, \lambda)$.
+Suppose $\Lambda^o(\vx) \equiv \prod_{k = 1}^{n} f'(x_k)$ in the odd-cycle
+ satisfies $P_{n}^o(\lambda^o) = 0$
+\big[where $\lambda^o$ is the value of $\Lambda^o(\vx)$,
+and $\lambda^o = \pm\sqrt \lambda$\,\big],
+then $P^o_{n}(\sqrt \lambda) P^o_{n/2}(-\sqrt \lambda)$
+is a factor of $P_{n}(\lambda)$.
 %
@@
   we have $- x_1 = r x_1 - {x_1}^3$, or ${x_1}^2 = r + 1$.
-Since $\lambda^\odd = r - 3 {x_1}^2$,
-$P^\odd_1(r, \lambda^\odd) = \lambda^\odd + 2 r + 3$.
-%
-The minimal polynomial of 2-cycles
-  $P_2(r,\lambda) = -\big[(2r+3)^2 - \lambda\big]\,(\lambda + 2r^2-9)$,
+Since $\lambda^o = r - 3 {x_1}^2$,
+$P^o_1(\lambda^o) = \lambda^o + 2 r + 3$.
+%
+The 2-cycle polynomial
+  $P_2(\lambda) = -\big[(2r+3)^2 - \lambda\big]\,(\lambda + 2r^2-9)$,
   indeed contains
-  $P^\odd_1(r, \sqrt \lambda) \, P^\odd_1(r, -\sqrt \lambda)
+  $P^o_1(\sqrt \lambda) \, P^o_1(r, -\sqrt \lambda)
    = (\sqrt \lambda + 2 r + 3)(-\sqrt \lambda + 2 r + 3)$

### 2013-05-15 doc/pc-ijbc.tex
pc-ijbc: add logtime.gp, editing

@@
 \newcommand{\Rlam}{(R, \lambda)}
+\newcommand{\rlam}{(r, \lambda)}
 
@@
 After many iterations, there can be three ultimate patterns:
-  (i) a \emph{fixed point} or a constant (including infinity),
+  (i) a \emph{fixed point} (including infinity),
       e.g., \reffig{cobweb}(a);
-  (ii) a periodic \emph{cycle} or a self-repeating loop,
+  (ii) a periodic \emph{cycle},
       e.g., \reffigs{cobweb}(b)-(e);
@@
 %
-It is stable if $x_1$ deviates slightly from $x^*$
-  and the sequence still converges to $x^*$.
+It is stable if a small deviation from $x^*$
+  gets reduced by successive iterations.
 %
 For a differentiable $f$,
-  a stable fixed point requires $|f'(x^*)| \le 1$
-  to reduce deviations in successive iterations \cite{strogatz}.
+  this is equivalent to $|f'(x^*)| \le 1$
+  \cite{strogatz}.
 
@@
 
-The onset polynomial
-  $P_n(R, \lambda = 1)$ for the $n$-cycles
-  can be further factorized.
+The $n$-cycle polynomial
+  $P_n(R, \lambda)$
+  can be further factorized at $\lambda = 1$.
 %
@@
 %
-One can show that this intersection happens only
-  at the onset of the $n$-cycle, where $\lambda = 1$,
-%
-  and the $d$-cycle branches out, or ``bifurcates,'' $n/d$-fold
-  to become the $n$-cycle.
+One can show that (1) such an intersection happens only
+  at the onset of the longer $n$-cycle, where $\lambda = 1$,
+%
+  and (2) $d$ and $n$ are coprime \cite{blackhurst}.
 %
@@
   undergoes period-doubling and becomes the 2-cycle \refeq{xr2}.
-As a result, the polynomial $P_n(R, \lambda)$ from the $n$-cycle
-  has to accommodate $P_d(R, \lambda')$ from the $d$-cycle as a factor,
+As a result, the $n$-cycle polynomial $P_n(R, \lambda)$
+  has to accommodate the $d$-cycle one $P_d(R, \lambda')$ as a factor,
   with $\lambda'$ being a primitive $(n/d)\,$th root of $\lambda = 1$.
 
-If an $n$-cycle is not born out of the above branching,
-  we call it \emph{original}.
-The two types of cycles exist
-  as separate factors of $P_n(R, \lambda = 1)$.
-One can then show that the factor $S_n(R)$ responsible for the original cycles
+We can therefore distinguish \emph{original} cycles
+  from those born out of the above branching.
+Similar to \refeq{QP},
+  the contributions from the non-original cycles
+  born out of the $d$-cycles
+  can be written as a cyclotomic product
+  $\prod_{(k, c) = 1}
+      P_{d}
+        \left(
+          R, e^{2k\pi i/c}
+        \right)$,
+where $k$ runs through integers from 1 to $c=n/d$,
+  that are coprime to $c$.
+With these contributions removed,
+  we obtain the polynomial $S_n(R)$ responsible for the original cycles:
   %or the \emph{original factor} below,
-  is given by
   \begin{equation}
@@
   \end{equation}
-where the inner product on the denominator is carried over
-   $k$ from 1 to $c$ that are coprime to $c$.
-
+%
+%
+%
 Take the $n = 4$ case as an example, we have
@@
 Dividing $P_4(R, 1)$ by the two factors yields
-$S_4(R) = (4R-3)^3 - 108$,
-  whose only real root $R_a=(3+\sqrt[3]{108})/4$ corresponds to
-  the onset of the original cycle.
-Note $R_a' = 5/4$ is excluded from $S_4(R)$
-  as it is due to period-doubling the 2-cycle.
+$S_4(R) = (4R-3)^3 - 108$.
+%  whose only real root $R_a=(3+\sqrt[3]{108})/4$ corresponds to
+%  the onset of the original cycle.
+Note $R_a' = 5/4$ is not original,
+  for it is born out of period-doubling the 2-cycle.
 The two cycles are compared in \reffigs{cobweb}(d) and (e).
@@
 
-%\begin{theorem}
-The degrees in $R$ of $A_n\Rlam$, $P_n\Rlam$ and $S_n(R)$ are
-\begin{subequations}\small
+In the numerical implementation
+  (see \refsec{end}),
+  it is helpful to know the degrees in $R$ of the polynomials
+  to evaluate the determinant by Lagrange interpolation. 
+We first show that:
+\begin{equation}
+\deg_R A_n\Rlam = \textstyle\sum_{d|n} \varphi(n/d) 2^{d-1},
+\label{eq:degRA}
+\end{equation}
+%
+The first few values are
+1, 3, 6, 12, 20, 42, 70, 144, 270, 540, \dots, from $n =1$.%1034, 2112, 4108, \dots,
+
+From \refeq{xr},
+  every term in the expansion of the determinant $|\vct A|$
+  can be written as
+  $\prod_{p} A_{p,q}$,
+  in which, $p$ runs through all cyclic polynomials,
+  and $\{q = q(p)\}$ is a permutation of $\{p\}$.
+Thus, $\deg_R |\vct A|$ is
+  reached by the term that maximizes the product.
+Recall that $A_{p,q}$ results from reducing
+  $\Lambda(\vx) \, C_p(\vx)$ to $C_q(\vx)$
+  by a sequence of substitutions ${x_k}^2 = R-x_{k+1}$.
+It follows that to increase $\deg_R$ by 1,
+  $\deg_\vx$ is decreased by at least 2.
+Accordingly,
+  $\deg_R A_{p,q} \le \deg_\vx(\Lambda \, C_p) - \deg_\vx C_q$.
+Now running $p$ and $q$ through the $\NB$ cyclic polynomials
+  yields
+\[
+  \deg_R |\vct A | = \deg_R \textstyle\prod_{p} A_{p,q} \le n \, \NB(n),
+\]
+where we have used $\deg_\vx \Lambda(\vx) = n$.
+%
+The equality can be achieved, if each $q$ is the ``complement'' of $p$,
+  that is, if $\prod_k x_k^{e_k}$ is the generator of $C_p$,
+  $C_q$ can be generated from $\prod_k x_k^{1-e_k}$.
+For example, for $n=4$,
+  $C_1 = x_1 + \cdots + x_4$
+  is the complement of
+  $C_{123} = x_{234} + \cdots + x_{123}$;
+  while $C_{12}$ is its own complement.
+Finally, we reach \refeq{degRA} by \refeq{necklace}.
+
+Now, taking the degrees in $R$ of \refeq{primfac} and \refeq{origfac}
+  yields
+%
+\begin{subequations}
 \begin{align}
-\deg_R A_n\Rlam &= \sum_{d|n} \varphi(n/d) 2^{d-1}, \\
-\deg_R P_n\Rlam &\equiv \beta(n) = \sum_{d|n} \mu(n/d) 2^{d-1}, \\
-\deg S_n(R) &= \beta(n) - \sum_{d | n, d < n} \beta(d) \, \varphi(n/d).
+\deg_R P_n\Rlam &\equiv \beta(n) = \sum_{d|n} \mu\Big(\frac{n}{d}\Big) 2^{d-1}, \\
+    \deg S_n(R) &= \beta(n)
+  - \sum_{d | n, d < n} \beta(d) \, \varphi\Big(\frac{n}{d}\Big).
 \end{align}
@@
 \end{subequations}
-%\label{thm:degR}
-%\end{theorem}
-%
-%
-%
-\begin{proof}
-We first prove \refeqsub{degR}{a}.
-%
-We recall the subscript $p$ of $C_p$ denotes a sequence of indices $k$
-  in the generating monomial $\prod_k {x_k}^{e_k}$.
-But for a square-free cyclic polynomial,
-  each $k$ occurs no more than once,
-so $p$ also represents a \emph{set} of indices,
-%
-e.g.,
-$p = 1$ represents $\{1\}$,
-  ($C_1 = x_1 + \dots + x_n$, generator: $x_1$)
-and
-$p = 13$ represents $\{1, 3\}$
-  ($C_{13} = x_1 \, x_3 + x_2 \, x_4 + \dots + x_n \, x_2$,
-  generator: $x_1 \, x_3 $, assuming $n \ge 4$).
-%more examples are listed in \reftab{sqrfreepoly}).
-%
-In this proof,
-we shall also use $p$ to denote the corresponding index set,
-  $|p|$ the set size, i.e., the number of indices in the set,
-  and
-  $\bar p \equiv \{1,\ldots,n\} \backslash p$ the complementary set.
-%
-Obviously, $|\bar p| + |p| = n$.
-%
-Further, we will include $p$ that correspond to alternative generators
-  of the same cyclic polynomial,
-e.g., we allow $p = \{2\}$, $\{3\}$, \dots, $\{n\}$,
-  although they represent the same cyclic polynomial $C_1$
-  as $p = \{1\}$.
-
-Next, we recall the matrix elements $T_{pq}(R)$ arise from the square-free reduction
-of $\Lambda(\vx) C_p(\vx) = (-2)^n x_1 \dots x_n \, C_p(\vx)$.
-%
-A single replacement ${x_k}^2 \rightarrow R - x_{k+1}$
-produces two new terms:
-in the first, ${x_k}^2 \rightarrow R$,
-and in the second, ${x_k}^2 \rightarrow - x_{k+1}$.
-We call the two type 1 and type 2 replacements, respectively.
-%
-If a monomial term $t(R, \vx)$
-results from $l_1$ type 1 and $l_2$ type 2 replacements
-during the reduction of a term $s(\vx)$ in $\Lambda(\vx) C_p(\vx)$,
-then the degrees in $\vct x$, for any $x_k$, of $s(\vx)$ and $t(R, \vx)$
-are related as
-%
-\begin{equation}
-  \deg_\vx s(\vx) - \deg_\vx t(R, \vx) = 2 l_1 + l_2.
-\label{eq:degxdiffst}
-\end{equation}
-%
-Similarly, the degrees in $R$ satisfy
-\[
-  \deg_R s(\vx) - \deg_R t(R, \vx) = - l_1,
-\]
-but since $\deg_R s(\vx) = 0$,
-\begin{equation}
-  \deg_R t(R, \vx) = l_1.
-\label{eq:degRt}
-\end{equation}
-
-%
-Now if the monomial $t(R, \vx)$ settles in the $q$th column of
-  the matrix $\vct T(R)$, as part
-  of $T_{pq}(R) C_q(\vx)$ in \refeq{xcp0},
-then
-  $t(R, \vx)$
-  must be
-%the product of
-%  a monomial of $R$ \big[as part of $T_{pq}(R)$\big]
-%  and one of the
-  a generator of $C_q(\vx)$;
-so
-%
-\begin{equation}
-  \deg_\vx t(R, \vx) = |q|.
-\label{eq:degxt}
-\end{equation}
-%
-Since $s(\vx)$ is part of $\Lambda(\vx) C_p(\vx)$,
-  we have
-%
-\begin{equation}
-  \deg_\vx s(\vx) = \deg_\vx \Lambda(\vx) + \deg_\vx C_p(\vx)
-  = n + |p|.
-\label{eq:degxs}
-\end{equation}
-%
-%
-From \refeqs{degxdiffst}, \req{degxt}, \req{degxs}, we get
-\[
-  n + |p| - |q| = 2 \, l_1 + l_2,
-\]
-and
-\begin{equation}
-  l_1  =    (n + |p| - |q| - l_2)/2
-             \le  (n + |p| - |q|)/2.
-\label{eq:l1limit}
-\end{equation}
-By \refeq{degRt}, we get
-\begin{align*}
-  \deg_R T_{pq}(R)
-  = \max\{ \deg_R t(R, \vx) \}
-  = \max\{ l_1 \}
-  \le   (n + |p| - |q|)/2,
-\end{align*}
-where the equality holds when all replacements are type 1 ($l_2 = 0$).
-%
-Finally, each term of the determinant
-$A_n\Rlam = \big|\lambda \, \vct I - \vct T(R)\big|$
-is given by
-$(-1)^s \prod_{p} \big[\lambda \, \delta_{p q} - T_{pq}(R)\big]$,
-where $p$ runs through rows of the matrix
-  and $\{q\}$ is a permutation of $\{p\}$,
-  with $(-1)^s$ being the proper sign.
-%
-Summing over rows under this condition yields
-\begin{align*}
-  \deg_R A_n\Rlam
-  = \max \sum_{p \in \Pset} \deg T_{pq}(R)
-  \le \NB \, \big(n + |p| - |q|\big)/2 = n \NB/2,
-\end{align*}
-where equality can be achieved if $q = \bar p$ in every row.
-By \refeq{necklace} we have \refeqsub{degR}{a}.
-%
-\refeqsub{degR}{b} and (c) follow from taking taking the degree in $R$ of
-  \refeq{prod} and \refeq{origfac}.
-\refeqsub{degR}{b} and (\ref{eq:degR}c) were known \cite{mira, stephenson1, blackhurst}.
-%
-\end{proof}
-%
-The first few $\deg_R A_n\Rlam$,
+%
+The two formulas are known \cite{mira, stephenson1, blackhurst}.
+%
+%
+The first few
   $\deg_R P_n\Rlam$,
   and $\deg S_n(R)$ are
-  1, 3, 6, 12, 20, 42, 70, 144, 270, 540, \dots,  %1034, 2112, 4108, \dots,
   1, 1, 3, 6, 15, 27, 63, 120, 252, 495, \dots, %1023, 2010, 4095, \dots,
@@
 %
-To filter out the contributions from shorter $d$-cycles with $d|n$,
-  we repeat compute the characteristic equations for all divisors $d$
-  and then apply \req{primfac}.
+The contributions from shorter $d$-cycles
+  can be removed by
+  % computing the characteristic equations for all divisors $d$ and applying
+  \refeq{primfac}.
 %
@@
 When implemented on a computer,
-it is often helpful to evaluate $A_n(\lambda)$ by Lagrange interpolation,
-that is, we evaluate $A_n(r, \lambda)$ at a few different $r$,
-e.g., $r = 0, \pm1, \pm2,\ldots$, then piece them together
+it is often helpful to evaluate the characteristic polynomial
+by Lagrange interpolation,
+that is, by evaluating $A_n\Rlam$ at a few different $R$,
+e.g., $R = 0, \pm1, \pm2,\ldots$, then piecing them together
 to a polynomial.
@@
 %
-For polynomials of larger $n$ are saved in in the website in \refsec{end}.
-%
-The representative $r$ values are listed in \reftab{rval}.
-%
-
-The algorithm (implemented as a Mathematica program)
-was quite efficient.
-%
-For the logistic map, the bifurcation point for $n = 8$
-took three seconds to compute on a desktop computer
-(single core, Intel\textsuperscript{\textregistered} Dual-Core CPU 2.50GHz).
-%
-In comparison,
-  the same problem took roughly 5.5 hours \cite{kk1}
-  using Gr\"obner basis
-  and 44 minutes in a later study \cite{lewis}.
-To be fair, using the latest Magma, computing the Gr\"obner basis
-  took 81 and 14 minutes, on the same machine
-  for \refeq{logmap} and \refeq{logmaps}, respectively;
-even so, our approach still had a 200-fold speed-up.
+As shown in \reffig{logtime}, the algorithm
+outperformed the resultant \cite{burm} and
+  Gr\"obner basis \cite{kk1} methods,
+  by at least two orders of magnitudes.
+%
+Note that the resultant of $f^n(x)-x$ and $\frac{d}{dx}f^n(x)-\lambda$
+  is the determinant of the Sylvester matrix, which has
+  $2^{n+1}-1$ rows and columns
+  [as $\deg_x f^n(x) = 2^n$],
+  while the matrix of the characteristic equation \refeq{xr}
+  is of only $\NB \approx 2^n/n$ [cf. \refeq{necklace}] rows and columns.
+Thus, the current algorithm is expected to be faster.
+
+\begin{figure}[h]
+  \begin{center}
+  \begin{minipage}{\linewidth}
+        \includegraphics[angle=-90, width=\linewidth]{logtime.pdf}
+  \end{minipage}%
+  \end{center}
+  \caption{\label{fig:logtime}
+  Time to compute the $n$-cycle bifurcation polynomials,
+    measured from a single core of
+    Intel\textsuperscript{\textregistered} 2.5GHz Dual-Core CPU
+  (Mathematica version: 8, Magma version: 2.18-4).
+  }
+\end{figure}
+%
 
@@
 %
-We therefore save the polynomials and programs of the three maps on the web site
+We therefore save the polynomials and programs on the web site
 http://logperiod.appspot.com.
+%
+The representative $r$ values are listed in \reftab{rval}.
 
@@
   y_{k+1} = b \, x_k.
-\tag{$\ref{eq:henon}'$}
+%\tag{$\ref{eq:henon}'$}
 \label{eq:henons}
@@
 \end{equation}
-This map is closely related to the one studied by Brown \cite{brown3, brown4}.
 %
@@
   that is, $f(-x) = -f(x)$.
+%
+In fact, all antisymmetric cubic maps \cite{brown3, brown4}
+  can be mapped to \refeq{cubic} by a change of variables.
 We shall show below that this odd parity can be used to reduce the amount of calculation.
@@
 
-The characteristic polynomial $A_n(r, \lambda)$
+The characteristic polynomial $A_n\rlam$
   from the determinant equation
@@
 Again, it encompasses the factors
-  from the shorter $d$-cycles, as long as $d|n$.
-The polynomial for the $n$-cycles can be obtained
-  by \refeq{primfac} with proper substitutions, e.g.,
+  from the shorter $d$-cycles ($d|n$),
+  and the $n$-cycle polynomial can be obtained
+  from \refeq{primfac} by proper substitutions, e.g.,
   $R\rightarrow r$.
 %The degree of the polynomial,
-The degree in $\lambda$ of
-the minimal polynomial $P_n(r, \lambda)$ of the $n$-cycles,
-  after some algebra,
-  is given by
-%
-%
-%\begin{theorem}
-%The degree in $\lambda$ of
-%the minimal polynomial $P_n(r, \lambda)$ of the $n$-cycles is
+The degree in $\lambda$ of $P_n\rlam$
+  is given by, after some algebra,
+%
+%
 \begin{equation}
@@
 \end{equation}
-%where $\odd(n)$ %$= [1 - (-1)^n]/2$
-%is $1$ for an odd $n$,
-%but $0$ for an even $n$.
-%\label{thm:cublyndon}
-%\end{theorem}
 %
@@
   with negative $r$ are imaginary.
-However, in a closely-related map
+However, in a transformed map
 $z_{k+1} = r \, z_k \, (1 - {z_k}^2)$,
@@
 Following similar steps in \refsec{degR},
-we find the corresponding degrees in $r$
-of the characteristic polynomial $A_n(r, \lambda)$
-  and minimal polynomial $P_n(r, \lambda)$ of the $n$-cycles
-are $n N_e(n)$ and $n L_e(n)$, respectively.
+we find that
+  $\deg_r A_n(r, \lambda) = n N_e(n)$
+  and $\deg_r P_n(r, \lambda) = n L_e(n)$.
 
@@
 %
-The existence of odd-cycles is why we used even, but not odd, cyclic polynomials
-  in the solution.
-An odd $2n$-cyclic polynomials is also always zero
-  in an $n$-odd-cycle,
-e.g., $C_1 = x_1 + x_2 + \dots + x_n - x_1 - x_2 - \dots - x_n = 0$;
-and the zero determinant condition \refeq{xr}
+It follows that a cyclic polynomial
+  formed by the $2n$ points
+  with an odd degree in $\vxn{2n}$
+  is also always zero,
+  e.g., $C_1 = x_1 + x_2 + \dots + x_n - x_1 - x_2 - \dots - x_n = 0$.
+Accordingly, the characteristic equation \refeq{xr}
   would omit the $n$-odd-cycles from the solution.
+The existence of odd-cycles is why we use even, but not odd,
+  cyclic polynomials in the solution.
 
@@
 
+Finally, we mention that the $n$-cycle polynomial $P_n\rlam$
+  is an even polynomial of $r$ if $n$ is a multiple of 4.
+%This follows from that the transformation
+%  $x_k \equiv (-)^k i y_k, r \equiv -r'$
+%  yields the identical map: $y_{k+1} = r' y_k - {y_k}^3$.
+Practically, we can cut the computating time by half
+  when calculating the determinant by Lagrange interpolation
+  in this case.
+
 \nonumsection{Acknowledgments} \noindent
-I thank Drs. T. Gilbert and Y. Mei for helpful communications.
+It is a pleasure to thank T. Gilbert, Y. Mei and the referees
+  for helpful communications and suggestions.
 Computing time on the Shared University Grid at Rice,

### 2013-05-15 doc/pc-ijbc.tex
add a few references, hengb.magma scripts
sightly improve doc

@@
 
-We will illustrate the algorithm on the logistic map \cite{may, strogatz}
-  defined in \refeq{logmap}.
+We will illustrate the algorithm on the logistic map% \cite{may, strogatz}
+  defined in \refeq{logmap},
+  although it can be readily generalized.
+%
 If $r$ is real,
@@
   %$(\vx)$ formed by the cycle points $\vx = \{x_1, \ldots, x_n\}$,
-  is given by
+  is given by \cite{riordan}
 \begin{equation}
@@
 $\Lambda(\vxn{n})$ = $[\Lambda(\vxn{d})]^c$.
+%
 By factorizing $\lambda - \Lambda^c$
-  in terms of complex roots of unity, we get
+  in terms of the $c$ complex roots of $\lambda$,
+  we get
+%
 \begin{align}
@@
 where $k$ runs through integers from 1 to $c=n/d$,
-  that are coprime to $c$.
+  which are coprime to $c$.
+%
+This product for cycle intersection is equivalent to a previous
+  formula in terms of canonical matrices \cite{blackhurst}.
+%
 With these contributions removed,
@@
 %
-By a change of variables
+By a change of variables \cite{huang}
   $x_k^\mathrm{new} \equiv a \, x_k^\mathrm{old},
@@
   are the trace and determinant of $\vct J^n(x_1)$,
-  respectively \cite{hitzl}.
+  respectively \cite{huang, hitzl}.
 The onset and bifurcation points
@@
 %
-In fact, all antisymmetric cubic maps \cite{brown3, brown4}
+In fact, all antisymmetric cubic maps \cite{may2, brown3, brown4}
   can be mapped to \refeq{cubic} by a change of variables.
@@
 while the even ones sum to
-%or the cube-free cyclic polynomials for the cubic map of even degrees in $\vx$
-%is given by
 \begin{equation}
@@
 %
-$N_e(n) = $ 2, 4, 6, 14, 26, 68, 158, 424, \dots, from $n = 1$.
+$N_e(n) =$ 2, 4, 6, 14, 26, 68, 158, 424, \dots, from $n = 1$.
 %
@@
 
-Finally, we mention that the $n$-cycle polynomial $P_n\rlam$
-  is an even polynomial of $r$ if $n$ is a multiple of 4.
-%This follows from that the transformation
-%  $x_k \equiv (-)^k i y_k, r \equiv -r'$
-%  yields the identical map: $y_{k+1} = r' y_k - {y_k}^3$.
-Practically, we can cut the computating time by half
-  when calculating the determinant by Lagrange interpolation
-  in this case.
+Finally, we mention that the $n$-cycle polynomial $P_n\rlam$,
+  after divided by the contribution from the odd-cycles,
+  is an even polynomial of $r$ for an even $n$.
+%
+This follows from that the transformed variables
+  $y_k \equiv (-)^k i x_k$
+satisfy
+  $y_{k+1} = (-r) y_k - {y_k}^3$.
+Thus, there is a one-to-one correspondence
+  between the cycles for $r$ and $-r$.
+%
+Since the mapping applies to an even $m$-odd-cycle,
+  hence the corresponding $2m$-cycle,
+  $P_n\rlam$ is an even polynomial of $r$
+  if $n$ is a multiple of 4.
+%
+This fact allows one to cut the computating time by half
+  in calculating the determinant by Lagrange interpolation
+  in these cases.
 
@@
 
+\bibitem[Riordan(1958)]{riordan}
+  Riordan, J. [1958]
+  {\it An Introduction to Combinatorial Analysis}
+  (Wiley, New York).
+
 \bibitem[Hao(1989)]{hao}
@@
 
+\bibitem[Huang(1985)]{huang}
+  Huang, Y.-N. [1985]
+  ``Determination of the stable periodic orbits for the Henon map by analytical method,''
+  {\it Chin. Phys. Lett.}
+  \textbf{2},
+  97--100.
+
 \bibitem[Hitzl(1985)]{hitzl}
@@
 
+\bibitem[May(1979)]{may2}
+  May, R. M. [1979]
+  ``Bifurcations and dynamic complexity in ecological systems,''
+  {\it Ann. N. Y. Acad. Sci.}
+  \textbf{316},
+  517--529.
+
 \bibitem[Brown(1984a)]{brown3}

### 2013-05-15 doc/pc.tex
add a few references, hengb.magma scripts
sightly improve doc

@@
 The mapping is reversible, or one-to-one.
+%
 For example, if $n = 3$,
@@
 %
-Thus,
+Thus, we have \cite{riordan}
 %
@@
 \end{equation}
-This map is closely related to the one studied by Brown \cite{brown3}.
+This map is closely related to the one studied by Brown \cite{may2, brown3}.
 Since the new replacement rule
@@
 
+\bibitem{riordan}
+  J. Riordan
+  \textit{An Introduction to Combinatorial Analysis}
+  (Wiley, New York, 1958).
+
 \bibitem{hao} B.-L. Hao,
@@
 
+\bibitem{huang}
+  Y. N. Huang
+  Determination of the stable periodic orbits for the Henon map by analytical method,
+  \textit{Chin. Phys. Lett.}
+  \textbf{2},
+  97--100
+  (1985).
+
 \bibitem{hitzl}
@@
 
+\bibitem{may2}
+  R. M. May,
+  Bifurcations and dynamic complexity in ecological systems,
+  \textit{Ann. N. Y. Acad. Sci.}
+  \textbf{316},
+  517--529
+  (1979).
+
 \bibitem{brown3}

### 2013-05-15 prog/mknsolv.py

@@ -206,7 +206,7 @@ rsolv[poly_, x_, prec_:10, wprec_:100, fnbra_:None, svbra_:False,
       intv = RootIntervals[poly][[1]];
     ][[1]];
     Print[Length[intv], " intervals determined ", intv[[1]], "... in ", y, "s"];
-    If [ Length[intv] > 0 && svbra, 
+    If [ Length[intv] > 0 && svbra,
       xsave[fnbraout, intv, True, True];
     ],
     intv = xload[fnbra, True];

### 2013-05-16 doc/pc-ijbc.tex
small change of code
semi-cycle --> half-cycle

@@
 
-\begin{table}[h]\footnotesize
+\begin{table}[h]
+  %\small
   \tbl{
@@
 
-\begin{table}[h]\footnotesize
+\begin{table}[h]%\footnotesize
 %\caption{
@@
 \begin{equation}
-  L_e(n) = \frac{1}{n} \sum_{cd = n} \mu(c)
-    \left[
-      1 + \odd(c)\frac{3^d-1}{2}
-    \right],
+  L_e(n) = \delta_{n, 1} +
+    \frac{1}{n} \sum_{cd = n} \mu(c) \odd(c)\frac{3^d-1}{2},
 \label{eq:cublyndon}
@@
 
-%\subsection{\label{sec:oddcycle}Odd-cycles}
+%\subsection{\label{sec:halfcycle}Odd-cycles}
 
@@
   \begin{minipage}{\linewidth}
-        \includegraphics[angle=-90, width=\linewidth]{oddcycle.pdf}
+        \includegraphics[angle=-90, width=\linewidth]{halfcycle.pdf}
   \end{minipage}%
   \end{center}
-  \caption{\label{fig:oddcycle}
+  \caption{\label{fig:halfcycle}
   Odd-cycles of the cubic map.}
@@
 The symmetry $f(-x) = -f(x)$ permits
-  a particular \emph{odd-cycle},
-  see \reffig{oddcycle} for examples.
+  a particular \emph{half-cycle},
+  see \reffig{halfcycle} for examples.
 If $x_{n+1} = -x_1$ has a solution,
@@
 Accordingly, the characteristic equation \refeq{xr}
-  would omit the $n$-odd-cycles from the solution.
-The existence of odd-cycles is why we use even, but not odd,
+  would omit the $n$-half-cycles from the solution.
+The existence of half-cycles is why we use even, but not odd,
   cyclic polynomials in the solution.
 
-Since the $n$-odd-cycles satisfy a polynomial of lower degree,
+Since the $n$-half-cycles satisfy a polynomial of lower degree,
   the $n$-cycle polynomial $P_{2n}(\lambda)$
@@
 %
-Suppose $\Lambda^o(\vx) \equiv \prod_{k = 1}^{n} f'(x_k)$ in the odd-cycle
+Suppose $\Lambda^o(\vx) \equiv \prod_{k = 1}^{n} f'(x_k)$ in the half-cycle
  satisfies $P_{n}^o(\lambda^o) = 0$
@@
 %
-For example, by solving the $n = 2$ odd-cycle,
+For example, by solving the $n = 2$ half-cycle,
   we have $- x_1 = r x_1 - {x_1}^3$, or ${x_1}^2 = r + 1$.
@@
 Finally, we mention that the $n$-cycle polynomial $P_n\rlam$,
-  after divided by the contribution from the odd-cycles,
+  after divided by the contribution from the half-cycles,
   is an even polynomial of $r$ for an even $n$.
@@
 %
-Since the mapping applies to an even $m$-odd-cycle,
+Since the mapping applies to an even $m$-half-cycle,
   hence the corresponding $2m$-cycle,

### 2013-05-16 doc/pc.tex
small change of code
semi-cycle --> half-cycle

@@
 $x_1, x_2, \ldots, x_n, -x_1, -x_2, \ldots, -x_n$
-(see \reffig{oddcycle}),
+(see \reffig{halfcycle}),
 which makes all odd cyclic polynomials zero,
@@
     \begin{center}
-        \includegraphics[angle=-90, width=\linewidth]{oddcycle.pdf}
+        \includegraphics[angle=-90, width=\linewidth]{halfcycle.pdf}
     \end{center}
   \end{minipage}%
-  \caption{\label{fig:oddcycle}
+  \caption{\label{fig:halfcycle}
   Odd-cycles of the cubic map.}
@@
 $^\dagger$
-The factors from odd-cycles (see \refsec{oddcycle}) are struck out.
+The factors from half-cycles (see \refsec{halfcycle}) are struck out.
 }\\
@@
 $^\ddagger$
-The $n = 4$ odd-cycles satisfy
+The $n = 4$ half-cycles satisfy
 $(\lambda^\odd + 9)^2 - 2(\lambda^\odd-27) r^2 - 8 r^4 = 0$,
@@
 
-\subsection{\label{sec:oddcycle}Odd-cycles}
+\subsection{\label{sec:halfcycle}Odd-cycles}
 
@@
   for $x_{n+1} = - x_{(n/2)+1} = x_1$.
-We call such a cycle an odd-cycle,
-see \reffig{oddcycle} for examples.
+We call such a cycle an half-cycle,
+see \reffig{halfcycle} for examples.
 %
@@
 %
-Suppose $\Lambda^\odd(\vx) \equiv \prod_{k = 1}^{n/2} f'(x_k)$ in the odd-cycle
+Suppose $\Lambda^\odd(\vx) \equiv \prod_{k = 1}^{n/2} f'(x_k)$ in the half-cycle
  satisfies $P_{n/2}^\odd(r, \lambda^\odd) = 0$
@@
 $^\dagger$
-$\zeta(s) = \sum_n n^{-s}$ is the zeta function.
-See ref. \cite{hardy} for proofs.
+$\zeta(s) = \sum_n n^{-s}$ is the zeta function, cf. ref. \cite{hardy}.
 }\\
@@
 
-Another fact is if $G_\alpha(s)$ is the generating function of $\alpha(n)$,
+If $G_\alpha(s)$ is the generating function of $\alpha(n)$,
 then $G_\alpha(s-1)$ is that of $n \alpha(n)$,
@@
 We now compute the generating function of $\mu(n)\odd(n)$.
-First, recall the generating function $G_\mu(s)$ of $\mu(n)$ is
+First, $\mu(n)/n^s$ can be expanded by
+  the distinct prime factors of $n$ as $\prod_p (-)/p^s$
+  (the term is zeroed by $\mu(n)$
+  if $n$ is divisible by a square of a prime).
+%
+Thus,
+the generating function $G_\mu(s)$ of $\mu(n)$:
 \[
@@
 %
-The follows directly from expanding the product
-  and the definition of $\mu(n)$,
-which is $-1$ to the power of the number of distinct prime factors.
+%The follows directly from expanding the product
+%  and the definition of $\mu(n)$,
+%which is $-1$ to the power of the number of distinct prime factors.
 %
 The same reasoning applies to
-$G_{\mu, \odd}(s) = \sum_{n \text{ odd}} \mu(n)/n^s$
+$G_{\mu, \odd}(s) = \sum_{n, \odd} \mu(n)/n^s$
 with the only difference being that all multiples $n$ of 2
@@
   = \sum_{n=1}^{\infty} \frac{\mu(n) \, \odd(n)}{n^s}
-  = \sum_{n \text{ odd}} \frac{\mu(n)}{n^s}
+  = \sum_{n, \odd} \frac{\mu(n)}{n^s}
   = \prod_{p \ge 3} \left( 1 - \frac{1}{p^s} \right).
@@
 Similarly,
-we can compute the generating function of $\odd(n)$ as
+the generating function of $\odd(n)$ is
 \[
@@
 \]
-This can also be derived by taking the generating function of
-both sides of the identity:
-$\sum_{d|n} \mu(d) \odd(d) \, \odd(n/d) = \delta_{n, 1}$
-\big[which is a modification of
-$\sum_{d|n} \mu(d) = \delta_{n, 1}$\big].
-%
-It follows that the generating function of $n \, \odd(n)$ is $G_\odd(s-1)$.
+%
+%This can also be derived by taking the generating function of
+%both sides of the identity:
+%$\sum_{d|n} \mu(d) \odd(d) \, \odd(n/d) = \delta_{n, 1}$
+%\big[which is a modification of
+%$\sum_{d|n} \mu(d) = \delta_{n, 1}$\big].
+%
+%It follows that the generating function of $n \, \odd(n)$ is $G_\odd(s-1)$.
 
@@
 \end{align*}
-Comparing the coefficients of the $n$th term ($n \ll M$),
-  we find
+Comparing the coefficients of the $n$th term yields
 \[
@@
 \bibitem{riordan}
-  J. Riordan
+  J. Riordan,
   \textit{An Introduction to Combinatorial Analysis}
@@
   (1984);
-
+%
   Solutions of period four for a non-linear difference equation,

### 2013-05-17 doc/pc-ijbc.tex
pc-ijbc: improve the discussion on the cubic map

@@
 \usepackage{ws-rotating}
+%\usepackage{multicol}
 \begin{document}
@@
 \newcommand{\odd}{\mathrm{odd}}
+\newcommand{\even}{\mathrm{even}}
 
@@
 % switch text to two-column
+%\begin{multicols}{2}
 \twocolumn
@@
 
-We will illustrate the algorithm on the logistic map% \cite{may, strogatz}
-  defined in \refeq{logmap},
-  although it can be readily generalized.
+We will illustrate the algorithm on the logistic map % \cite{may, strogatz}
+  \refeq{logmap}.
+%
+The generalizations are straightforward.
 %
@@
 %
-We attach the subscript $n$ to $A\Rlam$ because
-  it will later be used with $A_d\Rlam$ of divisors $d$ of $n$.
+We attach the subscript $n$ to the determinant because
+  it will later be used with those of divisors $d$ of $n$.
 %
@@
   is marginally stable when $R$ satisfies
-  characteristic equation $\big| \lambda \, \vct I - \vct T(R) \big| = 0$.
+  the characteristic equation
+  $\big| \lambda \, \vct I - \vct T(R) \big| = 0$.
   \label{thm:main}
@@
 \]
-With $\Lambda \rightarrow \lambda$, the characteristic equation (\ref{eq:xr}) reads
-\begin{equation}
-0
+With $\Lambda \rightarrow \lambda$,
+  the characteristic equation (\ref{eq:xr}) reads
+\begin{equation}
+A_1\Rlam
   %=\left| \begin{array}{cc}
@@
   %\end{array} \right|
-  = -4R - 2\lambda + \lambda^2.
+  = -4R - 2\lambda + \lambda^2
+  = 0.
   \tag{\ref{eq:xr}-1}
@@
 Thus, $R = (\lambda^2 -2\lambda)/4$;
-  and the fixed point begins at $R_a = -1/4$ ($\lambda = +1$), and
+  and the fixed point
+  %begins at $R_a = -1/4$ ($\lambda = +1$), and
   becomes unstable at $R_b = 3/4$ ($\lambda = -1$).
@@
 \begin{align}
-0 &= (4R - 4 + \lambda) [(4 R-\lambda)^2 - 4 \lambda].
+A_2 = (4R - 4 + \lambda) [(4 R-\lambda)^2 - 4 \lambda] = 0.
   \tag{\ref{eq:xr}-2}
@@
 %
-The first factor is responsible for the 2-cycle,
-  while the second factor is for the unstable fixed points. % (see later).
+The first factor, denoted as $P_2\Rlam = 4R -r+\lambda$,
+  is responsible for the 2-cycle,
+  while the second factor is for the fixed points (see \refsec{primfac}).
 Setting the former to zero yields $R = 1 - \lambda/4$;
@@
 
-For the $n = 4$ case
-\cite{brown1, stephenson1, stephenson3, bailey1, bailey2, kk1, lewis},
+For the $n = 4$ case,
+%\cite{brown1, stephenson1, stephenson3, bailey1, bailey2, kk1, lewis},
 %$C_0 = 1$,
@@
 %
-\begin{small}
+%\begin{small}
 \begin{align}
-0
+A_4
 %& = \left|
@@
     \big[
-    4096 R^6-12288 R^5 + 256 (\lambda + 48) (R^4- R^3) \notag \\
+    4096 R^6-12288 R^5 + 
+    256 (\lambda + 48) (R^4- R^3) \notag \\
 & \quad
@@
 & \quad
+    \big[(16 R^2 + \lambda)^2 - 16 (2R+1)^2 \lambda \big] \notag \\
+& \quad
     \big[ 16 (R-1)^2 - \lambda \big]
- \, \big[(16 R^2 + \lambda)^2 - 16 (2R+1)^2 \lambda \big],
+ = 0.
 \tag{\ref{eq:xr}-4}
@@
 \end{align}
-\end{small}
-%
-%
-%
-The first (sextic) factor, responsible for the 4-cycle,
-can be factorized as
-$ (
+%\end{small}
+%
+%
+%
+The first (sextic) factor, denoted as $P_4\Rlam$,
+  is responsible for the 4-cycle.
+%
+It can be factorized as
+$ P_4(R, 1)
+= (
     4R - 5
@@
   (4R - 3)^3 - 108
-  \big] =0$
-at the onset point $\lambda = 1$.
+  \big]$
+at the onset point. % $\lambda = 1$.
 %
@@
 %
-At the bifurcation point ($\lambda = -1$), we have
-$4096 R^6 - 12288 R^5 + 12032 (R^4 - R^3)
-  + 8432 R^2 + 4913 = 0$
+At the bifurcation point, % ($\lambda = -1$),
+we have $P_4(R, -1)
+ = 4096 R^6 - 12288 R^5 + 12032 (R^4 - R^3)
+  + 8432 R^2 + 4913$
 %which upon $R \rightarrow r(r-2)/4$ yields the same polynomial
@@
 Thus, it represents not only the $n$-cycles,
-  but also cycles of shorter periods $d$ ($d|n$).
+  but also the shorter $d$-cycles with $d|n$.
 %
@@
   concern $\lambda$ instead of $R$,
-  we will drop the argument $R$ in $P_n\Rlam$ and $A_n\Rlam$, etc.
+  we will drop the argument $R$ in $P_n\Rlam$, $A_n\Rlam$, etc.
 %\begin{remark}
@@
 %there is no irrelevant factor in \refeq{xr1} and
-$P_1(\lambda) = B_1^1(\lambda) = A_1(\lambda)
+$P_1 = B_1^1 = A_1
   = \lambda^2 - 2\,\lambda - 4\,R$.
@@
 %
-$P_2(\lambda) = A_2(\lambda) \, B_1^2(\lambda)^{-1} = 4R - 4 + \lambda$.
+$P_2 = A_2 / B_1^2 = 4R - 4 + \lambda$.
 %
@@
 %
-$P_4(\lambda)
-    = A_4(\lambda) \, B_2^2(\lambda)^{-1}$
+$P_4 = A_4 / B_2^2$
 indeed the yields the sextic factor.
@@
 %    -16(\lambda + 32)(\lambda - 16) R^2 - (\lambda-16)^3$.
-Note, $B_1^4(\lambda)$ is unused for $\mu(4) = 0$.
+Note, $B_1^4$ is unused for $\mu(4) = 0$.
 
@@
   after some transformation,
-  contributes one polynomial factor to $A_n\lam$
+  contributes a polynomial factor to $A_n\lam$
   [\refeq{prod}],
@@
   from the square-free cyclic polynomials
-  to the binary necklaces.
-%
-A binary necklace
-  is a nonequivalent binary $0$-$1$ string.
+  to the binary necklaces,
+%
+which are nonequivalent binary $0$-$1$ strings.
 %
@@
 By \refeq{xr},
-  $\NB$ is also $\deg_\lambda A_n$.
+  $\NB(n) = \deg_\lambda A_n\Rlam$.
 The first few $\NB(n)$ are
@@
 %\begin{theorem}
-Next the polynomial $P_n\lam$ can be written as
+Next, the $n$-cycle polynomial $P_n\lam$ can be written as
 \begin{equation}
   P_n\lam = \textstyle\prod_l [\lambda - \Lambda(\vxn{n}^{(l)})],
+\notag
 \end{equation}
@@
   \NB(n) = \textstyle\sum_{d|n} \LB(d).
-\label{eq:necklacelyndon}
+\notag
+%\label{eq:necklacelyndon}
 \end{equation}
@@
   which accommodates all fixed points of $f^n$,
-  %\refeq{necklacelyndon} shows that
   each distinct $d$-cycle (with $d|n$)
@@
 %
-One can show that (1) such an intersection happens only
+One can show that i) such an intersection happens only
   at the onset of the longer $n$-cycle, where $\lambda = 1$,
 %
-  and (2) $d$ and $n$ are coprime \cite{blackhurst}.
-%
-The simplest example is the first bifurcation point
-  at $R = 3/4$ for $d = 1, n = 2$,
-  where the fixed point \refeq{xr1}
-  undergoes period-doubling and becomes the 2-cycle \refeq{xr2}.
+  and ii) $d$ and $n$ are coprime \cite{blackhurst}.
+%
 As a result, the $n$-cycle polynomial $P_n(R, \lambda)$
@@
   with $\lambda'$ being a primitive $(n/d)\,$th root of $\lambda = 1$.
+%
+The simplest example is the first bifurcation point
+  at $R = 3/4$ for $d = 1, n = 2$,
+  where the fixed point %\refeq{xr1}
+  undergoes period-doubling and becomes the 2-cycle. % \refeq{xr2}.
 
 We can therefore distinguish \emph{original} cycles
-  from those born out of the above branching.
+  from those born out of the above intersection.
 Similar to \refeq{QP},
@@
 %
-Take the $n = 4$ case as an example, we have
+Take the $n = 4$ case as an example,
+[cf. \refsec{examples}],
+we have
 $\prod_{k=1,3} P_1(R, e^{k\pi i/2})
@@
 $P_2(R, -1) = 4R - 5$
-(for $c = 2$),
-and
-$P_4(R, 1)
-= (4R - 5) (16 R^2 + 8 R + 5)
-  \bigl[
-    (4R - 3)^3 - 108
-  \bigr]$.
-Dividing $P_4(R, 1)$ by the two factors yields
+(for $c = 2$).
+%
+Dividing $P_4(R, 1)$ 
+by the two factors yields
 $S_4(R) = (4R-3)^3 - 108$.
@@
 From \refeq{xr},
-  every term in the expansion of the determinant $|\vct A|$
+  every term in the determinant $|\vct A|$
   can be written as
@@
 Now running $p$ and $q$ through the $\NB$ cyclic polynomials
+ and using $\deg_\vx \Lambda(\vx) = n$
   yields
 \[
-  \deg_R |\vct A | = \deg_R \textstyle\prod_{p} A_{p,q} \le n \, \NB(n),
+  \deg_R |\vct A | = \deg_R \textstyle\prod_{p} A_{p,q} \le n \, \NB(n).
 \]
-where we have used $\deg_\vx \Lambda(\vx) = n$.
-%
-The equality can be achieved, if each $q$ is the ``complement'' of $p$,
-  that is, if $\prod_k x_k^{e_k}$ is the generator of $C_p$,
+%
+The equality can be achieved, if each $q$ is the complement of $p$,
+  that is, if $C_p$ is generated from $\prod_k x_k^{e_k}$,
   $C_q$ can be generated from $\prod_k x_k^{1-e_k}$.
@@
 Now, taking the degrees in $R$ of \refeq{primfac} and \refeq{origfac}
-  yields
+  yields two known formulas
+\cite{mira, stephenson1, blackhurst}:
 %
 \begin{subequations}
-\begin{align}
-\deg_R P_n\Rlam &\equiv \beta(n) = \sum_{d|n} \mu\Big(\frac{n}{d}\Big) 2^{d-1}, \\
+\begin{align*}
+\deg_R P_n\Rlam &\equiv \beta(n)
+  = \sum_{d|n} \mu\Big(\frac{n}{d}\Big) 2^{d-1}, \\
 \deg S_n(R) &= \beta(n)
   - \sum_{d | n, d < n} \beta(d) \, \varphi\Big(\frac{n}{d}\Big).
-\end{align}
+\end{align*}
 \label{eq:degR}
@@
 %
-The two formulas are known \cite{mira, stephenson1, blackhurst}.
-%
-%
-The first few
-  $\deg_R P_n\Rlam$,
-  and $\deg S_n(R)$ are
+The first few $\deg_R P_n\Rlam$ are
   1, 1, 3, 6, 15, 27, 63, 120, 252, 495, \dots, %1023, 2010, 4095, \dots,
+and $\deg S_n(R) = $
   1, 0, 1, 3, 11, 20, 57, 108, 240, 472, \dots, % 1013, 1959, 4083, \dots,
-  respectively, from $n = 1$.
+from $n = 1$.
 
@@
 
-Let us summarize the algorithm.
-%
-First, we list \refeqs{xcp}  with $\Lambda(\vx) = \prod_{k=1}^n f'(x_k)$.
-This step populates elements of the matrix $\vct T$.
-%
-The characteristic equation $A_n(\lambda) = \big|\lambda \, \vct I - \vct T\big| = 0$,
-with $\lambda$ being $+1$ and $-1$, then gives
-the polynomials at onset and bifurcation points, respectively.
-%
-The contributions from shorter $d$-cycles
-  can be removed by
-  % computing the characteristic equations for all divisors $d$ and applying
-  \refeq{primfac}.
-%
-
+%Let us summarize the algorithm.
+%%
+%First, we list \refeqs{xcp}  with $\Lambda(\vx) = \prod_{k=1}^n f'(x_k)$.
+%This step populates elements of the matrix $\vct T$.
+%%
+%The characteristic equation $A_n(\lambda) = \big|\lambda \, \vct I - \vct T\big| = 0$,
+%with $\lambda$ being $+1$ and $-1$, then gives
+%the polynomials at onset and bifurcation points, respectively.
+%%
+%The contributions from shorter $d$-cycles
+%  can be removed by
+%  % computing the characteristic equations for all divisors $d$ and applying
+%  \refeq{primfac}.
+%%
+
+The most time-consuming step is the evaluation of the determinant
+in \refeq{xr}.
+%
 When implemented on a computer,
@@
   = \lambda^2 - \Theta(\vx) \,\lambda +(-b)^n = 0,
+\notag
 %\tag{$\ref{eq:der}'$}
-\label{eq:henonder}
+%\label{eq:henonder}
 \end{equation}
@@
 %
-Unlike the logistic map, this map is antisymmetric,
-  that is, $f(-x) = -f(x)$.
-%
-In fact, all antisymmetric cubic maps \cite{may2, brown3, brown4}
-  can be mapped to \refeq{cubic} by a change of variables.
+Unlike the logistic map, this map is antisymmetric:
+  $f(-x) = -f(x)$.
+%
+It can be mapped to another antisymmetric cubic map \cite{may2, brown3, brown4}
+  by a change of variables.
 We shall show below that this odd parity can be used to reduce the amount of calculation.
@@
 
-The odd parity, however, allows us to limit
+The odd parity, however, limits
   the set of cube-free cyclic polynomials
@@
 %
-This is because \refeq{cubreplace} contains only linear and cubic terms,
-and a cyclic polynomial with an odd (even) degree in $\vx$
+This is because \refeq{cubreplace} %contains only linear and cubic terms,
+never reduces a cyclic polynomial with an odd (even) degree in $\vx$
 can never be reduced to one with an even (odd) degree.
@@
 %Similar to the logistic-map case,
-Even cube-free cyclic polynomials
-can be mapped to \emph{even ternary} necklaces,
+Even-degree cube-free cyclic polynomials
+correspond to \emph{even ternary} necklaces,
 in which each bead can assume
@@
     \right],
-\label{eq:cubnecklace}
+\notag
+%\label{eq:cubnecklace}
 \end{equation}
 where
-$\odd(c)$ %$\equiv \big[1 - (-1)^c\big]/2$
-is 1 if $c$ is odd or 0 if even.
+$\odd(c) \equiv c \mod 2$.
 %\label{thm:cubnecklace}
@@
 %
-Since $N_e \approx N_3/2$, using the parity saves about half of the equations
+Since $N_e \approx N_3/2$, using the parity
+  saves about half of the equations
   in computation.
@@
   from the determinant equation
-  has a degree $N_e(n)$ in $\lambda$.
-Again, it encompasses the factors
-  from the shorter $d$-cycles ($d|n$),
-  and the $n$-cycle polynomial can be obtained
-  from \refeq{primfac} by proper substitutions, e.g.,
+  has a degree $N_e(n)$ in $\lambda$,
+and it encompasses the factors
+  from the shorter $d$-cycles with $d|n$.
+The pure $n$-cycle polynomial $P_n\rlam$ can be obtained
+  from \refeq{primfac} by proper substitutions
   $R\rightarrow r$.
@@
 The degree in $\lambda$ of $P_n\rlam$
-  is given by, after some algebra,
+is given by the M\"obius inversion
+$L_e(n) = \sum_{d|n} \mu(n/d) N_e(d)$,
+which becomes, after some algebra,
 %
@@
   L_e(n) = \delta_{n, 1} +
-    \frac{1}{n} \sum_{cd = n} \mu(c) \odd(c)\frac{3^d-1}{2},
-\label{eq:cublyndon}
-\end{equation}
-%
-%
-For the first few values,
-  $L_e(n)$ = 2, 2, 4, 10, 24, 60, 156, 410, \ldots, starting from $n = 1$.
-%
-This is also the number of the $n$-cycles \cite{hao, hao2}.
-Note that, for $n>1$, $x_k$ in half of the cycles
+    \frac{1}{n} \sum_{cd = n} \mu(c) \odd(c)\frac{3^d-1}{2}.
+\notag
+%\label{eq:cublyndon}
+\end{equation}
+%
+%
+%For the first few values,
+The first few values are 2, 2, 4, 10, 24, 60, 156, 410, \ldots, starting from $n = 1$.
+%
+This is also the number of the $n$-cycles \cite{zeng}.
+%
+The $\delta_{n,1}$ term corresponds to the fixed point
+  at the origin,
+%
+%Excluding this term,
+and
+$L^*_e(n) \equiv L_e(n) - \delta_{n,1}$
+ is the number of nontrivial $n$-cycles \cite{hao, hao2}.
+For $n>1$, half of the cycles points $\vx$
   with negative $r$ are imaginary.
-However, in a transformed map
+They can, however, be made real by
+$x_k = \sqrt{r} z_k$,
+in a transformed map
 $z_{k+1} = r \, z_k \, (1 - {z_k}^2)$,
-which differs from \refeq{cubic} by $x_k = \sqrt{r} z_k$,
-$z_k$ in the negative-$r$ cycles are real.
+which share the same boundary polynomials of $r$.
 %
@@
 Following similar steps in \refsec{degR},
-we find that
+we find
   $\deg_r A_n(r, \lambda) = n N_e(n)$
@@
 
-%\subsection{\label{sec:halfcycle}Odd-cycles}
+%\subsection{\label{sec:halfcycle}Half-cycles}
 
@@
   \caption{\label{fig:halfcycle}
-  Odd-cycles of the cubic map.}
+  Half-cycles of the cubic map.}
 \end{figure}
@@
   a particular \emph{half-cycle},
+  that is a solution of $x_{n+1} = -x_1$,
   see \reffig{halfcycle} for examples.
-If $x_{n+1} = -x_1$ has a solution,
-  then $x_1, \ldots, x_{n}, -x_1, \ldots, -x_{n}$
-  is a $2n$-cycle, for $x_{2n+1} = - x_{n+1} = x_1$.
+%
+A repeatd $n$-half-cycle is a $2n$-cycle:
+  $x_1, \ldots, x_{n}, -x_1, \ldots, -x_{n}, x_1$.
 %
@@
   e.g., $C_1 = x_1 + x_2 + \dots + x_n - x_1 - x_2 - \dots - x_n = 0$.
-Accordingly, the characteristic equation \refeq{xr}
-  would omit the $n$-half-cycles from the solution.
-The existence of half-cycles is why we use even, but not odd,
-  cyclic polynomials in the solution.
-
-Since the $n$-half-cycles satisfy a polynomial of lower degree,
-  the $n$-cycle polynomial $P_{2n}(\lambda)$
+%
+We would have missed the $n$-half-cycle contributions
+  in $A_{2n}\rlam$ and $P_{2n}\rlam$,
+  had the characteristic equation been listed using odd,
+  instead of even cyclic polynomials of $\vx$.
+%The existence of half-cycles is why we use even, but not odd,
+%  cyclic polynomials in the solution.
+
+The polynomial $P^h_n\rlam$ for the $n$-half-cycles
+  share the the same degree in $\lambda$ with $P_n\rlam$.
+%
+We further define $P^{h*}_n\lam$
   (omitting the argument $r$)
-  can always be factorized.
-%
-Suppose $\Lambda^o(\vx) \equiv \prod_{k = 1}^{n} f'(x_k)$ in the half-cycle
- satisfies $P_{n}^o(\lambda^o) = 0$
-\big[where $\lambda^o$ is the value of $\Lambda^o(\vx)$,
-and $\lambda^o = \pm\sqrt \lambda$\,\big],
-then $P^o_{n}(\sqrt \lambda) P^o_{n/2}(-\sqrt \lambda)$
-is a factor of $P_{n}(\lambda)$.
-%
-For example, by solving the $n = 2$ half-cycle,
-  we have $- x_1 = r x_1 - {x_1}^3$, or ${x_1}^2 = r + 1$.
-Since $\lambda^o = r - 3 {x_1}^2$,
-$P^o_1(\lambda^o) = \lambda^o + 2 r + 3$.
+  as $P^h_n\lam$ for $n > 1$,
+  but as $P^h_n\lam/(\lambda - r)$ for $n = 1$,
+  to exclude the contribution from
+  the trivial solution $x=0$
+  (which is both a cycle and half-cycle).
+%
+Since a repeated $n$-half-cycle is a $2n$-cycle,
+  $P^{h*}_{n}\big(\sqrt \lambda\big)
+   P^{h*}_{n}\big(-\sqrt \lambda\big)$
+  is a factor of the $2n$-cycle polynomial $P_{2n}(\lambda)$.
+%
+For example, by solving the nontrivial 1-half-cycle or inversion point,
+  $- x_1 = f(x_1)$, we have ${x_1}^2 = r + 1$,
+%Since $\lambda^h = r - 3 {x_1}^2$,
+and
+$P^{h*}_1(\lambda) = \lambda + 2 r + 3$.
 %
 The 2-cycle polynomial
-  $P_2(\lambda) = -\big[(2r+3)^2 - \lambda\big]\,(\lambda + 2r^2-9)$,
+  $P_2(\lambda) = -\big[(2r+3)^2 - \lambda\big]\,(\lambda + 2r^2-9)$
   indeed contains
-  $P^o_1(\sqrt \lambda) \, P^o_1(r, -\sqrt \lambda)
-   = (\sqrt \lambda + 2 r + 3)(-\sqrt \lambda + 2 r + 3)$
+  $P^{h*}_1(\sqrt \lambda) \, P^{h*}_1(r, -\sqrt \lambda)
+   =
+  \big( \sqrt \lambda + 2 r + 3\big)
+  \big(-\sqrt \lambda + 2 r + 3\big)$
   as a factor.
-
-Finally, we mention that the $n$-cycle polynomial $P_n\rlam$,
-  after divided by the contribution from the half-cycles,
-  is an even polynomial of $r$ for an even $n$.
-%
-This follows from that the transformed variables
+%
+%
+We may therefore define a deducted polynomial as
+\begin{equation}
+\bar P_n\lam \equiv
+  \left.
+    P_n\lam
+  \middle/
+     \left[
+        P^{h*}_{n/2}(\sqrt\lambda)
+        P^{h*}_{n/2}(-\sqrt\lambda)
+      \right],
+  \right.
+\label{eq:Pded}
+\end{equation}
+for an even $n$, and $\bar P_n = P_n$ for an odd $n$.
+%
+As mentioned earily,
+  $\bar P_n$ can also be obtained
+  from the characteristic equation
+  derived for odd cyclic polynomials of $\vx$;
+%
+and $\deg_\lambda \bar P\lam$ is
+\begin{align*}
+%  N_o(n) &= \frac{1}{n} \sum_{c d = n} \varphi(c)
+%      \odd(c) \frac{3^d-1}{2}, \\
+  L_o(n) &= \delta_{n, 1} +
+      \frac{1}{n} \sum_{cd = n}
+    \mu(c) \left[1 - \tfrac{1}{2}\odd(c)\right] (3^d-1).
+\end{align*}
+%
+%and $L^*_o(n) \equiv L_o(n) - \delta_{n,1}$
+%further excludes the fixed point at the origin.
+%
+%Additionally,
+It follows from \refeq{Pded} that
+$L_e(n) = L_o(n) + \even(n) L_e(n/2)$,
+where $\even(n) = 1 - \odd(n)$.
+
+The $n$-half-cycle polynomial
+  are related to the $n$-cycle polynomial as
+  $P^h_n(r, \lambda) = P_n(-r, -\lambda)$
+  for an odd $n$.
+%
+This is because the transformed variables
   $y_k \equiv (-)^k i x_k$
 satisfy
-  $y_{k+1} = (-r) y_k - {y_k}^3$.
-Thus, there is a one-to-one correspondence
-  between the cycles for $r$ and $-r$.
-%
-Since the mapping applies to an even $m$-half-cycle,
-  hence the corresponding $2m$-cycle,
-  $P_n\rlam$ is an even polynomial of $r$
-  if $n$ is a multiple of 4.
-%
-This fact allows one to cut the computating time by half
-  in calculating the determinant by Lagrange interpolation
-  in these cases.
+  $y_{k+1} = (-r) \, y_k - {y_k}^3$.
+%
+Thus, each $n$-cycle
+  $\vx = \{x_1, x_2, \dots, x_n, x_1\}$
+can be mapped isomorphically (one-to-one) to an $n$-half-cycle
+  $\vct y = \{-i x_1, i x_2, \dots, - i x_n, i x_1\}$
+for the map with $-r$,
+and $\Lambda(\vx) = -\Lambda(\vct y)$.
+%
+Further, for an even $n$, the same transformation
+  maps an $n$-(half-)cycle at $r$ to
+       an $n$-(half-)cycle at $-r$,
+  with $\Lambda(\vx) = \Lambda(\vct y)$.
+%
+It follows that $A_{2n}\rlam$, $P^h_{2n}\rlam$, $\bar P_{2n}\rlam$,
+  and $P_{4n}\rlam$, are all even polynomials of $r$.
+%
+Thus, these polynomials need to be computed only
+  at the positive half of $r$ values
+  in Lagrange interpolation.
 
@@
 
+\bibitem[Zeng(1985)]{zeng}
+  Zeng, W. [1985]
+  ``On the number of stable cycles in the cubic map''
+  {\it Commun. Theor. Phys.}
+  \textbf{8}
+  273--280.
+
 \end{thebibliography}
 
+%\end{multicols}
+
 \end{document}

### 2013-05-22 doc/pc-ijbc.tex
editing pc-ijbc.tex, remove spaces

@@
 \newcommand{\vxn}[1]{\vx_{#1}}
+\newcommand{\vyn}[1]{\vct y_{#1}}
 \newcommand{\Tr}{\mathrm{Tr}}
@@
   connecting the cyclic polynomials of the cycle points.
-The minimal polynomials of the critical parameters
+The polynomials satisfied by the critical parameters
   of the logistic, H\'enon, and cubic maps are obtained
@@
   $x_2 = f(x_1)$,
-  $x_3 = f(x_2)$, $\ldots$
+  $x_3 = f(x_2)$,
+  $\ldots$,
 can be conveniently visualized on the cobweb plot,
@@
   each vertical arrow takes $(x_k, x_k)$ to $(x_k, y)$,
-  where $y = f(x_k) = x_{k+1}$;
-the next horizontal arrow then reflects $(x_k, y)$ to
+  where $y = x_{k+1} = f(x_k)$;
+by the following horizontal arrow,
+  it returns to the diagonal at
   $(y, y) = (x_{k+1}, x_{k+1})$,
-  the starting point of the next iteration.
+  which starts the next iteration.
 %
@@
 %
-The problem is to identify
+The problem of identifying
   all regions of $r$ that allow stable $n$-cycles,
-  which has been the objective of several previous
-  studies
+  has been the objective of several previous studies
   \cite{brown1, brown2, stephenson1, stephenson2, stephenson3,
@@
   which gradually eliminates $x_k$ out of the $n+1$ equations.
-As a special case, if $x_2, \dots, x_n$ are eliminated first,
-  the final elimination of $x_1$ can be accomplished
-  by setting the resultant of $f^n(x_1) = x_1$ and
-  \refeq{der} or $\frac{d}{dx}f^n (x_1) = \pm 1$
+If $x_2, \dots, x_n$ are eliminated first,
+  there are only two equations left:
+  $f^n(x_1) = x_1$
+  and
+  $\frac{d}{dx}f^n (x_1) = \pm 1$
+  [\refeq{der}];
+  the final elimination of $x_1$ can then be accomplished
+  by setting the resultant of the two equations
   to zero \cite{burm},
-  which furnishes the needed polynomial equation of $R$.
+  leading to the desired polynomial equation of $R$.
 %
@@
 Instead of solving \refeqs{logmaps} for $x_k$,
-  we will derive a set of \emph{homogeneous linear} equations
-  $\sum_j A_{ij} C_j = 0$
-  regarding cyclic polynomials $\{C_j\}$ of $x_k$
+  we will derive a set of equations
+  in terms of the cyclic polynomials $\{C_p\}$ of $x_k$
   (an example of a cyclic polynomial is $x_1 x_2 + x_2 x_3 + \dots + x_n x_1$).
 %
-Now the matrix formed by the coefficients $A_{ij}$ of the equations
+The advantage is that the new set of equations are
+  \emph{homogeneous}, \emph{linear} and \emph{complete},
+  i.e., there is an equation
+  $\sum_q A_{pq} C_q = 0$ for every cyclic polynomial labeled by $p$.
+%
+Now the matrix formed by the coefficients $A_{pq}$
   must have a zero determinant,
-  for the cyclic polynomials $\{C_j\}$ are not zeros altogether.
+  for the cyclic polynomials $\{C_p\}$ are not zeros altogether.
 %
 Thus, the zero-determinant condition $|\mathbf A| = 0$ gives
-  the needed polynomial equation of $R$,
-whose roots contain all fixed points of $f^n$.
+  the required polynomial equation of $R$.
+%whose roots contain all fixed points of $f^n$.
 %
@@
   e.g., $a = x_1 x_2 + x_2 x_3 + x_3 x_4 + x_4 x_1$
-  and $b = x_1 x_3 + x_2 x_4$ (for $n = 4$).
+  and $b = x_1 x_3 + x_2 x_4$ for $n = 4$.
 %
 It is, however, unnecessarily symmetric
-  (i.e., invariant under the exchange of any two $x_k$ and $x_{j}$),
+  (invariant under the exchange of any two $x_k$ and $x_{j}$),
   e.g., $a$ and $b$ are not symmetric,
@@
   distinct cyclic versions of a simpler polynomial of $x_k$, or a \emph{generator}.
+The generators of the above $a$ and $b$
+  are $x_1 x_2$ and $x_1 x_3$, respectively.
+%For example,
+%$x_1 x_2$ is a generator of $a$;
+%$x_1 x_3$ is that of $b$;
+%and
+%$x_1 x_2 + \frac{1}{2} x_1 x_3$ is that of $a + b$.
+%Note that, according this definition, the coefficient before $x_1 x_3$
+%  is 1 in the second case
+%  for there are only two distinct versions,
+%  but $\frac{1}{2}$ in the third case
+%  for there are four. % distinct versions of the generator.
+%
+%
+%
+Cyclic polynomials
+  generated from monomials of unit coefficient,
+  such as $a$ and $b$, % but not $a + b$ in the above example)
+  can be labeled as follows.
+If we write the monomial generator as
+  ${x_1}^{e_1} {x_2}^{e_2} \dots {x_n}^{e_n}$,
+  then the sequence $p$ of indices with
+  $e_1$ 1's, $e_2$ 2's, \ldots, $e_n$ $n$'s
+  serves as the label of the cyclic polynomial $C_p(\vxn{n})$,
+  where $\vxn{n} \equiv \{x_1, \ldots, x_n\}$
 For example,
-$x_1 x_2$ is a generator of $a$;
-$x_1 x_3$ is that of $b$;
+$C_{12}(\vxn{n})  = x_1 x_2 + x_2 x_3 + \dots + x_n x_1$
 and
-$x_1 x_2 + \frac{1}{2} x_1 x_3$ is that of $a + b$.
-Note that the coefficient before $x_1 x_3$
-  is 1 in the second case
-  for there are only two distinct versions,
-  but $\frac{1}{2}$ in the third case
-  for there are four. % distinct versions of the generator.
-
-Cyclic polynomials
-  generated from monomials of unit coefficient
-  (such as $a$ and $b$, but not $a + b$ in the above example)
-  can be labeled as follows.
-We write the monomial generator as
-  ${x_1}^{e_1} {x_2}^{e_2} \dots {x_n}^{e_n}$,
-  and form a sequence $p$ of indices with
-  $e_1$ 1's, $e_2$ 2's, \ldots, $e_n$ $n$'s.
-The sequence $p$ serves as the label of the cyclic polynomial $C_p(\vxn{n})$,
-  where $\vxn{n} \equiv \{x_1, \ldots, x_n\}$
-[we will, however, drop the subscript ``$_n$'' or
-  even the argument ``$(\vxn{n})$'' entirely when it is clear].
-For example,
-  $C_{12}(\vx)  = x_1 x_2 + x_2 x_3 + \dots + x_n x_1$ and
-  $C_{112}(\vx) = {x_1}^2 x_2 + {x_2}^2 x_3 + \dots + {x_n}^2 x_1$.
+$C_{112}(\vxn{n}) = {x_1}^2 x_2 + {x_2}^2 x_3 + \dots + {x_n}^2 x_1$.
+%
+Below, we may drop the subscript ``$_n$'' or
+  even the argument ``$(\vxn{n})$'' entirely when it is clear.
 In case the cyclic polynomial has several generators,
@@
   in the sense of lexicographic order,
-  e.g., we choose $x_1 x_2$ instead of $x_2 x_3$ for $C_{12}(\vx)$
+  e.g., we choose $x_1 x_2$ over $x_2 x_3$ for $C_{12}$
   because $12 < 23$ ($n \ge 3$).
-Finally, we add $C_0(\vx) \equiv 1$ for completeness.
+Finally, we add $C_0 \equiv 1$ for completeness.
 %
@@
   if it has no square or higher powers of $x_k$,
-e.g., $C_{12}(\vx) = x_1 x_2 + \cdots$ is square-free,
-  $C_{112}(\vx) = {x_1}^2 x_2 + \cdots$ is not.
+e.g., $C_{12} = x_1 x_2 + \cdots$ is square-free,
+  $C_{112} = {x_1}^2 x_2 + \cdots$ is not.
 %see \reftab{sqrfreepoly} for more examples.
@@
   For the logistic map \refeq{logmaps},
-  any cyclic polynomial $K(\vx)$
+  any cyclic polynomial $K(\vxn{n})$
   formed by the $n$-cycle points
-  $\vx = \{x_1, \ldots, x_n\}$
+  $\vxn{n} = \{x_1, \ldots, x_n\}$
   is a linear combination of
-  the square-free cyclic polynomials $C_p(\vx)$:
+  the square-free cyclic polynomials $C_p(\vxn{n})$:
 \[
-  K(\vx) = \sum_{p \in \Pset} f_p(R) \, C_p(\vx),
+  K(\vxn{n}) = \sum_{p \in \Pset} f_p(R) \, C_p(\vxn{n}),
 \]
@@
 %
-Given a cyclic polynomial $K(\vx)$,
+Given a cyclic polynomial $K(\vxn{n})$,
   we recursively apply \refeq{logmaps} as
@@
 Terms involving no $x_k$
-  are collected to serve as the coefficient before $C_0(\vx) \equiv 1$.
+  are collected to serve as the coefficient before $C_0(\vxn{n}) \equiv 1$.
 The coefficients $f_p$ are polynomials of $R$,
@@
   linearly connected by $\NB$ homogeneous equations.
-The matrix of the connecting coefficients thus has a vanishing determinant,
-  which furnishes the desired polynomial equation.
+The matrix of the connecting coefficients thus has a vanishing determinant.
+This condition furnishes the desired polynomial equation.
 
@@
 
-We first observe that the derivative of $f^n$
-is a cyclic polynomial:
-%
-%
-\begin{equation}
-  \Lambda(\vx)
+First, the derivative of $f^n$ is a cyclic polynomial:
+%
+%
+\begin{equation}
+  \Lambda(\vxn{n})
    = f'(x_1) \dots f'(x_n)
@@
 %
-Since $C_p(\vx)$ is also cyclic,
-  so is $\Lambda(\vx) \, C_p(\vx)$,
-The latter can be expanded by \refthm{sqrfree} as
-\begin{equation}
-  \Lambda(\vx) \, C_p(\vx) = \sum_{q \in \Pset} T_{pq}(R) \, C_q(\vx),
+For any square-free cyclic polynomial $C_p(\vxn{n})$,
+the product $\Lambda(\vxn{n}) \, C_p(\vxn{n})$ is also cyclic,
+  and can thus be expanded by \refthm{sqrfree} as
+\begin{equation}
+  \Lambda(\vxn{n}) \, C_p(\vxn{n}) = \sum_{q \in \Pset} T_{pq}(R) \, C_q(\vxn{n}),
 \label{eq:xcp0}
@@
 By \refeq{der},
-  $\Lambda(\vx)$ equals to $\lambda = +1$ or $-1$
+  $\Lambda(\vxn{n})$ equals to $\lambda = +1$ or $-1$
   at the onset or bifurcation point,
@@
   becomes a homogeneous linear equation of
-  $C_p(\vx)$:
-\begin{equation}
-  \lambda \, C_p(\vx) = \sum_{q \in \Pset} T_{pq}(R) \, C_q(\vx),
+  $C_p(\vxn{n})$:
+\begin{equation}
+  \lambda \, C_p(\vxn{n}) = \sum_{q \in \Pset} T_{pq}(R) \, C_q(\vxn{n}),
 \label{eq:xcp}
@@
 and
-$\vct C = \{C_p(\vx)\}$ is an $\NB$-dimensional column vector.
+$\vct C = \{C_p(\vxn{n})\}$ is an $\NB$-dimensional column vector.
 
 Since a set of homogeneous linear equations
-  has a non-trivial solution
-  (i.e., $C_p(\vx)$ do not vanish altogether)
+  has a nontrivial solution
+  ($C_p \ne 0$ for at least one $p$)
   only if the determinant of the coefficient matrix
@@
 %
-Now $A_n\Rlam$, after we expand the determinant,
+Now $A_n\Rlam$, from expanding the determinant,
   is a polynomial of $R$ and $\lambda$,
@@
 %
-We attach the subscript $n$ to the determinant because
-  it will later be used with those of divisors $d$ of $n$.
+%The attached subscript $n$ allows us
+%  to use the determinant later with
+%  similar determinants of divisors $d$ of $n$.
 %
@@
   At the onset and bifurcation points,
-  the square-free cyclic polynomials $C_p(\vx)$
-  of the cycle points $\vx = \{x_k\}$
-  are linearly related by % \refeq{xcp},
-  $\lambda \, C_p(\vx) = \sum_{q \in \Pset} T_{pq}(R) \, C_q(\vx)$,
+  the square-free cyclic polynomials $C_p(\vxn{n})$
+  of the cycle points $\vxn{n} = \{x_k\}$
+  are linearly related as
+  $\lambda \, C_p(\vxn{n}) = \sum_{q \in \Pset} T_{pq}(R) \, C_q(\vxn{n})$,
   with $\lambda$ being $+1$ and $-1$, respectively,
@@
   from the square-free reduction of the cyclic polynomial
-  $C_p(\vx) \, \prod_k f'(x_k)$. %[\refeq{logder}].
-  Thus, the fixed point of $f^n$
-  is marginally stable when $R$ satisfies
+  $C_p(\vxn{n}) \, \prod_k f'(x_k)$. %[\refeq{logder}].
+  Thus, the fixed points of $f^n$
+  are marginally stable when $R$ satisfies
   the characteristic equation
@@
   in the complex plane
-  for complex cycles $\vx$
+  for complex cycles of $\vxn{n}$
   if $\lambda$ is set to $\exp(i\theta)$ with $\theta \in [0, 2\pi]$.
@@
     a bulb in the inverted Mandelbrot set
-  (it follows from the transformation $z_k = -x_k, c = -R$, which
-  reduces \refeq{logmaps} to the quadratic map $z_{k+1} = c + {z_k}^2$
-  used in the Mandelbrot set \cite{mandelbrot}),
+  (the inversion $z_k = -x_k, c = -R$
+  reduces \refeq{logmaps} to the standard Mandelbrot form: $z_{k+1} = c + {z_k}^2$
+  \cite{mandelbrot}),
   see ref. \cite{stephenson2, stephenson3}. % and \reffig{logbulb}.
@@
 
-For $n = 1$, we have
+For $n = 1$ (the fixed point), we have
   $C_0 = 1$, $\Lambda = -2 \, C_1 = -2 \, x_1$, and
@@
 \end{equation}
-Thus, $R = (\lambda^2 -2\lambda)/4$;
+So $R = (\lambda^2 -2\lambda)/4$,
   and the fixed point
   %begins at $R_a = -1/4$ ($\lambda = +1$), and
-  becomes unstable at $R_b = 3/4$ ($\lambda = -1$).
-
-For $n = 2$, the cyclic polynomials
+  becomes unstable at $R_b = 3/4$ where $\lambda = -1$.
+
+For $n = 2$, the square-free cyclic polynomials
   are
 $C_0 = 1$,
-$C_1 = x_1 + x_2$,
-$C_{12} = x_1 x_2$;
-and $\Lambda = 4 \, x_1 x_2$.
-Thus,
+$C_1 = x_1 + x_2$
+and
+$C_{12} = x_1 x_2$,
+with $\Lambda = 4 \, x_1 x_2$.
+So
 $\Lambda \, C_0 = 4 \, C_{12}$,
@@
   = -8 \, R \, C_0 + 4 \, (R + 1) \, C_1$
-by the example after \refthm{sqrfree},
+(by the example after \refthm{sqrfree}),
 $\Lambda \, C_{12}
@@
   is responsible for the 2-cycle,
-  while the second factor is for the fixed points (see \refsec{primfac}).
+  while the second factor is for the fixed points (cf. \refsec{primfac}).
 Setting the former to zero yields $R = 1 - \lambda/4$;
@@
 %
-we only list the final characteristic equation \eqref{eq:xr}
-after the square reduction:%
+we only list the final characteristic equation \eqref{eq:xr}:
+%after the square-free reduction:
 %(with six square-free cyclic polynomials):
@@
   is derived for the fixed points of $f^n$.
-Thus, it represents not only the $n$-cycles,
+Thus, it encompasses not only the $n$-cycles,
   but also the shorter $d$-cycles with $d|n$.
 %
-Fortunately, the contributions from different cycles
+Fortunately, the contributions from cycles of different periods
   are separate factors of $A_n\Rlam$.
 For a large $n$,
-  the factor $P_n\Rlam$ that represents all $n$-cycles
+  the factor $P_n\Rlam$ of $n$-cycles only,
+  or the \emph{$n$-cycle polynomial} below,
   can be easily recognized
@@
   $B_d^c\Rlam \equiv \prod_{k=1}^c A_{d}(R, e^{2k\pi i/c} \lambda^{1/c})$,
-  $\lambda^{1/c}$ is a complex $c$th root of $\lambda$.
+  and
+  $\lambda^{1/c}$ is a complex $c$th root of $\lambda$;
+  the outer product runs over all divisors $d$ of $n$.
 %\end{theorem}
@@
   if $n$ is the product of $k$ distinct primes,
-  or 0 if $n$ is divisible by a square of a prime.
+  or 0 if $n$ is divisible by a square of a prime;
 %Thus,
-The first few $\mu(n) = 1, -1, -1, 0, -1, 1, -1, \ldots,$
+$\mu(n) = 1, -1, -1, 0, -1, 1, -1, \ldots,$
   from $n = 1$
@@
 
-Since the discussions in this and the next sections
-  concern $\lambda$ instead of $R$,
-  we will drop the argument $R$ in $P_n\Rlam$, $A_n\Rlam$, etc.
+The following discussion concerns the $\lambda$ dependence;
+  and we will drop the argument $R$ in $P_n\Rlam$, $A_n\Rlam$, etc.,
+  till the end of the next section.
 %\begin{remark}
 %$B_{d,c}\lambda$ is a polynomial of $\lambda$.
-Despite the argument $\lambda^{1/c}$,
-  the product $\prod_{k=1}^c A_d(e^{2k\pi i/c} \lambda^{1/c})$,
-  hence $B_d^c\lam$,
-  is free from radicals of powers of $\lambda^{1/c}$,
-  for it is invariant under $\lambda \rightarrow e^{2\pi i} \lambda$.
-Thus, $B_d^c\lam$ is a polynomial of $\lambda$,
-and $\deg_\lambda B_d^c\lam = \deg_\lambda A_d\lam$.
+Despite the radical argument $\lambda^{1/c}$,
+  the expanded product $\prod_{k=1}^c A_d(e^{2k\pi i/c} \lambda^{1/c})$
+  is free from radicals,
+  for it is invariant under $\lambda \rightarrow e^{2\pi i} \lambda$,
+  i.e., $B_d^c\lam$ is a polynomial of $\lambda$.
 Particularly, $B_n^1\lam = A_n\lam$.
+We also have $\deg_\lambda B_d^c\lam = \deg_\lambda A_d\lam$.
 %
@@
 %
-$P_2 = A_2 / B_1^2 = 4R - 4 + \lambda$.
+we have $P_2 = A_2 / B_1^2 = 4R - 4 + \lambda$.
 %
@@
 we can show that
-the last two factors of \refeq{xr4}
+the last two factors of the polynomial in \refeq{xr4}
 can be written as
@@
 $P_4 = A_4 / B_2^2$
-indeed the yields the sextic factor.
+indeed yields the sextic factor.
 %$    = 4096 R^6-12288 R^5+ 256 (\lambda + 48) (R^4- R^3)
 %    -16(\lambda + 32)(\lambda - 16) R^2 - (\lambda-16)^3$.
-Note, $B_1^4$ is unused for $\mu(4) = 0$.
+%Note, $B_1^4$ is unused for $\mu(4) = 0$.
 
@@
 
-%We will prove \refthm{primfac} by the following steps.
-%
-We now prove \refeq{primfac}.
-%
-To do so, we first find the degrees in $\lambda$ of
-  $A_n\lam$ [\refeq{necklace}] and $P_n\lam$ [\refeq{lyndon}].
-By comparing the degrees,
-  we then show that each $P_d\lam$ with $d|n$,
-  after some transformation,
-  contributes a polynomial factor to $A_n\lam$
-  [\refeq{prod}],
-  and the inversion of the relation
-  yields \refeq{primfac}.
+We now show \refeq{primfac} based on the fact that
+  each zero of the characteristic polynomial $A_n\lam$
+  corresponds to a distinct $d$-cycle with $d|n$.
+%\refeq{primfac} then follows from a simple M\"obius inversion.
+
+%We now prove \refeq{primfac}.
+%%
+%To do so, we first find the degrees in $\lambda$ of
+%  $A_n\lam$ [\refeq{necklace}] and $P_n\lam$ [\refeq{lyndon}].
+%By comparing the degrees,
+%  we then show that each $P_d\lam$ with $d|n$,
+%  after some transformation,
+%  contributes a polynomial factor to $A_n\lam$
+%  [\refeq{prod}],
+%  and the inversion of the relation
+%  yields \refeq{primfac}.
 
@@
 %
-The mapping is constructed as follows.
-%
-Given a cyclic polynomial, if the generator contains $x_k$,
+%The mapping is constructed as follows.
+%
+Now given a square-free cyclic polynomial, if its generator contains $x_k$,
   the $k$th character from the right of the necklace is 1,
@@
 %\begin{theorem}
-the number $\NB(n)$ of the square-free cyclic polynomials $C_p$,
-  %$(\vx)$ formed by the cycle points $\vx = \{x_1, \ldots, x_n\}$,
-  is given by \cite{riordan}
+the number $\NB(n)$ of the square-free cyclic polynomials
+  is equal to the number of length-$n$ binary necklaces,
+  which is given by \cite{riordan}
 \begin{equation}
@@
 where $\varphi(m)$ is Euler's totient function,
-which gives the number of integers from 1 to $m$
+  which counts the number of integers from 1 to $m$
   that are coprime to $m$,
@@
   $\varphi(1) = 1$,
-  $\varphi(3) = 2$ for 1 and 2,
+  $\varphi(3) = 2$ for 1 and 2 are coprime to 3,
   $\varphi(6) = 2$ for 1 and 5.
+%
 By \refeq{xr},
@@
 %\begin{theorem}
-Next, the $n$-cycle polynomial $P_n\lam$ can be written as
-\begin{equation}
-  P_n\lam = \textstyle\prod_l [\lambda - \Lambda(\vxn{n}^{(l)})],
+Next, the $n$-cycle polynomial $P_n\lam$ is defined as
+\begin{equation}
+  P_n\lam \equiv \textstyle\prod_l [\lambda - \Lambda(\vxn{n}^{(l)})],
 \notag
@@
   which is given by
-  \cite{hao, hao2, lutzky}.
+  \cite{hao, hao2, lutzky}
 \begin{equation}
@@
 %
-The first few $\LB$ are
+The first few $\LB(n)$ are
 2, 1, 2, 3, 6, 9, 18, 30, 56, 99, \dots %186, 335, 630, \ldots,
 from $n = 1$.
-
-Incidentally, $\LB$ is also the number of aperiodic necklaces of length $n$
+%
+%
+Incidentally, $\LB(n)$ is also the number of aperiodic necklaces of length $n$
 (e.g., for $n = 4$,
-  ``$0011$'' is aperiodic, but ``$0101$'' is not due to the shorter period 2).
-%
-Since an $n$-necklace is either aperiodic itself or
-  a repeated aperiodic $d$-necklace (with $d|n$),
-  we have
+  ``$0011$'' is aperiodic, but ``$0101$'' is not, owing to the shorter period 2).
+%
+An $n$-necklace is either aperiodic itself or
+  a repeat of an aperiodic $d$-necklace with $d|n$; so
 \begin{equation}
@@
 %
-Since the left side is the degree in $\lambda$ of $A_n\lam$,
-  which accommodates all fixed points of $f^n$,
-  each distinct $d$-cycle (with $d|n$)
+%Since the left side is the degree in $\lambda$ of $A_n\lam$,
+Thus, in order for $A_n\lam$ to accommodate all fixed points of $f^n$,
+  each distinct $d$-cycle with $d|n$
   contributes one and only one zero to $A_n\lam$.
@@
 %
-We may thus write
+Further, as the leading coefficient of $A_n\lam$
+  is unity by \refeq{xr}, we must have
 %\begin{theorem}
@@
   \big[\lambda - \Lambda\big(\vxn{n}^{(l)}\big) \big]$
-  with $\vxn{n}^{(l)}$ being the $n$ points
-  corresponding to the $l$th $d$-cycle.
-%
-In order words, $\vxn{n}^{(l)}$ is $\vxn{d}^{(l)}$
+  with $\vxn{n}^{(l)}$ being the $n$ consecutive points
+  in the $l$th $d$-cycle,
+%
+  or the $d$-cycle points $\vxn{d}^{(l)}$
   repeated for $c = n/d$ times:
 \begin{equation}
-  \vxn{n}^{(l)} =
+  \vxn{n}^{(l)}
+  =
+  \vxn{d}^{(l)} \times c
+  =
   \{
@@
     x_1^{(l)}, \ldots, x_d^{(l)}
-  \}
-  = \vxn{d}^{(l)} * c.
+  \}.
 \notag
@@
 It follows that
-$\Lambda(\vxn{n})$ = $[\Lambda(\vxn{d})]^c$.
+$\Lambda(\vxn{n}) = [ \Lambda(\vxn{d}) ]^c$.
 %
@@
       \big]
-    \Big\},
-    \notag
+    \Big\}
+    \notag \\
+  &=  \prod_{k=1}^c P_d\big(e^{2k\pi i/c} \lambda^{1/c}\big),
+\label{eq:QP}
 \end{align}
 %
-Now changing the order of the two products yields
-\begin{equation}
-Q_d^{c}\lam
-  =  \prod_{k=1}^c P_d\big(e^{2k\pi i/c} \lambda^{1/c}\big),
-\label{eq:QP}
-\end{equation}
-%
-%
-Despite the presence of $\lambda^{1/c}$,
-  $Q_d^c\lam$ is a polynomial of $\lambda$,
+where we have exchanged the order of the two products.
+%
+Despite the presence of the radical $\lambda^{1/c}$,
+  $Q_d^c\lam$ is still a polynomial of $\lambda$,
   thanks to the invariance
@@
  & = \prod_{k' = 1}^m \prod_{c | n} \prod_{k=1}^c
+      P_{n/c}\Big(
+        e^{2k\pi i/c}
+        \big(
+          e^{2 k' \pi i/m} \lambda^{1/m}
+        \big)^{1/c}
+      \Big) \\
+ & = \prod_{c | n} \prod_{k''=1}^{m c}
     P_{n/c}\big(
-        e^{2k\pi i/c + 2 k' \pi i/(m c)}
-        \lambda^{1/(m c)}
+      e^{2k''\pi i/(m c)} \lambda^{1/(m c)}
       \big) \\
- & = \prod_{c | n} \prod_{k''=1}^{m c}
-    P_{n/c}(e^{2k''\pi i/(m c)} \lambda^{1/(m c)}) \\
  &
-  = \prod_{c | n} Q_{n/c}^{m c}(\lambda).
+  = \prod_{c | n} Q_{n/c}^{m c}(\lambda)
+  = \prod_{d | n} Q_{d}^{m n/d}(\lambda).
 \end{align*}
 %\end{small}
-The M\"obious inversion yields
+The M\"obius inversion yields
 \begin{equation}
 Q_n^m\lam
-= \textstyle\prod_{d|n} \big[
+= \textstyle\prod_{d|n}
+  \big[
     B_d^{m n/d}\lam
@@
 
-The $n$-cycle polynomial
-  $P_n(R, \lambda)$
-  can be further factorized at $\lambda = 1$.
-%
-This is caused by the intersection of an $n$-cycle
-  and a shorter $d$-cycle ($d|n$, $d < n$),
-  which forces the two to share orbit.
-%
-One can show that i) such an intersection happens only
+At the onset point,
+  the $n$-cycle polynomial
+  $P_n(R, \lambda = +1)$
+  becomes reducible
+%
+  because of the intersection of an $n$-cycle
+  and a shorter $d$-cycle with $d|n$.
+%
+The intersection forces the two cycles to share orbit,
+ and corresponds to
+  a period-$(n/d)$-tupling \cite{hao}
+  of the shorter $d$-cycle.
+%
+One can show that i) it happens only
   at the onset of the longer $n$-cycle, where $\lambda = 1$,
@@
   where the fixed point %\refeq{xr1}
-  undergoes period-doubling and becomes the 2-cycle. % \refeq{xr2}.
-
-We can therefore distinguish \emph{original} cycles
-  from those born out of the above intersection.
+  undergoes a period-doubling and becomes the 2-cycle. % \refeq{xr2}.
+
+We can thus distinguish \emph{original} cycles
+  from those born out of the above cycle intersection. % period-tupling.
+%
 Similar to \refeq{QP},
-  the contributions from the non-original cycles
+  the contributions from the unoriginal cycles
   born out of the $d$-cycles
-  can be written as a cyclotomic product
+  can be arranged as a cyclotomic product
   $\prod_{(k, c) = 1}
@@
         \right)$,
-where $k$ runs through integers from 1 to $c=n/d$,
-  which are coprime to $c$.
+where $k$ runs through integers from 1 to $c=n/d$
+  that are coprime to $c$.
 %
@@
       %\right]
-    },
+    }.
   \label{eq:origfac}
   \end{equation}
-%
-%
-%
-Take the $n = 4$ case as an example,
+
+%
+%
+%
+Take the $n = 4$ case as an example
 [cf. \refsec{examples}],
@@
 %  the onset of the original cycle.
-Note $R_a' = 5/4$ is not original,
-  for it is born out of period-doubling the 2-cycle.
-The two cycles are compared in \reffigs{cobweb}(d) and (e).
+Note that $P_2(R,-1)$ is excluded because it corresponds to the 4-cycle
+  born out of period-doubling the 2-cycle.
+The original and unoriginal 4-cycles are compared
+  in \reffigs{cobweb}(e) and (d).
 
@@
 In the numerical implementation
-  (see \refsec{end}),
-  it is helpful to know the degrees in $R$ of the polynomials
-  to evaluate the determinant by Lagrange interpolation.
-We first show that:
+  (cf. \refsec{end}),
+  the degrees in $R$ of the polynomials are needed
+  for evaluating the determinant by Lagrange interpolation.
+We first show that
 \begin{equation}
@@
 Recall that $A_{p,q}$ results from reducing
-  $\Lambda(\vx) \, C_p(\vx)$ to $C_q(\vx)$
+  $\Lambda(\vxn{n}) \, C_p(\vxn{n})$ to $C_q(\vxn{n})$
   by a sequence of substitutions ${x_k}^2 = R-x_{k+1}$.
@@
 Now running $p$ and $q$ through the $\NB$ cyclic polynomials
- and using $\deg_\vx \Lambda(\vx) = n$
+  and using $\deg_\vx \Lambda(\vxn{n}) = n$
   yields
@@
   is the complement of
-  $C_{123} = x_{234} + \cdots + x_{123}$;
+  $C_{123} = x_2 x_3 x_4 + \cdots + x_1 x_2 x_3$,
   while $C_{12}$ is its own complement.
@@
 it is often helpful to evaluate the characteristic polynomial
-by Lagrange interpolation,
-that is, by evaluating $A_n\Rlam$ at a few different $R$,
-e.g., $R = 0, \pm1, \pm2,\ldots$, then piecing them together
+by Lagrange interpolation:
+we evaluate $A_n\Rlam$ at a few different $R$,
+e.g., $R = 0, \pm1, \pm2,\ldots$, then piece them together
 to a polynomial.
@@
 %
-Note that the resultant of $f^n(x)-x$ and $\frac{d}{dx}f^n(x)-\lambda$
+This is unsurprising,
+  because the resultant of $f^n(x)-x$ and $\frac{d}{dx}f^n(x)-\lambda$
   is the determinant of the Sylvester matrix, which has
@@
   is of only $\NB \approx 2^n/n$ [cf. \refeq{necklace}] rows and columns.
-Thus, the current algorithm is expected to be faster.
+%Thus, the current algorithm is expected to be faster.
 
@@
 %
-We therefore save the polynomials and programs on the web site
+The polynomials and programs are saved on the website
 http://logperiod.appspot.com.
@@
 %
-By a change of variables \cite{huang}
+By
   $x_k^\mathrm{new} \equiv a \, x_k^\mathrm{old},
-   y_k^\mathrm{new} \equiv a \, y_k^\mathrm{old}$,
+   y_k^\mathrm{new} \equiv a \, y_k^\mathrm{old}$
+\cite{huang},
 we have, in terms of the new variables,
@@
 The counterpart of \refeq{der}
-  can be found from the Jacobian of $n$th iterate of \refeq{henons}
+  can be found from the Jacobian of the $n$th iterate of \refeq{henons}
 \[
-  \vct J^n
+  \vct J_n
   \equiv
@@
 By the chain rule, we have
-  $\vct J^n (x_1) = \vct J^1(x_1) \cdots \vct J^1(x_n)$,
+  $\vct J_n (x_1) = \vct J(x_1) \cdots \vct J(x_n)$,
   where
-$\vct J^1(x_k)
+$\vct J(x_k)
   =
@@
     \end{array}
-  \right)$.
-Thus, the eigenvalues $\lambda$ of $\vct J^n$ can be found from
-%
-\begin{equation}
-\big|\, \lambda \, \vct I - \vct J^n(x_1) \,\big|
-  = \lambda^2 - \Theta(\vx) \,\lambda +(-b)^n = 0,
+  \right)$;
+and the eigenvalues $\lambda$ of $\vct J_n$ satisfy
+%
+\begin{equation}
+\big|\, \lambda \, \vct I - \vct J_n(x_1) \,\big|
+= \lambda^2 - \Theta(\vxn{n}) \,\lambda +(-b)^n = 0,
 \notag
@@
 %
-where $\Theta(\vx)$ and $(-b)^n$
-  are the trace and determinant of $\vct J^n(x_1)$,
+where $\Theta(\vxn{n})$ and $(-b)^n$
+  are the trace and determinant of $\vct J_n(x_1)$,
   respectively \cite{huang, hitzl}.
@@
   we have
-    $\Tr \, \vct J^n(x_1) = \cdots = \Tr \, \vct J^n(x_n)$,
-i.e., $\Theta(\vx)$ is a cyclic polynomial of $\vx = \{ x_k \}$.
-%e.g., %$\Theta(\vx) = 4 x_1 x_2 + 2 \, b$ for $n = 2$ and
-%$\Theta(\vx) = -8 x_1 x_2 x_3 - 2 \, b (x_1+ x_2+ x_3)$ for $n = 3$.
-%
-Thus, we can expand $\Theta(\vx) \, C_p(\vx)$
+    $\Tr \, \vct J_n(x_1) = \cdots = \Tr \, \vct J_n(x_n)$,
+  i.e., $\Theta(\vxn{n})$ is a cyclic polynomial of
+  $\vxn{n} = \{x_1, \dots, x_n \}$.
+%e.g., %$\Theta(\vxn{n}) = 4 x_1 x_2 + 2 \, b$ for $n = 2$ and
+%$\Theta(\vxn{n}) = -8 x_1 x_2 x_3 - 2 \, b (x_1+ x_2+ x_3)$ for $n = 3$.
+%
+  Thus, we can expand $\Theta(\vxn{n}) \, C_p(\vxn{n})$
   in terms of square-free cyclic polynomials,
-  and then replace $\Theta(\vx)$ by $\lambda + (-b)^n/\lambda$
+  and then replace $\Theta(\vxn{n})$ by $\lambda + (-b)^n/\lambda$
   in the final characteristic equation to obtain the desired polynomials
@@
   at the onset and bifurcation points for $n$ up to 9
-  are listed in the website in \refsec{end}.
+  are saved on the website in \refsec{end}.
 
@@
 %
-Unlike the logistic map, this map is antisymmetric:
-  $f(-x) = -f(x)$.
-%
-It can be mapped to another antisymmetric cubic map \cite{may2, brown3, brown4}
-  by a change of variables.
-We shall show below that this odd parity can be used to reduce the amount of calculation.
-
-First of all, the new replacement rule
-\begin{equation}
-  {x_k}^3 \rightarrow r \, x_k - x_{k+1}
+It is related to another cubic map
+  $y_{k+1} = a {y_k}^3 + (1-a) y_k$ \cite{may2, brown3, brown4}
+  by $y_k = x_k/\sqrt{r-1}, a = 1-r$.
+
+The solution is similar to the logistic case.
+%
+The new replacement rule
+\begin{equation}
+  {x_k}^3 \rightarrow r \, x_k - x_{k+1},
 \label{eq:cubreplace}
 \end{equation}
-no longer eliminates squares.
-%
-We must, therefore, extend the basis set of cyclic polynomials
+however, eliminates only cubes but not squares of $x_k$.
+%
+Consequently, we must extend the basis set of cyclic polynomials
   from the square-free ones to the cube-free ones,
   in listing equations \eqref{eq:xcp},
-  e.g.,
+with the new $\Lambda(\vxn{n})$ being
+  $\prod_{k=1}^n f'(x_k) = \prod_{k=1}^n (r - 3 {x_k}^2)$.
+For example,
   $C_{112} = {x_1}^2 x_2 + \dots + {x_n}^2 x_1$
@@
   is still not).
-
-The odd parity, however, limits
-  the set of cube-free cyclic polynomials
-  to those of even degrees in $\vx$.
-%
-This is because \refeq{cubreplace} %contains only linear and cubic terms,
-never reduces a cyclic polynomial with an odd (even) degree in $\vx$
-can never be reduced to one with an even (odd) degree.
-%
-%Thus, we only need polynomials of even degrees.
-%
-%We therefore have a theorem similar to \refthm{sqrfree}.
-%%
-%%
-%\begin{theorem}
-%  For the cubic map \refeq{cubic},
-%  any cyclic polynomial $K(\vx)$ of
-%  an $n$-cycle orbit
-%  $\vct x = \{x_1, \ldots, x_n\}$
-%  with an even degree in $\vct x$
-%  is a linear combination of
-%the even cube-free cyclic polynomials $C_p(\vx)$:
-%\[
-%  K(\vx) = \sum_{p \in \Pset} f_p(R) C_p(\vx),
-%\]
-%  where $\Pset = \{0, 11, 12, 13, \ldots, 1122, 1123, \ldots \}$ is
-%  the set of indices of all even cube-free cyclic polynomials,
-%  and $f_p(R)$ are polynomials of $R$.
-%  \label{thm:cubfree}
-%\end{theorem}
-%
-%
-%
-%
-With the above change, the rest derivation is similar to that of the logistic map.
-The new $\Lambda(\vx)$ should be
-$\prod_{k=1}^n f'(x_k) = \prod_{k=1}^n (r - 3 {x_k}^2)$.
+%
 %
@@
 %we have saved the data
-  are listed on the website in \refsec{end}.
+  are saved on the website in \refsec{end}.
 %
@@
   Smallest positive $r$ at the onset and bifurcation points
-  of the $n$-cycles of the cubic map.
+  of the $n$-cycles of the antisymmetric cubic map.
   }
@@
 
+%
+The enlarged basis considerably increases the computational cost.
+%
+The antisymmetry
+  $f(-x) = -f(x)$
+of the map, however, can help alleviate the burden.
+%
+First, we only need cyclic polynomials
+  of \emph{even} (or odd, see below for the difference) degrees in $\vxn{n}$.
+%
+This is because \refeq{cubreplace} %contains only linear and cubic terms,
+never reduces a cyclic polynomial with an odd (even) degree in $\vxn{n}$
+to one with an even (odd) degree.
+%
+Thus, the matrix $\vct T$ in \refeq{xcp} can be split into two independent blocks
+  with two separate sets of eigenvalues.
+%
+
 %Similar to the logistic-map case,
@@
 %
-The number of ternary necklaces is
-$N_3(n) = \frac{1}{n} \sum_{d|n} \varphi(n/d) 3^d$,
-%\begin{theorem}
-while the even ones sum to
+The number of even ternary necklaces is
 \begin{equation}
@@
 $\odd(c) \equiv c \mod 2$.
+$N_e(n) =$ 2, 4, 6, 14, 26, 68, 158, 424, \dots, from $n = 1$.
+%\begin{theorem}
 %\label{thm:cubnecklace}
@@
 %
-Since $N_e \approx N_3/2$, using the parity
-  saves about half of the equations
-  in computation.
-%
-$N_e(n) =$ 2, 4, 6, 14, 26, 68, 158, 424, \dots, from $n = 1$.
+Since the number of all (even and odd) ternary necklaces is
+$N_3(n) = \frac{1}{n} \sum_{d|n} \varphi(n/d) 3^d \approx 2 N_e$,
+half of the cyclic polynomials and their associated equations are spared.
+%
 %
@@
 The pure $n$-cycle polynomial $P_n\rlam$ can be obtained
-  from \refeq{primfac} by proper substitutions
+  from \refeq{primfac} with %proper substitutions
   $R\rightarrow r$.
@@
 %
-The $\delta_{n,1}$ term corresponds to the fixed point
+The $\delta_{n,1}$ term corresponds to the trivial fixed point
   at the origin,
@@
 %Excluding this term,
-and
-$L^*_e(n) \equiv L_e(n) - \delta_{n,1}$
- is the number of nontrivial $n$-cycles \cite{hao, hao2}.
-For $n>1$, half of the cycles points $\vx$
+and we can exclude it by a modification
+$L^*_e(n) \equiv L_e(n) - \delta_{n,1}$.
+For $n>1$, half of the cycles points $\vxn{n}$
   with negative $r$ are imaginary.
@@
 
-The symmetry $f(-x) = -f(x)$ permits
-  a particular \emph{half-cycle},
-  that is a solution of $x_{n+1} = -x_1$,
+Consider now a \emph{half-cycle},
+  which is a solution of $x_{n+1} = -x_1$,
   see \reffig{halfcycle} for examples.
 %
-A repeatd $n$-half-cycle is a $2n$-cycle:
-  $x_1, \ldots, x_{n}, -x_1, \ldots, -x_{n}, x_1$.
-%
-It follows that a cyclic polynomial
+Once repeated, an $n$-half-cycle becomes a $2n$-cycle:
+  $x_1, \ldots, x_{n}, -x_1, \ldots, -x_{n}, x_1$,
+by the antisymmetry $f(-x) = -f(x)$ of the map.
+%
+In such a $2n$-cycle, a cyclic polynomial
   formed by the $2n$ points
   with an odd degree in $\vxn{2n}$
-  is also always zero,
+  is always zero,
   e.g., $C_1 = x_1 + x_2 + \dots + x_n - x_1 - x_2 - \dots - x_n = 0$.
 %
-We would have missed the $n$-half-cycle contributions
+Consequently, we would have missed the $n$-half-cycle contributions
   in $A_{2n}\rlam$ and $P_{2n}\rlam$,
-  had the characteristic equation been listed using odd,
-  instead of even cyclic polynomials of $\vx$.
+  had the characteristic equation been listed using \emph{odd},
+  instead of even cyclic polynomials of $\vxn{n}$.
 %The existence of half-cycles is why we use even, but not odd,
@@
 
-The polynomial $P^h_n\rlam$ for the $n$-half-cycles
-  share the the same degree in $\lambda$ with $P_n\rlam$.
-%
-We further define $P^{h*}_n\lam$
-  (omitting the argument $r$)
-  as $P^h_n\lam$ for $n > 1$,
-  but as $P^h_n\lam/(\lambda - r)$ for $n = 1$,
-  to exclude the contribution from
-  the trivial solution $x=0$
-  (which is both a cycle and half-cycle).
+Similar to the $n$-cycle polynomial $P_n\rlam$,
+  we can define a polynomial $P^h_n\rlam$
+  for the $n$-half-cycles.
+%
+The two share the same degree in $\lambda$.
+%
+We further define
+$P^{h*}_n\rlam = P^h_n\rlam/(\lambda - r)^{\delta_{n,1}}$
+  to exclude the contribution from the trivial solution $x=0$,
+  which is both a cycle and half-cycle.
 %
@@
    P^{h*}_{n}\big(-\sqrt \lambda\big)$
-  is a factor of the $2n$-cycle polynomial $P_{2n}(\lambda)$.
-%
-For example, by solving the nontrivial 1-half-cycle or inversion point,
-  $- x_1 = f(x_1)$, we have ${x_1}^2 = r + 1$,
+  is a factor of the $2n$-cycle polynomial $P_{2n}(\lambda)$
+  (omitting the argument $r$ here).
+%
+For example, by solving $- x_1 = f(x_1)$,
+  we obtain the nontrivial 1-half-cycle or the inversion point:
+  ${x_1}^2 = r + 1$,
 %Since $\lambda^h = r - 3 {x_1}^2$,
@@
 %
-As mentioned earily,
+As discussed earlier,
   $\bar P_n$ can also be obtained
   from the characteristic equation
-  derived for odd cyclic polynomials of $\vx$;
+  derived for odd cyclic polynomials of $\vxn{n}$;
 %
@@
 
+Finally, we show that the computational cost
+  can be further cut by half for an even $n$.
 The $n$-half-cycle polynomial
@@
 %
-Thus, each $n$-cycle
-  $\vx = \{x_1, x_2, \dots, x_n, x_1\}$
+Thus, any $n$-cycle
+  $\vxn{n} = \{x_1, x_2, \dots, x_n, x_1\}$
 can be mapped isomorphically (one-to-one) to an $n$-half-cycle
-  $\vct y = \{-i x_1, i x_2, \dots, - i x_n, i x_1\}$
+$\vyn{n} = \{-i x_1, i x_2, \dots, - i x_n, i x_1\}$
 for the map with $-r$,
-and $\Lambda(\vx) = -\Lambda(\vct y)$.
+  and $\Lambda(\vxn{n}) = -\Lambda(\vyn{n})$.
 %
@@
        an $n$-(half-)cycle at $-r$,
-  with $\Lambda(\vx) = \Lambda(\vct y)$.
+       with $\Lambda(\vxn{n}) = \Lambda(\vyn{n})$.
 %

### 2013-05-22 doc/pc.tex
pc-ijbc: improve the discussion on the cubic map
editing pc-ijbc.tex, remove spaces

@@
 \affiliation{Applied Physics Program and Department of Bioengineering, \
-Rice Univeristy, Houston, TX 77005}
+Rice University, Houston, TX 77005}
 %\maketitle
@@
   each vertical arrow takes $(x_k, x_k)$ to $(x_k, y)$,
-  where $y = f(x_k) = x_{k+1}$;
+  where $y = x_{k+1} = f(x_k)$;
 the next horizontal arrow then reflects $(x_k, y)$ to
@@
   and a shorter $d$-cycle ($d|n$, $d < n$)
-  forces the two to share orbit
+  forces the two to share the same orbit
   (this cannot happen if $d \centernot| n$,
@@
 
-\subsection{\label{sec:halfcycle}Odd-cycles}
+\subsection{\label{sec:halfcycle}Half-cycles}
 
@@
 %
-We therefore save the polynomials and programs of the three maps on the web site
+We therefore save the polynomials and programs of the three maps on the website
 http://logperiod.appspot.com.
@@
 
-\section*{Acknowledgements}
+\section*{Acknowledgments}
 
@@
 
-\bibitem{lutzky} M. Lutzky,
+\bibitem{lutzky}
+  M. Lutzky,
   Counting stable cycles in unimodal iterations,
@@
 
+\bibitem{zeng}
+  W. Zeng,
+  On the number of stable cycles in the cubic map,
+  \textit{Commun. Theor. Phys.}
+  \textbf{8},
+  273--280
+  (1985).
+
 \end{thebibliography}

### 2013-05-27 doc/pc-ijbc.tex
pc-ijbc: remove figure and tables

@@
 
-\newcommand{\vx}{\vct x}
-\newcommand{\vxn}[1]{\vx_{#1}}
-\newcommand{\vyn}[1]{\vct y_{#1}}
+\newcommand{\vx}[1]{\vct x_{#1}}
+\newcommand{\vy}[1]{\vct y_{#1}}
+\newcommand{\vz}[1]{\vct z_{#1}}
 \newcommand{\Tr}{\mathrm{Tr}}
@@
 %
-The iterated sequence $x_1$,
-  $x_2 = f(x_1)$,
-  $x_3 = f(x_2)$,
-  $\ldots$,
-can be conveniently visualized on the cobweb plot,
-  as shown in \reffig{cobweb}.
-%
-Starting from $(x_1, x_1)$ on the diagonal,
-  each vertical arrow takes $(x_k, x_k)$ to $(x_k, y)$,
-  where $y = x_{k+1} = f(x_k)$;
-by the following horizontal arrow,
-  it returns to the diagonal at
-  $(y, y) = (x_{k+1}, x_{k+1})$,
-  which starts the next iteration.
-%
-%
-\begin{figure}[h]
-  \begin{center}
-  \begin{minipage}{\linewidth}
-        \includegraphics[angle=-90, width=\linewidth]{cobweb.pdf}
-  \end{minipage}%
-  \end{center}
-  \caption{\label{fig:cobweb}
-  Cobweb plot of the logistic map.}
-\end{figure}
+%The iterated sequence $x_1$,
+%  $x_2 = f(x_1)$,
+%  $x_3 = f(x_2)$,
+%  $\ldots$,
+%can be conveniently visualized on the cobweb plot,
+%  as shown in \reffig{cobweb}.
+%%
+%Starting from $(x_1, x_1)$ on the diagonal,
+%  each vertical arrow takes $(x_k, x_k)$ to $(x_k, y)$,
+%  where $y = x_{k+1} = f(x_k)$;
+%by the following horizontal arrow,
+%  it returns to the diagonal at
+%  $(y, y) = (x_{k+1}, x_{k+1})$,
+%  which starts the next iteration.
+%
+%
+%\begin{figure}[h]
+%  \begin{center}
+%  \begin{minipage}{\linewidth}
+%        \includegraphics[angle=-90, width=\linewidth]{cobweb.pdf}
+%  \end{minipage}%
+%  \end{center}
+%  \caption{\label{fig:cobweb}
+%  Cobweb plot of the logistic map.}
+%\end{figure}
 %
@@
   (i) a \emph{fixed point} (including infinity),
-      e.g., \reffig{cobweb}(a);
+      %e.g., \reffig{cobweb}(a);
   (ii) a periodic \emph{cycle},
-      e.g., \reffigs{cobweb}(b)-(e);
+      %e.g., \reffigs{cobweb}(b)-(e);
 or
-  (iii) a chaotic trajectory,
-      e.g., \reffig{cobweb}(f).
-We will focus on the first two cases here.
+  (iii) a chaotic trajectory.
+      %e.g., \reffig{cobweb}(f).
+We only discuss the first two cases here.
 
@@
   \cite{strogatz}.
-
+%
 An $n$-cycle is a sequence $x_1, \dots, x_n$,
@@
   e.g., $f^3(x) = f(f(f(x)))$.
-Obviously, any $x_k$ in an $n$-cycle of $f$ is a fixed point of $f^n$
-%
-\big[but the converse is untrue, for a fixed point of $f^n$
-  can also be a fixed point of $f^d$ for a divisor $d$ of $n$:
-  if $f^d(x) = x$, then $f^n(x) = f^d(\cdots f^d(x)\cdots) = x$\big].
+Obviously, any $x_k$ in an $n$-cycle of $f$ is a fixed point of $f^n$.
+%
+%\big[but the converse is untrue, for a fixed point of $f^n$
+%  can also be a fixed point of $f^d$ for a divisor $d$ of $n$:
+%  if $f^d(x) = x$, then $f^n(x) = f^d(\cdots f^d(x)\cdots) = x$\big].
 %
@@
 %
-The cycle and its stability depend on the parameter $r$.
-%
-The problem of identifying
-  all regions of $r$ that allow stable $n$-cycles,
-  has been the objective of several previous studies
+The cycle and its stability depend on the parameter $r$,
+%
+and a stable cycle corresponds to a window
+  between the onset point $r_a$ and bifurcation point $r_b$.
+%
+There are generally multiple such windows for a single $n$,
+  but all $r_a$ are zeros of a polynomial,
+  and all $r_b$ another.
+%
+Our goal is thus to find the two polynomials for a given $n$.
+%
+The problem has been tackled by several previous studies
   \cite{brown1, brown2, stephenson1, stephenson2, stephenson3,
@@
 Below we present a simple algorithm to do so.
-
-\section{\label{sec:logmap}Logistic map}
-
-We will illustrate the algorithm on the logistic map % \cite{may, strogatz}
-  \refeq{logmap}.
-%
-The generalizations are straightforward.
-%
-If $r$ is real,
-  we will find windows $(r_a, r_b)$,
-    within which stable $n$-cycles can exist.
+%
+%
 %
@@
 %  to onset and bifurcation points according to \refeq{der};
-Here, if $r > 0$, then
-  $r_a$ ($r_b$) are the onset (bifurcation) points.
-%
-There are generally multiple such windows for a single $n$,
-  but all onset points satisfy the same polynomial equation,
-  and all bifurcation points another.
-%
-Our goal is thus to find the two polynomials for a given $n$.
-
-To simplify the calculation, we first change variables \cite{mandelbrot, brown1, brown2, saha} as
+%Here, if $r > 0$, then
+%  $r_a$ ($r_b$) are the onset (bifurcation) points.
+%
+
+\section{\label{sec:logmap}Logistic map}
+
+To simplify the calculation, we first change variables \cite{mandelbrot, brown1} as
 %
@@
 
-\subsection{Overall plan}
+\subsection{Strategy}
 
@@
   (\refsecs{cyclic}-\ref{sec:examples}).
-The contributions from shorter $d$-cycles ($d|n$)
-  are lower-degree factors of the polynomials,
-  and can be readily removed (\refsec{primfac}).
+The polynomials contain
+  factors, contributed by short $d$-cycles with $d|n$
+  (which are also fixed points of $f^n$).
+The factors are removed in \refsec{primfac}.
 
@@
   in terms of $R$,
-  and then plug the solution into \req{der}.
+  and then plug the solution into \refeq{der}.
 The result would contain $R$ only,
@@
   in terms of the cyclic polynomials $\{C_p\}$ of $x_k$
-  (an example of a cyclic polynomial is $x_1 x_2 + x_2 x_3 + \dots + x_n x_1$).
+  (an example of a cyclic polynomial is
+  $x_1 x_2 + x_2 x_3 + \dots + x_n x_1$
+  with $n$ terms).
 %
@@
 %
-It is, however, unnecessarily symmetric
-  (invariant under the exchange of any two $x_k$ and $x_{j}$),
+It may not, however, be symmetric
+  (invariant under the exchange of any two $x_i$ and $x_{j}$),
   e.g., $a$ and $b$ are not symmetric,
-  although $a + b$ is.
+  only $a + b$ is.
 
@@
 Cyclic polynomials
-  generated from monomials of unit coefficient,
-  such as $a$ and $b$, % but not $a + b$ in the above example)
+  generated from monomials of unit coefficient
+  %such as $a$ and $b$, % but not $a + b$ in the above example)
   can be labeled as follows.
@@
   $e_1$ 1's, $e_2$ 2's, \ldots, $e_n$ $n$'s
-  serves as the label of the cyclic polynomial $C_p(\vxn{n})$,
-  where $\vxn{n} \equiv \{x_1, \ldots, x_n\}$
+  serves as the label of the cyclic polynomial $C_p(\vx{n})$,
+  where $\vx{n} \equiv \{x_1, \ldots, x_n\}$.
+%
 For example,
-$C_{12}(\vxn{n})  = x_1 x_2 + x_2 x_3 + \dots + x_n x_1$
+$C_{12}(\vx{n})  = x_1 x_2 + x_2 x_3 + \dots + x_n x_1$
 and
-$C_{112}(\vxn{n}) = {x_1}^2 x_2 + {x_2}^2 x_3 + \dots + {x_n}^2 x_1$.
-%
-Below, we may drop the subscript ``$_n$'' or
-  even the argument ``$(\vxn{n})$'' entirely when it is clear.
+$C_{112}(\vx{n}) = {x_1}^2 x_2 + {x_2}^2 x_3 + \dots + {x_n}^2 x_1$.
+%
+Below, we may drop %the subscript ``$_n$'' or even the argument
+  ``$(\vx{n})$'' when it is clear.
 In case the cyclic polynomial has several generators,
@@
   in the sense of lexicographic order,
-  e.g., we choose $x_1 x_2$ over $x_2 x_3$ for $C_{12}$
-  because $12 < 23$ ($n \ge 3$).
-Finally, we add $C_0 \equiv 1$ for completeness.
+  e.g., we choose $x_1 x_2$ over $x_2 x_3$ for $C_{12}(\vx{n})$,
+  because $12 < 23$.
+%
+Finally, we add $C_0(\vx{n}) \equiv 1$.
 %
@@
 We denote the set of all square-free $p$ by
-$\Pset = \{0, 1, 12, 13, \ldots, 123, 124, \ldots, 12\dots n\}$,
+$\Pset = \{0, 1, 12, 13, \ldots, 123, 124, \ldots, 12\cdots n\}$,
 and its size by $\NB$.
@@
   For the logistic map \refeq{logmaps},
-  any cyclic polynomial $K(\vxn{n})$
+  any cyclic polynomial $K(\vx{n})$
   formed by the $n$-cycle points
-  $\vxn{n} = \{x_1, \ldots, x_n\}$
+  $\vx{n} = \{x_1, \ldots, x_n\}$
   is a linear combination of
-  the square-free cyclic polynomials $C_p(\vxn{n})$:
+  the square-free cyclic polynomials $C_p(\vx{n})$:
 \[
-  K(\vxn{n}) = \sum_{p \in \Pset} f_p(R) \, C_p(\vxn{n}),
+  K(\vx{n}) = \sum_{p \in \Pset} f_p(R) \, C_p(\vx{n}),
 \]
@@
 %
-Given a cyclic polynomial $K(\vxn{n})$,
+Given a cyclic polynomial $K(\vx{n})$,
   we recursively apply \refeq{logmaps} as
@@
 Terms involving no $x_k$
-  are collected to serve as the coefficient before $C_0(\vxn{n}) \equiv 1$.
+  are collected to serve as the coefficient before $C_0(\vx{n}) \equiv 1$.
 The coefficients $f_p$ are polynomials of $R$,
@@
 For example, the cyclic polynomial
-  $K(\vxn{2}) = {x_1}^2 \, x_2 + {x_2}^2 \, x_1$
+  $K(\vx{2}) = {x_1}^2 \, x_2 + {x_2}^2 \, x_1$
 can be written as $K = (R + 1) \, C_{1} - 2 R \, C_0$
@@
   as a combination of the square-free ones.
-Below we show that at the onset and bifurcation points,
-  the square-free cyclic polynomials $C_p$ are themselves
-  linearly connected by $\NB$ homogeneous equations.
-The matrix of the connecting coefficients thus has a vanishing determinant.
-This condition furnishes the desired polynomial equation.
+At the onset and bifurcation points,
+  the $\NB$ square-free cyclic polynomials $C_p$ are themselves
+  linearly connected by \refeq{der}.
+This condition yields a characteristic equation,
+  which solves our problem.
 
@@
 
+%The matrix of the connecting coefficients thus has a vanishing determinant.
+%This condition furnishes the desired polynomial equation.
+
 First, the derivative of $f^n$ is a cyclic polynomial:
@@
 \begin{equation}
-  \Lambda(\vxn{n})
+  \Lambda(\vx{n})
    = f'(x_1) \dots f'(x_n)
@@
 %
-For any square-free cyclic polynomial $C_p(\vxn{n})$,
-the product $\Lambda(\vxn{n}) \, C_p(\vxn{n})$ is also cyclic,
+For any square-free cyclic polynomial $C_p(\vx{n})$,
+the product $\Lambda(\vx{n}) \, C_p(\vx{n})$ is also cyclic,
   and can thus be expanded by \refthm{sqrfree} as
 \begin{equation}
-  \Lambda(\vxn{n}) \, C_p(\vxn{n}) = \sum_{q \in \Pset} T_{pq}(R) \, C_q(\vxn{n}),
+  \Lambda(\vx{n}) \, C_p(\vx{n}) = \sum_{q \in \Pset} T_{pq}(R) \, C_q(\vx{n}),
 \label{eq:xcp0}
@@
 By \refeq{der},
-  $\Lambda(\vxn{n})$ equals to $\lambda = +1$ or $-1$
-  at the onset or bifurcation point,
+  $\Lambda(\vx{n})$ equals to $\lambda = +1$ ($-1$)
+  at the onset (bifurcation) point,
   respectively;
@@
   becomes a homogeneous linear equation of
-  $C_p(\vxn{n})$:
-\begin{equation}
-  \lambda \, C_p(\vxn{n}) = \sum_{q \in \Pset} T_{pq}(R) \, C_q(\vxn{n}),
+  $C_p(\vx{n})$:
+\begin{equation}
+  \lambda \, C_p(\vx{n}) = \sum_{q \in \Pset} T_{pq}(R) \, C_q(\vx{n}),
 \label{eq:xcp}
@@
 \begin{equation}
-  \big[ \lambda \, \vct I - \vct T(R) \big] \, \vct C = 0,
+  \big[ \vct T(R) - \lambda \, \vct I \big] \, \vct C = 0,
 \tag{\ref{eq:xcp}$'$}
@@
 and
-$\vct C = \{C_p(\vxn{n})\}$ is an $\NB$-dimensional column vector.
+$\vct C = \{C_p(\vx{n})\}$ is an $\NB$-dimensional column vector.
 
@@
 \begin{equation}
-  A_n\Rlam \equiv \big| \lambda \, \vct I - \vct T(R) \big| = 0.
+  A_n\Rlam \equiv \big| \vct T(R) - \lambda \, \vct I \big| = 0.
 \label{eq:xr}
@@
 %
-Now $A_n\Rlam$, from expanding the determinant,
-  is a polynomial of $R$ and $\lambda$,
-  the equation is the desired answer to our problem.
+This determinant $A_n\Rlam$
+  is the desired polynomial of $R$ and $\lambda$.
 %
@@
   At the onset and bifurcation points,
-  the square-free cyclic polynomials $C_p(\vxn{n})$
-  of the cycle points $\vxn{n} = \{x_k\}$
+  the square-free cyclic polynomials $C_p(\vx{n})$
+  of the cycle points $\vx{n} = \{x_k\}$
   are linearly related as
-  $\lambda \, C_p(\vxn{n}) = \sum_{q \in \Pset} T_{pq}(R) \, C_q(\vxn{n})$,
+  $\lambda \, C_p(\vx{n}) = \sum_{q \in \Pset} T_{pq}(R) \, C_q(\vx{n})$,
   with $\lambda$ being $+1$ and $-1$, respectively,
@@
   from the square-free reduction of the cyclic polynomial
-  $C_p(\vxn{n}) \, \prod_k f'(x_k)$. %[\refeq{logder}].
+  $C_p(\vx{n}) \, \prod_k f'(x_k)$. %[\refeq{logder}].
   Thus, the fixed points of $f^n$
@@
   the characteristic equation
-  $\big| \lambda \, \vct I - \vct T(R) \big| = 0$.
+  $\big| \vct T(R) - \lambda \, \vct I \big| = 0$.
   \label{thm:main}
 \end{theorem}
-
-%\begin{remark}
-More generally, the algorithm can trace a contour of marginal stability of $R$
-  in the complex plane
-  for complex cycles of $\vxn{n}$
-  if $\lambda$ is set to $\exp(i\theta)$ with $\theta \in [0, 2\pi]$.
-  The region enclosed by the contour corresponds to
-    a bulb in the inverted Mandelbrot set
-  (the inversion $z_k = -x_k, c = -R$
-  reduces \refeq{logmaps} to the standard Mandelbrot form: $z_{k+1} = c + {z_k}^2$
-  \cite{mandelbrot}),
-  see ref. \cite{stephenson2, stephenson3}. % and \reffig{logbulb}.
-%\end{remark}
 
@@
 %
-It is still helpful to have a mathematical software
-  at hand to verify certain steps
-  (e.g., in computing the determinants and their factorization).
-
-For $n = 1$ (the fixed point), we have
-  $C_0 = 1$, $\Lambda = -2 \, C_1 = -2 \, x_1$, and
+%It is still helpful to have a mathematical software
+%  at hand to verify certain steps
+%  (e.g., in computing the determinants and their factorization).
+%
+%
+For $n = 1$, % (the fixed point),
+we have two square-free cyclic polynomials
+$\{C_0, C_1\} = \{1, x_1\}$.
+$\Lambda = -2 \, x_1$, and
 \[
@@
 \]
-With $\Lambda \rightarrow \lambda$,
-  the characteristic equation (\ref{eq:xr}) reads
+The characteristic equation (\ref{eq:xr}) reads
 \begin{equation}
@@
   %\end{array} \right|
-  = -4R - 2\lambda + \lambda^2
+  \equiv -4R - 2\lambda + \lambda^2
   = 0.
@@
 
-For $n = 2$, the square-free cyclic polynomials
-  are
-$C_0 = 1$,
-$C_1 = x_1 + x_2$
+For $n = 2$, we have %three square-free cyclic polynomials
+$\{C_0, C_1, C_{12}\}
+  = \{1,  x_1 + x_2, x_1 x_2 \}$
 and
-$C_{12} = x_1 x_2$,
-with $\Lambda = 4 \, x_1 x_2$.
+$\Lambda = 4 \, x_1 x_2$.
 So
@@
   = -8 \, R \, C_0 + 4 \, (R + 1) \, C_1$
-(by the example after \refthm{sqrfree}),
+by the example after \refthm{sqrfree},
 $\Lambda \, C_{12}
-  = 4 \, (R - x_2) (R - x_1)$,
-and
-\[
-\Lambda
-  \left( \begin{array}{c}
-  C_0 \\
-  C_1 \\
-  C_{12}
-  \end{array} \right)
- =
-  \left( \begin{array}{ccc}
-  0           & 0         & 4 \\
-  -8R         & 4(R+1)    & 0 \\
-  4R^2        & -4R       & 4
-  \end{array} \right)
-  \left( \begin{array}{c}
-  C_0 \\
-  C_1 \\
-  C_{12}
-  \end{array} \right).
-\]
-%
-%
-%
-The characteristic equation \refeq{xr} reads
+= 4 \, (R - x_2) (R - x_1) = 4 \, (R^2C_0-RC_1+C_{12})$,
+and \refeq{xr} reads
+%\[
+%\Lambda
+%  \left( \begin{array}{c}
+%  C_0 \\
+%  C_1 \\
+%  C_{12}
+%  \end{array} \right)
+% =
+%  \left( \begin{array}{ccc}
+%  0           & 0         & 4 \\
+%  -8R         & 4(R+1)    & 0 \\
+%  4R^2        & -4R       & 4
+%  \end{array} \right)
+%  \left( \begin{array}{c}
+%  C_0 \\
+%  C_1 \\
+%  C_{12}
+%  \end{array} \right).
+%\]
+%
+%
+%
+%The characteristic equation (\ref{eq:xr}) reads
 %
@@
 \begin{align}
-A_2 = (4R - 4 + \lambda) [(4 R-\lambda)^2 - 4 \lambda] = 0.
+A_2 \equiv (4 - 4R - \lambda) [(4 R-\lambda)^2 - 4 \lambda] = 0.
   \tag{\ref{eq:xr}-2}
@@
 %
-The first factor, denoted as $P_2\Rlam = 4R -r+\lambda$,
-  is responsible for the 2-cycle,
-  while the second factor is for the fixed points (cf. \refsec{primfac}).
-Setting the former to zero yields $R = 1 - \lambda/4$;
-so the onset ($\lambda = +1$) value is $R_a = 3/4$ ($r_a = 3$)
-and the bifurcation ($\lambda = -1$) value is $R_b = 5/4$ ($r_b = 1+\sqrt 6$).
+Only the first factor, denoted as $P_2\Rlam = 4-4R -\lambda$,
+  corresponds to the 2-cycle  (cf. \refsec{primfac}).
+%  while the second factor is from the fixed points 
+So $R = 1 - \lambda/4$,
+and the onset ($\lambda = +1$) value is $R_a = 3/4$ %($r_a = 3$)
+and the bifurcation ($\lambda = -1$) value is $R_b = 5/4$. %($r_b = 1+\sqrt 6$).
 %
@@
 %whose corresponding $r = 1+\sqrt{1+4R}$
-%is identical to that in ref. \cite{gordon, burm}.
+%is identical to that in \cite{gordon, burm}.
 %%
@@
 %
-we only list the final characteristic equation \eqref{eq:xr}:
+we only list the final \refeq{xr}: %characteristic equation (\ref{eq:xr}):
 %after the square-free reduction:
@@
 %\right | \nonumber  \\
-& =
+& \equiv
     \big[
@@
 %
-It can be factorized as
+At the onset point, % $\lambda = 1$.
+we have %it can be factorized as
 $ P_4(R, 1)
 = (
-    4R - 5
+    5 - 4R
   )
@@
 \, \big[
-  (4R - 3)^3 - 108
-  \big]$
-at the onset point. % $\lambda = 1$.
-%
-%
-%
-It has two real roots:
+  108 - (4R - 3)^3
+  \big]$,
+%
+%
+%
+with two real roots:
 $R_a' = 5/4$
-\big($r_a' = 1+\sqrt{6} \approx 3.4495$\big)
-for the cycle from period-doubling the 2-cycle
-  \big[compare \reffigs{cobweb}(b) and (d)\big],
+%\big($r_a' = 1+\sqrt{6} \approx 3.4495$\big)
+for the period-doubled 2-cycle,
+  %\big[compare \reffigs{cobweb}(b) and (d)\big],
 and
 $R_a = (3+\sqrt[3]{108})/4$
-\big($r_a = 1+\sqrt{4+\sqrt[3]{108}} \approx 3.9601$\big)
-for an original cycle \big[\reffig{cobweb}(e)\big].
+%\big($r_a = 1+\sqrt{4+\sqrt[3]{108}} \approx 3.9601$\big)
+for an original 4-cycle. %\big[\reffig{cobweb}(e)\big].
 %
@@
  = 4096 R^6 - 12288 R^5 + 12032 (R^4 - R^3)
-  + 8432 R^2 + 4913$
+  + 8432 R^2 + 4913$.
 %which upon $R \rightarrow r(r-2)/4$ yields the same polynomial
 %obtained previously
-\cite{stephenson1, stephenson3, bailey2, kk1, lewis}.
+%\cite{stephenson1, stephenson3, bailey2, kk1, lewis}.
 %
@@
 %
-we have $P_2 = A_2 / B_1^2 = 4R - 4 + \lambda$.
+we have $P_2 = A_2 / B_1^2 = 4 - 4R - \lambda$.
 %
@@
 %Thus,
-we can show that
 the last two factors of the polynomial in \refeq{xr4}
@@
 
-%It can be, however, problematic,
-%   if $P_n(R, \lambda)$ is solved for $\lambda = 1$
-%   instead of a general $\lambda$,
-%   for $P_n(R, 1)$ itself can be further factorized.
-%
-Due to the technical nature of the derivation and subsequent discussions,
+%\begin{remark}
+Since the above derivation works also for complex cycles,
+  each complex $R$ root of the polynomial $P_n\Rlam$ trace
+  the outline of a bulb in the inverted Mandelbrot set,
+  %(the inversion $z_k = -x_k, c = -R$
+  %reduces \refeq{logmaps} to the standard Mandelbrot form: $z_{k+1} = c + {z_k}^2$
+  %\cite{mandelbrot}),
+  as $\lambda=\exp(i\theta)$ goes around the unit circle,
+  cf. \cite{stephenson2, stephenson3}. % and \reffig{logbulb}.
+%\end{remark}
+%
+The proof of \refeq{primfac} and subsequent discussions
+  are somewhat technical, so
   the reader may wish to skip the rest of \refsec{logmap}
@@
 
-We now show \refeq{primfac} based on the fact that
+Below we show \refeq{primfac} based on the fact that
   each zero of the characteristic polynomial $A_n\lam$
@@
 %\begin{theorem}
-Next, the $n$-cycle polynomial $P_n\lam$ is defined as
-\begin{equation}
-  P_n\lam \equiv \textstyle\prod_l [\lambda - \Lambda(\vxn{n}^{(l)})],
+Next, we define the $n$-cycle polynomial as
+\begin{equation}
+  P_n\lam \equiv \textstyle\prod_l [
+    \Lambda(\vx{n}^{(l)}) - \lambda
+  ],
 \notag
 \end{equation}
-where $\vxn{n}^{(l)}$ denotes the $l$th $n$-cycle.
+where $\vx{n}^{(l)}$ denotes the $l$th $n$-cycle.
 %
@@
 %
-Incidentally, $\LB(n)$ is also the number of aperiodic necklaces of length $n$
-(e.g., for $n = 4$,
-  ``$0011$'' is aperiodic, but ``$0101$'' is not, owing to the shorter period 2).
-%
-An $n$-necklace is either aperiodic itself or
-  a repeat of an aperiodic $d$-necklace with $d|n$; so
+One can verify that
+%Incidentally, $\LB(n)$ is also the number of aperiodic necklaces of length $n$
+%(e.g., for $n = 4$,
+%  ``$0011$'' is aperiodic, but ``$0101$'' is not, owing to the shorter period 2).
+%%
+%An $n$-necklace is either aperiodic itself or
+%  a repeat of an aperiodic $d$-necklace with $d|n$; so
 \begin{equation}
@@
 %
-Further, as the leading coefficient of $A_n\lam$
-  is unity by \refeq{xr}, we must have
+Comparing the leading coefficient of $A_n\lam$ leads to
+%is unity by \refeq{xr}, we must have
 %\begin{theorem}
@@
 where $Q_d^{n/d}(\lambda) \equiv \prod_l
-  \big[\lambda - \Lambda\big(\vxn{n}^{(l)}\big) \big]$
-  with $\vxn{n}^{(l)}$ being the $n$ consecutive points
+  \big[\Lambda\big(\vx{n}^{(l)}\big) - \lambda\big]$
+  with $\vx{n}^{(l)}$ being the $n$ consecutive points
   in the $l$th $d$-cycle,
 %
-  or the $d$-cycle points $\vxn{d}^{(l)}$
+  or the $d$-cycle points $\vx{d}^{(l)}$
   repeated for $c = n/d$ times:
 \begin{equation}
-  \vxn{n}^{(l)}
+  \vx{n}^{(l)}
   =
-  \vxn{d}^{(l)} \times c
+  \vx{d}^{(l)} \times c
   =
@@
 It follows that
-$\Lambda(\vxn{n}) = [ \Lambda(\vxn{d}) ]^c$.
-%
-By factorizing $\lambda - \Lambda^c$
+$\Lambda(\vx{n}) = [ \Lambda(\vx{d}) ]^c$.
+%
+By factorizing $\Lambda^c - \lambda$
   in terms of the $c$ complex roots of $\lambda$,
@@
 %    \Big\{
-%      \lambda - \big[\Lambda\big(\vxn{d}^{(l)}\big) \big]^{c}
+%      \lambda - \big[\Lambda\big(\vx{d}^{(l)}\big) \big]^{c}
 %    \Big\}
@@
     \prod_l
-    \Big\{
+    \left\{
       \prod_{k=1}^c \,
-      \big[
+      \left[
+          \Lambda\big(\vx{d}^{(l)}\big)
+          -
           e^{2k\pi i/c} \lambda^{1/c}
-          - \Lambda\big(\vxn{d}^{(l)}\big)
-      \big]
-    \Big\}
+      \right]
+    \right\}
     \notag \\
-  &=  \prod_{k=1}^c P_d\big(e^{2k\pi i/c} \lambda^{1/c}\big),
+  &=  \prod_{k=1}^c P_d\big(e^{2k\pi i/c} \lambda^{1/c}\big).
 \label{eq:QP}
@@
 %
-where we have exchanged the order of the two products.
-%
-Despite the presence of the radical $\lambda^{1/c}$,
-  $Q_d^c\lam$ is still a polynomial of $\lambda$,
+%where we have exchanged the order of the two products in the second step.
+%
+The radical $\lambda^{1/c}$
+  does not prevent
+  $Q_d^c\lam$ from being a polynomial of $\lambda$,
   thanks to the invariance
@@
 
-\refeq{primfac} can now be derived from
-  \refeqs{prod} and (\ref{eq:QP}),
+Now, from \refeqs{prod} and (\ref{eq:QP}), we have
 %\begin{small}
@@
 = \textstyle\prod_{d|n}
-  \big[
+  \left[
     B_d^{m n/d}\lam
-  \big]^{\mu(n/d)}.
+  \right]^{\mu(n/d)}.
 \notag
@@
 With these contributions removed,
-  we obtain the polynomial $S_n(R)$ responsible for the original cycles:
-  %or the \emph{original factor} below,
+  we obtain the polynomial responsible for the original cycles:
   \begin{equation}
@@
 %=(-4R-2i-1)(-4R+2i-1)
-=16R^2+8R+5$
+=(4R+1)^2+4$
 (for $c = 4$),
-$P_2(R, -1) = 4R - 5$
-(for $c = 2$).
+$P_2(R, -1) = 5 - 4R$
+(for $c = 2$, the period-doubled 2-cycle).
 %
@@
 by the two factors yields
-$S_4(R) = (4R-3)^3 - 108$.
+$S_4(R) = 108-(4R-3)^3$.
 %  whose only real root $R_a=(3+\sqrt[3]{108})/4$ corresponds to
 %  the onset of the original cycle.
-Note that $P_2(R,-1)$ is excluded because it corresponds to the 4-cycle
-  born out of period-doubling the 2-cycle.
-The original and unoriginal 4-cycles are compared
-  in \reffigs{cobweb}(e) and (d).
+%Note that $P_2(R,-1)$ is excluded because it corresponds to the 4-cycle
+%  born out of period-doubling the 2-cycle.
+%The original and unoriginal 4-cycles are compared
+%  in \reffigs{cobweb}(e) and (d).
 
@@
 
-\subsection{\label{sec:degR}Degrees in $R$}
-
-In the numerical implementation
-  (cf. \refsec{end}),
-  the degrees in $R$ of the polynomials are needed
-  for evaluating the determinant by Lagrange interpolation.
-We first show that
-\begin{equation}
-\deg_R A_n\Rlam = \textstyle\sum_{d|n} \varphi(n/d) 2^{d-1},
-\label{eq:degRA}
-\end{equation}
-%
-The first few values are
-1, 3, 6, 12, 20, 42, 70, 144, 270, 540, \dots, from $n =1$.%1034, 2112, 4108, \dots,
-
-From \refeq{xr},
-  every term in the determinant $|\vct A|$
-  can be written as
-  $\prod_{p} A_{p,q}$,
-  in which, $p$ runs through all cyclic polynomials,
-  and $\{q = q(p)\}$ is a permutation of $\{p\}$.
-Thus, $\deg_R |\vct A|$ is
-  reached by the term that maximizes the product.
-Recall that $A_{p,q}$ results from reducing
-  $\Lambda(\vxn{n}) \, C_p(\vxn{n})$ to $C_q(\vxn{n})$
-  by a sequence of substitutions ${x_k}^2 = R-x_{k+1}$.
-It follows that to increase $\deg_R$ by 1,
-  $\deg_\vx$ is decreased by at least 2.
-Accordingly,
-  $\deg_R A_{p,q} \le \deg_\vx(\Lambda \, C_p) - \deg_\vx C_q$.
-Now running $p$ and $q$ through the $\NB$ cyclic polynomials
-  and using $\deg_\vx \Lambda(\vxn{n}) = n$
-  yields
-\[
-  \deg_R |\vct A | = \deg_R \textstyle\prod_{p} A_{p,q} \le n \, \NB(n).
-\]
-%
-The equality can be achieved, if each $q$ is the complement of $p$,
-  that is, if $C_p$ is generated from $\prod_k x_k^{e_k}$,
-  $C_q$ can be generated from $\prod_k x_k^{1-e_k}$.
-For example, for $n=4$,
-  $C_1 = x_1 + \cdots + x_4$
-  is the complement of
-  $C_{123} = x_2 x_3 x_4 + \cdots + x_1 x_2 x_3$,
-  while $C_{12}$ is its own complement.
-Finally, we reach \refeq{degRA} by \refeq{necklace}.
-
-Now, taking the degrees in $R$ of \refeq{primfac} and \refeq{origfac}
-  yields two known formulas
-\cite{mira, stephenson1, blackhurst}:
-%
-\begin{subequations}
-\begin{align*}
-\deg_R P_n\Rlam &\equiv \beta(n)
-  = \sum_{d|n} \mu\Big(\frac{n}{d}\Big) 2^{d-1}, \\
-\deg S_n(R) &= \beta(n)
-  - \sum_{d | n, d < n} \beta(d) \, \varphi\Big(\frac{n}{d}\Big).
-\end{align*}
-\label{eq:degR}
-\end{subequations}
-%
-The first few $\deg_R P_n\Rlam$ are
-  1, 1, 3, 6, 15, 27, 63, 120, 252, 495, \dots, %1023, 2010, 4095, \dots,
-and $\deg S_n(R) = $
-  1, 0, 1, 3, 11, 20, 57, 108, 240, 472, \dots, % 1013, 1959, 4083, \dots,
-from $n = 1$.
-
-\begin{table}[h]
-  %\small
-  \tbl{
-  Smallest positive $r$ at the onset and bifurcation points
-  of the $n$-cycles of the logistic map.
-  }
-{
-\begin{tabular}{llll}
-%\begin{tabularx}{\linewidth}{
-%  >{\hsize=0.5\hsize\centering\arraybackslash}X
-%  >{\hsize=1.6\hsize}X
-%  >{\hsize=1.6\hsize}X
-%  >{\hsize=0.3\hsize\raggedright\arraybackslash}X
+%\subsection{\label{sec:degR}Degrees in $R$}
+%
+%
+%
+%In the numerical implementation
+%  (cf. \refsec{end}),
+%  the degrees in $R$ of the polynomials are needed
+%  for evaluating the determinant by Lagrange interpolation.
+%We now show that
+%\begin{equation}
+%\deg_R A_n\Rlam = \textstyle\sum_{d|n} \varphi(n/d) 2^{d-1},
+%\label{eq:degRA}
+%\end{equation}
+%%
+%The first few values are
+%1, 3, 6, 12, 20, 42, 70, 144, 270, 540, \dots, from $n =1$.%1034, 2112, 4108, \dots,
+%
+%From \refeq{xr},
+%  every term in the determinant $|\vct A|$
+%  can be written as
+%  $\prod_{p} A_{p,q}$,
+%  in which, $p$ runs through all cyclic polynomials,
+%  and $\{q = q(p)\}$ is a permutation of $\{p\}$.
+%Thus, $\deg_R |\vct A|$ is
+%  reached by the term that maximizes the product.
+%Recall that $A_{p,q}$ results from reducing
+%  $\Lambda(\vx{n}) \, C_p(\vx{n})$ to $C_q(\vx{n})$
+%  by a sequence of substitutions ${x_k}^2 = R-x_{k+1}$.
+%It follows that to increase $\deg_R$ by 1,
+%  $\deg_x$ is decreased by at least 2.
+%Accordingly,
+%  $\deg_R A_{p,q} \le \deg_x(\Lambda \, C_p) - \deg_x C_q$.
+%Now running $p$ and $q$ through the $\NB$ cyclic polynomials
+%  and using $\deg_x \Lambda(\vx{n}) = n$
+%  yields
+%\[
+%  \deg_R |\vct A | = \deg_R \textstyle\prod_{p} A_{p,q} \le n \, \NB(n).
+%\]
+%%
+%The equality is achieved, if each $q$ is the complement $\bar p$ of $p$,
+%  that is, if $C_p$ is generated from $\prod_k x_k^{e_k}$,
+%  $C_{\bar p}$ can be generated from $\prod_k x_k^{1-e_k}$
+%%  (which may be the same polynomial as $C_p$).
+%For example, for $n=4$,
+%  $C_1 = x_1 + \cdots + x_4$
+%  is the complement of
+%  $C_{123} = x_2 x_3 x_4 + \cdots + x_1 x_2 x_3$,
+%  while $C_{12}$ is its own complement.
+%Finally, we reach \refeq{degRA} by \refeq{necklace}.
+%
+%
+%Now, taking the degrees in $R$ of \refeq{primfac} and \refeq{origfac}
+%  yields two known formulas
+%\cite{mira, stephenson1, blackhurst}:
+%%
+%\begin{subequations}
+%\begin{align*}
+%\deg_R P_n\Rlam &\equiv \beta(n)
+%  = \sum_{d|n} \mu\Big(\frac{n}{d}\Big) 2^{d-1}, \\
+%\deg S_n(R) &= \beta(n)
+%  - \sum_{d | n, d < n} \beta(d) \, \varphi\Big(\frac{n}{d}\Big).
+%\end{align*}
+%\label{eq:degR}
+%\end{subequations}
+%%
+%The first few $\deg_R P_n\Rlam$ are
+%  1, 1, 3, 6, 15, 27, 63, 120, 252, 495, \dots, %1023, 2010, 4095, \dots,
+%and $\deg S_n(R) = $
+%  1, 0, 1, 3, 11, 20, 57, 108, 240, 472, \dots, % 1013, 1959, 4083, \dots,
+%from $n = 1$.
+%
+
+%\begin{table}[h]
+%  %\small
+%  \tbl{
+%  Smallest positive $r$ at the onset and bifurcation points
+%  of the $n$-cycles of the logistic map.
+%  }
+%{
+%\begin{tabular}{llll}
+%%\begin{tabularx}{\linewidth}{
+%%  >{\hsize=0.5\hsize\centering\arraybackslash}X
+%%  >{\hsize=1.6\hsize}X
+%%  >{\hsize=1.6\hsize}X
+%%  >{\hsize=0.3\hsize\raggedright\arraybackslash}X
+%%}
+%\hline
+%  $n^\dagger$
+%& Onset$^\ddagger$
+%& Bifurcation$^\ddagger$
+%& \#$^*$ \\
+%\hline
+%$1$     & $1.0000000000_1$      &  $3.0000000000_1$       & 1   \\
+%$2'$    & $3.0000000000_1$      &  $3.4494897428_1$       & 1   \\
+%$3$     & $3.8284271247_1$      &  $3.8414990075_3$       & 1   \\
+%$4$     & $3.9601018827_3$      &  $3.9607686524_6$       & 1   \\
+%$4''$   & $3.4494897428_1$      &  $3.5440903596_6$       & 1   \\
+%$5$     & $3.7381723753_{11}$   &  $3.7411207566_{15}$    & 3   \\
+%$6$     & $3.6265531617_{20}$   &  $3.6303887000_{27}$    & 4   \\
+%$6'$    & $3.8414990075_{3}$    &  $3.8476106612_{27}$    & 1   \\
+%$7$     & $3.7016407642_{57}$   &  $3.7021549282_{63}$    & 9   \\
+%$8$     & $3.6621089132_{108}$  &  $3.6624407072_{120}$   & 14  \\
+%$8'$    & $3.9607686524_{6}$    &  $3.9610986335_{120}$   & 1   \\
+%$8'''$  & $3.5440903596_{6}$    &  $3.5644072661_{120}$   & 1   \\
+%$9$     & $3.6871968733_{240}$  &  $3.6872742105_{252}$   & 28  \\
+%$10$    & $3.6052080669_{472}$  &  $3.6059169323_{495}$   & 48  \\
+%$10'$   & $3.7411207566_{15}$   &  $3.7425706462_{495}$   & 3   \\
+%$11$    & $3.6817160194_{1013}$ &  $3.6817266457_{1023}$  & 93  \\
+%$12$    & $3.5820230011_{1959}$ &  $3.5828117795_{2010}$  & 165 \\
+%$12'$   & $3.6303887000_{27}$   &  $3.6321857392_{2010}$  & 4   \\
+%$12''$  & $3.8476106612_{27}$   &  $3.8490363152_{2010}$  & 1   \\
+%$13$    & $3.6797024578_{4083}$ &  $3.6797038498_{4095}$  & 315 \\
+%\hline
+%\multicolumn{4}{p{\linewidth}}{
+%$^\dagger$
+%  $\,'$, $\,''$, or $\,'''$ means
+%    that the cycle is undergoing
+%    the first, second, or third successive period-doubling, respectively.
+%} \\
+%\multicolumn{4}{p{\linewidth}}{
+%$^\ddagger$
+%  The subscripts are the degrees of the corresponding minimal polynomial
+%    of $R = r(r-2)/4$.
+%} \\
+%\multicolumn{4}{p{\linewidth}}{
+%$^*$
+%  The number of similar cycles.
+%} \\
+%\hline
+%%\end{tabularx}
+%\end{tabular}
+%\label{tab:rval}
 %}
-\hline
-  $n^\dagger$
-& Onset$^\ddagger$
-& Bifurcation$^\ddagger$
-& \#$^*$ \\
-\hline
-$1$     & $1.0000000000_1$      &  $3.0000000000_1$       & 1   \\
-$2'$    & $3.0000000000_1$      &  $3.4494897428_1$       & 1   \\
-$3$     & $3.8284271247_1$      &  $3.8414990075_3$       & 1   \\
-$4$     & $3.9601018827_3$      &  $3.9607686524_6$       & 1   \\
-$4''$   & $3.4494897428_1$      &  $3.5440903596_6$       & 1   \\
-$5$     & $3.7381723753_{11}$   &  $3.7411207566_{15}$    & 3   \\
-$6$     & $3.6265531617_{20}$   &  $3.6303887000_{27}$    & 4   \\
-$6'$    & $3.8414990075_{3}$    &  $3.8476106612_{27}$    & 1   \\
-$7$     & $3.7016407642_{57}$   &  $3.7021549282_{63}$    & 9   \\
-$8$     & $3.6621089132_{108}$  &  $3.6624407072_{120}$   & 14  \\
-$8'$    & $3.9607686524_{6}$    &  $3.9610986335_{120}$   & 1   \\
-$8'''$  & $3.5440903596_{6}$    &  $3.5644072661_{120}$   & 1   \\
-$9$     & $3.6871968733_{240}$  &  $3.6872742105_{252}$   & 28  \\
-$10$    & $3.6052080669_{472}$  &  $3.6059169323_{495}$   & 48  \\
-$10'$   & $3.7411207566_{15}$   &  $3.7425706462_{495}$   & 3   \\
-$11$    & $3.6817160194_{1013}$ &  $3.6817266457_{1023}$  & 93  \\
-$12$    & $3.5820230011_{1959}$ &  $3.5828117795_{2010}$  & 165 \\
-$12'$   & $3.6303887000_{27}$   &  $3.6321857392_{2010}$  & 4   \\
-$12''$  & $3.8476106612_{27}$   &  $3.8490363152_{2010}$  & 1   \\
-$13$    & $3.6797024578_{4083}$ &  $3.6797038498_{4095}$  & 315 \\
-\hline
-\multicolumn{4}{p{\linewidth}}{
-$^\dagger$
-  $\,'$, $\,''$, or $\,'''$ means
-    that the cycle is undergoing
-    the first, second, or third successive period-doubling, respectively.
-} \\
-\multicolumn{4}{p{\linewidth}}{
-$^\ddagger$
-  The subscripts are the degrees of the corresponding minimal polynomial
-    of $R = r(r-2)/4$.
-} \\
-\multicolumn{4}{p{\linewidth}}{
-$^*$
-  The number of similar cycles.
-} \\
-\hline
-%\end{tabularx}
-\end{tabular}
-\label{tab:rval}
-}
-\end{table}
+%\end{table}
 
@@
 %%
-%First, we list \refeqs{xcp}  with $\Lambda(\vx) = \prod_{k=1}^n f'(x_k)$.
+%First, we list \refeqs{xcp}  with $\Lambda(\vx{n}) = \prod_{k=1}^n f'(x_k)$.
 %This step populates elements of the matrix $\vct T$.
@@
 
-The most time-consuming step is the evaluation of the determinant
-in \refeq{xr}.
+The most time-consuming step of the algorithm
+is the evaluation of the determinant in \refeq{xr}.
 %
 When implemented on a computer,
-it is often helpful to evaluate the characteristic polynomial
+it is helpful to evaluate the characteristic polynomial
 by Lagrange interpolation:
-we evaluate $A_n\Rlam$ at a few different $R$,
+we evaluate $A_n\Rlam$ at a few $\deg_R A_n + 1$ values of $R$,
 e.g., $R = 0, \pm1, \pm2,\ldots$, then piece them together
 to a polynomial.
+%
+By using \refeq{primfac}, we only need $\deg_R P_n + 1$ values
+  to directly compute $P_n\Rlam$.
+%
+%
+Here,
+$\deg_R A_n = \sum_{d|n} \varphi(n/d) 2^{d-1}$,
+and $\deg_R P_n = \sum_{d|n} \mu(n/d) 2^{d-1}$
+  \cite{mira, stephenson1}.
+%
 The strategy also allows a trivial parallelization.
-%
-The algorithm was coded into a Mathematica program,
-which was used to compute the polynomials for $n$ up to 13.
+
+We coded the algorithm into a Mathematica program,
+and computed the polynomials for $n$ up to 13.
 %
@@
   [as $\deg_x f^n(x) = 2^n$],
-  while the matrix of the characteristic equation \refeq{xr}
+  while the matrix in \refeq{xr}
   is of only $\NB \approx 2^n/n$ [cf. \refeq{necklace}] rows and columns.
@@
 The exact polynomials of these maps are generally too large to print on paper,
-  e.g., the polynomial for the logistic map with $n = 13$
+  e.g., the bifurcation polynomial of the 13-cycle
     takes roughly seven megabytes to write down.
@@
 %
-The representative $r$ values are listed in \reftab{rval}.
+%The representative $r$ values are listed in \reftab{rval}.
 
@@
 
-A simple two-dimensional extension of the logistic map
-  is the H\'enon map \cite{henon}:
-\begin{equation}
-  x_{k+1} = 1 + y_k - a \, {x_k}^2, \quad
-  y_{k+1} = b \, x_k.
-\label{eq:henon}
-\end{equation}
+The H\'enon map \cite{henon}
+\begin{equation}
+  X_{k+1} = 1 + Y_k - a \, {X_k}^2, \quad
+  Y_{k+1} = b \, X_k,
+%\label{eq:henon}
+\notag
+\end{equation}
+is a two-dimensional extension of the logistic map.
 %
 By
-  $x_k^\mathrm{new} \equiv a \, x_k^\mathrm{old},
-   y_k^\mathrm{new} \equiv a \, y_k^\mathrm{old}$
+  $x_k \equiv a \, X_k,
+   y_k \equiv a \, Y_k$
 \cite{huang},
-we have, in terms of the new variables,
+we have
 \begin{equation}
@@
 %Since neither $a$ nor $b$ is changed during the transformation,
-\refeq{henon} and \refeq{henons} share the
-same onset and bifurcation points
-in terms of $a$ and $b$.
+%\refeq{henon} and \refeq{henons} share
+%the same onset and bifurcation points
+%in terms of $a$ and $b$.
 %
@@
 we recover the logistic map \refeq{logmaps}.
-
+%
+%
 The second equation of \refeq{henons}
@@
 \big|\, \lambda \, \vct I - \vct J_n(x_1) \,\big|
-= \lambda^2 - \Theta(\vxn{n}) \,\lambda +(-b)^n = 0,
+= \lambda^2 - \Theta(\vx{n}) \,\lambda +(-b)^n = 0,
 \notag
@@
 %
-where $\Theta(\vxn{n})$ and $(-b)^n$
+where $\Theta(\vx{n})$ and $(-b)^n$
   are the trace and determinant of $\vct J_n(x_1)$,
   respectively \cite{huang, hitzl}.
-The onset and bifurcation points
-  correspond to $\lambda = +1$ and $-1$, respectively
-
+%The onset and bifurcation points
+%  correspond to $\lambda = +1$ and $-1$, respectively.
+%
+%
 Using the matrix identity $\Tr( \vct A \vct B) = \Tr(\vct B \vct A)$,
@@
     $\Tr \, \vct J_n(x_1) = \cdots = \Tr \, \vct J_n(x_n)$,
-  i.e., $\Theta(\vxn{n})$ is a cyclic polynomial of
-  $\vxn{n} = \{x_1, \dots, x_n \}$.
-%e.g., %$\Theta(\vxn{n}) = 4 x_1 x_2 + 2 \, b$ for $n = 2$ and
-%$\Theta(\vxn{n}) = -8 x_1 x_2 x_3 - 2 \, b (x_1+ x_2+ x_3)$ for $n = 3$.
-%
-  Thus, we can expand $\Theta(\vxn{n}) \, C_p(\vxn{n})$
+  i.e., $\Theta(\vx{n})$ is a cyclic polynomial. % of $\vx{n} = \{x_1, \dots, x_n \}$.
+%e.g., %$\Theta(\vx{n}) = 4 x_1 x_2 + 2 \, b$ for $n = 2$ and
+%$\Theta(\vx{n}) = -8 x_1 x_2 x_3 - 2 \, b (x_1+ x_2+ x_3)$ for $n = 3$.
+%
+  Thus, we can expand $\Theta(\vx{n}) \, C_p(\vx{n})$
   in terms of square-free cyclic polynomials,
-  and then replace $\Theta(\vxn{n})$ by $\lambda + (-b)^n/\lambda$
-  in the final characteristic equation to obtain the desired polynomials
-  (the procedure is similar to that in \refsec{algo} for the logistic map).
-%
-%
-%
-The polynomials of $a$ and $b$
-  at the onset and bifurcation points for $n$ up to 9
-  are saved on the website in \refsec{end}.
+  and then replace $\lambda$ by $\lambda + (-b)^n/\lambda$
+  in \refeq{xr}
+  to obtain the desired polynomials of $a$ and $b$.
+%
+%
+%
+The boundary polynomials
+  for $n$ up to 9 are saved on the website in \refsec{end}.
 
@@
 
-As an example of a higher-order %one-dimensional
-map, we consider the following cubic map \cite{strogatz}
-%
-\begin{equation}
-  x_{k + 1} = f(x_k) = r \, x_k - {x_k}^3.
+Consider a cubic version of the logistic map \refeq{logmap}:
+\begin{equation}
+  z_{k+1} = r \, z_k \, (1 - {z_k}^2).
+  \notag
+\end{equation}
+%
+By the transformation $x_k = \sqrt{r} z_k$,
+%
+we obtain a variant
+\cite{strogatz}
+%
+\begin{equation}
+  x_{k + 1} = f_r(x_k) = r \, x_k - {x_k}^3,
 \label{eq:cubic}
@@
 %
-It is related to another cubic map
-  $y_{k+1} = a {y_k}^3 + (1-a) y_k$ \cite{may2, brown3, brown4}
-  by $y_k = x_k/\sqrt{r-1}, a = 1-r$.
+which is somewhat simpler for algebraic manipulation.
+%
+Although the boundary polynomials of the two maps are the same,
+  real $\vz{n}$ cycles at negative $r$
+  would be mapped to imaginary $\vx{n}$ cycles.
+%
+This artifact is ignored below.
+%
+%For $n>1$, half of the $L^*_e(n)$ cycles
+%  with negative $r$ are imaginary.
+%They can, however, be made real by
+%the transformed map
+%shares the same boundary polynomials of $r$ with \refeq{cubic}.
+%
+Another related cubic map
+  $q_{k+1} = a {q_k}^3 + (1-a) q_k$ \cite{may2, brown3, brown4}
+  can be obtained through $q_k = x_k/\sqrt{r-1}, a = 1-r$.
 
@@
   from the square-free ones to the cube-free ones,
-  in listing equations \eqref{eq:xcp},
-with the new $\Lambda(\vxn{n})$ being
-  $\prod_{k=1}^n f'(x_k) = \prod_{k=1}^n (r - 3 {x_k}^2)$.
+  in listing equations \eqref{eq:xcp}.
 For example,
@@
   is still not).
+The new $\Lambda_r(\vx{n})$ is
+  $\prod_{k=1}^n f'_r(x_k) = \prod_{k=1}^n (r - 3 {x_k}^2)$.
 %
@@
 %
-The representative $r$ values are listed in \reftab{crval}.
-%
-
-\begin{table}[h]%\footnotesize
-%\caption{
-\tbl{
-  Smallest positive $r$ at the onset and bifurcation points
-  of the $n$-cycles of the antisymmetric cubic map.
-  }
-%\begin{center}
-{
-\begin{tabular}{l l l l}
-%\begin{tabularx}{\textwidth}{
-%  >{\hsize=0.5\hsize\centering\arraybackslash}X
-%  >{\hsize=1.6\hsize}X
-%  >{\hsize=1.6\hsize}X
-%  >{\hsize=0.3\hsize\raggedright\arraybackslash}X
+%The representative $r$ values are listed in \reftab{crval}.
+%
+
+%\begin{table}[h]%\footnotesize
+%%\caption{
+%\tbl{
+%  Smallest positive $r$ at the onset and bifurcation points
+%  of the $n$-cycles of the antisymmetric cubic map.
+%  }
+%%\begin{center}
+%{
+%\begin{tabular}{l l l l}
+%%\begin{tabularx}{\textwidth}{
+%%  >{\hsize=0.5\hsize\centering\arraybackslash}X
+%%  >{\hsize=1.6\hsize}X
+%%  >{\hsize=1.6\hsize}X
+%%  >{\hsize=0.3\hsize\raggedright\arraybackslash}X
+%%}
+%%\begin{tabular*}{\textwidth}{l l l l c | c l l l l}
+%\hline
+%  $n^\dagger$
+%& Onset$^\ddagger$
+%& Bifurcation$^\ddagger$
+%& \#$^*$ \\
+%\hline
+%$1$     & $1.0000000000_1$      &  $2.0000000000_1$       & 2   \\
+%$2'$    & $2.0000000000_1$      &  $2.2360679775_2$       & 2   \\
+%$3$     & $2.4504409645_{8}$    &  $2.4608286739_{12}$    & 4   \\
+%$4$     & $2.5478350393_{22}$   &  $2.5488312193_{32}$    & 8   \\
+%$4''$   & $2.2360679775_{2}$    &  $2.2880317545_{32}$    & 2   \\
+%$5$     & $2.3939250274_{112}$  &  $2.3957922744_{120}$   & 24  \\
+%$6$     & $2.3334877526_{304}$  &  $2.3355337580_{336}$   & 56  \\
+%$6'$    & $2.4608286739_{12}$   &  $2.4657090579_{336}$   & 4   \\
+%$7$     & $2.3729872678_{1080}$ &  $2.3732727868_{1092}$  & 156 \\
+%$8$     & $2.3525990555_{3108}$ &  $2.3527637793_{3200}$  & 400 \\
+%$8'$    & $2.5488312193_{32}$   &  $2.5493247379_{3200}$  & 8   \\
+%$8'''$  & $2.2880317545_{32}$   &  $2.2992279397_{3200}$  & 2   \\
+%\hline
+%\multicolumn{4}{p{\linewidth}}{
+%$^\dagger$
+%  $\,'$, $\,''$, or $\,'''$ means that the cycle is undergoing
+%    the first, second, or third successive period-doubling, respectively.
+%} \\
+%\multicolumn{4}{p{\linewidth}}{
+%$^\ddagger$
+%  The subscripts are the degrees of the corresponding minimal polynomial.
+%} \\
+%\multicolumn{4}{p{\linewidth}}{
+%$^*$
+%  The number of similar cycles
+%    (for $n > 1$, only half of them have positive $r$).
+%} \\
+%\hline
+%\end{tabular}
+%%\end{tabularx}
+%%\end{tabular*}
+%%\end{center}
+%\label{tab:crval}
 %}
-%\begin{tabular*}{\textwidth}{l l l l c | c l l l l}
-\hline
-  $n^\dagger$
-& Onset$^\ddagger$
-& Bifurcation$^\ddagger$
-& \#$^*$ \\
-\hline
-$1$     & $1.0000000000_1$      &  $2.0000000000_1$       & 2   \\
-$2'$    & $2.0000000000_1$      &  $2.2360679775_2$       & 2   \\
-$3$     & $2.4504409645_{8}$    &  $2.4608286739_{12}$    & 4   \\
-$4$     & $2.5478350393_{22}$   &  $2.5488312193_{32}$    & 8   \\
-$4''$   & $2.2360679775_{2}$    &  $2.2880317545_{32}$    & 2   \\
-$5$     & $2.3939250274_{112}$  &  $2.3957922744_{120}$   & 24  \\
-$6$     & $2.3334877526_{304}$  &  $2.3355337580_{336}$   & 56  \\
-$6'$    & $2.4608286739_{12}$   &  $2.4657090579_{336}$   & 4   \\
-$7$     & $2.3729872678_{1080}$ &  $2.3732727868_{1092}$  & 156 \\
-$8$     & $2.3525990555_{3108}$ &  $2.3527637793_{3200}$  & 400 \\
-$8'$    & $2.5488312193_{32}$   &  $2.5493247379_{3200}$  & 8   \\
-$8'''$  & $2.2880317545_{32}$   &  $2.2992279397_{3200}$  & 2   \\
-\hline
-\multicolumn{4}{p{\linewidth}}{
-$^\dagger$
-  $\,'$, $\,''$, or $\,'''$ means that the cycle is undergoing
-    the first, second, or third successive period-doubling, respectively.
-} \\
-\multicolumn{4}{p{\linewidth}}{
-$^\ddagger$
-  The subscripts are the degrees of the corresponding minimal polynomial.
-} \\
-\multicolumn{4}{p{\linewidth}}{
-$^*$
-  The number of similar cycles
-    (for $n > 1$, only half of them have positive $r$).
-} \\
-\hline
-\end{tabular}
-%\end{tabularx}
-%\end{tabular*}
-%\end{center}
-\label{tab:crval}
-}
-\end{table}
+%\end{table}
 
@@
 The antisymmetry
-  $f(-x) = -f(x)$
+  $f_r(-x) = -f_r(x)$
 of the map, however, can help alleviate the burden.
@@
 First, we only need cyclic polynomials
-  of \emph{even} (or odd, see below for the difference) degrees in $\vxn{n}$.
+  of \emph{even} % (or odd, see below for the difference)
+  degrees in $\vx{n}$.
 %
 This is because \refeq{cubreplace} %contains only linear and cubic terms,
-never reduces a cyclic polynomial with an odd (even) degree in $\vxn{n}$
-to one with an even (odd) degree.
-%
-Thus, the matrix $\vct T$ in \refeq{xcp} can be split into two independent blocks
-  with two separate sets of eigenvalues.
-%
-
-%Similar to the logistic-map case,
-Even-degree cube-free cyclic polynomials
-correspond to \emph{even ternary} necklaces,
-in which each bead can assume
-0, 1, or 2, with the total being even.
-%
-The number of even ternary necklaces is
+never reduces even-degree cyclic polynomials
+to odd-degree ones,
+or the other way around.
+%
+But if performed on odd-degree cyclic polynomials,
+  the method would miss a few symmetric cycles (discussed later).
+%Thus, the matrix $\vct T$ in \refeq{xcp} can be split into two independent blocks
+%  with two separate sets of eigenvalues.
+%
+
+The number of even-degree cube-free cyclic polynomials
+is equal to that of \emph{even ternary} necklaces
+(each bead assumes 0, 1, or 2, with the total being even),
+which is given by
+%
 \begin{equation}
@@
 where
-$\odd(c) \equiv c \mod 2$.
-$N_e(n) =$ 2, 4, 6, 14, 26, 68, 158, 424, \dots, from $n = 1$.
-%\begin{theorem}
-%\label{thm:cubnecklace}
-%\end{theorem}
-%
-Since the number of all (even and odd) ternary necklaces is
-$N_3(n) = \frac{1}{n} \sum_{d|n} \varphi(n/d) 3^d \approx 2 N_e$,
+$\odd(c) \equiv c \bmod 2$.
+%$N_e(n) =$ 2, 4, 6, 14, 26, 68, 158, 424, \dots, from $n = 1$.
+%
+This is roughly half of the number of all (even and odd) ternary necklaces:
+$N_3(n) = \frac{1}{n} \sum_{d|n} \varphi(n/d) 3^d \approx 2 N_e$.
+%
+%
+Since $N_e(n)$ is the degree in $\lambda$ of $A_n\rlam$,
   half of the cyclic polynomials and their associated equations are spared.
 %
-%
-
-The characteristic polynomial $A_n\rlam$
-  from the determinant equation
-  has a degree $N_e(n)$ in $\lambda$,
-and it encompasses the factors
-  from the shorter $d$-cycles with $d|n$.
-The pure $n$-cycle polynomial $P_n\rlam$ can be obtained
-  from \refeq{primfac} with %proper substitutions
-  $R\rightarrow r$.
-%The degree of the polynomial,
-The degree in $\lambda$ of $P_n\rlam$
-is given by the M\"obius inversion
-$L_e(n) = \sum_{d|n} \mu(n/d) N_e(d)$,
-which becomes, after some algebra,
+The degree $L_e(n)$ of the $n$-cycle polynomial $P_n\rlam$
+  can be obtained from
+  $N_e(n) = \sum_{d|n} L_e(d)$,
+and
 %
@@
   L_e(n) = \delta_{n, 1} +
-    \frac{1}{n} \sum_{cd = n} \mu(c) \odd(c)\frac{3^d-1}{2}.
+    \frac{1}{n} \sum_{cd = n} \mu(c) \odd(c)\frac{3^d-1}{2},
 \notag
@@
 %
-%For the first few values,
-The first few values are 2, 2, 4, 10, 24, 60, 156, 410, \ldots, starting from $n = 1$.
-%
-This is also the number of the $n$-cycles \cite{zeng}.
-%
-The $\delta_{n,1}$ term corresponds to the trivial fixed point
-  at the origin,
-%
-%Excluding this term,
-and we can exclude it by a modification
-$L^*_e(n) \equiv L_e(n) - \delta_{n,1}$.
-For $n>1$, half of the cycles points $\vxn{n}$
-  with negative $r$ are imaginary.
-They can, however, be made real by
-$x_k = \sqrt{r} z_k$,
-in a transformed map
-$z_{k+1} = r \, z_k \, (1 - {z_k}^2)$,
-which share the same boundary polynomials of $r$.
-%
-%
-Following similar steps in \refsec{degR},
-we find
-  $\deg_r A_n(r, \lambda) = n N_e(n)$
-  and $\deg_r P_n(r, \lambda) = n L_e(n)$.
+%The first few values are 2, 2, 4, 10, 24, 60, 156, 410, \ldots, starting from $n = 1$.
+%
+which is also the number of the $n$-cycles \cite{zeng}.
+%
+To exclude the contribution from the trivial fixed point $x = 0$,
+we define
+  $P^*_n\rlam \equiv P_n\rlam/(r-\lambda)^{\delta_{n,1}}$
+and
+  $L^*_e(n) \equiv \deg_\lambda P^*_n\rlam = L_e(n) - \delta_{n,1}$.
+%
+%For $n>1$, half of the $L^*_e(n)$ cycles
+%  with negative $r$ are imaginary.
+%They can, however, be made real by
+%$x_k = \sqrt{r} z_k$;
+%the transformed map
+%$z_{k+1} = r \, z_k \, (1 - {z_k}^2)$
+%shares the same boundary polynomials of $r$ with \refeq{cubic}.
+%
+%
+The degrees in $r$ are
+  $\deg_r A_n\rlam = n N_e(n)$
+  and
+  $\deg_r P^{(*)}_n\rlam = n L^{(*)}_e(n)$.
 
@@
 %
-\begin{figure}[h]
-  \begin{center}
-  \begin{minipage}{\linewidth}
-        \includegraphics[angle=-90, width=\linewidth]{halfcycle.pdf}
-  \end{minipage}%
-  \end{center}
-  \caption{\label{fig:halfcycle}
-  Half-cycles of the cubic map.}
-\end{figure}
-%
-%
-
-Consider now a \emph{half-cycle},
-  which is a solution of $x_{n+1} = -x_1$,
-  see \reffig{halfcycle} for examples.
-%
-Once repeated, an $n$-half-cycle becomes a $2n$-cycle:
-  $x_1, \ldots, x_{n}, -x_1, \ldots, -x_{n}, x_1$,
-by the antisymmetry $f(-x) = -f(x)$ of the map.
-%
-In such a $2n$-cycle, a cyclic polynomial
-  formed by the $2n$ points
-  with an odd degree in $\vxn{2n}$
+%\begin{figure}[h]
+%  \begin{center}
+%  \begin{minipage}{\linewidth}
+%        \includegraphics[angle=-90, width=\linewidth]{halfcycle.pdf}
+%  \end{minipage}%
+%  \end{center}
+%  \caption{\label{fig:halfcycle}
+%  Half-cycles of the cubic map.}
+%\end{figure}
+%
+%
+
+We now define a \emph{half-cycle}
+  as a solution of $x_{n+1} = -x_1$,
+  %see \reffig{halfcycle} for examples.
+  and a polynomial $H^{*}_n\rlam$,
+  analogous to $P^*_n\rlam$,
+  for the nontrivial ($x \ne 0$) $n$-half-cycles.
+%
+The polynomials $H^*_n\rlam$ and $P^*_n\rlam$
+  share the same degree in $\lambda$.
+%
+Once iterated, an $n$-half-cycle turns into a symmetric $2n$-cycle:
+  $x_1, \ldots, x_{n}, -x_1, \ldots, -x_{n}, x_1$.
+%
+%Since a repeated $n$-half-cycle is a $2n$-cycle,
+Dividing the $2n$-cycle polynomial $P^{*}_{2n}(\lambda)$
+  (omitting $r$)
+  by
+  $H^{*}_{n}\big(\sqrt \lambda\big)
+   H^{*}_{n}\big(-\sqrt \lambda\big)$
+%
+yields an \emph{asymmetric} $n$-cycle polynomial:
+\begin{equation}
+\bar P^*_n\lam \equiv
+  %\left.
+  \frac{
+    P^*_n\lam
+  }
+  %\middle/
+  { \quad
+    \left[
+      H^*_{n/2}(\sqrt\lambda)
+      H^*_{n/2}(-\sqrt\lambda)
+    \right]^{\even(n)}
+  },
+  %\right.
+\notag
+%\label{eq:Pded}
+\end{equation}
+%
+where $\even(n)=1-\odd(n)$.
+%
+The $\bar P^*_n\rlam$ is
+  identical to the $n$-cycle polynomial
+  derived from \refeq{xr} using odd-degree cyclic polynomials.
+%
+This is because,
+  in a symmetric $2n$-cycle,
+  an odd-degree cyclic polynomial formed by the $2n$ points
   is always zero,
-  e.g., $C_1 = x_1 + x_2 + \dots + x_n - x_1 - x_2 - \dots - x_n = 0$.
-%
-Consequently, we would have missed the $n$-half-cycle contributions
-  in $A_{2n}\rlam$ and $P_{2n}\rlam$,
-  had the characteristic equation been listed using \emph{odd},
-  instead of even cyclic polynomials of $\vxn{n}$.
-%The existence of half-cycles is why we use even, but not odd,
-%  cyclic polynomials in the solution.
-
-Similar to the $n$-cycle polynomial $P_n\rlam$,
-  we can define a polynomial $P^h_n\rlam$
-  for the $n$-half-cycles.
-%
-The two share the same degree in $\lambda$.
-%
-We further define
-$P^{h*}_n\rlam = P^h_n\rlam/(\lambda - r)^{\delta_{n,1}}$
-  to exclude the contribution from the trivial solution $x=0$,
-  which is both a cycle and half-cycle.
-%
-Since a repeated $n$-half-cycle is a $2n$-cycle,
-  $P^{h*}_{n}\big(\sqrt \lambda\big)
-   P^{h*}_{n}\big(-\sqrt \lambda\big)$
-  is a factor of the $2n$-cycle polynomial $P_{2n}(\lambda)$
-  (omitting the argument $r$ here).
-%
-For example, by solving $- x_1 = f(x_1)$,
-  we obtain the nontrivial 1-half-cycle or the inversion point:
-  ${x_1}^2 = r + 1$,
-%Since $\lambda^h = r - 3 {x_1}^2$,
+  e.g., $C_1 = x_1 + \dots + x_n - x_1 - \dots - x_n = 0$.
+%
+The characteristic equation from the odd-degree cyclic polynomials
+  would accordingly miss the symmetric cycles.
+%
+The degree in $\lambda$ of $\bar P^*\lam$ is
+%
+\begin{align*}
+  L_o(n) &= %\delta_{n, 1} +
+      \frac{1}{n} \sum_{cd = n}
+    \mu(c) \left[1 - \tfrac{1}{2}\odd(c)\right] (3^d-1),
+\end{align*}
 and
-  $P^{h*}_1(\lambda) = \lambda + 2 r + 3$.
-%
-The 2-cycle polynomial
-  $P_2(\lambda) = -\big[(2r+3)^2 - \lambda\big]\,(\lambda + 2r^2-9)$
-  indeed contains
-  $P^{h*}_1(\sqrt \lambda) \, P^{h*}_1(r, -\sqrt \lambda)
-   =
-  \big( \sqrt \lambda + 2 r + 3\big)
-  \big(-\sqrt \lambda + 2 r + 3\big)$
-  as a factor.
-%
-%
-We may therefore define a deducted polynomial as
-\begin{equation}
-\bar P_n\lam \equiv
-  \left.
-    P_n\lam
-  \middle/
-     \left[
-        P^{h*}_{n/2}(\sqrt\lambda)
-        P^{h*}_{n/2}(-\sqrt\lambda)
-      \right],
-  \right.
-\label{eq:Pded}
-\end{equation}
-for an even $n$, and $\bar P_n = P_n$ for an odd $n$.
-%
-As discussed earlier,
-  $\bar P_n$ can also be obtained
-  from the characteristic equation
-  derived for odd cyclic polynomials of $\vxn{n}$;
-%
-and $\deg_\lambda \bar P\lam$ is
-\begin{align*}
-%  N_o(n) &= \frac{1}{n} \sum_{c d = n} \varphi(c)
-%      \odd(c) \frac{3^d-1}{2}, \\
-  L_o(n) &= \delta_{n, 1} +
-      \frac{1}{n} \sum_{cd = n}
-    \mu(c) \left[1 - \tfrac{1}{2}\odd(c)\right] (3^d-1).
-\end{align*}
-%
-%and $L^*_o(n) \equiv L_o(n) - \delta_{n,1}$
-%further excludes the fixed point at the origin.
-%
-%Additionally,
-It follows from \refeq{Pded} that
-$L_e(n) = L_o(n) + \even(n) L_e(n/2)$,
-where $\even(n) = 1 - \odd(n)$.
-
-Finally, we show that the computational cost
-  can be further cut by half for an even $n$.
-The $n$-half-cycle polynomial
-  are related to the $n$-cycle polynomial as
-  $P^h_n(r, \lambda) = P_n(-r, -\lambda)$
+$L^*_e(n) = L_o(n) + \even(n) L^*_e(n/2)$.
+
+Finally, we can further cut the computational cost
+  by half for an even $n$.
+%
+If a sequence $x_k$ satisfies \refeq{cubic},
+then $y_k \equiv (-)^k i x_k$
+satisfies $y_{k+1} = f_{-r}(y_k)$.
+%
+Thus, for an odd $n$, any $n$-cycle
+  $\vx{n} = \{x_1, x_2, \dots, x_n, x_1\}$
+  of $f_r$
+  can be mapped isomorphically to
+  an $n$-half-cycle
+  $\vy{n} = \{-i x_1, i x_2, \dots, - i x_n, i x_1\}$
+  of $f_{-r}$,
+  with $\Lambda_r(\vx{n}) = -\Lambda_{-r}(\vy{n})$.
+%
+So the $n$-half-cycle and $n$-cycle polynomials
+  are related by
+  $H_n(r, \lambda) = P_n(-r, -\lambda)$
   for an odd $n$.
 %
-This is because the transformed variables
-  $y_k \equiv (-)^k i x_k$
-satisfy
-  $y_{k+1} = (-r) \, y_k - {y_k}^3$.
-%
-Thus, any $n$-cycle
-  $\vxn{n} = \{x_1, x_2, \dots, x_n, x_1\}$
-can be mapped isomorphically (one-to-one) to an $n$-half-cycle
-$\vyn{n} = \{-i x_1, i x_2, \dots, - i x_n, i x_1\}$
-for the map with $-r$,
-  and $\Lambda(\vxn{n}) = -\Lambda(\vyn{n})$.
-%
-Further, for an even $n$, the same transformation
-  maps an $n$-(half-)cycle at $r$ to
-       an $n$-(half-)cycle at $-r$,
-       with $\Lambda(\vxn{n}) = \Lambda(\vyn{n})$.
-%
-It follows that $A_{2n}\rlam$, $P^h_{2n}\rlam$, $\bar P_{2n}\rlam$,
-  and $P_{4n}\rlam$, are all even polynomials of $r$.
+Similarly, if $n$ is even,
+  the $n$-half-cycles and asymmetric $n$-cycles of $f_r$
+  can be isomorphically mapped to the corresponding ones of $f_{-r}$,
+  with $\Lambda_r(\vx{n}) = \Lambda_{-r}(\vy{n})$.
+%
+So $H^*_{n}\rlam$,
+  $\bar P^*_{n}\rlam$,
+  and $A_{n}\rlam$
+  are all even polynomials of $r$
+\big[but $\deg_r P^*_{n}\rlam$ is even only if $4|n$,
+  because if $n/2$ is odd, a symmetric $n$-cycle
+  would be mapped to an $(n/2)$-cycle\big].
 %
@@
   in Lagrange interpolation.
+%
 
@@
   for helpful communications and suggestions.
-Computing time on the Shared University Grid at Rice,
+Computing time on the Shared University Grid at Rice University,
   funded by NSF under Grant EIA-0216467, is gratefully acknowledged.
@@
   ``The birth of period three,''
-  {\it Mathematics Magazine}
+  {\it Math. Mag.}
   \textbf{68},
@@
   ``The birth of period 3, revisited,''
-  {\it Mathematics Magazine}
+  {\it Math. Mag.}
   \textbf{69},
@@
   ``Period three trajectories of the logistic map,''
-  {\it Mathematics Magazine}
+  {\it Math. Mag.}
   \textbf{69},
@@
   ``Period-3 orbits via Sylvester's theorem and resultants,''
-  {\it Mathematics Magazine}
+  {\it Math. Mag.}
   \textbf{74},
@@
   ``Period three begins,''
-  {\it Mathematics Magazine}
+  {\it Math. Mag.}
   \textbf{83},
@@
   ``Parallel integer relation detection: techniques and applications,''
-  {\it Mathematics of Computation}
+  {\it Math. Comput.}
   \textbf{70},
@@
   ``Ten problems in experimental mathematics,''
-  {\it The American Mathematical Monthly}
+  {\it Am. Math. Mon.}
   \textbf{113},
@@
   and  the Bailey-Broadhurst conjectures,''
-  {\it International Journal of Bifurcation and Chaos}
+  {\it Int. J. Bifurcat. Chaos}
   \textbf{14},
@@
   ``Heuristics to accelerate the Dixon resultant,''
-  {\it Mathematics and Computers in Simulation}
+  {\it Math. Comput. Simulat.}
   \textbf{77},
@@
   the interval complete solution of the counting problem,''
-  {\it Annals of Combinatorics}
+  {\it Ann. Comb.}
   \textbf{4},
@@
   ``Counting stable cycles in unimodal iterations,''
-  {\it Physics Letters A}
+  {\it Phys. Lett. A}
   \textbf{131},
@@
   ``Polynomials of the bifurcation points of the logistic map,''
-  {\it International Journal of Bifurcation and Chaos}
+  {\it Int. J. Bifurcat. Chaos}
   \textbf{21},
@@
   ``A two-dimensional mapping with a strange attractor,''
-  {\it Communications in Mathematical Physics}
+  {\it Commun. Math. Phys.}
   \textbf{50},
@@
   Huang, Y.-N. [1985]
-  ``Determination of the stable periodic orbits for the Henon map by analytical method,''
+  ``Determination of the stable periodic orbits for the H\'enon map by analytical method,''
   {\it Chin. Phys. Lett.}
@@
   Zeng, W. [1985]
-  ``On the number of stable cycles in the cubic map''
+  ``On the number of stable cycles in the cubic map,''
   {\it Commun. Theor. Phys.}

### 2013-05-27 doc/pc.tex
pc-ijbc: remove figure and tables

@@
 At the intersection,
-  the shorter $d$-cycle is branched or ``bifurcated''
-  by $(n/d)$-fold to the $n$-cycle.
+  the shorter $d$-cycle undergoes
+  a $(n/d)$-tupling to become the $n$-cycle.
 %
@@
 
-We will show below that such branching can only happen
+We will show below that such tupling can only happen
   at the onset of the $n$-cycle, where $\lambda = 1$.
 %
-Further, with a real $R$, only a two-fold branching is possible,
-  but a complex $R$ allows higher-fold branchings.
+Further, with a real $R$, only a two-fold tupling is possible,
+  but a complex $R$ allows higher-fold tuplings.
 
@@
   Y. N. Huang
-  Determination of the stable periodic orbits for the Henon map by analytical method,
+  Determination of the stable periodic orbits for the H\'enon map by analytical method,
   \textit{Chin. Phys. Lett.}

### 2013-05-31 logperiod/logperiod.py
add cub2.ma for both half-cycles and cycles

@@ -31,7 +31,7 @@ class MainPage(webapp2.RequestHandler):
         </ul></div>''',
 
         'last_update':
-        '<p>Last updated on May 10th, 2013.',
+        '<p>Last updated on May 31th, 2013.',
     }
     self.response.write(template.render(template_values))
 

### 2013-05-31 doc/pc-ijbc.tex
add cub2.ma for both half-cycles and cycles
discussion on cub2 in pc-ijbc

@@
   connecting the cyclic polynomials of the cycle points.
-The polynomials satisfied by the critical parameters
-  of the logistic, H\'enon, and cubic maps are obtained
+The polynomials satisfied by the parameters
+  of the logistic, H\'enon, and cubic maps
+  at the onset and bifurcation points are obtained
   for $n$ up to 13, 9, and 8,
@@
 
-Since the $n$-cycles points constitute a subset of the fixed points of $f^n$,
+Since the $n$-cycles points constitute
+  a subset of the fixed points of $f^n$,
 we will first find
@@
 The polynomials contain
-  factors, contributed by short $d$-cycles with $d|n$
-  (which are also fixed points of $f^n$).
+  factors contributed by short $d$-cycles with $d|n$,
+  which are also fixed points of $f^n$.
 The factors are removed in \refsec{primfac}.
 
-At the first glance, the polynomials of the fixed points of $f^n$
+At first glance, the polynomials of the fixed points of $f^n$
   can be obtained by brute force.
@@
 The result would contain $R$ only,
-  and is therefore the answer.
+  and therefore be the answer.
 But since \refeqs{logmaps} are nonlinear,
@@
   we will derive a set of equations
-  in terms of the cyclic polynomials $\{C_p\}$ of $x_k$
-  (an example of a cyclic polynomial is
-  $x_1 x_2 + x_2 x_3 + \dots + x_n x_1$
-  with $n$ terms).
+  in terms of the cyclic polynomials $\{C_p\}$ of $x_k$.
+  %(an example of a cyclic polynomial is
+  %$x_1 x_2 + x_2 x_3 + \dots + x_n x_1$
+  %with $n$ terms).
 %
@@
   i.e., there is an equation
-  $\sum_q A_{pq} C_q = 0$ for every cyclic polynomial labeled by $p$.
-%
-Now the matrix formed by the coefficients $A_{pq}$
+  $\sum_q A_{pq} C_q = 0$ for every cyclic polynomial $C_p$.
+%
+The matrix formed by the coefficients $A_{pq}$
   must have a zero determinant,
@@
 %
-It may not, however, be symmetric
-  (invariant under the exchange of any two $x_i$ and $x_{j}$),
+But it may not be symmetric
+  (invariant under the exchange of any $x_i$ and $x_{j}$),
   e.g., $a$ and $b$ are not symmetric,
@@
 
-\subsection{\label{sec:algo}Fixed points of $f^n$}
+\subsection{\label{sec:algo}Characteristic equation}
 
@@
 By \refeq{der},
-  $\Lambda(\vx{n})$ equals to $\lambda = +1$ ($-1$)
+  $\Lambda(\vx{n})$ equals $\lambda = +1$ ($-1$)
   at the onset (bifurcation) point,
@@
 Since a set of homogeneous linear equations
-  has a nontrivial solution
-  ($C_p \ne 0$ for at least one $p$)
+  has a nonzero solution of $\vct C$
   only if the determinant of the coefficient matrix
@@
 
-The following discussion concerns the $\lambda$ dependence;
-  and we will drop the argument $R$ in $P_n\Rlam$, $A_n\Rlam$, etc.,
-  till the end of the next section.
 %\begin{remark}
@@
 Despite the radical argument $\lambda^{1/c}$,
-  the expanded product $\prod_{k=1}^c A_d(e^{2k\pi i/c} \lambda^{1/c})$
-  is free from radicals,
-  for it is invariant under $\lambda \rightarrow e^{2\pi i} \lambda$,
-  i.e., $B_d^c\lam$ is a polynomial of $\lambda$.
+  the product
+  $B_d^c\Rlam = \prod_{k=1}^c A_d(R, e^{2k\pi i/c} \lambda^{1/c})$
+  is a polynomial of $\lambda$,
+  for it is invariant under
+  $\lambda \rightarrow e^{2\pi i} \lambda$.
+For convenience, we will drop the $R$ in ``$\Rlam$'' below till the end the next section.
 Particularly, $B_n^1\lam = A_n\lam$.
@@
   $\varphi(3) = 2$ for 1 and 2 are coprime to 3,
-  $\varphi(6) = 2$ for 1 and 5.
+  $\varphi(6) = 2$ for 1 and 5 \cite{hardy}.
 %
@@
 It follows that
-$\Lambda(\vx{n}) = [ \Lambda(\vx{d}) ]^c$.
-%
-By factorizing $\Lambda^c - \lambda$
+$\Lambda(\vx{n}) = \left[ \Lambda(\vx{d}) \right]^c$.
+%
+By factoring $\Lambda^c - \lambda$
   in terms of the $c$ complex roots of $\lambda$,
@@
 The simplest example is the first bifurcation point
-  at $R = 3/4$ for $d = 1, n = 2$,
+  at $R = 3/4$ for $d = 1$ and $n = 2$,
   where the fixed point %\refeq{xr1}
@@
 Similar to \refeq{QP},
-  the contributions from the unoriginal cycles
-  born out of the $d$-cycles
-  can be arranged as a cyclotomic product
+  the unoriginal cycles
+  from the shorter $d$-cycles with $d|n$
+  contributes a cyclotomic product
   $\prod_{(k, c) = 1}
@@
           R, e^{2k\pi i/c}
-        \right)$,
+        \right)$ to $P_n(R, 1)$,
 where $k$ runs through integers from 1 to $c=n/d$
@@
     {
-      \prod_{c d =  n, \; c > 1}
+      \prod_{c d =  n, \; d < n}
       %\left[ \,
@@
 
-The most time-consuming step of the algorithm
-is the evaluation of the determinant in \refeq{xr}.
+The most time-consuming step of the algorithm in \refsec{algo}
+is the evaluation of the determinant $A_n\Rlam$ in the characteristic
+equation (\ref{eq:xr}).
 %
 When implemented on a computer,
-it is helpful to evaluate the characteristic polynomial
-by Lagrange interpolation:
-we evaluate $A_n\Rlam$ at a few $\deg_R A_n + 1$ values of $R$,
+it is helpful to use Lagrange interpolation:
+we evaluate $A_n\Rlam$ at $\deg_R A_n + 1$ values of $R$,
 e.g., $R = 0, \pm1, \pm2,\ldots$, then piece them together
@@
   e.g., the bifurcation polynomial of the 13-cycle
-    takes roughly seven megabytes to write down.
+    takes roughly seven megabytes.
 %
@@
   in terms of square-free cyclic polynomials,
-  and then replace $\lambda$ by $\lambda + (-b)^n/\lambda$
-  in \refeq{xr}
-  to obtain the desired polynomials of $a$ and $b$.
-%
-%
-%
-The boundary polynomials
+  and then replace the eigenvalue of the coefficient matrix
+  by $\lambda + (-b)^n/\lambda$
+  in the characteristic equation.
+%
+%
+%
+The onset ($\lambda = 1$) and bifurcation ($\lambda = -1$)
+  polynomials of $a$ and $b$
   for $n$ up to 9 are saved on the website in \refsec{end}.
@@
 %
-But if performed on odd-degree cyclic polynomials,
-  the method would miss a few symmetric cycles (discussed later).
+But if applied on odd-degree cyclic polynomials,
+  the algorithm would miss some symmetric cycles (see later).
 %Thus, the matrix $\vct T$ in \refeq{xcp} can be split into two independent blocks
@@
 \begin{equation}
-  N_e(n) = \frac{1}{n} \sum_{c d = n} \varphi(c)
-    \left[
-      3^d - \odd(c) \frac{3^d-1}{2}
-    \right],
+  N_e(n) = 1 +
+    \frac{1}{2n} \sum_{c d = n} \varphi(c)
+    \left[ 2 - \odd(c) \, \right]
+    (3^d-1),
 \notag
@@
   L_e(n) = \delta_{n, 1} +
-    \frac{1}{n} \sum_{cd = n} \mu(c) \odd(c)\frac{3^d-1}{2},
+    \frac{1}{2n} \sum_{cd = n} \mu(c) \odd(c) \, (3^d-1),
 \notag
@@
 
-We now define a \emph{half-cycle}
-  as a solution of $x_{n+1} = -x_1$,
+We call a solution of $x_{n+1} = -x_1$ a \emph{half-cycle}.
   %see \reffig{halfcycle} for examples.
-  and a polynomial $H^{*}_n\rlam$,
-  analogous to $P^*_n\rlam$,
-  for the nontrivial ($x \ne 0$) $n$-half-cycles.
-%
-The polynomials $H^*_n\rlam$ and $P^*_n\rlam$
-  share the same degree in $\lambda$.
+The $n$-half-cycle polynomial $H^{*}_n\rlam$
+  can be defined in analogous to $P^*_n\rlam$.
 %
@@
 %Since a repeated $n$-half-cycle is a $2n$-cycle,
-Dividing the $2n$-cycle polynomial $P^{*}_{2n}(\lambda)$
-  (omitting $r$)
+Dividing the $2n$-cycle polynomial
+  $P^{*}_{2n}(r, \lambda)$
   by
-  $H^{*}_{n}\big(\sqrt \lambda\big)
-   H^{*}_{n}\big(-\sqrt \lambda\big)$
+  $H^{*}_{n}\big(r, \sqrt \lambda\big)
+   H^{*}_{n}\big(r, -\sqrt \lambda\big)$
 %
@@
 \begin{equation}
-\bar P^*_n\lam \equiv
+\hat P^*_n\rlam \equiv
   %\left.
   \frac{
-    P^*_n\lam
+    P^*_n\rlam
   }
@@
     \left[
-      H^*_{n/2}(\sqrt\lambda)
-      H^*_{n/2}(-\sqrt\lambda)
+      H^*_{n/2}(r, \sqrt\lambda)
+      H^*_{n/2}(r, -\sqrt\lambda)
     \right]^{\even(n)}
@@
 where $\even(n)=1-\odd(n)$.
-%
-The $\bar P^*_n\rlam$ is
-  identical to the $n$-cycle polynomial
+
+Now consider a quadradtic transformation $u_k = {x_k}^2/r$,
+  which converts \refeq{cubic} to
+  $u_{k+1} = F(u_k) = r^2 u_k (1 - u_k)^2$,
+whose $n$-cycles encompass
+  both $n$-half-cycles and asymmetric $n$-cycles of \refeq{cubic}.
+%
+The nontrivial $n$-cycle polynomial of $F$,
+  which is an even polynomial of $r$,
+  is the product $\hat P^*_n\rlam H^*_n\rlam$.
+%
+From this, we can show that
+  $\deg_\lambda \hat P^*\rlam$ is
+%
+\begin{align*}
+  L_o(n) &= %\delta_{n, 1} +
+      \frac{1}{2n} \sum_{cd = n}
+    \mu(c) \left[2 - \odd(c)\right] (3^d-1),
+\end{align*}
+and $\deg_\lambda H^*_n\rlam = \deg_\lambda P^*_n\rlam = L^*_e(n)$.
+%with
+%$L^*_e(n) = L_o(n) + \even(n) L^*_e(n/2)$.
+%
+
+%
+The polynomial $\hat P^*_n\rlam$ is also
+  equivalent to the $n$-cycle polynomial
   derived from \refeq{xr} using odd-degree cyclic polynomials.
@@
   an odd-degree cyclic polynomial formed by the $2n$ points
-  is always zero,
-  e.g., $C_1 = x_1 + \dots + x_n - x_1 - \dots - x_n = 0$.
-%
-The characteristic equation from the odd-degree cyclic polynomials
-  would accordingly miss the symmetric cycles.
-%
-The degree in $\lambda$ of $\bar P^*\lam$ is
-%
-\begin{align*}
-  L_o(n) &= %\delta_{n, 1} +
-      \frac{1}{n} \sum_{cd = n}
-    \mu(c) \left[1 - \tfrac{1}{2}\odd(c)\right] (3^d-1),
-\end{align*}
-and
-$L^*_e(n) = L_o(n) + \even(n) L^*_e(n/2)$.
+  is always zero
+  (e.g., $C_1 = x_1 + \dots + x_n - x_1 - \dots - x_n = 0$),
+%
+and thus escapes the characteristic equation.
+%
+%
 
@@
   are related by
-  $H_n(r, \lambda) = P_n(-r, -\lambda)$
+  $H^*_n(r, \lambda) = P^*_n(-r, -\lambda)$
   for an odd $n$.
@@
 So $H^*_{n}\rlam$,
-  $\bar P^*_{n}\rlam$,
+  $\hat P^*_{n}\rlam$,
   and $A_{n}\rlam$

### 2013-05-31 doc/pc.tex
discussion on cub2 in pc-ijbc

@@
   connecting the cyclic polynomials of the cycle points.
-The minimal polynomials of the critical parameters
-  of the logistic, H\'enon, and cubic maps are obtained
+The polynomials satisfied by the parameters
+  of the logistic, H\'enon, and cubic maps
+  at the onset and bifurcation points are obtained
   for $n$ up to 13, 9, and 8,
@@
 %Let us consider the first step of finding the fixed points of $f^n$.
-At the first glance, the polynomials of the fixed points of $f^n$
+At first glance, the polynomials of the fixed points of $f^n$
   can be obtained by brute force.
@@
 
-\subsection{\label{sec:algo}Algorithm for locating fixed points of $f^n$}
+\subsection{\label{sec:algo}Characteristic equation}
 

### 2013-06-03 doc/pc-ijbc.tex
add lsfit.ma, T14 polynomials

@@
   at the onset and bifurcation points are obtained
-  for $n$ up to 13, 9, and 8,
+  for $n$ up to 14, 9, and 8,
   respectively.
@@
 or
-  (iii) a chaotic trajectory.
+  (iii) a chaotic or aperiodic trajectory.
       %e.g., \reffig{cobweb}(f).
@@
   this is equivalent to $|f'(x^*)| \le 1$
-  \cite{strogatz}.
+  \cite{strogatz, hao}.
 %
@@
   where $\frac {d} {dx} f^n(x_1)$ reaches $+1$ and $-1$,
-  respectively \cite{strogatz}.
+  respectively \cite{strogatz, hao}.
 %
@@
 %
-Our goal is thus to find the two polynomials for a given $n$.
-%
-The problem has been tackled by several previous studies
+Our aim is thus to find the two polynomials for a given $n$.
+%
+The problem has been tackled in previous studies
   \cite{brown1, brown2, stephenson1, stephenson2, stephenson3,
@@
 
-\subsection{Strategy}
+\subsection{Plan}
 
@@
 The polynomials contain
-  factors contributed by short $d$-cycles with $d|n$,
+  extraneous factors contributed by short $d$-cycles with $d|n$,
   which are also fixed points of $f^n$.
@@
   in terms of $R$,
-  and then plug the solution into \refeq{der}.
-The result would contain $R$ only,
-  and therefore be the answer.
+  and then plug the solution into \refeq{der}
+  to get a polynomial equation of $R$.
 But since \refeqs{logmaps} are nonlinear,
@@
 If $x_2, \dots, x_n$ are eliminated first,
-  there are only two equations left:
-  $f^n(x_1) = x_1$
+  there are only two polynomial equations left:
+  $f^n(x_1) - x_1 = 0$
   and
-  $\frac{d}{dx}f^n (x_1) = \pm 1$
+  $\frac{d}{dx}f^n (x_1) \mp 1 = 0$
   [\refeq{der}];
   the final elimination of $x_1$ can then be accomplished
-  by setting the resultant of the two equations
-  to zero \cite{burm},
-  leading to the desired polynomial equation of $R$.
+  by setting the resultant of the two polynomials
+  to zero \cite{burm}.
+  %leading to the desired polynomial equation of $R$.
 %
@@
 %
+{\small
 \begin{align}
-A_2 \equiv (4 - 4R - \lambda) [(4 R-\lambda)^2 - 4 \lambda] = 0.
+A_2\Rlam \equiv (4 - 4R - \lambda)
+  \left[
+    (4 R-\lambda)^2 - 4 \lambda
+  \right] = 0.
   \tag{\ref{eq:xr}-2}
@@
 \end{align}
+}
 %
@@
 %
-%\begin{small}
+\begin{small}
 \begin{align}
-A_4
+A_4\Rlam
 %& = \left|
@@
 & \equiv
-    \big[
+    \Big[
     4096 R^6-12288 R^5 +
-    256 (\lambda + 48) (R^4- R^3) \notag \\
-& \quad
-    -16 (\lambda + 32)(\lambda - 16) R^2
-      -(\lambda - 16)^3 \big] \notag \\
+    256 (\lambda + 48) (R^4 - R^3) \notag \\
+& -16 (\lambda + 32)(\lambda - 16) R^2
+      -(\lambda - 16)^3 \Big] \notag \\
 & \quad
@@
 \end{align}
-%\end{small}
+\end{small}
 %
@@
 
-\subsection{\label{sec:primfac}$n$-cycle polynomial}
+\subsection{\label{sec:primfac}Polynomials of $n$-cycles}
 
@@
   $B_d^c\Rlam \equiv \prod_{k=1}^c A_{d}(R, e^{2k\pi i/c} \lambda^{1/c})$,
+  particularly, $B_n^1\rlam = A_n\rlam$,
   and
@@
   $\lambda \rightarrow e^{2\pi i} \lambda$.
-For convenience, we will drop the $R$ in ``$\Rlam$'' below till the end the next section.
-Particularly, $B_n^1\lam = A_n\lam$.
-We also have $\deg_\lambda B_d^c\lam = \deg_\lambda A_d\lam$.
+Also, $\deg_\lambda B_d^c\rlam = \deg_\lambda A_d\rlam$.
+For convenience, we will drop the $R$ in ``$\Rlam$'' or the arguments entirely below
+  till the end the next section.
 %
@@
 %  the degrees in $R$ of the polynomials are needed
-%  for evaluating the determinant by Lagrange interpolation.
+%  for evaluating the determinant by polynomial interpolation.
 %We now show that
@@
 When implemented on a computer,
-it is helpful to use Lagrange interpolation:
+it is helpful to use polynomial interpolation:
 we evaluate $A_n\Rlam$ at $\deg_R A_n + 1$ values of $R$,
@@
 We coded the algorithm into a Mathematica program,
-and computed the polynomials for $n$ up to 13.
+and computed the polynomials for $n$ up to 14.
 %
@@
 The exact polynomials of these maps are generally too large to print on paper,
-  e.g., the bifurcation polynomial of the 13-cycle
-    takes roughly seven megabytes.
+  e.g., the bifurcation polynomial of the 14-cycle
+    takes about 27 megabytes.
 %
@@
 Once iterated, an $n$-half-cycle turns into a symmetric $2n$-cycle:
-  $x_1, \ldots, x_{n}, -x_1, \ldots, -x_{n}, x_1$.
+$x_1, \ldots, x_{n}, -x_1, \ldots, -x_{n}, x_1$ \cite{hao}.
 %
@@
 
-Finally, we can further cut the computational cost
+Finally, we can further reduce the computational cost
   by half for an even $n$.
@@
   at the positive half of $r$ values
-  in Lagrange interpolation.
+  in polynomial interpolation.
 %
@@
 
+\bibitem[Hao(1989)]{hao}
+  Hao, B.-L. [1989]
+  {\it Elementary Symbolic Dynamics and Chaos in  Dissipative Systems}
+  (World Scientific, Singapore).
+
 \bibitem[Brown(1981)]{brown1}
@@
 
-\bibitem[Hao(1989)]{hao}
-  Hao, B.-L. [1989]
-  {\it Elementary Symbolic Dynamics and Chaos in  Dissipative Systems}
-  (World Scientific, Singapore).
-
 \bibitem[Hao(2000)]{hao2}

### 2013-06-03 doc/pc.tex
add lsfit.ma, T14 polynomials

@@
 or
-  (iii) a chaotic trajectory,
+  (iii) a chaotic or aperiodic trajectory,
       e.g., \reffig{cobweb}(f).
@@
   a stable fixed point requires $|f'(x^*)| \le 1$
-  to reduce deviations in successive iterations \cite{strogatz}.
+  to reduce deviations in successive iterations \cite{strogatz, hao}.
 
@@
 
-\subsection{\label{sec:primfac}Minimal polynomial for the $n$-cycles}
+\subsection{\label{sec:primfac}Polynomials of $n$-cycles}
 
@@
 The M\"obius inversion yields $L(n) = (1/n) \sum_{d\,|\,n} \mu(n/d) 2^{\,d}$.
-This formula was known to several authors \cite{hao, lutzky}.
+This formula was known to several authors \cite{hao2, lutzky}.
 
@@
 
-\bibitem{strogatz}
-  S. H. Strogatz,
-  \textit{Nonlinear Dynamics and Chaos}
-  (Addison-Wesley. Reading, MA, 1994).
-
 \bibitem{may}
@@
   (1976).
+
+\bibitem{strogatz}
+  S. H. Strogatz,
+  \textit{Nonlinear Dynamics and Chaos}
+  (Addison-Wesley. Reading, MA, 1994).
+
+\bibitem{hao} B.-L. Hao,
+  \textit{Elementary Symbolic Dynamics and Chaos in  Dissipative Systems}
+  (World Scientific, Singapore, 1989).
 
@@
 
-\bibitem{hao} B.-L. Hao,
-  \textit{Elementary Symbolic Dynamics and Chaos in  Dissipative Systems}
-  (World Scientific, Singapore, 1989);
+\bibitem{hao2} B.-L. Hao,
   Number of periodic orbits in continuous maps of

### 2013-06-03 logperiod/logperiod.py

@@ -31,7 +31,7 @@ class MainPage(webapp2.RequestHandler):
         </ul></div>''',
 
         'last_update':
-        '<p>Last updated on May 31th, 2013.',
+        '<p>Last updated on June 3rd, 2013.',
     }
     self.response.write(template.render(template_values))
 

### 2013-06-03 prog/mkinterp.py

@@ -39,40 +39,6 @@ for i in range(n):
   #s[i][1] = re.sub(r"[\\\n]", "", s[i][1])
   s[i][1] = re.sub(r"\\\n", "", s[i][1])
 
-'''
-# add mirrors
-t = []
-for i in range(n):
-  id = s[i][0]
-  if id <= 0: continue
-  for j in range(i):
-    if s[j][0] == -id:
-      break
-  else:
-    print "adding ", -s[i][0]
-    t = [[-s[i][0], s[i][1]]] + t
-s = t + s
-str = ''.join(  [("{%s, %s}\n" % (l[0], l[1])) for l in s]  )
-open("xxx.txt", "w").write(str)
-'''
-
-
-'''
-# check parity
-for i in range(n):
-  id = s[i][0]
-  if id >= 0: break
-  for j in range(i+1, n):
-    if s[j][0] == -id:
-      break
-  else:
-    continue
-
-  if s[i][1] == s[j][1]:
-    pass #print "i %s, id %s checked" % (i, id)
-  else:
-    print "i %s, id %s bad" % (i, id)
-'''
 
 
 ls = "ls = {"
@@ -90,19 +56,31 @@ xsave = """
 
 # logistic map
 fit_log = """
-p = Numerator[Together[InterpolatingPolynomial[ls, R]/.{R->T/4}]];
+tm = Timing[
+    p = InterpolatingPolynomial[ls, T/4];
+    ][[1]];
+Print["interpolation: ", tm];
 xsave["fit.txt", p, False, True];
-Print["trying to factorize..."];
-Timing[p = Factor[p];][[1]];
+Print["trying to factor..."];
+tm = Timing[
+    p = Factor[p];
+    ][[1]];
+Print["factoring: ", tm];
 xsave["fit.txt", p, False, True];
 """
 
 # cubic map
 fit_cubic = """
-p = Numerator[Together[InterpolatingPolynomial[ls, r]]];
+tm = Timing[
+    p = Numerator[Together[InterpolatingPolynomial[ls, r]]];
+    ][[1]];
+Print["interpolation: ", tm];
 xsave["fit.txt", p, False, True];
 Print["trying to factorize..."];
-Timing[p = Factor[p];][[1]];
+tm = Timing[
+    p = Factor[p];
+    ][[1]];
+Print["factoring: ", tm];
 xsave["fit.txt", p, False, True];
 """
 
[…]

### 2013-06-03 prog/mknsolv.py

@@ -317,7 +317,8 @@ elif fninp.startswith("T"):
   print "write %s for logistic map" % fnout
   src = src_log
 else:
-  print "bad input file: ", fninp
+  print "unrecognized input file %s, assume logistic map, output %s " % (fninp, fnout)
+  src = src_log
 
 src = codevars + xsave + nsolve + seqload + src
 open(fnout, "w").write(src)

### 2013-06-04 prog/etc/trimnsolv.py
modify mknsolv.py

@@ -1,16 +1,20 @@
 #!/usr/bin/env python
 
+''' trim the output `nsolv.txt' of mknsolv.py '''
+
 import re, sys, os
 
 
-fnin = "inp.txt"
+fnin = "nsolv.txt"
 if len(sys.argv) >= 2:
   fnin = sys.argv[1]
 
 sa = open(fnin).read().strip()
+# indented lines are attached to the previous ones
 sa = re.sub(r"\n ", " ", sa)
 sa = sa.split('\n')
 ls = []
+
 for k in range(len(sa)):
   s = sa[k].strip("{}() ")
   s = re.sub(r"\(", ",", s)
@@ -21,9 +25,9 @@ for k in range(len(sa)):
     ls = ls + [item]
     id = int(s[0].strip())
     if len(ls) != id:
-      print "Index mismatch: %s vs %s" % (id, len(ls))
+      sys.stderr.write( "Warning: index mismatch: %s vs %s\n" % (id, len(ls)) )
   except:
-    print "error occured %s" % s
+    sys.stderr.write( "error occured %s\n" % s )
     raise Exception
 s = "{" + ',\n'.join(ls) + "}"
 print s

### 2013-06-04 prog/mknsolv.py

@@ -1,84 +1,166 @@
 #!/usr/bin/env python
 
-''' make a mathematica script for numeric solutions of the logistic and cubic maps
-
-      mknsolv.py file [prec] [wprec] [fnbra] [kmin] [kmax] [tmfindroot] [tmfactor]
-
-    where
-      prec is the target precision
-      wprec is the working precision
-      fnbra is a saved brackets file for the locations of roots
-      kmin is the smallest root index
-      kmax is the largest root index (inclusive)
-      tmfindroot is the maximal time for time out
-      tmfactor is the maximal time to try to factor
-    the output is nsolv.ma, to run it type
-
+''' write a Mathematica script for numeric solutions of the logistic and cubic maps,
+    Cheng Zhang Copyright (c) 2012-2013
+    Quick usage example:
+    Type
+      mknsolv.py T14a.txt
+    then
       math < nsolv.ma
+    Type `mknsolve.py -h' for details '''
 
-    which writes nsolv.txt and possibly solvT.txt
-    for harder problem the onset
-      mknsolv.py T11a.txt 20 1000 fnbra
-      math < nsolv.ma
-'''
-import os, sys, re
+import os, sys, re, getopt
 
-if len(sys.argv) <= 1:
-  print "require an argument"
+fninp = None  # input polynomial equation
+fnout = "nsolv.ma" # output: Mathematica script
+fnres = "nsolv.txt" # root file, output of the Mathematica script
+fnresT = "solvT.txt" # special root file for the logistic map
+                     # output of the Mathematica script
+fneq = "eq.txt" # temporary one-line equation for fast loading
+fnbra = "intv.txt" # root brackets
+
+prec = 21
+wprec = None # WorkingPrecision for FindRoot[]
+kmin = kmax = None  # starting and ending root index
+tmroot = 1000  # this is based on T14a/b.txt data
+               # roughly the time needed for bsolv[] to get a root
+               # FindRoot[] usually takes 200~300s (wprec = 8000)
+nwarmup = 0 # number of steps for refining brackets before calling FindRoot[]
+            # the warm-up step computes the derivative, so it can be expensive
+verbose = False
[…]

### 2013-06-05 doc/pc-ijbc.tex
modify mknsolv.py
add bmp.ma, bmp.c and bmp.py

@@
 %\begin{multicols}{2}
-\twocolumn
+%\twocolumn
 
@@
 %$13$    & $3.6797024578_{4083}$ &  $3.6797038498_{4095}$  & 315 \\
+%$14$    & $3.5972109838_{8052}$ &  $3.5973201609_{8127}$  & 576 \\
+%$14'$   & $3.7021549282_{63}$   &  $3.7024116236_{8127}$  & 9   \\
 %\hline
@@
 
+\begin{figure}[h]
+  \begin{center}
+  \begin{minipage}{\linewidth}
+        \includegraphics[width=\linewidth]{T14b.png}
+  \end{minipage}%
+  \end{center}
+  \caption{\label{fig:T14b}
+  Coefficients of the 14-cycle bifurcation polynomial in two columns (left to right).
+  The $k$th line from the top is the coefficient before $(4R)^k$ in base-256.
+  The digits are shown by the grayscale from white (0) to black (255).
+  The leading bar before each line is the sign (black: $-$, white: $+$).
+  }
+\end{figure}
+
 We coded the algorithm into a Mathematica program,
-and computed the polynomials for $n$ up to 14.
+  and computed the polynomials for $n$ up to 14
+  (data on the website http://logperiod.appspot.com).
+%
+The bifurcation polynomial of the 14-cycle in shown in \reffig{T14b}.
+%
+%The exact polynomials of these maps are generally too large to print on paper,
+%  e.g., the bifurcation polynomial of the 14-cycle
+%    takes about 27 megabytes.
+%
+%The representative $r$ values are listed in \reftab{rval}.
+
+%Compared with other approaches \cite{hitzl, gordon, bailey2, kk1, hao, hao2}
+%it appeared to be simpler and more transparent,
+%as it only requires the computation of a determinant.
 %
@@
 %
-
-%
-The exact polynomials of these maps are generally too large to print on paper,
-  e.g., the bifurcation polynomial of the 14-cycle
-    takes about 27 megabytes.
-%
-The polynomials and programs are saved on the website
-http://logperiod.appspot.com.
-%
-%The representative $r$ values are listed in \reftab{rval}.
-
-%Compared with other approaches \cite{hitzl, gordon, bailey2, kk1, hao, hao2}
-%it appeared to be simpler and more transparent,
-%as it only requires the computation of a determinant.
 

### 2013-06-05 prog/etc/bmp.c

@@ -1,0 +1,286 @@
+/* write a grayscale bitmap:  ./bmp input output */
+#include <stdio.h>
+#include <stdlib.h>
+#include <string.h>
+
+typedef unsigned char  BYTE;  /* one byte (0-255) */
+typedef unsigned short WORD;  /* two bytes */
+typedef unsigned int   DWORD; /* four bytes */
+
+/* Bitmap format cf.
+ * http://en.wikipedia.org/wiki/BMP_file_format
+ * http://upload.wikimedia.org/wikipedia/commons/c/c4/BMPfileFormat.png
+ * http://www.fileformat.info/format/bmp/egff.htm */
+
+typedef struct {
+/* BYTE type[2]; */       /* = "BM", it is manipulated separately to make
+                             the size of this structure a multiple of 4 */
+  DWORD sizeFile;         /* = total file size == offset + bitmap-size */
+  DWORD reserved;         /* == 0 */
+  DWORD offset;           /* offset from start of file == sizeof(BitmapHeader) with "BM"
+                             + sizeof(DIBHeader) + size of palette */
+} BitmapHeader;
+
+typedef struct {
+  DWORD sizeStruct;       /* sizeof(DIBHeader) */
+  DWORD width, height;
+  WORD  planes;           /* 1 */
+  WORD  bitCount;         /* bits of each pixel, 8 for 256-color, 24 for RGB true color */
+  DWORD compression;      /* 0 */
+  DWORD sizeImage;        /* (width+?)(till multiple of 4) * height in bytes */
+  DWORD xPixelsPerMeter;  /* resolution in mspaint, 2952 */
+  DWORD yPixelsPerMeter;  /* resolution in mspaint, 2952 */
+  DWORD colorUsed;        /* 256 for 256-color, 0 for true color */
+  DWORD colorImportant;   /* 256 for 256-color, 0 for true color */
+#if 0
+  DWORD maskRed;          /* 0x00ff0000 */
+  DWORD maskGreen;        /* 0x0000ff00 */
+  DWORD maskBlue;         /* 0x000000ff */
+  DWORD maskAlpha;        /* 0xff000000 */
[…]

### 2013-06-05 prog/etc/bmp.py

@@ -1,0 +1,32 @@
+#!/usr/bin/env python
+
+''' script of calling bmp.ma and bmp.c '''
+
+import os, sys, subprocess
+
+
+def run(cmd):
+  sp = subprocess.Popen(["/bin/bash",  "-i", "-c", cmd])
+  sp.communicate()
+
+
+mathcode = "bmp.ma"
+if not os.path.exists(mathcode): raise Exception
+
+ccode = "bmp.c"
+exeprog = "bmp.exe"
+if not os.path.exists(exeprog):
+  if not os.path.exists(ccode): raise Exception
+  os.system("cc -O3 %s -o %s" % (ccode, exeprog))
+
+for i in range(1, 15):
+  for c in ("a", "b"):
+    fnT = "T%s%s.txt" % (i, c)
+    fnbit = "bit%s%s.txt" % (i, c)
+    fnbmp = "T%s%s.bmp" % (i, c)
+    fnpng = "T%s%s.png" % (i, c)
+    print fnT, fnbit, fnbmp, fnpng
+    if not os.path.exists(fnbit):
+      run( "math < %s %s %s" % (mathcode, fnT, fnbit) )
+    os.system("./%s %s %s" % (exeprog, fnbit, fnbmp))
+    os.system("convert -compress Lossless %s %s" % (fnbmp, fnpng) )

### 2013-06-06 doc/ijbc/response.txt
add response.txt

Dear Editor,

Thank you and the referees for extremely helpful suggestions and 
comments.  I have carefully modified the manuscript according to your 
suggestions and the referee reports. Below are the responses to the 
points raised by the referees. Additionally, the cycle polynomials 
for the logistic map have been computed for n = 14.

Regards,
Cheng

Response to Reviewer 1

Reviewer #1: There are several methods to compute these polynomials 
already in the literature: Kotsireas and Karamanos's Groebner base 
approach, Burm and Fishback's resultant approach, and Blackhurst's 
rational canonical matrix approach. (Bailey and Broadhurst's 
integer-relation detection approach could also be included, but their 
motivation was more to push the limits of their algorithm and less to 
shed light on chaos theory.) Adding one more method to these other 
methods doesn't hurt, but it's not really clear from the paper what 
this new approach contributes beyond Burm and Fishback's or 
Blackhurst's methods. Section 5 has a comparison between this new 
method and Kotsireas and Karamanos's approach, which is good, but the 
comparison could be improved. Instead of listing run times---which can 
be affected by such things as the hardware specifications, the 
algorithm being used (e.g, Buchburger's versus Faguere's F4 alorithm), 
and implementation details---it would be better to
give computational complexities. Since Groebner base algorithms are 
doubly exponential in the number of variables, it's not surprising this 
new method performs better. But how does it compare to Burm and 
Fishback's and Blackhurst's methods? What are the computational 
complexities of those methods and this new method? One advantage of 
Burm and Fishback's method, complexity issues aside, is the ease of 
programming: most computer algebra system have built-in commands to 
iterate functions and take resultants, but not to calculate cyclic 
polynomials. Does this new method also have reasons, beyond complexity 
issues, to prefer it over other methods?  In summary, section 5 needs 
to be expanded to more fully compare and contrast this new method with 
previous methods. At the very least, the computational complexities for 
this new method, Kotsireas and Karamanos's approach, Burm and 
Fishback's approach, and Blackurst's approach should be given.

Response:  First, I have implemented both the Grobner basis approach by 
Kotsireas and Karamanos and the resultant approach by Burm and Fishback 
using both Magma and Mathematica.  The results of two competing methods 
are compared with the current method in the new Fig. 1 of the current 
manuscript.  Clearly, for n >= 8, the present method are two orders of 
magnitudes more efficient than the competitors.  Further, Magma is 
known to be more optimized than Mathematica, and it is especially 
famous for its fast Grobner basis routine.  This is supported by Fig. 
1, the Grobner bases and resultants took much less time to compute 
using Magma.  Even so, our method, only implemented in a high-level 
language Mathematica, is still much faster.  This demonstrate the 
practical efficiency of the method.  Below I will further discuss that 
the underlying reason for the performance gain is linked to the use of 
the cyclic structure of the equations.

Secondly,  the current method is expected to outperform the resultant 
method.  The resultant of two polynomials is defined as the determinant 
of the Sylvester matrix of the two polynomials.  The side of the 
Sylvester matrix, which is square, is equal to the sum of the degrees 
of the two polynomials.  In this case,  the two polynomials are 
	f^n(x) – x,
and
            (f^n)'(x) -/+ 1.
It is easy to see that the matrix roughly has N = 2^(n+1) rows/columns. 
 Now the key step of our method is also the computation of a 
determinant, but it is the one from the characteristic equation.  Now 
our matrix only has roughly N = 2^n/n rows/columns.  So, even without 
specifying the underlying algorithm of computing the determinant, we 
expect the current method to outperform the resultant method.  This 
point is now added in Section 2.9 in the revised manuscript.  If we 
assume the Bareiss algorithm for the determinant, then the run time 
goes as N^3 ~ N^4, or 8^n ~ 16^n.  This estimate agrees with the 
results shown in Fig. 1.  However, the underlying routine of computing 
the determinant used by Mathematica or Magma may differ greatly in 
algorithm and implementation, therefore the specific algorithms are not 
discussed in the manuscript for brevity.  In short, the underlying 
reason for the performance gain is that the current algorithm exploits 
the cyclic structures of the equations, which greatly reduces the 
matrix size.

Thirdly, the Grobner basis method is expected to perform similarly to 
the resultant method.  This is supported by Fig. 1.  Conceptually, the 
resultant step can be considered as the construction of the final basic 
polynomial between x1 and R, after other x2, x3, ..., xn are 
eliminated.  The conceptual relation is briefly discussed in Section 
2.1 in the revised manuscript.  For this problem, the computational 
times of both methods grow exponentially with n, which is fortuitous, 
as it is expected to have worse scaling for a general problem of n 
variables as suggested by the referee.

On the other hand, Blackhurst's method, according to my understanding 
of the cited reference, is not an independent method that computes the 
cycle polynomials.  Instead, it is a formula that computes the *smaller 
factors* of the onset polynomial of the n-cycles.  So it needs another 
method to first compute the onset polynomial of n-cycles itself.  At 
the onset point, the polynomial of n-cycles can be factorized due to 
the intersection between the n-cycles and the shorter d-cycles (as 
discussed in the Section 2.8 of the current version). These 
intersections contribute smaller factors to the n-cycle polynomial.  
For example, in case of n = 4, the onset polynomial is
	P4(onset)  =  (5-4R) [(4R+1)^2 + 4] [108 – (4R-3)^3],
and the smaller factors are 5-4R (from the 2-cycles that are about to 
double their period) and (4R+1)^2 + 4 (from 1-cycles).  In the cited 
reference, Blackhurst showed a formula of finding the smaller factors 
in terms of canonical matrices.  The formula requires one to 
numerically compute the cycle points explicitly.  Alternatively, we 
show here that the factors can be compactly expressed as a cyclotomic 
product in the denominator of Eq. (13) of the current manuscript.  The 
latter approach is easier to use for it does not require the explicit 
computation of the cycle points at different R values (or the \lambda 
values in Blackhurst's paper) .  The relation between the two formulas 
are now pointed out in this version.  It is my understanding that 
Blackhurst's canonical-matrix formula requires *a priori* the d-cycle 
and n-cycle polynomials as well as the cycle points, which can be very 
difficult to obtain for a large n.  There may be, however, some 
unpublished ongoing work that I am not aware of.  If this is so, I am 
happy to add a reference.

Response to Reviewer 2

Reviewer #2: The paper is well written. However, the length could be 
greatly reduced. Most figures and tables are not so informative, so can 
be removed. Some examples can also be deleted. Derivations related to 
cycle counting seem not new, so the author may just give the results 
with some brief description and relevant references.

Response:  I have removed all previous figures and tables, minimized 
the derivations on the cycle counting, and simplified the examples.  
The overall length has been cut over a half, and the article looks more 
compact now.  Thank you for the suggestions.

### 2013-06-06 doc/pc-ijbc.tex
add response.txt

--- 2013-06-03 doc/pc-ijbc.tex
@@
 we will first find
-  the polynomials at the stability boundaries
+  the polynomials of marginal stability
   for the fixed points of $f^n$
@@
   the $\NB$ square-free cyclic polynomials $C_p$ are themselves
-  linearly connected by \refeq{der}.
-This condition yields a characteristic equation,
-  which solves our problem.
+  linearly connected by a characteristic equation.
 
@@
 where
-  $B_d^c\Rlam \equiv \prod_{k=1}^c A_{d}(R, e^{2k\pi i/c} \lambda^{1/c})$,
-  particularly, $B_n^1\rlam = A_n\rlam$,
-  and
-  $\lambda^{1/c}$ is a complex $c$th root of $\lambda$;
-  the outer product runs over all divisors $d$ of $n$.
+  $B_d^c\Rlam \equiv \prod_{k=1}^c A_{d}(R, e^{2k\pi i/c} \lambda^{1/c})$
+  with
+  $\lambda^{1/c}$ being a complex $c$th root of $\lambda$;
+Particularly, $B_n^1\rlam = A_n\rlam$.
+The outer product runs over all divisors $d$ of $n$.
 %\end{theorem}
@@
   $\varphi(1) = 1$,
-  $\varphi(3) = 2$ for 1 and 2 are coprime to 3,
-  $\varphi(6) = 2$ for 1 and 5 \cite{hardy}.
+  $\varphi(6) = 2$ for 1 and 5 are coprime to 6 \cite{hardy}.
 %
 By \refeq{xr},
-  $\NB(n) = \deg_\lambda A_n\Rlam$.
+  $\deg_\lambda A_n\lam = \NB(n)$.
 The first few $\NB(n)$ are
@@
 Thus, in order for $A_n\lam$ to accommodate all fixed points of $f^n$,
-  each distinct $d$-cycle with $d|n$
+  each distinct $d$-cycle ($d|n$)
   contributes one and only one zero to $A_n\lam$.
@@
 The most time-consuming step of the algorithm in \refsec{algo}
-is the evaluation of the determinant $A_n\Rlam$ in the characteristic
-equation (\ref{eq:xr}).
-%
-When implemented on a computer,
-it is helpful to use polynomial interpolation:
-we evaluate $A_n\Rlam$ at $\deg_R A_n + 1$ values of $R$,
-e.g., $R = 0, \pm1, \pm2,\ldots$, then piece them together
-to a polynomial.
-%
-By using \refeq{primfac}, we only need $\deg_R P_n + 1$ values
+  is the evaluation of the determinant $A_n(R, \lambda = \pm1)$
+  in the characteristic equation (\ref{eq:xr}).
+%
+In implementation,
+we found it helpful to use polynomial interpolation
+by first evaluating $A_n\Rlam$ at $\deg_R A_n + 1$ values of $R$,
+e.g., $R = 0, \pm1, \pm2,\ldots$, then piecing them together
+into a polynomial of $R$.
+%
+Further, using \refeq{primfac}, we only need $\deg_R P_n + 1$ values
   to directly compute $P_n\Rlam$.
@@
 Here,
-$\deg_R A_n = \sum_{d|n} \varphi(n/d) 2^{d-1}$,
-and $\deg_R P_n = \sum_{d|n} \mu(n/d) 2^{d-1}$
+$\deg_R A_n = n \NB(n)/2$
+and $\deg_R P_n = n \LB(n)/2$
   \cite{mira, stephenson1}.
 %
-The strategy also allows a trivial parallelization.
+%The strategy also allows a trivial parallelization.
+%
+%\begin{figure}[h]
+%  \begin{center}
+%  \begin{minipage}{\linewidth}
+%        \includegraphics[width=\linewidth]{T14b.png}
+%  \end{minipage}%
+%  \end{center}
+%  \caption{\label{fig:T14b}
+%  Coefficients of the 14-cycle bifurcation polynomial in two columns (left to right).
+%  The $k$th line from the top is the coefficient before $(4R)^k$ in base-256.
+%  The digits are shown by the grayscale from white (0) to black (255).
+%  The leading bar before each line is the sign (black: $-$, white: $+$).
+%  }
+%\end{figure}
 
@@
   and computed the polynomials for $n$ up to 14.
+The data are saved on the website http://logperiod.appspot.com.
+%
+%The bifurcation polynomial of the 14-cycle in shown in \reffig{T14b}.
+%
+%The exact polynomials of these maps are generally too large to print on paper,
+%  e.g., the bifurcation polynomial of the 14-cycle
+%    takes about 27 megabytes.
+%
+%The representative $r$ values are listed in \reftab{rval}.
+%
+%Compared with other approaches \cite{hitzl, gordon, bailey2, kk1, hao, hao2}
+%it appeared to be simpler and more transparent,
+%as it only requires the computation of a determinant.
 %
@@
 Thus, these polynomials need to be computed only
-  at the positive half of $r$ values
+  at the positive half of the $r$ values
   in polynomial interpolation.

### 2013-07-09 doc/pc-ijbc.tex
fix an error in the manuscript
document getls.py in the data/cub
improve html
add comments to lsfit.ma

@@
   at the onset and bifurcation points are obtained
-  for $n$ up to 14, 9, and 8,
+  for $n$ up to 14, 9, and 9,
   respectively.
@@
 By the chain rule, we have
-  $\vct J_n (x_1) = \vct J(x_1) \cdots \vct J(x_n)$,
+  $\vct J_n (x_1) = \vct J(x_n) \cdots \vct J(x_1)$,
   where
@@
 %and \reftab{cubpoly} ($\lambda = \pm1$);
-%for larger $n$ up to 8,
+%for larger $n$ up to 9,
 %we have saved the data

### 2013-07-09 doc/pc.tex
modify mknsolv.py
fix an error in the manuscript
document getls.py in the data/cub
improve html
add comments to lsfit.ma

@@
   at the onset and bifurcation points are obtained
-  for $n$ up to 13, 9, and 8,
+  for $n$ up to 14, 9, and 9,
   respectively.
@@
 The algorithm was coded into a Mathematica program,
-which was used to compute the polynomials for $n$ up to 13.
+which was used to compute the polynomials for $n$ up to 14.
 The polynomials for a general $\lambda$
@@
 $13$    & $3.6797024578_{4083}$ &  $3.6797038498_{4095}$  & 315 \\
+$14$    & $3.5972109838_{8052}$ &  $3.5973201609_{8127}$  & 576 \\
+$14'$   & $3.7021549282_{63}$   &  $3.7024116236_{8127}$  & 9   \\
 \hline
@@
 By the chain rule, we have
-  $\vct J^n (x_1) = \vct J^1(x_1) \cdots \vct J^1(x_n)$,
+  $\vct J^n (x_1) = \vct J^1(x_n) \cdots \vct J^1(x_1)$,
   where
@@
 and \reftab{cubpoly} ($\lambda = \pm1$);
-for larger $n$ up to 8,
+for larger $n$ up to 9,
 we have saved the data on the website in \refsec{end}.
@@
 The exact polynomials of these maps are generally too large to print on paper,
-  e.g., the polynomial for the logistic map with $n = 13$
-    takes roughly seven megabytes to write down.
+  e.g., the polynomial for the logistic map with $n = 14$
+    takes roughly 27 megabytes to write down.
 %

### 2013-07-09 data/cub/getls.py

@@ -1,17 +1,22 @@
 #!/usr/bin/env python
 
+# reads nsolv.txt (the output of the mathematica script generated by nsolv.py)
+# print a file that can be appended after crXX.txt
+
+
 import re, sys, os
 
 
-fnin = "inp.txt"
+fnin = "nsolv.txt"
 if len(sys.argv) >= 2:
   fnin = sys.argv[1]
 
 sa = open(fnin).read().strip()
-sa = re.sub(r"\n ", " ", sa)
+sa = re.sub(r"\n ", " ", sa) # joins even lines to preceeding odd lines
 sa = sa.split('\n')
 ls = []
 lsb = []
+#raw_input("%d elements" % len(sa))
 for k in range(len(sa)):
   s = sa[k].strip("{}() ")
   s = re.sub(r"\(", ",", s)
@@ -24,8 +29,8 @@ for k in range(len(sa)):
     #if len(ls) != id:
     #  print "Index mismatch: %s vs %s" % (id, len(ls))
     #print s[0].strip(), item
-    if item.startswith("-"):
-      lsb += [ item[1:] ]
+    #if item.startswith("-"):
+    #  lsb += [ item[1:] ]
   except:
     print "error occured %s" % s
     raise Exception

### 2013-09-02 doc/pc-ijbc.tex
pc-ijbc.tex small changes

@@
 \author{Cheng Zhang}
-%\affiliation{Applied Physics Program and Department of Bioengineering, \
-%Rice University, Houston, TX 77005}
 \address{Applied Physics Program \& Department of Bioengineering,
@@
 The onset and bifurcation points of the $n$-cycles of
-  a polynomial map are located
+  several polynomial maps are located
   through a characteristic equation
-  connecting the cyclic polynomials of the cycle points.
+  connecting cyclic polynomials of the cycle points.
 The polynomials satisfied by the parameters
@@
 %\begin{multicols}{2}
-%\twocolumn
+\twocolumn
 
@@
 After many iterations, there can be three ultimate patterns:
-  (i) a \emph{fixed point} (including infinity),
+  (i) a fixed point (possibly at the infinity),
       %e.g., \reffig{cobweb}(a);
-  (ii) a periodic \emph{cycle},
+  (ii) a periodic cycle,
       %e.g., \reffigs{cobweb}(b)-(e);
@@
 %
-It is stable if a small deviation from $x^*$
-  gets reduced by successive iterations.
-%
-For a differentiable $f$,
-  this is equivalent to $|f'(x^*)| \le 1$
+A stable fixed point requires that a small deviation from $x^*$
+  gets reduced in magnitude after an iteration of \refeq{logmap}.
+%
+Since $f$ is differentiable,
+  the condition is equivalent to $|f'(x^*)| \le 1$
   \cite{strogatz, hao}.
@@
   e.g., $f^3(x) = f(f(f(x)))$.
-Obviously, any $x_k$ in an $n$-cycle of $f$ is a fixed point of $f^n$.
+By definition, any $x_k$ in an $n$-cycle of $f$ is a fixed point of $f^n$
+(but the latter also permits an $x_k$ in a $d$-cycle with $d|n$).
 %
@@
 %
-Thus, a cycle can be classified as stable or unstable
-  according to the corresponding fixed point of $f^n$:
+Thus, the stability of a cycle can be defined
+  according to that of the corresponding fixed point of $f^n$:
   a stable cycle requires
-  $\big| \frac {d} {dx} f^n(x_1) \big| \le 1$,
+  $\big| \frac {d} {dx_1} f^n(x_1) \big| \le 1$,
   or by the chain rule,
@@
 \begin{equation}
-  \Big| f'(x_1) \cdots f'(x_n) \Big| \le 1,
+  \Big| f'(x_n) \cdots f'(x_1) \Big| \le 1,
 \label{eq:der}
@@
   are defined at the loci
-  where $\frac {d} {dx} f^n(x_1)$ reaches $+1$ and $-1$,
+  where $\frac {d} {dx_1} f^n(x_1)$ reaches $+1$ and $-1$,
   respectively \cite{strogatz, hao}.
@@
 %
-The problem has been tackled in previous studies
+The problem has been tackled either by hand for small $n$
 \cite{brown1, brown2, stephenson1, stephenson2, stephenson3,
-  saha, bechhoefer, gordon, burm, zhang, bailey1, bailey2, kk1, lewis}.
-Below we present a simple algorithm to do so.
+      saha, bechhoefer, gordon, burm, zhang}
+or by general computer algebra methods \cite{bailey1, bailey2, kk1, lewis}.
+%
+Below we present a specialized algorithm to do so.
 %
@@
   and
-  $\frac{d}{dx}f^n (x_1) \mp 1 = 0$
+  $\frac{d}{dx_1}f^n (x_1) \mp 1 = 0$
   [\refeq{der}];
@@
 %
-These approaches, however, do not
-  exploit the cyclic structure of \refeqs{logmaps},
-  and can thus be improved by the following alternative.
+These approaches, however, have not fully
+  exploited the cyclic structure of \refeqs{logmaps},
+  and can be improved by the following alternative.
 
@@
   i.e., there is an equation
-  $\sum_q A_{pq} C_q = 0$ for every cyclic polynomial $C_p$.
-%
-The matrix formed by the coefficients $A_{pq}$
+  $\sum_q A_{pq}(R) C_q = 0$ for every cyclic polynomial $C_p$.
+%
+The matrix $\mathbf A(R)$ formed by the coefficients $A_{pq}(R)$
   must have a zero determinant,
@@
 %
-Thus, the zero-determinant condition $|\mathbf A| = 0$ gives
+Thus, the zero-determinant condition $|\mathbf A(R)| = 0$ gives
   the required polynomial equation of $R$.
@@
 %
-But it may not be symmetric
-  (invariant under the exchange of any $x_i$ and $x_{j}$),
-  e.g., $a$ and $b$ are not symmetric,
-  only $a + b$ is.
-
-A cyclic polynomial can be generated by summing over
-  distinct cyclic versions of a simpler polynomial of $x_k$, or a \emph{generator}.
-The generators of the above $a$ and $b$
-  are $x_1 x_2$ and $x_1 x_3$, respectively.
-%For example,
-%$x_1 x_2$ is a generator of $a$;
-%$x_1 x_3$ is that of $b$;
-%and
-%$x_1 x_2 + \frac{1}{2} x_1 x_3$ is that of $a + b$.
-%Note that, according this definition, the coefficient before $x_1 x_3$
-%  is 1 in the second case
-%  for there are only two distinct versions,
-%  but $\frac{1}{2}$ in the third case
-%  for there are four. % distinct versions of the generator.
-%
-%
-%
-Cyclic polynomials
-  generated from monomials of unit coefficient
-  %such as $a$ and $b$, % but not $a + b$ in the above example)
+A cyclic polynomial is not necessarily symmetric,
+  that is, invariant under the exchange of any two $x_i$ and $x_{j}$,
+  e.g., the above $a$ and $b$ are not symmetric, but $a + b$ is.
+
+We call a cyclic polynomial simple
+  if it is equal to the sum of
+  all distinct cyclic versions of
+  a unit-coefficient monomial of $x_k$.
+%
+The monomial is called a generator of the cyclic polynomial.
+%
+For example, the above $a$ and $b$ are simple,
+  and their generators are $x_1 x_2$ and $x_1 x_3$, respectively.
+%
+A simple cyclic polynomial
+  $C_p(\vx{n})$, with $\vx{n} \equiv \{x_1, \ldots, x_n\}$,
 can be labeled as follows.
-If we write the monomial generator as
+%
+If the monomial generator is
   ${x_1}^{e_1} {x_2}^{e_2} \dots {x_n}^{e_n}$,
-  then the sequence $p$ of indices with
-  $e_1$ 1's, $e_2$ 2's, \ldots, $e_n$ $n$'s
-  serves as the label of the cyclic polynomial $C_p(\vx{n})$,
-  where $\vx{n} \equiv \{x_1, \ldots, x_n\}$.
+  we define the label $p$ as the sequence of indices with
+  $e_1$ 1's, $e_2$ 2's, \ldots, $e_n$ $n$'s.
 %
@@
 In case the cyclic polynomial has several generators,
-  we pick the one with the smallest $p$
+  we pick the one with the smallest label $p$
   in the sense of lexicographic order,
-  e.g., we choose $x_1 x_2$ over $x_2 x_3$ for $C_{12}(\vx{n})$,
-  because $12 < 23$.
+  e.g., we choose $x_1 x_2$ over $x_2 x_3$ as the generator of $C_{12}(\vx{n})$,
+  because ``$12$'' $<$ ``$23$.''
 %
@@
 
-A cyclic polynomial is \emph{square-free}
+A cyclic polynomial is square-free
   if it has no square or higher powers of $x_k$,
@@
 $\Pset = \{0, 1, 12, 13, \ldots, 123, 124, \ldots, 12\cdots n\}$,
-and its size by $\NB$.
+and its size by $\NB$ [cf. \refeq{necklace} below for the formula].
 % is the number of square-free cyclic polynomials.
@@
 %
-The set of square-free cyclic polynomials
+The set of the simple square-free cyclic polynomials
   furnishes a basis for expanding cyclic polynomials:
@@
   is a linear combination of
-  the square-free cyclic polynomials $C_p(\vx{n})$:
+  the simple square-free cyclic polynomials $C_p(\vx{n})$:
 \[
@@
   as a combination of the square-free ones.
-At the onset and bifurcation points,
+We will further show below that
+  at the onset and bifurcation points,
   the $\NB$ square-free cyclic polynomials $C_p$ are themselves
-  linearly connected by a characteristic equation.
+  linearly connected by a characteristic equation
+  furnished by \refeq{der},
+  which is the key step of the solution.
 
@@
 
-First, the derivative of $f^n$ is a cyclic polynomial:
+First, the derivative $\frac{d}{dx_1}f^n(x_1)$ is
+  a cyclic polynomial of $\vx{n} = \{x_1, \ldots, x_n\}$:
 %
@@
   \Lambda(\vx{n})
-   = f'(x_1) \dots f'(x_n)
+   = f'(x_n) \dots f'(x_1)
    = (-2)^n x_1 \dots x_n.
@@
 For $n = 1$, % (the fixed point),
-we have two square-free cyclic polynomials
-$\{C_0, C_1\} = \{1, x_1\}$.
-$\Lambda = -2 \, x_1$, and
+we have two simple square-free cyclic polynomials
+$\{C_0, C_1\} = \{1, x_1\}$, with
+$\Lambda = -2 \, x_1$. So
 \[
@@
 So $R = (\lambda^2 -2\lambda)/4$,
-  and the fixed point
-  %begins at $R_a = -1/4$ ($\lambda = +1$), and
-  becomes unstable at $R_b = 3/4$ where $\lambda = -1$.
+  so the fixed point becomes unstable at $R_b = 3/4$ where $\lambda = -1$.
 
@@
 %
-Only the first factor, denoted as $P_2\Rlam = 4-4R -\lambda$,
+Only the first factor $P_2\Rlam \equiv 4-4R -\lambda$
   corresponds to the 2-cycle  (cf. \refsec{primfac}).
@@
 %  in the Appendix.
+%
+In the next section, we show how to systematically eliminate
+the extraneous factors encountered in \refeqs{xr2} and \req{xr4}.
 
@@
 Thus, it encompasses not only the $n$-cycles,
-  but also the shorter $d$-cycles with $d|n$.
+  but also shorter $d$-cycles for divisors $d$ of $n$.
 %
@@
   or the \emph{$n$-cycle polynomial} below,
-  can be easily recognized
-  as the largest factor of $A_n\Rlam$.
+  can be recognized
+  as the largest irreducible factor of $A_n\Rlam$.
 %
 More systematically, we have
-
 %\begin{theorem}
@@
   with
-  $\lambda^{1/c}$ being a complex $c$th root of $\lambda$;
+  $\lambda^{1/c}$ being a complex $c$th root of $\lambda$.
 Particularly, $B_n^1\rlam = A_n\rlam$.
@@
   if $n$ is the product of $k$ distinct primes,
-  or 0 if $n$ is divisible by a square of a prime;
+  or 0 if $n$ is divisible by a square of a prime:
 %Thus,
@@
 Also, $\deg_\lambda B_d^c\rlam = \deg_\lambda A_d\rlam$.
-For convenience, we will drop the $R$ in ``$\Rlam$'' or the arguments entirely below
+For convenience, we will drop the $R$ in ``$\Rlam$'' %or the arguments entirely below
   till the end the next section.
@@
 %there is no irrelevant factor in \refeq{xr1} and
-$P_1 = B_1^1 = A_1
+$P_1(\lambda) = B_1^1(\lambda) = A_1(\lambda)
   = \lambda^2 - 2\,\lambda - 4\,R$.
@@
 %
-we have $P_2 = A_2 / B_1^2 = 4 - 4R - \lambda$.
+we have $P_2(\lambda) = A_2(\lambda) / B_1^2(\lambda) = 4 - 4R - \lambda$.
 %
@@
 %
-$P_4 = A_4 / B_2^2$
+$P_4(\lambda) = A_4(\lambda) / B_2^2(\lambda)$
 indeed yields the sextic factor.
@@
 %\begin{remark}
+The proof of \refeq{primfac} and subsequent discussions
+  are somewhat technical, so
+  the reader may wish to skip the rest of \refsec{logmap}
+  on first reading.
+%
 Since the above derivation works also for complex cycles,
-  each complex $R$ root of the polynomial $P_n\Rlam$ trace
+  each complex $R$ root of the polynomial $P_n\Rlam$ traces
   the outline of a bulb in the inverted Mandelbrot set,
@@
 %
-The proof of \refeq{primfac} and subsequent discussions
-  are somewhat technical, so
-  the reader may wish to skip the rest of \refsec{logmap}
-  on first reading.
 
@@
   each zero of the characteristic polynomial $A_n\lam$
-  corresponds to a distinct $d$-cycle with $d|n$.
+  corresponds to a \emph{distinct} $d$-cycle with $d|n$.
 %\refeq{primfac} then follows from a simple M\"obius inversion.
@@
 
-First, to count the square-free cyclic polynomials,
+First, to count the number of simple square-free cyclic polynomials,
   we notice a one-to-one mapping
-  from the square-free cyclic polynomials
+  from the simple square-free cyclic polynomials
   to the binary necklaces,
 %
-which are nonequivalent binary $0$-$1$ strings.
+which are defined as nonequivalent binary $0$-$1$ strings.
 %
@@
 %
-Now given a square-free cyclic polynomial, if its generator contains $x_k$,
+Now given a simple square-free cyclic polynomial, if its generator contains $x_k$,
   the $k$th character from the right of the necklace is 1,
-  otherwise 0,
-e.g. the above four necklaces correspond to
+  otherwise 0.
+For example, the above four necklaces correspond to
   $C_0$, $C_1$, $C_{12}$ and $C_{123}$, respectively.
@@
 \begin{equation}
-  P_n\lam \equiv \textstyle\prod_l [
-    \Lambda(\vx{n}^{(l)}) - \lambda
-  ],
+  P_n\lam \equiv \textstyle\prod_l \Big[
+    \Lambda\big(\vx{n}^{(l)}\big) - \lambda
+  \Big],
 \notag
@@
 Thus, $\deg_\lambda P_n\lam$
-  is equal to the number $\LB$ of the $n$-cycles,
+  is equal to the number $\LB(n)$ of the $n$-cycles,
   which is given by
@@
 \refeq{primfac} is the special case of $m = 1$,
-for $Q_n^1 = P_n$.
+for $Q_n^1(\lambda) = P_n(\lambda)$.
 
@@
 
-At the onset point,
-  the $n$-cycle polynomial
-  $P_n(R, \lambda = +1)$
-  becomes reducible
-%
-  because of the intersection of an $n$-cycle
-  and a shorter $d$-cycle with $d|n$.
+The $n$-cycle polynomial $P_n(R, \lambda)$
+  is generally irreducible.
+At the onset point $\lambda = +1$,
+  however, $P_n(R, +1)$ can be further factored,
+  cf. the paragraph after \refeq{xr4} for the $n = 4$ case.
+%
+This factorization is due to the intersection with
+  a shorter $d$-cycle with $d|n$.
 %
 The intersection forces the two cycles to share orbit,
- and corresponds to
-  a period-$(n/d)$-tupling \cite{hao}
-  of the shorter $d$-cycle.
-%
-One can show that i) it happens only
+  resulting a period-$(n/d)$-tupling
+  of the shorter $d$-cycle \cite{hao}.
+%
+One can show that i) the period tupling happens only
   at the onset of the longer $n$-cycle, where $\lambda = 1$,
@@
 %
-Further, using \refeq{primfac}, we only need $\deg_R P_n + 1$ values
+According to \refeq{primfac}, we only need $\deg_R P_n + 1$ values
   to directly compute $P_n\Rlam$.
@@
 Here,
-$\deg_R A_n = n \NB(n)/2$
-and $\deg_R P_n = n \LB(n)/2$
+$\deg_R A_n = n \NB(n)/2 = \sum_{d|n} \varphi(n/d) 2^{d-1}$
+and $\deg_R P_n = n \LB(n)/2 = \sum_{d|n} \mu(n/d) 2^{d-1}$
   \cite{mira, stephenson1}.
@@
   outperformed the resultant \cite{burm} and
-  Gr\"obner basis \cite{kk1} methods,
-  by at least two orders of magnitudes.
+  Gr\"obner basis \cite{kk1} methods.
+%  by at least two orders of magnitudes.
 %
@@
   [as $\deg_x f^n(x) = 2^n$],
-  while the matrix in \refeq{xr}
-  is of only $\NB \approx 2^n/n$ [cf. \refeq{necklace}] rows and columns.
+  while the coefficient matrix in \refeq{xr}
+  has only $\NB \approx 2^n/n$ [cf. \refeq{necklace}] rows and columns.
 %Thus, the current algorithm is expected to be faster.
@@
 %
-The second equation of \refeq{henons}
-allows us to replace $y_k$ by $b \, x_{k-1}$,
-  such that we can work with the cyclic polynomials of $x_k$ only.
+We may further eliminate $y_k$ using the second equation of \refeq{henons},
+  and work with the cyclic polynomials of only $x_k$.
 The square-free reduction is now
@@
 %
-which is somewhat simpler for algebraic manipulation.
-%
-Although the boundary polynomials of the two maps are the same,
-  real $\vz{n}$ cycles at negative $r$
-  would be mapped to imaginary $\vx{n}$ cycles.
-%
-This artifact is ignored below.
+which is more suitable for algebraic manipulation.
+%
+This transformation, however, introduces an artifact:
+  a real $\vz{n}$ cycle at a negative $r$
+  corresponds to an imaginary $\vx{n}$ cycle.
+%
+We ignore the artifact below,
+for it does not affect the boundary polynomials.
 %
@@
   $q_{k+1} = a {q_k}^3 + (1-a) q_k$ \cite{may2, brown3, brown4}
-  can be obtained through $q_k = x_k/\sqrt{r-1}, a = 1-r$.
+  can be studied through $q_k = x_k/\sqrt{r-1}, a = 1-r$.
 
@@
 \end{equation}
-however, eliminates only cubes but not squares of $x_k$.
-%
-Consequently, we must extend the basis set of cyclic polynomials
-  from the square-free ones to the cube-free ones,
+however, eliminates only cubes instead of squares of $x_k$.
+%
+Thus, we must extend the basis of simple square-free cyclic polynomials
+  to that of simple cube-free ones
   in listing equations \eqref{eq:xcp}.
@@
 %and \reftab{cubpoly} ($\lambda = \pm1$);
-%for larger $n$ up to 9,
+for $n$ up to 9
 %we have saved the data
@@
 
-%
-The enlarged basis considerably increases the computational cost.
-%
-The antisymmetry
-  $f_r(-x) = -f_r(x)$
-of the map, however, can help alleviate the burden.
-%
-First, we only need cyclic polynomials
-  of \emph{even} % (or odd, see below for the difference)
-  degrees in $\vx{n}$.
+The enlarged basis significantly increases the dimension of
+  the coefficient matrix in \refeq{xr}, hence the computation cost.
+%
+Below we discuss two techniques to alleviate the problem.
+%by exploiting the certain properties of the map.
+%First the antisymmetry: $f_r(-x) = -f_r(x)$
+%
+First, we may include only about half of the simple cyclic polynomials,
+  that is, those of \emph{even} degrees in $\vx{n}$, in the basis.
 %
 This is because \refeq{cubreplace} %contains only linear and cubic terms,
-never reduces even-degree cyclic polynomials
-to odd-degree ones,
+  never reduces even-degree cyclic polynomials to odd-degree ones,
   or the other way around.
 %
-But if applied on odd-degree cyclic polynomials,
-  the algorithm would miss some symmetric cycles (see later).
-%Thus, the matrix $\vct T$ in \refeq{xcp} can be split into two independent blocks
-%  with two separate sets of eigenvalues.
-%
-
+The characteristic polynomial obtained
+  from the basis of even-degree cyclic polynomials
+  is almost the same as that
+  from the basis of odd-degree cyclic polynomials,
+except that the former admits several symmetric cycles
+  that are absent in the latter.
+
+We define a \emph{half-cycle} as a solution of $x_{n+1} = -x_1$,
+  with $n$ being the smallest positive integer that satisfies
+  the relation.
+  %see \reffig{halfcycle} for examples.
+%
+Once iterated, an $n$-half-cycle turns into a symmetric $2n$-cycle:
+$x_1, \ldots, x_{n}, -x_1, \ldots, -x_{n}, x_1$ \cite{hao}.
+%
+In a symmetric $2n$-cycle,
+  an odd-degree cyclic polynomial formed by the $2n$ points
+  is always zero,
+  e.g., $C_1 = x_1 + \dots + x_n - x_1 - \dots - x_n = 0$.
+%
+Thus, the symmetric cycles may escape the characteristic equation
+  from the basis of odd-degree cyclic polynomials,
+  resulting a different $n$-cycle polynomial from
+  the one derived from the basis of even-degree cyclic polynomials.
+
+To be more precise, we first define the $n$-half-cycle polynomial $H_n\rlam$
+  in analogous to $P_n\rlam$.
+%
+It is convenient to exclude the contribution
+  from the trivial fixed point at $x = 0$
+  by defining the \emph{nontrivial} $n$-cycle polynomial
+  $P^*_n\rlam \equiv P_n\rlam/(r-\lambda)^{\delta_{n,1}}$,
+  and %the nontrivial
+  $n$-half-cycle polynomial
+  $H^*_n\rlam \equiv H_n\rlam/(r-\lambda)^{\delta_{n,1}}$.
+%
+%Since a repeated $n$-half-cycle is a $2n$-cycle,
+Dividing the $2n$-cycle polynomial
+  $P^{*}_{2n}(r, \lambda)$
+  by
+  $H^{*}_{n}\big(r, \sqrt \lambda\big)
+   H^{*}_{n}\big(r, -\sqrt \lambda\big)$
+%
+yields the \emph{asymmetric} $n$-cycle polynomial:
+\begin{equation}
+\tilde P^*_n\rlam \equiv
+  %\left.
+  \frac{
+    P^*_n\rlam
+  }
+  %\middle/
+  {
+    \left[
+    \prod_{\sigma = \pm 1}
+      H^*_{n/2}(r, \sigma \sqrt\lambda)
+%      H^*_{n/2}(r, -\sqrt\lambda)
+    \right]^{\even(n)}
+  },
+  %\right.
+\label{eq:Pasym}
+\end{equation}
+%]
+where $\even(n) \equiv 1 - n\bmod 2$.
+%
+One can verify that $\tilde P^*_n\rlam$ coincides with the $n$-cycle polynomial
+  derived from the basis of odd-degree cyclic polynomials.
+%
+
+We now calculate the degrees of the various polynomials
+  to facilitate the polynomial interpolation
+  mentioned in \refsec{end}.
 The number of even-degree cube-free cyclic polynomials
-is equal to that of \emph{even ternary} necklaces
-(each bead assumes 0, 1, or 2, with the total being even),
-which is given by
+is equal to that of \emph{even ternary} necklaces,
+in which each bead represents a number 0, 1, or 2,
+  with the total being even.
+This number is given by
 %
@@
 %
-This is roughly half of the number of all (even and odd) ternary necklaces:
-$N_3(n) = \frac{1}{n} \sum_{d|n} \varphi(n/d) 3^d \approx 2 N_e$.
-%
-%
-Since $N_e(n)$ is the degree in $\lambda$ of $A_n\rlam$,
-  half of the cyclic polynomials and their associated equations are spared.
+%This is roughly half of the number of all (even and odd) ternary necklaces:
+%$N_3(n) = \frac{1}{n} \sum_{d|n} \varphi(n/d) 3^d \approx 2 N_e$.
+%
+%
+%Since $N_e(n)$ is the degree in $\lambda$ of $A_n\rlam$,
+%  half of the cyclic polynomials and their associated equations are spared.
 %
@@
 %
-which is also the number of the $n$-cycles \cite{zeng}.
-%
-To exclude the contribution from the trivial fixed point $x = 0$,
-we define
-  $P^*_n\rlam \equiv P_n\rlam/(r-\lambda)^{\delta_{n,1}}$
+which is also the number of the $n$-cycles \cite{zeng},
+%
 and
@@
 %
-The degrees in $r$ are
+One can further show that the degrees in $r$ are
   $\deg_r A_n\rlam = n N_e(n)$
@@
 
-%\subsection{\label{sec:halfcycle}Half-cycles}
-
-%
-%
-%\begin{figure}[h]
-%  \begin{center}
-%  \begin{minipage}{\linewidth}
-%        \includegraphics[angle=-90, width=\linewidth]{halfcycle.pdf}
-%  \end{minipage}%
-%  \end{center}
-%  \caption{\label{fig:halfcycle}
-%  Half-cycles of the cubic map.}
-%\end{figure}
-%
-%
-
-We call a solution of $x_{n+1} = -x_1$ a \emph{half-cycle}.
-  %see \reffig{halfcycle} for examples.
-The $n$-half-cycle polynomial $H^{*}_n\rlam$
-  can be defined in analogous to $P^*_n\rlam$.
-%
-Once iterated, an $n$-half-cycle turns into a symmetric $2n$-cycle:
-$x_1, \ldots, x_{n}, -x_1, \ldots, -x_{n}, x_1$ \cite{hao}.
-%
-%Since a repeated $n$-half-cycle is a $2n$-cycle,
-Dividing the $2n$-cycle polynomial
-  $P^{*}_{2n}(r, \lambda)$
-  by
-  $H^{*}_{n}\big(r, \sqrt \lambda\big)
-   H^{*}_{n}\big(r, -\sqrt \lambda\big)$
-%
-yields an \emph{asymmetric} $n$-cycle polynomial:
-\begin{equation}
-\hat P^*_n\rlam \equiv
-  %\left.
-  \frac{
-    P^*_n\rlam
-  }
-  %\middle/
-  { \quad
-    \left[
-      H^*_{n/2}(r, \sqrt\lambda)
-      H^*_{n/2}(r, -\sqrt\lambda)
-    \right]^{\even(n)}
-  },
-  %\right.
-\notag
-%\label{eq:Pded}
-\end{equation}
-%
-where $\even(n)=1-\odd(n)$.
-
-Now consider a quadradtic transformation $u_k = {x_k}^2/r$,
+To find the degrees of $\tilde P^*_n\rlam$ and $H^*_n\rlam$,
+  we consider a quadratic transformation $u_k = {x_k}^2/r$,
   which converts \refeq{cubic} to
-  $u_{k+1} = F(u_k) = r^2 u_k (1 - u_k)^2$,
-whose $n$-cycles encompass
-  both $n$-half-cycles and asymmetric $n$-cycles of \refeq{cubic}.
-%
-The nontrivial $n$-cycle polynomial of $F$,
-  which is an even polynomial of $r$,
-  is the product $\hat P^*_n\rlam H^*_n\rlam$.
-%
-From this, we can show that
-  $\deg_\lambda \hat P^*\rlam$ is
+\begin{equation}
+  u_{k+1} = F(u_k) = r^2 u_k (1 - u_k)^2
+\label{eq:uk}
+\end{equation}
+%
+Since the new variable $u_k$ discards the sign of $x_k$,
+  the $n$-cycles of the new map \refeq{uk} encompass
+  both
+  asymmetric $n$-cycles
+  and
+  $n$-half-cycles
+  of the original map \refeq{cubic}.
+%
+We now note $d u_{n+1} / d u_1 = \sigma d x_{n+1} / d x_1$,
+  with $\sigma \equiv x_{n+1}/x_1$ equal to $+1$ and $-1$
+  in the $n$-cycles
+  and
+  $n$-half-cycles of \refeq{cubic}, respectively.
+%
+It follows that the nontrivial
+  % (excluding the fixed point $u_k = 0$)
+  $n$-cycle polynomial of \refeq{uk},
+  whose degree in $\lambda$ is $(1/n)\sum_{cd = n} \mu(c) (3^d - 1)$,
+  %which is an even polynomial of $r$,
+  can be written as
+  $\tilde P^*_n\rlam H^*_n(r, -\lambda)$,
+  up to a sign.
+%
+From this and \refeq{Pasym}, we find that
+  $\deg_\lambda \tilde P^*\rlam$ is equal to
 %
@@
 
-%
-The polynomial $\hat P^*_n\rlam$ is also
-  equivalent to the $n$-cycle polynomial
-  derived from \refeq{xr} using odd-degree cyclic polynomials.
-%
-This is because,
-  in a symmetric $2n$-cycle,
-  an odd-degree cyclic polynomial formed by the $2n$ points
-  is always zero
-  (e.g., $C_1 = x_1 + \dots + x_n - x_1 - \dots - x_n = 0$),
-%
-and thus escapes the characteristic equation.
-%
-%
-
-Finally, we can further reduce the computational cost
+We now turn to the second technique,
+  which reduces the computational cost
   by half for an even $n$.
@@
 %
-Thus, for an odd $n$, any $n$-cycle
+Now for an even $n$,
+  an asymmetric $n$-cycle
   $\vx{n} = \{x_1, x_2, \dots, x_n, x_1\}$
   of $f_r$
-  can be mapped isomorphically to
-  an $n$-half-cycle
-  $\vy{n} = \{-i x_1, i x_2, \dots, - i x_n, i x_1\}$
+  can be isomorphically mapped to
+  an asymmetric $n$-cycle
+  $\vy{n} = \{-i x_1, i x_2, \dots, i x_n, - i x_1\}$
   of $f_{-r}$,
-  with $\Lambda_r(\vx{n}) = -\Lambda_{-r}(\vy{n})$.
-%
-So the $n$-half-cycle and $n$-cycle polynomials
-  are related by
-  $H^*_n(r, \lambda) = P^*_n(-r, -\lambda)$
-  for an odd $n$.
-%
-Similarly, if $n$ is even,
-  the $n$-half-cycles and asymmetric $n$-cycles of $f_r$
-  can be isomorphically mapped to the corresponding ones of $f_{-r}$,
   with $\Lambda_r(\vx{n}) = \Lambda_{-r}(\vy{n})$.
 %
-So $H^*_{n}\rlam$,
-  $\hat P^*_{n}\rlam$,
-  and $A_{n}\rlam$
-  are all even polynomials of $r$
-\big[but $\deg_r P^*_{n}\rlam$ is even only if $4|n$,
-  because if $n/2$ is odd, a symmetric $n$-cycle
-  would be mapped to an $(n/2)$-cycle\big].
-%
-Thus, these polynomials need to be computed only
+So $P^*_n(r, \lambda) = P^*_n(-r, \lambda)$,
+  i.e., the asymmetric $n$-cycle polynomial is an even polynomial of $r$
+  if $n$ is even.
+%
+Similarly, the nontrivial $n$-half-cycle polynomial $H^*_n\rlam$
+  also has an even degree in $r$ if $n$ is even.
+%
+Further, $\deg_r P^*_{n}\rlam$ is also even if $4|n$
+  by \refeq{Pasym},
+  but not so if $n/2$ is odd,
+  because a symmetric $n$-cycle % or an $(n/2)$-half-cycle,
+  $\vx{n} = \{x_1, \dots, x_{n/2}, -x_1, \dots, -x_{n/2}, x_1\}$
+  would be mapped to an $(n/2)$-cycle
+  $\vy{n} = \{-i x_1, \dots, - i x_{n/2}, -i x_1, \dots, -i x_{n/2}, -i x_1\}$,
+  breaking the isomorphism.
+%So, for an odd $m = n/2$, we only have
+%  $H^*_m(r, \lambda) = P^*_{m}(-r, -\lambda)$.
+%
+Thus, the above polynomials need to be evaluated only
   at the positive half of the $r$ values
-  in polynomial interpolation.
+  in the polynomial interpolation.
 %

### 2013-10-04 doc/pc-ijbc.tex
add numerical interpolation of resultant, magma

@@
 %  by at least two orders of magnitudes.
+For the implementation of the resultant method on Magma, we have included a version
+  that uses the polynomial interpolation technique
+  similar to the one described in the previous paragraph.
+This version performed slightly better than the purely symbolic version.
+The small oscillation in the running time is due to that the resultant contains
+  only the $n$th power of the $n$-cycle polynomial $P_n\Rlam$,
+thus, to recover the sign of $P_n\Rlam$ for an even $n$,
+  the number of evaluation points need to be doubled.
 %

### 2013-10-04 prog/magma/mkintmag.py

@@ -35,7 +35,7 @@ print "loaded";
 time f := Interpolation(x, y, 1);
 print "interpolation is done";
 Write("fit.txt", f : Overwrite := true);
-time ff := Factorization(f); 
+time ff := Factorization(f);
 print "factorization is done";
 Write("fit.txt", ff : Overwrite := true);
 """ % (lsx, lsy);

### 2013-10-07 doc/pc-ijbc.tex
small corrections to the text
add a script rmcmt.py to remove comments from pc-ijbc.tex and form IJBCxxx.pdf

--- 2013-09-02 doc/pc-ijbc.tex
@@
 \usepackage{multirow}
-\usepackage{centernot}
+%\usepackage{centernot}
 %\usepackage{hyperref}
@@
 
-%\newcommand{\eq}{}
-%\newcommand{\eqs}{}
 \newcommand{\eq}{Eq.}
@@
 \newcommand{\refthm}[1]{Theorem \ref{thm:#1}}
-\newcommand{\refthms}[1]{Theorems \ref{thm:#1}}
+\newcommand{\reflem}[1]{Lemma \ref{thm:#1}}
 \newcommand{\refsec}[1]{Section \ref{sec:#1}}
 \newcommand{\refsecs}[1]{Sections \ref{sec:#1}}
-\newcommand{\refapd}[1]{Appendix \ref{apd:#1}}
-\newcommand{\reftab}[1]{Table \ref{tab:#1}}
-\newcommand{\reftabs}[1]{Tables \ref{tab:#1}}
 \newcommand{\reffig}[1]{Fig. \ref{fig:#1}}
-\newcommand{\reffigs}[1]{Figs. \ref{fig:#1}}
-
-% ws-ijbc doesn't like the following lines
-%\newtheorem{theorem}{Theorem}
-%\newenvironment{remark}[1][1]%
-%{\par\noindent\textbf{Remark #1.} }{\medskip}
 
@@
 \author{Cheng Zhang}
-\address{Applied Physics Program \& Department of Bioengineering,
+\address{Applied Physics Program and Department of Bioengineering,
 Rice University, Houston, TX 77005, USA}
@@
 %can be conveniently visualized on the cobweb plot,
-%  as shown in \reffig{cobweb}.
 %%
@@
 Since $f$ is differentiable,
-  the condition is equivalent to $|f'(x^*)| \le 1$
+  the condition means $|f'(x^*)| \le 1$
   \cite{strogatz, hao}.
 %
-An $n$-cycle is a sequence $x_1, \dots, x_n$,
+An $n$-cycle is a sequence $x_1, \dots, x_n$
   such that $n$ is the smallest positive integer
-  that satisfies $x_1 = x_{n+1} = f^n(x_1)$,
+  satisfying $x_1 = x_{n+1} = f^n(x_1)$,
   where $f^n$ is the $n$th iterate of $f$,
@@
 By definition, any $x_k$ in an $n$-cycle of $f$ is a fixed point of $f^n$
-(but the latter also permits an $x_k$ in a $d$-cycle with $d|n$).
+(whereas the latter also permits an $x_k$ in any $d$-cycle with $d|n$).
 %
@@
 %
-and a stable cycle corresponds to a window
+and a stable cycle corresponds to a window of $r$
   between the onset point $r_a$ and bifurcation point $r_b$.
@@
   but all $r_a$ are zeros of a polynomial,
-  and all $r_b$ another.
+  and all $r_b$ zeros of another.
 %
@@
 %
-The problem has been tackled either by hand for small $n$
+The problem was tackled either by hand for small $n$
 \cite{brown1, brown2, stephenson1, stephenson2, stephenson3,
@@
 %
-Below we present a specialized algorithm to do so.
+Below we present a specialized algorithm, which offers some performance gain.
 %
@@
 %
-We will solve the cycle boundaries as zeros of some polynomials of $R$,
+We will solve the cycle boundaries as the zeros of some polynomials of $R$,
 and the corresponding polynomials for $r$ can be obtained by $R \rightarrow r(r-2)/4$.
@@
   and then plug the solution into \refeq{der}
-  to get a polynomial equation of $R$.
+  to get an equation of $R$.
 But since \refeqs{logmaps} are nonlinear,
@@
 %
-The matrix $\mathbf A(R)$ formed by the coefficients $A_{pq}(R)$
+The square matrix $\mathbf A(R)$ formed by the coefficients $A_{pq}(R)$
   must have a zero determinant,
@@
 A cyclic polynomial is an invariant
-  under the cycling of variables
+  under the cycling of the variables
   $x_1 \rightarrow x_2, x_2 \rightarrow x_3,
@@
 For example, the above $a$ and $b$ are simple,
-  and their generators are $x_1 x_2$ and $x_1 x_3$, respectively.
+  and $x_1 x_2$ and $x_1 x_3$ are their generators, respectively.
 %
@@
 %
-Below, we may drop %the subscript ``$_n$'' or even the argument
-  ``$(\vx{n})$'' when it is clear.
+Below we may drop %the subscript ``$_n$'' or even the argument
+  ``$(\vx{n})$'' when $n$ is clear from the context.
 In case the cyclic polynomial has several generators,
@@
   $C_{112} = {x_1}^2 x_2 + \cdots$ is not.
-%see \reftab{sqrfreepoly} for more examples.
-The label $p$ of a square-free polynomial
+The label $p$ of a simple square-free cyclic polynomial
   has no repeated index.
-We denote the set of all square-free $p$ by
+We denote the set of labels $p$ of all simple square-free cyclic polynomials by
 $\Pset = \{0, 1, 12, 13, \ldots, 123, 124, \ldots, 12\cdots n\}$,
@@
 The set of the simple square-free cyclic polynomials
-  furnishes a basis for expanding cyclic polynomials:
-
-\begin{theorem}
+  furnishes a basis for expanding an arbitrary cyclic polynomial:
+
+\begin{lemma}
   For the logistic map \refeq{logmaps},
@@
   where $\Pset$ % = \{0, 1, 12, 13, \ldots, 12\dots n\}$ is
-  is the set of indices of all square-free cyclic polynomials,
+  is the set of labels of all simple square-free cyclic polynomials,
   and $f_p(R)$ are polynomials of $R$.
   \label{thm:sqrfree}
-\end{theorem}
+\end{lemma}
 %
@@
   by one.
-Since both the replacement rules and the original polynomial are cyclic,
+Since both the replacement and the original polynomial are cyclic,
   so is the final square-free polynomial.
@@
 
-\refthm{sqrfree}
+\reflem{sqrfree}
   shows that any cyclic polynomial can be expanded
-  as a combination of the square-free ones.
-We will further show below that
+  as a combination of the simple square-free ones.
+The key step of the solution is to further show that
   at the onset and bifurcation points,
-  the $\NB$ square-free cyclic polynomials $C_p$ are themselves
+  the $\NB$ simple square-free cyclic polynomials $C_p$ are themselves
   linearly connected by a characteristic equation
-  furnished by \refeq{der},
-  which is the key step of the solution.
+  furnished by \refeq{der}.
 
@@
 %
-For any square-free cyclic polynomial $C_p(\vx{n})$,
+For any simple square-free cyclic polynomial $C_p(\vx{n})$,
 the product $\Lambda(\vx{n}) \, C_p(\vx{n})$ is also cyclic,
-  and can thus be expanded by \refthm{sqrfree} as
+  and can thus be expanded by \reflem{sqrfree} as
 \begin{equation}
@@
 
-Since a set of homogeneous linear equations
+Since the set of the homogeneous linear equations
   has a nonzero solution of $\vct C$
@@
   At the onset and bifurcation points,
-  the square-free cyclic polynomials $C_p(\vx{n})$
+  the simple square-free cyclic polynomials $C_p(\vx{n})$
   of the cycle points $\vx{n} = \{x_k\}$
@@
 For $n = 1$, % (the fixed point),
-we have two simple square-free cyclic polynomials
+we have only two simple square-free cyclic polynomials
 $\{C_0, C_1\} = \{1, x_1\}$, with
@@
 So $R = (\lambda^2 -2\lambda)/4$,
-  so the fixed point becomes unstable at $R_b = 3/4$ where $\lambda = -1$.
+  and the fixed point becomes unstable at $R_b = 3/4$ where $\lambda = -1$.
 
@@
   = -8 \, R \, C_0 + 4 \, (R + 1) \, C_1$
-by the example after \refthm{sqrfree},
+by the example after \reflem{sqrfree},
 $\Lambda \, C_{12}
@@
 %
-{\small
+%{\small
 \begin{align}
@@
 \end{align}
-}
+%}
 %
@@
 So $R = 1 - \lambda/4$,
-and the onset ($\lambda = +1$) value is $R_a = 3/4$ %($r_a = 3$)
-and the bifurcation ($\lambda = -1$) value is $R_b = 5/4$. %($r_b = 1+\sqrt 6$).
+and the onset ($\lambda = +1$)
+and bifurcation ($\lambda = -1$) values
+are $R_a = 3/4$ and $R_b = 5/4$, respectively.
 %
@@
 %
-\begin{small}
+%\begin{small}
 \begin{align}
@@
     \Big[
-    4096 R^6-12288 R^5 +
-    256 (\lambda + 48) (R^4 - R^3) \notag \\
+      2^{12}(R^6-3 R^5) +
+    2^8 (\lambda + 48) (R^4 - R^3) \notag \\
 & -16 (\lambda + 32)(\lambda - 16) R^2
@@
 \end{align}
-\end{small}
-%
-%
-%
-The first (sextic) factor, denoted as $P_4\Rlam$,
+%\end{small}
+%
+%
+%
+Only the first (sextic) factor, denoted as $P_4\Rlam$,
   is responsible for the 4-cycle.
@@
 %
-In the next section, we show how to systematically eliminate
+In the next section, we give a formula to systematically eliminate
 the extraneous factors encountered in \refeqs{xr2} and \req{xr4}.
@@
   is derived for the fixed points of $f^n$.
-Thus, it encompasses not only the $n$-cycles,
-  but also shorter $d$-cycles for divisors $d$ of $n$.
-%
-Fortunately, the contributions from cycles of different periods
+Thus, it encompasses not just the $n$-cycles,
+  but $d$-cycles for all divisors $d$ of $n$.
+%
+Fortunately, contributions from cycles of different periods
   are separate factors of $A_n\Rlam$.
@@
   $\lambda \rightarrow e^{2\pi i} \lambda$.
-Also, $\deg_\lambda B_d^c\rlam = \deg_\lambda A_d\rlam$.
+Also, $\deg_\lambda B_d^c\Rlam = \deg_\lambda A_d\Rlam$.
 For convenience, we will drop the $R$ in ``$\Rlam$'' %or the arguments entirely below
@@
 Since the above derivation works also for complex cycles,
-  each complex $R$ root of the polynomial $P_n\Rlam$ traces
+  each complex root of $R$ of the polynomial $P_n\Rlam$ traces
   the outline of a bulb in the inverted Mandelbrot set,
@@
   P_n\lam \equiv \textstyle\prod_l \Big[
-    \Lambda\big(\vx{n}^{(l)}\big) - \lambda
+    \Lambda_n\big(\vx{n}^{(l)}\big) - \lambda
   \Big],
@@
 \end{equation}
-where $\vx{n}^{(l)}$ denotes the $l$th $n$-cycle.
+where $\vx{n}^{(l)}$ denotes the $l$th $n$-cycle,
+and subscript $n$ is added to the function
+$\Lambda$ for clarity.
 %
@@
   which is given by
-  \cite{hao, hao2, lutzky}
+  \cite{lutzky, hao, hao2}
 \begin{equation}
@@
 Thus, in order for $A_n\lam$ to accommodate all fixed points of $f^n$,
-  each distinct $d$-cycle ($d|n$)
+  each distinct $d$-cycle with $d|n$
   contributes one and only one zero to $A_n\lam$.
@@
   \begin{equation}
-    A_n\lam = \textstyle\prod_{d|n} Q_d^{n/d}\lam,
+    A_n\lam = \textstyle\prod_{cd = n} Q_d^c\lam,
     \label{eq:prod}
   \end{equation}
-where $Q_d^{n/d}(\lambda) \equiv \prod_l
-  \big[\Lambda\big(\vx{n}^{(l)}\big) - \lambda\big]$
-  with $\vx{n}^{(l)}$ being the $n$ consecutive points
+where $Q_d^c(\lambda) \equiv \prod_l
+  \big[\Lambda_n\big(\vx{n}^{(l)}\big) - \lambda\big]$
+  with $\vx{n}^{(l)}$ being the $n = cd$ consecutive points
   in the $l$th $d$-cycle,
@@
   or the $d$-cycle points $\vx{d}^{(l)}$
-  repeated for $c = n/d$ times:
+  repeated for $c$ times:
 \begin{equation}
@@
 It follows that
-$\Lambda(\vx{n}) = \left[ \Lambda(\vx{d}) \right]^c$.
-%
-By factoring $\Lambda^c - \lambda$
+$\Lambda_n(\vx{n}) = \left[ \Lambda_d(\vx{d}) \right]^c$.
+%
+By factoring ${\Lambda_d}^c - \lambda$
   in terms of the $c$ complex roots of $\lambda$,
@@
       \left[
-          \Lambda\big(\vx{d}^{(l)}\big)
+          \Lambda_d\big(\vx{d}^{(l)}\big)
           -
@@
 %
-This factorization is due to the intersection with
-  a shorter $d$-cycle with $d|n$.
-%
-The intersection forces the two cycles to share orbit,
+This factorization is due to the intersection between
+  the $n$-cycle and a shorter $d$-cycle with $d|n$.
+%
+The intersection forces the two cycles to share the orbit
+  (which can be complex),
   resulting a period-$(n/d)$-tupling
@@
 As a result, the $n$-cycle polynomial $P_n(R, \lambda)$
-  has to accommodate the $d$-cycle one $P_d(R, \lambda')$ as a factor,
+  has to include the $d$-cycle polynomial $P_d(R, \lambda')$ as a factor,
   with $\lambda'$ being a primitive $(n/d)\,$th root of $\lambda = 1$.
@@
 We can thus distinguish \emph{original} cycles
-  from those born out of the above cycle intersection. % period-tupling.
+  from those born out of the above period-tupling.
 %
@@
   from the shorter $d$-cycles with $d|n$
-  contributes a cyclotomic product
+  contribute a cyclotomic product
   $\prod_{(k, c) = 1}
@@
 With these contributions removed,
-  we obtain the polynomial responsible for the original cycles:
+  we obtain the polynomial responsible for
+  the onset of the original $n$-cycles:
   \begin{equation}
@@
 In implementation,
-we found it helpful to use polynomial interpolation
-by first evaluating $A_n\Rlam$ at $\deg_R A_n + 1$ values of $R$,
-e.g., $R = 0, \pm1, \pm2,\ldots$, then piecing them together
+we found it helpful to compute the polynomial by interpolation.
+That is, we first evaluate $A_n\Rlam$ at $\deg_R A_n + 1$ values of $R$,
+e.g., $R = 0, \pm1, \pm2,\ldots$, then piece them together
 into a polynomial of $R$.
 %
-According to \refeq{primfac}, we only need $\deg_R P_n + 1$ values
-  to directly compute $P_n\Rlam$.
+Further, we can directly evaluate $P_n\Rlam$ by \refeq{primfac},
+  and thus reduce the number of evaluations to $\deg_R P_n + 1$.
 %
@@
 %
-%The representative $r$ values are listed in \reftab{rval}.
 %
@@
 %  by at least two orders of magnitudes.
-%
-This is unsurprising,
+For the implementation of the resultant method on Magma, we have included a version
+  that used the polynomial interpolation technique
+  similar to the one described in the previous paragraph.
+This version performed slightly better than the purely symbolic version.
+Since the resultant contains
+  only the $n$th power of the $n$-cycle polynomial $P_n\Rlam$,
+the number of evaluation points needs to be doubled
+  to recover the sign of $P_n\Rlam$ for an even $n$.
+%
+The current method works better than the resultant method
   because the resultant of $f^n(x)-x$ and $\frac{d}{dx}f^n(x)-\lambda$
@@
     measured from a single core of
-    Intel\textsuperscript{\textregistered} 2.5GHz Dual-Core CPU
+    an Intel\textsuperscript{\textregistered} 2.5GHz Dual-Core CPU
   (Mathematica version: 8, Magma version: 2.18-4).
@@
 
+In this and the next sections,
+we discuss two extensions of the above method.
 The H\'enon map \cite{henon}
@@
   Thus, we can expand $\Theta(\vx{n}) \, C_p(\vx{n})$
-  in terms of square-free cyclic polynomials,
+  in terms of the simple square-free cyclic polynomials,
   and then replace the eigenvalue of the coefficient matrix
@@
   at the onset and bifurcation points
-%for some small $n$ are shown in \reftab{cubpolygen} (general $\lambda$)
-%and \reftab{cubpoly} ($\lambda = \pm1$);
 for $n$ up to 9
@@
 %
-%The representative $r$ values are listed in \reftab{crval}.
 %
@@
 %
-First, we may include only about half of the simple cyclic polynomials,
-  that is, those of \emph{even} degrees in $\vx{n}$, in the basis.
+First, we may include in the basis
+  about only half of the simple cyclic polynomials,
+  that is, those of \emph{even} degrees in $\vx{n}$.
 %
 This is because \refeq{cubreplace} %contains only linear and cubic terms,
-  never reduces even-degree cyclic polynomials to odd-degree ones,
+  never reduces even-degree polynomials to odd-degree ones,
   or the other way around.
 %
-The characteristic polynomial obtained
+The characteristic equation obtained
   from the basis of even-degree cyclic polynomials
-  is almost the same as that
-  from the basis of odd-degree cyclic polynomials,
-except that the former admits several symmetric cycles
+  is the same as that
+  from the basis of odd-degree cyclic polynomials for an odd $n$.
+But for an even $n$, the former admits several symmetric cycles
   that are absent in the latter.
+The difference is due to the symmetry of \refeq{cubic},
+  and is discussed below.
 
@@
 %
-One can verify that $\tilde P^*_n\rlam$ coincides with the $n$-cycle polynomial
+One can verify that $\tilde P^*_n\rlam$ is the same as the $n$-cycle polynomial
   derived from the basis of odd-degree cyclic polynomials.
@@
 
-We now calculate the degrees of the various polynomials
-  to facilitate the polynomial interpolation
+We now calculate the degrees of the above polynomials
+  to facilitate the polynomial-interpolation technique
   mentioned in \refsec{end}.
@@
   which reduces the computational cost
-  by half for an even $n$.
-%
-If a sequence $x_k$ satisfies \refeq{cubic},
+  further by half for an even $n$.
+%
+If a sequence $\{x_k\}$ satisfies \refeq{cubic},
   then $y_k \equiv (-)^k i x_k$
@@
 %
-So $P^*_n(r, \lambda) = P^*_n(-r, \lambda)$,
+So $\tilde P^*_n(r, \lambda) = \tilde P^*_n(-r, \lambda)$,
   i.e., the asymmetric $n$-cycle polynomial is an even polynomial of $r$
@@
   at the positive half of the $r$ values
-  in the polynomial interpolation.
+  in the polynomial-interpolation technique.
 %

### 2013-10-07 doc/rmcmt.py

@@ -1,0 +1,18 @@
+#!/usr/bin/env python
+
+# remove comments
+
+fnin = "pc-ijbc.tex"
+fnout = "IJBC-D-12-00312R1.tex"
+
+lines = open(fnin).readlines()
+lines = [s for s in lines if
+    not s.strip().startswith("%") and
+    not s.strip().startswith("\\twocolumn") ]
+for i in range(len(lines)):
+  s = lines[i]
+  pos = s.find("%")
+  if pos >= 0:
+    lines[i] = s[:pos] + "\n"
+open(fnout, "w").writelines(lines)
+

### 2014-01-30 doc/pc-ijbc.tex
small corrections to the papers and web pages

@@
 \begin{abstract}
-The onset and bifurcation points of the $n$-cycles of
+The onset and bifurcation points of $n$-cycles of
   several polynomial maps are located
@@
       saha, bechhoefer, gordon, burm, zhang}
-or by general computer algebra methods \cite{bailey1, bailey2, kk1, lewis}.
+or by general computer-algebraic methods \cite{bailey1, bailey2, kk1, lewis}.
 %
@@
 %
-We will solve the cycle boundaries as the zeros of some polynomials of $R$,
+We will solve the cycle boundaries as zeros of some polynomials of $R$,
 and the corresponding polynomials for $r$ can be obtained by $R \rightarrow r(r-2)/4$.
@@
 The polynomials contain
-  extraneous factors contributed by short $d$-cycles with $d|n$,
+  extraneous factors contributed by shorter $d$-cycles with $d|n$,
   which are also fixed points of $f^n$.
@@
   we pick the one with the smallest label $p$
-  in the sense of lexicographic order,
+  in lexicographic order,
   e.g., we choose $x_1 x_2$ over $x_2 x_3$ as the generator of $C_{12}(\vx{n})$,
@@
 %
-The set of the simple square-free cyclic polynomials
+The set of simple square-free cyclic polynomials
   furnishes a basis for expanding an arbitrary cyclic polynomial:
@@
   we recursively apply \refeq{logmaps} as
-  $x_k^2 \rightarrow R - x_{k+1}$,
+  ${x_k}^2 \rightarrow R - x_{k+1}$,
   until all squares or higher powers of $x_k$ are eliminated.
@@
   shows that any cyclic polynomial can be expanded
-  as a combination of the simple square-free ones.
+  as a combination of simple square-free ones.
 The key step of the solution is to further show that
@@
   $\Lambda(\vx{n})$ equals $\lambda = +1$ ($-1$)
-  at the onset (bifurcation) point,
-  respectively;
+  at the onset (bifurcation) point;
   so \refeq{xcp0}
@@
 For a large $n$,
-  the factor $P_n\Rlam$ of $n$-cycles only,
+  the factor $P_n\Rlam$ of the $n$-cycles only,
   or the \emph{$n$-cycle polynomial} below,
@@
 For convenience, we will drop the $R$ in ``$\Rlam$'' %or the arguments entirely below
-  till the end the next section.
+  till the end of the next section.
 %
@@
 %  by at least two orders of magnitudes.
-For the implementation of the resultant method on Magma, we have included a version
-  that used the polynomial interpolation technique
+In implementing the resultant method on Magma, we have coded a version
+  that used the polynomial-interpolation technique
   similar to the one described in the previous paragraph.
@@
 The enlarged basis significantly increases the dimension of
-  the coefficient matrix in \refeq{xr}, hence the computation cost.
+  the coefficient matrix in \refeq{xr}, hence the computational cost.
 %
@@
 To be more precise, we first define the $n$-half-cycle polynomial $H_n\rlam$
-  in analogous to $P_n\rlam$.
+  analogous to $P_n\rlam$.
 %
@@
 %
-which is also the number of the $n$-cycles \cite{zeng},
+which is also the number of $n$-cycles \cite{zeng},
 %

### 2014-01-30 logperiod/logperiod.py

@@ -1,8 +1,11 @@
 import os, sys
 import webapp2, jinja2
 
+
+
 JINJA_ENVIRONMENT = jinja2.Environment(
     loader=jinja2.FileSystemLoader(os.path.dirname(__file__)))
+
 
 
 class MainPage(webapp2.RequestHandler):

### 2014-02-15 doc/pc.tex
Editing pc.tex

@@
 \usepackage{booktabs}
+%\usepackage{appendix}
+
+% strike-through style
+%http://tex.stackexchange.com/questions/20609/strikeout-in-math-mode
+%\usepackage{cancel} % strike out (cancel) in math mode
 \usepackage{calc}
-\usepackage{cancel} % strike out (cancel) in math mode
-%\usepackage{appendix}
-\begin{document}
+\newsavebox\CBox
+\newcommand\hcancel[2][0.5pt]{%
+  \ifmmode\sbox\CBox{$#2$}\else\sbox\CBox{#2}\fi%
+  \makebox[0pt][l]{\usebox\CBox}%
+  \rule[0.5\ht\CBox-#1/2]{\wd\CBox}{#1}}
 
@@
 
+\begin{document}
+
 \title{Cycles of the logistic map}
@@
 %
-The onset and bifurcation points of the $n$-cycles of
-  a polynomial map are located
+The onset and bifurcation points of $n$-cycles of
+  several polynomial maps are located
   through a characteristic equation
-  connecting the cyclic polynomials of the cycle points.
+  connecting cyclic polynomials of the cycle points.
 The polynomials satisfied by the parameters
@@
   $
-  \big[ \cancel{(R-X)^2 - X}\big]
+  \hcancel{
+    \big[ (R-X)^2 - X \big]
+  }
   (R + X - 1)
@@
 $\begin{aligned}
-\big[\cancel{
-  X^2-(3R+1)X-R^3
-}\big]
+  \hcancel{
+    \big[ X^2-(3R+1)X-R^3 \big]
+  }
   \big[
@@
 $\begin{aligned}
-\big[ \cancel{
-  (R-1)^2 - X
-} \big]
-\big[ \cancel{
-(R^2+X)^2 -(2R+1)^2 X
-} \big]
+  \hcancel{
+    \big[ (R-1)^2 - X \big]
+  }
+  \hcancel{
+    \big[ (R^2+X)^2 -(2R+1)^2 X \big]
+  }
 \big[
@@
 $\begin{aligned}
-&\big[ \cancel{
-  X^2-5 X (R^2+R)-X - R^5
+&
+  \hcancel{
+    \big[ X^2-5 X (R^2+R)-X - R^5 \big]
     %R^5+5 X (R^2+R)-X^2+X
-} \big]
+  }
 \big[
@@
 $\begin{aligned}
-&\big[\cancel {
-  (R-1)^3 + X
-}\big]
-\big[\cancel {
- (R^3 - X)^2 - (3R+1)^2 X
-}\big]
-\big[\cancel {
-\big(R(R-1)^2-1-X\big)^2-(R-2)^2 X
-}\big]
+&
+  \hcancel {
+    \big[ (R-1)^3 + X \big]
+    \big[ (R^3 - X)^2 - (3R+1)^2 X \big]
+    \big[ \big(R(R-1)^2-1-X\big)^2-(R-2)^2 X \big]
+  }
 \big[
@@
 $\begin{aligned}
-&\big[\cancel {
-  -R^7 - 7 X R (R+1)^2 + X^2 - X
-}\big]
+&
+  \hcancel {
+    \big[ -R^7 - 7 X R (R+1)^2 + X^2 - X \big]
+  }
 \big[
@@
 $\NB(n) = (1/n) \sum_{d|n} \varphi(n/d) 2^d$ [\refeq{necklace}]
-is the number of the square-free cyclic polynomials.
-%
-The change of variable $\lambda \rightarrow X$ and
+is the number of the simple square-free cyclic polynomials.
+%
+The change of variable $\lambda \rightarrow 2^n X$ and
   the division by $2^{n \NB(n)}$ make the polynomials more compact.
@@
 &
-$-(\cancel{3-\T})$
+$-\hcancel{ (3 - \T) }$
 &
@@
 -
-\big( \cancel{
-  \T^2-\T+7
-}\big)
+\hcancel{
+  ( \T^2 - \T + 7 )
+}
   (\T-7)
@@
 $\begin{aligned}
- - \T^3 + 8\T^2 - 18\T + 81
+ (- \T^3 + 8\T^2 - 18\T + 81 )
 \end{aligned}$
@@
 $\begin{aligned}
-\big( \cancel{
-  \T - 5
-} \big)
-\big[ \cancel{
-  (\T+1)^2 + 4
-} \big]
+\hcancel{
+  (\T - 5)
+  \big[ (\T+1)^2 + 4 \big]
+}
 \big[
@@
 -
-&\big( \cancel{
-\T^4-\T^3+\T^2+9 \T+31
-} \big)
+&
+\hcancel{
+  ( \T^4-\T^3+\T^2+9 \T+31 )
+}
 \big(
@@
 $\begin{aligned}
-&\big( \cancel{
-\T^2-9 \T+21
-} \big)
-\big( \cancel{
-\T^2+3 \T+3
-} \big)
-\big( \cancel{
-\T^3-8\T^2} \\
-+&\cancel{18\T-81
-} \big)
+&
+\hcancel{
+  (\T^2-9 \T+21)
+  (\T^2+3 \T+3)
+  (\T^3-8\T^2} \\
+&
+  \hcancel{ +18\T-81 ) }
 \big(
@@
 -
-&\big( \cancel{
-\T^6-\T^5+\T^4-\T^3
+&
+\hcancel{
+  (\T^6-\T^5+\T^4-\T^3
 %\T^3(\T^2+1)(\T-1)
- +15T^2+97 \T+127
-} \big) \\
+ +15T^2+97 \T+127)
+} \\
 &\big(
@@
 \\
-13
+
+%13
+%&
+%
+%\begin{minipage}{.48\linewidth}
+%%\vspace{1mm}
+%$\begin{aligned}
+%-&
+%  \hcancel{
+%  \big(
+%    \T^{12}-\T^{11}+\T^{10}
+%    %-\T^9+\T^8-\T^7+\T^6+25 \T^5+703 \T^4+5121 \T^3+14847 \T^2
+%    -\dots
+%    +18433 \T+8191
+%  \big)
+%} \\
+%\big(
+%&\T^{4083}
+% - 8191\T^{4082}
+%+ 33529856 \T^{4081}
+%- \dots \\
+%-&30826655683291995
+%\dots
+%27828275886475354111
+%\big)
+%\end{aligned}$
+%%\vspace{2mm}
+%\end{minipage}
+%
+%&
+%\begin{minipage}{.49\linewidth}
+%%\vspace{1mm}
+%$\begin{aligned}
+%-&\T^{4095} + 8192 \T^{4094} -33538048 \T^{4093} \\
+%+&\dots
+%-7361199006999 % 0439512081857
+%\dots
+%96207964555264\T
+%\\
+%+&29448390363448812
+%%0567620
+%\dots
+%%1182
+%352154556569141249
+%\end{aligned}$
+%\vspace{2mm}
+\\
+14
 &
@@
 $\begin{aligned}
--&\big(\cancel{
-\T^{12}-\T^{11}+\T^{10}
-%-\T^9+\T^8-\T^7+\T^6+25 \T^5+703 \T^4+5121 \T^3+14847 \T^2
--\dots
-+18433 \T+8191
-}\big) \\
+&
+\hcancel{
   \big(
-&\T^{4083}
- - 8191\T^{4082}
-+ 33529856 \T^{4081}
+    \T^6 + 3 \T^5 + 9 \T^4 + 27 \T^3 + 67\T^2 + 89 \T + 43
+  \big)
+} \\
+&\hcancel{
+  \big(
+    \T^6 - 25 \T^5 + 261 \T^4 -1457 \T^3 + 4589 \T^2 - 7737 \T +5461
+  \big)
+} \\
+&\hcancel{
+  \big(
+    -\T^{63} + 128 \T^{62} - \dots
+    + 978621573341\dots3892330031361
+    %+ 97862157334118736160267353892330031361
+  \big)
+} \\
+\big(
+&\T^{8052}
+- 16102\T^{8051}
++ 129605001\T^{8050}
 - \dots \\
--&30826655683291995
++&354338440786337482
 \dots
-27828275886475354111
+91101574588267047561
 \big)
@@
 $\begin{aligned}
--&\T^{4095} + 8192 \T^{4094} -33538048 \T^{4093} \\
+-&\T^{8127} + 16252 \T^{8126} - 132031248 \T^{8125} \\
 +&\dots
--7361199006999 % 0439512081857
++234550833883692
 \dots
-96207964555264\T
-\\
-+&29448390363448812
-%0567620
+06625000000000000\T
+\\
++&
+93826059892194743
 \dots
-%1182
-352154556569141249
+18759918212890625
 \end{aligned}$
-%\vspace{2mm}
+
 \end{minipage}
@@
   $
-  \big[
-  \cancel{\lambda - (2r+3)^2}
-  \big]
+  \hcancel{ [\lambda - (2r+3)^2 ] }
   (\lambda + 2r^2 - 9)
@@
 $\begin{aligned}
-&\big[ \cancel{
+&
+\hcancel{
+  \big[
     (\lambda-8r^4+54r^2+81)^2
     -4 (r^2-9)^2 \lambda
-} \big]
+  \big]
+}
 \,^\ddagger\,
@@
 \\
-8
+%8
+%&
+%$\begin{aligned}
+%&-8192 (r^4+1) (2 r^4-18 r^2+41) \\
+%&(8 r^4-48 r^3+108 r^2-108 r+41) \\
+%&(8 r^4+48 r^3+108 r^2+108 r+41) \dots\\
+%%&(16 r^8-216 r^6+410 r^4+2142 r^2+1681) \\
+%%&(8192 r^{32}-\dots-7984925229121) \\
+%%&(16384 r^{36}-\dots-1310720000000000) \\
+%%&(131072 r^{40}-\dots-13422659310152401)^2 \\
+%&(22016722240\dots14954924752896r^{3108} \\
+%&-\dots-180097954\dots2522413056\times 10^{400})
+%\end{aligned}$
+%&
+%$\begin{aligned}
+%-&(17592186044416 r^{80} +\dots+ \\
+%&144564714832407908402064153121600801) \\
+%&(4841528421712030\dots03048551060078592 r^{3200}\\
+%&-\dots-25263420710\dots173884723232001)
+%\end{aligned}$
+%\\
+9
 &
 $\begin{aligned}
-&-8192 (r^4+1) (2 r^4-18 r^2+41) \\
-&(8 r^4-48 r^3+108 r^2-108 r+41) \\
-&(8 r^4+48 r^3+108 r^2+108 r+41) \dots\\
-%&(16 r^8-216 r^6+410 r^4+2142 r^2+1681) \\
-%&(8192 r^{32}-\dots-7984925229121) \\
-%&(16384 r^{36}-\dots-1310720000000000) \\
-%&(131072 r^{40}-\dots-13422659310152401)^2 \\
-&(22016722240\dots14954924752896r^{3108} \\
-&-\dots-180097954\dots2522413056\times 10^{400})
+&(r^6 + r^3 + 1)
+(64 r^6 - 576 r^5 + 2160 r^4 - 4328 r^3 + 4896 r^2 \\
+&- 2970 r + 757)
+(65536 r^{24} + 196608 r^{23} - \dots + 328385156401) \cdots\\
+&(100257396069318593562485\dots27041918452769115602944 r^{9792} \\
+&+\dots+100777071891533412274\dots669779415034840760335533)
 \end{aligned}$
@@
 $\begin{aligned}
--&(17592186044416 r^{80} +\dots+ \\
-&144564714832407908402064153121600801) \\
-&(4841528421712030\dots03048551060078592 r^{3200}\\
-&-\dots-25263420710\dots173884723232001)
+&4205099973631272542535\dots26734123312649890430976 r^{9828} \\
+&-619915838112722198220\dots14445875084684733448192 r^{9826} \\
+&+\dots+186361973456670282\dots45890460766629265408 r^{3} \\
+&+279917391437103331960\dots789652523552928732020736
 \end{aligned}$
 \\
-\hline
+%
+%
+%
+\hline
+%
+%
+%
 \multicolumn{3}{p{\linewidth}}
@@
 \begin{tabularx}{\linewidth}{
-  >{\hsize=0.5\hsize\centering\arraybackslash}X
+  >{\hsize=0.5\hsize\raggedright\arraybackslash}X
   >{\hsize=1.6\hsize}X
@@
 $8'''$  & $2.2880317545_{32}$   &  $2.2992279397_{3200}$  & 2   \\
+$9$     & $2.3651805877_{9792}$ &  $2.3652188703_{9828}$  & 1092 \\
 \hline

### 2014-10-29 doc/pc-ijbc.tex
add the pdf files

@@
 %
-Thus, the stability of a cycle can be defined
+Thus, the stability of an $n$-cycle can be defined
   according to that of the corresponding fixed point of $f^n$:
-  a stable cycle requires
+  a stable $n$-cycle requires
   $\big| \frac {d} {dx_1} f^n(x_1) \big| \le 1$,
@@
 
-Since the set of the homogeneous linear equations
+Since the set of homogeneous linear equations
   has a nonzero solution of $\vct C$
@@
 %\begin{theorem}
-the number $\NB(n)$ of the square-free cyclic polynomials
+the number $\NB(n)$ of square-free cyclic polynomials
   is equal to the number of length-$n$ binary necklaces,
@@
 Thus, $\deg_\lambda P_n\lam$
-  is equal to the number $\LB(n)$ of the $n$-cycles,
+  is equal to the number $\LB(n)$ of $n$-cycles,
   which is given by
@@
 To find the degrees of $\tilde P^*_n\rlam$ and $H^*_n\rlam$,
-  we consider a quadratic transformation $u_k = {x_k}^2/r$,
+  we consider the quadratic transformation $u_k = {x_k}^2/r$,
   which converts \refeq{cubic} to

### 2014-10-29 doc/pc.tex
add the pdf files

@@
       e.g., \reffig{cobweb}(f).
-We will focus on the first two cases here.
+We only consider the first two cases here.
 
@@
 $\NB(n) = (1/n) \sum_{d|n} \varphi(n/d) 2^d$ [\refeq{necklace}]
-is the number of the simple square-free cyclic polynomials.
+is the number of simple square-free cyclic polynomials.
 %

### 2014-10-29 logperiod/logperiod.py

@@ -19,6 +19,10 @@ class MainPage(webapp2.RequestHandler):
 <ul>
 <li>Cheng Zhang,
 <i>Cycles of the logistic map</i>,
+<a href="http://www.worldscientific.com/doi/abs/10.1142/S0218127414500059">
+International Journal of Bifurcation and Chaos
+<b>24</b> (2014) 1450005</a>;
+also, an earlier preprint:
 <a href="http://arxiv.org/abs/1204.0546">arXiv:1204.0546</a>, 2012.
 </li>
 </ul>''',
@@ -35,7 +39,7 @@ class MainPage(webapp2.RequestHandler):
         </ul></div>''',
 
         'last_update':
-        '<p>Last updated on June 3rd, 2013.',
+        '<p>Last updated on April 2nd, 2014.',
     }
     self.response.write(template.render(template_values))
 
